### 2020-09-21 manuscript/manuscript_ajp_2020.tex
started manuscript from Tiare's overleaf project

\documentclass[prb,preprint]{revtex4} 
% The line above defines the type of LaTeX document.
% Note that AJP uses the same style as Phys. Rev. B (prb).

% The % character begins a comment, which continues to the end of the line.

\usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
\usepackage{amsfonts} % needed for bold Greek, Fraktur, and blackboard bold
\usepackage{graphicx} % needed for figures

\begin{document}

% Be sure to use the \title, \author, \affiliation, and \abstract macros
% to format your title page.  Don't use lower-level macros to  manually
% adjust the fonts and centering.

\title{Molecular dynamics simulation of synchronization in driven particles}
% In a long title you can use \\ to force a line break at a certain location.

\author{Tiare Guerrero}
\email{guer9330@pacificu.edu} % optional
%\altaffiliation[permanent address: ]{101 Main Street, 
%  Anytown, USA} % optional second address
% If there were a second author at the same address, we would put another 
% \author{} statement here.  Don't combine multiple authors in a single
% \author statement.
\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}
% Please provide a full mailing address here.

\author{Danielle McDermott}
\email{mcdermott@pacific.edu}
\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}

% See the REVTeX documentation for more examples of author and affiliation lists.
\date{\today}

\begin{abstract}

  %DM editorial - too many ``we'' statements, not enough emphasize on importance.
  %more detail on the methods?
  %will need to rewrite results/conclusions as we shape the manuscript.

  %What problem did you study and why is it important?
  We study synchronization of interacting particles
  driven by an externally applied force while confined to a narrow channel. 
  %What methods did you use?
  With
  numerical simulations, we control the particle interactions,
  external force and particle environment
  in order to mimick experimental studies of driven colloidal particles
  confined by light-fields.
  We use molecular dynamics simulations to model the particle dynamics,
  using overdamped equations of motion suitable for a viscous suspension
  of microscopic particles.
  %What were your principal results?
  We study 
  particle synchronization under a variety of conditions,
  including static and dynamic patterns formed on
  periodic and quasiperiod substrates,
  kink propagation on these surfaces,
  and the limits of applied force that
  cause the particles to transition to chaotic behavior.
  %What conclusions have you drawn from these results?
  We demonstrate the transition from
  trapped to sliding dynamics in
  quasiperiodic landscapes differs
  from that of a periodic landscape by [TBD],
  and that kinks of high density propagate
  [more/less ?  ] when [what?].
  We include sample code and opportunties
  for students to reproduce our results and propose
  new numerical experiments.

  %Hew to this recipe (MMRC) witlessly
  %1. M—Give the motivation and context
  %2. M—Explain what you did in sufficient
  %detail so the audience knows if your work
  %is relevant and applicable to his or hers
  %3. R—Emphasize your key results
  %4. C—Tell the reader what you think the
  %results mean

\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

\maketitle % title page is now complete

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.

Synchronization is one of the most diverse fundamental physical phenomena. Synchronization has been studied for over three centuries, from Huygens pendulum clocks to the rhythmic beats of the flapping wings in a flock of birds. It is a goal of physicists to discover synchronization in different forms and learn how to control the phenomenon that occurs when weakly coupled competing oscillators adjust rhythms to match each other. A synchronization phenomenon that the physics community is particularly interested in is dynamic phase locking, which occurs when naturally oscillating motions are driven by an external modulation \cite{juniper2015}. Another interest of ours is to study the transition from ordered, synchronized dynamics, to disordered, chaotic dynamics. Chaotic dynamics is the irregular, unpredictable time evolution of nonlinear systems and occurs in mechanical oscillators \cite{chaos}. Here, we analyze the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).

\section{Molecular Dynamics Model}

The simulations use overdamped dynamics with Euler's method in a classical two-dimensional model for particles confined to a periodic potential. With only a few particles in two-dimensions, the simulation runs quickly, making this an appropriate model for undergraduates to explore.

Particles interact by the Yukawa potential.

A single particle has the equation of motion 
\begin{center}
$\eta \vec{v_i} = \vec{F}_{landscape,i} + \sum_{j}^{} \vec{F}_{ij} + \vec{F}_{Drive}(t)$.\\ 
\end{center}
This includes the force of the landscape, inter-particle interactions $\vec{F}_{ij} = - \nabla V(\vec{r}_{ij})$, and a driving force $\vec{F}_{Drive}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y}$, where $\omega = 2 \pi f$. The landscape is a sine function that is position dependent and calculate the landscape force on the particle directly from its location. The driving force does add energy into the system, and some of it is lost. The damping comes from the viscous fluid providing a nonconservative force.

Overdamped dynamics is a common assumption in models of colloid particles. This is an assumption that the suspending fluid is highly viscous and exerts a damping force on the particles equivalent to a linear drag force $F_{drag} = - \eta v$ and the acceleration of the particle is zero. The equation of motion we include makes both assumptions and is rearranged to reflect that. The equation of motion is not integrated for the velocity, instead it provides a direct calculation of the velocity.

In this model the Verlet method is equivalent to the Euler method.  Euler's method is then used to calculate the position. Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method. It is a nice opportunity to teach an extension of a method they know.

\section{MD Simulations}

\subsection{Single particle system}  % In subsection headings, only the first word is capitalized.

We used our model to generate a system, Fig. 1a), where the particle hops between troughs in the energy landscape. In the attached movie, Figure1.mp4, we apply a constant $F_{AC}$ with frequency $f$ then slowly increase $F_{DC}$  to achieve a variety of modes. A mode is a periodic pattern of hops with a constant average particle velocity, $\bar{v}_{y}$ over a range of driving forces $F_{DC}$. In the velocity-force plot in Fig. 1b) $\bar{v}_{y}$ is increasing non-uniformly, with steps, indicating mode locking. A related experiment \cite{juniper2015} revealed the microscopic dynamics of mode locking by driving colloids across a periodic landscape generated by optical tweezers.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.25]{single}
\caption{\textbf{(a)} The particle is driven with a constant $F_{AC}$ and $f$ through a periodic potential landscape where blue are minima and red are maxima in the potential. \textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of the driving force $F_{DC}$. In the animation the magenta dot represents the $\bar{v}_{y}$ at which the particle in Fig. 1a) is moving.}
\end{figure}
\end{center}

\subsection{Multi-particle system}

We also simulated a twenty particle system confined to a narrow channel, as shown in Fig. 2a). The interparticle forces of neighboring particles cause the system to form a buckled chain when the system is annealed. When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion. A driven particle can exhibit mode locking with a well-chosen AC drive and frequency. In the attached movie, Figure2.mp4, we show the complex dynamics of mode locking, where the driven particle leap-frogs past the other particles.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.40]{twenty}
\caption{\textbf{(a)} The orange particle is driven with a constant $F_{AC}$ and $f$ through 19 particles, colored green, confined by a quasi one-dimensional channel. The landscape is colored as in Fig. 1. \textbf{(b)} $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
\end{figure}
\end{center}

\subsection{Kinked system}
\label{DispEqSection}	% You can label sections for reference

\section{Quasiperiodic substrate}
\label{DispEqSection}	% You can label sections for reference

\section{Associated problems}

\section{Conclusion}

\begin{acknowledgments}

We acknowledge Harvey Gould and Jan Tobochnik, who supported our development of this article.  We acknowledge funding from the M.J. Murdock Charitable Trust and the Pacific PRISM program.

\end{acknowledgments}

\begin{thebibliography}{99}
% The numeral (here 99) in curly braces is nominally the number of entries in
% the bibliography. It's supposed to affect the amount of space around the
% numerical labels, so only the number of digits should matter--and even that
% seems to make no discernible difference.

\bibitem{juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, Microscopic dynamics of synchronization in driven colloids. Nat. Commun. 6, 7187 (2015).

%\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

%\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.

%\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
%\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).

%\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.

%\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
%entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
%\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.

%\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.

%\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
%and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
%are incompatible with AJP's editing process.

%\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook} for an excellent overview of math symbols and equations, with examples.

%\bibitem{labelnames} Thinking up a good label name takes a moment, but 
%it's worth the trouble; we strongly advise against using labels like 
%\texttt{eq2}, which become extremely confusing after you decide to add 
%another equation before Eq.~(\ref{deriv}).

%\bibitem{footnotes} You need to process a file twice to get the counters correct.

%\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
%Phys. Today \textbf{42} (10), 9--11 (1989).  
% Note that the issue number (10) in this citation is required, because
% each issue of Physics Today starts over with page 1.  Also note the use of
% an en-dash (--), not a hyphen (-), for the page range.

%\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
%\url{<http://ajp.dickinson.edu>}.

%\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
%\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
% Note that this book is paginated by chapter; "3-10" is a single page reference
% that uses a hyphen, not a range of pages that would us an en-dash (--).

%\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
%a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
%bibliographic references must be incorporated into the manuscript file
%as shown here, at least when you send an editable file for production.

%\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
%Am. J. Phys. \textbf{58} (3), 209--211.  
% The issue number (3) in this citation is optional, because AJP's pagination 
% is by volume.

%\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
%\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
%G. W. F. Drake (AIP Press, New York, 1996), p.~520.

%\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
%Institute of Physics, New York, 1990). Available online at 
%\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
%it have been made out of date by advancing technology, most of this manual 
%is still as useful as ever. Just be sure to follow AJP's specific rules
%whenever they conflict with those in the manual.

\end{thebibliography}

% If your manuscript is conditionally accepted, the editors will ask you to
% submit your editable LaTeX source file.  Before doing so, you should move
% all tables and figure captions to the end, as shown below.  Tables come 
% first, followed by figure captions (with figure inclusions commented-out).
% Figures should be submitted as separate files, collected with the
% LaTeX file into a single .zip archive.

%\newpage   % Start a new page for tables

%\begin{table}[h!]
%\centering
%\caption{Elementary bosons}
%\begin{ruledtabular}
%\begin{tabular}{l c c c c p{5cm}}
%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
%\hline
%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
%\end{tabular}
%\end{ruledtabular}
%\label{bosons}
%\end{table}

%\newpage   % Start a new page for figure captions

%\section*{Figure captions}

%\begin{figure}[h!]
%\centering
%\includegraphics{GasBulbData.eps}   % This line stays commented-out
%\caption{Pressure as a function of temperature for a fixed volume of air.  
%The three data sets are for three different amounts of air in the container. 
%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
%that this is a vector graphic, so it can be viewed at any scale without
%seeing pixels.)}

%\label{gasbulbdata}
%\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=5in]{ThreeSunsets.jpg}   % This line stays commented-out
%\caption{Three overlaid sequences of photos of the setting sun, taken
%near the December solstice (left), September equinox (center), and
%June solstice (right), all from the same location at 41$^\circ$ north
%latitude. The time interval between images in each sequence is approximately
%four minutes.}
%\label{sunsets}
%\end{figure}

\end{document}

### 2020-09-27 manuscript/manuscript_ajp_2020.tex
changed last sentence of abstract
outlined details, started introduction

@@
   We study synchronization of interacting particles
-  driven by an externally applied force while confined to a narrow channel. 
+  confined to a narrow channel 
+  driven by an externally applied force.  
   %What methods did you use?
@@
   [more/less ?  ] when [what?].
-  We include sample code and opportunties
-  for students to reproduce our results and propose
+  We include sample code
+  and exercises for students
+  that include 
+  opportunties
+  to reproduce our results and propose
   new numerical experiments.
@@
 
-\section{Introduction} % Section titles are automatically converted to all-caps.
-% Section numbering is automatic.
+\section{Introduction} %
+%
 
-Synchronization is one of the most diverse fundamental physical phenomena.
-Synchronization has been studied for over three centuries, from Huygens pendulum clocks to the rhythmic beats of the flapping wings in a flock of birds.
-It is a goal of physicists to discover synchronization in different forms and learn how to control the phenomenon that occurs when weakly coupled competing oscillators adjust rhythms to match each other.
-A synchronization phenomenon that the physics community is particularly interested in is dynamic phase locking, which occurs when naturally oscillating motions are driven by an external modulation \cite{juniper2015}.
-Another interest of ours is to study the transition from ordered, synchronized dynamics, to disordered, chaotic dynamics.
-Chaotic dynamics is the irregular, unpredictable time evolution of nonlinear systems and occurs in mechanical oscillators \cite{chaos}.
-Here, we analyze the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
+%Outline
+%describe types of physical systems 
+Numerical simulations of confined, driven particles
+can describe a diverse variety of physical phenomena.
+Particles which interact over long distances
+include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
+Particles which interact over short distances include
+bubble arrays/emulsions [more systems and references].
+
+Narrow channels studies are useful to provide insights 
+of how particles move through geometries
+such as wires, microchannels, and biological systems such as neuron axons and capillaries [more detail and references].
+Stabilized charged particles form patterns
+due to the interplay of the confining environment
+and particle interactions.
+Many such systems execute local oscillations
+about stable points [elaborate].
+%
+An applied external force
+increases the diversity of behaviors,
+and can cause particles to flow in
+a variety of non-linear complex behaviors
+including
+synchronized, aperiod, or chaotic dynamical patterns.
+%
+The presence of a modulating surface
+can modify these patterns in a variety of ways,
+changing the onset of dynamical flows,
+and the overall flow patterns.
+
+Colloidal particles trapped in light fields have proven
+a particularly useful medium for studying these behaviors.%cite 
+The relatively large size of the colloids
+and ease in control has lead to a rich array of 
+experimental results. %THIS IS A TERRIBLE SENTENCE.
+Such studies are considered model systems
+for experimental systems relatively hard to access and visualize,
+such as cold atoms or electron gases. %ELABORATE AND CITE
+
+Synchronization has been studied for over three centuries,
+and is observed in different forms
+from Huygens pendulum clocks
+to the rhythmic beats of the flapping wings in a flock of birds.
+Controlling
+synchronization phenomena in weakly coupled oscillators
+can be achieved with an external driving force
+that causes the syncing of natural oscillation frequencies,
+dynamic phase locking \cite{juniper2015}.
+[useful and interesting because?]
+
+Disordered chaotic dynamics are also possible,
+where irregular, unpredictable time evolution of
+nonlinear systems and occurs in mechanical oscillators \cite{chaos}.
+
+In the following paper we describe
+our molecular dynamics model in Section~\ref{sec:MD},
+including various particle interactions and confining environments.
+In Section~\ref{sec:sync} we
+demonstrate how uniform environments and applied forces
+and create synchronized flow patterns.
+We present these results using standard tools of non-linear oscillators
+such phase diagrams.
+We modify the environment and applied forces
+and show aperiodic, or nearly periodic flow behaviors
+in Section~\ref{sec:quasiperiod}.
+Finally we explore the transition to chaos in 
+in Section~\ref{sec:chaos}.
+
+%Here we model the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
 
 \section{Molecular Dynamics Model}
-
+\label{sec:MD}
 The simulations use overdamped dynamics with Euler's method in a classical two-dimensional model for particles confined to a periodic potential.
@@
 
-\section{MD Simulations}
+%\section{MD Simulations}
 
@@
 
-\subsection{Multi-particle system}
+\subsection{Synchronization in multi-particle systems}
+\label{sec:sync}
 
-We also simulated a twenty particle system confined to a narrow channel, as shown in Fig.
+We simulated a twenty particle system confined to a narrow channel, as shown in Fig.
 2a).
@@
 \section{Quasiperiodic substrate}
-\label{DispEqSection}	% You can label sections for reference
+\label{sec:quasiperiod}	% You can label sections for reference
+
+\section{Chaotic dynamics}
+\label{sec:chaos}	% You can label sections for reference
 

### 2020-10-05 manuscript/manuscript_ajp_2020.tex
updated text in model/simulation

@@
   new numerical experiments.
+  With only a few particles in two-dimensions,
+  the simulation runs quickly,
+  making this an appropriate model for undergraduates to explore.
 
@@
 Numerical simulations of confined, driven particles
-can describe a diverse variety of physical phenomena.
+can be used to model a diverse variety of physical phenomena.
 Particles which interact over long distances
@@
 
-Narrow channels studies are useful to provide insights 
-of how particles move through geometries
-such as wires, microchannels, and biological systems such as neuron axons and capillaries [more detail and references].
+Particles in confined geometries behave differently than free particles.
 Stabilized charged particles form patterns
@@
 and particle interactions.
+Narrow channels studies are useful to provide insights 
+of how particles move through systems 
+such as wires and fluid microchannels.
+Biological systems such as
+neuron axons and capillaries can also be studied
+with these models [more detail and references].
 Many such systems execute local oscillations
@@
 \label{sec:MD}
-The simulations use overdamped dynamics with Euler's method in a classical two-dimensional model for particles confined to a periodic potential.
-With only a few particles in two-dimensions, the simulation runs quickly, making this an appropriate model for undergraduates to explore.
+We use a classical two-dimensional model for 
+studying particle dynamics. 
+Particles are confined in a two-dimensional (2D) 
+simulation of area $A = L \times L$ where $L=36.5$.
+An individual particle has
+position $\vec{r}_i = x_i \hat{i} + y_i \hat{j}$.
+We use periodic boundary conditions
+such that a particle leaving the edges of the system is mapped
+back to a position within the simulation 
+by the rules $x_i+L=x_i$ and $y_i+L=y_i$.
 
-Particles interact by the Yukawa potential.
+Particles are subject to external driving forces
+$F_{Drive}(t)$
+that change as a function of time.
+We create several model light fields,
+creating a landscape of potential minima and maxima
+that modify the local force on a particle as a function of position
+$\vec{F}_{landscape,i} = \vec{F}_{landscape}(\vec{r}_i)$
+These landscape potential are static,
+with fixed minima and maxima
+that are periodic or quasi-periodic,
+as described in Sec.~\ref{sec:results}.
 
+We model particle interactions with
+the Yukawa potential $\vec{F}_{ij} = \nabla V_{ij}(r_{ij})$,
+\begin{equation}
+V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+\end{equation}
+where $r_{ij} = |\vec{r}_i - \vec{r}_j|$.
+This is a
+screened Coulomb potential
+$E_0=2$ scales strength of repulsion
+where $E_0 = k q_1 q_2$  [CHECK scaling/units].
+$\kappa = 1/R_0$ is the screening parameter,
+that screening accounts for the lengthscale at
+which many particle
+interactions and local environment
+that reduces the interaction range of individual particles.
+We fix $R_0$ to be unity in our simulation units.
+
+Particle dynamics are
+modeled with an overdamped
+equation of motion
+integrated with the Verlet method.
 A single particle has the equation of motion 
-\begin{center}
-$\eta \vec{v_i} = \vec{F}_{landscape,i} + \sum_{j}^{} \vec{F}_{ij} + \vec{F}_{Drive}(t)$.\\ 
-\end{center}
-This includes the force of the landscape, inter-particle interactions $\vec{F}_{ij} = - \nabla V(\vec{r}_{ij})$, and a driving force $\vec{F}_{Drive}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y}$, where $\omega = 2 \pi f$.
+\begin{equation}
+\eta \vec{v_i} = \vec{F}_{landscape,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{Drive}(t).
+\end{equation}
+where $\eta = 1$.
+Since $\vec{a}$ is zero,
+the Verlet method simplifies to 
+the Euler method
+$\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)$.
+
+The driving force $\vec{F}_{Drive}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y}$, where frequency is defined as $\omega = 2 \pi f$.
+We modify $f$ and observe the change in dynamics.
 The landscape is a sine function that is position dependent and calculate the landscape force on the particle directly from its location.
@@
 
-%\section{MD Simulations}
+\section{Results}
+\label{sec:results}
 
-\subsection{Single particle system}  % In subsection headings, only the first word is capitalized.
+\subsection{Single particle system}
+% In subsection headings, only the first word is capitalized.
+\label{sec:one}
 
@@
 \subsection{Kinked system}
-\label{DispEqSection}	% You can label sections for reference
+\label{sec:static}	% You can label sections for reference
 

### 2020-10-06 manuscript/manuscript_ajp_2020.tex
equations
added the description for the driving force, starting to trim down the length of the subscripts for paper (rather than talk/proposal).

@@
 An individual particle has
-position $\vec{r}_i = x_i \hat{i} + y_i \hat{j}$.
+position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
 We use periodic boundary conditions
@@
 
-Particles are subject to external driving forces
-$F_{Drive}(t)$
-that change as a function of time.
+Particles are subject an external time-dependent driving force
+$\vec{F}_{D}(t)$
+applied parallel to the y-direction.
+We model this force as
+\begin{equation}
+\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y},
+\end{equation}
+with modifiable parameters including
+a constant component $F_{DC}$,
+and a time dependent component with amplitude $F_{AC}$
+and frequency $\omega = 2 \pi f$.
+The frequency is scaled in time units,
+where [finish].
+ We demonstrate how a single particle (Sec.~\ref{sec:one})
+ and many particles
+ move (Sec.~\ref{sec:twenty})
+ in response to this applied force in a variety of light fields.
+ In Sec.~\ref{sec:kink} we set $F_{DC}$
+ to zero and track the motion
+ of a high density area of a particle chain
+ (i.e. kink dynamics).
+ %The driving force does add energy into the system, and some of it is lost.
+
  We create several model light fields,
@@
  that modify the local force on a particle as a function of position
-$\vec{F}_{landscape,i} = \vec{F}_{landscape}(\vec{r}_i)$
-These landscape potential are static,
+ $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i)$
+ These landscape potential $V(\vec{r}) $are static,
+ generating a conservative force $\vec{F}_l= -\nabla V_l(\vec{r})$
  with fixed minima and maxima
@@
  as described in Sec.~\ref{sec:results}.
+ One example of a periodic light field is
+ that used in Sec.~\ref{sec:kink}
+ where 
+ \begin{equation}
+   V_l = V_0 \cos{(N_p \pi y / L)}
+ \end{equation}
+ where $N_p$ are the number of troughs in the landscape,
+ and $V_0$ is an adjustable parameter
+ to set the depth of the troughs.
 
@@
 integrated with the Verlet method.
+Overdamped dynamics is a common assumption in models of colloidal particles.
+This is an assumption that the suspending fluid is highly viscous
+and exerts a damping force on the particles equivalent
+to a linear drag force.
+%
+The damping comes from a viscous fluid model
+providing a nonconservative force,
+modeled as a linear friction $F_{drag} = -\eta \vec{v}_i$
+sufficient so that
+the acceleration of the particle is zero.
+
+The equation of motion we include makes both assumptions and is rearranged to reflect that.
+The equation of motion is not integrated for the velocity, instead it provides a direct calculation of the velocity.
+
 A single particle has the equation of motion 
 \begin{equation}
-\eta \vec{v_i} = \vec{F}_{landscape,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{Drive}(t).
+\eta \vec{v}_i = \vec{F}_{l,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
 \end{equation}
@@
 
-The driving force $\vec{F}_{Drive}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y}$, where frequency is defined as $\omega = 2 \pi f$.
-We modify $f$ and observe the change in dynamics.
-The landscape is a sine function that is position dependent and calculate the landscape force on the particle directly from its location.
-The driving force does add energy into the system, and some of it is lost.
-The damping comes from the viscous fluid providing a nonconservative force.
-
-Overdamped dynamics is a common assumption in models of colloid particles.
-This is an assumption that the suspending fluid is highly viscous and exerts a damping force on the particles equivalent to a linear drag force $F_{drag} = - \eta v$ and the acceleration of the particle is zero.
-The equation of motion we include makes both assumptions and is rearranged to reflect that.
-The equation of motion is not integrated for the velocity, instead it provides a direct calculation of the velocity.
-
 In this model the Verlet method is equivalent to the Euler method.
 Euler's method is then used to calculate the position.
-Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
-It is a nice opportunity to teach an extension of a method they know.
+%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
 

### 2020-10-14 manuscript/manuscript_ajp_2020.tex
updated script to loop f_dc by fixing sequence

@@
 We use a classical two-dimensional model for 
-studying particle dynamics. 
+studying the dynamics of $N$ interacting particles. 
 Particles are confined in a two-dimensional (2D) 
 simulation of area $A = L \times L$ where $L=36.5$.
-An individual particle has
+An individual particle $i$ has
 position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
@@
  that modify the local force on a particle as a function of position
- $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i)$
- These landscape potential $V(\vec{r}) $are static,
+ $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i).$
+ The landscape potential $V(\vec{r}) $ are static,
  generating a conservative force $\vec{F}_l= -\nabla V_l(\vec{r})$
@@
  We model particle interactions with
- the Yukawa potential $\vec{F}_{ij} = \nabla V_{ij}(r_{ij})$,
+ the Yukawa potential $\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$,
  \begin{equation}
@@
 
-Particle dynamics are
-modeled with an overdamped
+We model the 
+particle dynamics 
+with an overdamped
 equation of motion
 integrated with the Verlet method.
-Overdamped dynamics is a common assumption in models of colloidal particles.
-This is an assumption that the suspending fluid is highly viscous
+Here 
+the suspending fluid is highly viscous
 and exerts a damping force on the particles equivalent
 to a linear drag force.
-%
+%Overdamped dynamics is a common assumption in models of colloidal particles.
+%This is an assumption that 
 The damping comes from a viscous fluid model
@@
 
-The equation of motion we include makes both assumptions and is rearranged to reflect that.
-The equation of motion is not integrated for the velocity, instead it provides a direct calculation of the velocity.
-
 A single particle has the equation of motion 
@@
 where $\eta = 1$.
+The equation of motion provides a direct calculation of the velocity
+of an individual particle from its location in in space.
 Since $\vec{a}$ is zero,
 the Verlet method simplifies to 
-the Euler method
-$\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)$.
-
-In this model the Verlet method is equivalent to the Euler method.
-Euler's method is then used to calculate the position.
-%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
+the Euler method,
+which is used to calculate the position. %Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
+\begin{equation}
+\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t).
+\end{equation}
 
@@
 \label{sec:static}	% You can label sections for reference
+We confine $N$ particles to $N-1$ troughs to create a
+local high density region.
+$F_{DC}/F_{AC} = 1$ [CHECK!]
 

### 2020-10-14 kink_step.sh

@@ -1,0 +1,51 @@
+#Modify DC current and run the MD simulation by modifying the input file Pcw0
+
+DIR1=""
+echo $DIR1
+
+for current in $(seq 0.01 0.1 0.01)
+do
+    echo $current
+    dir0=current_'printf "%1.2" $current'  #check number precision
+    echo $dir0
+
+    #-------------------
+    if [ ! -d $dir0 ]
+    then
+        mkdir $dir0
+    fi
+    #------------------
+
+    cd $dir0
+    pwd
+
+    restart=0
+
+    if [ $restart -eq 0 ] && [ -f *.sh.o* ]
+    then
+	echo "Already run"
+    else
+	#make the new configuration file Pa0
+	sed 's/current 0.2/current '"$current"'/' <../Pcw0> Pcw0
+	cp ../restart_config .
+	#run the physics MD code
+	rm velocity_data/XV_data_t\=00*
+
+	#run the simulation
+	/home/danielle/Research/YDrive_AR/Source_Code/run_wstripe
+
+	#extract velocity info into local file
+	python measuring_kink_velocity.py > avg_kink_vel.txt
+
+	#extract the first line of the file
+	avg=`tail -n 1 avg_kink_vel.txt`
+
+    fi
+
+    cd ../
+
+    #combine all info in a single file
+    echo $current $avg >> avg_kink_vel.txt
+done
+	
+exit

### 2020-10-16 kink_project/kink_step.sh
updated kink measurement

@@ -1,0 +1,54 @@
+#Modify DC current and run the MD simulation by modifying the input file Pcw0
+
+DIR1=""
+echo $DIR1
+
+for current in $(seq 0.001 0.001 0.1)
+do
+    echo $current
+    string_current=`printf "%1.3f" $current`
+    dir0=current_$string_current  #check number precision
+    echo $dir0
+
+    #-------------------
+    if [ ! -d $dir0 ]
+    then
+        mkdir $dir0
+    fi
+    #------------------
+
+    cd $dir0
+    pwd
+
+
+    #make the new configuration file Pa0
+    sed 's/current 0.2/current '"$current"'/' <../Pcw0> Pcw0
+
+    #the high DC currents (current > 0.5) don't need to run
+    #for so long we could include another sed call to reduce the total simulation time
+    #
+    
+    
+    cp ../restart_config .
+    #run the physics MD code
+    rm velocity_data/XV_data_t\=00*
+
+    #run the simulation
+    #/home/danielle/Research/YDrive_AR/Source_Code/substrate_run_wstripe
+
+    #extract velocity info into local file
+    python3 ~/pymodules/animation_code/measuring_kink_velocity.py > avg_kink_vel.txt
+
+    #extract the first line of the file
+    #avg=`tail -n 1 avg_kink_vel.txt`
+
+    #python ~/pymodules/animation_code/channel_colloid_movie_maker.py 
+	
+    cd ../
+    pwd
+
+    #combine all info in a single file
+    echo $current $avg >> avg_kink_vel.txt
+done
+	
+

### 2020-10-16 kink_project/kink_step_analysis.sh

@@ -1,0 +1,37 @@
+#Modify DC current and run the MD simulation by modifying the input file Pcw0
+
+DIR1=""
+echo $DIR1
+
+for current in $(seq 0.001 0.001 0.1)
+do
+    echo $current
+    string_current=`printf "%1.3f" $current`
+    dir0=current_$string_current  #check number precision
+    echo $dir0
+
+    #-------------------
+    if [ ! -d $dir0 ]
+    then
+        mkdir $dir0
+    fi
+    #------------------
+
+    cd $dir0
+    pwd
+
+
+    #extract velocity info into local file
+    python3 ~/pymodules/animation_code/measuring_kink_velocity.py > avg_kink_vel.txt
+
+    #extract the first line of the file
+    avg=`tail -n 1 avg_kink_vel.txt`
+	
+    cd ../
+    pwd
+
+    #combine all info in a single file
+    echo $current $avg >> avg_kink_vel.txt
+done
+	
+

### 2020-10-16 kink_project/measuring_kink_velocity.py

@@ -1,0 +1,1 @@
+/home/danielle/pymodules/animation_code/measuring_kink_velocity.py

### 2020-10-22 manuscript/manuscript_ajp_2020.tex
commented/outline

@@
   %What methods did you use?
-  With
-  numerical simulations, we control the particle interactions,
+  Using 
+  numerical simulations
+  we control the particle interactions,
   external force and particle environment
@@
   confined by light-fields.
-  We use molecular dynamics simulations to model the particle dynamics,
+  The molecular dynamics simulations
+  model the particle dynamics 
   using overdamped equations of motion suitable for a viscous suspension
@@
   %What were your principal results?
-  We study 
+  We observe
   particle synchronization under a variety of conditions,
@@
 %
-
 %Outline
-%describe types of physical systems 
+%-----------------------------------------------------------
+%describe types of physical systems - particle types
 Numerical simulations of confined, driven particles
-can be used to model a diverse variety of physical phenomena.
+can be used to model a variety of physical phenomena.
 Particles which interact over long distances
@@
 
+%-----------------------------------------------
+%environments
 Particles in confined geometries behave differently than free particles.
@@
 about stable points [elaborate].
-%
+%----------------------------------------------------------
+%external forces
 An applied external force
@@
 
+%-------------------------------------------------------------
+%experimental - colloids specifically
 Colloidal particles trapped in light fields have proven
@@
 
+%------------------------------------------------------------------
+%synchronization
 Synchronization has been studied for over three centuries,
@@
 
+%---------------------------------------------------------------
+%kinks and nanofriction
+
+%-----------------------------------------------------------------
+%transition from synchronized to chaotic
 Disordered chaotic dynamics are also possible,
@@
 
+%paper outline
 In the following paper we describe
@@
 We present these results using standard tools of non-linear oscillators
-such phase diagrams.
+such phase diagrams of particle velocity vs. position.
 We modify the environment and applied forces
@@
 position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
-We use periodic boundary conditions
+Particles are subject to
+periodic boundary conditions
 such that a particle leaving the edges of the system is mapped

### 2020-10-22 manuscript/manuscript_ajp_2020.tex
updated section labels, single particle section started, added q1D channel

@@
  as described in Sec.~\ref{sec:results}.
+ In every simulation, we confine
+ the particles to a quasi-one-dimensional geometry
+ using 
+ \begin{equation}
+   V_{q1D} = V_0 \cos{(\pi x / L)}
+ \end{equation}.
+
  One example of a periodic light field is
- that used in Sec.~\ref{sec:kink}
+ %that used in Sec.~\ref{sec:one}
  where 
@@
  where $E_0 = k q_1 q_2$  [CHECK scaling/units].
- $\kappa = 1/R_0$ is the screening parameter,
-that screening accounts for the lengthscale at
+ $\kappa = 1/R_0$ is the screening parameter 
+that accounts for the lengthscale at
 which many particle
@@
 the acceleration of the particle is zero.
+[This model is encountered in Ch. 2 of Taylor's Classical Mechanics....]
 
@@
 The equation of motion provides a direct calculation of the velocity
-of an individual particle from its location in in space.
-Since $\vec{a}$ is zero,
+of an individual particle from its location.
+Since we model the acceleration $\vec{a}$ as zero,
 the Verlet method simplifies to 
@@
 
-We used our model to generate a system, Fig.
-1a), where the particle hops between troughs in the energy landscape.
+We place a single particle in a periodic light field is
+\begin{equation}
+  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
+\end{equation}
+where $N_p=20$ are the number of troughs in the landscape,
+and $V_{0x}=2$ and $V_{0x}=2$.
+
+We used our model to generate a system, Fig.~\ref{fig:1}(a), where the particle hops between troughs in the energy landscape.
 In the attached movie, Figure1.mp4, we apply a constant $F_{AC}$ with frequency $f$ then slowly increase $F_{DC}$  to achieve a variety of modes.
@@
 1a) is moving.}
+\label{fig:1}
 \end{figure}

### 2020-10-22 manuscript/manuscript_ajp_2020.tex
added more single particle

@@
 and $V_{0x}=2$ and $V_{0x}=2$.
+This is illustrated in Fig.~\ref{fig:1}(a) where
+the red regions show local maxima and the blue local minima.
+We apply an external applied force, 
+with 
+a constant $F_{AC}$ with frequency $\omega$ then slowly increase $F_{DC}$.
+The particle hops between troughs in the energy landscape
+when the superposition of $F_{AC}$ and $F_{DC}$ is large enough
+to overcome the barrier height.
+By modifying $F_{DC}$ we 
+achieve a variety of oscillation modes.
+A mode is a periodic pattern of hops
+with a constant average particle velocity, $\bar{v}_{y}$
+over a range of driving forces $F_{DC}$.
+We illustrate mode-locking in 
+the velocity-force plot in Fig.~\ref{fig:1}(b).
+Here $\bar{v}_{y}$ is increasing in non-uniform steps.
+Our simulations reproduce 
+Juniper {\it et al.} \cite{juniper2015}
+which demonstrated
+mode locking in driven colloids on a
+optical periodic landscape.
 
-We used our model to generate a system, Fig.~\ref{fig:1}(a), where the particle hops between troughs in the energy landscape.
-In the attached movie, Figure1.mp4, we apply a constant $F_{AC}$ with frequency $f$ then slowly increase $F_{DC}$  to achieve a variety of modes.
-A mode is a periodic pattern of hops with a constant average particle velocity, $\bar{v}_{y}$ over a range of driving forces $F_{DC}$.
-In the velocity-force plot in Fig.
-1b) $\bar{v}_{y}$ is increasing non-uniformly, with steps, indicating mode locking.
-A related experiment \cite{juniper2015} revealed the microscopic dynamics of mode locking by driving colloids across a periodic landscape generated by optical tweezers.
+We show the dynamics 
+in the attached movie, Figure1.mp4.
 

### 2020-11-03 manuscript/manuscript_ajp_2020.tex
added symbols for talk

@@
 \end{equation}
+
+\begin{equation}
+\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(2 \pi f t)] \hat{y} 
+\end{equation}
+
+\begin{equation}
+F_{DC} = 0.01
+\end{equation}
+
+\begin{equation}
+F_{AC} = 0.2 
+\end{equation}
+
+\begin{equation}
+f = 0.01 
+\end{equation}
+
+\begin{equation}
+\bar{v}_y = n \lambda f
+\end{equation}
+
+\begin{equation}
+\bar{v}_y = \lambda f
+\end{equation}
+
+\begin{equation}
+\lambda = S_Y / 20
+\end{equation}
+
+\begin{equation}
+F_{p} = 0.1
+\end{equation}
+
 with modifiable parameters including
@@
 Here $\bar{v}_{y}$ is increasing in non-uniform steps.
-Our simulations reproduce 
+Our simulations reproduce results presented in 
 Juniper {\it et al.} \cite{juniper2015}
 which demonstrated
-mode locking in driven colloids on a
+mode locking in
+experiments of 
+driven colloids on a
 optical periodic landscape.

### 2020-11-05 manuscript/manuscript_ajp_2020.tex
updated introduction text

@@
   periodic and quasiperiod substrates,
-  kink propagation on these surfaces,
-  and the limits of applied force that
-  cause the particles to transition to chaotic behavior.
+  high density kink propagation.
+  We note 
+  the limits of applied force that
+  cause the dynamics to transition to chaotic behavior.
   %What conclusions have you drawn from these results?
@@
 
+%------------------------------------------------------------------
+%synchronization
+Synchronization is a universal phenomena. 
+Christiaan Huygens is credited with its discovery
+with his 1665 observation of
+in-phase oscillation of pendulum clocks \cite{Pikovsky2003}.  
+Huygens explanation
+that the clocks vibrations are coupled through the supporting
+wall has since been rigorously demonstrated by 20th century
+researchers \cite{Ramirez2016}.
+Examples of synchronization occur
+in many naturally oscillating systems,
+from fireflies syncing with a pulsed LED \cite{},
+to simultaneous flapping of birds wings \cite{},
+to neuronal firing cardiac muscle \cite{} and brain tissue \cite{}.
+
+%phase locking
+Dynamical mode locking is a controlled 
+synchronization phenomena in 
+which an external driving force
+causes the syncing of natural oscillation frequencies
+in
+weakly coupled oscillators.
+Mode locking is often observed in quantum electronic
+devices such as Josephson junctions \cite{}
+and phase-locked loops \cite{}.
+Instead of ohmic current-voltage (IV) relationships,
+such devices exhibit stepped regions
+such as Shapiro steps \cite{} [explain].
+
+Recently studies of colloidal particles confined
+in optical traps have
+been used to examine the microscopic dynamics
+of mode-locking when subject to external driving force \cite{juniper2015}.
+
 %-----------------------------------------------
@@
 of how particles move through systems 
-such as wires and fluid microchannels.
+such as wires and microchannels.
 Biological systems such as
@@
 Colloidal particles trapped in light fields have proven
-a particularly useful medium for studying these behaviors.%cite 
+a particularly useful medium for studying these behaviors.  %cite 
 The relatively large size of the colloids
@@
 such as cold atoms or electron gases. %ELABORATE AND CITE
-
-%------------------------------------------------------------------
-%synchronization
-Synchronization has been studied for over three centuries,
-and is observed in different forms
-from Huygens pendulum clocks
-to the rhythmic beats of the flapping wings in a flock of birds.
-Controlling
-synchronization phenomena in weakly coupled oscillators
-can be achieved with an external driving force
-that causes the syncing of natural oscillation frequencies,
-dynamic phase locking \cite{juniper2015}.
-[useful and interesting because?]
 
@@
 \end{equation}
-
-\begin{equation}
-\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(2 \pi f t)] \hat{y} 
-\end{equation}
-
-\begin{equation}
-F_{DC} = 0.01
-\end{equation}
-
-\begin{equation}
-F_{AC} = 0.2 
-\end{equation}
-
-\begin{equation}
-f = 0.01 
-\end{equation}
-
-\begin{equation}
-\bar{v}_y = n \lambda f
-\end{equation}
-
-\begin{equation}
-\bar{v}_y = \lambda f
-\end{equation}
-
-\begin{equation}
-\lambda = S_Y / 20
-\end{equation}
-
-\begin{equation}
-F_{p} = 0.1
-\end{equation}
-
 with modifiable parameters including
@@
 \end{document}
+
+\begin{equation}
+\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(2 \pi f t)] \hat{y} 
+\end{equation}
+
+\begin{equation}
+F_{DC} = 0.01
+\end{equation}
+
+\begin{equation}
+F_{AC} = 0.2 
+\end{equation}
+
+\begin{equation}
+f = 0.01 
+\end{equation}
+
+\begin{equation}
+\bar{v}_y = n \lambda f
+\end{equation}
+
+\begin{equation}
+\bar{v}_y = \lambda f
+\end{equation}
+
+\begin{equation}
+\lambda = S_Y / 20
+\end{equation}
+
+\begin{equation}
+F_{p} = 0.1
+\end{equation}

### 2020-11-06 code/AJP_code.py
started the single particle code

@@ -1,0 +1,74 @@
+#################################################################
+'''
+Molecular dynamics simulation of synchronization in driven particles
+
+Danielle McDermott
+Tiare Guerrero
+'''
+#################################################################
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+
+##################################################################
+def landscape_potential(V0,y,period):
+    '''
+    '''
+    
+    return V0*np.cos(2*np.pi*y/period)
+
+###################################################################
+def external_drive(F_AC,F_DC,frequency,time):
+    '''
+    '''
+    
+    return F_DC + F_AC*np.sin(2*np.pi*frequency*time)
+
+#####################################################################
+def md_step(y, vy, dt, time):
+    '''
+    '''
+
+    F_AC = 0.05
+    F_DC = 0.05
+    V0 = 0.5
+    period = 1.0
+    frequency = 0.1
+    
+    #integrate the equation of motion \eta v = F^net
+
+    vy += landscape_potential(V0,y,period)
+    vy += external_drive(F_AC,F_DC,frequency,time)
+
+    y += vy*dt
+    
+    return y, vy
+
+
+
+if __name__ == "__main__":
+
+    dt = 0.01
+    y = 0
+    vy = 0
+    time = 0.0
+
+    maxtime=100
+
+    y_data = np.zeros(maxtime)
+    vy_data = np.zeros(maxtime)
+    time_data = np.zeros(maxtime)
+
+    for int_time in range(0,maxtime):
+
+        y, vy = md_step(y, vy, dt, time)
+
+        y_data[int_time] = y
+        vy_data[int_time] = vy
+        time_data[int_time] = time
+
+        time += dt
+
+
+    plt.plot(time_data,y_data)
+    plt.savefig("AJP.png")

### 2020-11-06 manuscript/manuscript_ajp_2020.tex
updated text and section references

@@
 
+%another confinement technique:
+Acoustic tweezers and surface acoustic wave (SAW) \cite{}
+%confines single cells and particles with lower energy than light / lasers
+%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
+%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
+
 %---------------------------------------------------------------
@@
 
+%----------------------------------------------------------------------------
 %paper outline
 In the following paper we describe
-our molecular dynamics model in Section~\ref{sec:MD},
-including various particle interactions and confining environments.
-In Section~\ref{sec:sync} we
-demonstrate how uniform environments and applied forces
-and create synchronized flow patterns.
+our molecular dynamics model in Section~\ref{sec:MD}.
+%including various  and confining environments.
+We include code to simulate
+and visualize the dynamics in this section
+and supplementary material.
+In Section~\ref{sec:results} we summarize
+our results,
+including synchronized motion of a single confined particle
+driven across a periodic landscape in 
+Section~\ref{sec:one} and
+multiple interacting particles
+in Section~\ref{sec:sync}.
+%we
+%demonstrate how uniform environments and applied forces
+%and create synchronized flow patterns.
 We present these results using standard tools of non-linear oscillators
-such phase diagrams of particle velocity vs. position.
-We modify the environment and applied forces
-and show aperiodic, or nearly periodic flow behaviors
-in Section~\ref{sec:quasiperiod}.
-Finally we explore the transition to chaos in 
+such phase diagrams of particle velocity versus position.
+In Section~\ref{sec:quasiperiod},
+we show how an aperiodic landscape modifies the particle dynamics.
+Finally we explore the transition to chaotic dynamics in 
 in Section~\ref{sec:chaos}.
+Our conclusions
+are in Section~\ref{sec:conclusion}. 
+In each section
+we suggest exercises for interested students,
+and summarize our suggestions in Section~\ref{sec:problems}.
 
@@
  as described in Sec.~\ref{sec:results}. 
- In every simulation, we confine
- the particles to a quasi-one-dimensional geometry
- using 
- \begin{equation}
-   V_{q1D} = V_0 \cos{(\pi x / L)}
- \end{equation}.
-
  One example of a periodic light field is
@@
  to set the depth of the troughs.
+
+ In multi-particle simulations, we confine
+ the particles along the x-direction with a
+ quasi-one-dimensional geometry
+ using a periodic function.
+ \begin{equation}
+   V_{q1D} = V_0 \cos{(\pi x / L)}
+ \end{equation}.
+ %%We could also use a Gaussian function.
 
@@
 
-We place a single particle in a periodic light field is
+We place a single particle in a periodic landscape 
 \begin{equation}
+  \label{eq:landscape}
   V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
@@
 the red regions show local maxima and the blue local minima.
+The code for generating
+a two dimensional colored plot
+of the potential landscape
+is calculated by evaluating
+the analytic function in Eq.~\ref{eq:landscape}
+for a grid of values $(x_n,y_n)$.
+%is included in the supplementary material,
+
 We apply an external applied force, 
@@
 \section{Associated problems}
+\label{sec:problems}	% You can label sections for reference
 
 \section{Conclusion}
+\label{sec:conclusion}	% You can label sections for reference
 
@@
 
-We acknowledge Harvey Gould and Jan Tobochnik, who supported our development of this article.  We acknowledge funding from the M.J. Murdock Charitable Trust and the Pacific PRISM program.
+  We acknowledge Harvey Gould and Jan Tobochnik, who supported our development of this article.
+  Charles and Cynthia Reichhardt advised 
+  the project and provided the molecular dynamics code.
+  We acknowledge funding from the M.J. Murdock Charitable Trust
+  and the Pacific Research Institute for Science and Mathematics (PRISM).
 

### 2020-11-06 manuscript/manuscript_ajp_2020.tex
updated MD model

@@
 \usepackage{graphicx} % needed for figures
+\usepackage{pythontex}
 
@@
   including static and dynamic patterns formed on
-  periodic and quasiperiod substrates,
-  high density kink propagation.
-  We note 
-  the limits of applied force that
-  cause the dynamics to transition to chaotic behavior.
+  periodic and quasiperiod substrates
+  and the propagation of 
+  high density kinks.
   %What conclusions have you drawn from these results?
@@
   [more/less ?  ] when [what?].
+  We also explore 
+  the limits of applied force that
+  cause the dynamics to transition to chaotic behavior.
   We include sample code
@@
 multiple interacting particles
-in Section~\ref{sec:sync}.
+in Section~\ref{sec:sync},
+including stationary propagation of high density kinks
+in Sec.~\ref{sec:kink}.
 %we
@@
 Finally we explore the transition to chaotic dynamics in 
-in Section~\ref{sec:chaos}.
-Our conclusions
-are in Section~\ref{sec:conclusion}. 
+Section~\ref{sec:chaos}
+and conclude 
+in Section~\ref{sec:conclusion}. 
 In each section
@@
  and many particles
- move (Sec.~\ref{sec:twenty})
+ move (Sec.~\ref{sec:sync})
  in response to this applied force in a variety of light fields.
@@
  \begin{equation}
-   V_l = V_0 \cos{(N_p \pi y / L)}
+   V_l(y) = V_0 \cos{(N_p \pi y / L)}
  \end{equation}
@@
  In multi-particle simulations, we confine
- the particles along the x-direction with a
+ the particles along the $x-$direction with a
  quasi-one-dimensional geometry
@@
  \begin{equation}
-   V_{q1D} = V_0 \cos{(\pi x / L)}
+   V_{q1D}(x) = V_0 \cos{(\pi x / L)}
  \end{equation}.
@@
 
+The simulation is controlled by a $for()$ loop
+which runs from an intial to maximum $time$ integer.
+Each time step represents a simulation time of $\Delta t=0.001$.
+At each timestep
+we evaluate the net force on each particle as a function of its position
+$\vec{r}_i(t)$
+and then use the equation of motion to move particles
+to an updated position
+$\vec{r}_i(t+\Delta t)$.
+%
 We model the 
@@
 providing a nonconservative force,
-modeled as a linear friction $F_{drag} = -\eta \vec{v}_i$
+modeled as a linear friction $\vec{F}_{drag} = -\eta \vec{v}_i$
 sufficient so that
 the acceleration of the particle is zero.
-[This model is encountered in Ch. 2 of Taylor's Classical Mechanics....]
+Such a model is appropriate when the particles
+are small and the viscosity is high [finish... reference...]
+%[This model is encountered in Ch. 2 of Taylor's Classical Mechanics....]
 
@@
 the Euler method,
-which is used to calculate the position. %Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
+which is used to calculate the position at subsequent time steps.
+%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
 \begin{equation}
@@
 
-We place a single particle in a periodic landscape 
+We place a single particle in a periodic landscape with
+corrugations along the y-direction 
 \begin{equation}
   \label{eq:landscape}
-  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
+  V_l(y) = V_{0y} \cos{(N_p \pi y / L)} 
 \end{equation}
@@
 with 
-a constant $F_{AC}$ with frequency $\omega$ then slowly increase $F_{DC}$.
+a constant $F_{AC}$ with frequency $\omega = 2\pi f$
+then slowly increase $F_{DC}$.
 The particle hops between troughs in the energy landscape
@@
 the velocity-force plot in Fig.~\ref{fig:1}(b).
-Here $\bar{v}_{y}$ is increasing in non-uniform steps.
+Here $\bar{v}_{y}$ is increasing in non-uniform steps,
+with a quantized height of
+$\bar{v}_{y} = n \lambda f$,
+where $n$ is an integer,
+$\lambda = S_Y/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
+of the landscape,
+and $f = 0.01$ cycles per time unit.
+
 Our simulations reproduce results presented in 
@@
 
-We show the dynamics 
-in the attached movie, Figure1.mp4.
+We illustrate the hopping pattern in Fig.~\ref{fig:1}(c)
+and 
+show the dynamics 
+in supplementary materials \cite{supp1}.
 
@@
 
-We simulated a twenty particle system confined to a narrow channel, as shown in Fig.
-2a).
+We simulated a twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
+with a single period.
+\begin{equation}
+  \label{eq:channel}
+  V_l(x) = V_{0x} \cos{(\pi x/L)}
+\end{equation}
+where the trough heights is larger  $V_{0x}$,
+and the associated force
+\begin{equation}
+\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
+\end{equation}
+restores particles to the center of a long narrow region of the simulation.
+This is shown in Fig.~\ref{fig:2}(a)
+where red regions are high potential
+and blue regions are low potential.
+
+The initial configuration of the system is shown i
+Fig.~\ref{fig:2}(a).  
+We annealed the system into a ground-state configuration
+by raising the system to a high temperature $T$,
+and slowly lowering the temperature in steps of $dT=-0.01$
+until the particles form a buckled chain due to the
+competition between particle repulsion and channel confinement.
+
 The interparticle forces of neighboring particles cause the system to form a buckled chain when the system is annealed.
+
 When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion.
@@
 \subsection{Kinked system}
-\label{sec:static}	% You can label sections for reference
+\label{sec:kink}	% You can label sections for reference
 We confine $N$ particles to $N-1$ troughs to create a
@@
 \bibitem{juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, Microscopic dynamics of synchronization in driven colloids. Nat. Commun. 6, 7187 (2015).
+
+\bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
 
@@
 \end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Supplementary Materials}
+
+\subsection{Gridded Contour Plot of landscape}
+%code is located in
+%~/pymodules/animation_code/channel_colloid_movie_maker.py
+
+%\begin{pyverbatim}
+##########################################################
+#ADD CONTOUR PLOT
+##########################################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color in the quasi1D potential to contain 
+    the particles in a trough.  
+    Can also add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #assuming Tiare's trough system, so we won't want to cover the entire range
+    X = np.arange(0, L/2.0, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 2.0 # set by what "looks good"
+    Z = Z_mag*np.sin(2*np.pi*X/L)
+    if corrugated == True:
+        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
+
+    cmap=cm.coolwarm_r
+
+    #alphs is the degree of transparency, again, set by what looks good.
+    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
+
+    #ax1.set_xlim(15,20)
+    #ax1.set_ylim(15,20)
+
+    #ax1.set_xlabel(r"$X$")
+    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
+
+    #ax1.set_xticks([])
+    #ax1.set_yticks([])
+    return
+ %   \end{pyverbatim}

### 2020-11-06 manuscript/manuscript_ajp_2020.tex
updated figure captions

@@
 \includegraphics[scale=.25]{single}
-\caption{\textbf{(a)} The particle is driven with a constant $F_{AC}$ and $f$ through a periodic potential landscape where blue are minima and red are maxima in the potential.
-\textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of the driving force $F_{DC}$.
-In the animation the magenta dot represents the $\bar{v}_{y}$ at which the particle in Fig.
-1a) is moving.}
+\caption{\textbf{(a)} The particle is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through a periodic spatial potential landscape.
+The landscape is represented with a colormap where blue are minima and red are maxima in the potential.
+\textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of a constant driving force $F_{DC}$.
+In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\bar{v}_{y}$ at which the particle in Fig.
+1(a) is moving.}
 \label{fig:1}
@@
 restores particles to the center of a long narrow region of the simulation.
-This is shown in Fig.~\ref{fig:2}(a)
+The landscape is illustrated in Fig.~\ref{fig:2}(a)
 where red regions are high potential
@@
 
-The initial configuration of the system is shown i
+The initial configuration of the system is shown in 
 Fig.~\ref{fig:2}(a).  
@@
 and slowly lowering the temperature in steps of $dT=-0.01$
-until the particles form a buckled chain due to the
+until the particles form a buckled chain in the low region of the channel
+due to the
 competition between particle repulsion and channel confinement.
-
-The interparticle forces of neighboring particles cause the system to form a buckled chain when the system is annealed.
+The interparticle forces between neighboring particles
+cause the system to form a buckled chain. % when the system is annealed.
+The molecular dynamics of simulated annealing
+is described in Ref.~\ref{},
+and presented simulations begin with particle configurations
+that result from the annealing process,
+as listed in Appendix [ref] and available in supplementary material.
 
@@
 \includegraphics[scale=.40]{twenty}
-\caption{\textbf{(a)} The orange particle is driven with a constant $F_{AC}$ and $f$ through 19 particles, colored green, confined by a quasi one-dimensional channel.
-The landscape is colored as in Fig.
-1.
-\textbf{(b)} $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
+\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
+The landscape is colored as in Fig.~\ref{fig1}(a).
+\textbf{(b)} Average $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
+\label{fig:2}
 \end{figure}

### 2020-11-10 manuscript/manuscript_ajp_2020.tex
updated text with unit definitions

@@
 %Outline
-%-----------------------------------------------------------
-%describe types of physical systems - particle types
-Numerical simulations of confined, driven particles
-can be used to model a variety of physical phenomena.
-Particles which interact over long distances
-include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
-Particles which interact over short distances include
-bubble arrays/emulsions [more systems and references].
-
 %------------------------------------------------------------------
-%synchronization
-Synchronization is a universal phenomena. 
-Christiaan Huygens is credited with its discovery
-with his 1665 observation of
-in-phase oscillation of pendulum clocks \cite{Pikovsky2003}.  
-Huygens explanation
-that the clocks vibrations are coupled through the supporting
-wall has since been rigorously demonstrated by 20th century
-researchers \cite{Ramirez2016}.
+%synchronization = widest audience possible
+Synchronization is a universal phenomena
+that can be modeled with numerical studies of confined,
+driven particles.
+Christiaan Huygens 1665 observation of
+in-phase oscillation of pendulum clocks \cite{Pikovsky2003}
+[has been adapted into many useful technologies...]
+%Huygens explanation
+%that the clocks vibrations are coupled through the supporting
+%wall has since been rigorously demonstrated by 20th century
+%researchers \cite{Ramirez2016}.
 Examples of synchronization occur
 in many naturally oscillating systems,
-from fireflies syncing with a pulsed LED \cite{},
+from fireflies signaling in time with a with a pulsed LED \cite{},
 to simultaneous flapping of birds wings \cite{},
-to neuronal firing cardiac muscle \cite{} and brain tissue \cite{}.
+to neuronal firing in cardiac muscle \cite{} and brain tissue \cite{}.
 
@@
 which an external driving force
-causes the syncing of natural oscillation frequencies
-in
-weakly coupled oscillators.
+causes
+%the natural oscillation frequencies
+%in
+weakly coupled oscillators to come into phase.
 Mode locking is often observed in quantum electronic
 devices such as Josephson junctions \cite{}
-and phase-locked loops \cite{}.
+and phase-locked current loops \cite{}.
 Instead of ohmic current-voltage (IV) relationships,
@@
 
+%-----------------------------------------------------------
+%describe types of physical systems - particle types
+Numerical simulations of confined, driven particles
+can be used to model a variety of physical phenomena.
+Particles which interact over long distances
+include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
+Particles which interact over short distances include
+bubble arrays/emulsions [more systems and references].
+
 %----------------------------------------------------------------------------
@@
 we suggest exercises for interested students,
-and summarize our suggestions in Section~\ref{sec:problems}.
+as summarized in Section~\ref{sec:problems}.
 
@@
 Particles are confined in a two-dimensional (2D) 
-simulation of area $A = L \times L$ where $L=36.5$.
+simulation of area $A = L \times L$ where $L=36.5 a_0$
+where $a_0$ is a dimensionless unit of length.
 An individual particle $i$ has
@@
 by the rules $x_i+L=x_i$ and $y_i+L=y_i$.
+We summarize unit units of our simulated variables in Table ~\ref{tab:1}.
+
+\begin{table}[h!]
+\centering
+\caption{Simulation units defined in the code.}
+\begin{ruledtabular}
+\begin{tabular}{c c p{5cm}}
+Quantity & Unit \\
+\hline
+time &  $\eta / E_0$ \\
+length &  $a_0$ \\
+velocity &  \\
+force & $E_0 / a_0$\\
+electric potential & V(r_{ij} = q^2 E_0/r_{ij}), $E_0 = Z^*^2/()4\pi \epsilon \epsilon_0 a_0$ \\
+charge/dimensionless interaction strength $q$ \\
+effective colloidal charge & $Z^*$ \\
+solvent dielectic constant & $\epsilon$ \\
+\end{tabular}
+\end{ruledtabular}
+\label{tab:1}
+\end{table}
 

### 2020-11-12 manuscript/manuscript_ajp_2020.tex
edited language, rearranged intro.

@@
   confined to a narrow channel 
-  driven by an externally applied force.  
+  driven by an external applied force.  
   %What methods did you use?
@@
   we control the particle interactions,
-  external force and particle environment
+  external force and environment
   in order to mimick experimental studies of driven colloidal particles
@@
 driven particles.
-Christiaan Huygens 1665 observation of
-in-phase oscillation of pendulum clocks \cite{Pikovsky2003}
-[has been adapted into many useful technologies...]
-%Huygens explanation
-%that the clocks vibrations are coupled through the supporting
-%wall has since been rigorously demonstrated by 20th century
-%researchers \cite{Ramirez2016}.
+%Christiaan Huygens 
+%[has been adapted into many useful technologies...]
 Examples of synchronization occur
 in many naturally oscillating systems,
-from fireflies signaling in time with a with a pulsed LED \cite{},
+from Huygens 1665 observation of
+in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
+to fireflies signaling in time with a with a pulsed LED \cite{},
 to simultaneous flapping of birds wings \cite{},
@@
 of mode-locking when subject to external driving force \cite{juniper2015}.
+[this is important because...]
+%experimental - colloids specifically
+Colloidal particles trapped in light fields have proven
+a particularly useful medium for studying complex dynamical behaviors.  %cite 
+The relatively large size of the colloids
+and ease in control has lead to a rich array of 
+experimental results. %THIS IS A TERRIBLE SENTENCE.
+Such studies are considered model systems
+for experimental systems relatively hard to access and visualize,
+such as cold atoms or electron gases. %ELABORATE AND CITE
+
+%-----------------------------------------------------------
+%particle interaction types
+Particles which interact over long distances
+include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
+Particles which interact over short distances include
+bubble arrays/emulsions [more systems and references].
 
@@
 %----------------------------------------------------------
-%external forces
-An applied external force
-increases the diversity of behaviors,
-and can cause particles to flow in
-a variety of non-linear complex behaviors
-including
-synchronized, aperiod, or chaotic dynamical patterns.
-%
 The presence of a modulating surface
@@
 and the overall flow patterns.
+%
+
+%external forces
+It is often useful to study the
+dynamics of particles subject to 
+an applied external force,
+for instance the flow of charges in a conductor,
+or cells responding to a chemical gradient.
+The external force 
+increases the diversity of dynamical behaviors,
+and can cause particles to flow in
+a variety of non-linear complex patterns
+that may be 
+synchronized.
+Disordered chaotic dynamics are also possible,
+where irregular, unpredictable time evolution of
+nonlinear systems and occurs in mechanical oscillators \cite{chaos}.
 
 %-------------------------------------------------------------
-%experimental - colloids specifically
-Colloidal particles trapped in light fields have proven
-a particularly useful medium for studying these behaviors.  %cite 
-The relatively large size of the colloids
-and ease in control has lead to a rich array of 
-experimental results. %THIS IS A TERRIBLE SENTENCE.
-Such studies are considered model systems
-for experimental systems relatively hard to access and visualize,
-such as cold atoms or electron gases. %ELABORATE AND CITE
 
 %another confinement technique:
-Acoustic tweezers and surface acoustic wave (SAW) \cite{}
+%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
 %confines single cells and particles with lower energy than light / lasers
@@
 %transition from synchronized to chaotic
-Disordered chaotic dynamics are also possible,
-where irregular, unpredictable time evolution of
-nonlinear systems and occurs in mechanical oscillators \cite{chaos}.
 
-%-----------------------------------------------------------
 %describe types of physical systems - particle types
-Numerical simulations of confined, driven particles
-can be used to model a variety of physical phenomena.
-Particles which interact over long distances
-include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
-Particles which interact over short distances include
-bubble arrays/emulsions [more systems and references].
-
+In this work,
+we perform 
+numerical simulations of confined, driven particles
+to model a variety of physical phenomena.
 %----------------------------------------------------------------------------
@@
 back to a position within the simulation 
-by the rules $x_i+L=x_i$ and $y_i+L=y_i$.
-We summarize unit units of our simulated variables in Table ~\ref{tab:1}.
+by $x_i+L=x_i$ and $y_i+L=y_i$.
+We summarize the units of the simulated variables in Table ~\ref{tab:1}.
 
@@
 \hline
-time &  $\eta / E_0$ \\
 length &  $a_0$ \\
-velocity &  \\
-force & $E_0 / a_0$\\
-electric potential & V(r_{ij} = q^2 E_0/r_{ij}), $E_0 = Z^*^2/()4\pi \epsilon \epsilon_0 a_0$ \\
-charge/dimensionless interaction strength $q$ \\
+viscosity/damping constant & $\eta$ \\
+dimensionless interaction strength & $q$ \\
 effective colloidal charge & $Z^*$ \\
 solvent dielectic constant & $\epsilon$ \\
+time &  $\eta / E_0$ \\
+velocity &  $\eta E_0 / a_0$ \\
+force & $E_0 / a_0$\\
+electric potential & $V(r_{ij}) = q^2 E_0/r_{ij}$ \\
+energy & $E_0 = {Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
 \end{tabular}
@@
 and frequency $\omega = 2 \pi f$.
-The frequency is scaled in time units,
-where [finish].
- We demonstrate how a single particle (Sec.~\ref{sec:one})
- and many particles
- move (Sec.~\ref{sec:sync})
- in response to this applied force in a variety of light fields.
- In Sec.~\ref{sec:kink} we set $F_{DC}$
- to zero and track the motion
- of a high density area of a particle chain
- (i.e. kink dynamics).
- %The driving force does add energy into the system, and some of it is lost.
+%The frequency is scaled in time units,
+%where [finish].
 
- We create several model light fields,
- creating a landscape of potential minima and maxima
- that modify the local force on a particle as a function of position
- $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i).$
- The landscape potential $V(\vec{r}) $ are static,
- generating a conservative force $\vec{F}_l= -\nabla V_l(\vec{r})$
+ We model several enviroments
+ %creating a landscape of potential minima and maxima
+ %that modify the force on a particle as a function of position
+ $\vec{F}_{l}(\vec{r}) = -\nabla V_l(\vec{r}).$
+ The landscape potential $V(\vec{r}) $ are static 
  with fixed minima and maxima
@@
  as described in Sec.~\ref{sec:results}. 
- One example of a periodic light field is
+ One example of a periodic landscape is
  %that used in Sec.~\ref{sec:one}
@@
  \end{equation}
- where $N_p$ are the number of troughs in the landscape,
+ where $N_p$ are the number of periods,
  and $V_0$ is an adjustable parameter
@@
 The equation of motion provides a direct calculation of the velocity
-of an individual particle from its location.
-Since we model the acceleration $\vec{a}$ as zero,
+of an individual particle from its location in the simulation
+with respect to other particles $j$.
+Since we model the acceleration as zero,
 the Verlet method simplifies to 
@@
 \label{sec:results}
-
+ We demonstrate how a single particle (Sec.~\ref{sec:one})
+ and many particles
+ move (Sec.~\ref{sec:sync})
+ in response to this applied force in a variety of environments.
+ In Sec.~\ref{sec:kink} we set $F_{DC}$
+ to zero and track the motion
+ of a high density area of a particle chain
+ (i.e. kink dynamics).
+ %The driving force does add energy into the system, and some of it is lost.
+%
 \subsection{Single particle system}
@@
 where $N_p=20$ are the number of troughs in the landscape,
-and $V_{0x}=2$ and $V_{0x}=2$.
+and $V_{0y}=0.2$.
 This is illustrated in Fig.~\ref{fig:1}(a) where
-the red regions show local maxima and the blue local minima.
+the red (blue) regions show local maxima (minima).
 The code for generating
@@
 
+%single DC case with figure
+
+%increased DC
 We apply an external applied force, 
@@
 a constant $F_{AC}$ with frequency $\omega = 2\pi f$
-then slowly increase $F_{DC}$.
+then slowly increase $F_{DC}$
+at a rate of [].
 The particle hops between troughs in the energy landscape
@@
 
-  We acknowledge Harvey Gould and Jan Tobochnik, who supported our development of this article.
+  We acknowledge Harvey Gould and Jan Tobochnik,
+  who invited us to write the article and
+  supported its development.
   Charles and Cynthia Reichhardt advised 
-  the project and provided the molecular dynamics code.
+  the project and provided the original molecular dynamics code
+  written in the C programming language.
   We acknowledge funding from the M.J. Murdock Charitable Trust

### 2020-11-17 manuscript/manuscript_ajp_2020.tex
added detail to single particle system

@@
 The simulation is controlled by a $for()$ loop
-which runs from an intial to maximum $time$ integer.
-Each time step represents a simulation time of $\Delta t=0.001$.
+which runs from an initial to maximum $time$ integer.
+Each integer timestep
+represents a simulation time of $\Delta t=0.001$.
 At each timestep
@@
 $\vec{r}_i(t)$
-and then use the equation of motion to move particles
+and then integrate
+the equation of motion to move particles
 to an updated position
@@
 %
-We model the 
+The integration is simple
+because 
+we model the 
 particle dynamics 
 with an overdamped
-equation of motion
-integrated with the Verlet method.
+equation of motion.
+%integrated with the Verlet method.
 Here 
@@
 are small and the viscosity is high [finish... reference...]
-%[This model is encountered in Ch. 2 of Taylor's Classical Mechanics....]
+This model is encountered in standard texts,
+for instance Ch. 2 of Taylor's Classical Mechanics.
 
-A single particle has the equation of motion 
+A particle has the equation of motion 
 \begin{equation}
@@
 
-We place a single particle in a periodic landscape with
-corrugations along the y-direction 
+We drive a single particle across a periodic landscape 
+along the y-direction 
 \begin{equation}
@@
 \end{equation}
-where $N_p=20$ are the number of troughs in the landscape,
-and $V_{0y}=0.2$.
+with $N_p=20$ troughs in the landscape.
+%and $V_{0y}=0.2$.
 This is illustrated in Fig.~\ref{fig:1}(a) where
@@
 %is included in the supplementary material,
+The numerical implementation of the landscape 
+is calculated with
+\begin{equation}
+  \label{eq:landscape}
+  F_y(y) = F_{0y} \sin{(N_p \pi y / L)} 
+\end{equation}
+where $F_{0y} = 0.1$.
+We drive the particle with
+$F_{AC}=0.2$, $F_{DC}=0.01$, and $f=0.01$ cycles per time unit.
+When the superposition of $F_{AC}$ and $F_{DC}$ is large enough
+to overcome the barrier height of the landscape troughs,
+the particle hops between troughs in the energy landscape.
+In Fig.~\ref{fig:0} we
+show the relationship between the applied force and particle
+position.
+In Fig.~\ref{fig:0}(a)
+we plot the applied driving force
+as a function of time
+and in Fig.~\ref{fig:0}(b) 
+we show the position of the particle
+as a function of time.
+The initial position is near $y=0$
+and the initial driving force is minimum
+$F_D(t=0) = F_{DC}$.
+Over the time period $T/2 = 50$ %time units
+the particle moves
+in the positive y-direction
+while $F_{D}(t) > 0 $
+through three
+substrate troughs, reaching a maximum of $y/\lambda = 3$.
+When $F_{D}(t) < 0 $
+the particle moves in the negative y-direction
+reaching a minimum position
+of $y/\lambda = 1$
+over the period $T = 1/f = 100$.
+The average velocity $\bar{v}_y$
+is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
+over the period of the driving force.
+In Fig. ~\ref{fig:0}
+the displacement is a single wavelength
+of the substrate $y(t_0+T) - y(t_0) = \lambda$.
+Thus the average velocity 
+is $\bar{v}_y = \lambda f$, where $T = 1/f$.
 
 %single DC case with figure
+%dc_current 0.01
+%ac_current 0.2
+%ac_frequency 0.0001
+%fp_y 0.1
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=.25]{position}
+\caption{The position as a function of time of a single driven particle
+  normalized by the period of the substrate $\lambda$.
+  }
+\label{fig:0}
+\end{figure}
+\end{center}
 
+The hopping pattern of the driven particle is periodic,
+and could be achieved with a variety of
+driving forces.  %, as we will demonstrate in Fig.~\ref{fig:1}
+In Fig.~\ref{fig:1}
+we show the result increasing the 
+force to the particle as a function of time.  
 %increased DC
@@
 then slowly increase $F_{DC}$
-at a rate of [].
-The particle hops between troughs in the energy landscape
-when the superposition of $F_{AC}$ and $F_{DC}$ is large enough
-to overcome the barrier height.
+at a rate of $\Delta F_{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
+or $40$ time units.
+%this seems fast, but it is slow enough to estimate
+%the velocity accurately.
+%this is not be so for a multiple particle system!
 By modifying $F_{DC}$ we 
@@
 
-We illustrate the hopping pattern in Fig.~\ref{fig:1}(c)
+We illustrate the hopping pattern in Fig.~\ref{fig:1}(b)
 and 

### 2020-11-19 manuscript/manuscript_ajp_2020.tex
updated text

@@
   we control the particle interactions,
-  external force and environment
+  external force and confining environment
   in order to mimick experimental studies of driven colloidal particles
@@
   The molecular dynamics simulations
-  model the particle dynamics 
-  using overdamped equations of motion suitable for a viscous suspension
-  of microscopic particles.
+  %model the particle dynamics 
+  use overdamped equations of motion suitable for a viscous suspension
+  of microscopic particles
+  to model the dynamics.
   %What were your principal results?
@@
   and the propagation of 
-  high density kinks.
+  high density regions of particles,
+  or kinks.
   %What conclusions have you drawn from these results?
@@
   and exercises for students
-  that include 
+  %that include
+  with 
   opportunties
@@
 in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
-to fireflies signaling in time with a with a pulsed LED \cite{},
-to simultaneous flapping of birds wings \cite{},
-to neuronal firing in cardiac muscle \cite{} and brain tissue \cite{}.
+to fireflies signaling in time with a pulsed light emitting diode \cite{},
+to coordinated flapping of birds wings \cite{},
+to simultaneous neuronal firing in cardiac muscle \cite{}
+and brain tissue \cite{}.
 
@@
 and phase-locked current loops \cite{}.
-Instead of ohmic current-voltage (IV) relationships,
+Instead of ohmic current-voltage (I-V) relationships,
 such devices exhibit stepped regions
@@
 
-Recently studies of colloidal particles confined
-in optical traps have
+Recent experiments of colloidal particles confined
+in optical traps
+subject to external driving forces 
+have
 been used to examine the microscopic dynamics
-of mode-locking when subject to external driving force \cite{juniper2015}.
-[this is important because...]
+of mode-locking \cite{juniper2015}.
 %experimental - colloids specifically
-Colloidal particles trapped in light fields have proven
+Colloidal particles trapped in light fields are %have proven
 a particularly useful medium for studying complex dynamical behaviors.  %cite 
-The relatively large size of the colloids
-and ease in control has lead to a rich array of 
-experimental results. %THIS IS A TERRIBLE SENTENCE.
-Such studies are considered model systems
+The relatively large size of the colloids (micrometers)
+makes colloids easy to control and image,
+and the interaction forces between colloids can be modified
+by tuning the chemistry of the suspending fluid or surface ligands
+of the colloidal particles \cite{Grier2003}.
+This ease in control of colloids has lead to a rich array of 
+experimental results  
+considered models
 for experimental systems relatively hard to access and visualize,
@@
 %external forces
-It is often useful to study the
+The
 dynamics of particles subject to 
-an applied external force,
-for instance the flow of charges in a conductor,
+an applied external force apply to many physical systems.
+For instance the flow of charges in a conductor,
 or cells responding to a chemical gradient.
@@
 %-------------------------------------------------------------
+
+Numerical modeling of colloids can provide mechanistic insight
+that can be difficult to achieve in experimental conditions
+where Brownian motion and other sources of noise dominate.
+[elaborate]
 
@@
 We present these results using standard tools of non-linear oscillators
-such phase diagrams of particle velocity versus position.
+such phase diagrams of velocity versus position.
 In Section~\ref{sec:quasiperiod},
@@
 
+We model particle interaction forces
+$\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$ 
+with
+the Yukawa potential energy 
+\begin{equation}
+  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+\end{equation}
+where particle $i$ and $j$ are distance
+$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
+This 
+screened Coulomb potential
+%$E_0=2$ scales strength of repulsion
+is scaled in terms of energy unit $E_0$
+defined in Table ~\ref{tab:1}.
+%$ = k q_1 q_2$. %[CHECK scaling/units].
+$\kappa = 1/R_0$ is the screening parameter 
+that describe the lengthscale at
+which particles interact.
+We fix $R_0$ to be $a_0$.
+In experiments charge screening is observed
+due to ions in the suspending fluid and
+the charges of surrounding particles
+which
+reduces the interaction range of individual particles.
+This allows the numerical models to run more efficiently
+since particles do not need to interact over long range.
+[explain particle in cell models].
+
 \begin{table}[h!]
@@
 length &  $a_0$ \\
-viscosity/damping constant & $\eta$ \\
+%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
+energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
 dimensionless interaction strength & $q$ \\
 effective colloidal charge & $Z^*$ \\
-solvent dielectic constant & $\epsilon$ \\
+solvent dielectic constant & $\epsilon \epsilon_0$\\
+force & $E_0 / a_0$\\
+viscosity/damping constant & $\eta$ \\
 time &  $\eta / E_0$ \\
-velocity &  $\eta E_0 / a_0$ \\
-force & $E_0 / a_0$\\
-electric potential & $V(r_{ij}) = q^2 E_0/r_{ij}$ \\
-energy & $E_0 = {Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
+velocity &  $ E_0 / \eta a_0$ \\
 \end{tabular}
@@
 
- We model several enviroments
+We use several model enviroments to confine the particles,
+again assuming the confining force arises from a potential function 
  %creating a landscape of potential minima and maxima
@@
  as described in Sec.~\ref{sec:results}.
+
  One example of a periodic landscape is
@@
  %%We could also use a Gaussian function.
-
- We model particle interactions with
- the Yukawa potential $\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$,
- \begin{equation}
-   V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
- \end{equation}
- where $r_{ij} = |\vec{r}_i - \vec{r}_j|$.
- This is a
- screened Coulomb potential
- $E_0=2$ scales strength of repulsion
- where $E_0 = k q_1 q_2$  [CHECK scaling/units].
- $\kappa = 1/R_0$ is the screening parameter 
-that accounts for the lengthscale at
-which many particle
-interactions and local environment
-that reduces the interaction range of individual particles.
-We fix $R_0$ to be unity in our simulation units.
 
@@
 The hopping pattern of the driven particle is periodic,
-and could be achieved with a variety of
+and could be achieved over a range of
 driving forces.  %, as we will demonstrate in Fig.~\ref{fig:1}
-In Fig.~\ref{fig:1}
-we show the result increasing the 
-force to the particle as a function of time.  
+We explore the ranges of periodic hopping patterns
+by increasing $F_{DC}$ as a function of time,
+as shown in 
+%
+Fig.~\ref{fig:1}.
+%we show the result increasing the 
+%force to the particle as a function of time.  
 %increased DC

### 2020-11-20 manuscript/manuscript_ajp_2020.tex
added code with verbatim command

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Supplementary Materials}
+
+\subsection{Gridded Contour Plot of landscape}
+%code is located in
+%~/pymodules/animation_code/channel_colloid_movie_maker.py
+
+\begin{verbatim}
+##########################################################
+#ADD CONTOUR PLOT
+##########################################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color in the quasi1D potential to contain 
+    the particles in a trough.  
+    Can also add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #assuming Tiare's trough system, so we won't want to cover the entire range
+    X = np.arange(0, L/2.0, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 2.0 # set by what "looks good"
+    Z = Z_mag*np.sin(2*np.pi*X/L)
+    if corrugated == True:
+        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
+
+    cmap=cm.coolwarm_r
+
+    #alphs is the degree of transparency, again, set by what looks good.
+    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
+
+    #ax1.set_xlim(15,20)
+    #ax1.set_ylim(15,20)
+
+    #ax1.set_xlabel(r"$X$")
+    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
+
+    #ax1.set_xticks([])
+    #ax1.set_yticks([])
+    return
+\end{verbatim}
+
 \begin{acknowledgments}
@@
 
-%\begin{pyverbatim}
+\begin{verbatim}
 ##########################################################
@@
     return
- %   \end{pyverbatim}
+\end{verbatim}

### 2020-11-24 manuscript/manuscript_ajp_2020.tex
updated some typos

@@
 % The % character begins a comment, which continues to the end of the line.
-
 \usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
@@
 by $x_i+L=x_i$ and $y_i+L=y_i$.
-We summarize the units of the simulated variables in Table ~\ref{tab:1}.
-
-We model particle interaction forces
-$\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$ 
-with
-the Yukawa potential energy 
-\begin{equation}
-  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
-\end{equation}
-where particle $i$ and $j$ are distance
-$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
-This 
-screened Coulomb potential
-%$E_0=2$ scales strength of repulsion
-is scaled in terms of energy unit $E_0$
-defined in Table ~\ref{tab:1}.
-%$ = k q_1 q_2$. %[CHECK scaling/units].
-$\kappa = 1/R_0$ is the screening parameter 
-that describe the lengthscale at
-which particles interact.
-We fix $R_0$ to be $a_0$.
-In experiments charge screening is observed
-due to ions in the suspending fluid and
-the charges of surrounding particles
-which
-reduces the interaction range of individual particles.
-This allows the numerical models to run more efficiently
-since particles do not need to interact over long range.
-[explain particle in cell models].
+The units of the simulated variables are in Table ~\ref{tab:1}.
 
@@
 
+We model particle interaction forces
+$\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$ 
+with
+the Yukawa potential energy 
+\begin{equation}
+  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+\end{equation}
+where particle $i$ and $j$ are distance
+$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
+This 
+screened Coulomb potential
+%$E_0=2$ scales strength of repulsion
+is scaled in terms of energy unit $E_0$
+defined in Table ~\ref{tab:1}.
+%$ = k q_1 q_2$. %[CHECK scaling/units].
+$\kappa = 1/R_0$ is the screening parameter 
+that describes the lengthscale at
+which particles interact.
+We fix $R_0$ to be $a_0$.
+In experiments charge screening is observed
+due to ions in the suspending fluid and
+the charges of surrounding particles
+which
+reduces the interaction range of individual particles. % \cite{}.
+Because the particles interact over short ranges, 
+the numerical models can be run efficiency
+using a neighbor list algorithm
+determined using a cell method.
+[explain!]
+
 Particles are subject an external time-dependent driving force
@@
 We use several model enviroments to confine the particles,
-again assuming the confining force arises from a potential function 
+assuming the confining force arises from a potential function 
  %creating a landscape of potential minima and maxima
@@
  as described in Sec.~\ref{sec:results}.
-
- One example of a periodic landscape is
- %that used in Sec.~\ref{sec:one}
- where 
- \begin{equation}
-   V_l(y) = V_0 \cos{(N_p \pi y / L)}
- \end{equation}
- where $N_p$ are the number of periods,
- and $V_0$ is an adjustable parameter
- to set the depth of the troughs.
-
+% 
+% One example of a periodic landscape is
+%% %that used in Sec.~\ref{sec:one}
+% where 
+% \begin{equation}
+%   V_l(y) = V_0 \cos{(N_p \pi y / L)}
+% \end{equation}
+% where $N_p$ are the number of periods,
+% and $V_0$ is an adjustable parameter
+% to set the depth of the troughs.
+%
  In multi-particle simulations, we confine
- the particles along the $x-$direction with a
- quasi-one-dimensional geometry
- using a periodic function.
+ the particles along the $x-$direction 
+ using a periodic function 
  \begin{equation}
@@
  %%We could also use a Gaussian function.
+ This channel potential keeps the particles
+ interacting at short range confined primarily to motion
+ along the y-direction
+ but allows for some lateral motion of particles.
+ This is sometimes referred to as a
+ quasi-one-dimensional geometry.
 
@@
 %integrated with the Verlet method.
-Here 
-the suspending fluid is highly viscous
-and exerts a damping force on the particles equivalent
-to a linear drag force.
+%The suspending fluid is highly viscous
+%and exerts a damping force on the particles equivalent
+%to a linear drag force.
 %Overdamped dynamics is a common assumption in models of colloidal particles.
@@
 are small and the viscosity is high [finish... reference...]
-This model is encountered in standard texts,
-for instance Ch. 2 of Taylor's Classical Mechanics.
+This model should be familiar to readers
+modeling Milliken's oil drops
+in a standard classical mechanics text \cite{Taylor2005}.
+%This model is encountered in standard texts,
+%for instance Ch. 2 of Taylor's Classical Mechanics.
 
@@
 with respect to other particles $j$.
-Since we model the acceleration as zero,
+Since the acceleration as zero,
 the Verlet method simplifies to 
@@
 The hopping pattern of the driven particle is periodic,
-and could be achieved over a range of
-driving forces.  %, as we will demonstrate in Fig.~\ref{fig:1}
+and could be achieved over a range of $F_{DC}$.  %, as we will demonstrate in Fig.~\ref{fig:1}
 We explore the ranges of periodic hopping patterns

### 2020-12-17 manuscript/manuscript_ajp_2020.tex
changed wording of abstract AGAIN

@@
   %What problem did you study and why is it important?
-  We study synchronization of interacting particles
+  We study synchronization of interacting particles, 
+  where the particles are 
   confined to a narrow channel
+  and 
   driven by an external applied force.  
   %What methods did you use?
-  Using 
+  Our
   numerical simulations
+  mimick experimental studies of driven colloidal particles
+  confined by light-fields.
+  Much like experiments on colloids, 
   we control the particle interactions,
-  external force and confining environment
-  in order to mimick experimental studies of driven colloidal particles
-  confined by light-fields.
-  The molecular dynamics simulations
-  %model the particle dynamics 
-  use overdamped equations of motion suitable for a viscous suspension
-  of microscopic particles
-  to model the dynamics.
+  external force and confining environment.
+  We assume the particles move through
+  a viscous liquid,
+  so we model the dynamics of each particle
+  with 
+  overdamped equations of motion.
   %What were your principal results?
@@
 Synchronization is a universal phenomena
-that can be modeled with numerical studies of confined,
+that can be modeled with numerical studies of confined 
 driven particles.

### 2020-12-17 manuscript/manuscript_ajp_2020.tex
added reference

@@
 Examples of synchronization occur
-in many naturally oscillating systems,
+in many natural periodic systems,
 from Huygens 1665 observation of
@@
 
+\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
+
 \bibitem{juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, Microscopic dynamics of synchronization in driven colloids. Nat. Commun. 6, 7187 (2015).

### 2020-12-17 manuscript/manuscript_ajp_2020.tex
read C&C very helpful 2018 skyrmion paper

@@
 Examples of synchronization occur
-in many natural periodic systems,
-from Huygens 1665 observation of
-in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
-to fireflies signaling in time with a pulsed light emitting diode \cite{},
+in many biological systems with periodic behavior,
+from fireflies signaling in time with a pulsed light emitting diode \cite{},
 to coordinated flapping of birds wings \cite{},
-to simultaneous neuronal firing in cardiac muscle \cite{}
+to simultaneous firing of neurons in cardiac muscle \cite{}
 and brain tissue \cite{}.
 
+Huygens 1665 observation of
+in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
+to
+
 %phase locking
+
+Either coupled oscillators or a single particle on a corrugated
+potential with an applied AC drive.
+
+Relationship between substrate period and intrinsic velocity
+with phase locking caused by AC force modulates drive
+where the particle velocity is constant even though the applied
+DC force is increased.
+
+Particles - velocity-force curves
+Josephson Junctions - voltage-current curves
+
+what distinguishes a Shapiro step?
+where else are they witnessed?
+
 Dynamical mode locking is a controlled 
@@
 \centering
-\caption{Simulation units defined in the code.}
+\caption{Simulation units.}
 \begin{ruledtabular}
@@
 We model particle interaction forces
-$\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$ 
+$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
 with
@@
 \begin{equation}
-  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
 \end{equation}
@@
  \begin{equation}
-   V_{q1D}(x) = V_0 \cos{(\pi x / L)}
+   U_{q1D}(x) = U_0 \cos{(\pi x / L)}
  \end{equation}.
  %%We could also use a Gaussian function.
- This channel potential keeps the particles
- interacting at short range confined primarily to motion
+ This 
+ quasi-one-dimensional geometry
+ confines the particles
+ primarily to move 
  along the y-direction
  but allows for some lateral motion of particles.
- This is sometimes referred to as a
- quasi-one-dimensional geometry.
+ Otherwise the repulsive interaction between
+ particles would cause them to spread throughout the system.
 
@@
 
+  \bibitem{} Reichhardt, C., & Reichhardt, C.
+J.
+O.
+(2015).
+Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
+Physical Review B - Condensed Matter and Materials Physics, 92(22).
+https://doi.org/10.1103/PhysRevB.92.224432
+
 \bibitem{juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, Microscopic dynamics of synchronization in driven colloids. Nat. Commun. 6, 7187 (2015).

### 2020-12-18 manuscript/pre_draft.tex
changing tack to write an AJP not a PRE

--- 2020-12-17 manuscript/manuscript_ajp_2020.tex
@@
 %synchronization = widest audience possible
-Synchronization is a universal phenomena
-that can be modeled with numerical studies of confined 
-driven particles.
+Synchronization is a universal phenomena \cite{Pikovsky2003}.
 %Christiaan Huygens 
 %[has been adapted into many useful technologies...]
-Examples of synchronization occur
-in many biological systems with periodic behavior,
-from fireflies signaling in time with a pulsed light emitting diode \cite{},
-to coordinated flapping of birds wings \cite{},
+Huygens 1665 observation of
+in-phase motions of pendulum clocks,
+provides a classic example,
+where two periodic oscillators
+were synchronized due to
+a coupling by the mounting wall \cite{Bennet2002}.
+Such physical couplings are also observed
+in [examples]
+
+Biological systems benefit from cooperative
+synchronzation.
+Birds coordinate flapping of wings in order to [] \cite{},
 to simultaneous firing of neurons in cardiac muscle \cite{}
@@
 
-Huygens 1665 observation of
-in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
-to
+Such systems can be driven to form new synchronized patterns,
+for instance
+firefly [swarms] signal in time with a pulsed light emitting diode \cite{},
+[more examples]
+Driven coupled oscillations are sufficiently
+broad and useful to be the subject of computational modeling.
 
@@
 
-Either coupled oscillators or a single particle on a corrugated
-potential with an applied AC drive.
+Synchronization can be modeled with numerical studies of confined 
+driven particles.
+Studies modeling synchronized behaviors
+can be performed with
+coupled oscillators []
+An alternative method is to
+study the dynamics of a single particle
+confined in a periodic 
+potential landscape subject
+to with an applied driving force with constant or direct (DC)
+and alterating (AC)
+components.
 
@@
 
+\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygen's clocks, Proc. Roy. Soc. A 458, 563 (2002).
+
 \bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
 
-  \bibitem{} Reichhardt, C., & Reichhardt, C.
+%  \bibitem{} Reichhardt, C., & Reichhardt, C.
 J.

### 2020-12-18 manuscript/manuscript_ajp_2020.tex
rearranging the intro to be more undergrad compelling
liking the reshape!

@@
-\documentclass[prb,preprint]{revtex4} 
+%\documentclass[prb,preprint]{revtex4} 
+\documentclass[twocolumn,preprintnumbers,amsmath,amssymb,aps,prx]{revtex4}
 % The line above defines the type of LaTeX document.
@@
 \begin{abstract}
-
-  %DM editorial - too many ``we'' statements, not enough emphasize on importance.
-  %more detail on the methods?
-  %will need to rewrite results/conclusions as we shape the manuscript.
-
   %What problem did you study and why is it important?
-  We study synchronization of interacting particles, 
-  where the particles are 
+  We discuss a
+  numerical model
+  of particles
   confined to a narrow channel 
-  and 
-  driven by an external applied force.  
-  %What methods did you use?
-  Our
-  numerical simulations
-  mimick experimental studies of driven colloidal particles
-  confined by light-fields.
-  Much like experiments on colloids, 
-  we control the particle interactions,
-  external force and confining environment.
-  We assume the particles move through
-  a viscous liquid,
-  so we model the dynamics of each particle
-  with 
-  overdamped equations of motion.
-  %What were your principal results?
-  We observe
-  particle synchronization under a variety of conditions,
-  including static and dynamic patterns formed on
-  periodic and quasiperiod substrates
-  and the propagation of 
-  high density regions of particles,
-  or kinks.
-  %What conclusions have you drawn from these results?
-  We demonstrate the transition from
-  trapped to sliding dynamics in
-  quasiperiodic landscapes differs
-  from that of a periodic landscape by [TBD],
-  and that kinks of high density propagate
-  [more/less ?  ] when [what?].
-  We also explore 
-  the limits of applied force that
-  cause the dynamics to transition to chaotic behavior.
+  driven
+  across a washboard potential energy landscape.
+  The model 
+  exhibits
+  synchronization effects that provide insight
+  to the behavior of 
+  many experimental systems of
+  interest to condensed matter physics 
+  including 
+  magnetically driven colloidal particles
+  confined by light-fields, 
+  voltage driven superconducting vortices
+  confined in a Josephson junction,
+  and ac and dc driven
+  charge and spin density waves.
+  We present the basics
+  of the molecular dynamics simulations
+  for particles moving through
+  a viscous liquid.
+  %so we model the dynamics of each particle
+  %with 
+  %overdamped equations of motion.
+  We demonstrate how to visualize
+  the system
+  and measure hallmarks of synchronization, 
+  Shapiro steps,
+  that exhibit non-Ohmic step-like behavior 
+  in the 
+  the particle velocity as a function of applied driving force.
   We include sample code
@@
 Synchronization is a universal phenomena
-that can be modeled with numerical studies of confined 
-driven particles.
+where individual oscillators adjust rhythm due
+to an external stimuli \cite{Pikovsky2003}.
 %Christiaan Huygens 
 %[has been adapted into many useful technologies...]
-Examples of synchronization occur
-in many biological systems with periodic behavior,
-from fireflies signaling in time with a pulsed light emitting diode \cite{},
-to coordinated flapping of birds wings \cite{},
+Huygens' 1665 experiments on
+the 
+motions of two pendula on wall-mounted clocks,
+demonstrated the tendency of 
+two periodic oscillators in close
+proximity to swing in time, i.e. to synchronize \cite{Bennett2002}.
+Physical synchronous behavior are observed
+in many everyday systems
+such as the
+coupled flickering candle flames \cite{Okamoto2016} 
+and metronomes \cite{Jia2015}.
+Biological systems benefit from cooperative
+synchronzation.
+Birds coordinate
+flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
+frogs communicate by croaking patterns dictated by location \cite{Aihara2014},
+and humans synchronize clapping in time with music \cite{Tranchant2016}.
+
 to simultaneous firing of neurons in cardiac muscle \cite{}
-and brain tissue \cite{}.
+and brain tissue (i.e. brain waves) \cite{}.
 
-Huygens 1665 observation of
-in-phase oscillation of pendulum clocks \cite{Pikovsky2003},
-to
+Such systems can be driven to form new synchronized patterns,
+for instance
+firefly [swarms] signal in time with a pulsed light emitting diode \cite{},
+[more examples]
+Driven coupled oscillations are sufficiently
+broad and useful to be the subject of computational modeling.
 
@@
 \centering
-\includegraphics[scale=.25]{position}
+\includegraphics[width=\columnwidth]{position}
 \caption{The position as a function of time of a single driven particle
@@
 
-  \bibitem{} Reichhardt, C., & Reichhardt, C.
+\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygen's clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
+
+\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima. Synchronization in flickering of three-coupled candle flames. Sci Rep {\bf 6}, 36145 (2016)
+
+\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
+
+\bibitem{Portugal2014} S.
+Portugal, T.
+Hubel, J.
+Fritz, S.
+Heese, D.
+Trobe, B.
+Voelkl, S.
+Hailes, A.
+M.
+Wilson and J.
+R.
+Usherwood.
+Upwash exploitation and downwash avoidance by flap phasing in ibis formation flight.
+Nature {\bf 505}, 399 (2014).
+
+  \bibitem{Aihara2014} I.
+Aihara, T.
+Mizumoto, T.
+Otsuka, H.
+Awano, K.
+Nagira, H.
+G.
+Okuno and K.
+Aihara.
+Spatio-Temporal Dynamics in Collective Frog Choruses Examined by Mathematical Modeling and Field Observations.
+Sci Rep {\bf 4}, 3891 (2014).
+
+    %  \bibitem{} Reichhardt, C., & Reichhardt, C.
 J.
@@
 https://doi.org/10.1103/PhysRevB.92.224432
+
+    \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, Keeping the Beat: A Large Sample Study of Bouncing and Clapping to Music. PLoS ONE 11(7): e0160178. (2016).
 

### 2020-12-18 manuscript/manuscript_ajp_2020.tex
finished general introduction!

@@
 and humans synchronize clapping in time with music \cite{Tranchant2016}.
-
-to simultaneous firing of neurons in cardiac muscle \cite{}
-and brain tissue (i.e. brain waves) \cite{}.
-
-Such systems can be driven to form new synchronized patterns,
-for instance
-firefly [swarms] signal in time with a pulsed light emitting diode \cite{},
-[more examples]
-Driven coupled oscillations are sufficiently
-broad and useful to be the subject of computational modeling.
+At a cellular level, 
+neurons simultaneously fire in cardiac muscle \cite{MartinHall1999}
+and brain tissue  \cite{Singer1999}.
+
+%Given the prevalence of synchronization,
+%it is the subject of many computational models.
+Here we focus numerical studies 
+of the synchronized dynamics
+of confined particles driven over
+a washboard shaped potential energy landscape. 
+We chose this model for its
+relevance to condensed matter systems
 
 %phase locking
-
-Synchronization can be modeled with numerical studies of confined 
-driven particles.
+The hallmark of phase locking is
+that the ratio of frequencies is an integer number \cite{Bak1986}
+
 Studies modeling synchronized behaviors
@@
 
+  %intro to oscillators
 \bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
@@
 \bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
+
+  %biological examples
 
@@
 
+  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, Keeping the Beat: A Large Sample Study of Bouncing and Clapping to Music. PLoS ONE 11(7): e0160178. (2016).
+
+  \bibitem{MartinHall1999} G. Martin Hall, Sonya Bahar, and Daniel J. Gauthier, Prevalence of Rate-Dependent Behaviors in Cardiac Muscle. Phys. Rev. Lett. {\bf 82}, 2995 (1999).
+
+  \bibitem{Singer1999} W. Singer. Striving for coherence. Nature, {\bf 397} 391, 1999.
+
+    %condensed matter intro
+    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
+    %reichhardt review
+
     %  \bibitem{} Reichhardt, C., & Reichhardt, C.
@@
 https://doi.org/10.1103/PhysRevB.92.224432
-
-    \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, Keeping the Beat: A Large Sample Study of Bouncing and Clapping to Music. PLoS ONE 11(7): e0160178. (2016).
 

### 2020-12-22 manuscript/manuscript_ajp_2020.tex
updated condensed matter references

@@
 Synchronization is a universal phenomena
-where individual oscillators adjust rhythm due
+in which individual oscillators adjust rhythm due
 to an external stimuli \cite{Pikovsky2003}.
@@
 %[has been adapted into many useful technologies...]
-Huygens' 1665 experiments on
+Synchronization was first reported in the scientific literature
+when in 1665 
+Huygens' experiments on
 the 
-motions of two pendula on wall-mounted clocks,
+motions of two pendula on wall-mounted clocks 
 demonstrated the tendency of 
 two periodic oscillators in close
-proximity to swing in time, i.e. to synchronize \cite{Bennett2002}.
-Physical synchronous behavior are observed
+proximity to swing in time, i.e. to synchronize,
+due to interactions through the wall \cite{Bennett2002}.
+Synchronous behaviors are observed
 in many everyday systems
 such as the
-coupled flickering candle flames \cite{Okamoto2016} 
-and metronomes \cite{Jia2015}.
+flickering candle flames coupled by temperature fluctuations \cite{Okamoto2016} 
+and metronomes coupled through the the supporting table \cite{Jia2015}.
 Biological systems benefit from cooperative
-synchronzation.
-Birds coordinate
+synchronzation such as when 
+birds coordinate
 flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
@@
 and brain tissue \cite{Singer1999}.
+
+Synchronization is also referred to as 
+phase-locking or mode-locking.
+%phase locking
+Dynamical systems %with multiple frequencies
+exhibit phase-locking 
+when oscillators with different frequencies couple
+so the frequency ratio or mode 
+is an integer number \cite{Bak1986} .
+This can be demonstrated
+with Lissajous figures, i.e. parametric graphs of two periodic functions
+which make looped patterns determined by the mode, % frequency ratio,
+first reported in 1857 \cite{Lissajous1857}
+and easily generated with a computer code 
+or oscilloscope \cite{Tong1997}. 
+%with a frequency generator,
+%where two combined frequencies at perpendicular orientations
+
+Synchronization is often achieved via external forcing.
+Examples of synchronization via external forcing include
+pushing a child on a swing or
+using a pacemaker (an electrical generator)
+that pulses to regulate a heart beat.
+This kind of 
+dynamical mode locking
+is often observed in quantum electronic
+devices such as Josephson junctions \cite{Josephson1962,Josephson1965}
+i.e. phase-locked current loops \cite{} 
+which exhibit phase locking via
+stepped regions in current-voltage (I-V) 
+instead of ohmic relationships.
+Also known as Shapiro steps \cite{Shapiro1963},
+these steps have been observed broadly in 
+velocity-force curves and voltage-current curves
+as indicators of phase locking \cite{Golubov2004}.
+
+Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
+
+Synchronization has many important
+technological applications
+and is often studied with simplified computational models.
+%mini review of synchronization in electronics
+%careful - the following is all simulations
+Recent studies demonstrate
+that coupled electronic oscillators can be
+programmed for use as microcontrollers for robotic locomotion \cite{Dutta2019}.
 
@@
 relevance to condensed matter systems
-
-%phase locking
-The hallmark of phase locking is
-that the ratio of frequencies is an integer number \cite{Bak1986}
 
@@
 
-Particles - velocity-force curves
-Josephson Junctions - voltage-current curves
-
-what distinguishes a Shapiro step?
-where else are they witnessed?
-
-Dynamical mode locking is a controlled 
-synchronization phenomena in 
-which an external driving force
-causes
-%the natural oscillation frequencies
-%in
-weakly coupled oscillators to come into phase.
-Mode locking is often observed in quantum electronic
-devices such as Josephson junctions \cite{}
-and phase-locked current loops \cite{}.
-Instead of ohmic current-voltage (I-V) relationships,
-such devices exhibit stepped regions
-such as Shapiro steps \cite{} [explain].
-
-Recent experiments of colloidal particles confined
+Recent experiments of particles confined
 in optical traps
@@
 been used to examine the microscopic dynamics
-of mode-locking \cite{juniper2015}.
+of mode-locking in colloids \cite{juniper2015} and ions \cite{Bushev2013}.
 %experimental - colloids specifically
@@
 
+  %useful quick ref
+  %http://www.scholarpedia.org/article/Synchronization
+
   %intro to oscillators
@@
 
+    %technological applications
+    \bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
+
     %condensed matter intro
     \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
+
+    \bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
+
+    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures The Physics Teacher {\bf 35}, 491 (1997).
+
+    \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
+    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
+
+    \bibitem{Stewart1968}  W. C. Stewart CURRENT‐VOLTAGE CHARACTERISTICS OF JOSEPHSON JUNCTIONS Appl. Phys. Lett. 12, 277 (1968).
+
+    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
+
+    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il’ichev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
+
+      quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
+    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
+
       %reichhardt review
+      %C.
+Reichhardt and C.
+J.
+Olson Reichhardt, “Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review,” Rep.
+Prog.
+Phys.
+80, 026501 (2017).
 
@@
 
-\bibitem{juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, Microscopic dynamics of synchronization in driven colloids. Nat. Commun. 6, 7187 (2015).
+    \bibitem{juniper2015} M.
+P.
+N.
+Juniper, A.
+V.
+Straube, R.
+Besseling, D.
+G.
+A.
+L.
+Aarts, and R.
+P.
+A.
+Dullens, Microscopic dynamics of synchronization in driven colloids.
+Nat.
+Commun.
+6, 7187 (2015).
+
+    \bibitem{Bushev2013} P.
+Bushev, G.
+Hétet, L.
+Slodička, D.
+Rotter, M.
+A.
+Wilson, F.
+Schmidt-Kaler, J.
+Eschner, and R.
+Blatt, Shot-Noise-Limited Monitoring and Phase Locking of the Motion of a Single Trapped Ion, Phys.
+Rev.
+Lett.
+{\bf 110}, 133602 (2013).
 

### 2020-12-23 manuscript/manuscript_ajp_2020.tex
updated text and references

@@
 % \author statement.
-\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}
+%\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}
 % Please provide a full mailing address here.
@@
   to the behavior of 
-  many experimental systems of
-  interest to condensed matter physics 
+  experimental systems 
+  %interest to condensed matter physics 
   including 
   magnetically driven colloidal particles
-  confined by light-fields, 
-  voltage driven superconducting vortices
-  confined in a Josephson junction,
-  and ac and dc driven
-  charge and spin density waves.
+  confined by light-fields.
+  %and
+  %atoms on surfaces.
+  %voltage driven superconducting vortices
+  %confined in a Josephson junction,
+  %and ac and dc driven
+  %charge and spin density waves.
   We present the basics
@@
   for particles moving through
-  a viscous liquid.
+  a viscous liquid
+  applied to single and multiple particle systems.
   %so we model the dynamics of each particle
@@
   %overdamped equations of motion.
-  We demonstrate how to visualize
-  the system
-  and measure hallmarks of synchronization, 
-  Shapiro steps,
-  that exhibit non-Ohmic step-like behavior 
-  in the 
+  We demonstrate how to 
+  visualize
+  the system with
+  animations of the particle motion 
+  and detect synchronization using
+  measurements of
   the particle velocity as a function of applied driving force.
@@
 Synchronization is a universal phenomena
-in which individual oscillators adjust rhythm due
-to an external stimuli \cite{Pikovsky2003}.
-%Christiaan Huygens 
-%[has been adapted into many useful technologies...]
-Synchronization was first reported in the scientific literature
-when in 1665 
-Huygens' experiments on
-the 
-motions of two pendula on wall-mounted clocks 
-demonstrated the tendency of 
-two periodic oscillators in close
-proximity to swing in time, i.e. to synchronize,
-due to interactions through the wall \cite{Bennett2002}.
-Synchronous behaviors are observed
+in which individual oscillators adjust frequency due
+to interaction or an external stimulus \cite{Pikovsky2003}.
+Synchronous behaviors where oscillators move in-phase (i.e. in time)
+are observed
 in many everyday systems
@@
 flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
-frogs communicate by croaking patterns dictated by location \cite{Aihara2014},
+frogs communicate by croaking patterns modulated by location \cite{Aihara2014},
 and humans synchronize clapping in time with music \cite{Tranchant2016}.
@@
 
-Synchronization is also referred to as 
-phase-locking or mode-locking.
+%Christiaan Huygens 
+%[has been adapted into many useful technologies...]
+A particular form of 
+synchronization is phase-locking,
+which first appeared in the scientific literature
+with 
+Huygens' 1665 experiments on
+the 
+motions of two pendula on wall-mounted clocks.
+Huygens demonstrated the tendency of 
+two periodic oscillators in close
+proximity to swing in time %, i.e. to synchronize,
+due to interactions through the wall 
+no matter the original phase of the clocks \cite{Bennett2002}.
 %phase locking
@@
 
-Synchronization is often achieved via external forcing.
-Examples of synchronization via external forcing include
-pushing a child on a swing or
-using a pacemaker (an electrical generator)
-that pulses to regulate a heart beat.
-This kind of 
-dynamical mode locking
-is often observed in quantum electronic
-devices such as Josephson junctions \cite{Josephson1962,Josephson1965}
-i.e. phase-locked current loops \cite{} 
-which exhibit phase locking via
-stepped regions in current-voltage (I-V) 
-instead of ohmic relationships.
-Also known as Shapiro steps \cite{Shapiro1963},
-these steps have been observed broadly in 
-velocity-force curves and voltage-current curves
-as indicators of phase locking \cite{Golubov2004}.
-
-Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
-
-Synchronization has many important
+Synchronization is often achieved via external forcing
+such as when
+%single particle oscillators
+pushing a child on a swing at the high point on her path, or
+using pacemaker (an electrical generator)
+pulses to regulate a heart beat.
+%multiple particle oscillators
+[Fireflies and pulsed LED].
+
+Dynamical mode locking 
+has many important
 technological applications
 and is often studied with simplified computational models.
+These studies can be performed
+with coupled oscillators \cite{Kuramoto193?}
+or with a single particle driven across a periodic potential landscape \cite{}.
+%Single particle models avoid many-body effects
+%while offering insight.
+
+%Oscillators ordered into chains or lattices.
+Synchronization 
+is %often
+observed
+in quantum electronic
+devices such as Josephson junctions \cite{Josephson1962,Josephson1965}
+i.e. two superconductors sandwiching an insulating layer.
+When subject to an external voltage,
+Cooper pairs in the superconducting materials
+tunnel through the insulating layer.
+Phase-locking is observed as 
+%phase-locked current loops \cite{} 
+stepped regions in current-voltage (I-V) relationship in these devices,
+where a constant current results from a range of voltages
+due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
+%instead of ohmic relationships.
+Known as Shapiro steps \cite{Shapiro1963},
+these indicators of phase locking 
+have been observed broadly in a variety of systems
+either in 
+velocity-force curves and voltage-current curves \cite{Golubov2004}.
+Shapiro steps
+are hallmarks of
+non-Ohmic behavior in voltage-current curves,
+where these steps are generated
+by the tendency of the response of a system
+to be flat across a range of applied driving forces or voltages,
+which can be probed with applied AC forces.
+
+%  atoms on surfaces.
+%  voltage driven superconducting vortices
+%  confined in a Josephson junction,
+%  and ac and dc driven
+%  charge and spin density waves.
+%
+%
 %mini review of synchronization in electronics
 %careful - the following is all simulations
-Recent studies demonstrate
-that coupled electronic oscillators can be
-programmed for use as microcontrollers for robotic locomotion \cite{Dutta2019}.
-
-%Given the prevalence of synchronization,
-%it is the subject of many computational models.
-Here we focus numerical studies 
-of the synchronized dynamics
-of confined particles driven over
-a washboard shaped potential energy landscape. 
-We chose this model for its
-relevance to condensed matter systems
-
-Studies modeling synchronized behaviors
-can be performed with
-coupled oscillators []
-An alternative method is to
-study the dynamics of a single particle
-confined in a periodic 
-potential landscape subject
-to with an applied driving force with constant or direct (DC)
-and alterating (AC)
-components.
-
-Relationship between substrate period and intrinsic velocity
-with phase locking caused by AC force modulates drive
-where the particle velocity is constant even though the applied
-DC force is increased.
+%Recent studies demonstrate
+%that coupled electronic oscillators can be
+%programmed for use as microcontrollers for robotic locomotion \cite{Dutta2019}.
 
@@
 been used to examine the microscopic dynamics
-of mode-locking in colloids \cite{juniper2015} and ions \cite{Bushev2013}.
+of mode-locking in colloids interacting via magnetic dipole
+or electrostatic interactions
+in experiment \cite{Juniper2015, Lutz2004} and
+simulation \cite{Herrera-Velarde2007, Herrera-Velarde2008}.
 %experimental - colloids specifically
@@
 a particularly useful medium for studying complex dynamical behaviors.  %cite
-The relatively large size of the colloids (micrometers)
-makes colloids easy to control and image,
-and the interaction forces between colloids can be modified
+Colloid particles are micron-sized,
+a relatively large size to control and image.
+The interaction forces between colloids can be modified
 by tuning the chemistry of the suspending fluid or surface ligands
@@
 such as cold atoms or electron gases. %ELABORATE AND CITE
+%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
 
@@
 where irregular, unpredictable time evolution of
-nonlinear systems and occurs in mechanical oscillators \cite{chaos}.
+nonlinear systems occurs in mechanical oscillators \cite{chaos}.
 
@@
 [elaborate]
+
+%Given the prevalence of synchronization,
+%it is the subject of many computational models.
+Here we focus numerical studies 
+of the synchronized dynamics
+of confined particles driven over
+a washboard shaped potential energy landscape. 
+We chose this model for its
+relevance to condensed matter systems
+and ease of simulation.
+%We examine
+The period of the substrate
+can be used to control the
+intrinsic velocity of the driven particle.
 
@@
 such phase diagrams of velocity versus position.
+%PHASE DIAGRAMS SHOWNING COUPLING, OR QUASIPERIODIC COUPLING
+%INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
 In Section~\ref{sec:quasiperiod},
@@
 \end{equation}
+%v is the standard I note for substrates
 with $N_p=20$ troughs in the landscape.
@@
 Our simulations reproduce results presented in 
-Juniper {\it et al.} \cite{juniper2015}
+Juniper {\it et al.} \cite{Juniper2015}
 which demonstrated
@@
 
+\begin{enumerate}
+\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
+%D. Métivier, L. Wetzel, and S. Gupta
+%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
+%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)
+
+\item Brownian motion without fluid dynamics using  Ermak's algorithm
+
+\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are neglible
+
+  \item The Fokker-Planck Equation
+
+\end{enumerate}
+
 \section{Conclusion}
@@
 \bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
+
+%  Coupling between two singing wineglasses
+%Tal Arane, Ana K. R. Musalem and Moti Fridman
+%American Journal of Physics 77, 1066 (2009); https://doi.org/10.1119/1.3119175
+
+%Synchronization of a thermoacoustic oscillator by an external sound source
+%G. Penelet and T. Biwa
+%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189
 
@@
 
-    \bibitem{juniper2015} M.
+    \bibitem{Juniper2015} M.
 P.
@@
 
-    \bibitem{Bushev2013} P.
-Bushev, G.
-Hétet, L.
-Slodička, D.
-Rotter, M.
-A.
-Wilson, F.
-Schmidt-Kaler, J.
-Eschner, and R.
-Blatt, Shot-Noise-Limited Monitoring and Phase Locking of the Motion of a Single Trapped Ion, Phys.
+    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, PHYSICAL REVIEW E {\bf 77}, 041407 (2008).
+
+    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Castañeda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
+
+%      Lutz et al. 关11,12兴 created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
+    \bibitem{Lutz2004} C.
+Lutz, M.
+Kollmann, and C.
+Bechinger, Phys.
 Rev.
 Lett.
-{\bf 110}, 133602 (2013).
+{\bf 93}, 026001 (2004); C.
+Lutz, M.
+Kollmann, C.
+Bechinger, and P.
+Leiderer, J.
+Phys.: Condens.
+Matter {\bf 16}, S4075 (2004).
 

### 2020-12-24 manuscript/manuscript_ajp_2020.tex
updated josephson junction and colloid text

@@
 such as the
-flickering candle flames coupled by temperature fluctuations \cite{Okamoto2016} 
-and metronomes coupled through the the supporting table \cite{Jia2015}.
+flickering candle flames coupled by temperature fluctuations \cite{Okamoto2016},
+vibrations of singing wineglasses \cite{Arane2009}, 
+and metronomes coupled through a supporting platform \cite{Jia2015}.
 Biological systems benefit from cooperative
-synchronzation such as when 
-birds coordinate
-flapping of wings in order to optimize energy use during flight \cite{Portugal2014},
-frogs communicate by croaking patterns modulated by location \cite{Aihara2014},
-and humans synchronize clapping in time with music \cite{Tranchant2016}.
+synchronzation such as 
+birds coordinating wing flaps
+to optimize energy use during flight \cite{Portugal2014},
+frogs alternating croaking patterns \cite{Aihara2014},
+and humans synchronizing clapping in time with music \cite{Tranchant2016}.
 At a cellular level, 
@@
 A particular form of 
-synchronization is phase-locking,
+synchronization is phase-locking or mode-locking,
 which first appeared in the scientific literature
@@
 Huygens demonstrated the tendency of
-two periodic oscillators in close
-proximity to swing in time %, i.e. to synchronize,
-due to interactions through the wall 
+the pendula 
+%two periodic oscillators in close proximity
+to swing in time %, i.e. to synchronize,
+due to interactions through the wall,  
 no matter the original phase of the clocks \cite{Bennett2002}.
@@
 exhibit phase-locking 
-when oscillators with different frequencies couple
+when oscillators with different rhythms couple
 so the frequency ratio or mode 
-is an integer number \cite{Bak1986} .
-This can be demonstrated
-with Lissajous figures, i.e. parametric graphs of two periodic functions
-which make looped patterns determined by the mode, % frequency ratio,
+is an integer number \cite{Bak1986}.
+%Dynamical mode locking
+The phenomena 
+is often studied with simplified computational models
+and can be visualized with %demonstrated
+with phase plots or Lissajous figures.
+A mode-locked system is confined to 
+a closed loop in a 
+parametric space showing the relationship between two periodic functions
+with patterns determined by the mode, % frequency ratio,
 first reported in 1857 \cite{Lissajous1857}
@@
 %where two combined frequencies at perpendicular orientations
-
-Synchronization is often achieved via external forcing
-such as when
+({\it Could these for Fig. 1})
+
+External forcing can cause or regulate 
+synchronization. % is often achieved via external forcing
+%such as when
 %single particle oscillators
-pushing a child on a swing at the high point on her path, or
+For instance 
+%pushing a child on a swing at the high point on her path, or
 using pacemaker (an electrical generator)
-pulses to regulate a heart beat.
-%multiple particle oscillators
-[Fireflies and pulsed LED].
-
-Dynamical mode locking 
-has many important
-technological applications
-and is often studied with simplified computational models.
-These studies can be performed
-with coupled oscillators \cite{Kuramoto193?}
-or with a single particle driven across a periodic potential landscape \cite{}.
+pulses to regulate a heart beat
+or using a pulsed light to control the pattern of flashing
+fireflies \cite{Agrawal2013}.
+These dynamical drive studies can be performed
+on coupled oscillators %\cite{Kuramoto193?}
+or a single particle driven across a periodic potential landscape.
+A single particle particle oscillator
+within a potential well is 
+much like a skateboarder in a half-pipe.  % \cite{}.
 %Single particle models avoid many-body effects
 %while offering insight.
+The applied driving force can be constant (dc) or sinusoidal (ac).
+With a pure 
+dc drive the landscape modulates 
+the average particle velocity.
+An ac drive creates mode-locking,
+where the average particle velocity
+is fixed for a range of dc drive forces \cite{Reichhardt2015}.
 
 %Oscillators ordered into chains or lattices.
-Synchronization 
+%has many important
+%technological applications
+Dynamical mode-locking
 is %often
@@
 in quantum electronic
-devices such as Josephson junctions \cite{Josephson1962,Josephson1965}
-i.e. two superconductors sandwiching an insulating layer.
+devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
+A single junction contains 
+two superconductoring layers which sandwich an insulating layer.
 When subject to an external voltage,
@@
 stepped regions in current-voltage (I-V) relationship in these devices,
-where a constant current results from a range of voltages
-due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
+where voltage is the analog of external driving force
+and current is that of particle velocity.
+%where a constant current results from a range of voltages
+%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
 %instead of ohmic relationships.
-Known as Shapiro steps \cite{Shapiro1963},
-these indicators of phase locking 
-have been observed broadly in a variety of systems
-either in 
-velocity-force curves and voltage-current curves \cite{Golubov2004}.
-Shapiro steps
-are hallmarks of
+Known as Shapiro steps, % \cite{},
+these phase locked currents  
+have been observed due to applied ac voltages in 
+single Josephson junctions \cite{Shapiro1963, Golubov2004} and
+coupled arrays of junctions \cite{Benz1990}.
+%either in 
+%velocity-force curves and voltage-current curves \cite{Golubov2004}.
+Shapiro steps vary in width depending on the strength of the
+applied AC forces,
+and are observed in a variety of systems
+displaying
+%are hallmarks of
 non-Ohmic behavior in voltage-current curves,
-where these steps are generated
-by the tendency of the response of a system
-to be flat across a range of applied driving forces or voltages,
-which can be probed with applied AC forces.
-
+including
+ac and dc driven
+charge and spin density waves.
+
+%where these steps are generated
+%by the tendency of the response of a system
+%to be flat across a range of applied driving forces or voltages,
+%which can be probed with
 %  atoms on surfaces.
@@
 %  confined in a Josephson junction,
-%  and ac and dc driven
-%  charge and spin density waves.
+
 %
@@
 
-Recent experiments of particles confined
+Experiments of colloid particles confined
 in optical traps
@@
 been used to examine the microscopic dynamics
-of mode-locking in colloids interacting via magnetic dipole
-or electrostatic interactions
-in experiment \cite{Juniper2015, Lutz2004} and
-simulation \cite{Herrera-Velarde2007, Herrera-Velarde2008}.
+of mode-locking,
+which cannot be easily imaged in electronics.
 %experimental - colloids specifically
 Colloidal particles trapped in light fields are %have proven
-a particularly useful medium for studying complex dynamical behaviors.  %cite
+a useful medium for studying complex dynamical behaviors.  %cite
 Colloid particles are micron-sized,
@@
 by tuning the chemistry of the suspending fluid or surface ligands
-of the colloidal particles \cite{Grier2003}.
-This ease in control of colloids has lead to a rich array of 
-experimental results  
-considered models
-for experimental systems relatively hard to access and visualize,
-such as cold atoms or electron gases. %ELABORATE AND CITE
+of the colloidal particles.
+Because colloids are easy to control and study, 
+they are used as experimental models
+for systems relatively hard to access and visualize,
+such as cold atoms or electron gases \cite{Grier2003}. %ELABORATE AND CITE
 %Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
-
+Mode-locking 
+in colloids has been acheived in systems interacting via magnetic dipoles 
+or electric forces 
+in experiment \cite{Juniper2015, Lutz2004} and
+simulation \cite{Herrera-Velarde2007, Herrera-Velarde2008}.
 %-----------------------------------------------------------
 %particle interaction types
-Particles which interact over long distances
-include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more detail and references]
-Particles which interact over short distances include
-bubble arrays/emulsions [more systems and references].
+%Particles which interact over long distances
+%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [mor%e detail and references]
+%Particles which interact over short distances include
+%bubble arrays/emulsions [more systems and references].
 
@@
 %paper outline
-In the following paper we describe
+%In the following paper
+We describe
 our molecular dynamics model in Section~\ref{sec:MD}.
@@
 
+\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, Coupling between two singing wineglasses, Am. J. Phys. {\bf 77}, 1066 (2009). %; https://doi.org/10.1119/1.3119175
+
 \bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
-
-%  Coupling between two singing wineglasses
-%Tal Arane, Ana K. R. Musalem and Moti Fridman
-%American Journal of Physics 77, 1066 (2009); https://doi.org/10.1119/1.3119175
 
@@
 
-    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures The Physics Teacher {\bf 35}, 491 (1997).
+    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
+
+    \bibitem{Agrawal2013} D. K. Agrawal, J. Woodhouse, and A. A. Seshia, Physical Review Letters {\bf 111}, 084101 (2013).
 
@@
     \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
+
+    \bibitem{Benz1990}  S.
+P.
+Benz, M.
+S.
+Rzchowski, M.
+Tinkham, and C.
+J.
+Lobb, Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays, Phys.
+Rev.
+Lett.
+64, 693 (1990); D.
+Dom´ınguez and J.
+V.
+Jos´e, Giant Shapiro steps with screening currents, Phys.
+Rev.
+Lett.
+69,
+514 (1992).
 
@@
 
-    %  \bibitem{} Reichhardt, C., & Reichhardt, C.
+    \bibitem{Reichhardt2015} C.
+Reichhardt, and C.
 J.
 O.
+Reichhardt,  Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
+Phys.
+Rev.
+B {\bf 92}, (22).
 (2015).
-Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
-Physical Review B - Condensed Matter and Materials Physics, 92(22).
-https://doi.org/10.1103/PhysRevB.92.224432
 
@@
 
+      \bibitem{Grier2003} D. G. Grier, A revolution in optical manipulation. Nature {\bf 424}, 810–816 (2003).
+
 %      Lutz et al. 关11,12兴 created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls

### 2020-12-24 manuscript/manuscript_ajp_2020.tex
nearly finished with intro

@@
 simulation \cite{Herrera-Velarde2007, Herrera-Velarde2008}.
+
 %-----------------------------------------------------------
@@
 Stabilized charged particles form patterns
-due to the interplay of the confining environment
+due to the interplay of the confining landscape 
 and particle interactions.
@@
 of how particles move through systems 
-such as wires and microchannels.
-Biological systems such as
-neuron axons and capillaries can also be studied
-with these models [more detail and references].
-Many such systems execute local oscillations
-about stable points [elaborate].
+such as charge carries in quantum wires \cite{Tarucha1995} and
+slime molds in microchannels \cite{Gholami2015}.
+%Biological systems such as
+%neuron axons and capillaries can also be studied
+%with these models [more detail and references].
+%Many such systems execute local oscillations
+%about stable points [elaborate].
 %----------------------------------------------------------
-The presence of a modulating surface
-can modify these patterns in a variety of ways,
-changing the onset of dynamical flows,
-and the overall flow patterns.
+%The presence of a modulating surface
+%can modify these patterns in a variety of ways,
+%changing the onset of dynamical flows,
+%and the overall flow patterns.
 %
-
 %external forces
-The
-dynamics of particles subject to 
-an applied external force apply to many physical systems.
-For instance the flow of charges in a conductor,
-or cells responding to a chemical gradient.
-The external force 
-increases the diversity of dynamical behaviors,
-and can cause particles to flow in
-a variety of non-linear complex patterns
-that may be 
-synchronized.
-Disordered chaotic dynamics are also possible,
-where irregular, unpredictable time evolution of
-nonlinear systems occurs in mechanical oscillators \cite{chaos}.
-
+%The
+%dynamics of particles subject to 
+%an applied external force apply to many physical systems.
+%For instance the flow of charges in a conductor,
+%or cells responding to a chemical gradient.
+%The external force 
+%increases the diversity of dynamical behaviors,
+%and can cause particles to flow in
+%a variety of non-linear complex patterns
+%that may be 
+%synchronized.
+%Disordered chaotic dynamics are also possible,
+%where irregular, unpredictable time evolution of
+%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
 %-------------------------------------------------------------
-
-Numerical modeling of colloids can provide mechanistic insight
-that can be difficult to achieve in experimental conditions
-where Brownian motion and other sources of noise dominate.
-[elaborate]
 
@@
 and ease of simulation.
+Numerical modeling of colloids can provide mechanistic insight
+that can be difficult to achieve in experimental conditions
+where Brownian motion and other sources of noise dominate.
 %We examine
@@
 can be used to control the
-intrinsic velocity of the driven particle.
-
-%another confinement technique:
-%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
-%confines single cells and particles with lower energy than light / lasers
-%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
-%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
+intrinsic velocity of the dc driven particle,
+and the applied ac drive can
+create Shapiro steps in the force-velocity relationship.
 
@@
 %transition from synchronized to chaotic
-
 %describe types of physical systems - particle types
-In this work,
-we perform 
-numerical simulations of confined, driven particles
-to model a variety of physical phenomena.
-%----------------------------------------------------------------------------
+%%In this work,
+%we perform 
+%numerical simulations of confined, driven particles
+%to model a variety of physical phenomena.
+%-----------------------------------------------------------------------
 %paper outline
@@
 and supplementary material.
-In Section~\ref{sec:results} we summarize
-our results,
+We summarize
+our results 
+in Section~\ref{sec:results} 
 including synchronized motion of a single confined particle
@@
 
+    \bibitem{Tarucha1995}  Tarucha, S.; Honda, T.; Saku, T. Solid State Commun. 1995, 94, 413.
+
+    \bibitem{Gholami2015} A.
+Gholami, O.
+Steinbock, V.
+Zykov, and E.
+Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
+Rev.
+Lett.
+{\bf 114}, 018103 (2015).
+
 \bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
@@
 \end{verbatim}
+
+%another confinement technique:
+%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
+%confines single cells and particles with lower energy than light / lasers
+%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
+%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1

### 2020-12-24 manuscript/manuscript_ajp_2020.tex
cited Taylor, working on model

@@
 We include code to simulate
-and visualize the dynamics in this section
+and visualize the landscape and dynamics in this section
 and supplementary material.
@@
 %INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
-In Section~\ref{sec:quasiperiod},
-we show how an aperiodic landscape modifies the particle dynamics.
-Finally we explore the transition to chaotic dynamics in 
-Section~\ref{sec:chaos}
-and conclude 
-in Section~\ref{sec:conclusion}. 
+%In Section~\ref{sec:quasiperiod},
+%we show how an aperiodic landscape modifies the particle dynamics.
+%Finally we explore the transition to chaotic dynamics in 
+%Section~\ref{sec:chaos}
+%and conclude 
+%in Section~\ref{sec:conclusion}. 
 In each section
@@
 Such a model is appropriate when the particles
-are small and the viscosity is high [finish... reference...]
+are small and the viscosity of the suspending medium is high.
+% [finish... reference...]
 This model should be familiar to readers
@@
 
+      %Molecular dynamics references
+
+    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
+    \bibitem{Allen2020} Allen and Tildsley, The Computer Simulation of Liquids.
+
+      \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
+
 \bibitem{supp1} See Figure1.mp4 in appropriate %\url{}

### 2020-12-25 code/AJP_code.py
commented the single particle code

@@ -35,38 +35,49 @@ def md_step(y, vy, dt, time):
     period = 1.0
     frequency = 0.1
     
-    #integrate the equation of motion \eta v = F^net
+    #integrate the equation of motion \eta v = F^net (eta=1)
 
+    #substrate
     vy += landscape_potential(V0,y,period)
+
+    #driving force
     vy += external_drive(F_AC,F_DC,frequency,time)
 
+    #calculate the new position
     y += vy*dt
     
     return y, vy
 
 
-
+#-------------------------------------------------------------------
 if __name__ == "__main__":
 
-    dt = 0.01
+    #define the constants (parameters and initial conditions)
+    dt = 0.01 #hmm... not as in manuscript... single particle in a smoothly varying environment
     y = 0
     vy = 0
     time = 0.0
 
+    #integer time steps
     maxtime=100
 
+    #define arrays to hold data as a function of time
     y_data = np.zeros(maxtime)
     vy_data = np.zeros(maxtime)
     time_data = np.zeros(maxtime)
 
+    #loop through the integer time steps in the simulation
     for int_time in range(0,maxtime):
 
+        #apply the force calculations for the current position/time
         y, vy = md_step(y, vy, dt, time)
 
+        #update the data
         y_data[int_time] = y
         vy_data[int_time] = vy
         time_data[int_time] = time
 
+        #update the time (simulation units)
         time += dt
 
 

### 2020-12-25 code/AJP_code.py
included a writemovietime

@@ -12,7 +12,7 @@ import matplotlib.pyplot as plt
 
 ##################################################################
 def landscape_potential(V0,y,period):
-    '''
+    '''but what is the landscape force?
     '''
     
     return V0*np.cos(2*np.pi*y/period)
@@ -24,16 +24,29 @@ def external_drive(F_AC,F_DC,frequency,time):
     
     return F_DC + F_AC*np.sin(2*np.pi*frequency*time)
 
+####################################################################
+def ramp_dc_force(F_DC,time,drop,F_DC_incr):
+    '''
+    '''
+    F_DC_max = 0.5
+    
+    if time % drop == 0 and F_DC < F_DC_max:
+        F_DC += F_DC_incr
+
+    return F_DC
+
 #####################################################################
-def md_step(y, vy, dt, time):
+def md_step(y, vy, dt, time, F_DC):
     '''
     '''
 
-    F_AC = 0.05
-    F_DC = 0.05
-    V0 = 0.5
-    period = 1.0
-    frequency = 0.1
+    F_AC = 0.2
+    #F_DC = 0.005 #5 #increment slowly
+    period = 1.825
+    V0 = 0.1*2*np.pi/period
+    frequency = 0.0001
+    SX = 36.5
+    SY = 36.5
     
     #integrate the equation of motion \eta v = F^net (eta=1)
 
@@ -45,6 +58,8 @@ def md_step(y, vy, dt, time):
 
     #calculate the new position
     y += vy*dt
+    if y > SY:
+        y -= SY
     
     return y, vy
 
@@ -53,33 +68,49 @@ def md_step(y, vy, dt, time):
 if __name__ == "__main__":
 
     #define the constants (parameters and initial conditions)
-    dt = 0.01 #hmm... not as in manuscript... single particle in a smoothly varying environment
+    dt = 0.001 #
     y = 0
     vy = 0
     time = 0.0
+    period = 1.825
 
+    F_DC = 0
+    F_DC_incr = 0.001
+    drop = 4000
+    
     #integer time steps
-    maxtime=100
-
+    maxtime=200000
+    writemovietime=1000
+    
     #define arrays to hold data as a function of time
-    y_data = np.zeros(maxtime)
-    vy_data = np.zeros(maxtime)
-    time_data = np.zeros(maxtime)
+    array_length = int(maxtime/writemovietime)
+    y_data = np.zeros(array_length)
+    vy_data = np.zeros(array_length)
+    time_data = np.zeros(array_length)
 
     #loop through the integer time steps in the simulation
[…]

### 2020-12-25 code/AJP_code.py
fixed mistake with inertia

@@ -15,14 +15,20 @@ def landscape_potential(V0,y,period):
     '''but what is the landscape force?
     '''
     
-    return V0*np.cos(2*np.pi*y/period)
+    return V0*np.sin(2*np.pi*y/period)
 
 ###################################################################
 def external_drive(F_AC,F_DC,frequency,time):
     '''
     '''
+
+    F_ext = F_DC + F_AC*np.sin(2*np.pi*frequency*time) #
+
+    #if time % 1000:
+    #    print(time,F_ext)
     
-    return F_DC + F_AC*np.sin(2*np.pi*frequency*time)
+    return F_ext
+
 
 ####################################################################
 def ramp_dc_force(F_DC,time,drop,F_DC_incr):
@@ -36,22 +42,22 @@ def ramp_dc_force(F_DC,time,drop,F_DC_incr):
     return F_DC
 
 #####################################################################
-def md_step(y, vy, dt, time, F_DC):
+def md_step(y, dt, time, F_DC):
     '''
     '''
 
     F_AC = 0.2
     #F_DC = 0.005 #5 #increment slowly
     period = 1.825
-    V0 = 0.1*2*np.pi/period
-    frequency = 0.0001
+    V0 = 0.1 #*2*np.pi/period
+    frequency = 0.01
     SX = 36.5
     SY = 36.5
     
     #integrate the equation of motion \eta v = F^net (eta=1)
 
-    #substrate
-    vy += landscape_potential(V0,y,period)
+    #reset vy for every timestep!  
+    vy = landscape_potential(V0,y,period)
 
     #driving force
     vy += external_drive(F_AC,F_DC,frequency,time)
@@ -60,6 +66,8 @@ def md_step(y, vy, dt, time, F_DC):
     y += vy*dt
     if y > SY:
         y -= SY
+    elif y < 0:
+        y += SY
     
     return y, vy
 
@@ -75,7 +83,7 @@ if __name__ == "__main__":
     period = 1.825
 
     F_DC = 0
-    F_DC_incr = 0.001
+    F_DC_incr = 0.0 #01
     drop = 4000
     
     #integer time steps
@@ -96,10 +104,11 @@ if __name__ == "__main__":
             #print(F_DC)
 
         #apply the force calculations for the current position/time
-        y, vy = md_step(y, vy, dt, time, F_DC)
+        #note vy is not necessary 
+        y, vy = md_step(y, dt, time, F_DC)
 
         if int_time % writemovietime == 0:
[…]

### 2020-12-26 code/MD_colloid.py
renamed to more informative

@@ -1,6 +1,11 @@
+#!/usr/bin/env python3
+
+
 #################################################################
 '''
+Supplementary Material for
 Molecular dynamics simulation of synchronization in driven particles
+American Journal of Physics
 
 Danielle McDermott
 Tiare Guerrero
@@ -64,6 +69,8 @@ def md_step(y, dt, time, F_DC):
 
     #calculate the new position
     y += vy*dt
+
+    #check periodic boundary conditions
     if y > SY:
         y -= SY
     elif y < 0:

### 2020-12-27 code/calc_Reynolds.py
demonstrating why we use the linear drag regime

@@ -1,0 +1,28 @@
+#!/usr/bin/env python3
+
+#at standard temperature and pressure, converted to SI units (i.e. m-kg-sec)
+D = 1e-6 #micrometer
+rho = 0.9982 * 1e-3 * 1e6 #g/cm^3  1g=10^-3kg, 1/cm^3*(100cm/1m)^3
+v = 1e-6 #micrometer / sec
+
+#"kinematic viscosity" - not the right units
+#eta = 0.01 #cm^2 / sec
+
+#"dynamics viscosity" - same units as Taylor
+eta = 1.0016e-3 #mPa *sec = mN/m^2 *sec
+
+
+#unit check:  m*m/sec*kg/(m^3)*1/(N/m^2*sec)
+#blech! 
+#unit check:  kg/m * m^2 / (N*sec^2) 
+#unit check:  m*kg / (N*sec^2) = m*kg / (kg*m s^2 /s^2)
+#kg cancels!  m cancels! s^2 cancels!
+#unitless Reynold's number
+
+
+#1 micrometer = 10^-6 meters
+#1 centimeter = 10^-2 meters
+#1 micrometer = 10^-4 centimeters
+
+R = D*v*rho/eta
+print(R)

### 2020-12-28 manuscript/manuscript_ajp_2020.tex
cleaned up latex comments

@@
   %What problem did you study and why is it important?
-  We discuss a
-  numerical model
-  of particles
-  confined to a narrow channel 
+  Particles
+  %confined to a narrow channel 
   driven
-  across a washboard potential energy landscape.
-  The model 
-  exhibits
-  synchronization effects that provide insight
-  to the behavior of 
+  across a washboard potential energy landscape
+  exhibit a variety of synchronization effects
+  in
   experimental systems 
@@
   confined by light-fields.
+  %  Numerical model
+  We discuss a simple
+  numerical model that
+  %exhibits
+  provides insight
+  to synchronization behavior
   %and
@@
   %charge and spin density waves.
-  We present the basics
-  of the molecular dynamics simulations
+  %We present the basics
+  using
+  molecular dynamics simulations
   for particles moving through
-  a viscous liquid
-  applied to single and multiple particle systems.
+  a viscous liquid.
+  %applied to single and multiple particle systems.
   %so we model the dynamics of each particle
@@
   the system with
-  animations of the particle motion 
-  and detect synchronization using
-  measurements of
-  the particle velocity as a function of applied driving force.
+  numerical representations of the landscape
+  and
+  animations of the particle motion.
+  Our results show a variety of systems that
+  synchronize 
+  %and detect synchronization using
+  %measurements of
+  particle velocity as a function of applied driving force,
+  and characterize these behaviors
+  with force-velocity curves and phase diagrams.
   We include sample code
@@
   with 
-  opportunties
+  opportunities
   to reproduce our results and propose
   new numerical experiments.
-  With only a few particles in two-dimensions,
-  the simulation runs quickly,
-  making this an appropriate model for undergraduates to explore.
+  %With only a few particles in two-dimensions,
+  %the simulation runs quickly,
+  %making this an appropriate model for undergraduates to explore.
 
@@
 Biological systems benefit from cooperative
-synchronzation such as 
+synchronization such as 
 birds coordinating wing flaps
@@
 the 
-motions of two pendula on wall-mounted clocks.
+motions of two wall-mounted pendulum clocks.
 Huygens demonstrated the tendency of
@@
 %where two combined frequencies at perpendicular orientations
-({\it Could these for Fig. 1})
+({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
 
@@
 %single particle oscillators
-For instance 
+For instance a
 %pushing a child on a swing at the high point on her path, or
-using pacemaker (an electrical generator)
+pacemaker (an electrical generator)
 pulses to regulate a heart beat
-or using a pulsed light to control the pattern of flashing
-fireflies \cite{Agrawal2013}.
-These dynamical drive studies can be performed
-on coupled oscillators %\cite{Kuramoto193?}
+or controlling the pattern of flashing
+fireflies with a pulsed light \cite{Agrawal2013}.
+These behaviors can be modeled with
+numerical studies %can be performed
+where
+a driving force is applied to simple harmonic system,
+either
+coupled oscillators %\cite{Kuramoto193?}
 or a single particle driven across a periodic potential landscape.
@@
 within a potential well is 
-much like a skateboarder in a half-pipe.  % \cite{}.
-%Single particle models avoid many-body effects
-%while offering insight.
-The applied driving force can be constant (dc) or sinusoidal (ac).
-With a pure 
+much like a skateboarder in a half-pipe or
+a child on a swing
+moving back and forth through equilibrium.  % \cite{}.
+Single particle studies 
+are useful to understand synchronization
+in the absence of collective effects.
+With a constant or 
 dc drive the landscape modulates 
-the average particle velocity.
-An ac drive creates mode-locking,
+the particle velocity, below some threshold below
+the dc force is not strong enough to push the particle
+across a potential maximum so the average velocity is zero,
+a phenomena known as depinning \cite{Reichhardt2017},
+and dissipating energy from the system at all driving forces.
+A sinusoidal or ac drive creates mode-locking,
 where the average particle velocity
@@
 %that coupled electronic oscillators can be
-%programmed for use as microcontrollers for robotic locomotion \cite{Dutta2019}.
-
+%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
+
+\section{Colloidal Models}
+\label{sec:colloids}
+
+Experiments with colloid particles,
+such as plastic beads suspended in
+highly de-ionized water \cite{},
+are useful model systems
+to understand complex behaviors.
+%silica spheres in organic solvents
+%magnetic spheres?
+%
 Experiments of colloid particles confined
@@
 been used to examine the microscopic dynamics
-of mode-locking,
+of individual particles during mode-locking,
 which cannot be easily imaged in electronics.
@@
 Colloidal particles trapped in light fields are %have proven
-a useful medium for studying complex dynamical behaviors.  %cite
-Colloid particles are micron-sized,
-a relatively large size to control and image.
-The interaction forces between colloids can be modified
+a useful medium for studying complex dynamical behaviors  %cite
+due to their 
+relatively large size of microns,
+making them relatively simple 
+to control and image.
+Additionally colloids can mimic different
+systems since 
+the interaction forces between colloids can be modified
 by tuning the chemistry of the suspending fluid or surface ligands
-of the colloidal particles.
+of the particles.
 Because colloids are easy to control and study, 
@@
 Mode-locking 
-in colloids has been acheived in systems interacting via magnetic dipoles 
+in colloids has been achieved in systems interacting via magnetic dipoles 
 or electric forces 
@@
 %Particles which interact over long distances
-%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [mor%e detail and references]
+%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
 %Particles which interact over short distances include
-%bubble arrays/emulsions [more systems and references].
-
-%-----------------------------------------------
-%environments
-Particles in confined geometries behave differently than free particles.
-Stabilized charged particles form patterns
-due to the interplay of the confining landscape 
-and particle interactions.
-Narrow channels studies are useful to provide insights 
-of how particles move through systems 
-such as charge carries in quantum wires \cite{Tarucha1995} and
-slime molds in microchannels \cite{Gholami2015}.
-%Biological systems such as
-%neuron axons and capillaries can also be studied
-%with these models [more detail and references].
-%Many such systems execute local oscillations
-%about stable points [elaborate].
-%----------------------------------------------------------
+%bubble arrays/emulsions [more systems and references].----------------------
 %The presence of a modulating surface
@@
 %and the overall flow patterns.
-%
+%  adjustable strength, geometry and length scale of substrate potential
+%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
+%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).
+
 %external forces
@@
 %it is the subject of many computational models.
-Here we focus numerical studies 
-of the synchronized dynamics
+Here we perform numerical studies 
+on the synchronized dynamics
 of confined particles driven over
@@
 We describe
-our molecular dynamics model in Section~\ref{sec:MD}.
+our molecular dynamics model in Section~\ref{sec:MD}
+In this section, we restrict our discussion to a single particle,
+and include additional information
+for multiple particles in Section~\ref{sec:sync}.
 %including various  and confining environments.
-We include code to simulate
-and visualize the landscape and dynamics in this section
-and supplementary material.
 We summarize
@@
 in Sec.~\ref{sec:kink}.
+We include code to simulate
+and visualize the landscape and dynamics in this section
+and supplementary material.
 %we
@@
 such phase diagrams of velocity versus position.
-%PHASE DIAGRAMS SHOWNING COUPLING, OR QUASIPERIODIC COUPLING
+%PHASE DIAGRAMS SHOWING COUPLING, OR QUASI-PERIODIC COUPLING
 %INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
@@
 
-%Here we model the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
-
-\section{Molecular Dynamics Model}
+%Here we model the microscopic dynamics of phase locking in a colloidal model syestem using molecular dynamics (MD).
+
+\section{Molecular Dynamics Simulation}
 \label{sec:MD}
+In this section we describe the dynamics of the particles
+using the model forces
+and the motion using an modified form of Newton's second law
+suitable for microscopic particles in a suspending fluid.
+
 We use a classical two-dimensional model for 
@@
 An individual particle $i$ has
-position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
+position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$
+and velocity $\vec{v}_i = d\vec{r}_i/dt$.  
 Particles are subject to
 periodic boundary conditions
-such that a particle leaving the edges of the system is mapped
+such that a particle leaving the edge of the system is mapped
 back to a position within the simulation 
-by $x_i+L=x_i$ and $y_i+L=y_i$.
-The units of the simulated variables are in Table ~\ref{tab:1}.
+by the transformation $x_i+L \rightarrow x_i$ and $y_i+L \rightarrow y_i$.
+%and particles interact across PBC.
+
+Particles are subject an external time-dependent driving force
+$\vec{F}_{D}(t)$
+applied parallel to the y-direction.
+We model this force as
+\begin{equation}
+  \vec{F}^{D}(t) = [F^{DC} + F^{AC} \sin(\omega t)] \hat{y},
+    \label{eq:drive}
+\end{equation}
+with modifiable parameters including
+a constant component $F^{DC}$,
+and a time dependent component with amplitude $F^{AC}$
+and frequency $\omega = 2 \pi f$.
+%The frequency is scaled in time units,
+%where [finish].
+When $F^{DC}$ is non-zero,  
+%In several simulations
+we slowly increase 
+$F^{DC}$ from zero
+to avoid transient effects.
+
+We confine the particles using a position dependent 
+potential energy function, called a landscape or substrate.
+The confining force %arises from a potential function 
+ %creating a landscape of potential minima and maxima
+%that modify the force on a particle as a function of position
+is calculated as 
+ $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
+ %The landscape potential energy $U(\vec{r})$ is static 
+ %with fixed minima and maxima
+ %that are periodic or quasi-periodic,
+ %as described in Sec.~\ref{sec:results}.
+% 
+The periodic landscape is modulated in the y-direction as
+%% %that used in Sec.~\ref{sec:one}
+% where 
+ \begin{equation}
+   U_{washboard}(y) = U_0 \cos{(N_p \pi y / L)}
+     \label{eq:ysubstrate}
+\end{equation}
+ where $N_p$ are the number of periods,
+ % $L$ is the period length,
+ and $U_0$ is an adjustable parameter
+ to set the depth of the troughs.
+ We define the substrate strength to be
+ the force 
+ $A_p = 2\pi U_0/L$.
+ %
+
+%because 
+We model the 
+particle dynamics 
+with an overdamped
+equation of motion.
+%integrated with the Verlet method.
+%The suspending fluid is highly viscous
+%and exerts a damping force on the particles equivalent
+%to a linear drag force.
+%Overdamped dynamics is a common assumption in models of colloidal particles.
+%This is an assumption that
+The term ``overdamped'' or critically damped indicates
+that an oscillator cannot undergo periodic
+undulations due to some external force. %such as
+%suspension in a viscous fluid \cite{}.
+In our colloidal model we assume
+the damping comes from the viscosity of the fluid,
+where a sphere of radius $0.5 \mu m$ has a Reynolds number
+of $R \approx 10^{-6}$, indicating that linear drag dominates its motion.
+See Section~\ref{sec:problems} Exercise~\ref{ex:reynolds} for more information
+about the Reynold's number.
+We model this
+nonconservative force,
+with the linear friction $\vec{F}_{drag} = -\eta \vec{v}_i$
+sufficient so that
+the acceleration of the particle is zero.
+Such a model is appropriate when the particles
+are small and the viscosity of the suspending medium is high.
+% [finish... discussion of Reynolds number]
+This model should be familiar to readers
+modeling Millikan's oil drops
+in a standard classical mechanics text \cite{Taylor2005}.
+%This model is encountered in standard texts,
+%for instance Ch. 2 of Taylor's Classical Mechanics.
+%more precise: 6\pi \eta a \vec{v}
+
+Newton's second law for an individual particle
+$m \vec{a}_i = \sum \vec{F}$ is simplified
+by the assumption $\vec{a}_i$ is zero in overdamped model.
+%Newton's second law can be rearranged %for the velocity
+%to
+The equation of motion for an isolated particle 
+\begin{equation}
+  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{D}(t).
+    \label{eq:motion}
+\end{equation}
+where the viscosity coefficient $\eta = 1$.
+In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
+we invite the reader to confirm this result.
+The equation of motion provides a direct calculation of the velocity
+of an individual particle from its location $\vec{r}_i$ %in the simulation
+with respect to other particles $j$.
+
+The molecular dynamics simulation is controlled by a $for()$ loop
+ which runs from an initial to maximum integer number of time steps $t_i$.
+Each integer time step interval $t_{i+1}-t_i$
+represents a simulation time interval of $\Delta t$ 
+simulation units.  %as described in Table 1
+At each time step
+we evaluate the net force on each particle as a function of its position
+$\vec{r}_i(t)$
+and then integrate
+the equation of motion to move particles
+to an updated position
+$\vec{r}_i(t+\Delta t)$.
+%
+Since the acceleration as zero,
+[more background here - do the students necessarily know the Verlet method?  no]
+the Verlet method simplifies to 
+the Euler method,
+which is used to calculate the position at subsequent time steps.
+%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
+\begin{equation}
+  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t).
+    \label{eq:euler}
+\end{equation}
+
+The units of the simulated variables are summarized in Table ~\ref{tab:1}.
 
@@
 effective colloidal charge & $Z^*$ \\
-solvent dielectic constant & $\epsilon \epsilon_0$\\
+solvent dielectric constant & $\epsilon \epsilon_0$\\
 force & $E_0 / a_0$\\
@@
 
-We model particle interaction forces
-$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
-with
-the Yukawa potential energy 
-\begin{equation}
-  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
-\end{equation}
-where particle $i$ and $j$ are distance
-$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
-This 
-screened Coulomb potential
-%$E_0=2$ scales strength of repulsion
-is scaled in terms of energy unit $E_0$
-defined in Table ~\ref{tab:1}.
-%$ = k q_1 q_2$. %[CHECK scaling/units].
-$\kappa = 1/R_0$ is the screening parameter 
-that describes the lengthscale at
-which particles interact.
-We fix $R_0$ to be $a_0$.
-In experiments charge screening is observed
-due to ions in the suspending fluid and
-the charges of surrounding particles
-which
-reduces the interaction range of individual particles. % \cite{}.
-Because the particles interact over short ranges, 
-the numerical models can be run efficiency
-using a neighbor list algorithm
-determined using a cell method.
-[explain!]
-
-Particles are subject an external time-dependent driving force
-$\vec{F}_{D}(t)$
-applied parallel to the y-direction.
-We model this force as
-\begin{equation}
-\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y},
-\end{equation}
-with modifiable parameters including
-a constant component $F_{DC}$,
-and a time dependent component with amplitude $F_{AC}$
-and frequency $\omega = 2 \pi f$.
-%The frequency is scaled in time units,
-%where [finish].
-
-We use several model enviroments to confine the particles,
-assuming the confining force arises from a potential function 
- %creating a landscape of potential minima and maxima
- %that modify the force on a particle as a function of position
- $\vec{F}_{l}(\vec{r}) = -\nabla V_l(\vec{r}).$
- The landscape potential $V(\vec{r}) $ are static 
- with fixed minima and maxima
- that are periodic or quasi-periodic,
- as described in Sec.~\ref{sec:results}.
-% 
-% One example of a periodic landscape is
-%% %that used in Sec.~\ref{sec:one}
-% where 
-% \begin{equation}
-%   V_l(y) = V_0 \cos{(N_p \pi y / L)}
-% \end{equation}
-% where $N_p$ are the number of periods,
-% and $V_0$ is an adjustable parameter
-% to set the depth of the troughs.
-%
- In multi-particle simulations, we confine
- the particles along the $x-$direction 
- using a periodic function 
- \begin{equation}
-   U_{q1D}(x) = U_0 \cos{(\pi x / L)}
- \end{equation}.
- %%We could also use a Gaussian function.
- This 
- quasi-one-dimensional geometry
- confines the particles
- primarily to move 
- along the y-direction
- but allows for some lateral motion of particles.
- Otherwise the repulsive interaction between
- particles would cause them to spread throughout the system.
-
-The simulation is controlled by a $for()$ loop
-which runs from an initial to maximum $time$ integer.
-Each integer timestep
-represents a simulation time of $\Delta t=0.001$.
-At each timestep
-we evaluate the net force on each particle as a function of its position
-$\vec{r}_i(t)$
-and then integrate
-the equation of motion to move particles
-to an updated position
-$\vec{r}_i(t+\Delta t)$.
-%
-The integration is simple
-because 
-we model the 
-particle dynamics 
-with an overdamped
-equation of motion.
-%integrated with the Verlet method.
-%The suspending fluid is highly viscous
-%and exerts a damping force on the particles equivalent
-%to a linear drag force.
-%Overdamped dynamics is a common assumption in models of colloidal particles.
-%This is an assumption that 
-The damping comes from a viscous fluid model
-providing a nonconservative force,
-modeled as a linear friction $\vec{F}_{drag} = -\eta \vec{v}_i$
-sufficient so that
-the acceleration of the particle is zero.
-Such a model is appropriate when the particles
-are small and the viscosity of the suspending medium is high.
-% [finish... reference...]
-This model should be familiar to readers
-modeling Milliken's oil drops
-in a standard classical mechanics text \cite{Taylor2005}.
-%This model is encountered in standard texts,
-%for instance Ch. 2 of Taylor's Classical Mechanics.
-
-A particle has the equation of motion 
-\begin{equation}
-\eta \vec{v}_i = \vec{F}_{l,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
-\end{equation}
-where $\eta = 1$.
-The equation of motion provides a direct calculation of the velocity
-of an individual particle from its location in the simulation
-with respect to other particles $j$.
-Since the acceleration as zero,
-the Verlet method simplifies to 
-the Euler method,
-which is used to calculate the position at subsequent time steps.
-%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
-\begin{equation}
-\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t).
-\end{equation}
-
 \section{Results}
@@
  in response to this applied force in a variety of environments.
- In Sec.~\ref{sec:kink} we set $F_{DC}$
+ In Sec.~\ref{sec:kink} we set $F^{DC}$
  to zero and track the motion
@@
 \begin{equation}
-  \label{eq:landscape}
-  V_l(y) = V_{0y} \cos{(N_p \pi y / L)} 
+  \label{eq:landscape_potential}
+  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
 \end{equation}
-%v is the standard I note for substrates
-with $N_p=20$ troughs in the landscape.
+with $N_p=20$ troughs in the landscape
+and landscape period $\lambda = L/N_p = 1.825 a_0$.
+%({\it redundant, just refer back to eq. in Model?})
 %and $V_{0y}=0.2$.
@@
 \begin{equation}
-  \label{eq:landscape}
-  F_y(y) = F_{0y} \sin{(N_p \pi y / L)} 
+  \label{eq:force}
+  F_y(y) = A_{p} \sin{(N_p \pi y / L)} 
 \end{equation}
-where $F_{0y} = 0.1$.
+where $A_{p} = 0.1$.
+
+Because we are performing molecular dynamics
+for a single particle on a smooth potential energy landscape,
+we use a large simulation time step of 
+$\Delta t = 0.01$.
+In Sec.~\ref{sec:sync},
+we decrease the time step
+to treat multiple particle interactions.
+
 We drive the particle with
-$F_{AC}=0.2$, $F_{DC}=0.01$, and $f=0.01$ cycles per time unit.
-When the superposition of $F_{AC}$ and $F_{DC}$ is large enough
+$F^{AC}=0.2$, $F^{DC}=0.01$, and $f=0.01$ cycles per time unit.
+When the superposition of $F^{AC}$ and $F^{DC}$ is large enough
 to overcome the barrier height of the landscape troughs,
@@
 and the initial driving force is minimum
-$F_D(t=0) = F_{DC}$.
+$F_D(t=0) = F^{DC}$.
 Over the time period $T/2 = 50$ %time units
@@
 In Fig. ~\ref{fig:0}
-the displacement is a single wavelength
+the average displacement during one time period is a single wavelength
 of the substrate $y(t_0+T) - y(t_0) = \lambda$.
 Thus the average velocity 
-is $\bar{v}_y = \lambda f$, where $T = 1/f$.
+is $\bar{v}_y = \lambda f$. %, where $T = 1/f$.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{position}
+\includegraphics[width=\columnwidth]{position.png}
 \caption{The position as a function of time of a single driven particle
@@
 
+Phase locked steps occur for average displacements integer
+multiples of the substrate period $n\lambda$.
+
+We sample the average velocity $\langle v_y \rangle $
+as a function of $F^{DC}$.
+
 The hopping pattern of the driven particle is periodic,
-and could be achieved over a range of $F_{DC}$.  %, as we will demonstrate in Fig.~\ref{fig:1}
+and could be achieved over a range of $F^{DC}$.  %, as we will demonstrate in Fig.~\ref{fig:1}
 We explore the ranges of periodic hopping patterns
-by increasing $F_{DC}$ as a function of time,
+by increasing $F^{DC}$ as a function of time,
 as shown in 
@@
 with 
-a constant $F_{AC}$ with frequency $\omega = 2\pi f$
-then slowly increase $F_{DC}$
-at a rate of $\Delta F_{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
+a constant $F^{AC}$ with frequency $\omega = 2\pi f$
+then slowly increase $F^{DC}$
+at a rate of $\Delta F^{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
 or $40$ time units.
@@
 %this is not be so for a multiple particle system!
-By modifying $F_{DC}$ we 
+By modifying $F^{DC}$ we 
 achieve a variety of oscillation modes.
@@
 with a constant average particle velocity, $\bar{v}_{y}$
-over a range of driving forces $F_{DC}$.
+over a range of driving forces $F^{DC}$.
 We illustrate mode-locking in 
@@
 where $n$ is an integer,
-$\lambda = S_Y/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
+$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
 of the landscape,
@@
 Our simulations reproduce results presented in 
-Juniper {\it et al.} \cite{Juniper2015}
+Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
 which demonstrated
@@
 \centering
-\includegraphics[scale=.25]{single}
-\caption{\textbf{(a)} The particle is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through a periodic spatial potential landscape.
+\includegraphics[width=\columnwidth]{single}
+\caption{\textbf{(a)} The particle is driven with a constant amplitude $F^{AC}$ and frequency $\omega$ through a periodic spatial potential landscape.
 The landscape is represented with a colormap where blue are minima and red are maxima in the potential.
-\textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of a constant driving force $F_{DC}$.
+\textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of a constant driving force $F^{DC}$.
 In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\bar{v}_{y}$ at which the particle in Fig.
@@
 
-We simulated a twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
+%-----------------------------------------------
+%environments
+Particles in confined geometries behave differently than free particles.
+Stabilized charged particles form patterns
+due to the interplay of the confining landscape 
+and particle interactions.
+Narrow channels studies are useful to provide insights 
+of how particles move through systems 
+such as charge carries in quantum wires \cite{Tarucha1995} and
+slime molds in microchannels \cite{Gholami2015}.
+%Biological systems such as
+%neuron axons and capillaries can also be studied
+%with these models [more detail and references].
+%Many such systems execute local oscillations
+%about stable points [elaborate].
+%------------------------------------
+ In multi-particle simulations, we confine
+ the particles to a narrow region
+ along the $x-$direction 
+ using a periodic function 
+ \begin{equation}
+   U_{q1D}(x) = U_{q0} \cos{(\pi x / L)}
+     \label{eq:xsubstrate}
+ \end{equation}
+ where $U_{q0}$ defines the channel depth.
+ %%We could also use a Gaussian function.
+ This 
+ quasi-one-dimensional geometry
+ confines the particles
+ primarily to move 
+ along the y-direction
+ but allows for some lateral motion of particles.
+ Otherwise the repulsive interaction between
+ particles would cause them to spread throughout the system.
+ %
+ The total landscape potential energy function is the sum
+ \begin{equation}
+   U_{landscape}(x,y) =  U_{q1D}(x) + U_{washboard}(y)
+   \label{eq:xylandscape}
+ \end{equation}
+
+We explore collective effects in a 
+twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
 with a single period.
@@
   \label{eq:channel}
-  V_l(x) = V_{0x} \cos{(\pi x/L)}
+  U_l(x) = U_{0x} \cos{(\pi x/L)}.
 \end{equation}
-where the trough heights is larger  $V_{0x}$,
-and the associated force
-\begin{equation}
-\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
-\end{equation}
-restores particles to the center of a long narrow region of the simulation.
-The landscape is illustrated in Fig.~\ref{fig:2}(a)
+%where the trough heights is larger  $V_{0x}$,
+%and the associated force
+%\begin{equation}
+%\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
+%\end{equation}
+%restores particles to the center of a long narrow region of the simulation.
+The landscape potential energy is illustrated in Fig.~\ref{fig:2}(a)
 where red regions are high potential
 and blue regions are low potential.
+
+ We model particle interaction forces
+$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
+with
+the Yukawa potential energy 
+\begin{equation}
+  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+  \label{eq:yukawa}
+\end{equation}
+where particle $i$ and $j$ are distance
+$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
+This 
+screened Coulomb potential
+%$E_0=2$ scales strength of repulsion
+is scaled in terms of energy unit $E_0$
+defined in Table ~\ref{tab:1}.
+%$ = k q_1 q_2$. %[CHECK scaling/units].
+$\kappa = 1/R_0$ is the screening parameter 
+that describes the length scale at
+which particles interact.
+We fix the screening length scale $R_0$ to be $a_0$
+(i.e. unity in simulation units).
+In experiments charge screening is observed
+due to ions in the suspending fluid and
+the charges of surrounding particles
+which
+reduces the interaction range of individual particles. % \cite{}.
+Because the particles interact over short ranges, 
+the numerical models can be run efficiency
+using a neighbor list algorithm
+determined using a cell method.
+[explain and reference!]
+
+Newton's second law can be rearranged %for the velocity
+to
+the equation of motion a single particle subject to collective effects is 
+\begin{equation}
+  \eta \vec{v}_i = \vec{F}^l_{i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
+    \label{eq:motion}
+\end{equation}
 
@@
 The molecular dynamics of simulated annealing
-is described in Ref.~\ref{},
-and presented simulations begin with particle configurations
+is described in Ref.~\ref{Allen2017}.
+Once the ground state particle configuration is obtained,
+no further annealing is necessary,
+so the
+our simulations begin with particle configurations
 that result from the annealing process,
@@
 \centering
-\includegraphics[scale=.40]{twenty}
-\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
+\includegraphics[width=\columnwidth]{twenty}
+\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
 The landscape is colored as in Fig.~\ref{fig1}(a).
-\textbf{(b)} Average $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
+\textbf{(b)} Average $\bar{v}_{y}$ versus $F^{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
 \label{fig:2}
@@
 local high density region.
-$F_{DC}/F_{AC} = 1$ [CHECK!]
-
-\section{Quasiperiodic substrate}
+$F^{DC}/F^{AC} = 1$ [CHECK!]
+
+\section{Quasi-periodic substrate}
 \label{sec:quasiperiod}	% You can label sections for reference
@@
 \begin{enumerate}
+\item Stokes' law the viscous drag on a sphere is
+$\vec{F}_{lin} = 3 \pi \eta D \vec{v}$ \cite{}
+where the fluid viscosity is $\eta$,
+$D$ is the particle diameter.
+Assuming a colloid with diameter 
+$D = 1 \mu m$ and
+the viscosity of water at room temperature is
+$\eta = 0.01 cm^2/sec$ \cite{} %CONFIRM!
+%density $\rho = 0.9982 g/cm^3$
+%https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
+Reynold's number $R = D v \rho / \eta$
+where $\rho$ is the fluid density and $v$ the particle's speed.
+When $R$ is small, the quadratic and higher order drag terms
+may be ignored in favor of the linear drag term.
+A typical $v$ in experiment is on the order of $v \sim 1 \mu /s$,
+thus $R \approx 10^-6$.
+\label{ex:reynolds}
+
+\item Newton's second law states that the sum of forces on a particle is proportional to the acceleration of the particle.
+  \begin{equation}
+  m \vec{a}_i = \sum \vec{F}
+  \label{eq:n2l}
+  \end{equation}
+  Demonstrate that Eq.~\ref{eq:motion} is obtained from Newton's second law.
+  \label{ex:n2l}
+
 \item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
@@
 
-\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are neglible
+\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
 
   \item The Fokker-Planck Equation
+
+  \item Aubrey-Kontorova + commensurability
+
+  \item nanotribology
+
+    kink motion
+    Vanossi et al J.Phys.: Condens. Matter 19 (2007)
 
@@
 
-\subsection{Gridded Contour Plot of landscape}
+\subsection{Grid Contour Plot of landscape}
 %code is located in
 %~/pymodules/animation_code/channel_colloid_movie_maker.py
+Testing section - how will putting the code directly in the appendix appear?
 
 \begin{verbatim}
-##########################################################
+############################################
 #ADD CONTOUR PLOT
-##########################################################
+############################################
 def add_contour(ax,L,N,corrugated = True):
     '''
-    Hardwired to color in the quasi1D potential to contain 
+    Hardwired to color quasi1D potential
+    that contains 
     the particles in a trough.  
-    Can also add the washboard/corrugated substrate.
+    Can add the washboard/corrugated substrate.
 
@@
 
-    #assuming Tiare's trough system, so we won't want to cover the entire range
+    #we don't want to cover the entire range
     X = np.arange(0, L/2.0, 0.1)
@@
 
-    #alphs is the degree of transparency, again, set by what looks good.
-    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
+    #alpha = transparency. set by what looks good.
+    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
 
@@
 
-\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygen's clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
+\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygens' clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
 
@@
       %reichhardt review
-      %C.
+    \bibitem{Reichhardt2017} C.
 Reichhardt and C.
@@
 
-    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, PHYSICAL REVIEW E {\bf 77}, 041407 (2008).
+    \bibitem{Juniper2018} Juniper, M.
+P.
+N., Zimmermann, U., Straube, A.
+V., Besseling, R., Aarts, D.
+G.
+A.
+L., Löwen, H., and Dullens, R.
+P.
+A.
+Dynamic mode locking in a driven colloidal system: Experiments and theory.
+New Journal of Physics, 19(1).
+(2017).
+%https://doi.org/10.1088/1367-2630/aa53cd
+
+    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
 
@@
 
-      \bibitem{Grier2003} D. G. Grier, A revolution in optical manipulation. Nature {\bf 424}, 810–816 (2003).
-
-%      Lutz et al. 关11,12兴 created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
+      \bibitem{Grier2003} D. G. Grier, A revolution in optical manipulation. Nature {\bf 424}, 810 (2003).
+
+%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
     \bibitem{Lutz2004} C.
@@
 
-    \bibitem{Tarucha1995}  Tarucha, S.; Honda, T.; Saku, T. Solid State Commun. 1995, 94, 413.
+    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
 
@@
     \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
-    \bibitem{Allen2020} Allen and Tildsley, The Computer Simulation of Liquids.
+    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).
 
@@
 
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[width=5in]{ThreeSunsets.jpg}   % This line stays commented-out
-%\caption{Three overlaid sequences of photos of the setting sun, taken
-%near the December solstice (left), September equinox (center), and
-%June solstice (right), all from the same location at 41$^\circ$ north
-%latitude. The time interval between images in each sequence is approximately
-%four minutes.}
-%\label{sunsets}
-%\end{figure}
-
 \end{document}
-
-\begin{equation}
-\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(2 \pi f t)] \hat{y} 
-\end{equation}
-
-\begin{equation}
-F_{DC} = 0.01
-\end{equation}
-
-\begin{equation}
-F_{AC} = 0.2 
-\end{equation}
-
-\begin{equation}
-f = 0.01 
-\end{equation}
-
-\begin{equation}
-\bar{v}_y = n \lambda f
-\end{equation}
-
-\begin{equation}
-\bar{v}_y = \lambda f
-\end{equation}
-
-\begin{equation}
-\lambda = S_Y / 20
-\end{equation}
-
-\begin{equation}
-F_{p} = 0.1
-\end{equation}
 

### 2020-12-29 code/plot_3Dlandscape.py
made a 3D landscape, but not happy with what that represents to audience, making 2D rep instead

@@ -1,0 +1,153 @@
+#!/usr/bin/env python3
+
+#numeric and basic plotting libraries
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+#from matplotlib import cm
+import matplotlib.cm as cm
+
+import matplotlib.gridspec as gridspec
+
+from mpl_toolkits.mplot3d import Axes3D
+#import mpl_toolkits.mplot3d.Axes3D as Axes3D
+
+
+#set default font of plot
+plt.rc('font', size=20)
+
+##########################################################
+#ADD CONTOUR PLOT
+##########################################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color in the quasi1D potential to contain 
+    the particles in a trough.  
+    Can also add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    #set up plot of 1 row, 3 columns to make the first plot smaller
+    gs=gridspec.GridSpec(1,3)
+    
+    ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
+    ax2 = fig.add_subplot(gs[0,1:], projection='3d')  #scatter plot of particles
+
+    a_p = L/N
+
+    #assuming Tiare's trough system, so we won't want to cover the entire range
+    X = np.arange(0, L/2, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 0.1 # set by what "looks good"
+
+    #create a narrow confining channel for 2D systems
+    if 0:
+        Z = Z_mag*np.cos(2*np.pi*X/L)
+    
+        #create washboard
+    elif corrugated == True:
+        Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
+
+    cmap=cm.coolwarm #_r
+
+    #alphs is the degree of transparency, again, set by what looks good.
+
+    #if 0:
+    cset = ax1.contourf(X, Y, Z, cmap=cmap,alpha=0.5)
+    #else:
[…]

### 2020-12-29 code/plot_landscape.py
made fig. 0

@@ -9,17 +9,14 @@ import matplotlib.cm as cm
 
 import matplotlib.gridspec as gridspec
 
-from mpl_toolkits.mplot3d import Axes3D
-#import mpl_toolkits.mplot3d.Axes3D as Axes3D
-
 
 #set default font of plot
-plt.rc('font', size=20)
+plt.rc('font', size=24)
 
 ##########################################################
 #ADD CONTOUR PLOT
 ##########################################################
-def add_contour(ax,L,N,corrugated = True):
+def add_contour(ax,ax2,L,N): 
     '''
     Hardwired to color in the quasi1D potential to contain 
     the particles in a trough.  
@@ -29,16 +26,9 @@ def add_contour(ax,L,N,corrugated = True):
 
     Optional Arguments:
 
-    corrugated (default = True)  
     Adds the washboard in the y-direction.  
     Hardwired for a single parameter set.    
     '''
-
-    #set up plot of 1 row, 3 columns to make the first plot smaller
-    gs=gridspec.GridSpec(1,3)
-    
-    ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
-    ax2 = fig.add_subplot(gs[0,1:], projection='3d')  #scatter plot of particles
 
     a_p = L/N
 
@@ -49,62 +39,42 @@ def add_contour(ax,L,N,corrugated = True):
 
     Z_mag = 0.1 # set by what "looks good"
 
-    #create a narrow confining channel for 2D systems
+    #create a narrow confining channel for multiparticle 2D systems
     if 0:
         Z = Z_mag*np.cos(2*np.pi*X/L)
     
         #create washboard
-    elif corrugated == True:
-        Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
 
+    Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
+
+    #blue are minima, red are maxima
     cmap=cm.coolwarm #_r
 
-    #alphs is the degree of transparency, again, set by what looks good.
+    #alpha is the degree of transparency, again, set by what looks good.
 
-    #if 0:
[…]

### 2020-12-29 code/plot_landscape.py
made fig. 0

@@ -62,7 +62,7 @@ def add_contour(ax,ax2,L,N):
     ax.set_ylim(0, L)
 
     ax.set_xlabel(r"x",labelpad=-20)
-    ax.set_ylabel(r"y",rotation='horizontal',ha='right')
+    ax.set_ylabel(r"y",rotation='horizontal',ha='right',labelpad=-15)
 
     ax.set_xticks([0,L/2])
     ax.set_yticks([0,L])
@@ -73,7 +73,7 @@ def add_contour(ax,ax2,L,N):
     #ax2.set_xlim(-Z_mag*1.2,Z_mag*1.2)
     ax2.set_xticks([-Z_mag,Z_mag])
     ax2.set_xticklabels([r'-U$_0$','U$_0$'])
-    ax2.set_yticks([])
+    #ax2.set_yticks([])
     return 
 
 ################################################################
@@ -121,8 +121,8 @@ if __name__ == "__main__":
 
     ax1.annotate(r" $\vec{F}^{landscape}$", xytext=(xp, yp+4), xy=(xp, yp), arrowprops=dict(facecolor='black', arrowstyle="<-"),ha="center")
 
-    ax1.text(0.05,0.95,"(a)",transform = ax1.transAxes)
-    ax2.text(0.05,0.95,"(b)",transform = ax2.transAxes)
+    ax1.text(0.03,0.94,"(a)",transform = ax1.transAxes)
+    ax2.text(0.03,0.94,"(b)",transform = ax2.transAxes)
     
     #plot the "side view" of the potential
 
@@ -131,7 +131,7 @@ if __name__ == "__main__":
     #annotate variables on plot
 
     #configure and save the image
-    fig.tight_layout(pad=0.0) #h_pad=-0.5,w_pad=1.0,pad=0.5)
+    fig.tight_layout(pad=0.5) #h_pad=-0.5,w_pad=1.0,pad=0.5)
     image_test_name = "landscape.png"
     plt.savefig(image_test_name)
 

### 2020-12-29 code/plot_landscape.py
made figure in pdf

@@ -132,7 +132,7 @@ if __name__ == "__main__":
 
     #configure and save the image
     fig.tight_layout(pad=0.5) #h_pad=-0.5,w_pad=1.0,pad=0.5)
-    image_test_name = "landscape.png"
+    image_test_name = "landscape.pdf"
     plt.savefig(image_test_name)
 
     #sys.exit()

### 2020-12-29 code/plot_landscape.py
adding period bar

@@ -119,6 +119,13 @@ if __name__ == "__main__":
 
     ax2.annotate(r" $\vec{F}^{landscape}$", xytext=(zp, yp+0.5), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05)) #arrowstyle="<-",
 
+    #add period
+    ax2.annotate('r$\lambda = L/N_p$', xy=(5, 1.5), ha='center', va='center')
+    ax2.annotate('', xy=(4, 1), xytext=(6, 1),
+                 xycoords='data', textcoords='data',
+                 arrowprops={'arrowstyle': '|-|'})
+
+    
     ax1.annotate(r" $\vec{F}^{landscape}$", xytext=(xp, yp+4), xy=(xp, yp), arrowprops=dict(facecolor='black', arrowstyle="<-"),ha="center")
 
     ax1.text(0.03,0.94,"(a)",transform = ax1.transAxes)

### 2020-12-29 code/plot_landscape.py
annotation of period length

@@ -63,6 +63,7 @@ def add_contour(ax,ax2,L,N):
 
     ax.set_xlabel(r"x",labelpad=-20)
     ax.set_ylabel(r"y",rotation='horizontal',ha='right',labelpad=-15)
+    ax2.set_ylabel(r"y",rotation='horizontal',ha='right',labelpad=-15)
 
     ax.set_xticks([0,L/2])
     ax.set_yticks([0,L])
@@ -117,14 +118,21 @@ if __name__ == "__main__":
     scatter1=ax1.scatter(xp,yp,edgecolor='k',s=200)
     scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
 
-    ax2.annotate(r" $\vec{F}^{landscape}$", xytext=(zp, yp+0.5), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05)) #arrowstyle="<-",
+    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05)) #arrowstyle="<-",
+    ax2.annotate(r" $\vec{F}^{landscape}$", xy=(0+0.02, Sy/2-1), ha='center', va='center') 
 
-    #add period
-    ax2.annotate('r$\lambda = L/N_p$', xy=(5, 1.5), ha='center', va='center')
-    ax2.annotate('', xy=(4, 1), xytext=(6, 1),
+    #add annotation showing period
+    ax2.annotate(r'$\lambda$', xy=(-0.9*Z_mag,2*Sy/3), ha='center', va='center')
+    ax2.annotate('', xy=(-1.01*Z_mag,2*Sy/3-Sy/6),
+                 xytext=(-1.01*Z_mag,2*Sy/3+Sy/6),
                  xycoords='data', textcoords='data',
-                 arrowprops={'arrowstyle': '|-|'})
+                 arrowprops={'arrowstyle': '<|-|>','color':"red"})
 
+    ax1.annotate(r'$\lambda$', xy=(2,2*Sy/3), ha='center', va='center')
+    ax1.annotate('', xy=(0.5,2*Sy/3-Sy/6),
+                 xytext=(0.5,2*Sy/3+Sy/6),
+                 xycoords='data', textcoords='data',
+                 arrowprops={'arrowstyle': '<|-|>','color':"red"})
     
[…]

### 2020-12-29 code/plot_landscape.py
added F^drive

@@ -103,7 +103,7 @@ if __name__ == "__main__":
 
     #place single particle on plot
     xp=Sx*0.25
-    yp=Sy*0.41
+    yp=Sy*0.59
     Z_mag=0.1
     zp=Z_mag*np.cos(2*np.pi*yp/(Sy/n_corr))
 
@@ -112,14 +112,14 @@ if __name__ == "__main__":
 
     #slope = dy/dz, dz=1, zf-zp=Z_mag, yf-yp=slope
     zf=zp-Z_mag/1.8+0.02
-    yf=yp-slope*Z_mag/1.8+0.6
+    yf=yp - slope*Z_mag/1.8 - 0.6
     
 
     scatter1=ax1.scatter(xp,yp,edgecolor='k',s=200)
     scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
 
-    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05)) #arrowstyle="<-",
-    ax2.annotate(r" $\vec{F}^{landscape}$", xy=(0+0.02, Sy/2-1), ha='center', va='center') 
+    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05,color='magenta')) #arrowstyle="<-",
+    ax2.annotate(r"$\mathrm{\vec{F}^{l}}$", xy=(0+0.02, Sy/2), ha='center', va='center',color='magenta') 
 
     #add annotation showing period
     ax2.annotate(r'$\lambda$', xy=(-0.9*Z_mag,2*Sy/3), ha='center', va='center')
@@ -134,7 +134,8 @@ if __name__ == "__main__":
                  xycoords='data', textcoords='data',
                  arrowprops={'arrowstyle': '<|-|>','color':"red"})
     
-    ax1.annotate(r" $\vec{F}^{landscape}$", xytext=(xp, yp+4), xy=(xp, yp), arrowprops=dict(facecolor='black', arrowstyle="<-"),ha="center")
+    ax1.annotate(r"$\mathrm{\vec{F}^{l}}$", xytext=(xp, yp-6), xy=(xp, yp), arrowprops=dict(color='magenta', arrowstyle="<-"),ha="center")
[…]

### 2020-12-29 code/plot_landscape.py
updated arrows

@@ -118,8 +118,8 @@ if __name__ == "__main__":
     scatter1=ax1.scatter(xp,yp,edgecolor='k',s=200)
     scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
 
-    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(facecolor='black', shrink=0.05,color='magenta')) #arrowstyle="<-",
-    ax2.annotate(r"$\mathrm{\vec{F}^{l}}$", xy=(0+0.02, Sy/2), ha='center', va='center',color='magenta') 
+    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(shrink=0.05,color='magenta')) #arrowstyle="<-",
+    ax2.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(0+0.02, Sy/2), ha='center', va='center',color='magenta') 
 
     #add annotation showing period
     ax2.annotate(r'$\lambda$', xy=(-0.9*Z_mag,2*Sy/3), ha='center', va='center')
@@ -134,8 +134,11 @@ if __name__ == "__main__":
                  xycoords='data', textcoords='data',
                  arrowprops={'arrowstyle': '<|-|>','color':"red"})
     
-    ax1.annotate(r"$\mathrm{\vec{F}^{l}}$", xytext=(xp, yp-6), xy=(xp, yp), arrowprops=dict(color='magenta', arrowstyle="<-"),ha="center")
-    ax1.annotate(r"$\mathrm{\vec{F}^{D}}$", xytext=(xp, yp+8), xy=(xp, yp), arrowprops=dict(color='gray', arrowstyle="<-"),ha="center")
+    ax1.annotate("", xy=(xp, yp-6), xytext=(xp, yp), arrowprops=dict(color='magenta', shrink=0.05),ha="center")
+    ax1.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(xp+1, yp-6),ha="left",va="center")
+    
+    ax1.annotate("", xy=(xp, yp+8), xytext=(xp, yp), arrowprops=dict(color='gray', shrink=0.05), ha="center")
+    ax1.annotate(r"$\mathrm{\vec{F}^{D}(t)}$",  xy=(xp+1, yp+8),ha="left")
 
     ax1.text(0.03,0.94,"(a)",transform = ax1.transAxes)
     ax2.text(0.03,0.94,"(b)",transform = ax2.transAxes)

### 2020-12-29 manuscript/manuscript_ajp_2020.tex
added schematic of simulation!

@@
 We describe
-our molecular dynamics model in Section~\ref{sec:MD}
-In this section, we restrict our discussion to a single particle,
-and include additional information
-for multiple particles in Section~\ref{sec:sync}.
+our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
+%In this section, we restrict our discussion to a single particle,
+%and include additional information
+%for multiple particles in Section~\ref{sec:sync}.
 %including various  and confining environments.
@@
 driven across a periodic landscape in 
-Section~\ref{sec:one} and
-multiple interacting particles
-in Section~\ref{sec:sync},
-including stationary propagation of high density kinks
-in Sec.~\ref{sec:kink}.
-We include code to simulate
-and visualize the landscape and dynamics in this section
-and supplementary material.
+Section~\ref{sec:one}.
+In Section~\ref{sec:sync}
+we 
+extend the model to include multiple particles,
+and show how confined 
+interacting particles respond to the same applied driving force.
+%including stationary propagation of high density kinks
+%in Sec.~\ref{sec:kink}.
+%We include code to simulate
+%and visualize the landscape and dynamics in this section
+%and supplementary material.
 %we
@@
 %and create synchronized flow patterns.
-We present these results using standard tools of non-linear oscillators
-such phase diagrams of velocity versus position.
+%We present these results using standard tools of non-linear oscillators
+%such phase diagrams of velocity versus position.
 %PHASE DIAGRAMS SHOWING COUPLING, OR QUASI-PERIODIC COUPLING
@@
 %in Section~\ref{sec:conclusion}. 
-In each section
-we suggest exercises for interested students,
-as summarized in Section~\ref{sec:problems}.
+We conclude with
+exercises for interested students 
+in Section~\ref{sec:problems}.
 
@@
 \label{sec:MD}
-In this section we describe the dynamics of the particles
-using the model forces
-and the motion using an modified form of Newton's second law
-suitable for microscopic particles in a suspending fluid.
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{landscape.pdf}
+\caption{
+  Schematic of the simulation
+  of a single particle
+  driven across a washboard potential
+  energy landscape.
+  (a) View of the $x-y$ plane. %of the simulation
+  The time-dependent applied driving force $\vec{F}^D$
+  is parallel to the y-axis.
+  The force due to the landscape %$\vec{F}^l$
+  is calculated due to the gradient of the potential
+  energy 
+  $\vec{F}^l = -\nabla U(\vec{r})$.
+  (b) The potential energy function
+  along the y-axis $U_l(y)$
+  with period $\lambda = L/N_p$
+  where the number of periods is $N_p = 3$.
+  }
+\label{fig:landscape0}
+\end{figure}
+\end{center}
 
 We use a classical two-dimensional model for 
-studying the dynamics of $N$ interacting particles.
+studying the dynamics of $N$ interacting particles,
+using the net force on each particle to calculate
+its trajectory.
 Particles are confined in a two-dimensional (2D) 
@@
 and velocity $\vec{v}_i = d\vec{r}_i/dt$.
-Particles are subject to
+The edges of the system are treated with
 periodic boundary conditions
@@
 %and particles interact across PBC.
+We show a schematic of the system in Fig.~\ref{fig:0}
+
+We confine the particles using a position dependent 
+potential energy function, called a landscape or substrate.
+The confining force %arises from a potential function 
+ %creating a landscape of potential minima and maxima
+%that modify the force on a particle as a function of position
+is calculated as 
+ $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
+ %The landscape potential energy $U(\vec{r})$ is static 
+ %with fixed minima and maxima
+ %that are periodic or quasi-periodic,
+ %as described in Sec.~\ref{sec:results}.
+% 
+The periodic landscape is modulated in the y-direction as
+%% %that used in Sec.~\ref{sec:one}
+% where 
+ \begin{equation}
+   U(y) = U_0 \cos{(N_p \pi y / L)}
+     \label{eq:ysubstrate}
+\end{equation}
+ where $N_p$ are the number of periods,
+ % $L$ is the period length,
+ and $U_0$ is an adjustable parameter
+ to set the depth of the troughs.
+ We define the substrate strength to be
+ the maximum force the substrate can exert on a particle 
+ $A_p = 2\pi U_0/L$.
+ %
 
@@
 
-We confine the particles using a position dependent 
-potential energy function, called a landscape or substrate.
-The confining force %arises from a potential function 
- %creating a landscape of potential minima and maxima
-%that modify the force on a particle as a function of position
-is calculated as 
- $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
- %The landscape potential energy $U(\vec{r})$ is static 
- %with fixed minima and maxima
- %that are periodic or quasi-periodic,
- %as described in Sec.~\ref{sec:results}.
-% 
-The periodic landscape is modulated in the y-direction as
-%% %that used in Sec.~\ref{sec:one}
-% where 
- \begin{equation}
-   U_{washboard}(y) = U_0 \cos{(N_p \pi y / L)}
-     \label{eq:ysubstrate}
-\end{equation}
- where $N_p$ are the number of periods,
- % $L$ is the period length,
- and $U_0$ is an adjustable parameter
- to set the depth of the troughs.
- We define the substrate strength to be
- the force 
- $A_p = 2\pi U_0/L$.
- %
-
 %because 
@@
 %This is an assumption that
-The term ``overdamped'' or critically damped indicates
+The term `overdamped or critically damped indicates
 that an oscillator cannot undergo periodic
@@
 length &  $a_0$ \\
+energy & $E_0$ \\
 %electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
-energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
-dimensionless interaction strength & $q$ \\
-effective colloidal charge & $Z^*$ \\
-solvent dielectric constant & $\epsilon \epsilon_0$\\
+%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
+%dimensionless interaction strength & $q$ \\
+%effective colloidal charge & $Z^*$ \\
+%solvent dielectric constant & $\epsilon \epsilon_0$\\
 force & $E_0 / a_0$\\
@@
 time &  $\eta / E_0$ \\
-velocity &  $ E_0 / \eta a_0$ \\
+velocity &  $ (E_0 / \eta) a_0$ \\
 \end{tabular}

### 2020-12-30 manuscript/manuscript_ajp_2020.tex
found a sign error!

@@
   across a washboard potential energy landscape
-  exhibit a variety of synchronization effects
-  in
-  experimental systems 
-  %interest to condensed matter physics 
-  including 
-  magnetically driven colloidal particles
-  confined by light-fields.
+  exhibit a variety of synchronization effects.
+  %in
   %  Numerical model
@@
   a viscous liquid.
+  This model reproduces behaviors observed
+  in experimental systems 
+  of interest to condensed matter physics 
+  including 
+  magnetically driven colloidal particles
+  confined by light-fields.
+  %
   %applied to single and multiple particle systems.
@@
   animations of the particle motion.
-  Our results show a variety of systems that
-  synchronize 
+  Our results show a variety of synchronization effects 
+  in single and multi-particle systems, 
   %and detect synchronization using
   %measurements of
+  which we characterize with
+  plots of 
   particle velocity as a function of applied driving force,
-  and characterize these behaviors
-  with force-velocity curves and phase diagrams.
-  We include sample code
-  and exercises for students
-  %that include
-  with 
-  opportunities
-  to reproduce our results and propose
-  new numerical experiments.
+  and phase diagrams of position versus velocity.
+  %We include sample code
+  %and exercises for students
+  %with 
+  %opportunities
+  %to reproduce our results and propose
+  %new numerical experiments.
   %With only a few particles in two-dimensions,
@@
   %making this an appropriate model for undergraduates to explore.  
-
-  %Hew to this recipe (MMRC) witlessly
-  %1. M—Give the motivation and context
-  %2. M—Explain what you did in sufficient
-  %detail so the audience knows if your work
-  %is relevant and applicable to his or hers
-  %3. R—Emphasize your key results
-  %4. C—Tell the reader what you think the
-  %results mean
-
 \end{abstract}
@@
 
-Experiments with colloid particles,
-such as plastic beads suspended in
-highly de-ionized water \cite{},
-are useful model systems
-to understand complex behaviors.
-%silica spheres in organic solvents
-%magnetic spheres?
+Complex dynamics can be studied with
+colloid particles with experiments and simulation.
+In experiment, colloids are typically spheres of 
+plastic suspended in
+highly de-ionized water or silica in suspended in organic solvent.
+%experimental - colloids specifically
+The spheres are a few microns in size
+and move at rates of microns per second,
+so a system can be imaged
+with a traditional optical camera
+due to the large size and slow speed of the particles.
+Individual colloids exhibit 
+Brownian motion,
+where particles change direction in a seemly random fashion
+due to unseen 
+collisions 
+with particles comprising the suspending fluid \cite{}.
+Brownian motion is a temperature dependent
+phenomena affecting quantum mechanically small systems. \cite{}
+[elaborate].
+
+Due to the relative ease of
+manipulation and imagining, 
+colloids are used as experimental models
+for systems relatively hard to access and visualize. 
+%SAME SENTENCE TWICE
+Collections of colloids can
+be used to study the properties of solids and liquids
+%comprised of smaller particles
+%such as atoms \cite{} or electrons \cite{}
+or more exotic systems 
+such as cold atoms or electron gases \cite{Grier2003}.  
+The interaction forces between colloids can be controlled 
+by altering the chemistry of the suspending fluid
+or surface ligands of the particles.
+Thus colloids can 
+be modified to mimic different
+systems such as hard spheres interacting via contact forces \cite{},
+dipole interactions \cite{},
+and long range electrostatic interactions \cite{}.
+
+Light is a
+tool for manipulating the colloidal environment.
+A single laser beam can be used to create an optical trap,
+which uses 
+photon radiation pressure to
+control colloid motions.
+A circular optical trap is designed so the center is
+a local energy minimum where 
+a colloid in the beam center is subject to a
+uniform distribution of photon bombardment. %, making 
+Colloids at a trap edge
+experience a net force
+due to the uneven 
+distribution of photon collisions on its surface.
+Depending on the shape of the trap and location of the particle in the trap,
+the radiation pressure either pushes colloids toward the local minima
+or ejects it from the trap.
+A single optically trapped colloid executing Brownian motion
+is a useful probe of microscopic forces,
+and has been studied in detail in Ref.~\cite{Volpe2013}.
+
+Complex environments can be
+engineered with light by %, typically made 
+using diffraction gratings to create a patterned
+potential energy landscape 
+with one or more laser beams \cite{}.
 %
+
 Experiments of colloid particles confined
-in optical traps
+in optical traps arrays or patterns 
 subject to external driving forces 
@@
 been used to examine the microscopic dynamics
-of individual particles during mode-locking,
-which cannot be easily imaged in electronics.
-%experimental - colloids specifically
-Colloidal particles trapped in light fields are %have proven
-a useful medium for studying complex dynamical behaviors  %cite
-due to their 
-relatively large size of microns,
-making them relatively simple 
-to control and image.
-Additionally colloids can mimic different
-systems since 
-the interaction forces between colloids can be modified
-by tuning the chemistry of the suspending fluid or surface ligands
-of the particles.
-Because colloids are easy to control and study, 
-they are used as experimental models
-for systems relatively hard to access and visualize,
-such as cold atoms or electron gases \cite{Grier2003}. %ELABORATE AND CITE
+of individual particles during mode-locking \cite{Juniper2015}.
+This produced step-by-step diagrams
+of particle dynamics that cannot be 
+imaged in electronic systems such as Josephson junctions.
 %Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
-Mode-locking 
-in colloids has been achieved in systems interacting via magnetic dipoles 
-or electric forces 
-in experiment \cite{Juniper2015, Lutz2004} and
-simulation \cite{Herrera-Velarde2007, Herrera-Velarde2008}.
-
+Thus the study of
+mode-locking is a useful problem
+of complex quantum mechanical systems.
+Mode-locked 
+colloid dynamics have been achieved in 
+experiments \cite{Juniper2015, Lutz2004} and
+simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
+for a variety of interaction types such as 
+magnetic dipoles and electric forces.
 %-----------------------------------------------------------
@@
 
+Numerical modeling of colloids can provide mechanistic insight
+that can be difficult to achieve in experimental conditions
+where Brownian motion and other sources of noise dominate.
+
 %Given the prevalence of synchronization,
@@
 and ease of simulation.
-Numerical modeling of colloids can provide mechanistic insight
-that can be difficult to achieve in experimental conditions
-where Brownian motion and other sources of noise dominate.
 %We examine
@@
 our results 
-in Section~\ref{sec:results} 
+%in Section~\ref{sec:results} 
 including synchronized motion of a single confined particle
@@
 
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{landscape.pdf}
-\caption{
-  Schematic of the simulation
-  of a single particle
-  driven across a washboard potential
-  energy landscape.
-  (a) View of the $x-y$ plane. %of the simulation
-  The time-dependent applied driving force $\vec{F}^D$
-  is parallel to the y-axis.
-  The force due to the landscape %$\vec{F}^l$
-  is calculated due to the gradient of the potential
-  energy 
-  $\vec{F}^l = -\nabla U(\vec{r})$.
-  (b) The potential energy function
-  along the y-axis $U_l(y)$
-  with period $\lambda = L/N_p$
-  where the number of periods is $N_p = 3$.
-  }
-\label{fig:landscape0}
-\end{figure}
-\end{center}
-
-We use a classical two-dimensional model for 
+We use a classical model for 
 studying the dynamics of $N$ interacting particles,
@@
 %and particles interact across PBC.
-We show a schematic of the system in Fig.~\ref{fig:0}
+We show a schematic of the system in Fig.~\ref{fig:landscape0}(a).
 
@@
 % 
-The periodic landscape is modulated in the y-direction as
+The landscape is modulated in the y-direction
+with the periodic function 
 %% %that used in Sec.~\ref{sec:one}
@@
  and $U_0$ is an adjustable parameter
- to set the depth of the troughs.
- We define the substrate strength to be
- the maximum force the substrate can exert on a particle 
- $A_p = 2\pi U_0/L$.
+ to set the depth of the minima
+ with simulation units of energy $E_0 = 1$. 
+ %We define the substrate strength to be
+ %the maximum force the substrate can exert on a particle 
+ %$A_p = 2\pi U_0/L$.
  %
+ We plot this function in 
+ Fig.~\ref{fig:landscape0}
+ we use $N_p = 3$ to illustrate the features of
+ Eq.~\ref{eq:ysubstrate}.
+ In Fig.~\ref{fig:landscape0}(a) we show 
+ the $x-y$ plane with a contour plot
+ of the the 2D potential energy landscape,
+ where 
+ the maxima are colored red and the minima colored blue.
+ In Fig.~\ref{fig:landscape0}(b) we plot the function
+ $U(y)$ to illustrate how the magnitude
+ $\vec{F}^{l}_i$ is calculated from particle position in the $y-$direction.
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{landscape.pdf}
+\caption{
+  Schematic of the simulation
+  of a single particle
+  driven across a washboard potential
+  energy landscape.
+  The period of the landscape, $\lambda = L/N_p$ 
+  where $N_p = 3$, is marked in red.
+  The force due to the landscape %$\vec{F}^l$
+  is calculated from the gradient of the potential
+  energy 
+  $\vec{F}^l = -\nabla U(\vec{r})$.
+  (a) View of the $x-y$ plane. %of the simulation
+  The time-dependent applied driving force $\vec{F}^D$
+  is parallel to the y-axis.
+  The landscape is shown with a contour plot,
+  with maxima in the potential energy marked in red
+  and minima marked in blue.
+  A particle is shown in the region between minima and maxima
+  subject to competing forces due to the landscape and applied driving force.
+  (b) The potential energy function
+  along the y-axis $U_l(y)$,
+  The particle in (a) is shown at the same $y-$position,
+  where the magnitude of force $\vec{F}^l$ is calculated as the slope of this function,
+  directed along the $y-$direction in panel (a).
+  }
+\label{fig:landscape0}
+\end{figure}
+\end{center}
 
@@
 and frequency $\omega = 2 \pi f$.
-%The frequency is scaled in time units,
-%where [finish].
+We illustrate this force in Fig.~\ref{fig:landscape0}(a)
+in the positive $y-$direction.
+%but it may 
+%be zero or negative depending the the parameters and time.
 When $F^{DC}$ is non-zero,  
@@
 %This is an assumption that
-The term `overdamped or critically damped indicates
+The term overdamped or critically damped indicates
 that an oscillator cannot undergo periodic
@@
 where a sphere of radius $0.5 \mu m$ has a Reynolds number
-of $R \approx 10^{-6}$, indicating that linear drag dominates its motion.
+of $R \approx 10^{-6}$, indicating that linear drag dominates
+the particle motion.
 See Section~\ref{sec:problems} Exercise~\ref{ex:reynolds} for more information
 about the Reynold's number.
-We model this
+In the overdamped model the
+linear friction produced by this 
 nonconservative force,
-with the linear friction $\vec{F}_{drag} = -\eta \vec{v}_i$
+$\vec{F}_{drag} = -\eta \vec{v}_i$ is 
 sufficient so that
@@
 are small and the viscosity of the suspending medium is high.
-% [finish... discussion of Reynolds number]
-This model should be familiar to readers
-modeling Millikan's oil drops
-in a standard classical mechanics text \cite{Taylor2005}.
-%This model is encountered in standard texts,
-%for instance Ch. 2 of Taylor's Classical Mechanics.
-%more precise: 6\pi \eta a \vec{v}
 
@@
 %to
-The equation of motion for an isolated particle 
+The equation of motion for an isolated particle is
+%solved for velocity 
 \begin{equation}
@@
 \end{equation}
-where the viscosity coefficient $\eta = 1$.
+with the viscosity coefficient $\eta = 1$,
+which we describe in more detail in Exercise~\ref{ex:reynolds}.
 In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
 we invite the reader to confirm this result.
+
 The equation of motion provides a direct calculation of the velocity
 of an individual particle from its location $\vec{r}_i$ %in the simulation
-with respect to other particles $j$.
-
+and the simulation time.
 The molecular dynamics simulation is controlled by a $for()$ loop
@@
 Since the acceleration as zero,
-[more background here - do the students necessarily know the Verlet method?  no]
-the Verlet method simplifies to 
-the Euler method,
-which is used to calculate the position at subsequent time steps.
-%Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
+the integration of the equation of motion
+is performed via 
+the Euler method 
 \begin{equation}
-  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t).
+  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)
     \label{eq:euler}
 \end{equation}
-
+for a small time step $\Delta t$.
+In Section~\ref{sec:problems} Exercise~\ref{ex:euler}
+we elaborate on
+the numerical methods for 
+solving differential equations,
+and demonstrate how the Verlet method
+simplifies to the Euler method when $\vec{a}=0$.
+%
 The units of the simulated variables are summarized in Table ~\ref{tab:1}.
@@
 \hline
-length &  $a_0$ \\
-energy & $E_0$ \\
+length &  $a_0 = 1$ \\
+energy & $E_0 = 1$ \\
 %electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
@@
 force & $E_0 / a_0$\\
-viscosity/damping constant & $\eta$ \\
-time &  $\eta / E_0$ \\
-velocity &  $ (E_0 / \eta) a_0$ \\
+viscosity coefficient & $\eta = 1$ \\
+velocity &  $ E_0 / (\eta a_0) $ \\
+time &  $(\eta / E_0) {a_0}^2$ \\
 \end{tabular}
@@
 
-\section{Results}
-\label{sec:results}
- We demonstrate how a single particle (Sec.~\ref{sec:one})
- and many particles
- move (Sec.~\ref{sec:sync})
- in response to this applied force in a variety of environments.
- In Sec.~\ref{sec:kink} we set $F^{DC}$
- to zero and track the motion
- of a high density area of a particle chain
- (i.e. kink dynamics).
+%\section{Results}
+%\label{sec:results}
+% We demonstrate how a single particle (Sec.~\ref{sec:one})
+% and many particles
+% move (Sec.~\ref{sec:sync})
+% in response to this applied force in a variety of environments.
+% In Sec.~\ref{sec:kink} we set $F^{DC}$
+% to zero and track the motion
+% of a high density area of a particle chain
+% (i.e. kink dynamics).
  %The driving force does add energy into the system, and some of it is lost.
 %
-\subsection{Single particle system}
+\section{Mode-locking of a single particle}
 % In subsection headings, only the first word is capitalized.
@@
 We drive a single particle across a periodic landscape 
-along the y-direction 
-\begin{equation}
-  \label{eq:landscape_potential}
-  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
-\end{equation}
-with $N_p=20$ troughs in the landscape
-and landscape period $\lambda = L/N_p = 1.825 a_0$.
+along the y-direction described in Eq.~\ref{eq:ysubstrate}
+%\begin{equation}
+%  \label{eq:landscape_potential}
+%  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
+%\end{equation}
+with $N_p=20$ %troughs in the landscape
+and landscape period $\lambda = 1.825 a_0$.
 %({\it redundant, just refer back to eq. in Model?})
 %and $V_{0y}=0.2$.
-This is illustrated in Fig.~\ref{fig:1}(a) where
-the red (blue) regions show local maxima (minima).
-The code for generating
-a two dimensional colored plot
-of the potential landscape
-is calculated by evaluating
-the analytic function in Eq.~\ref{eq:landscape}
-for a grid of values $(x_n,y_n)$.
-%is included in the supplementary material,
+%This is illustrated in Fig.~\ref{fig:1}(a) where
+%the red (blue) regions show local maxima (minima).
+%
 The numerical implementation of the landscape 
@@
   \label{eq:force}
-  F_y(y) = A_{p} \sin{(N_p \pi y / L)} 
+  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
 \end{equation}
-where $A_{p} = 0.1$.
-
-Because we are performing molecular dynamics
-for a single particle on a smooth potential energy landscape,
-we use a large simulation time step of 
-$\Delta t = 0.01$.
-In Sec.~\ref{sec:sync},
-we decrease the time step
-to treat multiple particle interactions.
-
-We drive the particle with
-$F^{AC}=0.2$, $F^{DC}=0.01$, and $f=0.01$ cycles per time unit.
-When the superposition of $F^{AC}$ and $F^{DC}$ is large enough
-to overcome the barrier height of the landscape troughs,
-the particle hops between troughs in the energy landscape.
+where the force is scaled with parameter $A_{p} = 0.1$
+in simulation units for force. % $E_0/a_0$.
+
+%%HMMM... HAVE YOU INTRODUCED A PHASE SHIFT?
+
 In Fig.~\ref{fig:0} we
@@
 In Fig.~\ref{fig:0}(a)
-we plot the applied driving force
-as a function of time
-and in Fig.~\ref{fig:0}(b) 
-we show the position of the particle
+we plot the applied driving force defined in Eq.~\ref{eq:drive}
 as a function of time.
-The initial position is near $y=0$
-and the initial driving force is minimum
-$F_D(t=0) = F^{DC}$.
-Over the time period $T/2 = 50$ %time units
+The time independent constants are 
+$F^{AC}=0.2$, $F^{DC}=0.01$, and $f=0.01$ cycles per time unit.
+The time period of the driving force is
+$T = 1/f = 100$,
+with the initial driving force at is minimum value 
+$F^D(0) = F^{DC}$.
+
+In Fig.~\ref{fig:0}(b) 
+we show the $y-$position of the particle
+as a function of time,
+where we 
+normalize $y$ by the spatial period of the washboard as
+$y/\lambda$.
+The initial particle position is $y=0$,
+where the landscape force is minimum $F^l = 0$.
+Subsequent substrate 
+%CHECK!!! I THINK THIS IS WRONG!!!
+%BY NOT INCLUDING THE SIGN YOU'VE DEFINED IT BACKWARDS!!!!!
+%AND LOCATED THE INITIAL POSITION OF THE PARTICLE
+%AT A LOCAL MAXIMA!!!!!
+%The substrate maxima are located at integer multiples of $y/\lambda = 0, 1, 2 $ 
+%and
+minima are located at integer multiples $y/\lambda = 1/2, 3/2, 5/2, $ {\it et cetera}.
+%This is apparent in the spacing of $y/\lambda$ in time,
+%where the visual gaps between positions in Fig.~\ref{fig:0}(b) 
+%at half integer multiples $y/\lambda = 1/2, 3/2, 5/2$ indicate regions the particle was moving slowly.
+%measure/plot velocity?
+
+When $F^D(t) > A_p$, a particle can 
+overcome the barrier height of the landscape troughs,
+and 
+the particle hops between minima in the energy landscape.
+In Fig.~\ref{fig:0} we demonstrate this relationship,
+where over half of a driving period ($T = 50$) %time units
+while $F_{D}(t) > 0 $ 
 the particle moves
 in the positive y-direction
-while $F_{D}(t) > 0 $
 through three
@@
 of $y/\lambda = 1$
-over the period $T = 1/f = 100$.
+over the total period $T = 100$.
 The average velocity $\bar{v}_y$
@@
 may be ignored in favor of the linear drag term.
-A typical $v$ in experiment is on the order of $v \sim 1 \mu /s$,
+A velocity $v$ in experiment is on the order of $v \sim 1 \mu /s$,
 thus $R \approx 10^-6$.
+
+This model should be familiar to readers
+of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
+when studying 
+models Millikan's oil drops.
 \label{ex:reynolds}
@@
   \label{ex:n2l}
+
+\item
+  Generally when solving differential equations,
+  the Euler method is effective for solving linear equations,
+  such as the one-dimensional 
+  $f(y) = df/dy$ 
+  but not higher order methods.
+
+  The Verlet method simplifies to
+
+  %FOLLOW UP WITH THIS!
+  Because we are performing molecular dynamics
+  for a single particle on a smooth potential energy landscape,
+  we use a large simulation time step of 
+  $\Delta t = 0.01$.
+  In Sec.~\ref{sec:sync},
+  we decrease the time step
+  to treat multiple particle interactions.
+
+  \label{ex:euler}
+
+\item Drawing the contour
+
+  The code for generating
+a two dimensional colored plot
+of the potential landscape
+is calculated by evaluating
+the analytic function in Eq.~\ref{eq:landscape}
+for a grid of values $(x_n,y_n)$.
+%is included in the supplementary material,
 
@@
 
+      \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013
+
 %Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls

### 2020-12-31 code/MD_colloid.py
updated MD code to handle more parameters

@@ -14,13 +14,31 @@ Tiare Guerrero
 import numpy as np
 import math
 import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+#set default font of plot
+plt.rc('font', size=24)
 
 ##################################################################
-def landscape_potential(V0,y,period):
-    '''but what is the landscape force?
+def landscape_force(F0,y,period):
+    '''landscape potential is equation (1) in the manuscript, while force is equation (5) - for now anyway
+
+    U(y) = U0 cos(Np*pi*y/L)
+
+    F_y = -dU/dy = -U0/period * sin(Np*pi*y/L)
+
+    potential minima occur at U(y) = -U0, or cos(Np*pi*y/L) = -1
+    meaning Np*pi*y/L = m pi, where m is odd
+    
+    Required Parameters
+    period: float 
+    the spatial period of the washboard potential, should be the system length divided by the number of minima  (L/Np)
+
+    y: float
+    the location in the y-direction of the individual particle
     '''
     
-    return V0*np.sin(2*np.pi*y/period)
+    return -F0*np.sin(np.pi*y/period)
 
 ###################################################################
 def external_drive(F_AC,F_DC,frequency,time):
@@ -51,10 +69,10 @@ def md_step(y, dt, time, F_DC):
     '''
     '''
 
-    F_AC = 0.2
+    F_AC = 0.05
     #F_DC = 0.005 #5 #increment slowly
     period = 1.825
-    V0 = 0.1 #*2*np.pi/period
+    F0 = 0.1 #np.pi/period
     frequency = 0.01
     SX = 36.5
     SY = 36.5
@@ -62,7 +80,7 @@ def md_step(y, dt, time, F_DC):
     #integrate the equation of motion \eta v = F^net (eta=1)
 
     #reset vy for every timestep!  
-    vy = landscape_potential(V0,y,period)
+    vy = landscape_force(F0,y,period)
 
     #driving force
     vy += external_drive(F_AC,F_DC,frequency,time)
@@ -84,29 +102,34 @@ if __name__ == "__main__":
 
     #define the constants (parameters and initial conditions)
     dt = 0.001 #
-    y = 0
+    Sy=36.5
     vy = 0
     time = 0.0
     period = 1.825
 
[…]

### 2020-12-31 manuscript/manuscript_ajp_2020.tex
updated single particle figure

@@
 Subsequent substrate
-%CHECK!!! I THINK THIS IS WRONG!!!
-%BY NOT INCLUDING THE SIGN YOU'VE DEFINED IT BACKWARDS!!!!!
-%AND LOCATED THE INITIAL POSITION OF THE PARTICLE
-%AT A LOCAL MAXIMA!!!!!
-%The substrate maxima are located at integer multiples of $y/\lambda = 0, 1, 2 $ 
-%and
-minima are located at integer multiples $y/\lambda = 1/2, 3/2, 5/2, $ {\it et cetera}.
-%This is apparent in the spacing of $y/\lambda$ in time,
-%where the visual gaps between positions in Fig.~\ref{fig:0}(b) 
-%at half integer multiples $y/\lambda = 1/2, 3/2, 5/2$ indicate regions the particle was moving slowly.
-%measure/plot velocity?
 
@@
 \centering
-\includegraphics[width=\columnwidth]{position.png}
-\caption{The position as a function of time of a single driven particle
+\includegraphics[width=\columnwidth]{single_particle.pdf}
+\caption{(a) The applied driving force $F^D(t)$ where the parameter $F^{DC}$ is ramped to a constant value.  (b) 
+  The position as a function of time of a single driven particle
   normalized by the period of the substrate $\lambda$.

### 2021-01-01 code/MD_colloid.py
annoated panel letters

@@ -188,6 +188,9 @@ if __name__ == "__main__":
         #peaks of the FD curve
         ax2.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
         ax1.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
-     
+
+    ax1.text(0.02,0.9,"(a)",transform = ax1.transAxes,backgroundcolor="white")
+    ax2.text(0.02,0.9,"(b)",transform = ax2.transAxes,backgroundcolor="white")
+        
     plt.tight_layout(pad=0.1)
     plt.savefig("single_particle.pdf")

### 2021-01-01 code/MD_colloid.py
fixed notation subscript to superscript

@@ -164,7 +164,7 @@ if __name__ == "__main__":
     ax2 = fig.add_subplot(gs[1,0]) #,sharex=ax1)  #scatter plot of particles
     
     #plot the data
-    ax1.plot(time_data,FDC_data,label="F$_{DC}$")
+    ax1.plot(time_data,FDC_data,label="F$^{DC}$")
     ax1.plot(time_data,F_drive,label="F$^D$(t)",lw=5)
     ax1.legend(loc=4,fontsize=20,borderaxespad=0.1,frameon=0) #,labelspacing=0.2
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)

### 2021-01-01 code/MD_colloid.py
removed ^D in ylabel to be more accurate

@@ -171,7 +171,7 @@ if __name__ == "__main__":
     #plt.xlim(155,157)
     ax2.set_xlabel("time")
     ax2.set_ylabel(r"y/$\lambda$")
-    ax1.set_ylabel(r"F$^D$(t)")
+    ax1.set_ylabel(r"F(t)")
 
     ax1.set_xticks([])
 

### 2021-01-01 code/MD_colloid.py
changed legend handle length to avoid crash with vertical scale

@@ -166,7 +166,7 @@ if __name__ == "__main__":
     #plot the data
     ax1.plot(time_data,FDC_data,label="F$^{DC}$")
     ax1.plot(time_data,F_drive,label="F$^D$(t)",lw=5)
-    ax1.legend(loc=4,fontsize=20,borderaxespad=0.1,frameon=0) #,labelspacing=0.2
+    ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)
     #plt.xlim(155,157)
     ax2.set_xlabel("time")

### 2021-01-01 code/MD_colloid.py
fixed rounding error from if conditional

@@ -129,9 +129,10 @@ if __name__ == "__main__":
     #loop through the integer time steps in the simulation
     for int_time in range(0,maxtime):
 
-        if int_time > 0 and F_DC < F_DC_max: 
+        if int_time > 0 and abs(F_DC - F_DC_max) > F_DC_incr: 
             F_DC = ramp_dc_force(F_DC,int_time,drop,F_DC_incr)
-            #print(F_DC)
+            print(F_DC)
+
 
         #apply the force calculations for the current position/time
         #note vy is not necessary 

### 2021-01-02 manuscript/manuscript_ajp_2020.tex
updated fig. 2

@@
 in which individual oscillators adjust frequency due
-to interaction or an external stimulus \cite{Pikovsky2003}.
-Synchronous behaviors where oscillators move in-phase (i.e. in time)
+to external stimulus \cite{Pikovsky2003}.
+In phase oscillations
+%Synchronous behaviors where oscillators move in-phase
+%(i.e. in time motions)
 are observed
@@
 frogs alternating croaking patterns \cite{Aihara2014},
-and humans synchronizing clapping in time with music \cite{Tranchant2016}.
+and humans clapping in time with music \cite{Tranchant2016}.
 At a cellular level, 
@@
 %Dynamical mode locking
-The phenomena 
-is often studied with simplified computational models
-and can be visualized with %demonstrated
+%The phenomena
+Synchronization 
+is often studied with simple computational models
+and can be visualized 
 with phase plots or Lissajous figures.
-A mode-locked system is confined to 
+In phase space 
+a mode-locked system is confined to 
 a closed loop in a 
@@
 a child on a swing
-moving back and forth through equilibrium.  % \cite{}.
+moving back and forth. % through equilibrium.  % \cite{}.
 Single particle studies 
@@
 across a potential maximum so the average velocity is zero,
-a phenomena known as depinning \cite{Reichhardt2017},
+a phenomena refered to as pinning \cite{Reichhardt2017},
 and dissipating energy from the system at all driving forces.
@@
 with particles comprising the suspending fluid \cite{}.
-Brownian motion is a temperature dependent
-phenomena affecting quantum mechanically small systems. \cite{}
-[elaborate].
+Brownian motion is a temperature and viscosity dependent
+phenomena. \cite{}
+[elaborate - move to associated problems?].
 
@@
 photon radiation pressure to
-control colloid motions.
+control colloid motions \cite{Ashkin1997}.
 A circular optical trap is designed so the center is
@@
 intrinsic velocity of the dc driven particle,
-and the applied ac drive can
-create Shapiro steps in the force-velocity relationship.
+and the applied ac drive can cause mode-locking
+which appears as
+Shapiro steps in the force-velocity relationship.
 
@@
 such that a particle leaving the edge of the system is mapped
-back to a position within the simulation 
+back to a position within the simulation boundaries 
 by the transformation $x_i+L \rightarrow x_i$ and $y_i+L \rightarrow y_i$.
@@
 potential energy function, called a landscape or substrate.
-The confining force %arises from a potential function 
- %creating a landscape of potential minima and maxima
-%that modify the force on a particle as a function of position
-is calculated as 
- $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
  %The landscape potential energy $U(\vec{r})$ is static 
@@
  the maxima are colored red and the minima colored blue.
+ The confining force on a particle $i$
+ %arises from a potential function 
+ %creating a landscape of potential minima and maxima
+ %that modify the force on a particle as a function of position
+ is calculated as 
+ $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
  In Fig.~\ref{fig:landscape0}(b) we plot the function
  $U(y)$ to illustrate how the magnitude
- $\vec{F}^{l}_i$ is calculated from particle position in the $y-$direction.
+ $\vec{F}^{l}_i$ is calculated from particle position $y_i$.  
+ %in the $y-$direction.
 
@@
 and frequency $\omega = 2 \pi f$.
-We illustrate this force in Fig.~\ref{fig:landscape0}(a)
-in the positive $y-$direction.
+%in the positive $y-$direction.
 %but it may 
@@
 to avoid transient effects.
+We illustrate this force in Fig.~\ref{fig:0}(a).
 
@@
 %This is an assumption that
-The term overdamped or critically damped indicates
-that an oscillator cannot undergo periodic
-undulations due to some external force. %such as
+%The term overdamped or critically damped indicates
+%that an oscillator cannot undergo periodic
+%undulations due to some external force. %such as
 %suspension in a viscous fluid \cite{}.
@@
 
-We drive a single particle across a periodic landscape 
-along the y-direction described in Eq.~\ref{eq:ysubstrate}
-%\begin{equation}
-%  \label{eq:landscape_potential}
-%  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
-%\end{equation}
-with $N_p=20$ %troughs in the landscape
-and landscape period $\lambda = 1.825 a_0$.
+In Fig.~\ref{fig:0} we
+show the relationship between the applied force and particle
+position % as a function of time.
+for 
+%We drive
+a single particle across a periodic landscape. 
+%along the y-direction
 %({\it redundant, just refer back to eq. in Model?})
@@
 The numerical implementation of the landscape 
-is calculated with
+is calculated with Eq.~\ref{eq:ysubstrate} as 
 \begin{equation}
@@
 \end{equation}
-where the force is scaled with parameter $A_{p} = 0.1$
-in simulation units for force. % $E_0/a_0$.
-
-%%HMMM... HAVE YOU INTRODUCED A PHASE SHIFT?
-
-In Fig.~\ref{fig:0} we
-show the relationship between the applied force and particle
-position.
+where the force is scaled with parameter $A_{p} = 0.1$ force units 
+%in simulation units for force. % $E_0/a_0$.
+%The substrate is described in 
+%\begin{equation}
+%  \label{eq:landscape_potential}
+%  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
+%\end{equation}
+with $N_p=20$ %troughs in the landscape
+and spatial period $\lambda = 1.825 a_0$.
+%
 In Fig.~\ref{fig:0}(a)
@@
 The time independent constants are 
-$F^{AC}=0.2$, $F^{DC}=0.01$, and $f=0.01$ cycles per time unit.
-The time period of the driving force is
-$T = 1/f = 100$,
-with the initial driving force at is minimum value 
-$F^D(0) = F^{DC}$.
+$F^{AC}=0.2$ and $f=0.01$ cycles per time unit.
+The temporal period of the driving force is
+$T = 1/f = 100$.
+To avoid quenching the system, 
+the dc driving force is initially zero   
+and 
+slowly increased %$F^{DC}$
+at a rate of $\Delta F^{DC} = 0.01$ every $\Delta t = 4000$ integer timesteps 
+to the constant value $F^{DC}=0.1$,
+as shown in the blue curve in Fig.~\ref{fig:0}(a)
+where $F^{DC}$ increases for the first $40$ time units.
+The combined ac and dc drive $F^D(t)$ is shown in orange,
+where 
+the magnitude of the ac applied force is initially zero
+since $\sin{(0)}=0$.
+The vertical dashed lines in panels (a) and (b) coincide
+with the condition $\sin{(\omega t)} = 1$,
+where the applied force is maximum once $F^{DC}$ has reached its constant value.
+
+%with the initial driving force at is minimum value 
+%$F^D(0) = F^{DC}$.
 
@@
 where we 
-normalize $y$ by the spatial period of the washboard as
+normalize $y$ by the spatial period of the potential %washboard as
 $y/\lambda$.
@@
 where the landscape force is minimum $F^l = 0$.
-Subsequent substrate
+The horizontal dashed lines
+coincide with the condition the substrate force is
+minimum 
+$\sin{(\pi y / \lambda)} = 1 $. 
+%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
+The crossing of the particle position $y$
+with the horizontal and vertical lines
+indicates the synchronization
+of the driving force with the lattice position of the particle,
+where driving force is maximum when the particle
+is at the landscape minimum.
 
@@
 the particle hops between minima in the energy landscape.
+{\it UPDATE:} 
 In Fig.~\ref{fig:0} we demonstrate this relationship,
@@
 \includegraphics[width=\columnwidth]{single_particle.pdf}
-\caption{(a) The applied driving force $F^D(t)$ where the parameter $F^{DC}$ is ramped to a constant value.  (b) 
+\caption{(a) The applied driving force $F^D(t)$ (orange) where the parameter $F^{DC}$ (blue) is ramped to a constant value.  (b) 
   The position as a function of time of a single driven particle
@@
 %increased DC
-We apply an external applied force, 
-with 
-a constant $F^{AC}$ with frequency $\omega = 2\pi f$
-then slowly increase $F^{DC}$
-at a rate of $\Delta F^{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
-or $40$ time units.
+%We apply an external applied force, 
+%with 
+%a constant $F^{AC}$ with frequency $\omega = 2\pi f$
+%then slowly increase $F^{DC}$
+%at a rate of $\Delta F^{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
+%or $40$ time units.
 %this seems fast, but it is slow enough to estimate
@@
 %this is not be so for a multiple particle system!
-By modifying $F^{DC}$ we 
-achieve a variety of oscillation modes.
+The particle 
+achieves a variety of oscillation modes as a function of $F^{DC}$.
 A mode is a periodic pattern of hops
@@
 $\bar{v}_{y} = n \lambda f$,
-where $n$ is an integer,
-$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
-of the landscape,
-and $f = 0.01$ cycles per time unit.
+where $n$ is an integer.  
+%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
+%of the landscape,
+%and $f = 0.01$ cycles per time unit.
 
@@
 
+     \bibitem{Ashkin1997} Arthur Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).
+
       \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013

### 2021-01-02 code/MD_colloid.py
rewriting to sweep F_DC, but I may not need to if I just use the ramp and tune the parameters

@@ -12,7 +12,7 @@ Tiare Guerrero
 '''
 #################################################################
 import numpy as np
-import math
+import math, sys
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 
@@ -96,9 +96,9 @@ def md_step(y, dt, time, F_DC):
     
     return y, vy
 
-
-#-------------------------------------------------------------------
-if __name__ == "__main__":
+def single_particle(parameters):
+    '''Run MD simulation for a single particle driven across a washboard potential with an oscillating driving force
+    '''
 
     #define the constants (parameters and initial conditions)
     dt = 0.001 #
@@ -131,8 +131,6 @@ if __name__ == "__main__":
 
         if int_time > 0 and abs(F_DC - F_DC_max) > F_DC_incr: 
             F_DC = ramp_dc_force(F_DC,int_time,drop,F_DC_incr)
-            print(F_DC)
-
 
         #apply the force calculations for the current position/time
         #note vy is not necessary 
@@ -150,6 +148,7 @@ if __name__ == "__main__":
         #update the time (simulation units)
         time += dt
 
+    #for plot
     #calculate the driving force from F_DC and time
     F_AC = 0.05
     freq = 0.01
@@ -195,3 +194,43 @@ if __name__ == "__main__":
         
     plt.tight_layout(pad=0.1)
     plt.savefig("single_particle.pdf")
+
+def set_parameters():
+    '''Hardcode simulation parameters here.  In a compiled language like C this would be in a separate file that would be read into the code at execution time, so you wouldn't need to recompile to change the parameters
+    '''
+
+    #use a python dict (i.e. a hash to organize the parameters)
+    dict={}
+
+    dict['dt'] = 0.001 #timestep in simulation units
+
+    dict['Sy']=36.5         #height of system
+    dict['Sx']=36.5         #width of system
+    dict['vy0'] = 0          #initial velocity of particle
+    dict['time0'] = 0        #initial time in integer timesteps
+    dict['Np'] = 20         #number of troughs in the substrate
+    dict['period'] = Sy/Np  #spatial period of substrate in y-direction
+
+    #start the particle in a local minima (not a local max!)
+    dict['y'] = period #Sy/2
+
+    dict['F_DC'] = 0              #initial F_DC
+    dict['F_DC_incr'] = 0.01      #amount to increase FDC at every drop step
+    dict['F_DC_max'] = 0.1        #"constant" driving force for most of simulation
[…]

### 2021-01-03 code/MD_colloid.py
fixed parameter interface

@@ -1,6 +1,5 @@
 #!/usr/bin/env python3
 
-
 #################################################################
 '''
 Supplementary Material for
@@ -20,7 +19,7 @@ import matplotlib.gridspec as gridspec
 plt.rc('font', size=24)
 
 ##################################################################
-def landscape_force(F0,y,period):
+def landscape_force(y,parameters):
     '''landscape potential is equation (1) in the manuscript, while force is equation (5) - for now anyway
 
     U(y) = U0 cos(Np*pi*y/L)
@@ -37,14 +36,20 @@ def landscape_force(F0,y,period):
     y: float
     the location in the y-direction of the individual particle
     '''
+
+    period = parameters['period']
+    F0 = parameters['F0']
     
     return -F0*np.sin(np.pi*y/period)
 
 ###################################################################
-def external_drive(F_AC,F_DC,frequency,time):
+def external_drive(F_DC,time, parameters):
     '''
     '''
 
+    F_AC = parameters['F_AC']
+    frequency = parameters['freq']
+    
     F_ext = F_DC + F_AC*np.sin(2*np.pi*frequency*time) #
 
     #if time % 1000:
@@ -54,10 +59,12 @@ def external_drive(F_AC,F_DC,frequency,time):
 
 
 ####################################################################
-def ramp_dc_force(F_DC,time,drop,F_DC_incr):
+def ramp_dc_force(F_DC, time, parameters):
     '''
     '''
-    F_DC_max = 0.5
+    F_DC_max = parameters['F_DC_max']
+    drop = parameters['drop']
+    F_DC_incr = parameters['F_DC_incr']
     
     if time % drop == 0 and F_DC < F_DC_max:
         F_DC += F_DC_incr
@@ -65,25 +72,20 @@ def ramp_dc_force(F_DC,time,drop,F_DC_incr):
     return F_DC
 
 #####################################################################
-def md_step(y, dt, time, F_DC):
+def md_step(y, time, F_DC, parameters):
     '''
     '''
 
-    F_AC = 0.05
-    #F_DC = 0.005 #5 #increment slowly
-    period = 1.825
-    F0 = 0.1 #np.pi/period
-    frequency = 0.01
-    SX = 36.5
-    SY = 36.5
+    dt = parameters['dt']
+    SY = parameters['Sy']
     
     #integrate the equation of motion \eta v = F^net (eta=1)
 
-    #reset vy for every timestep!  
[…]

### 2021-01-03 code/MD_colloid.py
made updating parameters much easier for this system!

@@ -153,7 +153,7 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     ax2.text(0.02,0.9,"(b)",transform = ax2.transAxes,backgroundcolor="white")
         
     plt.tight_layout(pad=0.1)
-    plt.savefig("single_particle.pdf")
+    plt.savefig(parameters['filename'])
     
     return 
 
@@ -217,7 +217,7 @@ def single_particle(parameters):
 
     
 #########################################################################
-def set_parameters():
+def set_parameters_fig2():
     '''Hardcode simulation parameters here.  In a compiled language like C this would be in a separate file that would be read into the code at execution time, so you wouldn't need to recompile to change the parameters
     '''
 
@@ -259,9 +259,21 @@ def set_parameters():
 if __name__ == "__main__":
 
     #define simulation constants/controls
-    parameters = set_parameters()
+    parameters = set_parameters_fig2()
+
+    parameters['filename']="single_particle.pdf"
 
     #run a single MD simulation for a set of parameters
     single_particle(parameters)
 
+    #reset some parameters for subsequent figures
+    parameters['F_DC_incr'] = 0.001      #amount to increase FDC at every drop step
+    parameters['F_DC_max'] = 0.3        #"constant" driving force for most of simulation
+    parameters['drop'] = 4000           #integer timesteps to "ramp" the DC force
+    parameters['filename']="single_particle_new.pdf"
+    parameters['y0'] = 5.0*parameters['period']
+
+    #run a single MD simulation for a set of parameters
+    single_particle(parameters)
+    
     sys.exit()

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
finished simple Reynolds number exercise

@@
 In our colloidal model we assume
-the damping comes from the viscosity of the fluid,
-where a sphere of radius $0.5 \mu m$ has a Reynolds number
-of $R \approx 10^{-6}$, indicating that linear drag dominates
-the particle motion.
-See Section~\ref{sec:problems} Exercise~\ref{ex:reynolds} for more information
-about the Reynold's number.
+the particle is suspending in a viscous fluid
+that provides friction, or damping.
 In the overdamped model the
@@
 the acceleration of the particle is zero.
-Such a model is appropriate when the particles
-are small and the viscosity of the suspending medium is high.
+The friction coefficient $\eta$
+is proportional to the fluid viscosity.
+Such a model in which inertia is set to zero
+is appropriate for small particles
+moving through a high viscosity fluid
+such as a colloid moving in water.
+We discuss this further in 
+Section~\ref{sec:problems} Exercise~\ref{ex:reynolds}. %for more information
 
@@
 \end{equation}
-with the viscosity coefficient $\eta = 1$,
+with the viscosity coefficient $\eta = 1$ in units,
 which we describe in more detail in Exercise~\ref{ex:reynolds}.
@@
 %solvent dielectric constant & $\epsilon \epsilon_0$\\
-force & $E_0 / a_0$\\
-viscosity coefficient & $\eta = 1$ \\
-velocity &  $ E_0 / (\eta a_0) $ \\
-time &  $(\eta / E_0) {a_0}^2$ \\
+force & $F_0 = E_0 / a_0$\\
+velocity &  $ a_0 / \tau $ \\
+viscosity coefficient & $\eta = F_0 \tau / a_0 = 1 $\\
+time &  $ \tau = \eta a_0 / F_0 $ \\
+
 \end{tabular}
@@
 \includegraphics[width=\columnwidth]{single_particle.pdf}
-\caption{(a) The applied driving force $F^D(t)$ (orange) where the parameter $F^{DC}$ (blue) is ramped to a constant value.  (b) 
-  The position as a function of time of a single driven particle
+\caption{(a) The applied driving force $F^D(t)$ (orange) in Eq.~\ref{eq:drive}
+  where the parameter $F^{DC}$ (blue) is slowly increased from zero to a constant value
+  as described in the text.  (b) 
+  The $y-$position of the driven particle as a function of time %of a single driven particle
   normalized by the period of the substrate $\lambda$.
@@
 \begin{enumerate}
-\item Stokes' law the viscous drag on a sphere is
-$\vec{F}_{lin} = 3 \pi \eta D \vec{v}$ \cite{}
-where the fluid viscosity is $\eta$,
+\item Stokes' law describes the viscous drag on a sphere
+  moving at velocity $\vec{v}$ as 
+  $\vec{F}^{lin} = 3 \pi \eta D \vec{v}$ \cite{}
+  where $\eta$ is the dynamic fluid viscosity and 
   $D$ is the particle diameter.
-Assuming a colloid with diameter 
-$D = 1 \mu m$ and
-the viscosity of water at room temperature is
-$\eta = 0.01 cm^2/sec$ \cite{} %CONFIRM!
-%density $\rho = 0.9982 g/cm^3$
-%https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
-Reynold's number $R = D v \rho / \eta$
+  (In simulation we
+  subsume the constants $3 \pi D$
+  such that $\eta \rightarrow 3 \pi D \eta$.)
+  Often drag forces are
+  modeled as a polynomial series
+  $\vec{F}^{drag} = \vec{F}^{lin} + \vec{F}^{quad} + ... $.
+  Truncating the series to the first term
+  is justified by calculating the Reynolds number  
+  $R = D v \rho / \eta$
   where $\rho$ is the fluid density and $v$ the particle's speed.
@@
   may be ignored in favor of the linear drag term.
-A velocity $v$ in experiment is on the order of $v \sim 1 \mu /s$,
-thus $R \approx 10^-6$.
+
+  Demonstrate the Reynolds number is low
+  for this system.
+
+  Reasonable experimental values for
+  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
+  Viscosity of water decreases with temperature
+  from $1.3 \times 10^{-3} Pa s$ at $10^{\circ}C$ to 
+  from $0.31 \times 10^{-3} Pa s$ at $90^{\circ}C$,
+  making $\eta \sim 10^{-3} Pa s $.
+  Likewise the density $\rho$ varies with temperature
+  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.
+
+  [citation for these values better than wikipedia] \cite{} %CONFIRM!
+  %density $\rho = 0.9982 g/cm^3$
+  %https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
 
@@
 models Millikan's oil drops.
+
+[could certainly do more with this question to make it more computational.
+For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
+Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...]
+
 \label{ex:reynolds}
@@
 
-\item Brownian motion without fluid dynamics using  Ermak's algorithm
+\item Brownian motion.
+Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
+These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
+In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
+A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
+Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
+\cite{Allen2017}
+
+  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
+
+  Measure the rate of diffusion.
 
@@
 \section{Supplementary Materials}
-
-\subsection{Grid Contour Plot of landscape}
-%code is located in
-%~/pymodules/animation_code/channel_colloid_movie_maker.py
-Testing section - how will putting the code directly in the appendix appear?
-
-\begin{verbatim}
-############################################
-#ADD CONTOUR PLOT
-############################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color quasi1D potential
-    that contains 
-    the particles in a trough.  
-    Can add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    a_p = L/N
-
-    #we don't want to cover the entire range
-    X = np.arange(0, L/2.0, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 2.0 # set by what "looks good"
-    Z = Z_mag*np.sin(2*np.pi*X/L)
-    if corrugated == True:
-        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
-
-    cmap=cm.coolwarm_r
-
-    #alpha = transparency. set by what looks good.
-    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
-
-    #ax1.set_xlim(15,20)
-    #ax1.set_ylim(15,20)
-
-    #ax1.set_xlabel(r"$X$")
-    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
-
-    #ax1.set_xticks([])
-    #ax1.set_yticks([])
-    return
-\end{verbatim}
 
@@
     \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
+
     \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).
@@
 %%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Grid Contour Plot of landscape}
+%code is located in
+%~/pymodules/animation_code/channel_colloid_movie_maker.py
+Testing section - how will putting the code directly in the appendix appear?
+
+\begin{verbatim}
+############################################
+#ADD CONTOUR PLOT
+############################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color quasi1D potential
+    that contains 
+    the particles in a trough.  
+    Can add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #we don't want to cover the entire range
+    X = np.arange(0, L/2.0, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 2.0 # set by what "looks good"
+    Z = Z_mag*np.sin(2*np.pi*X/L)
+    if corrugated == True:
+        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
+
+    cmap=cm.coolwarm_r
+
+    #alpha = transparency. set by what looks good.
+    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
+
+    #ax1.set_xlim(15,20)
+    #ax1.set_ylim(15,20)
+
+    #ax1.set_xlabel(r"$X$")
+    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
+
+    #ax1.set_xticks([])
+    #ax1.set_yticks([])
+    return
+\end{verbatim}

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
renamed and removed sections

@@
 
-\subsection{Synchronization in multi-particle systems}
+\section{Synchronization in multi-particle systems}
 \label{sec:sync}
@@
 
-\subsection{Kinked system}
+\section{Kinked system}
 \label{sec:kink}	% You can label sections for reference
@@
 
-\section{Quasi-periodic substrate}
-\label{sec:quasiperiod}	% You can label sections for reference
-
-\section{Chaotic dynamics}
-\label{sec:chaos}	% You can label sections for reference
+%\section{Quasi-periodic substrate}
+%\label{sec:quasiperiod}	% You can label sections for reference
+
+%\section{Chaotic dynamics}
+%\label{sec:chaos}	% You can label sections for reference
 
@@
   Viscosity of water decreases with temperature
-  from $1.3 \times 10^{-3} Pa s$ at $10^{\circ}C$ to 
-  from $0.31 \times 10^{-3} Pa s$ at $90^{\circ}C$,
-  making $\eta \sim 10^{-3} Pa s $.
+  from $1.3 \times 10^{-3} Pa-s$ at $10^{\circ}C$ to 
+  from $0.31 \times 10^{-3} Pa-s$ at $90^{\circ}C$,
+  making $\eta \sim 10^{-3} Pa-s$,
+  where 1 pascal $ = 1 Pa = 1 N/m^2$.
   Likewise the density $\rho$ varies with temperature

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
moved discussion of Josephson junctions to conclusions

@@
 
-%Oscillators ordered into chains or lattices.
-%has many important
-%technological applications
-Dynamical mode-locking
-is %often
-observed
-in quantum electronic
-devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
-A single junction contains 
-two superconductoring layers which sandwich an insulating layer.
-When subject to an external voltage,
-Cooper pairs in the superconducting materials
-tunnel through the insulating layer.
-Phase-locking is observed as 
-%phase-locked current loops \cite{} 
-stepped regions in current-voltage (I-V) relationship in these devices,
-where voltage is the analog of external driving force
-and current is that of particle velocity.
-%where a constant current results from a range of voltages
-%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
-%instead of ohmic relationships.
-Known as Shapiro steps, % \cite{},
-these phase locked currents  
-have been observed due to applied ac voltages in 
-single Josephson junctions \cite{Shapiro1963, Golubov2004} and
-coupled arrays of junctions \cite{Benz1990}.
-%either in 
-%velocity-force curves and voltage-current curves \cite{Golubov2004}.
-Shapiro steps vary in width depending on the strength of the
-applied AC forces,
-and are observed in a variety of systems
-displaying
-%are hallmarks of
-non-Ohmic behavior in voltage-current curves,
-including
-ac and dc driven
-charge and spin density waves.
-
-%where these steps are generated
-%by the tendency of the response of a system
-%to be flat across a range of applied driving forces or voltages,
-%which can be probed with
-%  atoms on surfaces.
-%  voltage driven superconducting vortices
-%  confined in a Josephson junction,
-
-%
-%
-%mini review of synchronization in electronics
-%careful - the following is all simulations
-%Recent studies demonstrate
-%that coupled electronic oscillators can be
-%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
-
 \section{Colloidal Models}
@@
 of complex quantum mechanical systems.
-Mode-locked 
-colloid dynamics have been achieved in 
-experiments \cite{Juniper2015, Lutz2004} and
-simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
-for a variety of interaction types such as 
-magnetic dipoles and electric forces.
-%-----------------------------------------------------------
-%particle interaction types
-%Particles which interact over long distances
-%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
-%Particles which interact over short distances include
-%bubble arrays/emulsions [more systems and references].----------------------
-%The presence of a modulating surface
-%can modify these patterns in a variety of ways,
-%changing the onset of dynamical flows,
-%and the overall flow patterns.
-%  adjustable strength, geometry and length scale of substrate potential
-%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
-%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).
 
@@
 
-\section{Synchronization in multi-particle systems}
+\section{Synchronized particle chains}
 \label{sec:sync}
+
+Mode-locked 
+colloid dynamics have been achieved in 
+experiments \cite{Juniper2015, Lutz2004} and
+simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
+for a variety of interaction types such as 
+magnetic dipoles and electric forces.
+%-----------------------------------------------------------
+%particle interaction types
+%Particles which interact over long distances
+%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
+%Particles which interact over short distances include
+%bubble arrays/emulsions [more systems and references].----------------------
+%The presence of a modulating surface
+%can modify these patterns in a variety of ways,
+%changing the onset of dynamical flows,
+%and the overall flow patterns.
+%  adjustable strength, geometry and length scale of substrate potential
+%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
+%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).
 
@@
 with
-the Yukawa potential energy 
+the Yukawa potential $V_{ij} = U_{ij} / q$ 
 \begin{equation}
-  U_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
+  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
   \label{eq:yukawa}
@@
 defined in Table ~\ref{tab:1}.
-%$ = k q_1 q_2$. %[CHECK scaling/units].
+[elaborate for students $F_{Coulomb} = = k q_1 q_2 / r^2$, check scaling/units].
 $\kappa = 1/R_0$ is the screening parameter 
@@
 
+%Oscillators ordered into chains or lattices.
+%has many important
+%technological applications
+Dynamical mode-locking
+is %often
+observed
+in quantum electronic
+devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
+A single junction contains 
+two superconductoring layers which sandwich an insulating layer.
+When subject to an external voltage,
+Cooper pairs in the superconducting materials
+tunnel through the insulating layer.
+Phase-locking is observed as 
+%phase-locked current loops \cite{} 
+stepped regions in current-voltage (I-V) relationship in these devices,
+where voltage is the analog of external driving force
+and current is that of particle velocity.
+%where a constant current results from a range of voltages
+%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
+%instead of ohmic relationships.
+Known as Shapiro steps, % \cite{},
+these phase locked currents  
+have been observed due to applied ac voltages in 
+single Josephson junctions \cite{Shapiro1963, Golubov2004} and
+coupled arrays of junctions \cite{Benz1990}.
+%either in 
+%velocity-force curves and voltage-current curves \cite{Golubov2004}.
+Shapiro steps vary in width depending on the strength of the
+applied AC forces,
+and are observed in a variety of systems
+displaying
+%are hallmarks of
+non-Ohmic behavior in voltage-current curves,
+including
+ac and dc driven
+charge and spin density waves.
+
+%where these steps are generated
+%by the tendency of the response of a system
+%to be flat across a range of applied driving forces or voltages,
+%which can be probed with
+%  atoms on surfaces.
+%  voltage driven superconducting vortices
+%  confined in a Josephson junction,
+
+%
+%
+%mini review of synchronization in electronics
+%careful - the following is all simulations
+%Recent studies demonstrate
+%that coupled electronic oscillators can be
+%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
moved discussion of colloid interactions to chain section

@@
 
-Complex environments can be
-engineered with light by %, typically made 
-using diffraction gratings to create a patterned
-potential energy landscape 
-with one or more laser beams \cite{}.
-%
-
 Experiments of colloid particles confined
@@
  %$A_p = 2\pi U_0/L$.
+ %
+ In experiment 
+ complex environments can be
+ engineered with light by %, typically made 
+ using diffraction gratings to create a patterned
+ potential energy landscape 
+ with one or more laser beams \cite{}.
  %

### 2021-01-05 manuscript/manuscript_ajp_2020.tex
fixed some language on driving force/mode locking

@@
 $F^{DC}$ from zero
-to avoid transient effects.
-We illustrate this force in Fig.~\ref{fig:0}(a).
+to avoid transient behavior
+by ensuring the particle is subject to a smoothly varying force.
+We illustrate the increase
+of $F^{DC}$ in Fig.~\ref{fig:0}(a).
 
@@
 %We drive
-a single particle across a periodic landscape. 
+a single particle driven across a periodic landscape. 
 %along the y-direction
@@
 $T = 1/f = 100$.
-To avoid quenching the system, 
+To avoid transient oscillations at early times, 
 the dc driving force is initially zero   
 and 
-slowly increased %$F^{DC}$
+slowly increased %$F^{DC}$.
 at a rate of $\Delta F^{DC} = 0.01$ every $\Delta t = 4000$ integer timesteps 
-to the constant value $F^{DC}=0.1$,
-as shown in the blue curve in Fig.~\ref{fig:0}(a)
-where $F^{DC}$ increases for the first $40$ time units.
-The combined ac and dc drive $F^D(t)$ is shown in orange,
+to the constant value $F^{DC}=0.1$.
+In Fig.~\ref{fig:0}(a) we plot $F^{DC}$
+in blue to show the increase in 
+$F^{DC}$ for the first $40$ time units.
+In orange we show 
+the combined ac and dc drive $F^D(t)$,
 where 
-the magnitude of the ac applied force is initially zero
-since $\sin{(0)}=0$.
+the magnitude of the ac applied force is initially zero.
+%since $\sin{(0)}=0$.
 The vertical dashed lines in panels (a) and (b) coincide
 with the condition $\sin{(\omega t)} = 1$,
-where the applied force is maximum once $F^{DC}$ has reached its constant value.
+where the applied force is maximum once $F^{DC}$ has become constant.
 
@@
 normalize $y$ by the spatial period of the potential %washboard as
-$y/\lambda$.
+$\lambda$.
 The initial particle position is $y=0$,
@@
 minimum 
-$\sin{(\pi y / \lambda)} = 1 $. 
+$\sin{(\pi y / \lambda)} = 1 $, so $F^l = -A_p$.
 %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
@@
 of the driving force with the lattice position of the particle,
-where driving force is maximum when the particle
-is at the landscape minimum.
-
+where driving force is maximum positive when the
+force on the particle from the landscape is maximum negative.
+It can be shown this synchronization
+occurs for any initial position of $y$.
+
+The slope of $y/\lambda$
+is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
+This can be seen in 
+Fig.~\ref{fig:0} %we demonstrate this relationship,
+where local extrema appear in $y/\lambda$
+when $F_{D}(t) \approx 0 $ and 
 When $F^D(t) > A_p$, a particle can 
-overcome the barrier height of the landscape troughs,
+overcome the barrier height of the landscape maxima,
 and 
 the particle hops between minima in the energy landscape.
-{\it UPDATE:} 
-In Fig.~\ref{fig:0} we demonstrate this relationship,
-where over half of a driving period ($T = 50$) %time units
-while $F_{D}(t) > 0 $ 
+
 the particle moves

### 2021-01-05 manuscript/manuscript_ajp_2020.tex
updated text for new Fig. 2 and suggested new figure (or panel)

@@
 occurs for any initial position of $y$.
+({\it exercise to student})
 
@@
 the particle hops between minima in the energy landscape.
-
+In this example
+we note 
 the particle moves
 in the positive y-direction
-through three
-substrate troughs, reaching a maximum of $y/\lambda = 3$.
+through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$.
 When $F_{D}(t) < 0 $
 the particle moves in the negative y-direction 
-reaching a minimum position
-of $y/\lambda = 1$
-over the total period $T = 100$.
+for a short time.
+%reaching a minimum position
+%of $y/\lambda = 1$
+%over the total period $T = 100$.
 The average velocity $\bar{v}_y$
@@
 over the period of the driving force.
-In Fig. ~\ref{fig:0}
-the average displacement during one time period is a single wavelength
-of the substrate $y(t_0+T) - y(t_0) = \lambda$.
+%In Fig. ~\ref{fig:0}
+%the average displacement during one time period is a single wavelength
+%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
 Thus the average velocity 
-is $\bar{v}_y = \lambda f$. %, where $T = 1/f$.
+is $\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
+
+[add example where particle moves backward].
 

### 2021-01-06 manuscript/manuscript_ajp_2020.tex
finished Ex. 2

@@
 \end{equation}
-with the viscosity coefficient $\eta = 1$ in units,
-which we describe in more detail in Exercise~\ref{ex:reynolds}.
+with the viscosity coefficient $\eta = 1$,
+which we describe in more detail in Table~\ref{tab:1}
+and Exercise~\ref{ex:reynolds}.
 In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
@@
 where local extrema appear in $y/\lambda$
-when $F_{D}(t) \approx 0 $ and 
+when $F_{D}(t) \approx 0 $. 
 When $F^D(t) > A_p$, a particle can 
@@
 
-\item Newton's second law states that the sum of forces on a particle is proportional to the acceleration of the particle.
+\item Newton's second law states that
+  the acceleration of a particle $i$
+  is proportional to 
+  the sum of forces on a particle 
   \begin{equation}
-  m \vec{a}_i = \sum \vec{F}
+  m_i \vec{a}_i = \sum \vec{F}_i
   \label{eq:n2l}
   \end{equation}
-  Demonstrate that Eq.~\ref{eq:motion} is obtained from Newton's second law.
+  where the constant of proportionality is the
+  inertial mass $m_i$
+  The addition of a dissipative force in a dynamical model
+  on a colloid is typically modeled
+  with a drag force proportional to the particle's velocity
+  in the opposite direction of motion 
+  $\vec{F}^{drag} = - \eta \vec{v}_i$
+  where $\eta$ is the drag coefficient.
+  Demonstrate
+  the ratio of $m/\eta$ has units of time, 
+  %This ratio of the acceleration coefficient $m$
+  %to the drag coefficient $\eta$
+  %is
+  known as the momentum relaxation time.
+  The momentum relaxation time is 
+  known to be small for
+  particles with low Reynolds numbers,
+  indivating 
+  a regime in which the acceleration term can be ignored
+  entirely.
+  Demonstrate that a particle confined to a landscape exerting force
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
+  can be modeled with the equation of motion described in 
+  Eq.~\ref{eq:motion}. 
   \label{ex:n2l}

### 2021-01-07 manuscript/manuscript_ajp_2020.tex
fixed language in intro/abstract and rearranged for clarity

@@
   across a washboard potential energy landscape
-  exhibit a variety of synchronization effects.
+  move in 
+  synchronized patterns.   
+  %exhibit a variety of synchronization effects.
   %in
@@
   in experimental systems 
-  of interest to condensed matter physics 
-  including 
+  of %interest to condensed matter physics %including 
   magnetically driven colloidal particles
@@
   %overdamped equations of motion.
-  We demonstrate how to 
-  visualize
-  the system with
-  numerical representations of the landscape
-  and
-  animations of the particle motion.
   Our results show a variety of synchronization effects 
@@
   and phase diagrams of position versus velocity.
+  %We demonstrate how to 
+  %visualize
+  %the system with
+  %numerical representations of the landscape
+  %and
+  %animations of the particle motion.
   %We include sample code
@@
 to external stimulus \cite{Pikovsky2003}.
-In phase oscillations
-%Synchronous behaviors where oscillators move in-phase
-%(i.e. in time motions)
-are observed
-in many everyday systems
+Many everyday systems
+exhibit in-phase oscillations of components 
 such as the
-flickering candle flames coupled by temperature fluctuations \cite{Okamoto2016},
+flickering patterns of
+candle flames coupled by temperature fluctuations \cite{Okamoto2016},
 vibrations of singing wineglasses \cite{Arane2009}, 
@@
 Biological systems benefit from cooperative
-synchronization such as 
-birds coordinating wing flaps
+synchronization -- %such as 
+birds coordinate wing flaps
 to optimize energy use during flight \cite{Portugal2014},
-frogs alternating croaking patterns \cite{Aihara2014},
-and humans clapping in time with music \cite{Tranchant2016}.
-At a cellular level, 
+frogs alternate croaking patterns \cite{Aihara2014},
+humans clap in time with music \cite{Tranchant2016}
+and 
+at a cellular level, 
 neurons simultaneously fire in cardiac muscle \cite{MartinHall1999}
 and brain tissue \cite{Singer1999}.
+External forcing can cause or regulate 
+synchronization. % is often achieved via external forcing
+%such as when
+%single particle oscillators
+For instance,
+an electrical pacemaker %(an electrical generator)
+pulses to regulate a heart beat,
+and 
+a flashing light can modify the
+pattern of flashing fireflies .% \cite{Agrawal2013}.
 
@@
 exhibit phase-locking 
-when oscillators with different rhythms couple
-so the frequency ratio or mode 
-is an integer number \cite{Bak1986}.
+when oscillators with different rhythms adjust %couple
+to a frequency ratio or mode 
+of an integer number \cite{Bak1986}.
 %Dynamical mode locking
@@
 and can be visualized 
-with phase plots or Lissajous figures.
+with phase
+plots or Lissajous figures.
 In phase space 
@@
 %where two combined frequencies at perpendicular orientations
-({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
-
-External forcing can cause or regulate 
-synchronization. % is often achieved via external forcing
-%such as when
-%single particle oscillators
-For instance a
-%pushing a child on a swing at the high point on her path, or
-pacemaker (an electrical generator)
-pulses to regulate a heart beat
-or controlling the pattern of flashing
-fireflies with a pulsed light \cite{Agrawal2013}.
-These behaviors can be modeled with
-numerical studies %can be performed
-where
-a driving force is applied to simple harmonic system,
-either
-coupled oscillators %\cite{Kuramoto193?}
-or a single particle driven across a periodic potential landscape.
-A single particle particle oscillator
-within a potential well is 
-much like a skateboarder in a half-pipe or
-a child on a swing
-moving back and forth. % through equilibrium.  % \cite{}.
-Single particle studies 
-are useful to understand synchronization
-in the absence of collective effects.
-With a constant or 
-dc drive the landscape modulates 
-the particle velocity, below some threshold below
-the dc force is not strong enough to push the particle
-across a potential maximum so the average velocity is zero,
-a phenomena refered to as pinning \cite{Reichhardt2017},
-and dissipating energy from the system at all driving forces.
-A sinusoidal or ac drive creates mode-locking,
-where the average particle velocity
-is fixed for a range of dc drive forces \cite{Reichhardt2015}.
-
-\section{Colloidal Models}
-\label{sec:colloids}
-
-Complex dynamics can be studied with
-colloid particles with experiments and simulation.
-In experiment, colloids are typically spheres of 
-plastic suspended in
-highly de-ionized water or silica in suspended in organic solvent.
-%experimental - colloids specifically
-The spheres are a few microns in size
-and move at rates of microns per second,
-so a system can be imaged
-with a traditional optical camera
-due to the large size and slow speed of the particles.
-Individual colloids exhibit 
-Brownian motion,
-where particles change direction in a seemly random fashion
-due to unseen 
-collisions 
-with particles comprising the suspending fluid \cite{}.
-Brownian motion is a temperature and viscosity dependent
-phenomena. \cite{}
-[elaborate - move to associated problems?].
-
-Due to the relative ease of
-manipulation and imagining, 
-colloids are used as experimental models
-for systems relatively hard to access and visualize. 
-%SAME SENTENCE TWICE
-Collections of colloids can
-be used to study the properties of solids and liquids
-%comprised of smaller particles
-%such as atoms \cite{} or electrons \cite{}
-or more exotic systems 
-such as cold atoms or electron gases \cite{Grier2003}.  
-The interaction forces between colloids can be controlled 
-by altering the chemistry of the suspending fluid
-or surface ligands of the particles.
-Thus colloids can 
-be modified to mimic different
-systems such as hard spheres interacting via contact forces \cite{},
-dipole interactions \cite{},
-and long range electrostatic interactions \cite{}.
-
-Light is a
-tool for manipulating the colloidal environment.
-A single laser beam can be used to create an optical trap,
-which uses 
-photon radiation pressure to
-control colloid motions \cite{Ashkin1997}.
-A circular optical trap is designed so the center is
-a local energy minimum where 
-a colloid in the beam center is subject to a
-uniform distribution of photon bombardment. %, making 
-Colloids at a trap edge
-experience a net force
-due to the uneven 
-distribution of photon collisions on its surface.
-Depending on the shape of the trap and location of the particle in the trap,
-the radiation pressure either pushes colloids toward the local minima
-or ejects it from the trap.
-A single optically trapped colloid executing Brownian motion
-is a useful probe of microscopic forces,
-and has been studied in detail in Ref.~\cite{Volpe2013}.
-
-Experiments of colloid particles confined
-in optical traps arrays or patterns 
-subject to external driving forces 
-have
-been used to examine the microscopic dynamics
-of individual particles during mode-locking \cite{Juniper2015}.
-This produced step-by-step diagrams
-of particle dynamics that cannot be 
-imaged in electronic systems such as Josephson junctions.
-%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
-Thus the study of
-mode-locking is a useful problem
-of complex quantum mechanical systems.
-
-%external forces
-%The
-%dynamics of particles subject to 
-%an applied external force apply to many physical systems.
-%For instance the flow of charges in a conductor,
-%or cells responding to a chemical gradient.
-%The external force 
-%increases the diversity of dynamical behaviors,
-%and can cause particles to flow in
-%a variety of non-linear complex patterns
-%that may be 
-%synchronized.
-%Disordered chaotic dynamics are also possible,
-%where irregular, unpredictable time evolution of
-%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
-%-------------------------------------------------------------
-
-Numerical modeling of colloids can provide mechanistic insight
-that can be difficult to achieve in experimental conditions
-where Brownian motion and other sources of noise dominate.
+%({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
+It should be noted that oscillation phase and phase space
+  refer to different uses of the word ``phase.''  Oscillation
+  phase $\phi_0$ is the constant portion of the argument in a periodic function
+  $\sin{(\omega t + \phi_0)}$ while phase space refers
+  to plots of velocity versus position (such as $v_y$ vs. $y$)
+  that are used to characterize oscillating systems.
 
@@
 a washboard shaped potential energy landscape.
+Numerical studies %of harmonic systems
+can yield insights
+to the mechanics of naturally oscillating systems.
 We chose this model for its
@@
 and ease of simulation.
-%We examine
-The period of the substrate
-can be used to control the
-intrinsic velocity of the dc driven particle,
-and the applied ac drive can cause mode-locking
-which appears as
-Shapiro steps in the force-velocity relationship.
-
 %---------------------------------------------------------------
 %kinks and nanofriction
-
 %-----------------------------------------------------------------
@@
 %In the following paper
+In Section~\ref{sec:colloids} we describe colloid particles,
+an relevent
+experimental analog of our simulations.
 We describe
@@
 in Section~\ref{sec:problems}.
+
+\section{Colloidal Models}
+\label{sec:colloids}
+
+Complex dynamics can be studied with
+colloid particles with experiments and simulation.
+In experiment, colloids are typically spheres of 
+plastic suspended in
+highly de-ionized water or silica in suspended in organic solvent.
+%experimental - colloids specifically
+Because 
+the spheres are a few microns in size
+and move at rates of microns per second,
+the position of a particle %is large and slow enough to
+can be imaged as a function of time 
+with a traditional optical camera.
+%due to the large size and slow speed of the particles.
+Individual colloids exhibit 
+Brownian motion,
+where particles change direction %in a seemingly random fashion
+due to unseen 
+collisions 
+with particles comprising the suspending fluid \cite{}.
+Brownian motion is a temperature and viscosity dependent
+phenomena. \cite{}
+[elaborate - move to associated problems?].
+
+Due to the relative ease of
+manipulation and imagining, 
+colloids are used as experimental models
+for systems relatively hard to access and visualize. 
+%SAME SENTENCE TWICE
+Collections of colloids can
+be used to study the properties of solids and liquids
+%comprised of smaller particles
+%such as atoms \cite{} or electrons \cite{}
+or more exotic systems 
+such as cold atoms or electron gases \cite{Grier2003}.  
+The interaction forces between colloids can be controlled 
+by altering the chemistry of the suspending fluid
+or surface ligands of the particles.
+Thus colloids can 
+be modified to mimic different
+systems such as hard spheres interacting via contact forces \cite{},
+dipole interactions \cite{},
+and long range electrostatic interactions \cite{}.
+
+Light is a
+tool for manipulating the colloidal environment.
+A single laser beam can be used to create an optical trap,
+which uses 
+photon radiation pressure to
+control colloid motions \cite{Ashkin1997}.
+A circular optical trap is designed so the center is
+a local energy minimum where 
+a colloid in the beam center is subject to a
+uniform distribution of photon bombardment. %, making 
+Colloids at a trap edge
+experience a net force
+due to the uneven 
+distribution of photon collisions on its surface.
+Depending on the shape of the trap and location of the particle in the trap,
+the radiation pressure either pushes colloids toward the local minima
+or ejects it from the trap.
+A single optically trapped colloid executing Brownian motion
+is a useful probe of microscopic forces,
+and has been studied in detail in Ref.~\cite{Volpe2013}.
+
+Experiments of colloid particles confined
+in optical traps arrays or patterns 
+subject to external driving forces 
+have
+been used to examine the microscopic dynamics
+of individual particles during mode-locking \cite{Juniper2015}.
+This produced step-by-step diagrams
+of particle dynamics that cannot be 
+imaged in electronic systems such as Josephson junctions.
+%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
+Thus the study of
+mode-locking is a useful problem
+of complex quantum mechanical systems.
+
+%external forces
+%The
+%dynamics of particles subject to 
+%an applied external force apply to many physical systems.
+%For instance the flow of charges in a conductor,
+%or cells responding to a chemical gradient.
+%The external force 
+%increases the diversity of dynamical behaviors,
+%and can cause particles to flow in
+%a variety of non-linear complex patterns
+%that may be 
+%synchronized.
+%Disordered chaotic dynamics are also possible,
+%where irregular, unpredictable time evolution of
+%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
+%-------------------------------------------------------------
+
+Numerical modeling of colloids can provide mechanistic insight
+that can be difficult to achieve in experimental conditions
+where Brownian motion and other sources of noise dominate.
 
@@
 
+A single particle on this landscape
+responds to the applied driving force
+by synchronizing its motion across the landscape maxima 
+to the periodic pattern of 
+applied driving force.
 In Fig.~\ref{fig:0} we
@@
 The time independent constants are 
-$F^{AC}=0.2$ and $f=0.01$ cycles per time unit.
+$F^{AC}=0.05$ and $f=0.01$ cycles per time unit.
 The temporal period of the driving force is
@@
 the particle hops between minima in the energy landscape.
-In this example
-we note 
+Here 
 the particle moves
 in the positive y-direction
-through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$.
-When $F_{D}(t) < 0 $
-the particle moves in the negative y-direction 
-for a short time.
+through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
+with 
+the average velocity 
+$\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
 %reaching a minimum position
@@
 %over the total period $T = 100$.
-The average velocity $\bar{v}_y$
-is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
-over the period of the driving force.
+%The average velocity $\bar{v}_y$
+%is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
+%over the period of the driving force.
 %In Fig. ~\ref{fig:0}
@@
 %of the substrate $y(t_0+T) - y(t_0) = \lambda$.
-Thus the average velocity 
-is $\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
-
-[add example where particle moves backward].
-
 %single DC case with figure
 %dc_current 0.01
-%ac_current 0.2
-%ac_frequency 0.0001
+%ac_current 0.05
+%ac_frequency 0.01
 %fp_y 0.1
@@
 \caption{(a) The applied driving force $F^D(t)$ (orange) in Eq.~\ref{eq:drive}
-  where the parameter $F^{DC}$ (blue) is slowly increased from zero to a constant value
+  where the parameter $F^{DC}$ (blue) is slowly increased from zero
+  to a constant value
   as described in the text.  (b) 
-  The $y-$position of the driven particle as a function of time %of a single driven particle
+  The $y-$position of the driven particle
+  as a function of time %of a single driven particle
   normalized by the period of the substrate $\lambda$.
@@
 
+The ratio of $F^{AC}/F^{DC}$ and the barrier height $A_p$
+control the rate and length of the particle hops
+forward and backward in the landscape.
+When $F^{AC}/F^{DC} > 1$
+and $F^{DC} - F^{AC} > A_p$ the particle
+moves in the negative y-direction 
+during part of the cycle.
+To explore the possible hopping patterns,
+we sweep through a range of $F^{DC}$ for fixed $F^{AC}$ and $A_p$,
+as shown in Fig.~\ref{fig:1}(b).
+We keep $F^{DC}$ constant
+for $\Delta t = 10^4$ timesteps
+and 
+sample the average velocity $\langle v_y \rangle $ 
+as a function of $F^{DC}$.
+
+We perform this sweep for several values
+of $F^{AC}$ including the limiting case that the applied force
+is a constant value.
+When $F^{AC} = 0$, no steps appear
+in the $\langle v_y \rangle $ vs $F^{DC}$ curve.
+
+Synchronization
+of the driving force with the landscape,
+despite the overall magnitude
+of $F^{DC}$.
+
 Phase locked steps occur for average displacements integer
@@
 
-We sample the average velocity $\langle v_y \rangle $
-as a function of $F^{DC}$.
-
-The hopping pattern of the driven particle is periodic,
-and could be achieved over a range of $F^{DC}$.  %, as we will demonstrate in Fig.~\ref{fig:1}
-We explore the ranges of periodic hopping patterns
-by increasing $F^{DC}$ as a function of time,
-as shown in 
-%
-Fig.~\ref{fig:1}.
-%we show the result increasing the 
-%force to the particle as a function of time.  
-%increased DC
-%We apply an external applied force, 
-%with 
-%a constant $F^{AC}$ with frequency $\omega = 2\pi f$
-%then slowly increase $F^{DC}$
-%at a rate of $\Delta F^{DC} = 0.001$ every $\Delta t = 4000$ integer timesteps
-%or $40$ time units.
-%this seems fast, but it is slow enough to estimate
-%the velocity accurately.
-%this is not be so for a multiple particle system!
 The particle 
@@
 the velocity-force plot in Fig.~\ref{fig:1}(b).
-Here $\bar{v}_{y}$ is increasing in non-uniform steps,
+Here $\langle v_{y} \rangle$ is increasing in non-uniform steps,
 with a quantized height of
-$\bar{v}_{y} = n \lambda f$,
+$\langle v_{y} \rangle = n \lambda f$,
 where $n$ is an integer.  
@@
 
-We illustrate the hopping pattern in Fig.~\ref{fig:1}(b)
-and 
+We 
 show the dynamics 
@@
 \includegraphics[width=\columnwidth]{single}
-\caption{\textbf{(a)} The particle is driven with a constant amplitude $F^{AC}$ and frequency $\omega$ through a periodic spatial potential landscape.
-The landscape is represented with a colormap where blue are minima and red are maxima in the potential.
-\textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of a constant driving force $F^{DC}$.
-In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\bar{v}_{y}$ at which the particle in Fig.
-1(a) is moving.}
+\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{DC}$.}
 \label{fig:1}
@@
 \end{center}
+
+%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
+
+%We examine
+The period of the substrate
+can be used to control the
+intrinsic velocity of the dc driven particle,
+and the applied ac drive can cause mode-locking
+which appears as non-linear 
+steps in the force-velocity relationship.
+
+Fundamental models
+of synchronization 
+can include many coupled oscillators
+or focus on 
+a single particle driven across a periodic potential landscape.
+Single particle studies 
+are useful to understand synchronization
+in the absence of collective effects.
+%A single particle particle oscillator
+%within a potential well is 
+%much like a skateboarder in a half-pipe or
+%a child on a swing
+%moving back and forth. % through equilibrium.  % \cite{}.
+The relationship between the driving force and
+landscape can change the pattern of motion.  
+With a constant or 
+dc drive the landscape modulates 
+the particle velocity, below some threshold  
+the dc force is not strong enough to push the particle
+across a potential maximum so the average velocity is zero,
+a phenomena refered to as pinning \cite{Reichhardt2017}.  
+%and dissipating energy from the system at all driving forces.
+A sinusoidal or ac drive creates mode-locking,
+where the average particle velocity
+is fixed for a range of dc drive forces \cite{Reichhardt2015}.
 
@@
 
-    \bibitem{Agrawal2013} D. K. Agrawal, J. Woodhouse, and A. A. Seshia, Physical Review Letters {\bf 111}, 084101 (2013).
+      %PRACTICAL APPLICATION
+    %\bibitem{Agrawal2013} D.
+K.
+Agrawal, J.
+Woodhouse, and A.
+A.
+Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
 

### 2021-01-08 manuscript/manuscript_ajp_2020.tex
this manuscript is getting really good!

@@
 \begin{abstract}
+  Synchronization
+  plays a key role in many physical processes.
+  %Simplified models
+  %such as 
   %What problem did you study and why is it important?
@@
   move in 
-  synchronized patterns.   
+  synchronized patterns,
+  as observed in 
+  experiments %al systems 
+  of %interest to condensed matter physics %including 
+  magnetically driven colloidal particles
+  confined by light-fields.
   %exhibit a variety of synchronization effects.
@@
   a viscous liquid.
-  This model reproduces behaviors observed
-  in experimental systems 
-  of %interest to condensed matter physics %including 
-  magnetically driven colloidal particles
-  confined by light-fields.
   %
@@
 a washboard shaped potential energy landscape.
-Numerical studies %of harmonic systems
-can yield insights
-to the mechanics of naturally oscillating systems.
+%Numerical studies %of harmonic systems
+%can yield insights
+%to the mechanics of naturally oscillating systems.
 We chose this model for its
@@
 %and conclude 
-%in Section~\ref{sec:conclusion}. 
+In Section~\ref{sec:conclusion}
+we describe how our work with colloids applies more broadly
+to many physical systems
+such as dusty plasmas, superconducting vortices and Josephson junctions.
 We conclude with
@@
 colloid particles with experiments and simulation.
-In experiment, colloids are typically spheres of 
+In typical experiments colloids are spheres of 
 plastic suspended in
@@
 where particles change direction %in a seemingly random fashion
-due to unseen 
+due to 
 collisions 
-with particles comprising the suspending fluid \cite{}.
-Brownian motion is a temperature and viscosity dependent
-phenomena. \cite{}
-[elaborate - move to associated problems?].
-
-Due to the relative ease of
-manipulation and imagining, 
-colloids are used as experimental models
-for systems relatively hard to access and visualize. 
-%SAME SENTENCE TWICE
-Collections of colloids can
-be used to study the properties of solids and liquids
-%comprised of smaller particles
-%such as atoms \cite{} or electrons \cite{}
-or more exotic systems 
-such as cold atoms or electron gases \cite{Grier2003}.  
-The interaction forces between colloids can be controlled 
-by altering the chemistry of the suspending fluid
-or surface ligands of the particles.
-Thus colloids can 
-be modified to mimic different
-systems such as hard spheres interacting via contact forces \cite{},
-dipole interactions \cite{},
-and long range electrostatic interactions \cite{}.
+with unseen particles comprising the suspending fluid \cite{}.
+%[elaborate - move to associated problems?].
 
@@
 %because
-We model the 
-particle dynamics 
-with an overdamped
-equation of motion.
-%integrated with the Verlet method.
-%The suspending fluid is highly viscous
-%and exerts a damping force on the particles equivalent
-%to a linear drag force.
-%Overdamped dynamics is a common assumption in models of colloidal particles.
-%This is an assumption that
-%The term overdamped or critically damped indicates
-%that an oscillator cannot undergo periodic
-%undulations due to some external force. %such as
-%suspension in a viscous fluid \cite{}.
-In our colloidal model we assume
-the particle is suspending in a viscous fluid
-that provides friction, or damping.
-In the overdamped model the
-linear friction produced by this 
-nonconservative force,
-$\vec{F}_{drag} = -\eta \vec{v}_i$ is
-sufficient so that
-the acceleration of the particle is zero.
-The friction coefficient $\eta$
-is proportional to the fluid viscosity.
-Such a model in which inertia is set to zero
-is appropriate for small particles
-moving through a high viscosity fluid
-such as a colloid moving in water.
-We discuss this further in 
+The inertia of 
+small particles is greatly reduced by interactions
+with fluid particles \cite{Purcell1977}.
+Our model 
+colloids are overdamped
+-- i.e. suspended in a continuous viscous fluid
+that dissipates energy at a rate such 
+that the particles do not accelerate.
+%that greatly impedes their motions.
+Energy dissipation from the fluid is modeled
+with a frictional force on particle with velocity $\vec{v}_i$
+%that removes energy from
+%the particles,
+%which we model as
+$\vec{F}^{drag}_i = -\eta \vec{v}_i$
+%proportional to the particle velocity 
+with a friction coefficient $\eta$
+proportional to the fluid viscosity.
+We discuss friction models for
+spheres moving through fluids in 
 Section~\ref{sec:problems} Exercise~\ref{ex:reynolds}. %for more information
-
+%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
 Newton's second law for an individual particle
-$m \vec{a}_i = \sum \vec{F}$ is simplified
-by the assumption $\vec{a}_i$ is zero in overdamped model.
+%$m \vec{a}_i = \sum \vec{F}$
+is simplified
+by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
 %Newton's second law can be rearranged %for the velocity
 %to
-The equation of motion for an isolated particle is
+The overdamped equation of motion for an isolated particle is
 %solved for velocity 
@@
 \end{equation}
-with the viscosity coefficient $\eta = 1$,
-which we describe in more detail in Table~\ref{tab:1}
-and Exercise~\ref{ex:reynolds}.
-In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
+with  $\eta = 1$.  
+%which we describe in more detail in Table~\ref{tab:1}
+%and Exercise~\ref{ex:reynolds}.
+In %Section~\ref{sec:problems}
+Exercise~\ref{ex:n2l}
 we invite the reader to confirm this result.
@@
 \label{sec:sync}
+The interaction forces between colloids can be controlled 
+by altering the chemistry of the suspending fluid
+or surface ligands of the particles.
+Thus colloids can 
+be modified to mimic different
+systems such as hard spheres interacting via contact forces \cite{},
+dipole interactions \cite{},
+and long range electrostatic interactions \cite{}.
 
@@
 
-\item Brownian motion.
+\item {\bf Brownian motion}
+  is a temperature and viscosity dependent
+  phenomena. \cite{}
   Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
@@
 \label{sec:conclusion}	% You can label sections for reference
+Due to the relative ease of
+manipulation and imagining, 
+colloids are used as experimental models
+for systems relatively hard to access and visualize. 
+%SAME SENTENCE TWICE
+Collections of colloids can
+be used to study the properties of solids and liquids
+%comprised of smaller particles
+%such as atoms \cite{} or electrons \cite{}
+or more exotic systems 
+such as cold atoms or electron gases \cite{Grier2003}.
 
@@
 
+    \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
+
       %PRACTICAL APPLICATION

### 2021-01-10 code/MD_colloid.py
modified varible names/labels to have lowercase superscripts

@@ -123,8 +123,8 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     # time = m/(4*freq)
 
         #plot the data
-    ax1.plot(time_data,FDC_data,label="F$^{DC}$")
-    ax1.plot(time_data,F_drive,label="F$^D$(t)",lw=5)
+    ax1.plot(time_data,FDC_data,label="F$^{dc}$")
+    ax1.plot(time_data,F_drive,label="F$^d$(t)",lw=5)
     ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)
     #plt.xlim(155,157)
@@ -152,7 +152,64 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     ax1.text(0.02,0.9,"(a)",transform = ax1.transAxes,backgroundcolor="white")
     ax2.text(0.02,0.9,"(b)",transform = ax2.transAxes,backgroundcolor="white")
         
-    plt.tight_layout(pad=0.1)
+    plt.tight_layout(pad=0.2)
+    plt.savefig(parameters['filename'])
+    
+    return 
+
+#####################################################################
+def plot_velocity_force(velocity_data,FDC_data,p):
+    '''Make Fig. 3 in AJP
+    '''
+
+    #for plot
+    #calculate the driving force from F_DC and time
+    F_AC = p['F_AC']
+    freq = p['freq']
+    period = p['period']
+    
+    fig = plt.figure(figsize=(8,4))
+    gs=gridspec.GridSpec(1,1)
+    ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
+
+    #calculate from np.array rather than incrementally from subroutines
+    F_drive = FDC_data + F_AC*np.sin(2*np.pi*freq*time_data)
+
+    #max occurs at
+    # 2*np.pi*freq*time_data = m*pi/2, where m = 1, 5, 9, 13, ...
+    # time = m/(4*freq)
+
+        #plot the data
+    ax1.plot(time_data,FDC_data,label="F$^{dc}$")
+    ax1.plot(time_data,F_drive,label="F$^d$(t)",lw=5)
[…]

### 2021-01-10 manuscript/manuscript_ajp_2020.tex
do next, fig. 3~

@@
   (a) View of the $x-y$ plane. %of the simulation
-  The time-dependent applied driving force $\vec{F}^D$
+  The time-dependent applied driving force $\vec{F}^d$
   is parallel to the y-axis.
@@
 \begin{equation}
-  \vec{F}^{D}(t) = [F^{DC} + F^{AC} \sin(\omega t)] \hat{y},
+  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
     \label{eq:drive}
@@
 with modifiable parameters including
-a constant component $F^{DC}$,
-and a time dependent component with amplitude $F^{AC}$
+a constant component $F^{dc}$,
+and a time dependent component with amplitude $F^{ac}$
 and frequency $\omega = 2 \pi f$.
@@
 %be zero or negative depending the the parameters and time.
-When $F^{DC}$ is non-zero,  
+When $F^{dc}$ is non-zero,  
 %In several simulations
 we slowly increase 
-$F^{DC}$ from zero
+$F^{dc}$ from zero
 to avoid transient behavior
@@
 We illustrate the increase
-of $F^{DC}$ in Fig.~\ref{fig:0}(a).
+of $F^{dc}$ in Fig.~\ref{fig:0}(a).
 
@@
 \begin{equation}
-  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{D}(t).
+  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{d}(t).
     \label{eq:motion}
@@
 % in response to this applied force in a variety of environments.
-% In Sec.~\ref{sec:kink} we set $F^{DC}$
+% In Sec.~\ref{sec:kink} we set $F^{dc}$
 % to zero and track the motion
@@
 
-A single particle on this landscape
+A single particle %on this landscape
 responds to the applied driving force
-by synchronizing its motion across the landscape maxima 
+by synchronizing its motion across the landscape %maxima 
 to the periodic pattern of 
 applied driving force.
-In Fig.~\ref{fig:0} we
-show the relationship between the applied force and particle
-position % as a function of time.
-for 
-%We drive
-a single particle driven across a periodic landscape. 
 %along the y-direction
@@
 \end{equation}
-where the force is scaled with parameter $A_{p} = 0.1$ force units 
-%in simulation units for force. % $E_0/a_0$.
-%The substrate is described in 
-%\begin{equation}
-%  \label{eq:landscape_potential}
-%  U_l(y) = U_{0y} \cos{(N_p \pi y / L)} 
-%\end{equation}
-with $N_p=20$ %troughs in the landscape
-and spatial period $\lambda = 1.825 a_0$.
+where the force is scaled with parameter $A_{p}$.
+In this section, we fix the landscape parameters
+to $A_{p} = 0.1$ force units
+with $N_p=20$ minima in the landscape
+corresponding to a spatial period $\lambda = 1.825 a_0$.
+
+In Fig.~\ref{fig:0} 
+a single driven particle adjusts
+its motion so the particle traverses
+the periodic landscape with the same rhythm as 
+the applied time-dependent force $F^d(t)$.
 %
 In Fig.~\ref{fig:0}(a)
-we plot the applied driving force defined in Eq.~\ref{eq:drive}
-as a function of time.
+we plot $F^d(t)$ defined in Eq.~\ref{eq:drive}.
+%as a function of time.
 The time independent constants are 
-$F^{AC}=0.05$ and $f=0.01$ cycles per time unit.
+$F^{ac}=0.05$ and $f=0.01$ cycles per time unit.
 The temporal period of the driving force is
-$T = 1/f = 100$.
+$T = 1/f = 100$ time units.
 To avoid transient oscillations at early times, 
@@
 and 
-slowly increased %$F^{DC}$.
-at a rate of $\Delta F^{DC} = 0.01$ every $\Delta t = 4000$ integer timesteps 
-to the constant value $F^{DC}=0.1$.
-In Fig.~\ref{fig:0}(a) we plot $F^{DC}$
+slowly increased %$F^{dc}$.
+at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  
+to the constant value $F^{dc}=0.1$.
+In Fig.~\ref{fig:0}(a) we plot $F^{dc}$
 in blue to show the increase in 
-$F^{DC}$ for the first $40$ time units.
+$F^{dc}$ for the first $40$ time units
 In orange we show 
-the combined ac and dc drive $F^D(t)$,
-where 
-the magnitude of the ac applied force is initially zero.
+the combined ac and dc drive $F^d(t)$ 
+when the magnitude of the ac applied force is initially zero.
 %since $\sin{(0)}=0$.
-The vertical dashed lines in panels (a) and (b) coincide
-with the condition $\sin{(\omega t)} = 1$,
-where the applied force is maximum once $F^{DC}$ has become constant.
+We mark the maxima of $F^{ac}(t)$
+with the
+vertical dashed lines %in panels (a) and (b)
+(i.e. $\sin{(\omega t)} = 1$).
 
 %with the initial driving force at is minimum value 
-%$F^D(0) = F^{DC}$.
+%$F^d(0) = F^{dc}$.
 
@@
 where we 
-normalize $y$ by the spatial period of the potential %washboard as
-$\lambda$.
-The initial particle position is $y=0$,
-where the landscape force is minimum $F^l = 0$.
+normalize $y$ by $\lambda$, the spatial period of the potential.
+The initial particle position is $y = 1$,
+where the landscape force is negative $F^l < 0$,
+causing the particle to move into
+a landscape minima at the start of the simulation.
+As the driving force increases,
+%the effects of the landscape become less obvious,
+and the motion of the particle
+becomes locked to the driving period $T$.
 The horizontal dashed lines
 coincide with the condition the substrate force is
-minimum 
-$\sin{(\pi y / \lambda)} = 1 $, so $F^l = -A_p$.
+minimum $F^l = -A_p$ 
+(i.e. $\sin{(\pi y / \lambda)} = 1$).
 %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
-The crossing of the particle position $y$
-with the horizontal and vertical lines
-indicates the synchronization
-of the driving force with the lattice position of the particle,
-where driving force is maximum positive when the
-force on the particle from the landscape is maximum negative.
-It can be shown this synchronization
-occurs for any initial position of $y$.
-({\it exercise to student})
-
+Once the particle motion
+coincides with the applied drive, 
+the particle position $y$
+crosses the intersection of
+the horizontal and vertical lines.
+This indicates 
+the driving force is maximum positive when the
+force on the particle from the landscape is maximum negative,
+indicating synchronization.
 The slope of $y/\lambda$
-is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
+is proportional to the net force on the particle.
 This can be seen in 
@@
 when $F_{D}(t) \approx 0 $. 
-When $F^D(t) > A_p$, a particle can 
+We invite interested students to repeat this
+simulation for any initial particle position %of $y$
+and a range of simulation constants
+to demonstrate that synchronization in this model
+does not depend on a particular set of conditions.
+%but is a direct consequence of the simplicity of the model.
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{single_particle.pdf}
+\caption{(a) The applied driving force $F^d(t)$ (orange) in Eq.~\ref{eq:drive}
+  where the parameter $F^{dc}$ (blue) is slowly increased from zero
+  to a constant value
+  as described in the text.  (b) 
+  The $y-$position of the driven particle
+  as a function of time %of a single driven particle
+  normalized by the period of the substrate $\lambda$.
+  }
+\label{fig:0}
+\end{figure}
+\end{center}
+
+The competition between the driving force and landscape potential
+can produce a variety of hopping patterns in the particle motion.
+If $A_p$ is large compared to the extrema of $F^{d}(t)$,
+the particle is trapped in a single
+minima so it oscillates back and forth with no net velocity.
+When $F^d(t) > A_p$, a particle can 
 overcome the barrier height of the landscape maxima,
@@
 the particle hops between minima in the energy landscape.
-Here 
+In Fig.~\ref{fig:0}
 the particle moves
@@
 %of the substrate $y(t_0+T) - y(t_0) = \lambda$.
-%single DC case with figure
+%single dc case with figure
 %dc_current 0.01
@@
 %fp_y 0.1
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{single_particle.pdf}
-\caption{(a) The applied driving force $F^D(t)$ (orange) in Eq.~\ref{eq:drive}
-  where the parameter $F^{DC}$ (blue) is slowly increased from zero
-  to a constant value
-  as described in the text.  (b) 
-  The $y-$position of the driven particle
-  as a function of time %of a single driven particle
-  normalized by the period of the substrate $\lambda$.
-  }
-\label{fig:0}
-\end{figure}
-\end{center}
-
-The ratio of $F^{AC}/F^{DC}$ and the barrier height $A_p$
+
+The ratio of $F^{ac}$, $F^{dc}$ and the barrier height $A_p$
 control the rate and length of the particle hops
 forward and backward in the landscape.
-When $F^{AC}/F^{DC} > 1$
-and $F^{DC} - F^{AC} > A_p$ the particle
+When $F^{ac}/F^{dc} > 1$
+and $F^{dc} - F^{ac} > A_p$ the particle
 moves in the negative y-direction 
@@
 To explore the possible hopping patterns,
-we sweep through a range of $F^{DC}$ for fixed $F^{AC}$ and $A_p$,
+we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$,
 as shown in Fig.~\ref{fig:1}(b).
-We keep $F^{DC}$ constant
+We keep $F^{dc}$ constant
 for $\Delta t = 10^4$ timesteps
@@
 sample the average velocity $\langle v_y \rangle $ 
-as a function of $F^{DC}$.
+as a function of $F^{dc}$.
 
 We perform this sweep for several values
-of $F^{AC}$ including the limiting case that the applied force
+of $F^{ac}$ including the limiting case that the applied force
 is a constant value.
-When $F^{AC} = 0$, no steps appear
-in the $\langle v_y \rangle $ vs $F^{DC}$ curve.
+When $F^{ac} = 0$, no steps appear
+in the $\langle v_y \rangle $ vs $F^{dc}$ curve.
 
@@
 despite the overall magnitude
-of $F^{DC}$.
+of $F^{dc}$.
 
@@
 The particle 
-achieves a variety of oscillation modes as a function of $F^{DC}$.
+achieves a variety of oscillation modes as a function of $F^{dc}$.
 A mode is a periodic pattern of hops
 with a constant average particle velocity, $\bar{v}_{y}$
-over a range of driving forces $F^{DC}$.
+over a range of driving forces $F^{dc}$.
 We illustrate mode-locking in 
@@
 \includegraphics[width=\columnwidth]{single}
-\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{DC}$.}
+\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{dc}$.}
 \label{fig:1}
@@
 When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion.
-A driven particle can exhibit mode locking with a well-chosen AC drive and frequency.
+A driven particle can exhibit mode locking with a well-chosen ac drive and frequency.
 In the attached movie, Figure2.mp4, we show the complex dynamics of mode locking, where the driven particle leap-frogs past the other particles.
@@
 \includegraphics[width=\columnwidth]{twenty}
-\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
+\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{ac}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
 The landscape is colored as in Fig.~\ref{fig1}(a).
-\textbf{(b)} Average $\bar{v}_{y}$ versus $F^{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
+\textbf{(b)} Average $\bar{v}_{y}$ versus $F^{dc}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
 \label{fig:2}
@@
 local high density region.
-$F^{DC}/F^{AC} = 1$ [CHECK!]
+$F^{dc}/F^{ac} = 1$ [CHECK!]
 
@@
   Demonstrate that a particle confined to a landscape exerting force
-  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
   can be modeled with the equation of motion described in 
@@
 Shapiro steps vary in width depending on the strength of the
-applied AC forces,
+applied ac forces,
 and are observed in a variety of systems

### 2021-01-11 code/MD_colloid.py
added an aval_statistics subroutine - but not seeing a clean result - is this sampling of transients or a typo somewhere?

@@ -72,7 +72,26 @@ def ramp_dc_force(F_DC, time, parameters):
     return F_DC
 
 #####################################################################
-def md_step(y, time, F_DC, parameters):
+def average_velocity(time, vy, avg_vy, parameters):
+    '''calculate the average velocity over a range of time values for N particles.  
+    Use all vy values, not just those saved during "writemovietime.  So far just "
+    written for the single particle case, where the code is not so interesting.  Subroutine 
+    generally sums all vxi and vyi values across n particles and averages
+    '''
+
+    decifactor = parameters['decifactor']
+
+    avg_vy += vy
+            
+    if time == decifactor:
+
+        avg_vy /= decifactor
+
+    return avg_vy
+
+
+#####################################################################
+def md_step(y, time, F_DC, avg_vy, parameters):
     '''
     '''
 
@@ -87,6 +106,9 @@ def md_step(y, time, F_DC, parameters):
     #driving force
     vy += external_drive(F_DC, time, parameters)
 
+    #calculate the average velocity over all vy values
+    avg_vy = average_velocity(time, vy, avg_vy, parameters)
+    
     #calculate the new position
     y += vy*dt
 
@@ -96,7 +118,7 @@ def md_step(y, time, F_DC, parameters):
     elif y < 0:
         y += SY
     
-    return y, vy
+    return y, vy, avg_vy
 
 
 #####################################################################
@@ -157,57 +179,46 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     
     return 
 
+
 #####################################################################
-def plot_velocity_force(velocity_data,FDC_data,p):
+#def plot_velocity_force(time_data,FDC_data,vy_data,parameters):
+#    '''
+#    '''
+
+#####################################################################
+def plot_velocity_force(time_data,avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC_data,p):
     '''Make Fig. 3 in AJP
     '''
 
     #for plot
     #calculate the driving force from F_DC and time
-    F_AC = p['F_AC']
-    freq = p['freq']
-    period = p['period']
+    #F_AC = p['F_AC']
+    #freq = p['freq']
+    #period = p['period']
     
-    fig = plt.figure(figsize=(8,4))
+    fig = plt.figure(figsize=(6,4))
[…]

### 2021-01-12 code/MD_colloid.py
reproduced the C code!

@@ -186,7 +186,7 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
 #    '''
 
 #####################################################################
-def plot_velocity_force(time_data,avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC_data,p):
+def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC_data,p):
     '''Make Fig. 3 in AJP
     '''
 
@@ -210,7 +210,7 @@ def plot_velocity_force(time_data,avg_FDC_data,avg_vy_data,parameters): #velocit
     #plot the data
     #ax1.plot(FDC_data,vy_data) #,label="F$^{dc}$")
     ax1.plot(avg_FDC_data,avg_vy_data,'.') #,label="F$^{dc}$")
-    #ax1.plot(time_data,F_drive,label="F$^d$(t)",lw=5)
+
     #ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
 
     #plt.xlim(155,157)
@@ -295,10 +295,12 @@ def single_particle(parameters,plot="y-position"):
 
     if plot == "y-position":
         plot_force_position_vs_time(time_data,FDC_data,y_data,parameters)
+        return
+    
     elif plot == "y-velocity":  
-        plot_velocity_force(time_data,avg_FDC_data,avg_vy_data,parameters)
+        return np.average(avg_vy_data)
       
-    return
+
 
 
     
@@ -330,7 +332,7 @@ def set_parameters():
     dict['F_DC_incr'] = 0.01      #amount to increase FDC at every drop step
     dict['F_DC_max'] = 0.1        #"constant" driving force for most of simulation
     dict['drop'] = 4000           #integer timesteps to "ramp" the DC force
-    #dict['decifactor'] = 4000     #decimation factor integer timesteps to average force
+    dict['decifactor'] = 4000     #decimation factor integer timesteps to average force
 
     #control the oscillating component of driving force
     dict['F_AC'] = 0.05              #amplitude of force oscillation
@@ -363,17 +365,37 @@ if __name__ == "__main__":
 
     if make_fig3: 
         #reset some parameters for subsequent figures
-        parameters['F_DC_incr'] = 0.001      #amount to increase FDC at every drop step
-        parameters['F_DC_max'] = 1.0         #"constant" driving force for most of simulation
-        parameters['drop'] = 2000            #integer timesteps to "ramp" the DC force
[…]

### 2021-01-12 manuscript/manuscript_ajp_2020.tex
write about new fig. 3 make exercise to explore backwards motion

@@
 responds to the applied driving force
-by synchronizing its motion across the landscape %maxima 
-to the periodic pattern of 
-applied driving force.
+by moving across the landscape %maxima
+synchronized with 
+the period of $F^d(t)$.
+%applied driving force.
 %along the y-direction
@@
 where the force is scaled with parameter $A_{p}$.
+When $F^d(t) > A_p$, a particle can 
+overcome the barrier height of the landscape,
+and 
+the particle hops between minima in the energy landscape.
 In this section, we fix the landscape parameters
@@
 In Fig.~\ref{fig:0} 
-a single driven particle adjusts
-its motion so the particle traverses
+the driven particle adjusts
+its motion to traverse
 the periodic landscape with the same rhythm as 
@@
 In Fig.~\ref{fig:0}(a)
-we plot $F^d(t)$ defined in Eq.~\ref{eq:drive}.
-%as a function of time.
-The time independent constants are 
+we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
+as a function of time with
+%The time independent
+constants 
 $F^{ac}=0.05$ and $f=0.01$ cycles per time unit.
@@
 we show the $y-$position of the particle
-as a function of time,
-where we 
-normalize $y$ by $\lambda$, the spatial period of the potential.
+as a function of time.
+We 
+normalize $y$ by $\lambda$, the spatial period of the potential
+to show how the particle moves between substrate minima.  
 The initial particle position is $y = 1$,
-where the landscape force is negative $F^l < 0$,
-causing the particle to move into
+where the $F^l$ is negative, 
+causing the particle to move to
 a landscape minima at the start of the simulation.
@@
 %the effects of the landscape become less obvious,
-and the motion of the particle
+the motion of the particle
 becomes locked to the driving period $T$.
+The particle moves
+in the positive y-direction
+through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
+with 
+the average velocity 
+$\bar{v}_y = 2 \lambda f$. % where $T = 1/f$.
 The horizontal dashed lines
@@
 If $A_p$ is large compared to the extrema of $F^{d}(t)$,
-the particle is trapped in a single
-minima so it oscillates back and forth with no net velocity.
-When $F^d(t) > A_p$, a particle can 
-overcome the barrier height of the landscape maxima,
-and 
-the particle hops between minima in the energy landscape.
-In Fig.~\ref{fig:0}
-the particle moves
-in the positive y-direction
-through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
-with 
-the average velocity 
-$\bar{v}_y = 2 \lambda f$ where $T = 1/f$.
+the particle oscillates back and forth
+in a single minima
+with no net velocity.  
+%In Fig.~\ref{fig:0}
+
 %reaching a minimum position
@@
 
-The ratio of $F^{ac}$, $F^{dc}$ and the barrier height $A_p$
+The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
 control the rate and length of the particle hops
 forward and backward in the landscape.
-When $F^{ac}/F^{dc} > 1$
-and $F^{dc} - F^{ac} > A_p$ the particle
+When $F^{dc} - F^{ac} < -A_p$ the particle
 moves in the negative y-direction 
 during part of the cycle.
+We explore this in Ex.~\ref{ex:backwards}.
 To explore the possible hopping patterns,
@@
 of $F^{dc}$.
-
-Phase locked steps occur for average displacements integer
-multiples of the substrate period $n\lambda$.
 
@@
 
+Phase locked steps occur for average displacements integer
+multiples of the substrate period $n\lambda$.
+
 Our simulations reproduce results presented in 
@@
 mode locking in
-experiments of 
+experiments and simulations of 
 driven colloids on a
@@
 \centering
-\includegraphics[width=\columnwidth]{single}
-\caption{(Average particle velocity in the y-direction $\langle v_{y} \rangle$ as a function of a constant driving force $F^{dc}$.}
+\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
+\caption{(Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$.  We fix the amplitude of $F^d(t)$ as $F^{ac}=0.05$ as in Fig.~\ref{fig:0}}.
 \label{fig:1}

### 2021-01-12 code/MD_colloid.py
not normalizing vy correctly OR not zeroing properly

@@ -196,7 +196,7 @@ def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC
     #freq = p['freq']
     #period = p['period']
     
-    fig = plt.figure(figsize=(6,4))
+    fig = plt.figure(figsize=(7,4))
     gs=gridspec.GridSpec(1,1)
     ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
 
@@ -332,7 +332,7 @@ def set_parameters():
     dict['F_DC_incr'] = 0.01      #amount to increase FDC at every drop step
     dict['F_DC_max'] = 0.1        #"constant" driving force for most of simulation
     dict['drop'] = 4000           #integer timesteps to "ramp" the DC force
-    dict['decifactor'] = 4000     #decimation factor integer timesteps to average force
+    dict['decifactor'] = 5000     #decimation factor integer timesteps to average force
 
     #control the oscillating component of driving force
     dict['F_AC'] = 0.05              #amplitude of force oscillation
@@ -369,11 +369,11 @@ if __name__ == "__main__":
         #parameters['drop'] = 2000            #integer timesteps to "ramp" the DC force
         #parameters['decifactor'] = 2000      #integer timesteps to "ramp" the DC force
 
-        #parameters['maxtime']=3000000        #total time steps in simulation
+        #parameters['maxtime']=100000           #total time steps in simulation can be short
         parameters['filename']="sweep_FDC_vs_vx.pdf"
         
         delta_Fdc = 0.001
-        Fdc_max=0.4
+        Fdc_max=0.3
         max_value = int(Fdc_max/delta_Fdc)
         avg_vy_data = np.zeros(max_value)
         Fdc_data = np.arange(0,Fdc_max,delta_Fdc)

### 2021-01-13 manuscript/manuscript_ajp_2020.tex
removed ramp in F^DC and removed related text

@@
 %be zero or negative depending the the parameters and time.
-When $F^{dc}$ is non-zero,  
-%In several simulations
-we slowly increase 
-$F^{dc}$ from zero
-to avoid transient behavior
-by ensuring the particle is subject to a smoothly varying force.
-We illustrate the increase
-of $F^{dc}$ in Fig.~\ref{fig:0}(a).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%RAMP!!!
+%%%When $F^{dc}$ is non-zero,  we slowly increase $F^{dc}$ from zero to avoid transient behavior by ensuring the particle is subject to a smoothly varying force.
+We illustrate the increase of $F^{dc}$ in Fig.~\ref{fig:0}(a).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The inertia of 
-small particles is greatly reduced by interactions
+small particles is reduced by interactions
 with fluid particles \cite{Purcell1977}.
@@
 %The time independent
-constants 
+constants $F^{dc}=0.1$, 
 $F^{ac}=0.05$ and $f=0.01$ cycles per time unit.
@@
 $T = 1/f = 100$ time units.
-To avoid transient oscillations at early times, 
-the dc driving force is initially zero   
-and 
-slowly increased %$F^{dc}$.
-at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  
-to the constant value $F^{dc}=0.1$.
-In Fig.~\ref{fig:0}(a) we plot $F^{dc}$
-in blue to show the increase in 
-$F^{dc}$ for the first $40$ time units
-In orange we show 
-the combined ac and dc drive $F^d(t)$ 
-when the magnitude of the ac applied force is initially zero.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%RAMP
+%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$.
+at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$.
+In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %since $\sin{(0)}=0$.
@@
 \includegraphics[width=\columnwidth]{single_particle.pdf}
-\caption{(a) The applied driving force $F^d(t)$ (orange) in Eq.~\ref{eq:drive}
-  where the parameter $F^{dc}$ (blue) is slowly increased from zero
-  to a constant value
-  as described in the text.  (b) 
+\caption{(a) The applied driving force $F^d(t)$. % (Eq.~\ref{eq:drive}).
+  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
+  (b) 
   The $y-$position of the driven particle

### 2021-01-13 code/MD_colloid.py

@@ -132,7 +132,7 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     freq = p['freq']
     period = p['period']
     
-    fig = plt.figure(figsize=(8,8))
+    fig = plt.figure(figsize=(8,7.25))
     gs=gridspec.GridSpec(2,1)
     ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
     ax2 = fig.add_subplot(gs[1,0]) #,sharex=ax1)  #scatter plot of particles
@@ -145,9 +145,9 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     # time = m/(4*freq)
 
         #plot the data
-    ax1.plot(time_data,FDC_data,label="F$^{dc}$")
+    #ax1.plot(time_data,FDC_data,label="F$^{dc}$")
     ax1.plot(time_data,F_drive,label="F$^d$(t)",lw=5)
-    ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
+    #ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)
     #plt.xlim(155,157)
     ax2.set_xlabel("time")
@@ -160,6 +160,9 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     ax2.set_xlim(0,time_data[-1]+1)
     #ax2.set_ylim(0,y_data/period[-1]+0.1)
 
+    ax1.text(0.9,0.85,"(a)",transform = ax1.transAxes,backgroundcolor="white")
+    ax2.text(0.004,0.89,"(b)",transform = ax2.transAxes,backgroundcolor="white",zorder=-10)
+    
     #add horizontal lines for potential minima
     for i in [1,3,5]:
         #ax2.hline(i)
@@ -171,10 +174,9 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
         ax2.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
         ax1.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
 
[…]

### 2021-01-14 code/MD_colloid.py
fixed typo in condition to normalize avg_vy

@@ -72,10 +72,13 @@ def ramp_dc_force(F_DC, time, parameters):
     return F_DC
 
 #####################################################################
-def average_velocity(time, vy, avg_vy, parameters):
-    '''calculate the average velocity over a range of time values for N particles.  
-    Use all vy values, not just those saved during "writemovietime.  So far just "
-    written for the single particle case, where the code is not so interesting.  Subroutine 
+def average_velocity(int_time, vy, avg_vy, parameters):
+    '''calculate the average velocity over 
+    a range of time values for N particles.  
+    Use all vy values, not just those 
+    saved during "writemovietime.  So far just "
+    written for the single particle case, 
+    where the code is not so interesting.  Subroutine 
     generally sums all vxi and vyi values across n particles and averages
     '''
 
@@ -83,20 +86,22 @@ def average_velocity(time, vy, avg_vy, parameters):
 
     avg_vy += vy
             
-    if time == decifactor:
-
+    if int_time % parameters['decifactor'] == 0: 
         avg_vy /= decifactor
-
+        #print(int_time, avg_vy)
+        
     return avg_vy
 
 
 #####################################################################
-def md_step(y, time, F_DC, avg_vy, parameters):
+def md_step(y, int_time, F_DC, avg_vy, parameters):
     '''
     '''
 
     dt = parameters['dt']
     SY = parameters['Sy']
+
+    time = int_time * dt
     
     #integrate the equation of motion \eta v = F^net (eta=1)
 
@@ -107,8 +112,13 @@ def md_step(y, time, F_DC, avg_vy, parameters):
     vy += external_drive(F_DC, time, parameters)
 
     #calculate the average velocity over all vy values
-    avg_vy = average_velocity(time, vy, avg_vy, parameters)
-    
+    avg_vy = average_velocity(int_time, vy, avg_vy, parameters)
+
+    '''
+    decifactor = parameters['decifactor']
+    if int_time == decifactor:
+        print(int_time, avg_vy)
+    '''
     #calculate the new position
     y += vy*dt
 
@@ -271,8 +281,8 @@ def single_particle(parameters,plot="y-position"):
 
         #apply the force calculations for the current position/time
         #note vy is not necessary 
-        y, vy, avg_vy = md_step(y, time, F_DC, avg_vy, parameters)
-
+        y, vy, avg_vy = md_step(y, int_time, F_DC, avg_vy, parameters)
+        
         if int_time % writemovietime == 0:
[…]

### 2021-01-14 code/MD_colloid.py
fixed vy label and set axes limits

@@ -227,10 +227,10 @@ def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC
 
     #plt.xlim(155,157)
     ax1.set_xlabel("F$^{dc}$")
-    ax1.set_ylabel(r"v$_y$")
+    ax1.set_ylabel(r"$\langle$v$_y \rangle$")
 
-    #ax1.set_xlim(0,time_data[-1]+1)
-    #ax2.set_ylim(0,y_data/period[-1]+0.1)
+    ax1.set_xlim(0,avg_FDC_data[-1])
+    ax1.set_ylim(avg_vy_data[0]-0.001,avg_vy_data[-1])
         
     plt.tight_layout(pad=0.2)
     plt.savefig(parameters['filename'])
@@ -335,7 +335,7 @@ def set_parameters():
     dict['time0'] = 0       #initial time in integer timesteps
 
     #start the particle in a local minima (not a local max!)
-    dict['y0'] = 1. #period  #Sy/2
+    dict['y0'] = 0. #period  #Sy/2
 
     #landscape potential
     dict['F0'] = 0.1
@@ -393,7 +393,7 @@ if __name__ == "__main__":
         #parameters['drop'] = 2000            #integer timesteps to "ramp" the DC force
         #parameters['decifactor'] = 2000      #integer timesteps to "ramp" the DC force
 
-        parameters['maxtime']=100000           #total time steps in simulation can be short
+        parameters['maxtime']=100000          #shorter and I don't get steps
         parameters['filename']="sweep_FDC_vs_vx.pdf"
         
         delta_Fdc = 0.001

### 2021-01-14 manuscript/manuscript_ajp_2020.tex
moved multiparticle to conclusion

@@
 %In Fig.~\ref{fig:0}
-
 %reaching a minimum position
@@
 %over the total period $T = 100$.
-%The average velocity $\bar{v}_y$
-%is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
-%over the period of the driving force.
 %In Fig. ~\ref{fig:0}
@@
 The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
-control the rate and length of the particle hops
+control the rate and length of the particle motions 
 forward and backward in the landscape.
@@
 We keep $F^{dc}$ constant
-for $\Delta t = 10^4$ timesteps
+for $\Delta t = 10^5$ simulation timesteps
 and 
@@
 as a function of $F^{dc}$.
-
-We perform this sweep for several values
-of $F^{ac}$ including the limiting case that the applied force
-is a constant value.
-When $F^{ac} = 0$, no steps appear
-in the $\langle v_y \rangle $ vs $F^{dc}$ curve.
-
-Synchronization
-of the driving force with the landscape,
-despite the overall magnitude
-of $F^{dc}$.
+We plot the results in Fig.~\ref{fig:1}
+for $F^{ac} = 0.05$, $f=0.01$, and the landscape force $\vec{F}^{l}$
+shown in Fig.~\ref{fig:0}.
+The steps in $\langle v_y \rangle$ occur because 
+the average velocity of the particle
+is constant across a range of $F^{dc}$.
+This synchronization
+of the particle velocity can be measured
+in terms of the landscape period.
+%despite the overall magnitude
+%of $F^{dc}$.
+Each step represents a different pattern of hops
+between substrate minima
+performed by the particle.
+The average velocity $\langle{v}_y\rangle$
+is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
+over the period of the driving force.
+At low $F^{dc}$, the particle starts and ends in the same minima.
 
@@
 We illustrate mode-locking in 
-the velocity-force plot in Fig.~\ref{fig:1}(b).
+the velocity-force plot in Fig.~\ref{fig:1}.
 Here $\langle v_{y} \rangle$ is increasing in non-uniform steps,
@@
 
+We perform this sweep for several values
+of $F^{ac}$ including the limiting case that the applied force
+is a constant value.
+When $F^{ac} = 0$, no steps appear
+in the $\langle v_y \rangle $ vs $F^{dc}$ curve.
+
 \begin{center}
@@
 \includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
-\caption{(Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$.  We fix the amplitude of $F^d(t)$ as $F^{ac}=0.05$ as in Fig.~\ref{fig:0}}.
+\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$.
+  We fix the remaining parameters in $F^d(t)$ as $F^{ac}=0.05$ and $f = 0.01$ as in Fig.~\ref{fig:0}}.
 \label{fig:1}
@@
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
+
+\section{Associated problems}
+\label{sec:problems}	% You can label sections for reference
+
+\begin{enumerate}
+\item Stokes' law describes the viscous drag on a sphere
+  moving at velocity $\vec{v}$ as 
+  $\vec{F}^{lin} = 3 \pi \eta D \vec{v}$ \cite{}
+  where $\eta$ is the dynamic fluid viscosity and 
+  $D$ is the particle diameter.
+  (In simulation we
+  subsume the constants $3 \pi D$
+  such that $\eta \rightarrow 3 \pi D \eta$.)
+  Often drag forces are
+  modeled as a polynomial series
+  $\vec{F}^{drag} = \vec{F}^{lin} + \vec{F}^{quad} + ... $.
+  Truncating the series to the first term
+  is justified by calculating the Reynolds number  
+  $R = D v \rho / \eta$
+  where $\rho$ is the fluid density and $v$ the particle's speed.
+  When $R$ is small, the quadratic and higher order drag terms
+  may be ignored in favor of the linear drag term.
+
+  Demonstrate the Reynolds number is low
+  for this system.
+
+  Reasonable experimental values for
+  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
+  Viscosity of water decreases with temperature
+  from $1.3 \times 10^{-3} Pa-s$ at $10^{\circ}C$ to 
+  from $0.31 \times 10^{-3} Pa-s$ at $90^{\circ}C$,
+  making $\eta \sim 10^{-3} Pa-s$,
+  where 1 pascal $ = 1 Pa = 1 N/m^2$.
+  Likewise the density $\rho$ varies with temperature
+  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.
+
+  [citation for these values better than wikipedia] \cite{} %CONFIRM!
+  %density $\rho = 0.9982 g/cm^3$
+  %https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
+
+This model should be familiar to readers
+of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
+when studying 
+models Millikan's oil drops.
+
+[could certainly do more with this question to make it more computational.
+For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
+Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...]
+
+\label{ex:reynolds}
+
+\item Newton's second law states that
+  the acceleration of a particle $i$
+  is proportional to 
+  the sum of forces on a particle 
+  \begin{equation}
+  m_i \vec{a}_i = \sum \vec{F}_i
+  \label{eq:n2l}
+  \end{equation}
+  where the constant of proportionality is the
+  inertial mass $m_i$
+  The addition of a dissipative force in a dynamical model
+  on a colloid is typically modeled
+  with a drag force proportional to the particle's velocity
+  in the opposite direction of motion 
+  $\vec{F}^{drag} = - \eta \vec{v}_i$
+  where $\eta$ is the drag coefficient.
+  Demonstrate
+  the ratio of $m/\eta$ has units of time, 
+  %This ratio of the acceleration coefficient $m$
+  %to the drag coefficient $\eta$
+  %is
+  known as the momentum relaxation time.
+  The momentum relaxation time is 
+  known to be small for
+  particles with low Reynolds numbers,
+  indivating 
+  a regime in which the acceleration term can be ignored
+  entirely.
+  Demonstrate that a particle confined to a landscape exerting force
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
+  can be modeled with the equation of motion described in 
+  Eq.~\ref{eq:motion}. 
+  \label{ex:n2l}
+
+\item
+  Generally when solving differential equations,
+  the Euler method is effective for solving linear equations,
+  such as the one-dimensional 
+  $f(y) = df/dy$ 
+  but not higher order methods.
+
+  The Verlet method simplifies to
+
+  %FOLLOW UP WITH THIS!
+  Because we are performing molecular dynamics
+  for a single particle on a smooth potential energy landscape,
+  we use a large simulation time step of 
+  $\Delta t = 0.01$.
+  In Sec.~\ref{sec:sync},
+  we decrease the time step
+  to treat multiple particle interactions.
+
+  \label{ex:euler}
+
+\item Drawing the contour
+
+  The code for generating
+a two dimensional colored plot
+of the potential landscape
+is calculated by evaluating
+the analytic function in Eq.~\ref{eq:landscape}
+for a grid of values $(x_n,y_n)$.
+%is included in the supplementary material,
+
+\item {\bf Brownian motion}
+  is a temperature and viscosity dependent
+  phenomena. \cite{}
+  Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
+These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
+In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
+A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
+Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
+\cite{Allen2017}
+
+  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
+
+  Measure the rate of diffusion.
+
+\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
+
+  \item The Fokker-Planck Equation
+
+  \item Aubrey-Kontorova + commensurability
+
+  \item nanotribology
+
+    kink motion
+    Vanossi et al J.Phys.: Condens. Matter 19 (2007)
+
+\end{enumerate}
+
+\section{Conclusion}
+\label{sec:conclusion}	% You can label sections for reference
+Due to the relative ease of
+manipulation and imagining, 
+colloids are used as experimental models
+for systems relatively hard to access and visualize. 
+%SAME SENTENCE TWICE
+Collections of colloids can
+be used to study the properties of solids and liquids
+%comprised of smaller particles
+%such as atoms \cite{} or electrons \cite{}
+or more exotic systems 
+such as cold atoms or electron gases \cite{Grier2003}.
+
+%Oscillators ordered into chains or lattices.
+%has many important
+%technological applications
+Dynamical mode-locking
+is %often
+observed
+in quantum electronic
+devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
+A single junction contains 
+two superconductoring layers which sandwich an insulating layer.
+When subject to an external voltage,
+Cooper pairs in the superconducting materials
+tunnel through the insulating layer.
+Phase-locking is observed as 
+%phase-locked current loops \cite{} 
+stepped regions in current-voltage (I-V) relationship in these devices,
+where voltage is the analog of external driving force
+and current is that of particle velocity.
+%where a constant current results from a range of voltages
+%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
+%instead of ohmic relationships.
+Known as Shapiro steps, % \cite{},
+these phase locked currents  
+have been observed due to applied ac voltages in 
+single Josephson junctions \cite{Shapiro1963, Golubov2004} and
+coupled arrays of junctions \cite{Benz1990}.
+%either in 
+%velocity-force curves and voltage-current curves \cite{Golubov2004}.
+Shapiro steps vary in width depending on the strength of the
+applied ac forces,
+and are observed in a variety of systems
+displaying
+%are hallmarks of
+non-Ohmic behavior in voltage-current curves,
+including
+ac and dc driven
+charge and spin density waves.
+
+%where these steps are generated
+%by the tendency of the response of a system
+%to be flat across a range of applied driving forces or voltages,
+%which can be probed with
+%  atoms on surfaces.
+%  voltage driven superconducting vortices
+%  confined in a Josephson junction,
+
+%
+%
+%mini review of synchronization in electronics
+%careful - the following is all simulations
+%Recent studies demonstrate
+%that coupled electronic oscillators can be
+%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Supplementary Materials}
 
@@
 
-\section{Associated problems}
-\label{sec:problems}	% You can label sections for reference
-
-\begin{enumerate}
-\item Stokes' law describes the viscous drag on a sphere
-  moving at velocity $\vec{v}$ as 
-  $\vec{F}^{lin} = 3 \pi \eta D \vec{v}$ \cite{}
-  where $\eta$ is the dynamic fluid viscosity and 
-  $D$ is the particle diameter.
-  (In simulation we
-  subsume the constants $3 \pi D$
-  such that $\eta \rightarrow 3 \pi D \eta$.)
-  Often drag forces are
-  modeled as a polynomial series
-  $\vec{F}^{drag} = \vec{F}^{lin} + \vec{F}^{quad} + ... $.
-  Truncating the series to the first term
-  is justified by calculating the Reynolds number  
-  $R = D v \rho / \eta$
-  where $\rho$ is the fluid density and $v$ the particle's speed.
-  When $R$ is small, the quadratic and higher order drag terms
-  may be ignored in favor of the linear drag term.
-
-  Demonstrate the Reynolds number is low
-  for this system.
-
-  Reasonable experimental values for
-  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
-  Viscosity of water decreases with temperature
-  from $1.3 \times 10^{-3} Pa-s$ at $10^{\circ}C$ to 
-  from $0.31 \times 10^{-3} Pa-s$ at $90^{\circ}C$,
-  making $\eta \sim 10^{-3} Pa-s$,
-  where 1 pascal $ = 1 Pa = 1 N/m^2$.
-  Likewise the density $\rho$ varies with temperature
-  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.
-
-  [citation for these values better than wikipedia] \cite{} %CONFIRM!
-  %density $\rho = 0.9982 g/cm^3$
-  %https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
-
-This model should be familiar to readers
-of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
-when studying 
-models Millikan's oil drops.
-
-[could certainly do more with this question to make it more computational.
-For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
-Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...]
-
-\label{ex:reynolds}
-
-\item Newton's second law states that
-  the acceleration of a particle $i$
-  is proportional to 
-  the sum of forces on a particle 
-  \begin{equation}
-  m_i \vec{a}_i = \sum \vec{F}_i
-  \label{eq:n2l}
-  \end{equation}
-  where the constant of proportionality is the
-  inertial mass $m_i$
-  The addition of a dissipative force in a dynamical model
-  on a colloid is typically modeled
-  with a drag force proportional to the particle's velocity
-  in the opposite direction of motion 
-  $\vec{F}^{drag} = - \eta \vec{v}_i$
-  where $\eta$ is the drag coefficient.
-  Demonstrate
-  the ratio of $m/\eta$ has units of time, 
-  %This ratio of the acceleration coefficient $m$
-  %to the drag coefficient $\eta$
-  %is
-  known as the momentum relaxation time.
-  The momentum relaxation time is 
-  known to be small for
-  particles with low Reynolds numbers,
-  indivating 
-  a regime in which the acceleration term can be ignored
-  entirely.
-  Demonstrate that a particle confined to a landscape exerting force
-  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
-  can be modeled with the equation of motion described in 
-  Eq.~\ref{eq:motion}. 
-  \label{ex:n2l}
-
-\item
-  Generally when solving differential equations,
-  the Euler method is effective for solving linear equations,
-  such as the one-dimensional 
-  $f(y) = df/dy$ 
-  but not higher order methods.
-
-  The Verlet method simplifies to
-
-  %FOLLOW UP WITH THIS!
-  Because we are performing molecular dynamics
-  for a single particle on a smooth potential energy landscape,
-  we use a large simulation time step of 
-  $\Delta t = 0.01$.
-  In Sec.~\ref{sec:sync},
-  we decrease the time step
-  to treat multiple particle interactions.
-
-  \label{ex:euler}
-
-\item Drawing the contour
-
-  The code for generating
-a two dimensional colored plot
-of the potential landscape
-is calculated by evaluating
-the analytic function in Eq.~\ref{eq:landscape}
-for a grid of values $(x_n,y_n)$.
-%is included in the supplementary material,
-
-\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
-%D. Métivier, L. Wetzel, and S. Gupta
-%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
-%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)
-
-\item {\bf Brownian motion}
-  is a temperature and viscosity dependent
-  phenomena. \cite{}
-  Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
-These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
-In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
-A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
-Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
-\cite{Allen2017}
-
-  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
-
-  Measure the rate of diffusion.
-
-\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
-
-  \item The Fokker-Planck Equation
-
-  \item Aubrey-Kontorova + commensurability
-
-  \item nanotribology
-
-    kink motion
-    Vanossi et al J.Phys.: Condens. Matter 19 (2007)
-
-\end{enumerate}
-
-\section{Conclusion}
-\label{sec:conclusion}	% You can label sections for reference
-Due to the relative ease of
-manipulation and imagining, 
-colloids are used as experimental models
-for systems relatively hard to access and visualize. 
-%SAME SENTENCE TWICE
-Collections of colloids can
-be used to study the properties of solids and liquids
-%comprised of smaller particles
-%such as atoms \cite{} or electrons \cite{}
-or more exotic systems 
-such as cold atoms or electron gases \cite{Grier2003}.
-
-%Oscillators ordered into chains or lattices.
-%has many important
-%technological applications
-Dynamical mode-locking
-is %often
-observed
-in quantum electronic
-devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
-A single junction contains 
-two superconductoring layers which sandwich an insulating layer.
-When subject to an external voltage,
-Cooper pairs in the superconducting materials
-tunnel through the insulating layer.
-Phase-locking is observed as 
-%phase-locked current loops \cite{} 
-stepped regions in current-voltage (I-V) relationship in these devices,
-where voltage is the analog of external driving force
-and current is that of particle velocity.
-%where a constant current results from a range of voltages
-%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
-%instead of ohmic relationships.
-Known as Shapiro steps, % \cite{},
-these phase locked currents  
-have been observed due to applied ac voltages in 
-single Josephson junctions \cite{Shapiro1963, Golubov2004} and
-coupled arrays of junctions \cite{Benz1990}.
-%either in 
-%velocity-force curves and voltage-current curves \cite{Golubov2004}.
-Shapiro steps vary in width depending on the strength of the
-applied ac forces,
-and are observed in a variety of systems
-displaying
-%are hallmarks of
-non-Ohmic behavior in voltage-current curves,
-including
-ac and dc driven
-charge and spin density waves.
-
-%where these steps are generated
-%by the tendency of the response of a system
-%to be flat across a range of applied driving forces or voltages,
-%which can be probed with
-%  atoms on surfaces.
-%  voltage driven superconducting vortices
-%  confined in a Josephson junction,
-
-%
-%
-%mini review of synchronization in electronics
-%careful - the following is all simulations
-%Recent studies demonstrate
-%that coupled electronic oscillators can be
-%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Supplementary Materials}
-
 \begin{acknowledgments}
@@
 \end{verbatim}
+
+\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
+%D. Métivier, L. Wetzel, and S. Gupta
+%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
+%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)

### 2021-01-16 manuscript/manuscript_ajp_2020.tex
updated fig. 1 to have good colors and arrow lengths

@@
   %What problem did you study and why is it important?
-  Particles
-  %confined to a narrow channel 
-  driven
+  Modeling synchronization
+  with simulations and table-top experiments
+  can 
+  provide insight
+  to complex behaviors
+  in the natural world.
+  Driving particles
   across a washboard potential energy landscape
-  move in 
-  synchronized patterns,
-  as observed in 
-  experiments %al systems 
-  of %interest to condensed matter physics %including 
-  magnetically driven colloidal particles
-  confined by light-fields.
+  is a 
+  common 
+  technique to isolate complex 
+  synchronized patterns 
+  in both simulations and experiments.
+  %as observed in 
+  %experiments %al systems 
+  %of %interest to condensed matter physics %including 
+  %magnetically driven colloidal particles
+  %confined by light-fields.
   %exhibit a variety of synchronization effects.
@@
   We discuss a simple
-  numerical model that
+  numerical model %that
   %exhibits
-  provides insight
-  to synchronization behavior
+  %provides insight
+  %to synchronization behavior
   %and
@@
 Many everyday systems
-exhibit in-phase oscillations of components 
+exhibit in-phase coupled oscillations %of components 
 such as the
 flickering patterns of
-candle flames coupled by temperature fluctuations \cite{Okamoto2016},
-vibrations of singing wineglasses \cite{Arane2009}, 
-and metronomes coupled through a supporting platform \cite{Jia2015}.
+candle flames mediated by temperature fluctuations \cite{Okamoto2016},
+vibrations of singing wineglasses interacting 
+through sound waves \cite{Arane2009}, 
+and metronomes vibrating through a supporting platform \cite{Jia2015}.
 Biological systems benefit from cooperative
@@
 the pendula 
-%two periodic oscillators in close proximity
-to swing in time %, i.e. to synchronize,
-due to interactions through the wall,  
-no matter the original phase of the clocks \cite{Bennett2002}.
+to swing in time, 
+even when started out of phase,
+due to interactions through the wall \cite{Bennett2002}.
 %phase locking
@@
 %({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
-It should be noted that oscillation phase and phase space
-  refer to different uses of the word ``phase.''  Oscillation
-  phase $\phi_0$ is the constant portion of the argument in a periodic function
+It should be noted that the term phase
+has two scientific meanings, 
+``oscillation phase'' and ``phase space''
+%refer to different uses of the word ``phase.''
+Oscillation phase $\phi_0$ is the constant portion of the argument in a periodic function
   $\sin{(\omega t + \phi_0)}$ while phase space refers
@@
 control colloid motions \cite{Ashkin1997}.
-A circular optical trap is designed so the center is
-a local energy minimum where 
-a colloid in the beam center is subject to a
-uniform distribution of photon bombardment. %, making 
-Colloids at a trap edge
-experience a net force
-due to the uneven 
+A circular optical trap is designed
+with a local energy minimum 
+at its center.
+A colloid in the beam center is subject to a
+uniform distribution of photon bombardment,
+and motions away from the center create a net force
+due to an uneven 
 distribution of photon collisions on its surface.
-Depending on the shape of the trap and location of the particle in the trap,
-the radiation pressure either pushes colloids toward the local minima
+%Colloids at a trap edge
+%experience a net force
+%due to the 
+Depending on the %shape of the trap and
+location of the particle in the trap,
+the radiation pressure either restores colloids toward the local minima
 or ejects it from the trap.
@@
 
+In experiments  
+ complex environments can be
+ engineered with light by %, typically made 
+ using diffraction gratings to create a patterned
+ potential energy landscape 
+ with one or more laser beams \cite{}.
 Experiments of colloid particles confined
@@
  %
- In experiment 
- complex environments can be
- engineered with light by %, typically made 
- using diffraction gratings to create a patterned
- potential energy landscape 
- with one or more laser beams \cite{}.
- %
  We plot this function in 
  Fig.~\ref{fig:landscape0}
- we use $N_p = 3$ to illustrate the features of
- Eq.~\ref{eq:ysubstrate}.
+ for $N_p = 3$. %to illustrate the features of
  In Fig.~\ref{fig:landscape0}(a) we show 
- the $x-y$ plane with a contour plot
- of the the 2D potential energy landscape,
+ the $x-y$ plane with a contour plot of $U(y)$ %Eq.~\ref{eq:ysubstrate}
+ to illustrate
+ the 2D potential energy landscape,
  where 
@@
   energy landscape.
-  The period of the landscape, $\lambda = L/N_p$ 
-  where $N_p = 3$, is marked in red.
+  The period of the landscape is $\lambda = L/N_p$,  
+  %is marked in red,
+  where $N_p = 3$.  
   The force due to the landscape %$\vec{F}^l$
@@
   A particle is shown in the region between minima and maxima
-  subject to competing forces due to the landscape and applied driving force.
+  subject to competing forces of the landscape and applied driving force.
   (b) The potential energy function
-  along the y-axis $U_l(y)$,
-  The particle in (a) is shown at the same $y-$position,
-  where the magnitude of force $\vec{F}^l$ is calculated as the slope of this function,
-  directed along the $y-$direction in panel (a).
+  along the y-axis $U_l(y)$.  
+  The particle in (a) is shown at the same $y-$position.
+  The slope of $U_l(y)$ is the 
+  magnitude of force $\vec{F}^l$. %is calculated
+  %as the slope of this function,
+  %directed along the $y-$direction in panel (a).
   }
@@
 \centering
-\caption{Simulation units.}
+\caption{Simulation units and approximate values
+  in experiment.}
 \begin{ruledtabular}
-\begin{tabular}{c c p{5cm}}
-Quantity & Unit \\
+\begin{tabular}{c c c } %p{5cm}}
+Quantity & Simulation Unit & Experimental range\\
 \hline
-length &  $a_0 = 1$ \\
-energy & $E_0 = 1$ \\
+length &  $a_0 = 1$ & $ < a_0 <$\\
+energy & $E_0 = 1$ & $ < E_0 <$ \\
 %electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
@@
 %solvent dielectric constant & $\epsilon \epsilon_0$\\
-force & $F_0 = E_0 / a_0$\\
-velocity &  $ a_0 / \tau $ \\
-viscosity coefficient & $\eta = F_0 \tau / a_0 = 1 $\\
-time &  $ \tau = \eta a_0 / F_0 $ \\
+force & $F_0 = E_0 / a_0$ & $<F_0<$\\
+velocity &  $ a_0 / \tau $ &  $ < v < $\\
+viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
+time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
 
@@
 vertical dashed lines %in panels (a) and (b)
-(i.e. $\sin{(\omega t)} = 1$).
+-- i.e. $\sin{(\omega t)} = 1$.
 
@@
 coincide with the condition the substrate force is
-minimum $F^l = -A_p$ 
-(i.e. $\sin{(\pi y / \lambda)} = 1$).
+minimum $F^l = -A_p$,  
+i.e. $\sin{(\pi y / \lambda)} = 1$.
 %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
@@
 can produce a variety of hopping patterns in the particle motion. 
-If $A_p$ is large compared to the extrema of $F^{d}(t)$,
-the particle oscillates back and forth
-in a single minima
-with no net velocity.  
 %In Fig.~\ref{fig:0}
@@
 %fp_y 0.1
-
+%
 The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
-control the rate and length of the particle motions 
+control the rate and distance a  particle moves 
 forward and backward in the landscape.
-When $F^{dc} - F^{ac} < -A_p$ the particle
-moves in the negative y-direction 
-during part of the cycle.
-We explore this in Ex.~\ref{ex:backwards}.
 To explore the possible hopping patterns,
@@
 and 
-sample the average velocity $\langle v_y \rangle $ 
+measure the average velocity $\langle v_y \rangle $ 
 as a function of $F^{dc}$.
@@
 over the period of the driving force.
-At low $F^{dc}$, the particle starts and ends in the same minima.
+
+If $A_p$ is large compared to the extrema of $F^{d}(t)$,
+the particle oscillates back and forth
+in a single minima
+with no net velocity.
+In Fig.~\ref{fig:1}, this occurs at low
+low $F^{dc}$ when $\langle v_y \rangle$ is zero.
 
@@
 
-Our simulations reproduce results presented in 
-Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
-which demonstrated
-mode locking in
-experiments and simulations of 
-driven colloids on a
-optical periodic landscape.
-
-We 
-show the dynamics 
-in supplementary materials \cite{supp1}.
-
-We perform this sweep for several values
+We explore a range of parameters in Ex.~\ref{ex:parameters}
+where 
+we perform this sweep for several values
 of $F^{ac}$ including the limiting case that the applied force
@@
 in the $\langle v_y \rangle $ vs $F^{dc}$ curve. 
+When $F^{dc} - F^{ac} < -A_p$ the particle
+moves in the negative y-direction 
+during part of the cycle.
+
+We 
+show the dynamics 
+in supplementary materials \cite{supp1}.
 
@@
 \includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$.
-  We fix the remaining parameters in $F^d(t)$ as $F^{ac}=0.05$ and $f = 0.01$ as in Fig.~\ref{fig:0}}.
+\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
+  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
+  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.}
 \label{fig:1}
@@
 
+\item
+  \label{ex:parameters}
+
 \item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
@@
 \label{sec:conclusion}	% You can label sections for reference
+Our simulations reproduce results presented in 
+Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
+which demonstrated
+mode locking in
+experiments and simulations of 
+driven colloids on a
+optical periodic landscape.
 Due to the relative ease of

### 2021-01-16 code/plot_landscape.py

@@ -119,22 +119,22 @@ if __name__ == "__main__":
     scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
 
     ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(shrink=0.05,color='magenta')) #arrowstyle="<-",
-    ax2.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(0+0.02, Sy/2), ha='center', va='center',color='magenta') 
+    ax2.annotate(r"$|\mathrm{\vec{F}^{\ell}}|$", xy=(0+0.02, Sy/2), ha='center', va='center',color='black') 
 
     #add annotation showing period
     ax2.annotate(r'$\lambda$', xy=(-0.9*Z_mag,2*Sy/3), ha='center', va='center')
     ax2.annotate('', xy=(-1.01*Z_mag,2*Sy/3-Sy/6),
                  xytext=(-1.01*Z_mag,2*Sy/3+Sy/6),
                  xycoords='data', textcoords='data',
-                 arrowprops={'arrowstyle': '<|-|>','color':"red"})
+                 arrowprops={'arrowstyle': '<|-|>','color':"black"})
 
     ax1.annotate(r'$\lambda$', xy=(2,2*Sy/3), ha='center', va='center')
     ax1.annotate('', xy=(0.5,2*Sy/3-Sy/6),
                  xytext=(0.5,2*Sy/3+Sy/6),
                  xycoords='data', textcoords='data',
-                 arrowprops={'arrowstyle': '<|-|>','color':"red"})
+                 arrowprops={'arrowstyle': '<|-|>','color':"black"})
     
-    ax1.annotate("", xy=(xp, yp-6), xytext=(xp, yp), arrowprops=dict(color='magenta', shrink=0.05),ha="center")
+    ax1.annotate("", xy=(xp, yp-4), xytext=(xp, yp), arrowprops=dict(color='magenta', shrink=0.05),ha="center")
     ax1.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(xp+1, yp-6),ha="left",va="center")
     
     ax1.annotate("", xy=(xp, yp+8), xytext=(xp, yp), arrowprops=dict(color='gray', shrink=0.05), ha="center")

### 2021-01-16 manuscript/manuscript_ajp_2020.tex
removed all \bar

@@
 with fluid particles \cite{Purcell1977}.
-Our model 
+In this model 
 colloids are overdamped
 -- i.e. suspended in a continuous viscous fluid
-that dissipates energy at a rate such 
+that dissipates energy %at a rate
+such 
 that the particles do not accelerate.
@@
 spheres moving through fluids in 
-Section~\ref{sec:problems} Exercise~\ref{ex:reynolds}. %for more information
+%Section~\ref{sec:problems}
+Exercise~\ref{ex:reynolds}. %for more information
 %We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
@@
 \begin{equation}
-  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{d}(t).
+  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{d}(t).
     \label{eq:motion}
@@
 %and Exercise~\ref{ex:reynolds}.
-In %Section~\ref{sec:problems}
-Exercise~\ref{ex:n2l}
-we invite the reader to confirm this result.
-
+%In %Section~\ref{sec:problems}
+%Exercise~\ref{ex:n2l}
+%we invite the reader to confirm this result.
 The equation of motion provides a direct calculation of the velocity
@@
 and the simulation time.
+
 The molecular dynamics simulation is controlled by a $for()$ loop
- which runs from an initial to maximum integer number of time steps $t_i$.
-Each integer time step interval $t_{i+1}-t_i$
+which runs from an initial to maximum integer number of time steps.
+%$t_i$.
+Each integer time step interval %$t_{i+1}-t_i$
 represents a simulation time interval of $\Delta t$ 
@@
 the equation of motion to move particles
-to an updated position
-$\vec{r}_i(t+\Delta t)$.
-%
+to an updated position.
+%$\vec{r}_i(t+\Delta t)$.%
 Since the acceleration as zero,
@@
 \end{equation}
-for a small time step $\Delta t$.
-In Section~\ref{sec:problems} Exercise~\ref{ex:euler}
-we elaborate on
+for a small time step $\Delta t = 0.001 \tau$.
+In %Section~\ref{sec:problems}
+Exercise~\ref{ex:euler}
+we describe 
 the numerical methods for 
-solving differential equations,
-and demonstrate how the Verlet method
-simplifies to the Euler method when $\vec{a}=0$.
+solving differential equations.
 %
@@
 \caption{Simulation units and approximate values
-  in experiment.}
+  in experiment. (coming soon!)}
 \begin{ruledtabular}
@@
 constants $F^{dc}=0.1$, 
-$F^{ac}=0.05$ and $f=0.01$ cycles per time unit.
+$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
 The temporal period of the driving force is
-$T = 1/f = 100$ time units.
+$T = 1/f = 100 \tau$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 to show how the particle moves between substrate minima.  
-The initial particle position is $y = 1$,
-where the $F^l$ is negative, 
-causing the particle to move to
-a landscape minima at the start of the simulation.
+The initial particle position is $y = 1 a_0$,
+where the $F^l$ is negative.
+%JUST BECAUSE
+%causing the particle to move to
+%a landscape minima at the start of the simulation.
 As the driving force increases,
@@
 the motion of the particle
-becomes locked to the driving period $T$.
+synchronizes with the driving period $T$.
 The particle moves
 in the positive y-direction
-through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$,
+through $\Delta y = 2 \lambda$ over the time period $T$,
 with 
 the average velocity 
-$\bar{v}_y = 2 \lambda f$. % where $T = 1/f$.
+$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
 The horizontal dashed lines
@@
 %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
-Once the particle motion
-coincides with the applied drive, 
+%Once the particle motion
+%coincides with the applied drive,
+%indicating synchronization,
+The %shows %indicates the
+driving force is maximum when the landscape 
+force on the particle is minimum,
+as indicated with the coincidence of 
 the particle position $y$
-crosses the intersection of
+with the intersection of
 the horizontal and vertical lines.
-This indicates 
-the driving force is maximum positive when the
-force on the particle from the landscape is maximum negative,
-indicating synchronization.
 The slope of $y/\lambda$
@@
 when $F_{D}(t) \approx 0 $.
-We invite interested students to repeat this
-simulation for any initial particle position %of $y$
-and a range of simulation constants
-to demonstrate that synchronization in this model
-does not depend on a particular set of conditions.
-%but is a direct consequence of the simplicity of the model.
 
@@
 We keep $F^{dc}$ constant
-for $\Delta t = 10^5$ simulation timesteps
+for $10^5$ simulation timesteps
 and 
@@
 as a function of $F^{dc}$.
+The average velocity $\langle{v}_y\rangle$
+is the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
+over the period of the driving force.
 We plot the results in Fig.~\ref{fig:1}
-for $F^{ac} = 0.05$, $f=0.01$, and the landscape force $\vec{F}^{l}$
+for $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
 shown in Fig.~\ref{fig:0}.
-The steps in $\langle v_y \rangle$ occur because 
+Discrete steps in $\langle v_y \rangle$ occur because 
 the average velocity of the particle
@@
 performed by the particle.
-The average velocity $\langle{v}_y\rangle$
-is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
-over the period of the driving force.
 
@@
 with no net velocity.
-In Fig.~\ref{fig:1}, this occurs at low
+In Fig.~\ref{fig:1}, this occurs at 
 low $F^{dc}$ when $\langle v_y \rangle$ is zero.
@@
 A mode is a periodic pattern of hops
-with a constant average particle velocity, $\bar{v}_{y}$
+with a constant average particle velocity, $\langle {v}_{y} \rangle$
 over a range of driving forces $F^{dc}$.
@@
 
-\item Newton's second law states that
+\item{Equation of Motion and Integration Methods}
+
+  Newton's second law states that
   the acceleration of a particle $i$
@@
   Eq.~\ref{eq:motion}. 
-  \label{ex:n2l}
-
-\item
+  %\label{ex:n2l}
+
+%\item
   Generally when solving differential equations,
@@
   The Verlet method simplifies to
+
+  and demonstrate how the Verlet method
+  simplifies to the Euler method when $\vec{a}=0$.
 
@@
   \label{ex:euler}
+
+  We invite interested students to repeat this
+simulation for any initial particle position %of $y$
+and a range of simulation constants
+to demonstrate that synchronization in this model
+does not depend on a particular set of conditions.
+%but is a direct consequence of the simplicity of the model.
 
@@
 The landscape is colored as in Fig.~\ref{fig1}(a).
-\textbf{(b)} Average $\bar{v}_{y}$ versus $F^{dc}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
+\textbf{(b)} Average $\langle {v}_{y} \rangle $ versus $F^{dc}$, where $\langle {v}_{y} \rangle$ is the average particle velocity of the driven particle in the y-direction.}
 \label{fig:2}

### 2021-01-16 code/MD_colloid.py
updated x-label to include simulation units

@@ -160,7 +160,7 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     #ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)
     #plt.xlim(155,157)
-    ax2.set_xlabel("time")
+    ax2.set_xlabel("time (\tau)")
     ax2.set_ylabel(r"y/$\lambda$")
     ax1.set_ylabel(r"F(t)")
 
@@ -168,13 +168,13 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
 
     ax1.set_xlim(0,time_data[-1]+1)
     ax2.set_xlim(0,time_data[-1]+1)
-    #ax2.set_ylim(0,y_data/period[-1]+0.1)
+    ax2.set_ylim(-0.1,y_data[-1]/period+0.2)
 
     ax1.text(0.9,0.85,"(a)",transform = ax1.transAxes,backgroundcolor="white")
-    ax2.text(0.004,0.89,"(b)",transform = ax2.transAxes,backgroundcolor="white",zorder=-10)
+    ax2.text(0.9,0.84,"(b)",transform = ax2.transAxes,backgroundcolor="white",zorder=-10)
     
     #add horizontal lines for potential minima
-    for i in [1,3,5]:
+    for i in [1,3,5,7]:
         #ax2.hline(i)
         #, label = "U(y) = -U$_0$")
         ax2.axhline(y=i, color = "black", linestyle = "--")
@@ -374,8 +374,8 @@ if __name__ == "__main__":
 
     parameters = set_parameters()
 
-    make_fig2 = False
-    make_fig3 = True
+    make_fig2 = True #False
+    make_fig3 = False #True
 
     #--------------------------------------------------------------
     #make Fig. 2 - run a single particle at a single driving force

### 2021-01-16 manuscript/manuscript_ajp_2020.tex
updated text around Fig.3

@@
 We 
-normalize $y$ by $\lambda$, the spatial period of the potential
+normalize $y$ by $\lambda$ %, the spatial period of the potential
 to show how the particle moves between substrate minima.  
-The initial particle position is $y = 1 a_0$,
-where the $F^l$ is negative.
+The initial particle position is $y = 0 $. %1 a_0$,
+%where the $F^l$ is negative.
 %JUST BECAUSE
@@
 synchronizes with the driving period $T$.
+We measure 
+average particle velocity $\langle{v}_y\rangle$
+as the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
+over the period of the driving force.
 The particle moves
@@
   The $y-$position of the driven particle
-  as a function of time %of a single driven particle
+  %of a single driven particle
   normalized by the period of the substrate $\lambda$.
+  %as a function of time
   }
@@
 To explore the possible hopping patterns,
-we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$,
-as shown in Fig.~\ref{fig:1}(b).
-We keep $F^{dc}$ constant
+we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
+to illustrate
+a variety of oscillation modes as a function of $F^{dc}$.
+A mode is a periodic pattern of hops
+with a constant average particle velocity, $\langle {v}_{y} \rangle$
+over a range of driving forces $F^{dc}$.
+%as shown
+In Fig.~\ref{fig:1} 
+we keep $F^{dc}$ constant
 for $10^5$ simulation timesteps
@@
 measure the average velocity $\langle v_y \rangle $ 
-as a function of $F^{dc}$.
-The average velocity $\langle{v}_y\rangle$
-is the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
-over the period of the driving force.
-We plot the results in Fig.~\ref{fig:1}
-for $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
+as a function of $F^{dc}$,
+with $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
 shown in Fig.~\ref{fig:0}.
-Discrete steps in $\langle v_y \rangle$ occur because 
-the average velocity of the particle
-is constant across a range of $F^{dc}$.
-This synchronization
-of the particle velocity can be measured
-in terms of the landscape period.
+%We plot the results in Fig.~\ref{fig:1} for 
+The modes appear as 
+discrete steps in $\langle v_y \rangle$ %occur because
+across a range of $F^{dc}$,
+
+%the average velocity of the particle
+%is constant 
 %despite the overall magnitude
@@
 between substrate minima
-performed by the particle.
-
-If $A_p$ is large compared to the extrema of $F^{d}(t)$,
+performed by the particle
+due to the landscape confinement.  
+In Fig.~\ref{fig:1} at %this occurs at 
+low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
+Since 
+$A_p$ is large compared to the extrema of $F^{d}(t)$,
 the particle oscillates back and forth
-in a single minima
-with no net velocity.
-In Fig.~\ref{fig:1}, this occurs at 
-low $F^{dc}$ when $\langle v_y \rangle$ is zero.
-
-The particle 
-achieves a variety of oscillation modes as a function of $F^{dc}$.
-A mode is a periodic pattern of hops
-with a constant average particle velocity, $\langle {v}_{y} \rangle$
-over a range of driving forces $F^{dc}$.
-We illustrate mode-locking in 
-the velocity-force plot in Fig.~\ref{fig:1}.
-Here $\langle v_{y} \rangle$ is increasing in non-uniform steps,
-with a quantized height of
+in a single minima with no net velocity.
+At higher $F^{dc}$ the particle velocity 
+$\langle v_{y} \rangle$ is increasing in steps of uniform height,
 $\langle v_{y} \rangle = n \lambda f$,
 where $n$ is an integer.
+The step width is non-linear 
+and can have a variety of
+interesting patterns - including
+a Devil's staircase pattern \cite{Bak1986}.
 %$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
@@
 
+This synchronization
+of the particle velocity can be measured
+in terms of the landscape period.
 Phase locked steps occur for average displacements integer

### 2021-01-17 manuscript/manuscript_ajp_2020.tex
updated Fig.3, exercises

@@
 In Section~\ref{sec:colloids} we describe colloid particles,
-an relevent
+an relevant
 experimental analog of our simulations.
@@
 
-%Here we model the microscopic dynamics of phase locking in a colloidal model syestem using molecular dynamics (MD).
+%Here we model the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
 
@@
 
-In Fig.~\ref{fig:0} 
-the driven particle adjusts
+%In Fig.~\ref{fig:0} 
+The driven particle adjusts
 its motion to traverse
@@
 -- i.e. $\sin{(\omega t)} = 1$.
-
+%
+%
 %with the initial driving force at is minimum value 
 %$F^d(0) = F^{dc}$. 
-
+%
 In Fig.~\ref{fig:0}(b) 
@@
 normalize $y$ by $\lambda$ %, the spatial period of the potential
-to show how the particle moves between substrate minima.  
+to show  particle motion between substrate minima.  
 The initial particle position is $y = 0 $. %1 a_0$,
@@
 The horizontal dashed lines
-coincide with the condition the substrate force is
-minimum $F^l = -A_p$,  
+coincide with %the condition the is
+minimum substrate force  $F^l = -A_p$,  
 i.e. $\sin{(\pi y / \lambda)} = 1$.
@@
 %indicating synchronization,
-The %shows %indicates the
+The particle synchronizes its motion such that the 
 driving force is maximum when the landscape 
-force on the particle is minimum,
-as indicated with the coincidence of 
-the particle position $y$
+force is minimum,
+as indicated with %the coincidence of 
 with the intersection of
-the horizontal and vertical lines.
+horizontal and vertical lines
+and the particle position $y$.
 The slope of $y/\lambda$
@@
 to illustrate
-a variety of oscillation modes as a function of $F^{dc}$.
+distinct oscillation modes as a function of $F^{dc}$.
 A mode is a periodic pattern of hops
@@
 At higher $F^{dc}$ the particle velocity 
-$\langle v_{y} \rangle$ is increasing in steps of uniform height,
+$\langle v_{y} \rangle$ increases in steps of uniform height,
 $\langle v_{y} \rangle = n \lambda f$,
@@
 and can have a variety of
-interesting patterns - including
-a Devil's staircase pattern \cite{Bak1986}.
+interesting patterns \cite{Bak1986}.
 %$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
@@
 
-This synchronization
-of the particle velocity can be measured
-in terms of the landscape period.
-Phase locked steps occur for average displacements integer
-multiples of the substrate period $n\lambda$.
+%This synchronization
+%of the particle velocity can be measured
+%in terms of the landscape period.
+%Phase locked steps occur for average displacements integer
+%multiples of the substrate period $n\lambda$.
 
@@
 during part of the cycle.
-
-We 
-show the dynamics 
-in supplementary materials \cite{supp1}.
-
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
-  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
-  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.}
-\label{fig:1}
-\end{figure}
-\end{center}
-
-%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
-
 %We examine
@@
 
+We 
+show the dynamics 
+in supplementary materials \cite{supp1}.
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
+\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
+  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
+  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.
+[{\it I believe the slight slope in this curve is due to sampling - where does the particle start/end ?}]}
+\label{fig:1}
+\end{figure}
+\end{center}
+
+%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
+
+[Insert Phase Plots section/figure?]
+
+\section{Associated problems}
+\label{sec:problems}	% You can label sections for reference
+
+\begin{enumerate}
+\item {\bf Drag Models and Reynolds Numbers}
+  Stokes' law describes the viscous drag on a sphere
+  moving at velocity $\vec{v}$ as 
+  $\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
+  where $\eta$ is the dynamic fluid viscosity and 
+  $D$ is the particle diameter \cite{Taylor2005}.
+  In simulation we
+  subsume the constants $3 \pi D$
+  such that $\eta \rightarrow 3 \pi D \eta$.
+  Often drag forces are
+  modeled as a polynomial series
+  $\vec{F}^{drag} = -b \vec{v} - c v^2 \hat{v} + ... $.
+  Truncating the series to the first term
+  is justified by demonstrating the sphere
+  has a low Reynolds number  
+  $R = D v \rho / \eta$
+  where $\rho$ is the fluid density and $v$ the particle's speed.
+  When $R$ is small, the quadratic and higher order drag terms
+  may be ignored in favor of the linear drag term.
+  %
+  Using reasonable values for the
+  experimental analog of this system, 
+  demonstrate the Reynolds number is low
+  for this system.
+
+  Reasonable experimental values for
+  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
+  Viscosity of water decreases with temperature
+  from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
+  from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
+  making $\eta \sim 10^{-3}$ Pa-s,
+  where 1 Pascal is $1$ N/m$^2$.
+  Likewise the density $\rho$ varies with temperature
+  and $\rho \sim 10^3$ kg/cm$^3$ is a reasonable approximation.
+  \cite{asce}
+
+  This model should be familiar to readers
+  of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
+  when studying 
+  models Millikan's oil drops.
+  [{\it could certainly do more with this question to make it more computational.
+For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
+Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...}]
+
+\label{ex:reynolds}
+
+\item{\bf Equation of Motion}
+
+  Newton's second law states that
+  the acceleration of a particle $i$
+  is proportional to 
+  the sum of forces on a particle 
+  \begin{equation}
+  m_i \vec{a}_i = \sum \vec{F}_i
+  \label{eq:n2l}
+  \end{equation}
+  where the constant of proportionality is the
+  inertial mass $m_i$
+  The addition of a dissipative force in a dynamical model
+  on a colloid is typically modeled
+  with a drag force proportional to the particle's velocity
+  in the opposite direction of motion 
+  $\vec{F}^{drag} = - \eta \vec{v}_i$
+  where $\eta$ is the drag coefficient.
+  The ratio of $m/\eta$ has units of time, 
+  %This ratio of the acceleration coefficient $m$
+  %to the drag coefficient $\eta$
+  %is
+  known as the momentum relaxation time.
+  The momentum relaxation time is 
+  known to be small for
+  particles with low Reynolds numbers,
+  indicating 
+  a regime in which the acceleration term can be ignored
+  entirely.
+  (a) Using Newton's Second Law for
+  a small momentum relaxation time, 
+  demonstrate that a particle confined to a landscape exerting force
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
+  can be modeled with the equation of motion described in 
+  Eq.~\ref{eq:motion}. 
+  \label{ex:n2l}
+
+  \item {\bf Integration Methods}
+  Our equation of motion provides
+  a direct calculation for particle velocity.
+  To calculate the position of the particle we
+  integrate the equation of motion using
+  the standard definition of velocity
+  $\vec{v}_i = d\vec{r}_i/dt$.
+  %
+  In our model we use the
+  Euler method to solve this equation.
+  Generally when solving ordinary differential equations,
+  the Euler method is effective for solving linear equations
+  of the form
+  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
+  The solution is calculated algorithmically
+  by stepping in time through $n$ integer steps
+  $t_n = t_0 + n \Delta t$.
+  At each subsequent step the new
+  value for $y$ is calculated as a map solution using
+  discrete times 
+  $y_{n+1} = y_n + f(t_n,y_n)$.
+  The Euler method can be applied to non-linear
+  equations effectively if the time step $\Delta t$
+  is kept sufficiently small.  
+  \cite{Newman}
+
+  Generally molecular dynamics algorithms
+  are solved with higher order methods
+  such as the Verlet method or Runge-Kutta methods.
+
+  and demonstrate how the Verlet method
+  simplifies to the Euler method when $\vec{a}=0$.
+
+  %FOLLOW UP WITH THIS!
+  Because we are performing molecular dynamics
+  for a single particle on a smooth potential energy landscape,
+  we use a large simulation time step of 
+  $\Delta t = 0.01$.
+  In Sec.~\ref{sec:sync},
+  we decrease the time step
+  to treat multiple particle interactions.
+
+  \label{ex:euler}
+
+  We invite interested students to repeat this
+  simulation for any initial particle position %of $y$
+  and a range of simulation constants
+  to demonstrate that synchronization in this model
+  does not depend on a particular set of conditions.
+  %but is a direct consequence of the simplicity of the model.
+
+\item {\bf Visualizing the motion}
+  Drawing the contour
+
+  The code for generating
+a two dimensional colored plot
+of the potential landscape
+is calculated by evaluating
+the analytic function in Eq.~\ref{eq:ysubstrate}
+for a grid of values $(x_n,y_n)$.
+%is included in the supplementary material,
+
+Also the animation library in python...
+
+\item {\bf Brownian motion}
+  is a temperature and viscosity dependent
+  phenomena. \cite{}
+  Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
+These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
+In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
+A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
+Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
+\cite{Allen2017}
+
+  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
+
+  Measure the rate of diffusion.
+
+\item {\bf Exploring Parameters of the Model}
+  \label{ex:parameters}
+
+%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
+%  \item The Fokker-Planck Equation
+%  \item Aubrey-Kontorova + commensurability
+%  \item nanotribology
+ %   kink motion
+ %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
+
+\end{enumerate}
+
+\section{Conclusion}
+\label{sec:conclusion}	% You can label sections for reference
 Fundamental models
@@
 across a potential maximum so the average velocity is zero,
-a phenomena refered to as pinning \cite{Reichhardt2017}.  
+a phenomena referred to as pinning \cite{Reichhardt2017}.  
 %and dissipating energy from the system at all driving forces.
@@
 
-\section{Associated problems}
-\label{sec:problems}	% You can label sections for reference
-
-\begin{enumerate}
-\item Stokes' law describes the viscous drag on a sphere
-  moving at velocity $\vec{v}$ as 
-  $\vec{F}^{lin} = 3 \pi \eta D \vec{v}$ \cite{}
-  where $\eta$ is the dynamic fluid viscosity and 
-  $D$ is the particle diameter.
-  (In simulation we
-  subsume the constants $3 \pi D$
-  such that $\eta \rightarrow 3 \pi D \eta$.)
-  Often drag forces are
-  modeled as a polynomial series
-  $\vec{F}^{drag} = \vec{F}^{lin} + \vec{F}^{quad} + ... $.
-  Truncating the series to the first term
-  is justified by calculating the Reynolds number  
-  $R = D v \rho / \eta$
-  where $\rho$ is the fluid density and $v$ the particle's speed.
-  When $R$ is small, the quadratic and higher order drag terms
-  may be ignored in favor of the linear drag term.
-
-  Demonstrate the Reynolds number is low
-  for this system.
-
-  Reasonable experimental values for
-  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
-  Viscosity of water decreases with temperature
-  from $1.3 \times 10^{-3} Pa-s$ at $10^{\circ}C$ to 
-  from $0.31 \times 10^{-3} Pa-s$ at $90^{\circ}C$,
-  making $\eta \sim 10^{-3} Pa-s$,
-  where 1 pascal $ = 1 Pa = 1 N/m^2$.
-  Likewise the density $\rho$ varies with temperature
-  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.
-
-  [citation for these values better than wikipedia] \cite{} %CONFIRM!
-  %density $\rho = 0.9982 g/cm^3$
-  %https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
-
-This model should be familiar to readers
-of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
-when studying 
-models Millikan's oil drops.
-
-[could certainly do more with this question to make it more computational.
-For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
-Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...]
-
-\label{ex:reynolds}
-
-\item{Equation of Motion and Integration Methods}
-
-  Newton's second law states that
-  the acceleration of a particle $i$
-  is proportional to 
-  the sum of forces on a particle 
-  \begin{equation}
-  m_i \vec{a}_i = \sum \vec{F}_i
-  \label{eq:n2l}
-  \end{equation}
-  where the constant of proportionality is the
-  inertial mass $m_i$
-  The addition of a dissipative force in a dynamical model
-  on a colloid is typically modeled
-  with a drag force proportional to the particle's velocity
-  in the opposite direction of motion 
-  $\vec{F}^{drag} = - \eta \vec{v}_i$
-  where $\eta$ is the drag coefficient.
-  Demonstrate
-  the ratio of $m/\eta$ has units of time, 
-  %This ratio of the acceleration coefficient $m$
-  %to the drag coefficient $\eta$
-  %is
-  known as the momentum relaxation time.
-  The momentum relaxation time is 
-  known to be small for
-  particles with low Reynolds numbers,
-  indivating 
-  a regime in which the acceleration term can be ignored
-  entirely.
-  Demonstrate that a particle confined to a landscape exerting force
-  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
-  can be modeled with the equation of motion described in 
-  Eq.~\ref{eq:motion}. 
-  %\label{ex:n2l}
-
-%\item
-  Generally when solving differential equations,
-  the Euler method is effective for solving linear equations,
-  such as the one-dimensional 
-  $f(y) = df/dy$ 
-  but not higher order methods.
-
-  The Verlet method simplifies to
-
-  and demonstrate how the Verlet method
-  simplifies to the Euler method when $\vec{a}=0$.
-
-  %FOLLOW UP WITH THIS!
-  Because we are performing molecular dynamics
-  for a single particle on a smooth potential energy landscape,
-  we use a large simulation time step of 
-  $\Delta t = 0.01$.
-  In Sec.~\ref{sec:sync},
-  we decrease the time step
-  to treat multiple particle interactions.
-
-  \label{ex:euler}
-
-  We invite interested students to repeat this
-simulation for any initial particle position %of $y$
-and a range of simulation constants
-to demonstrate that synchronization in this model
-does not depend on a particular set of conditions.
-%but is a direct consequence of the simplicity of the model.
-
-\item Drawing the contour
-
-  The code for generating
-a two dimensional colored plot
-of the potential landscape
-is calculated by evaluating
-the analytic function in Eq.~\ref{eq:landscape}
-for a grid of values $(x_n,y_n)$.
-%is included in the supplementary material,
-
-\item {\bf Brownian motion}
-  is a temperature and viscosity dependent
-  phenomena. \cite{}
-  Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
-These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
-In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
-A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
-Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
-\cite{Allen2017}
-
-  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
-
-  Measure the rate of diffusion.
-
-\item
-  \label{ex:parameters}
-
-\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
-
-  \item The Fokker-Planck Equation
-
-  \item Aubrey-Kontorova + commensurability
-
-  \item nanotribology
-
-    kink motion
-    Vanossi et al J.Phys.: Condens. Matter 19 (2007)
-
-\end{enumerate}
-
-\section{Conclusion}
-\label{sec:conclusion}	% You can label sections for reference
 Our simulations reproduce results presented in 
@@
 
-    \bibitem{Stewart1968}  W. C. Stewart CURRENT‐VOLTAGE CHARACTERISTICS OF JOSEPHSON JUNCTIONS Appl. Phys. Lett. 12, 277 (1968).
+    \bibitem{Stewart1968}  W. C. Stewart Current‐Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
 
@@
 
+      \bibitem{Newman} M. Newman, Computational Physics...
+
 \bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
+
+\bibitem{asce}
+  What is the method for citing non-fundamental constants?
+    (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
+    (2) IAPWS 2008 - http://www.iapws.org/relguide/viscosity.html
+  %[citation for these values better than wikipedia] \cite{} %CONFIRM!
+  %density $\rho = 0.9982 g/cm^3$
 

### 2021-01-18 manuscript/manuscript_ajp_2020.tex
slight edits to conclusion, added notes in table 1 about experimental values (see tex doc)

@@
 \caption{Simulation units and approximate values
-  in experiment. (coming soon!)}
+  in experiment ~\cite{Juniper2015}.
+{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
 \begin{ruledtabular}
@@
 \hline
-length &  $a_0 = 1$ & $ < a_0 <$\\
+length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
 energy & $E_0 = 1$ & $ < E_0 <$ \\
@@
 viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
+%juniper uses water–ethanol mixture
 time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
+
+%FROM JUNIPER2015
+%l¼3.5 mm and a laser power per trap of WE0.75mW (trap stiffness: k=3.8\times10^7 kg /s^2; trap depth: V0 = 75 k_B T
+%ref51
+%Juniper, M.
+P.
+N., Besseling, R., Aarts, D.
+G.
+A.
+L.
+& Dullens, R.
+P.
+A.
+Acousto- optically generated potential energy landscapes: potential mapping using colloids under flow.
+Opt.
+Express 27, 28707–28716 (2012).
+%U(x) measured in ratio of k_BT from -75 to -25
+%0 < vAC < 8 micrometer/s and frequency f=0.25 to 0.75 Hz.
+%0 < vDC < 5 micrometer/s
+%convert to force units?
+%check when steps exist - in Juniper - steps don't exist for n=1or n=3, even though steps exist for n¼0,2,4,5 and 6.
+%flexible chains
+%dipole interaction $\Gamma \propto B^2$
+%\Gamma =15 (B=0.43mT) and a stiff chain at \Gamma=392 (B=2.2mT).
+%Kink
+%16 particles in a strong potential energy landscape of 15 minima (trap spacing: l¼5.5 mm; laser power per trap: WE1.75 mW; trap stiffness: k¼8.7?10?7 kg s?2; trap depth: V0¼200 kBT),
+
+%Volpe AJP Parameters
+%We will consider a silica microparticle in water with radius R=1micro m, mass m=11picograms, viscosity eta=0.001 Ns/m^2; $\gamma=6\pi \eta R$,  T=300K, and \tau=0.6\micro s.
 
@@
 \label{sec:conclusion}	% You can label sections for reference
-Fundamental models
-of synchronization 
-can include many coupled oscillators
-or focus on 
-a single particle driven across a periodic potential landscape.
-Single particle studies 
-are useful to understand synchronization
-in the absence of collective effects.
+%Fundamental models
+%of synchronization 
+%can %include many coupled oscillators
+%or
+%focus on 
+A single particle driven across a periodic potential landscape 
+%Single particle studies are useful
+to understand synchronization
+in the absence of collective effects
+due to interactions between particles.
 %A single particle particle oscillator
@@
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
-
 Our simulations reproduce results presented in 
@@
 %SAME SENTENCE TWICE
+
 Collections of colloids can
@@
 such as cold atoms or electron gases \cite{Grier2003}.
-
 %Oscillators ordered into chains or lattices.
@@
 ac and dc driven
-charge and spin density waves.
+charge and spin density waves
+and superconducting vortices in landscapes 
+engineered with periodic patterns of pinning sites.
+Our results can be relevant 
+to synchronization effects
+in a broad range of experiments systems
+including optically confined colloids,
+superconductors with periodic pinning arrays, 
+and the charge and spin of atomic systems.
 
@@
 %  confined in a Josephson junction,
-
-%
-%
 %mini review of synchronization in electronics
@@
 %programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
+
+%\section{Quasi-periodic substrate}
+%\label{sec:quasiperiod}	% You can label sections for reference
+
+%\section{Chaotic dynamics}
+%\label{sec:chaos}	% You can label sections for reference
+
+\begin{acknowledgments}
+
+  We acknowledge Harvey Gould and Jan Tobochnik,
+  who invited us to write the article and
+  supported its development.
+  Charles and Cynthia Reichhardt advised 
+  the project and provided the original molecular dynamics code
+  written in the C programming language.
+  We acknowledge funding from the M.J. Murdock Charitable Trust
+  and the Pacific Research Institute for Science and Mathematics. % (PRISM).
+
+\end{acknowledgments}
+
+\begin{thebibliography}{99}
+% The numeral (here 99) in curly braces is nominally the number of entries in
+% the bibliography. It's supposed to affect the amount of space around the
+% numerical labels, so only the number of digits should matter--and even that
+  % seems to make no discernible difference.
+
+  %useful quick ref
+  %http://www.scholarpedia.org/article/Synchronization
+
+  %intro to oscillators
+\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
+
+\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygens' clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
+
+\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima. Synchronization in flickering of three-coupled candle flames. Sci Rep {\bf 6}, 36145 (2016)
+
+\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, Coupling between two singing wineglasses, Am. J. Phys. {\bf 77}, 1066 (2009). %; https://doi.org/10.1119/1.3119175
+
+\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
+
+%Synchronization of a thermoacoustic oscillator by an external sound source
+%G. Penelet and T. Biwa
+%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189
+
+  %biological examples
+
+\bibitem{Portugal2014} S.
+Portugal, T.
+Hubel, J.
+Fritz, S.
+Heese, D.
+Trobe, B.
+Voelkl, S.
+Hailes, A.
+M.
+Wilson and J.
+R.
+Usherwood.
+Upwash exploitation and downwash avoidance by flap phasing in ibis formation flight.
+Nature {\bf 505}, 399 (2014).
+
+  \bibitem{Aihara2014} I.
+Aihara, T.
+Mizumoto, T.
+Otsuka, H.
+Awano, K.
+Nagira, H.
+G.
+Okuno and K.
+Aihara.
+Spatio-Temporal Dynamics in Collective Frog Choruses Examined by Mathematical Modeling and Field Observations.
+Sci Rep {\bf 4}, 3891 (2014).
+
+  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, Keeping the Beat: A Large Sample Study of Bouncing and Clapping to Music. PLoS ONE 11(7): e0160178. (2016).
+
+  \bibitem{MartinHall1999} G. Martin Hall, Sonya Bahar, and Daniel J. Gauthier, Prevalence of Rate-Dependent Behaviors in Cardiac Muscle. Phys. Rev. Lett. {\bf 82}, 2995 (1999).
+
+  \bibitem{Singer1999} W. Singer. Striving for coherence. Nature, {\bf 397} 391, 1999.
+
+    %technological applications
+    \bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
+
+    %condensed matter intro
+    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
+
+    \bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
+
+    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
+
+    \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
+
+      %PRACTICAL APPLICATION
+    %\bibitem{Agrawal2013} D.
+K.
+Agrawal, J.
+Woodhouse, and A.
+A.
+Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
+
+    \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
+    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
+
+    \bibitem{Stewart1968}  W. C. Stewart Current‐Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
+
+    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
+
+    \bibitem{Benz1990}  S.
+P.
+Benz, M.
+S.
+Rzchowski, M.
+Tinkham, and C.
+J.
+Lobb, Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays, Phys.
+Rev.
+Lett.
+64, 693 (1990); D.
+Dom´ınguez and J.
+V.
+Jos´e, Giant Shapiro steps with screening currents, Phys.
+Rev.
+Lett.
+69,
+514 (1992).
+
+    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il’ichev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
+
+      quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
+    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
+
+      %reichhardt review
+    \bibitem{Reichhardt2017} C.
+Reichhardt and C.
+J.
+Olson Reichhardt, “Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review,” Rep.
+Prog.
+Phys.
+80, 026501 (2017).
+
+    \bibitem{Reichhardt2015} C.
+Reichhardt, and C.
+J.
+O.
+Reichhardt,  Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
+Phys.
+Rev.
+B {\bf 92}, (22).
+(2015).
+
+    \bibitem{Juniper2015} M.
+P.
+N.
+Juniper, A.
+V.
+Straube, R.
+Besseling, D.
+G.
+A.
+L.
+Aarts, and R.
+P.
+A.
+Dullens, Microscopic dynamics of synchronization in driven colloids.
+Nat.
+Commun.
+6, 7187 (2015).
+
+    \bibitem{Juniper2018} Juniper, M.
+P.
+N., Zimmermann, U., Straube, A.
+V., Besseling, R., Aarts, D.
+G.
+A.
+L., Löwen, H., and Dullens, R.
+P.
+A.
+Dynamic mode locking in a driven colloidal system: Experiments and theory.
+New Journal of Physics, 19(1).
+(2017).
+%https://doi.org/10.1088/1367-2630/aa53cd
+
+    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
+
+    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Castañeda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
+
+    \bibitem{Grier2003} D. G. Grier, A revolution in optical manipulation. Nature {\bf 424}, 810 (2003).
+
+     \bibitem{Ashkin1997} Arthur Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).
+
+      \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013
+
+%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
+    \bibitem{Lutz2004} C.
+Lutz, M.
+Kollmann, and C.
+Bechinger, Phys.
+Rev.
+Lett.
+{\bf 93}, 026001 (2004); C.
+Lutz, M.
+Kollmann, C.
+Bechinger, and P.
+Leiderer, J.
+Phys.: Condens.
+Matter {\bf 16}, S4075 (2004).
+
+    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
+
+    \bibitem{Gholami2015} A.
+Gholami, O.
+Steinbock, V.
+Zykov, and E.
+Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
+Rev.
+Lett.
+{\bf 114}, 018103 (2015).
+
+      %Molecular dynamics references
+
+    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
+
+    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).
+
+    \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
+
+      \bibitem{Newman} M. Newman, Computational Physics...
+
+\bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
+
+\bibitem{asce}
+  What is the method for citing non-fundamental constants?
+    (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
+    (2) IAPWS 2008 - http://www.iapws.org/relguide/viscosity.html
+  %[citation for these values better than wikipedia] \cite{} %CONFIRM!
+  %density $\rho = 0.9982 g/cm^3$
+
+%\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.
+
+%\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.
+
+%\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
+%\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).
+
+%\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.
+
+%\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
+%entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
+%\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.
+
+%\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.
+
+%\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
+%and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
+%are incompatible with AJP's editing process.
+
+%\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook} for an excellent overview of math symbols and equations, with examples.
+
+%\bibitem{labelnames} Thinking up a good label name takes a moment, but 
+%it's worth the trouble; we strongly advise against using labels like 
+%\texttt{eq2}, which become extremely confusing after you decide to add 
+%another equation before Eq.~(\ref{deriv}).
+
+%\bibitem{footnotes} You need to process a file twice to get the counters correct.
+
+%\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
+%Phys. Today \textbf{42} (10), 9--11 (1989).  
+% Note that the issue number (10) in this citation is required, because
+% each issue of Physics Today starts over with page 1.  Also note the use of
+% an en-dash (--), not a hyphen (-), for the page range.
+
+%\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
+%\url{<http://ajp.dickinson.edu>}.
+
+%\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
+%\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
+% Note that this book is paginated by chapter; "3-10" is a single page reference
+% that uses a hyphen, not a range of pages that would us an en-dash (--).
+
+%\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
+%a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
+%bibliographic references must be incorporated into the manuscript file
+%as shown here, at least when you send an editable file for production.
+
+%\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
+%Am. J. Phys. \textbf{58} (3), 209--211.  
+% The issue number (3) in this citation is optional, because AJP's pagination 
+% is by volume.
+
+%\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
+%\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
+%G. W. F. Drake (AIP Press, New York, 1996), p.~520.
+
+%\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
+%Institute of Physics, New York, 1990). Available online at 
+%\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
+%it have been made out of date by advancing technology, most of this manual 
+%is still as useful as ever. Just be sure to follow AJP's specific rules
+%whenever they conflict with those in the manual.
+
+\end{thebibliography}
+
+% If your manuscript is conditionally accepted, the editors will ask you to
+% submit your editable LaTeX source file.  Before doing so, you should move
+% all tables and figure captions to the end, as shown below.  Tables come 
+% first, followed by figure captions (with figure inclusions commented-out).
+% Figures should be submitted as separate files, collected with the
+% LaTeX file into a single .zip archive.
+
+%\newpage   % Start a new page for tables
+
+%\begin{table}[h!]
+%\centering
+%\caption{Elementary bosons}
+%\begin{ruledtabular}
+%\begin{tabular}{l c c c c p{5cm}}
+%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
+%\hline
+%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
+%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
+%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
+%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
+%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
+%\end{tabular}
+%\end{ruledtabular}
+%\label{bosons}
+%\end{table}
+
+%\newpage   % Start a new page for figure captions
+
+%\section*{Figure captions}
+
+%\begin{figure}[h!]
+%\centering
+%\includegraphics{GasBulbData.eps}   % This line stays commented-out
+%\caption{Pressure as a function of temperature for a fixed volume of air.  
+%The three data sets are for three different amounts of air in the container. 
+%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
+%that this is a vector graphic, so it can be viewed at any scale without
+%seeing pixels.)}
+
+%\label{gasbulbdata}
+%\end{figure}
+
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Supplementary Materials}
+
+\subsection{Gridded Contour Plot of landscape}
+%code is located in
+%~/pymodules/animation_code/channel_colloid_movie_maker.py
+
+\begin{verbatim}
+##########################################################
+#ADD CONTOUR PLOT
+##########################################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color in the quasi1D potential to contain 
+    the particles in a trough.  
+    Can also add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #assuming Tiare's trough system, so we won't want to cover the entire range
+    X = np.arange(0, L/2.0, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 2.0 # set by what "looks good"
+    Z = Z_mag*np.sin(2*np.pi*X/L)
+    if corrugated == True:
+        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
+
+    cmap=cm.coolwarm_r
+
+    #alphs is the degree of transparency, again, set by what looks good.
+    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
+
+    #ax1.set_xlim(15,20)
+    #ax1.set_ylim(15,20)
+
+    #ax1.set_xlabel(r"$X$")
+    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
+
+    #ax1.set_xticks([])
+    #ax1.set_yticks([])
+    return
+\end{verbatim}
+
+%another confinement technique:
+%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
+%confines single cells and particles with lower energy than light / lasers
+%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
+%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Grid Contour Plot of landscape}
+%code is located in
+%~/pymodules/animation_code/channel_colloid_movie_maker.py
+Testing section - how will putting the code directly in the appendix appear?
+
+\begin{verbatim}
+############################################
+#ADD CONTOUR PLOT
+############################################
+def add_contour(ax,L,N,corrugated = True):
+    '''
+    Hardwired to color quasi1D potential
+    that contains 
+    the particles in a trough.  
+    Can add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    corrugated (default = True)  
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #we don't want to cover the entire range
+    X = np.arange(0, L/2.0, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 2.0 # set by what "looks good"
+    Z = Z_mag*np.sin(2*np.pi*X/L)
+    if corrugated == True:
+        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
+
+    cmap=cm.coolwarm_r
+
+    #alpha = transparency. set by what looks good.
+    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
+
+    #ax1.set_xlim(15,20)
+    #ax1.set_ylim(15,20)
+
+    #ax1.set_xlabel(r"$X$")
+    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
+
+    #ax1.set_xticks([])
+    #ax1.set_yticks([])
+    return
+\end{verbatim}
+
+\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
+%D. Métivier, L. Wetzel, and S. Gupta
+%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
+%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)
 
@@
 $F^{dc}/F^{ac} = 1$ [CHECK!]
-
-%\section{Quasi-periodic substrate}
-%\label{sec:quasiperiod}	% You can label sections for reference
-
-%\section{Chaotic dynamics}
-%\label{sec:chaos}	% You can label sections for reference
-
-\begin{acknowledgments}
-
-  We acknowledge Harvey Gould and Jan Tobochnik,
-  who invited us to write the article and
-  supported its development.
-  Charles and Cynthia Reichhardt advised 
-  the project and provided the original molecular dynamics code
-  written in the C programming language.
-  We acknowledge funding from the M.J. Murdock Charitable Trust
-  and the Pacific Research Institute for Science and Mathematics (PRISM).
-
-\end{acknowledgments}
-
-\begin{thebibliography}{99}
-% The numeral (here 99) in curly braces is nominally the number of entries in
-% the bibliography. It's supposed to affect the amount of space around the
-% numerical labels, so only the number of digits should matter--and even that
-  % seems to make no discernible difference.
-
-  %useful quick ref
-  %http://www.scholarpedia.org/article/Synchronization
-
-  %intro to oscillators
-\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge Univ. Press, Cambridge, 2003).
-
-\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygens' clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
-
-\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima. Synchronization in flickering of three-coupled candle flames. Sci Rep {\bf 6}, 36145 (2016)
-
-\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, Coupling between two singing wineglasses, Am. J. Phys. {\bf 77}, 1066 (2009). %; https://doi.org/10.1119/1.3119175
-
-\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and Xiao, J. Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes. Sci. Rep. {\bf 5}, 17008 (2015).
-
-%Synchronization of a thermoacoustic oscillator by an external sound source
-%G. Penelet and T. Biwa
-%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189
-
-  %biological examples
-
-\bibitem{Portugal2014} S.
-Portugal, T.
-Hubel, J.
-Fritz, S.
-Heese, D.
-Trobe, B.
-Voelkl, S.
-Hailes, A.
-M.
-Wilson and J.
-R.
-Usherwood.
-Upwash exploitation and downwash avoidance by flap phasing in ibis formation flight.
-Nature {\bf 505}, 399 (2014).
-
-  \bibitem{Aihara2014} I.
-Aihara, T.
-Mizumoto, T.
-Otsuka, H.
-Awano, K.
-Nagira, H.
-G.
-Okuno and K.
-Aihara.
-Spatio-Temporal Dynamics in Collective Frog Choruses Examined by Mathematical Modeling and Field Observations.
-Sci Rep {\bf 4}, 3891 (2014).
-
-  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, Keeping the Beat: A Large Sample Study of Bouncing and Clapping to Music. PLoS ONE 11(7): e0160178. (2016).
-
-  \bibitem{MartinHall1999} G. Martin Hall, Sonya Bahar, and Daniel J. Gauthier, Prevalence of Rate-Dependent Behaviors in Cardiac Muscle. Phys. Rev. Lett. {\bf 82}, 2995 (1999).
-
-  \bibitem{Singer1999} W. Singer. Striving for coherence. Nature, {\bf 397} 391, 1999.
-
-    %technological applications
-    \bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
-
-    %condensed matter intro
-    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
-
-    \bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
-
-    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
-
-    \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
-
-      %PRACTICAL APPLICATION
-    %\bibitem{Agrawal2013} D.
-K.
-Agrawal, J.
-Woodhouse, and A.
-A.
-Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
-
-    \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
-    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
-
-    \bibitem{Stewart1968}  W. C. Stewart Current‐Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
-
-    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
-
-    \bibitem{Benz1990}  S.
-P.
-Benz, M.
-S.
-Rzchowski, M.
-Tinkham, and C.
-J.
-Lobb, Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays, Phys.
-Rev.
-Lett.
-64, 693 (1990); D.
-Dom´ınguez and J.
-V.
-Jos´e, Giant Shapiro steps with screening currents, Phys.
-Rev.
-Lett.
-69,
-514 (1992).
-
-    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il’ichev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
-
-      quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
-    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
-
-      %reichhardt review
-    \bibitem{Reichhardt2017} C.
-Reichhardt and C.
-J.
-Olson Reichhardt, “Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review,” Rep.
-Prog.
-Phys.
-80, 026501 (2017).
-
-    \bibitem{Reichhardt2015} C.
-Reichhardt, and C.
-J.
-O.
-Reichhardt,  Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
-Phys.
-Rev.
-B {\bf 92}, (22).
-(2015).
-
-    \bibitem{Juniper2015} M.
-P.
-N.
-Juniper, A.
-V.
-Straube, R.
-Besseling, D.
-G.
-A.
-L.
-Aarts, and R.
-P.
-A.
-Dullens, Microscopic dynamics of synchronization in driven colloids.
-Nat.
-Commun.
-6, 7187 (2015).
-
-    \bibitem{Juniper2018} Juniper, M.
-P.
-N., Zimmermann, U., Straube, A.
-V., Besseling, R., Aarts, D.
-G.
-A.
-L., Löwen, H., and Dullens, R.
-P.
-A.
-Dynamic mode locking in a driven colloidal system: Experiments and theory.
-New Journal of Physics, 19(1).
-(2017).
-%https://doi.org/10.1088/1367-2630/aa53cd
-
-    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
-
-    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Castañeda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
-
-    \bibitem{Grier2003} D. G. Grier, A revolution in optical manipulation. Nature {\bf 424}, 810 (2003).
-
-     \bibitem{Ashkin1997} Arthur Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).
-
-      \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013
-
-%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
-    \bibitem{Lutz2004} C.
-Lutz, M.
-Kollmann, and C.
-Bechinger, Phys.
-Rev.
-Lett.
-{\bf 93}, 026001 (2004); C.
-Lutz, M.
-Kollmann, C.
-Bechinger, and P.
-Leiderer, J.
-Phys.: Condens.
-Matter {\bf 16}, S4075 (2004).
-
-    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
-
-    \bibitem{Gholami2015} A.
-Gholami, O.
-Steinbock, V.
-Zykov, and E.
-Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
-Rev.
-Lett.
-{\bf 114}, 018103 (2015).
-
-      %Molecular dynamics references
-
-    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
-
-    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).
-
-    \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
-
-      \bibitem{Newman} M. Newman, Computational Physics...
-
-\bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
-
-\bibitem{asce}
-  What is the method for citing non-fundamental constants?
-    (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
-    (2) IAPWS 2008 - http://www.iapws.org/relguide/viscosity.html
-  %[citation for these values better than wikipedia] \cite{} %CONFIRM!
-  %density $\rho = 0.9982 g/cm^3$
-
-%\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.
-
-%\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.
-
-%\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
-%\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).
-
-%\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.
-
-%\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
-%entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
-%\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.
-
-%\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.
-
-%\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
-%and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
-%are incompatible with AJP's editing process.
-
-%\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook} for an excellent overview of math symbols and equations, with examples.
-
-%\bibitem{labelnames} Thinking up a good label name takes a moment, but 
-%it's worth the trouble; we strongly advise against using labels like 
-%\texttt{eq2}, which become extremely confusing after you decide to add 
-%another equation before Eq.~(\ref{deriv}).
-
-%\bibitem{footnotes} You need to process a file twice to get the counters correct.
-
-%\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
-%Phys. Today \textbf{42} (10), 9--11 (1989).  
-% Note that the issue number (10) in this citation is required, because
-% each issue of Physics Today starts over with page 1.  Also note the use of
-% an en-dash (--), not a hyphen (-), for the page range.
-
-%\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
-%\url{<http://ajp.dickinson.edu>}.
-
-%\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
-%\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
-% Note that this book is paginated by chapter; "3-10" is a single page reference
-% that uses a hyphen, not a range of pages that would us an en-dash (--).
-
-%\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
-%a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
-%bibliographic references must be incorporated into the manuscript file
-%as shown here, at least when you send an editable file for production.
-
-%\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
-%Am. J. Phys. \textbf{58} (3), 209--211.  
-% The issue number (3) in this citation is optional, because AJP's pagination 
-% is by volume.
-
-%\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
-%\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
-%G. W. F. Drake (AIP Press, New York, 1996), p.~520.
-
-%\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
-%Institute of Physics, New York, 1990). Available online at 
-%\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
-%it have been made out of date by advancing technology, most of this manual 
-%is still as useful as ever. Just be sure to follow AJP's specific rules
-%whenever they conflict with those in the manual.
-
-\end{thebibliography}
-
-% If your manuscript is conditionally accepted, the editors will ask you to
-% submit your editable LaTeX source file.  Before doing so, you should move
-% all tables and figure captions to the end, as shown below.  Tables come 
-% first, followed by figure captions (with figure inclusions commented-out).
-% Figures should be submitted as separate files, collected with the
-% LaTeX file into a single .zip archive.
-
-%\newpage   % Start a new page for tables
-
-%\begin{table}[h!]
-%\centering
-%\caption{Elementary bosons}
-%\begin{ruledtabular}
-%\begin{tabular}{l c c c c p{5cm}}
-%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
-%\hline
-%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
-%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
-%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
-%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
-%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
-%\end{tabular}
-%\end{ruledtabular}
-%\label{bosons}
-%\end{table}
-
-%\newpage   % Start a new page for figure captions
-
-%\section*{Figure captions}
-
-%\begin{figure}[h!]
-%\centering
-%\includegraphics{GasBulbData.eps}   % This line stays commented-out
-%\caption{Pressure as a function of temperature for a fixed volume of air.  
-%The three data sets are for three different amounts of air in the container. 
-%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
-%that this is a vector graphic, so it can be viewed at any scale without
-%seeing pixels.)}
-
-%\label{gasbulbdata}
-%\end{figure}
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Supplementary Materials}
-
-\subsection{Gridded Contour Plot of landscape}
-%code is located in
-%~/pymodules/animation_code/channel_colloid_movie_maker.py
-
-\begin{verbatim}
-##########################################################
-#ADD CONTOUR PLOT
-##########################################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color in the quasi1D potential to contain 
-    the particles in a trough.  
-    Can also add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    a_p = L/N
-
-    #assuming Tiare's trough system, so we won't want to cover the entire range
-    X = np.arange(0, L/2.0, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 2.0 # set by what "looks good"
-    Z = Z_mag*np.sin(2*np.pi*X/L)
-    if corrugated == True:
-        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
-
-    cmap=cm.coolwarm_r
-
-    #alphs is the degree of transparency, again, set by what looks good.
-    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
-
-    #ax1.set_xlim(15,20)
-    #ax1.set_ylim(15,20)
-
-    #ax1.set_xlabel(r"$X$")
-    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
-
-    #ax1.set_xticks([])
-    #ax1.set_yticks([])
-    return
-\end{verbatim}
-
-%another confinement technique:
-%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
-%confines single cells and particles with lower energy than light / lasers
-%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
-%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Grid Contour Plot of landscape}
-%code is located in
-%~/pymodules/animation_code/channel_colloid_movie_maker.py
-Testing section - how will putting the code directly in the appendix appear?
-
-\begin{verbatim}
-############################################
-#ADD CONTOUR PLOT
-############################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color quasi1D potential
-    that contains 
-    the particles in a trough.  
-    Can add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    a_p = L/N
-
-    #we don't want to cover the entire range
-    X = np.arange(0, L/2.0, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 2.0 # set by what "looks good"
-    Z = Z_mag*np.sin(2*np.pi*X/L)
-    if corrugated == True:
-        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
-
-    cmap=cm.coolwarm_r
-
-    #alpha = transparency. set by what looks good.
-    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
-
-    #ax1.set_xlim(15,20)
-    #ax1.set_ylim(15,20)
-
-    #ax1.set_xlabel(r"$X$")
-    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
-
-    #ax1.set_xticks([])
-    #ax1.set_yticks([])
-    return
-\end{verbatim}
-
-\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
-%D. Métivier, L. Wetzel, and S. Gupta
-%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
-%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)

### 2021-01-19 manuscript/manuscript_ajp_2020.tex
worked on constants and exercises

@@
  %the maximum force the substrate can exert on a particle 
- %$A_p = 2\pi U_0/L$.
  %
@@
 \centering
-\caption{Simulation units and approximate values
-  in experiment ~\cite{Juniper2015}.
-{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
+\caption{Simulation units and comparable
+  experimental values~\cite{Juniper2015}.}
+%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
 \begin{ruledtabular}
@@
 force & $F_0 = E_0 / a_0$ & $<F_0<$\\
-velocity &  $ a_0 / \tau $ &  $ < v < $\\
+velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
 viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
@@
 time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
+period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
+potential amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
+temperature & $T_0 = 0$ \footnote{a. see Ex.~\ref{ex:brownian} to include temperature.} & $T \sim 300K $ \\
 
@@
 \end{equation}
-where the force is scaled with parameter $A_{p}$.
-When $F^d(t) > A_p$, a particle can 
-overcome the barrier height of the landscape,
-and 
-the particle hops between minima in the energy landscape.
+where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
 In this section, we fix the landscape parameters
 to $A_{p} = 0.1$ force units
-with $N_p=20$ minima in the landscape
+with $N_p=20$ minima %in the landscape
 corresponding to a spatial period $\lambda = 1.825 a_0$.
@@
 the applied time-dependent force $F^d(t)$.
+When $F^d(t) > A_p$, a particle can 
+overcome the barrier height of the landscape,
+and 
+the particle hops between minima in the energy landscape.
 %
@@
 and can have a variety of
-interesting patterns \cite{Bak1986}.
+interesting patterns
+such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
 %$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
@@
 
-We 
-show the dynamics 
-in supplementary materials \cite{supp1}.
+In the following section
+we include exercises to explore our numerical model,
+including the 
+to linear drag equation in Ex.~\ref{ex:reynolds}
+the equation of motion in Ex.~\ref{ex:n2l},
+and 
+numerical integration techniques in Ex.~\ref{ex:euler}.
+We explore changes in the particle motion
+with parameter changes in Ex.~\ref{ex:parameters}.
+Methods to visualize the dynamics of the particle motion
+are in Ex.~\ref{ex:animation}.
+An extended model that includes finite temperature effects
+is in Ex.~\ref{ex:brownian}.
 
@@
 %In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
-
-[Insert Phase Plots section/figure?]
 
@@
   models Millikan's oil drops.
+
   [{\it could certainly do more with this question to make it more computational.
 For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
-Suggest students model something big and include inertia and quadratic drag, but then we're fairly off topic...}]
+Suggest students model something big to imagine their own life at low Reynolds number...
+fairly off topic...}]
 
@@
 \item{\bf Equation of Motion}
+  \label{ex:n2l}
 
@@
   is proportional to 
-  the sum of forces on a particle 
+  the sum of forces on the particle 
   \begin{equation}
@@
   where $\eta$ is the drag coefficient.
-  The ratio of $m/\eta$ has units of time, 
-  %This ratio of the acceleration coefficient $m$
-  %to the drag coefficient $\eta$
-  %is
-  known as the momentum relaxation time.
-  The momentum relaxation time is 
-  known to be small for
-  particles with low Reynolds numbers,
-  indicating 
-  a regime in which the acceleration term can be ignored
+  The ratio of $m/\eta$ is %has units of time, % and is 
+  known as the momentum relaxation time, %.
+  and is small for
+  particles with low Reynolds numbers.
+  When $m/\eta$ is small,
+  particle acceleration can be ignored
   entirely.
@@
   Eq.~\ref{eq:motion}.
-  \label{ex:n2l}
+
+  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.}
 
@@
 \item {\bf Brownian motion}
+  \label{ex:brownian}
   is a temperature and viscosity dependent
@@
  %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
+
+\item {\bf Visualizing motion + phase plots}
+    \label{ex:animation}
 

### 2021-01-19 manuscript/manuscript_ajp_2020.tex
worked on exercises

@@
 
-  Reasonable experimental values for
+  To first order 
+  approximate experimental values for
   a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
@@
   Likewise the density $\rho$ varies with temperature
-  and $\rho \sim 10^3$ kg/cm$^3$ is a reasonable approximation.
+  but  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
+  first order approximation.
   \cite{asce}
@@
 
-  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.}
+  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.
+This is closely related to the next exercise which is also primarily analytic rather than computational}
 
   \item {\bf Integration Methods}
+    \label{ex:euler}
     Our equation of motion provides
@@
   the standard definition of velocity
-  $\vec{v}_i = d\vec{r}_i/dt$.
-  %
-  In our model we use the
-  Euler method to solve this equation.
+  $\vec{v}_i = d\vec{r}_i/dt$ 
+  via the 
+  %In our model we use the
+  Euler method. % to solve this equation.
   Generally when solving ordinary differential equations,
@@
   equations effectively if the time step $\Delta t$
-  is kept sufficiently small.  
-  \cite{Newman}
-
-  Generally molecular dynamics algorithms
+  is kept sufficiently small \cite{Newman}.
+  Apply the Euler method to our equation
+  of motion to solve for the position of a particle
+  $y_n$ at the $nth$ timestep.
+
+  {\it invite/guide students to play with the timestep and study the results}
+  %FOLLOW UP WITH THIS!
+  %Because we are performing molecular dynamics
+  %for a single particle on a smooth potential energy landscape,
+  %we use a large simulation time step of 
+  %$\Delta t = 0.01$.
+  %In Sec.~\ref{sec:sync},
+  %we decrease the time step
+  %to treat multiple particle interactions.
+
+  Often molecular dynamics algorithms 
   are solved with higher order methods
   such as the Verlet method or Runge-Kutta methods.
-
-  and demonstrate how the Verlet method
-  simplifies to the Euler method when $\vec{a}=0$.
-
-  %FOLLOW UP WITH THIS!
-  Because we are performing molecular dynamics
-  for a single particle on a smooth potential energy landscape,
-  we use a large simulation time step of 
-  $\Delta t = 0.01$.
-  In Sec.~\ref{sec:sync},
-  we decrease the time step
-  to treat multiple particle interactions.
-
-  \label{ex:euler}
-
-  We invite interested students to repeat this
-  simulation for any initial particle position %of $y$
-  and a range of simulation constants
-  to demonstrate that synchronization in this model
-  does not depend on a particular set of conditions.
+  [{\it explain Verlet and/or RK4...}]
+  Demonstrate how the Verlet method
+  simplifies to the Euler method when
+  the particle acceleration $\vec{a}=0$.
+
+  {\it invite/guide students to play with the timestep and study the results in comparison to Euler method}
+
+  %We invite interested students to repeat this
+  %simulation for any initial particle position %of $y$
+  %and a range of simulation constants
+  %to demonstrate that synchronization in this model
+  %does not depend on a particular set of conditions.
   %but is a direct consequence of the simplicity of the model.
-
-\item {\bf Visualizing the motion}
-  Drawing the contour
-
-  The code for generating
-a two dimensional colored plot
-of the potential landscape
-is calculated by evaluating
-the analytic function in Eq.~\ref{eq:ysubstrate}
-for a grid of values $(x_n,y_n)$.
-%is included in the supplementary material,
-
-Also the animation library in python...
 
@@
 
+  Drawing the contour
+
+  The code for generating
+  a two dimensional colored plot
+  of the potential landscape
+  is calculated by evaluating
+  the analytic function in Eq.~\ref{eq:ysubstrate}
+  for a grid of values $(x_n,y_n)$.
+  %is included in the supplementary material,
+
+  Also the animation library in python...
+
+  Phase plots...
+
 \end{enumerate}
@@
 %Single particle studies are useful
-to understand synchronization
-in the absence of collective effects
-due to interactions between particles.
+is useful 
+to study synchronization
+in the absence of collective effects of particle interactions.
+%due to interactions between particles.
 %A single particle particle oscillator
@@
 
-\bibitem{supp1} See Figure1.mp4 in appropriate %\url{}
+      \bibitem{supp1} Supplementary videos coming soon.
+        %See Figure1.mp4 in appropriate %\url{}
 
 \bibitem{asce}
-  What is the method for citing non-fundamental constants?
-    (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
-    (2) IAPWS 2008 - http://www.iapws.org/relguide/viscosity.html
+  %Non-fundamental constants for water viscosity are available
+  %in several databases including 
+  %  (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
+  IAPWS R12-08, 
+  Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance, 
+  September 2008, 
+  %IAPWS 2008 -
+  http://www.iapws.org/relguide/viscosity.html
   %[citation for these values better than wikipedia] \cite{} %CONFIRM!

### 2021-01-20 manuscript/manuscript_ajp_2020.tex
small changes to integration exercise

@@
     \label{ex:euler}
-    Our equation of motion provides
-  a direct calculation for particle velocity.
     To calculate the position of the particle we
@@
     Euler method. % to solve this equation.
-  Generally when solving ordinary differential equations,
+    Our equation of motion provides
+    a direct calculation for particle velocity.
+    %
+  When solving ordinary differential equations,
   the Euler method is effective for solving linear equations
@@
   Apply the Euler method to our equation
-  of motion to solve for the position of a particle
-  $y_n$ at the $nth$ timestep.
-
-  {\it invite/guide students to play with the timestep and study the results}
+  of motion to solve for the analytic expression
+  of position of a particle
+  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
+
+  In our simulations we use the timestep $\Delta t = 0.001$,
+  examine Fig.~\ref{fig:0}
+  for timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
+  over the same maximum time
+  (i.e. decrease the overall simulation time).
+  How to the motions of the particle compare when the timestep
+  becomes large?
+
   %FOLLOW UP WITH THIS!
@@
 
-      \bibitem{Newman} M. Newman, Computational Physics...
+      \bibitem{Newman} M. Newman, Computational Physics, CreateSpace Independent Publishing Platform. (2012).
 

### 2021-01-21 manuscript/manuscript_ajp_2020.tex
updated intro into a single section, started generalizing the conclusion

@@
 
+%\section{Colloidal Models}
+%\label{sec:colloids}
+
+Complex dynamics can be studied with
+colloid particles with experiments and simulation.
+In typical experiments colloids are spheres of 
+plastic suspended in
+highly de-ionized water or silica in suspended in organic solvent.
+%experimental - colloids specifically
+Because 
+the spheres are a few microns in size
+and move at rates of microns per second,
+the position of a particle %is large and slow enough to
+can be imaged as a function of time 
+with a traditional optical camera.
+%due to the large size and slow speed of the particles.
+Individual colloids exhibit 
+Brownian motion,
+where particles change direction %in a seemingly random fashion
+due to 
+collisions 
+with unseen particles comprising the suspending fluid \cite{}.
+%[elaborate - move to associated problems?].
+
+Light is a
+tool for manipulating the colloidal environment.
+A single laser beam can be used to create an optical trap,
+which uses 
+photon radiation pressure to
+control colloid motions \cite{Ashkin1997}.
+A circular optical trap is designed
+with a local energy minimum 
+at its center.
+A colloid in the beam center is subject to a
+uniform distribution of photon bombardment,
+and motions away from the center create a net force
+due to an uneven 
+distribution of photon collisions on its surface.
+%Colloids at a trap edge
+%experience a net force
+%due to the 
+Depending on the %shape of the trap and
+location of the particle in the trap,
+the radiation pressure either restores colloids toward the local minima
+or ejects it from the trap.
+An optically trapped colloid executing Brownian motion
+is a useful probe of microscopic forces,
+and has been studied in detail in Ref.~\cite{Volpe2013}.
+
+%In experiments  
+ Complex environments can be
+ engineered with light by %, typically made 
+ using diffraction gratings to create a patterned
+ potential energy landscape 
+ with one or more laser beams \cite{Grier2003}.
+ How a particle moves
+ in an optical landscape can
+ change
+ when 
+ subject to external driving forces.
+ Individual particles can
+ perform 
+ synchronized % with the environment
+ motions
+ that lock together particle location and velocity.
+ Experimental studies of
+ the microscopic dynamics 
+ colloids performing phase-locked motions
+ produce step-by-step diagrams
+ of particle dynamics useful for
+ understanding synchronization at a single particle level \cite{Juniper2015}.
+
+%Numerical modeling of colloids can provide mechanistic insight
+%that can be difficult to achieve in experimental conditions
+%where Brownian motion and other sources of noise dominate.
+%external forces
+%The
+%dynamics of particles subject to 
+%an applied external force apply to many physical systems.
+%For instance the flow of charges in a conductor,
+%or cells responding to a chemical gradient.
+%The external force 
+%increases the diversity of dynamical behaviors,
+%and can cause particles to flow in
+%a variety of non-linear complex patterns
+%that may be 
+%synchronized.
+%Disordered chaotic dynamics are also possible,
+%where irregular, unpredictable time evolution of
+%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
+%-------------------------------------------------------------
+
 %Given the prevalence of synchronization,
@@
 %In the following paper
-In Section~\ref{sec:colloids} we describe colloid particles,
-an relevant
-experimental analog of our simulations.
+%In Section~\ref{sec:colloids} we describe colloid particles,
+%an relevant
+%experimental analog of our simulations.
 We describe
@@
 Section~\ref{sec:one}.
-In Section~\ref{sec:sync}
-we 
-extend the model to include multiple particles,
-and show how confined 
-interacting particles respond to the same applied driving force.
+%In Section~\ref{sec:sync}
+%we 
+%extend the model to include multiple particles,
+%and show how confined 
+%interacting particles respond to the same applied driving force.
 %including stationary propagation of high density kinks
@@
 %and conclude 
+We conclude with
+exercises for interested students 
+in Section~\ref{sec:problems}.
 In Section~\ref{sec:conclusion}
@@
 such as dusty plasmas, superconducting vortices and Josephson junctions.
-We conclude with
-exercises for interested students 
-in Section~\ref{sec:problems}.
-
-\section{Colloidal Models}
-\label{sec:colloids}
-
-Complex dynamics can be studied with
-colloid particles with experiments and simulation.
-In typical experiments colloids are spheres of 
-plastic suspended in
-highly de-ionized water or silica in suspended in organic solvent.
-%experimental - colloids specifically
-Because 
-the spheres are a few microns in size
-and move at rates of microns per second,
-the position of a particle %is large and slow enough to
-can be imaged as a function of time 
-with a traditional optical camera.
-%due to the large size and slow speed of the particles.
-Individual colloids exhibit 
-Brownian motion,
-where particles change direction %in a seemingly random fashion
-due to 
-collisions 
-with unseen particles comprising the suspending fluid \cite{}.
-%[elaborate - move to associated problems?].
-
-Light is a
-tool for manipulating the colloidal environment.
-A single laser beam can be used to create an optical trap,
-which uses 
-photon radiation pressure to
-control colloid motions \cite{Ashkin1997}.
-A circular optical trap is designed
-with a local energy minimum 
-at its center.
-A colloid in the beam center is subject to a
-uniform distribution of photon bombardment,
-and motions away from the center create a net force
-due to an uneven 
-distribution of photon collisions on its surface.
-%Colloids at a trap edge
-%experience a net force
-%due to the 
-Depending on the %shape of the trap and
-location of the particle in the trap,
-the radiation pressure either restores colloids toward the local minima
-or ejects it from the trap.
-A single optically trapped colloid executing Brownian motion
-is a useful probe of microscopic forces,
-and has been studied in detail in Ref.~\cite{Volpe2013}.
-
-In experiments  
- complex environments can be
- engineered with light by %, typically made 
- using diffraction gratings to create a patterned
- potential energy landscape 
- with one or more laser beams \cite{}.
-Experiments of colloid particles confined
-in optical traps arrays or patterns 
-subject to external driving forces 
-have
-been used to examine the microscopic dynamics
-of individual particles during mode-locking \cite{Juniper2015}.
-This produced step-by-step diagrams
-of particle dynamics that cannot be 
-imaged in electronic systems such as Josephson junctions.
-%Recent work with atomic systems such as Bose-Einstein condensates \cite{Zhang2020}
-Thus the study of
-mode-locking is a useful problem
-of complex quantum mechanical systems.
-
-%external forces
-%The
-%dynamics of particles subject to 
-%an applied external force apply to many physical systems.
-%For instance the flow of charges in a conductor,
-%or cells responding to a chemical gradient.
-%The external force 
-%increases the diversity of dynamical behaviors,
-%and can cause particles to flow in
-%a variety of non-linear complex patterns
-%that may be 
-%synchronized.
-%Disordered chaotic dynamics are also possible,
-%where irregular, unpredictable time evolution of
-%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
-%-------------------------------------------------------------
-
-Numerical modeling of colloids can provide mechanistic insight
-that can be difficult to achieve in experimental conditions
-where Brownian motion and other sources of noise dominate.
 
@@
 \label{sec:conclusion}	% You can label sections for reference
+A single particle oscillator
+in a potential well is 
+much like a skateboarder in a half-pipe or
+a child on a swing.
+If subject to an applied force,
+a confined oscillator may 
+synchronize its location
+to the periodic pattern of the external drive,
+moving back and forth in time with
+the beat. 
 %Fundamental models
@@
 %focus on
-A single particle driven across a periodic potential landscape 
+We have used 
+a single particle driven across a periodic potential landscape 
 %Single particle studies are useful
-is useful 
-to study synchronization
-in the absence of collective effects of particle interactions.
+to study synchronization dynamics. 
 %due to interactions between particles.
-%A single particle particle oscillator
-%within a potential well is 
-%much like a skateboarder in a half-pipe or
-%a child on a swing
-%moving back and forth. % through equilibrium.  % \cite{}.
 The relationship between the driving force and
@@
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
+
 Our simulations reproduce results presented in 
@@
 for systems relatively hard to access and visualize. 
-%SAME SENTENCE TWICE
-
 Collections of colloids can
@@
 engineered with periodic patterns of pinning sites.
+Thus the study of
+mode-locking is a useful problem
+of complex quantum mechanical systems.
 Our results can be relevant 

### 2021-01-22 manuscript/manuscript_ajp_2020.tex
started on the differential equations

@@
   is kept sufficiently small \cite{Newman}.
+  In our simulations we use the timestep $\Delta t = 0.001$,
+  but we find for a single particle
+  we can just as easily used 
+  %examine 
+  %for
+  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
+  over the same maximum time
+  (i.e. decrease the overall simulation time and sampling rate)
+  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
+  This is due to the linear nature of the solution,
+  and the lack of interaction with neighboring particles.
   Apply the Euler method to our equation
@@
   $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
-
-  In our simulations we use the timestep $\Delta t = 0.001$,
-  examine Fig.~\ref{fig:0}
-  for timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
-  over the same maximum time
-  (i.e. decrease the overall simulation time).
-  How to the motions of the particle compare when the timestep
-  becomes large?
+  %How to the motions of the particle compare when the timestep
+  %becomes large?
 
@@
   %we use a large simulation time step of 
-  %$\Delta t = 0.01$.
-  %In Sec.~\ref{sec:sync},
+  %$\Delta t = 0.01$.  %In Sec.~\ref{sec:sync},
   %we decrease the time step
@@
   such as the Verlet method or Runge-Kutta methods.
-  [{\it explain Verlet and/or RK4...}]
+  These methods include  higher order terms
+  that provide accurate solutions for
+  second order differential equations,
+  i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$,
+  where $f_2(y,t)$ is a second derivative function.
+  In Newton's second law this would be proportional
+  to the net force on a single particle.
+  We do not integrate $f_2(y,t)$ since 
+  $a = dv/dt = 0$,
+  and thus rearrange $f_2(y,t)$ to solve directly for $v$,
+  as described in Ex.~\ref{ex:n2l}.
+  The Taylor expansion of the position function $y(t)$
+  \begin{equation}
+    y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 \pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
+  \end{equation}
+  is exact at first order
+  for the $n$-th time step.
+
   Demonstrate how the Verlet method
@@
   the particle acceleration $\vec{a}=0$.
-
-  {\it invite/guide students to play with the timestep and study the results in comparison to Euler method}
 

### 2021-01-26 manuscript/manuscript_ajp_2020.tex
slight text edits including abstract

@@
   plays a key role in many physical processes.
-  %Simplified models
-  %such as 
-  %What problem did you study and why is it important?
-  Modeling synchronization
-  with simulations and table-top experiments
-  can 
-  provide insight
-  to complex behaviors
-  in the natural world.
-  Driving particles
-  across a washboard potential energy landscape
-  is a 
-  common 
-  technique to isolate complex 
-  synchronized patterns 
-  in both simulations and experiments.
-  %as observed in 
-  %experiments %al systems 
-  %of %interest to condensed matter physics %including 
-  %magnetically driven colloidal particles
-  %confined by light-fields.
-  %exhibit a variety of synchronization effects.
-  %in
-  %  Numerical model
   We discuss a simple
   numerical model %that
+  of synchronized particles 
   %exhibits
@@
   a viscous liquid.
+  %Simplified models
+  %such as 
+  %What problem did you study and why is it important?
+  Modeling synchronization
+  with simulations and table-top experiments
+  can 
+  provide insight
+  to complex behaviors
+  in the natural world.
+  We drive 
+  particles
+  across a washboard potential energy landscape, 
+  a 
+  common 
+  technique to isolate complex 
+  synchronized patterns 
+  in both simulations and experiments.
+  %as observed in 
+  %experiments %al systems 
+  %of %interest to condensed matter physics %including 
+  %magnetically driven colloidal particles
+  %confined by light-fields.
+  %exhibit a variety of synchronization effects.
+  %in
+  %  Numerical model
   %
@@
 %and conclude 
-We conclude with
+We include 
 exercises for interested students 
@@
 
+ Particles are subject an external time-dependent driving force
+$\vec{F}_{D}(t)$
+applied parallel to the y-direction.
+We model this force as
+\begin{equation}
+  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
+    \label{eq:drive}
+\end{equation}
+with modifiable parameters including
+a constant component $F^{dc}$,
+and a time dependent component with amplitude $F^{ac}$
+and frequency $\omega = 2 \pi f$.
+%in the positive $y-$direction.
+%but it may 
+%be zero or negative depending the the parameters and time.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%RAMP!!!
+%%%When $F^{dc}$ is non-zero,  we slowly increase $F^{dc}$ from zero to avoid transient behavior by ensuring the particle is subject to a smoothly varying force.
+We illustrate the increase of $F^{dc}$ in Fig.~\ref{fig:0}(a).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%because
+The inertia of 
+small particles is reduced by interactions
+with fluid particles \cite{Purcell1977}.
+In our model
+we assume 
+colloids are overdamped
+-- i.e. colloids are suspended in a continuous viscous fluid
+that dissipates energy %at a rate
+such 
+that the particles do not accelerate.
+%that greatly impedes their motions.
+Energy dissipation from the fluid is modeled
+with a frictional force on particle with velocity $\vec{v}_i$ as
+%that removes energy from
+%the particles,
+%which we model as
+$\vec{F}^{drag}_i = -\eta \vec{v}_i$
+%proportional to the particle velocity 
+with a friction coefficient $\eta$
+proportional to the fluid viscosity.
+We discuss friction models for
+spheres moving through fluids in 
+%Section~\ref{sec:problems}
+Exercise~\ref{ex:reynolds}. %for more information
+%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
 \begin{center}
@@
 \end{center}
-
- Particles are subject an external time-dependent driving force
-$\vec{F}_{D}(t)$
-applied parallel to the y-direction.
-We model this force as
-\begin{equation}
-  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
-    \label{eq:drive}
-\end{equation}
-with modifiable parameters including
-a constant component $F^{dc}$,
-and a time dependent component with amplitude $F^{ac}$
-and frequency $\omega = 2 \pi f$.
-%in the positive $y-$direction.
-%but it may 
-%be zero or negative depending the the parameters and time.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%RAMP!!!
-%%%When $F^{dc}$ is non-zero,  we slowly increase $F^{dc}$ from zero to avoid transient behavior by ensuring the particle is subject to a smoothly varying force.
-We illustrate the increase of $F^{dc}$ in Fig.~\ref{fig:0}(a).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%because
-The inertia of 
-small particles is reduced by interactions
-with fluid particles \cite{Purcell1977}.
-In this model 
-colloids are overdamped
--- i.e. suspended in a continuous viscous fluid
-that dissipates energy %at a rate
-such 
-that the particles do not accelerate.
-%that greatly impedes their motions.
-Energy dissipation from the fluid is modeled
-with a frictional force on particle with velocity $\vec{v}_i$
-%that removes energy from
-%the particles,
-%which we model as
-$\vec{F}^{drag}_i = -\eta \vec{v}_i$
-%proportional to the particle velocity 
-with a friction coefficient $\eta$
-proportional to the fluid viscosity.
-We discuss friction models for
-spheres moving through fluids in 
-%Section~\ref{sec:problems}
-Exercise~\ref{ex:reynolds}. %for more information
-%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
 Newton's second law for an individual particle
@@
 \end{equation}
-with  $\eta = 1$.  
-%which we describe in more detail in Table~\ref{tab:1}
+with  $\eta = 1$ in units of $v_0 / F_0$. 
+%(see Table~\ref{tab:1}).
 %and Exercise~\ref{ex:reynolds}.
@@
 Each integer time step interval %$t_{i+1}-t_i$
-represents a simulation time interval of $\Delta t$ 
-simulation units.  %as described in Table 1
+represents a simulation time of $\Delta t$ 
+simulation units $\tau$.  %as described in Table 1
 At each time step
@@
 velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
-viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $ <\eta<$\\
+viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
 %juniper uses water–ethanol mixture
@@
 to illustrate
-distinct oscillation modes as a function of $F^{dc}$.
+distinct oscillation modes. % as a function of $F^{dc}$.
 A mode is a periodic pattern of hops
@@
   a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
-  Viscosity of water decreases with temperature
+  %Likewise
+  To first order $\eta \sim 10^{-3}$ Pa-s 
+  since 
+  viscosity of water decreases with temperature
   from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
   from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
-  making $\eta \sim 10^{-3}$ Pa-s,
   where 1 Pascal is $1$ N/m$^2$.
-  Likewise the density $\rho$ varies with temperature
+  Likewise the liquid density $\rho$ varies with temperature
   but  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
-  first order approximation.
-  \cite{asce}
+  first order approximation
+  \cite{asce}.
 
@@
 
+  {\it small timesteps matter a great deal when particle interactions
+    are included in the model.  I have demonstrated that
+    without particle interactions we can increase the timestep
+  with no penalty, so this isn't a very interesting problem.}
+
   %FOLLOW UP WITH THIS!
@@
 
+  {\it I have python code that does all of this, but I don't have it
+    set up to play nice with my new python MD code}
+
   Also the animation library in python...
@@
 %Single particle studies are useful
-to study synchronization dynamics. 
+to study synchronization dynamics
+that arise due to the interplay
+between a particles environment and external forces.
 %due to interactions between particles.
@@
 %technological applications
-Dynamical mode-locking
+Dynamical mode-locking, the primary synchronization
+effect explored in this paper, 
 is %often

### 2021-01-28 manuscript/manuscript_ajp_2020.tex
updated exercise and table text

@@
 \centering
-\caption{Simulation units and comparable
-  experimental values~\cite{Juniper2015}.}
+\caption{Simulation parameters and units and comparable
+  experimental values~\cite{Juniper2015}.
+  Blanks %in the experimental parameters
+  indicate
+  units, rather than parameters that
+  are not easily represented by a single value.}
 %{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
@@
 \begin{tabular}{c c c } %p{5cm}}
-Quantity & Simulation Unit & Experimental range\\
+Quantity & Simulation Unit & Experimental value\\
 \hline
 length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
-energy & $E_0 = 1$ & $ < E_0 <$ \\
+energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
 %electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
@@
 %solvent dielectric constant & $\epsilon \epsilon_0$\\
-force & $F_0 = E_0 / a_0$ & $<F_0<$\\
+force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
+time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
 velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
+driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
 viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
 %juniper uses water–ethanol mixture
-time &  $ \tau = \eta a_0 / F_0 $ & $ < \tau <$\\
-period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
-potential amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
-temperature & $T_0 = 0$ \footnote{a. see Ex.~\ref{ex:brownian} to include temperature.} & $T \sim 300K $ \\
+substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
+substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
+temperature & $T_0 = 0$ \footnote{see Ex.~\ref{ex:brownian} to include temperature in the limit where $U_0 \sim k_B T$.} & $T \sim 300K $ \\
 
@@
 %We will consider a silica microparticle in water with radius R=1micro m, mass m=11picograms, viscosity eta=0.001 Ns/m^2; $\gamma=6\pi \eta R$,  T=300K, and \tau=0.6\micro s.
+%thermofisher off the shelf paramagnetic beads
+%https://www.thermofisher.com/us/en/home/references/protocols/proteins-expression-isolation-and-analysis/protein-isolation-protocol/m-270-carboxylic-acid.html
+%~2\times10^9 beads per 30 mg -> 1.5 \times 10^-11 g, 15 ng
 
@@
 including the 
-to linear drag equation in Ex.~\ref{ex:reynolds}
+to linear drag equation in Ex.~\ref{ex:reynolds}, 
 the equation of motion in Ex.~\ref{ex:n2l},
@@
 numerical integration techniques in Ex.~\ref{ex:euler}.
+An extended model that includes finite temperature effects
+is in Ex.~\ref{ex:brownian}.
 We explore changes in the particle motion
@@
 are in Ex.~\ref{ex:animation}.
-An extended model that includes finite temperature effects
-is in Ex.~\ref{ex:brownian}.
 
@@
 
-\begin{enumerate}
-\item {\bf Drag Models and Reynolds Numbers}
+%\begin{enumerate}
+%\item
+\subsection{Drag Models and Reynolds Numbers.}
   Stokes' law describes the viscous drag on a sphere
@@
   subsume the constants $3 \pi D$
-  such that $\eta \rightarrow 3 \pi D \eta$.
+  such that $3 \pi D \eta \rightarrow \eta $.
+  %
   Often drag forces are
-  modeled as a polynomial series
-  $\vec{F}^{drag} = -b \vec{v} - c v^2 \hat{v} + ... $.
+  modeled as a polynomial series ~\cite{Taylor2005}
+  \begin{equation}
+    \vec{F}^{drag} = -b \vec{v} - c v^2 \hat{v} + \ldots  .
+  \end{equation}
+  %This model should be familiar to readers
+  %of a standard classical mechanics text, such as Ref.
+  %when studying 
+  %models Millikan's oil drops.
   Truncating the series to the first term
@@
   where $\rho$ is the fluid density and $v$ the particle's speed.
-  When $R$ is small, the quadratic and higher order drag terms
+  When $R$ is small, the quadratic and higher order terms
   may be ignored in favor of the linear drag term.
-  %
+
   Using reasonable values for the
   experimental analog of this system, 
-  demonstrate the Reynolds number is low
-  for this system.
-
-  To first order 
-  approximate experimental values for
-  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
+  demonstrate the Reynolds number is low.
+  In addition to the values listed in Table ~\ref{tab:1}, 
+ % Approximate experimental values for
+ % a colloid size and speed
+ % are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
+ % %Likewise
+ % To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s 
+ % since 
+ % viscosity of water decreases with temperature
+ % from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
+ % from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
+ % where 1 Pascal is $1$ N/m$^2$.
   %Likewise
-  To first order $\eta \sim 10^{-3}$ Pa-s 
-  since 
-  viscosity of water decreases with temperature
-  from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
-  from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
-  where 1 Pascal is $1$ N/m$^2$.
-  Likewise the liquid density $\rho$ varies with temperature
-  but  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
+  the liquid density $\rho$ varies with temperature
+  with $\rho \sim 10^3$ kg/cm$^3$ a reasonable
   first order approximation
@@
 
-  This model should be familiar to readers
-  of a standard classical mechanics text, such as Ref.~\cite{Taylor2005}
-  when studying 
-  models Millikan's oil drops.
-
-  [{\it could certainly do more with this question to make it more computational.
+%  [{\it could certainly do more with this question to make it more computational.
 For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
@@
 
-\item{\bf Equation of Motion}
+%\item
+\subsection{Equation of Motion}
   \label{ex:n2l}
@@
   where the constant of proportionality is the
-  inertial mass $m_i$
-  The addition of a dissipative force in a dynamical model
-  on a colloid is typically modeled
+  inertial mass $m_i$.  
+  The addition of a dissipative force to a dynamical equation 
+  of colloid motion 
+  is typically modeled
   with a drag force proportional to the particle's velocity
   in the opposite direction of motion 
-  $\vec{F}^{drag} = - \eta \vec{v}_i$
-  where $\eta$ is the drag coefficient.
-  The ratio of $m/\eta$ is %has units of time, % and is 
+  $\vec{F}^{drag} = - \gamma \vec{v}_i$
+  where $\gamma = 3 \pi \eta D$ is the drag coefficient
+  described in Ex.~\ref{ex:reynolds}.
+  The ratio of $m/\gamma$ is %has units of time, % and is 
   known as the momentum relaxation time, %.
@@
   particles with low Reynolds numbers.
-  When $m/\eta$ is small,
+  The mass of the
+  typical experimental colloid particle is $15$ picograms,
+  leading to a momentum relaxation time
+  % \tau = 15 nanograms/(3 pi D \eta)
+  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
+  on the order of microseconds.
+  %of $1.6 ~\mu$s.
+  Confirm for the values listed in Table ~\ref{tab:1},
+  the momentum relaxation time is 
+  $m/\gamma = 0.5 ~\mu$s.
+
+  When $m/\gamma$ is small,
   particle acceleration can be ignored
@@
 
-  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.
+%  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.
 This is closely related to the next exercise which is also primarily analytic rather than computational}
 
-  \item {\bf Integration Methods}
+%\item
+  \subsection{Integration Methods}
     \label{ex:euler}
@@
     Our equation of motion provides
-    a direct calculation for particle velocity.
-    %
+    a direct calculation for particle velocity,
+    as demonstrated in Ex.~\ref{ex:n2l}.
+
   When solving ordinary differential equations,
@@
   second order differential equations,
-  i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$,
-  where $f_2(y,t)$ is a second derivative function.
-  In Newton's second law this would be proportional
+  i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$.
+  %where $f_2(y,t)$ is a second derivative function.
+  In Newton's second law $f_2$ would be proportional
   to the net force on a single particle.
-  We do not integrate $f_2(y,t)$ since 
+
+  In our model 
+  we do not integrate $f_2(y,t)$ since 
   $a = dv/dt = 0$,
@@
   \begin{equation}
-    y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 \pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
+    y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
+    %\pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
   \end{equation}
@@
   simplifies to the Euler method when
-  the particle acceleration $\vec{a}=0$.
+  the particle acceleration $a=0$.
 
@@
 
-\item {\bf Brownian motion}
+%\item
+  \subsection{Brownian motion}
   \label{ex:brownian}
+  Brownian motion 
   is a temperature and viscosity dependent
-  phenomena. \cite{}
-  Consider the consequences of a non-zero temperature on the simulation, in which particles will collide with invisible particles making up the suspending fluid.
-These collisions are more likely at higher temperature due to the increased kinetic energy of the fluid particles, as described by the Maxwell-Boltzmann distribution \cite{}.
-In molecular dynamics simulations temperature effects can be modeled by including randomized forces $f^T$ to emulate the motion of particles undergoing Brownian motion.
-A distribution of randomizes forces contributes equally in all directions such that the force averaged over a finite time interval is zero $\langle f^T(t) \rangle = 0$.
-Random distributions of contain no correlations over the independent variable (time in this case) $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$ where the energy $k_B T$ derived from the Boltzmann constant $k_B$ and temperature $T$ has energy units $E_0$.
-\cite{Allen2017}
-
-  With no applied driving force, measure the minimum temperature required for a single particle to hop between minima in the potential landscape.
-
-  Measure the rate of diffusion.
-
-\item {\bf Exploring Parameters of the Model}
+  phenomena.
+  Particles change direction %randomly
+  due to collisions with fluid particles.
+  The frequency of collisions depends on the properties of
+  the suspending fluid.
+  These collisions are more likely at higher temperature
+  due to the increased kinetic energy of the fluid particles,
+  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.
+
+  %Consider a non-zero temperature in the simulation.
+  %in which particles will collide with invisible particles
+  %making up the suspending fluid.
+  In molecular dynamics simulations temperature effects
+  can be modeled by including randomized forces $f^T$
+  to emulate the motion of particles undergoing Brownian motion.
+  A distribution of random forces contributes equally in all
+  directions such that the force averaged over a finite time interval
+  is zero $\langle f^T(t) \rangle = 0$.
+  Random distributions are not correlated 
+  over the independent variable,
+  where we take our independent variable to be time 
+  $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$
+  for a system with 
+  energy $k_B T$
+  derived from the Boltzmann constant $k_B$
+  and temperature $T$ \cite{Allen2017}.
+  A particle
+  with energy $k_b T_{min} > U_0$ may 
+  hop over landscape
+  barriers.
+
+  % (a) 
+  In simulation we define our temperature parameter
+  $k_b T/E_0 \rightarrow T$
+  since we set the constants to unity.
+  This allows us to choose
+e  a temperature that is easily compared to
+  the other system parameters that scale the forces.
+  For instance, 
+  with
+  no applied driving force,
+  the minimum temperature required for a single particle
+  to hop between minima in the potential landscape is
+  $T_{min} > A_p$.
+  Assuming a particle is confined to
+  motion along the $y-$direction, 
+  measure the position vs. time
+  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$
+  when Brownian motion is included
+  in the model.
+  Confirm that a particle will hop a barrier
+  for sufficiently high $T/A_p$ ratios.
+
+  A quantity of interest
+  for a particle undergoing Brownian motion
+  is the rate of displacement
+  of the particle from its initial position 
+  This is measured as mean square displacement
+  as a function of time
+  \begin{equation}
+    \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
+  \end{equation}
+  where $t_0$ is the initial time at
+  initial position $\vec{r}(t_0)$.
+  With no substrate, we would expect
+  the root mean square displacement (RMSD)
+  to be proportional to the elapsed time 
+  \begin{equation}
+    \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
+  \end{equation}
+  Confirm this result for $A_p = 0$.
+  Measure the RMSD as a function of time
+  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$.
+  Compare your result to the
+  substrate free RMSD.
+
+  %(b)
+  How does Brownian motion affect
+  the formation of Shapiro steps?
+  With driving force reproduce the paper figures...
+
+%\item
+  \subsection{Exploring Parameters of the Model}
   \label{ex:parameters}
+
+  La la la...
 
@@
 
-\item {\bf Visualizing motion + phase plots}
+%\item
+  \subsection{Visualizing motion + phase plots}
   \label{ex:animation}
@@
 
-\end{enumerate}
+%\end{enumerate}
 
@@
 
+  \bibitem{Einstein1905} A Einstein, Investigations on the Theory of the Brownian Movement,  Dover Publications (1956).
+
 %\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

### 2021-01-29 code/MD_colloid.py
brownian motion code

@@ -18,6 +18,27 @@ import matplotlib.gridspec as gridspec
 #set default font of plot
 plt.rc('font', size=24)
 
+
+##################################################################
+def brownian_distribution(parameters):
+    '''
+    '''
+    mu, sigma = 0.0, 1.0 # mean and standard deviation
+
+    #temperature has units of force too, because of course it does
+    kb_T = parameters['temperature']
+
+    timesteps = int(parameters['maxtime'])
+    
+    #use numpy's built-in function to generate a randomized force
+    #do so in bulk for every timestep in the simulation
+    #scale the prefactor by 2 \eta kb T in simulation units    
+    fy_rand = kb_T * np.random.normal(mu, sigma, timesteps)
+
+    return fy_rand
+    
+    #fx_rand = np.random.normal(mu, sigma, int(N_part*(N_part-1)))
+    
 ##################################################################
 def landscape_force(y,parameters):
     '''landscape potential is equation (1) in the manuscript, while force is equation (5) - for now anyway
@@ -94,12 +115,15 @@ def average_velocity(int_time, vy, avg_vy, parameters):
 
 
 #####################################################################
-def md_step(y, int_time, F_DC, avg_vy, parameters):
+def md_step(y, int_time, F_DC, avg_vy, parameters, ft=0):
     '''
+
+    ft random kicks due to temperature affects
     '''
 
     dt = parameters['dt']
     SY = parameters['Sy']
+    temperature = parameters['temperature']
 
     time = int_time * dt
     
@@ -110,6 +134,9 @@ def md_step(y, int_time, F_DC, avg_vy, parameters):
 
     #driving force
     vy += external_drive(F_DC, time, parameters)
+
+    if ft != 0:
+        vy += ft
 
     #calculate the average velocity over all vy values
     avg_vy = average_velocity(int_time, vy, avg_vy, parameters)
@@ -129,6 +156,47 @@ def md_step(y, int_time, F_DC, avg_vy, parameters):
         y += SY
     
     return y, vy, avg_vy
+
+
+#####################################################################
+def plot_position_vs_time(time_data,y_data,p):
+    '''Make Fig. 2 in AJP
+    '''
+
+    #for plot
+    #calculate the driving force from F_DC and time
+    F_AC = p['F_AC']
+    freq = p['freq']
+    period = p['period']
+    
[…]

### 2021-01-29 manuscript/manuscript_ajp_2020.tex
updated some brownian text

@@
 substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
-temperature & $T_0 = 0$ \footnote{see Ex.~\ref{ex:brownian} to include temperature in the limit where $U_0 \sim k_B T$.} & $T \sim 300K $ \\
+temperature & $T_0 = 0$ \footnote{to learn more about the effects
+  of temperature on this simulation
+  see Ex.~\ref{ex:brownian} where we study the limit
+  $U_0 \sim k_B T$.} & $T \sim 300K $ \\
 
@@
   % (a) 
-  In simulation we define our temperature parameter
+  In simulation we define our temperature parameter to
   $k_b T/E_0 \rightarrow T$
   since we set the constants to unity.
-  This allows us to choose
-e  a temperature that is easily compared to
-  the other system parameters that scale the forces.
+  In these units we can compare 
+  simulation temperature directly
+  to force 
+  in order to estimate the degree of random fluctuation.
   For instance, 
@@
   Assuming a particle is confined to
-  motion along the $y-$direction, 
-  measure the position vs. time
-  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$
-  when Brownian motion is included
+  move along the $y-$direction,
+  include Brownian motion 
   in the model.
-  Confirm that a particle will hop a barrier
+  Measure the position vs. time
+  of a non-driven colloid for $T/A_p = 2.0, 4.0, 6.0$
+  and note  a particle will hop a barrier
   for sufficiently high $T/A_p$ ratios.
+  We find the crossover
+  to a hopping regime at $T/A_p \approx 5.6$
+  %when
 

### 2021-01-29 manuscript/manuscript_ajp_2020.tex
put Brownian motion into manuscript and updated code to make figure

@@
   Measure the position vs. time
-  of a non-driven colloid for $T/A_p = 2.0, 4.0, 6.0$
+  of a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$
   and note  a particle will hop a barrier
@@
   %when
+  \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
+      \caption{
+        Motion of a particle undergoing Brownian motion
+        on a washboard potential
+        energy landscape.
+        (a) $T/A_p = 4.0$ no hopping occurs.
+        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
+        (c) $T/A_p = 6.0$ many hops occur.
+        Note the scale of the $y-$axis differs in each panel.
+      }
+      \label{fig:brownian}
+    \end{figure}
+  \end{center}
+  In Fig.~\ref{fig:brownian}
 

### 2021-01-29 code/MD_colloid.py

@@ -159,7 +159,7 @@ def md_step(y, int_time, F_DC, avg_vy, parameters, ft=0):
 
 
 #####################################################################
-def plot_position_vs_time(time_data,y_data,p):
+def plot_position_vs_time(ax2,time_data,y_data,p):
     '''Make Fig. 2 in AJP
     '''
 
@@ -168,10 +168,6 @@ def plot_position_vs_time(time_data,y_data,p):
     F_AC = p['F_AC']
     freq = p['freq']
     period = p['period']
-    
-    fig = plt.figure(figsize=(8,8))
-    gs=gridspec.GridSpec(1,1)
-    ax2 = fig.add_subplot(gs[0,0])  #scatter plot of particles
 
     ax2.plot(time_data,y_data/period,lw=5) #,'o--') #,markevery=100)
     #plt.xlim(155,157)
@@ -191,10 +187,6 @@ def plot_position_vs_time(time_data,y_data,p):
     for i in [1,5,9,13]:
         ax2.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
     '''
-    
-    plt.tight_layout(pad=0.1,h_pad=-0.3)
-    #g.tight_layout(fig, rect=[0, 0, 1, 1], h_pad=p_val,w_pad=p_val,pad=0.0)
-    plt.savefig(parameters['filename'])
     
     return 
 
@@ -384,7 +376,7 @@ def single_particle(parameters,plot="y-position"):
         return np.average(avg_vy_data) #/decifactor
       
 
-def brownian_particle(parameters):
+def brownian_particle(parameters,ax):
     '''
     '''
 
@@ -458,7 +450,7 @@ def brownian_particle(parameters):
         #update the time (simulation units)
         time += dt
 
-    plot_position_vs_time(time_data,y_data,parameters)
+    plot_position_vs_time(ax,time_data,y_data,parameters)
     return
     
     
@@ -481,7 +473,7 @@ def set_parameters():
     dict['y0'] =  dict['Sy']/2
 
     #landscape potential
-    dict['F0'] = 0.1
+    dict['F0'] = 0.1 
     dict['Np'] = 20         #number of troughs in the substrate
     dict['period'] = dict['Sy']/dict['Np']  #spatial period of substrate in y-direction
 
@@ -543,14 +535,33 @@ if __name__ == "__main__":
     if make_brownian:
         
         parameters['dt'] = 0.1 #timestep in simulation units
-        parameters['maxtime']=10000000        #total time steps in simulation
[…]

### 2021-01-30 manuscript/manuscript_ajp_2020.tex
described Brownian figure

@@
   \label{ex:euler}
+  %{\it cut this one?  not really saying much}
     To calculate the position of the particle we
@@
   is a temperature and viscosity dependent
-  phenomena.
-  Particles change direction %randomly
+  phenomena in which 
+  particles change direction %randomly
   due to collisions with fluid particles.
@@
   include Brownian motion 
-  in the model.
-  Measure the position vs. time
-  of a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$
-  and note  a particle will hop a barrier
-  for sufficiently high $T/A_p$ ratios.
-  We find the crossover
-  to a hopping regime at $T/A_p \approx 5.6$
+  in the model,
+  we find the crossover
+  to a hopping regime at $T/A_p \approx 5.6$.
   %when
+  We demonstrate this hopping
+  pattern in 
+  %Measure the position vs. time
+  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
+  %and note  a particle will hop a barrier
+  %for sufficiently high $T/A_p$ ratios.
+  Reproduce these results.
+
   \begin{center}
@@
   In Fig.~\ref{fig:brownian}
+  we show the position versus time of a simple particle
+  confined to a sinusoidal landscape
+  undergoing Brownian motion.
+  We increase the temperature relative
+  to the amplitude of the landscape
+  troughs until the particle enters a hopping regime.
+  In  Fig.~\ref{fig:brownian}(a)
+  $T/A_p = 4.0$ and the particle executes a 
+  random walk centered at the potential minima $y/\lambda = 10$.
+  We ran many simulations and never observed a hop to another minima.
+  In  Fig.~\ref{fig:brownian}(b)
+  $T/A_p = 5.0$ where hops between
+  potential minima are possible but not probable,
+  a single hop occurs from
+  $y/\lambda = 10$ to $y/\lambda = 11$ at
+  $t \sim 13000 \tau$.
+  In other simulations with identical parameters,
+  we sometimes observed no hops or two hops between minima,
+  as expected with random fluctuating systems.
+  In  Fig.~\ref{fig:brownian}(c)
+  $T/A_p = 6.0$ 
+  we observe approximately 15 hops,
+  indicating the random thermalized kicks are
+  sufficiently large to make the particle perform
+  a random walk of hops a top the substrate
+  in addition to the small scale random walk executed
+  by all particles in this section.
 

### 2021-01-31 manuscript/manuscript_ajp_2020.tex
fixed some Brownian commentary and equations

@@
   the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
-  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.
-[{\it I believe the slight slope in this curve is due to sampling - where does the particle start/end ?}]}
+  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$. }
 \label{fig:1}
@@
   phenomena in which 
-  particles change direction %randomly
-  due to collisions with fluid particles.
+  visible particles change direction,
+  apparently at random, 
+  due to collisions with invisible fluid particles.
   The frequency of collisions depends on the properties of
   the suspending fluid.
-  These collisions are more likely at higher temperature
-  due to the increased kinetic energy of the fluid particles,
+  At higher temperatures
+  the increased kinetic energy of particles
+  makes collisions more likely, 
   as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.
@@
   In molecular dynamics simulations temperature effects
-  can be modeled by including randomized forces $f^T$
+  can be modeled with randomized forces $f^T$
   to emulate the motion of particles undergoing Brownian motion.
-  A distribution of random forces contributes equally in all
+  A random distribution of forces
+  causes motion
+  equally in all
   directions such that the force averaged over a finite time interval
-  is zero $\langle f^T(t) \rangle = 0$.
+  is zero
+  \begin{equation}
+    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0
+  \end{equation}
+  where $n$ is an integer indicating
+  discrete simulation timesteps
+  such that $t = N \Delta t$.
   Random distributions are not correlated 
   over the independent variable,
-  where we take our independent variable to be time 
-  $\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)$
-  for a system with 
-  energy $k_B T$
+  for the independent variable to be time
+  \begin{equation}
+  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
+  \end{equation}
+  for times $t$ and $\tau$,
+  where $\delta(t-\tau)$ is the Dirac-delta function.
+  Here the scaling factor energy of 
+  $k_B T$ is
   derived from the Boltzmann constant $k_B$
@@
 
-  La la la...
+  A range of interesting behaviors
+  can be explored by varying the
+  relative strength of the confining landscape
+  and external driving force.
 

### 2021-01-31 manuscript/manuscript_ajp_2020.tex
starting parameter problem

@@
 such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
+We note the individual steps
+are not strictly horizontal 
+since particles move continuously
+through the landscape, so changes in $F^{dc}$
+will create linear changes in 
+net particle displacement that are observable
+within a single step.
+
 %$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
@@
   and external driving force.
+  For the single driven particle,
+  the hopping patterns are typically characterized
+  by $n_f$ the number of steps forward
+  versus $n_b$ the number of steps backward within a single
+  time period,
+  for a total displacement of $n_f - n_b$ integer steps of $\lambda$
+  In Fig.~\ref{fig:0},
+  the particle moves forward through two minima, i.e. $n_f = 2$,
+  and does not move backward a full minima - $n_b = 0$,
+  in a single period, such that the pattern
+  is characterized as $2(2,0)$.
+  In experiments with single particles \cite{Juniper2015}, 
+  hopping patterns of $n_f = 0 - 6$ for $n_b = 0$,
+  $n_f = 0 - 5$ for $n_b = -1$,
+  and
+  $n_f = 2 - 3$ for $n_b = -2$
+  were realized 
+  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+
+  In order to achieve
+  backwards hops,
+  a particle must have a high ratio of $F^{ac}/F^{dc}$.
+
+  Additionally the frequency must be low so that
+  the high force portions of the cycle last
+  long enough to move a particle over substrate extrema.
 
@@
 Our simulations reproduce results presented in 
-Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
+Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
 which demonstrated
@@
 Commun.
-6, 7187 (2015).
-
-    \bibitem{Juniper2018} Juniper, M.
+6, 7187 (2015);
+    %\bibitem{Juniper2018}
+      Juniper, M.
 P.

### 2021-02-03 code/MD_colloid.py
varied freq. and F_AC to examine hopping patterns

@@ -160,7 +160,7 @@ def md_step(y, int_time, F_DC, avg_vy, parameters, ft=0):
 
 #####################################################################
 def plot_position_vs_time(ax2,time_data,y_data,p):
-    '''Make Fig. 2 in AJP
+    '''Brownian figure, Fig. 5
     '''
 
     #for plot
@@ -180,6 +180,7 @@ def plot_position_vs_time(ax2,time_data,y_data,p):
     #ax2.text(0.9,0.84,"(b)",transform = ax2.transAxes,backgroundcolor="white",zorder=-10)
     
     #add horizontal lines for potential minima
+
     '''
     for i in [1,3,5,7]:
         ax2.axhline(y=i, color = "black", linestyle = "--")
@@ -228,17 +229,21 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
 
     ax1.set_xlim(0,time_data[-1]+1)
     ax2.set_xlim(0,time_data[-1]+1)
-    ax2.set_ylim(-0.1,y_data[-1]/period+0.2)
+    #ax2.set_ylim(-0.1,y_data[-1]/period+0.2)
 
-    ax1.text(0.9,0.85,"(a)",transform = ax1.transAxes,backgroundcolor="white")
-    ax2.text(0.9,0.84,"(b)",transform = ax2.transAxes,backgroundcolor="white",zorder=-10)
+    ax1.text(0.9,0.86,"(a)",transform = ax1.transAxes,backgroundcolor="white")
+    ax2.text(0.9,0.06,"(b)",transform = ax2.transAxes,backgroundcolor="white")
+
+    ax2.set_ylim(0.0,8.501)
+    ax2.set_yticks([1,3,5,7])
     
     #add horizontal lines for potential minima
-    for i in [1,3,5,7]:
+    #'''
+    for i in range(1,10)[::2]:
         #ax2.hline(i)
         #, label = "U(y) = -U$_0$")
         ax2.axhline(y=i, color = "black", linestyle = "--")
-
+    #'''
     for i in [1,5,9,13]:
         #peaks of the FD curve
         ax2.axvline(x=i/(4*freq), color = "black", linestyle = "--") 
@@ -372,10 +377,17 @@ def single_particle(parameters,plot="y-position"):
         plot_force_position_vs_time(time_data,FDC_data,y_data,parameters)
         return
     
+    elif plot == "just_position":
[…]

### 2021-02-03 code/MD_colloid.py
added grid to count minima

@@ -15,6 +15,9 @@ import math, sys
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
 #set default font of plot
 plt.rc('font', size=24)
 
@@ -591,7 +594,7 @@ if __name__ == "__main__":
         for i in range(n_plots):
 
             ax = fig.add_subplot(gs[i,0])
-            ax.text(0.02,0.8,letter[i]+str_iv%(ind_var[i]),transform = ax.transAxes,backgroundcolor="white",zorder=-10)
+            ax.text(0.02,0.8,letter[i]+str_iv%(ind_var[i]),transform = ax.transAxes,backgroundcolor="white")
                         
             parameters['axis'] = ax
 
@@ -599,6 +602,17 @@ if __name__ == "__main__":
                 parameters['freq'] = frequency[i]
             else:
                 parameters['F_AC'] = F_AC[i]
+                '''
+                if i == 1:
+                    for j in [6,12,18]:
+                        ax.axhline(y=j, color="black", linestyle = "--")
+                elif i == 2:
+                    for j in [5,10,15]:
+                        ax.axhline(y=j, color="black", linestyle = "--")                  '''
+                #horizontal grid
+                ax.set_ylim(0,20)
+                ax.yaxis.set_minor_locator(AutoMinorLocator(5))
+                ax.grid(axis='y',which='both')
                 
             single_particle(parameters,plot="just_position")
 

### 2021-02-03 manuscript/manuscript_ajp_2020.tex
added parameters figs

--- 2021-01-31 manuscript/manuscript_ajp_2020.tex
@@
 The horizontal dashed lines
-coincide with %the condition the is
-minimum substrate force  $F^l = -A_p$,  
+coincide with the condition the particle is at a substrate minima
+where substrate force  $F^l = -A_p$,  
 i.e. $\sin{(\pi y / \lambda)} = 1$.
@@
 force is minimum,
-as indicated with %the coincidence of 
+as indicated %with the coincidence of 
 with the intersection of
-horizontal and vertical lines
-and the particle position $y$.
+vertical and horizontal lines.  
+%i.e. the particle position $y/\lambda$.  
 The slope of $y/\lambda$
@@
   the momentum relaxation time is 
-  $m/\gamma = 0.5 ~\mu$s.
+  $m/\gamma \approx 0.5 ~\mu$s.
 
@@
   and reproduce the motions shown in Fig.~\ref{fig:0}(b).
-  This is due to the linear nature of the solution,
-  and the lack of interaction with neighboring particles.
+  This is due to the linear nature of the solution
+  for an isolated particle.
   Apply the Euler method to our equation
@@
   %becomes large?
-
-  {\it small timesteps matter a great deal when particle interactions
-    are included in the model.  I have demonstrated that
-    without particle interactions we can increase the timestep
-  with no penalty, so this isn't a very interesting problem.}
-
+  [UPDATE]
+  Demonstrate the timestep
+  of a single particle can be made large
+  with no change to the overall physics.
+  You will need to modify the maximum
+  simulation time, and the frequency of data saved for plotting purposes.
+
+  Interaction with neighboring particles
+  makes a small timestep essential for molecular dynamics simulations.
+  Since particle-particle interactions are typically non-linear,
+  the interaction force changes significantly over small distances,
+  making this simulation a unique
+  exception to typical simulation timesteps.
+  %{\it small timesteps matter a great deal when particle interactions
+  %  are included in the model.  I have demonstrated that
+  %  without particle interactions we can increase the timestep
+  %with no penalty, so this isn't a very interesting problem.}
   %FOLLOW UP WITH THIS!
@@
   In Fig.~\ref{fig:brownian}
-  we show the position versus time of a simple particle
+  we show the position versus time of a particle
   confined to a sinusoidal landscape
@@
   Confirm this result for $A_p = 0$.
+  %[INSERT advice on length of time to run?]
   Measure the RMSD as a function of time
-  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$.
+  of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
+  as shown in Fig.~\ref{fig:brownian}.
   Compare your result to the
   substrate free RMSD.
+  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]
 
@@
   With driving force reproduce the paper figures...
+  %%[there is no way I want to run this with python...]
 
@@
 
-  A range of interesting behaviors
+  A range of oscillation behaviors
   can be explored by varying the
@@
   and external driving force.
+  For the single driven particle,
+  the hopping patterns are typically characterized
+  by $n_f$ the number of steps forward
+  versus $n_b$ the number of steps backward within a single
+  time period.
+  The total displacement of $n_f - n_b$ integer steps of
+  the substrate period $\lambda$ characterize
+  the net hop length.  
+  In Fig.~\ref{fig:0},
+  in a single period 
+  the particle moves forward through two minima, i.e. $n_f = 2$,
+  and does not move backward a full minima ($n_b = 0$).  
+  %such that the pattern
+  %is characterized as $2(2,0)$.
+  In order to achieve
+  backwards hops,
+  a particle must have a ratio of $F^{ac}/F^{dc} > 1$,
+  and a difference $|F^{ac} - F^{dc}| > A_p$.
+  %which can also produce large forward hops.
+  %INSERT figure with a range of hopping patterns for a run
+  The frequency must be sufficiently low so that
+  the time interval in which the applied force is large
+  is sustained so that a particle will
+  traverse a substrate extrema.
+  Experiments with single colloids \cite{Juniper2015} 
+  show 
+  hopping patterns with backward steps are more difficult
+  to achieve than forward,
+  with $n_f = 0$ to $6$ for $n_b = 0$,
+  $n_f = 0$ to $5$ for $n_b = -1$,
+  and
+  $n_f = 2$ to $3$ for $n_b = -2$
+  were realized 
+  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+
+  In Fig.~\ref{fig:hops}
+  we show the results for lowering the frequency
+  of the system for our original parameters.
+  For the parameters
+  $F^{dc}=0.1$, $F^{ac}=0.05$, and $a_p = 0.1$,
+  $n_b = 0$
+  across a broad range of frequencies,
+  and $n_f$ increases as frequency decreases.
+  Low frequencies
+  result in sustained positive or negative motion of a particle,
+  where in Fig.~\ref{fig:hops}(e)
+  the particle reaches the top edge of the system
+  and wraps back to $y=0$.
+
+  In Fig.~\ref{fig:hops_back}
+  we show the results for increasing $F^{ac}$
+  of the system for our original parameters.
+  Here $n_b$ increases from $n_b = 0$ in (a) to
+
+  \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
+      \caption{
+        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.    
+      }
+      \label{fig:hops}
+    \end{figure}
+  \end{center}
+  %In Fig.~\ref{fig:hops}
+
+  \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
+      \caption{
+        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
+        (a) The particle moves forward six minima with no steps backward.
+        (b) The particle moves forward eight minima with two steps backward.
+        (c) The particle moves forward nine minima with four steps backward.
+      }
+      \label{fig:hops_back}
+    \end{figure}
+  \end{center}
+  %In Fig.~\ref{fig:hops}
 
@@
  %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
-
   %\item
+
   \subsection{Visualizing motion + phase plots}
@@
 in a potential well is 
-much like a skateboarder in a half-pipe or
+like a skateboarder in a half-pipe or
 a child on a swing.
-If subject to an applied force,
-a confined oscillator may 
+%If subject to an applied force,
+A confined oscillator may 
 synchronize its location
@@
 the beat. 
+The relationship between the driving force and
+landscape can change the pattern of motion.  
+With a constant or 
+dc drive the landscape modulates 
+the particle velocity, below some threshold  
+the dc force is not strong enough to push the particle
+across a potential maximum so the average velocity is zero,
+a phenomena referred to as pinning \cite{Reichhardt2017}.
+Above the pinning threshold,
+a particle subject to a constant
+drive force will increase its speed at a rate propotional
+to the external drive.  
+%and dissipating energy from the system at all driving forces.
+A sinusoidal or ac drive can create mode-locking,
+where the average particle velocity
+is fixed for a range of dc drive forces \cite{Reichhardt2015}.
+This synchronization phenomena
+is useful for understanding the complex dynamical 
+systems.
+
 %Fundamental models
@@
 that arise due to the interplay
-between a particles environment and external forces.
+between environmental and external forces.
 %due to interactions between particles.
-The relationship between the driving force and
-landscape can change the pattern of motion.  
-With a constant or 
-dc drive the landscape modulates 
-the particle velocity, below some threshold  
-the dc force is not strong enough to push the particle
-across a potential maximum so the average velocity is zero,
-a phenomena referred to as pinning \cite{Reichhardt2017}.  
-%and dissipating energy from the system at all driving forces.
-A sinusoidal or ac drive creates mode-locking,
-where the average particle velocity
-is fixed for a range of dc drive forces \cite{Reichhardt2015}.
-
 Our simulations reproduce results presented in 
-Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
-which demonstrated
+Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
+which demonstrate 
 mode locking in
@@
 driven colloids on a
-optical periodic landscape.
+periodic optical landscape.
 Due to the relative ease of
@@
 colloids are used as experimental models
-for systems relatively hard to access and visualize. 
-Collections of colloids can
-be used to study the properties of solids and liquids
-%comprised of smaller particles
-%such as atoms \cite{} or electrons \cite{}
-or more exotic systems 
+for systems %relatively
+hard to access and visualize 
 such as cold atoms or electron gases \cite{Grier2003}.
+%Collections of colloids can
+%be used to study the properties of solids and liquids
+%or more exotic systems 
 %Oscillators ordered into chains or lattices.
@@
 devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
-A single junction contains 
-two superconductoring layers which sandwich an insulating layer.
-When subject to an external voltage,
-Cooper pairs in the superconducting materials
-tunnel through the insulating layer.
+%A single junction contains 
+%two superconductoring layers which sandwich an insulating layer.
+%When subject to an external voltage,
+%Cooper pairs in the superconducting materials
+%tunnel through the insulating layer.
 Phase-locking is observed as 
-%phase-locked current loops \cite{} 
 stepped regions in current-voltage (I-V) relationship in these devices,
@@
 and current is that of particle velocity.
-%where a constant current results from a range of voltages
-%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
-%instead of ohmic relationships.
 Known as Shapiro steps, % \cite{},
@@
 coupled arrays of junctions \cite{Benz1990}.
-%either in 
-%velocity-force curves and voltage-current curves \cite{Golubov2004}.
 Shapiro steps vary in width depending on the strength of the
@@
 Thus the study of
-mode-locking is a useful problem
+mode-locking is a useful probe 
 of complex quantum mechanical systems.

### 2021-02-03 manuscript/manuscript_ajp_2020.tex
added comment to Brownian motion

@@
         (c) $T/A_p = 6.0$ many hops occur.
-        Note the scale of the $y-$axis differs in each panel.
+        Note the scale of the $y-$axis differs in each panel
+        and the time scale on the $x-$axis is
+        much greater than the period in Fig.~\ref{fig:1}.
       }
@@
   by all particles in this section.
+  At these temperatures the rate
+  of hopping is much less than the
+  frequency of the applied drive and synchronized motion,
+  so the effects of temperature are may ignored
+  in these simulations.
 
@@
   Here $n_b$ increases from $n_b = 0$ in (a) to
+  $n_b = 2$ in (b) to $n_b = 4$ in (c).
 

### 2021-02-04 code/MD_colloid.py
made figures neater and more compact

@@ -531,17 +531,17 @@ if __name__ == "__main__":
 
     parameters = set_parameters()
 
+    #select which figure in the AJP you would like to make
     make_fig2 = False #True #False #True 
     make_fig3 = False #True
-    make_brownian = False #True
+    make_fig4 = False #True
     make_fig5 = False #True
-    make_fig6 = True #False #True
+    make_fig6 =  True #False #True
 
     letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
 
-            
     #--------------------------------------------------------------
-    #make Fig. 2 - run a single particle at a single driving force
+    #run a single particle at a single driving force
     #--------------------------------------------------------------
     if make_fig2:
         
@@ -556,104 +556,9 @@ if __name__ == "__main__":
         single_particle(parameters)
 
 
-    if make_fig5 or make_fig6:
-        
-        parameters['dt'] = 0.1 #timestep in simulation units
-        parameters['maxtime']=3000        #total time steps in simulation
-        parameters['writemovietime']=1   #interval to write data to arrays for plotting
-        parameters['decifactor']=1   #interval to write data to arrays for plotting
-
-        if make_fig5:
-            parameters['filename']="parameters_fig5.pdf"
-            frequency = [0.1, 0.05, 0.01, 0.005, 0.001]
-
-            ind_var = frequency
-            str_iv=" f=%1.3f"
-
-        else:
-            frequency = [0.01]
-            F_AC = [0.2, 0.3, 0.4]
-
-            ind_var = F_AC
-            str_iv=" $F^{ac}$=%1.2f"
-            
-            parameters['filename']="parameters_fig6.pdf"
-            parameters['freq'] = frequency[0]
-
-            #parameters['F0'] = 0.05              
-            #parameters['F_DC_max'] = 0.05        #"constant" driving force for most of simulation
-
-            
-        n_plots = len(ind_var)
-        
-        fig = plt.figure(figsize=(10,3*n_plots))
-
-        gs=gridspec.GridSpec(n_plots,1)
-        
-        #run a single MD simulation for a set of parameters
-        for i in range(n_plots):
-
-            ax = fig.add_subplot(gs[i,0])
-            ax.text(0.02,0.8,letter[i]+str_iv%(ind_var[i]),transform = ax.transAxes,backgroundcolor="white")
-                        
-            parameters['axis'] = ax
-
-            if make_fig5:
-                parameters['freq'] = frequency[i]
-            else:
[…]

### 2021-02-04 manuscript/manuscript_ajp_2020.tex
updated figures and text

--- 2021-02-03 manuscript/manuscript_ajp_2020.tex
@@
 
-  Using reasonable values for the
+  {\bf Using reasonable values for the
   experimental analog of this system, 
-  demonstrate the Reynolds number is low.
+  show that the Reynolds number is small.}
   In addition to the values listed in Table ~\ref{tab:1}, 
@@
   %of $1.6 ~\mu$s.
-  Confirm for the values listed in Table ~\ref{tab:1},
+  {\bf Confirm for the values listed in Table ~\ref{tab:1},
   the momentum relaxation time is 
-  $m/\gamma \approx 0.5 ~\mu$s.
+  $m/\gamma \approx 0.5 ~\mu$s. }
 
@@
   a small momentum relaxation time, 
-  demonstrate that a particle confined to a landscape exerting force
+  {\bf show that a particle confined to a landscape exerting force
   $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
   can be modeled with the equation of motion described in 
-  Eq.~\ref{eq:motion}.
+  Eq.~\ref{eq:motion}. }
 
@@
     as demonstrated in Ex.~\ref{ex:n2l}.  
-
   When solving ordinary differential equations,
@@
   $y_{n+1} = y_n + f(t_n,y_n)$.
+    {\bf Apply the Euler method to our equation
+  of motion to solve for the analytic expression
+  of position of a particle
+  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).}
+
   The Euler method can be applied to non-linear
@@
   for an isolated particle.
-  Apply the Euler method to our equation
-  of motion to solve for the analytic expression
-  of position of a particle
-  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
   %How to the motions of the particle compare when the timestep
   %becomes large?
-  [UPDATE]
-  Demonstrate the timestep
-  of a single particle can be made large
-  with no change to the overall physics.
+  %[UPDATE]
+  {\bf Demonstrate the simulation timestep 
+  can be large
+  with no change to the overall physics
+  in the motion of a single particle.}
   You will need to modify the maximum
@@
   are solved with higher order methods
-  such as the Verlet method or Runge-Kutta methods.
+  such as the Verlet or Runge-Kutta methods.
   These methods include  higher order terms
@@
   to the net force on a single particle.
-
   In our model 
@@
   $a = dv/dt = 0$,
-  and thus rearrange $f_2(y,t)$ to solve directly for $v$,
+  %and thus rearrange $f_2(y,t)$ to solve directly for $v$,
   as described in Ex.~\ref{ex:n2l}.
-  The Taylor expansion of the position function $y(t)$
-  \begin{equation}
-    y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
+  %The Taylor expansion of the position function $y(t)$
+  %\begin{equation}
+  %  y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
     %\pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
-  \end{equation}
-  is exact at first order
-  for the $n$-th time step.
-
-  Demonstrate how the Verlet method
-  simplifies to the Euler method when
-  the particle acceleration $a=0$.
-
+  %\end{equation}
+  %is exact at first order
+  %for the $n$-th time step.
+  %Demonstrate how the Verlet method
+  %simplifies to the Euler method when
+  %the particle acceleration $a=0$.
   %We invite interested students to repeat this
@@
   %but is a direct consequence of the simplicity of the model.
-
 %\item
@@
   \label{ex:brownian}
-  Brownian motion 
-  is a temperature and viscosity dependent
-  phenomena in which 
+  Brownian motion is a phenomena in which 
   visible particles change direction,
@@
   due to collisions with invisible fluid particles.
-  The frequency of collisions depends on the properties of
+  The rate of collisions depends on the temperature, viscosity
+  amd density of 
   the suspending fluid.
@@
   %making up the suspending fluid.
-  In molecular dynamics simulations temperature effects
-  can be modeled with randomized forces $f^T$
-  to emulate the motion of particles undergoing Brownian motion.
-  A random distribution of forces
-  causes motion
+  In molecular dynamics simulations
+  it is common to treat the 
+  invisible fluid particles as a continuous substance
+  to reduce computational expense.
+  Temperature effects
+  can be modeled by applying randomized forces $f^T$
+  to the visible particles.
+  %\footnote{%In our simulations %np.random.normal
+  We use the normal distristribution from the NumPy random module
+  to generate a series of $f^T_n$ values for
+  each integer timestep $n$ \cite{numpy}.
+  A normalized random distribution of forces
+  causes fluctuations in %particles to emulate Brownian
+  motion 
   equally in all
-  directions such that the force averaged over a finite time interval
-  is zero
+  directions such that the force $f^T$
+  averaged over a finite time interval
+  is zero.  In one dimension this is expressed as 
   \begin{equation}
@@
   \end{equation}
-  where $n$ is an integer indicating
-  discrete simulation timesteps
+  %where $n$ is an integer indicating
+  %discrete simulation timesteps
   such that $t = N \Delta t$.
-  Random distributions are not correlated 
+  Random normal distributions are not correlated 
   over the independent variable,
@@
   A particle
-  with energy $k_b T_{min} > U_0$ may 
+  with sufficient energy $k_b T_{min}$ may 
   hop over landscape
   barriers.
-
   % (a) 
-  In simulation we define our temperature parameter to
+  In our simulations,
+  we define temperature as 
   $k_b T/E_0 \rightarrow T$
-  since we set the constants to unity.
-  In these units we can compare 
-  simulation temperature directly
-  to force 
-  in order to estimate the degree of random fluctuation.
-  For instance, 
-  with
-  no applied driving force,
+  with constants set to unity
+  to
+  %In these units
+  compare directly with force. 
+  %in order to estimate the degree of random fluctuation.
+
+  {\bf With no applied driving force,
+    find 
   the minimum temperature required for a single particle
-  to hop between minima in the potential landscape is
-  $T_{min} > A_p$.
-  Assuming a particle is confined to
+  to hop over maxima in the potential landscape.}
+  %$T_{min} > A_p$.
+  Assume the particle is confined to
   move along the $y-$direction,
   include Brownian motion 
-  in the model,
-  we find the crossover
-  to a hopping regime at $T/A_p \approx 5.6$.
-  %when
-  We demonstrate this hopping
-  pattern in 
+  in the model.
+  In Fig.~\ref{fig:brownian},
+  we demonstrate the transition
+  from pinned to hopping
+  in 
   %Measure the position vs. time
   a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
-  %and note  a particle will hop a barrier
-  %for sufficiently high $T/A_p$ ratios.
-  Reproduce these results.
-
+  The crossover
+  to a hopping regime occurs at $T/A_p \approx 5.6$.
+  %Reproduce these results.  
   \begin{center}
@@
         (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
+        across a distance of $\Delta y = 2 \lambda$.
         (c) $T/A_p = 6.0$ many hops occur.
-        Note the scale of the $y-$axis differs in each panel.
+        Note the scale of the $y-$axis differs in each panel
+        and the time scale is
+        much greater than in Fig.~\ref{fig:1}.
       }
@@
   In  Fig.~\ref{fig:brownian}(a)
-  $T/A_p = 4.0$ and the particle executes a 
+  the temperature is $T/A_p = 4.0$.
+  The particle executes a 
   random walk centered at the potential minima $y/\lambda = 10$.
-  We ran many simulations and never observed a hop to another minima.
+  We ran many simulations and never observed a hop to another minima
+  within this simulation time.  
   In  Fig.~\ref{fig:brownian}(b)
@@
   a single hop occurs from
-  $y/\lambda = 10$ to $y/\lambda = 11$ at
-  $t \sim 13000 \tau$.
+  $y/\lambda = 10$ to $y/\lambda = 12$ at
+  $t \sim 40000 \tau$ and 
+  $y/\lambda = 10$ to $y/\lambda = 8$ at
+  $t \sim 280000 \tau$.
   In other simulations with identical parameters,
@@
   $T/A_p = 6.0$ 
-  we observe approximately 15 hops,
-  indicating the random thermalized kicks are
+  we observe many hops.
+  The random thermalized kicks are
   sufficiently large to make the particle perform
-  a random walk of hops a top the substrate
-  in addition to the small scale random walk executed
-  by all particles in this section.
-
-  A quantity of interest
-  for a particle undergoing Brownian motion
-  is the rate of displacement
-  of the particle from its initial position 
-  This is measured as mean square displacement
-  as a function of time
-  \begin{equation}
-    \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
-  \end{equation}
-  where $t_0$ is the initial time at
-  initial position $\vec{r}(t_0)$.
-  With no substrate, we would expect
-  the root mean square displacement (RMSD)
-  to be proportional to the elapsed time 
-  \begin{equation}
-    \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
-  \end{equation}
-  Confirm this result for $A_p = 0$.
-  %[INSERT advice on length of time to run?]
-  Measure the RMSD as a function of time
-  of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
-  as shown in Fig.~\ref{fig:brownian}.
-  Compare your result to the
-  substrate free RMSD.
+  what appears to be 
+  a random walk of hops atop the substrate.
+  %in addition to the small scale random walk executed
+  %by all particles in this section.
+
+  %A quantity of interest
+  %for a particle undergoing Brownian motion
+  %is the rate of displacement
+  %of the particle from its initial position 
+  %This is measured as mean square displacement
+  %as a function of time
+  %\begin{equation}
+  %  \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
+  %\end{equation}
+  %where $t_0$ is the initial time at
+  %initial position $\vec{r}(t_0)$.
+  %With no substrate, we would expect
+  %the root mean square displacement (RMSD)
+  %to be proportional to the elapsed time 
+  %\begin{equation}
+  %  \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
+  %\end{equation}
+  %Confirm this result for $A_p = 0$.
+  %%[INSERT advice on length of time to run?]
+  %Measure the RMSD as a function of time
+  %of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
+  %as shown in Fig.~\ref{fig:brownian}.
+  %Compare your result to the
+  %substrate free RMSD.
   %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]
@@
   %(b)
-  How does Brownian motion affect
-  the formation of Shapiro steps?
-  With driving force reproduce the paper figures...
+  For a driven particle,
+  we ignore 
+  the effects of temperature 
+  in these simulations.  
+  We note that even at $T/A_p = 6.0$ 
+  the hopping rate
+  is much less than the
+  frequency of the applied drive.
+  This can be seen in the time scale in Fig.~\ref{fig:brownian},
+  where the average hopping rate is approximately
+  every $15000\tau$,
+  a value much larger than $T = 100\tau$.
+  At sufficiently high temperatures,
+  Brownian motion does affect 
+  the formation of Shapiro steps
+  and can be observed in experiments.
+  %and could be included
+  %to emulate noise seen in some 
+  %How does Brownian motion affect
+  %With driving force reproduce the paper figures...
   %%[there is no way I want to run this with python...]
@@
   time period.
-  The total displacement of $n_f - n_b$ integer steps of
-  the substrate period $\lambda$ characterize
-  the net hop length.  
+  The total displacement of $(n_f - n_b) \lambda$ %integer steps of
+  is the net hop length.  
+  %the substrate period $$ characterize
   In Fig.~\ref{fig:0},
-  in a single period 
-  the particle moves forward through two minima, i.e. $n_f = 2$,
+  the particle moves forward through two minima ($n_f = 2$),
   and does not move backward a full minima ($n_b = 0$).  
@@
   backwards hops,
-  a particle must have a ratio of $F^{ac}/F^{dc} > 1$,
+  the driving parameters must have
+  a ratio of $F^{ac}/F^{dc} > 1$ 
   and a difference $|F^{ac} - F^{dc}| > A_p$.
@@
   The frequency must be sufficiently low so that 
-  the time interval in which the applied force is large
-  is sustained so that a particle will
-  traverse a substrate extrema.
+  the applied force is large
+  over a sustained time interval,
+  allowing a particle to hop a substrate maxima.
   Experiments with single colloids \cite{Juniper2015} 
@@
   for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+  {\bf Find the parameters
+  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
 
   In Fig.~\ref{fig:hops}
-  we show the results for lowering the frequency
-  of the system for our original parameters.
-  For the parameters
-  $F^{dc}=0.1$, $F^{ac}=0.05$, and $a_p = 0.1$,
-  $n_b = 0$
-  across a broad range of frequencies,
-  and $n_f$ increases as frequency decreases.
+  we show the effects of lowering the frequency
+  of applied driving force,
+  holding the remaining parameters fixed 
+  to 
+  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
+  We observe no backward steps 
+  ($n_b = 0$) 
+  across a broad range of frequencies.
+  The number of forward steps 
+  $n_f$ increases as frequency decreases.
   Low frequencies
@@
   and wraps back to $y=0$.
-
-  In Fig.~\ref{fig:hops_back}
-  we show the results for increasing $F^{ac}$
-  of the system for our original parameters.
-  Here $n_b$ increases from $n_b = 0$ in (a) to
-
   \begin{center}
@@
         Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.
+        In (e) the particle wraps the periodic boundary conditions.
       }
@@
 
+  In Fig.~\ref{fig:hops_back}
+  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
+  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
+  %of the system for our original parameters.
+  Here $n_b$ increases from $n_b = 0$ in (a) to
+  $n_b = 2$ in (b) to $n_b = 4$ in (c).  
   \begin{center}
@@
 
+  Shapiro steps
 %\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
@@
 
+    \bibitem{numpy} Harris, C.R., Millman, K.J., van der Walt, S.J. et al. Array programming with NumPy. Nature {\bf 585}, 357 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
+
 %\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

### 2021-02-05 code/MD_colloid.py
made new Shapiro steps that include more backwards flow for low Fdc

@@ -537,6 +537,7 @@ if __name__ == "__main__":
     make_fig4 = False #True
     make_fig5 = False #True
     make_fig6 =  True #False #True
+    make_fig7 = True
 
     letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
 
@@ -559,17 +560,25 @@ if __name__ == "__main__":
     #--------------------------------------------------------------
     #make shapiro steps with a range of F^{dc}
     #--------------------------------------------------------------
-    if make_fig3: 
+    if make_fig3 or make_fig7: 
         #reset some parameters for subsequent figures
         #parameters['F_DC_incr'] = 0.01        #amount to increase FDC at every drop step
         #parameters['drop'] = 2000            #integer timesteps to "ramp" the DC force
         #parameters['decifactor'] = 2000      #integer timesteps to "ramp" the DC force
 
         parameters['maxtime']=100000          #shorter and I don't get steps
-        parameters['filename']="sweep_FDC_vs_vx.pdf"
-        
-        delta_Fdc = 0.001
-        Fdc_max=0.3+delta_Fdc
+        parameters['filename']="fig7_sweep_FDC_vs_vx.pdf"
+
+        if make_fig3:
+            delta_Fdc = 0.001
+            Fdc_max=0.3+delta_Fdc
+
+        elif make_fig7:
+            delta_Fdc = 0.01
+            parameters['drop'] = 10000    #integer timesteps to "ramp" the DC force
+            parameters['F_AC'] = 0.4
+            Fdc_max=0.6+delta_Fdc
+            
         max_value = int(np.ceil(Fdc_max/delta_Fdc))
         avg_vy_data = np.zeros(max_value)
         Fdc_data = np.arange(0,Fdc_max,delta_Fdc)

### 2021-02-09 manuscript/manuscript_ajp_2020.tex
editing introduction

@@
   Our results show a variety of synchronization effects 
-  in single and multi-particle systems, 
+  in single particle systems, 
   %and detect synchronization using
   %measurements of
-  which we characterize with
-  plots of 
-  particle velocity as a function of applied driving force,
+  which we characterize by 
+  plotting 
+  particle velocity as a function of applied driving force 
   and phase diagrams of position versus velocity.
@@
 Synchronization is a universal phenomena
-in which individual oscillators adjust frequency due
-to external stimulus \cite{Pikovsky2003}.
-Many everyday systems
-exhibit in-phase coupled oscillations %of components 
-such as the
+in which
+individual oscillators change frequency due
+to external stimuli \cite{Pikovsky2003}.
+The
 flickering patterns of
@@
 through sound waves \cite{Arane2009}, 
-and metronomes vibrating through a supporting platform \cite{Jia2015}.
+and metronomes vibrating through a supporting platform \cite{Jia2015}
+are examples of in-phase coupled oscillations. %of components 
 Biological systems benefit from cooperative
@@
 External forcing can cause or regulate 
-synchronization. % is often achieved via external forcing
+synchronization %. % is often achieved via external forcing
 %such as when
 %single particle oscillators
-For instance,
+-- %For instance,
 an electrical pacemaker %(an electrical generator)
-pulses to regulate a heart beat,
+regulates a heart beat 
 and 
-a flashing light can modify the
-pattern of flashing fireflies .% \cite{Agrawal2013}.
+a pulsed light modifies the
+flashing pattern of fireflies .% \cite{Agrawal2013}.
 
@@
 %[has been adapted into many useful technologies...]
-A particular form of 
-synchronization is phase-locking or mode-locking,
-which first appeared in the scientific literature
+Synchronized phase-locking or mode-locking 
+first appeared in the scientific literature
 with 
 Huygens' 1665 experiments on
-the 
-motions of two wall-mounted pendulum clocks.
-Huygens demonstrated the tendency of
-the pendula 
-to swing in time, 
-even when started out of phase,
+motions of 
+pendula in two wall-mounted clocks.
+Even when started out of phase, 
+%Huygens demonstrated the tendency of
+coupled pendula tend to swing in time
 due to interactions through the wall \cite{Bennett2002}.
 %phase locking
-Dynamical systems %with multiple frequencies
-exhibit phase-locking 
-when oscillators with different rhythms adjust %couple
-to a frequency ratio or mode 
-of an integer number \cite{Bak1986}.
+A locked-mode is an integer frequency ratio.
+In Huygens clocks, 
+the pendula were observed swing at same rate in a 1:1 mode.
+For simple pendula of different lengths,
+a 2:1 mode can be seen when a pendulum four
+times the length of the other swings with twice the period.
+%
+%to a mode or frequency ratio  
+%of an integer number \cite{Bak1986}.
 %Dynamical mode locking
@@
 Synchronization 
-is often studied with simple computational models
-and can be visualized 
+%is often studied with simple computational models and
+can be visualized 
 with phase
-plots or Lissajous figures.
-In phase space 
-a mode-locked system is confined to 
-a closed loop in a 
-parametric space showing the relationship between two periodic functions
-with patterns determined by the mode, % frequency ratio,
-first reported in 1857 \cite{Lissajous1857}
-and easily generated with a computer code 
-or oscilloscope \cite{Tong1997}. 
+plots or Lissajous figures, 
+first reported in 1857 \cite{Lissajous1857}.
+%and easily generated with a computer code 
+%or oscilloscope \cite{Tong1997}. 
+A mode-locked system is confined to 
+a closed loop in  
+parametric phase space % showing the relationship between two periodic functions
+with patterns determined by the mode. % frequency ratio,
+({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
 %with a frequency generator,
 %where two combined frequencies at perpendicular orientations
-%({\it As we will demonstrate in phase plots in Figs. X, Y, Z})
-It should be noted that the term phase
-has two scientific meanings, 
-``oscillation phase'' and ``phase space''
+Note the term phase
+has two scientific meanings:  
+%``oscillation phase'' and ``phase space.''
 %refer to different uses of the word ``phase.''
-Oscillation phase $\phi_0$ is the constant portion of the argument in a periodic function
-  $\sin{(\omega t + \phi_0)}$ while phase space refers
-  to plots of velocity versus position (such as $v_y$ vs. $y$)
-  that are used to characterize oscillating systems.
+oscillation phase $\phi_0$ is the constant of the argument
+in a periodic function
+$\sin{(\omega t + \phi_0)}$ and phase space is
+used to characterize oscillating systems with
+parametric plots of $v_y$ vs. $y$.
 
@@
 Complex dynamics can be studied with
-colloid particles with experiments and simulation.
-In typical experiments colloids are spheres of 
-plastic suspended in
-highly de-ionized water or silica in suspended in organic solvent.
+colloid particles in experiments or simulations.
+Typical colloids are   
+plastic spheres suspended in
+de-ionized water or silica beads suspended in organic solvent.
 %experimental - colloids specifically
 Because 
-the spheres are a few microns in size
-and move at rates of microns per second,
-the position of a particle %is large and slow enough to
-can be imaged as a function of time 
-with a traditional optical camera.
+colloids are large %-- a few microns in size
+and move slowly %-- a few microns per second,
+particle position 
+can be imaged in real time 
+with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
+Experimental measurements of 
+step-by-step dynamics of 
+colloids performing phase-locked motions
+are useful for
+understanding synchronization at a single particle level \cite{Juniper2015}.
+
 %due to the large size and slow speed of the particles.
-Individual colloids exhibit 
-Brownian motion,
-where particles change direction %in a seemingly random fashion
-due to 
-collisions 
-with unseen particles comprising the suspending fluid \cite{}.
+%Individual colloids exhibit 
+%Brownian motion,
+%where particles change direction %in a seemingly random fashion
+%due to 
+%collisions 
+%with unseen particles comprising the suspending fluid \cite{}.
 %[elaborate - move to associated problems?].
@@
 tool for manipulating the colloidal environment.
-A single laser beam can be used to create an optical trap,
-which uses 
-photon radiation pressure to
-control colloid motions \cite{Ashkin1997}.
-A circular optical trap is designed
-with a local energy minimum 
-at its center.
-A colloid in the beam center is subject to a
-uniform distribution of photon bombardment,
-and motions away from the center create a net force
-due to an uneven 
-distribution of photon collisions on its surface.
+A circular optical trap uses 
+radiation pressure from 
+a laser beam to confine colloids \cite{Ashkin1997}.
+%Since photon density is high at the beam center,
+A colloid centered in the beam is %subject to a
+uniformly bombarded by photons while 
+%form a circular pattern with a higher density 
+%central 
+%energy minimum.
+%optical trap  trap colloids
+%with radiation pressure  which uses  photon 
+%control colloid motions 
+%A  is designed
+off-center colloids %away from center
+collide with photons unevenly,
+creating a net force.
 %Colloids at a trap edge
@@
 location of the particle in the trap,
-the radiation pressure either restores colloids toward the local minima
+the radiation pressure either moves colloids toward the local minimum 
 or ejects it from the trap.
@@
 and has been studied in detail in Ref.~\cite{Volpe2013}.
-
 %In experiments
- Complex environments can be
- engineered with light by %, typically made 
- using diffraction gratings to create a patterned
- potential energy landscape 
- with one or more laser beams \cite{Grier2003}.
+Diffraction gratings can be used to create
+more complex light environments, 
+%with one or more laser beams,
+such as periodic patterns of minima
+suitable for synchronization studies \cite{Grier2003}.
+
+A single particle oscillator
+in a potential well is 
+like a skateboarder in a half-pipe or
+a child on a swing.
+%If subject to an applied force,
  How a particle moves
@@
  subject to external driving forces.
- Individual particles can
- perform 
- synchronized % with the environment
- motions
- that lock together particle location and velocity.
- Experimental studies of
- the microscopic dynamics 
- colloids performing phase-locked motions
- produce step-by-step diagrams
- of particle dynamics useful for
- understanding synchronization at a single particle level \cite{Juniper2015}.
+ %Individual particles can
+ %move with synchronized location and velocity
+ % with the environment
+ %motions
+ %that lock together particle .
+ A confined oscillator may 
+ synchronize its location
+ to the periodic pattern of the external drive,
+ moving back and forth in time with
+ the beat. 
+ %The relationship between the driving force and
+ %landscape can change the pattern of motion.  
+ With a constant or 
+ dc drive the landscape modulates 
+ the particle velocity, below some threshold  
+ the dc force is not strong enough to push the particle
+ across a potential maximum so the average velocity is zero,
+ a phenomena referred to as pinning \cite{Reichhardt2017}.
+ Above the pinning threshold,
+ a particle subject to a constant
+ drive force will increase its speed at a rate propotional
+ to the external drive.  
+ %and dissipating energy from the system at all driving forces.
+ A sinusoidal or ac drive can create mode-locking,
+ where the average particle velocity
+ is fixed for a range of dc drive forces \cite{Reichhardt2015}.
+ %This synchronization phenomena
+ %is useful for understanding the complex dynamical 
+ %systems.
 
@@
         (a) $T/A_p = 4.0$ no hopping occurs.
-        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
-        across a distance of $\Delta y = 2 \lambda$.
+        (b) $T/A_p = 5.0$ a three hops occur %at $t = 130000$
+        across distances of $\Delta y = 2 \lambda$.
         (c) $T/A_p = 6.0$ many hops occur.
@@
         and the time scale is
-        much greater than in Fig.~\ref{fig:1}.
+        much greater than in Fig.~\ref{fig:0}.
       }
@@
       \caption{
-        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.
+        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency as marked.
         In (e) the particle wraps the periodic boundary conditions.
@@
       \caption{
-        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
+        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
         (a) The particle moves forward six minima with no steps backward.
@@
 
-  Shapiro steps
+    \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
+      \caption{
+        Mode-locked steps in $\langle v_y \rangle$ vs.
+$F^{dc}$ of a particle with frequency $f=0.01$ and $F^{ac}=0.4$.
+At low values of $F^{dc}$ the particle may move backwards, distorting the steps.
+      }
+      \label{fig:shapiro}
+    \end{figure}
+  \end{center}
+  %In Fig.~\ref{fig:hops}
 %\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
@@
 \label{sec:conclusion}	% You can label sections for reference
-A single particle oscillator
-in a potential well is 
-like a skateboarder in a half-pipe or
-a child on a swing.
-%If subject to an applied force,
-A confined oscillator may 
-synchronize its location
-to the periodic pattern of the external drive,
-moving back and forth in time with
-the beat. 
-The relationship between the driving force and
-landscape can change the pattern of motion.  
-With a constant or 
-dc drive the landscape modulates 
-the particle velocity, below some threshold  
-the dc force is not strong enough to push the particle
-across a potential maximum so the average velocity is zero,
-a phenomena referred to as pinning \cite{Reichhardt2017}.
-Above the pinning threshold,
-a particle subject to a constant
-drive force will increase its speed at a rate propotional
-to the external drive.  
-%and dissipating energy from the system at all driving forces.
-A sinusoidal or ac drive can create mode-locking,
-where the average particle velocity
-is fixed for a range of dc drive forces \cite{Reichhardt2015}.
-This synchronization phenomena
-is useful for understanding the complex dynamical 
-systems.
 
@@
 %focus on
-We have used 
-a single particle driven across a periodic potential landscape 
+%We have driven 
+A single particle driven across a periodic potential landscape 
 %Single particle studies are useful
-to study synchronization dynamics
-that arise due to the interplay
-between environmental and external forces.
+synchronizes its motion %to study synchronization dynamics
+%that arise
+to environmental and external forces,
+a phenomena known as mode-locking.  
 %due to interactions between particles.
-Our simulations reproduce results presented in 
+Our simulations reproduce experiments presented in 
 Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
-which demonstrate 
+of 
 mode locking in
-experiments and simulations of 
+%experiments and simulations of 
 driven colloids on a
 periodic optical landscape.
-Due to the relative ease of
-manipulation and imagining, 
-colloids are used as experimental models
+Colloids are 
+relatively easy to 
+manipulate and image in experiments,
+making ideal proxies 
 for systems %relatively
-hard to access and visualize 
 such as cold atoms or electron gases \cite{Grier2003}.
+%which are 
+%hard to access and visualize 
 %Collections of colloids can
@@
 %technological applications
-Dynamical mode-locking, the primary synchronization
-effect explored in this paper, 
+Dynamical mode-locking %, the primary synchronization
+%effect explored in this paper, 
 is %often
@@
 in quantum electronic
-devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
+devices %, such as Josephson junctions \cite{Josephson1962,Josephson1965}, 
 %A single junction contains 
@@
 %tunnel through the insulating layer.
-Phase-locking is observed as 
-stepped regions in current-voltage (I-V) relationship in these devices,
+%Phase-locking is observed in these devices
+as 
+stepped regions in current-voltage (I-V) relationship,
 where voltage is the analog of external driving force
@@
 Known as Shapiro steps, % \cite{},
-these phase locked currents  
+these mode-locked or phase-locked currents  
 have been observed due to applied ac voltages in 
@@
 applied ac forces,
-and are observed in a variety of systems
+and are observed in a variety of ac and dc driven systems
 displaying
@@
 including
-ac and dc driven
-charge and spin density waves
+charge waves, spin density waves
 and superconducting vortices in landscapes 
 engineered with periodic patterns of pinning sites.
-Thus the study of
-mode-locking is a useful probe 
-of complex quantum mechanical systems.
+%Thus the study of
+Mode-locking is a useful probe 
+of complex quantum mechanical systems
+since the motions of individual particles can only be inferred
+from other measurements.
 Our results can be relevant 
@@
     \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
+
+      \bibitem{Pertsinidis2001} A.
+Pertsinidis, and X.
+Ling,  Equilibrium Configurations and Energetics of Point Defects in Two-Dimensional Colloidal Crystals.
+{\it Phys Rev Lett}, {\bf 87}, 098303 (2001).
+%https://doi.org/10.1103/PhysRevLett.87.098303
 
@@
 
-      quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
+      %quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
+
     \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).

### 2021-02-09 manuscript/manuscript_ajp_2020.tex
moved phase plots description from introduction to exercises

@@
 Huygens' 1665 experiments on
-motions of 
-pendula in two wall-mounted clocks.
-Even when started out of phase, 
+motions of synchronized 
+pendula in wall-mounted clocks \cite{Bennett2002}.
+%Even when started out of phase, 
 %Huygens demonstrated the tendency of
-coupled pendula tend to swing in time
-due to interactions through the wall \cite{Bennett2002}.
+%coupled pendula tend to swing in time
+%due to interactions through the wall 
 %phase locking
@@
 In Huygens clocks,
-the pendula were observed swing at same rate in a 1:1 mode.
+%even when started out of phase, 
+the pendula were observed swing at same rate -- a 1:1 mode.
 For simple pendula of different lengths,
 a 2:1 mode can be seen when a pendulum four
-times the length of the other swings with twice the period.
+times the length of another swings with twice the period.
 %
@@
 %The phenomena
-Synchronization 
-%is often studied with simple computational models and
-can be visualized 
-with phase
-plots or Lissajous figures, 
-first reported in 1857 \cite{Lissajous1857}.
-%and easily generated with a computer code 
-%or oscilloscope \cite{Tong1997}. 
-A mode-locked system is confined to 
-a closed loop in  
-parametric phase space % showing the relationship between two periodic functions
-with patterns determined by the mode. % frequency ratio,
-({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
-%with a frequency generator,
-%where two combined frequencies at perpendicular orientations
-Note the term phase
-has two scientific meanings:  
-%``oscillation phase'' and ``phase space.''
-%refer to different uses of the word ``phase.''
-oscillation phase $\phi_0$ is the constant of the argument
-in a periodic function
-$\sin{(\omega t + \phi_0)}$ and phase space is
-used to characterize oscillating systems with
-parametric plots of $v_y$ vs. $y$.
 
@@
 location of the particle in the trap,
-the radiation pressure either moves colloids toward the local minimum 
+the radiation pressure either moves colloids toward the beam center 
+%local minimum 
 or ejects it from the trap.
 An optically trapped colloid executing Brownian motion
-is a useful probe of microscopic forces,
-and has been studied in detail in Ref.~\cite{Volpe2013}.
+is a useful probe of microscopic forces ~\cite{Volpe2013}.
 %In experiments
@@
 In Section~\ref{sec:conclusion}
-we describe how our work with colloids applies more broadly
-to many physical systems
+we describe how our results apply 
+to physical systems
 such as dusty plasmas, superconducting vortices and Josephson junctions.
@@
 
-  \subsection{Visualizing motion + phase plots}
+\subsection{Phase plots}
+  \label{ex:phase}
+
+  Synchronization 
+  %is often studied with simple computational models and
+can be visualized 
+with phase
+plots or Lissajous figures, 
+first reported in 1857 \cite{Lissajous1857}.
+%and easily generated with a computer code 
+%or oscilloscope \cite{Tong1997}. 
+A mode-locked system is confined to 
+a closed loop in  
+parametric phase space % showing the relationship between two periodic functions
+with patterns determined by the mode. % frequency ratio,
+({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
+%with a frequency generator,
+%where two combined frequencies at perpendicular orientations
+Note the term phase
+has two scientific meanings:  
+%``oscillation phase'' and ``phase space.''
+%refer to different uses of the word ``phase.''
+oscillation phase $\phi_0$ is the constant of the argument
+in a periodic function
+$\sin{(\omega t + \phi_0)}$ and phase space is
+used to characterize oscillating systems with
+parametric plots of $v_y$ vs. $y$.
+
+  \subsection{Visualizing motion}
   \label{ex:animation}
@@
   Also the animation library in python...
-
-  Phase plots...
-
-%\end{enumerate}
 

### 2021-02-10 code/MD_colloid.py
changed the case/switch like set of T/F declarations to a much simpler make_fig = integer

@@ -532,19 +532,24 @@ if __name__ == "__main__":
     parameters = set_parameters()
 
     #select which figure in the AJP you would like to make
+    '''
     make_fig2 = False #True #False #True 
-    make_fig3 = False #True
+    make_fig3 = True #
     make_fig4 = False #True
     make_fig5 = False #True
-    make_fig6 =  True #False #True
-    make_fig7 = True
+    make_fig6 = False #True
+    make_fig7 = False #True
+    '''
+
+    #Coded to make figures 2 to 8
+    make_fig = 7
 
     letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
 
     #--------------------------------------------------------------
     #run a single particle at a single driving force
     #--------------------------------------------------------------
-    if make_fig2:
+    if make_fig == 2:
         
         parameters['dt'] = 0.1 #timestep in simulation units
         parameters['maxtime']=4000        #total time steps in simulation
@@ -556,28 +561,31 @@ if __name__ == "__main__":
         #run a single MD simulation for a set of parameters
         single_particle(parameters)
 
-
     #--------------------------------------------------------------
     #make shapiro steps with a range of F^{dc}
     #--------------------------------------------------------------
-    if make_fig3 or make_fig7: 
+    if make_fig == 3 or make_fig == 7: 
         #reset some parameters for subsequent figures
         #parameters['F_DC_incr'] = 0.01        #amount to increase FDC at every drop step
         #parameters['drop'] = 2000            #integer timesteps to "ramp" the DC force
         #parameters['decifactor'] = 2000      #integer timesteps to "ramp" the DC force
 
         parameters['maxtime']=100000          #shorter and I don't get steps
-        parameters['filename']="fig7_sweep_FDC_vs_vx.pdf"
 
-        if make_fig3:
+        
+        if make_fig == 3:
             delta_Fdc = 0.001
             Fdc_max=0.3+delta_Fdc
+            parameters['filename']="fig3_sweep_FDC_vs_vx.pdf"
 
-        elif make_fig7:
+        elif make_fig == 7:
             delta_Fdc = 0.01
             parameters['drop'] = 10000    #integer timesteps to "ramp" the DC force
+            parameters['decifactor'] = 10000      #integer timesteps to "ramp" the DC force
+
             parameters['F_AC'] = 0.4
             Fdc_max=0.6+delta_Fdc
+            parameters['filename']="fig7_sweep_FDC_vs_vx.pdf"
             
[…]

### 2021-02-10 manuscript/manuscript_ajp_2020.tex
started on phases - rabbit hole - do next move to beginning of exercises and then include as subpanel on other figures

@@
   a closed loop in  
-parametric phase space % showing the relationship between two periodic functions
+  parametric phase space % showing the relationship
+  %between two periodic functions
   with patterns determined by the mode. % frequency ratio,
-({\it As we will demonstrate in phase plots in Figs. X, Y, Z}).
   %with a frequency generator,
@@
   parametric plots of $v_y$ vs. $y$.
+
+  In driven systems,
+  the y-position is monotonically increasing.
+  We are most interested in the position of the particle
+  within the substrate period
+
+  \begin{equation}
+  (y mod \lambda) / \lambda
+  \end{equation}
+
+  %Juniper so-called ‘phase portraits’, in which the phase velocity, d\phi(t)/dt,is plotted against the phase, \phi(t) = 2\pi (x(t)-\bar{v}t)/\lambda (ref. 53). The
+  %REF 53
+
+  \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{phase.pdf}
+      \caption{
+        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.
+      }
+      \label{fig:phase}
+    \end{figure}
+  \end{center}
 

### 2021-02-11 code/MD_colloid.py
making nice-ish phase plots - check phi_dot

@@ -261,9 +261,38 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
 
 
 #####################################################################
-#def plot_velocity_force(time_data,FDC_data,vy_data,parameters):
-#    '''
-#    '''
+
+def plot_phase(ax,y_data,avg_vy_data,p):
+    '''Make Fig. 8 in AJP
+    '''
+
+    #for plot
+    #calculate the driving force from F_DC and time
+
+    #plot the position within the period
+    #y_data /= p['period']
+    vbar = np.average(avg_vy_data)
+    time = np.arange(1,4001,1)*p['dt']
+        
+    plot_delay = 100
+        
+    #no subtraction
+    
+    phi_y_data = 2*np.pi*(y_data - vbar*time)/(p['period'])
+    dot_phi_y_data = 2*np.pi*(phi_y_data - vbar)/(p['period'])
+
+    if 0:
+        ax.scatter(phi_y_data[plot_delay:],dot_phi_y_data[plot_delay:]) #,lw=5)
+    else:
+        ax.scatter(phi_y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
+
+    ax.set_xlabel(r"$\phi_y(t)$")
+    ax.set_ylabel(r"$\dot{\phi}_y(t)$")
+
+    #ax1.set_xticks([])
+    #ax1.set_xlim(0,time_data[-1]+1)
+    
+    return 
 
 #####################################################################
 def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC_data,p):
@@ -379,6 +408,10 @@ def single_particle(parameters,plot="y-position"):
     if plot == "y-position":
         plot_force_position_vs_time(time_data,FDC_data,y_data,parameters)
         return
+
+    elif plot == "phase":
+        #plot_phase(y_data,avg_vy_data,parameters)
+        return y_data, avg_vy_data
     
     elif plot == "just_position":
         plot_position_vs_time(parameters['axis'], time_data,y_data,parameters)
@@ -532,34 +565,52 @@ if __name__ == "__main__":
     parameters = set_parameters()
 
     #select which figure in the AJP you would like to make
-    '''
-    make_fig2 = False #True #False #True 
-    make_fig3 = True #
-    make_fig4 = False #True
-    make_fig5 = False #True
-    make_fig6 = False #True
-    make_fig7 = False #True
-    '''
-
[…]

### 2021-02-11 code/MD_colloid.py
made the right phase variables with nice plots

@@ -279,15 +279,16 @@ def plot_phase(ax,y_data,avg_vy_data,p):
     #no subtraction
     
     phi_y_data = 2*np.pi*(y_data - vbar*time)/(p['period'])
-    dot_phi_y_data = 2*np.pi*(phi_y_data - vbar)/(p['period'])
+    dot_phi_y_data = 2*np.pi*(avg_vy_data - vbar)/(p['period'])
 
-    if 0:
-        ax.scatter(phi_y_data[plot_delay:],dot_phi_y_data[plot_delay:]) #,lw=5)
+    if 1:
+        ax.scatter(phi_y_data[plot_delay:],dot_phi_y_data[plot_delay:],s=5) #,lw=5)
     else:
         ax.scatter(phi_y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
 
     ax.set_xlabel(r"$\phi_y(t)$")
     ax.set_ylabel(r"$\dot{\phi}_y(t)$")
+    ax.yaxis.set_label_coords(-0.22, 0.5)
 
     #ax1.set_xticks([])
     #ax1.set_xlim(0,time_data[-1]+1)
@@ -586,21 +587,25 @@ if __name__ == "__main__":
             single_particle(parameters)
         elif make_fig == 8:
 
-            parameters['F_AC'] = 0.05
+            parameters['F_AC'] = 0.2
             parameters['freq'] = 0.01
-            parameters['F0'] = 0.05
+            #parameters['F0'] = 0.05
 
-            fig = plt.figure(figsize=(12,12))
+            fig = plt.figure(figsize=(12,11))
             gs=gridspec.GridSpec(2,2)
 
             parameters['filename']="phase.pdf"
 
-            AC = [0.05,0.1,0.2,0.3]
+            F0 = [0.0,0.05,0.1,0.2]
             k=0
             for i in range(2):
                 for j in range(2):
                     ax = fig.add_subplot(gs[i,j])  #scatter plot of particles
-                    parameters['F_AC'] = AC[k]
+                    ax.text(0.02,0.9,letter[k],
+                            transform = ax.transAxes,
+                            backgroundcolor="white",zorder=-10)
+
+                    parameters['F0'] = F0[k]
                     k+=1
                 
                     y_data, avg_vy_data = single_particle(parameters,plot="phase")
@@ -609,7 +614,7 @@ if __name__ == "__main__":
 
 
             
[…]

### 2021-02-12 manuscript/manuscript_ajp_2020.tex
updated abstract, intro, figure notation

@@
   plays a key role in many physical processes.
-  We discuss a simple
-  numerical model %that
-  of synchronized particles 
-  %exhibits
-  %provides insight
-  %to synchronization behavior
-  %and
-  %atoms on surfaces.
-  %voltage driven superconducting vortices
-  %confined in a Josephson junction,
-  %and ac and dc driven
-  %charge and spin density waves.
-  %We present the basics
-  using
-  molecular dynamics simulations
-  for particles moving through
-  a viscous liquid.
-  %Simplified models
-  %such as 
-  %What problem did you study and why is it important?
-  Modeling synchronization
-  with simulations and table-top experiments
-  can 
-  provide insight
-  to complex behaviors
+  Modeling 
+  single particle
+  synchronization 
+  with simulations or table-top experiments
+  can is a useful technique to isolate
+  complex behaviors %to 
+  %provide insight
   in the natural world.
-  We drive 
-  particles
-  across a washboard potential energy landscape, 
-  a 
-  common 
-  technique to isolate complex 
-  synchronized patterns 
-  in both simulations and experiments.
-  %as observed in 
-  %experiments %al systems 
-  %of %interest to condensed matter physics %including 
-  %magnetically driven colloidal particles
-  %confined by light-fields.
-  %exhibit a variety of synchronization effects.
-  %in
-  %  Numerical model
-  %
-  %applied to single and multiple particle systems.
-  %so we model the dynamics of each particle
-  %with 
-  %overdamped equations of motion.
-  Our results show a variety of synchronization effects 
-  in single particle systems, 
-  %and detect synchronization using
-  %measurements of
-  which we characterize by 
-  plotting 
-  particle velocity as a function of applied driving force 
-  and phase diagrams of position versus velocity.
+  We discuss a %simple
+  %numerical model %that
+  molecular dynamics simulation
+  of a single particle
+  moving through
+  a viscous liquid
+  driven 
+  across a washboard potential energy landscape.
+  Our results show many dynamical patterns
+  as we alter the landscape and driving force.
+  Under certain conditions,
+  the particle velocity and location
+  are synchronized or 
+  phase-locked.
+  We include molecular dynamics code %and exercises
+  to simulate and characterize
+  particle dynamics.
+  %including 
+  %plotting  particle velocity as a function of applied driving force 
+  %and phase diagrams of position versus velocity.
   %We demonstrate how to 
@@
 particle position 
-can be imaged in real time 
+can be captured in real time 
 with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
@@
 %Since photon density is high at the beam center,
-A colloid centered in the beam is %subject to a
-uniformly bombarded by photons while 
+A colloid centered in the trap is %subject to a
+uniformly bombarded by photons. % while 
 %form a circular pattern with a higher density 
@@
 %A  is designed
-off-center colloids %away from center
-collide with photons unevenly,
-creating a net force.
+Off-center colloids %away from center
+experience a net force
+due to uneven photon collisions across
+the particle surface.
 %Colloids at a trap edge
@@
 location of the particle in the trap,
-the radiation pressure either moves colloids toward the beam center 
+the radiation pressure either moves colloids toward center 
 %local minimum 
 or ejects it from the trap.
-An optically trapped colloid executing Brownian motion
-is a useful probe of microscopic forces ~\cite{Volpe2013}.
 %In experiments
@@
 a child on a swing.
-%If subject to an applied force,
- How a particle moves
- in an optical landscape can
- change
- when 
- subject to external driving forces.
- %Individual particles can
- %move with synchronized location and velocity
- % with the environment
- %motions
- %that lock together particle .
  A confined oscillator may 
@@
  moving back and forth in time with
- the beat. 
+ the beat,
+ or moving between substrate minima.
  %The relationship between the driving force and
  %landscape can change the pattern of motion.  
- With a constant or 
+ A constant or 
  dc drive the landscape modulates 
- the particle velocity, below some threshold  
+ the particle velocity.
+ Below some threshold  
  the dc force is not strong enough to push the particle
@@
  %systems.
+ When the applied force varies periodically,
+ the ac drive can 
+ cause the particle to hop back and forth across
+ the landscape minima.
+ Many synchronized patterns occur
+ controlled by the substrate period.
 
@@
 %to the mechanics of naturally oscillating systems.
-We chose this model for its
-relevance to condensed matter systems
-and ease of simulation.
+%We choose this model for its
+%relevance to condensed matter systems
+%and ease of simulation.
 %---------------------------------------------------------------
@@
 %paper outline
-%In the following paper
 %In Section~\ref{sec:colloids} we describe colloid particles,
@@
 our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
+We choose this model for its
+relevance to condensed matter systems
+and ease of simulation.
 %In this section, we restrict our discussion to a single particle,
@@
  Particles are subject an external time-dependent driving force
-$\vec{F}_{D}(t)$
+$\vec{F}^{D}(t)$
 applied parallel to the y-direction.
@@
 \begin{equation}
-  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
+  \vec{F}^{D}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
     \label{eq:drive}
 \end{equation}
-with modifiable parameters including
+with %parameters including
 a constant component $F^{dc}$,
-and a time dependent component with amplitude $F^{ac}$
+a time dependent component with amplitude $F^{ac}$
 and frequency $\omega = 2 \pi f$.
@@
   (a) View of the $x-y$ plane. %of the simulation
-  The time-dependent applied driving force $\vec{F}^d$
+  The time-dependent applied driving force $\vec{F}^D$
   is parallel to the y-axis.
@@
 \begin{equation}
-  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{d}(t).
+  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{D}(t).
     \label{eq:motion}
@@
 synchronized with 
-the period of $F^d(t)$.
+the period of $F^D(t)$.
 %applied driving force.
@@
 the periodic landscape with the same rhythm as 
-the applied time-dependent force $F^d(t)$.
-When $F^d(t) > A_p$, a particle can 
+the applied time-dependent force $F^D(t)$.
+When $F^D(t) > A_p$, a particle can 
 overcome the barrier height of the landscape,
@@
 In Fig.~\ref{fig:0}(a)
-we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
+we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
 as a function of time with
@@
 at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$.
-In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
+In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %with the initial driving force at is minimum value 
-%$F^d(0) = F^{dc}$. 
+%$F^D(0) = F^{dc}$. 
 %
@@
 \includegraphics[width=\columnwidth]{single_particle.pdf}
-\caption{(a) The applied driving force $F^d(t)$. % (Eq.~\ref{eq:drive}).
+\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
   %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
@@
 Since 
-$A_p$ is large compared to the extrema of $F^{d}(t)$,
+$A_p$ is large compared to the extrema of $F^{D}(t)$,
 the particle oscillates back and forth
@@
 
-In the following section
-we include exercises to explore our numerical model,
-including the 
+In Section ~\ref{sec:problems}
+we explore our numerical model.
+Analytic exercises examine the 
 to linear drag equation in Ex.~\ref{ex:reynolds}, 
@@
 numerical integration techniques in Ex.~\ref{ex:euler}.
-An extended model that includes finite temperature effects
-is in Ex.~\ref{ex:brownian}.
+Numerical exercises extend the model
+to include finite temperature effects
+in Ex.~\ref{ex:brownian}.
 We explore changes in the particle motion
@@
 \caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
-  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
-  The remaining parameters in $F^d(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
+  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
+  The remaining parameters in $F^D(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
 \label{fig:1}
@@
   {\bf show that a particle confined to a landscape exerting force
-  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
   can be modeled with the equation of motion described in 
@@
   as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.
+  An optically trapped colloid executing Brownian motion
+  is a useful probe of microscopic forces ~\cite{Volpe2013}.
 
@@
   %is often studied with simple computational models and
-  can be visualized 
+  can be detected with 
   with phase
-  plots or Lissajous figures, 
-  first reported in 1857 \cite{Lissajous1857}.
+  plots or Lissajous figures.
+  %First reported in 1815 by Nathanial Bowditch
+  %and later by Lissajous in 1857  \cite{Lissajous1857}.
+  Lissajous figures
+  combine two periodic signals
+  into a two dimensional plot.  
   %and easily generated with a computer code 
@@
   used to characterize oscillating systems with
-  parametric plots of $v_y$ vs. $y$.
-
-  In driven systems,
-  the y-position is monotonically increasing.
-  We are most interested in the position of the particle
-  within the substrate period
-
+  parametric plots.
+
+  In a non-driven system, an appropriate
+  phase space is $v_y$ versus $y$
+  in order to characterize whether a particle velocity
+  synchronizes to a particular spatial location.
+  In a system driven parallel to the $y-$direction,
+  the particle position is monotonically increasing
+  in time.
+  A synchronized driven particle
+  repeats a particular velocity
+  at the same $y-$position of the particle
+  within the substrate period.
+  We define a phase variable 
   \begin{equation}
-  (y mod \lambda) / \lambda
+    %(y mod \lambda) / \lambda
+    \phi(t) = 2\pi(y(t)-\bar{v}_y t)/\lambda
   \end{equation}
-
-  %Juniper so-called ‘phase portraits’, in which the phase velocity, d\phi(t)/dt,is plotted against the phase, \phi(t) = 2\pi (x(t)-\bar{v}t)/\lambda (ref. 53). The
-  %REF 53
+  that is centered about the average particle velocity $\bar{v}_y$
+  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
+  We plot this phase
+  versus the phase velocity 
+  \begin{equation}
+    %(y mod \lambda) / \lambda
+    \dot{\phi}(t) = 2\pi(v_y(t)-\bar{v}_y/\lambda.
+  \end{equation}
+  %Juniper %REF 53
 
@@
       \caption{
-        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.
+        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, and (d) $0.2$.
       }

### 2021-02-13 manuscript/manuscript_ajp_2020.tex
starting to fill in phase section

@@
 In Section ~\ref{sec:problems}
-we explore our numerical model.
-Analytic exercises examine the 
+we explore our model
+with suggested exercises for interested readers.
+We include analytic exercises to examine the 
 to linear drag equation in Ex.~\ref{ex:reynolds}, 
@@
 numerical integration techniques in Ex.~\ref{ex:euler}.
-Numerical exercises extend the model
+We extend the model with
+numerical exercises %extend the model
 to include finite temperature effects
@@
 \subsection{Drag Models and Reynolds Numbers.}
-  Stokes' law describes the viscous drag on a sphere
-  moving at velocity $\vec{v}$ as 
+Stokes' law describes the drag force
 $\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
+on a sphere
+moving through a viscous liquid at velocity $\vec{v}$ 
   where $\eta$ is the dynamic fluid viscosity and 
@@
   Synchronization 
-  %is often studied with simple computational models and
   can be detected with 
-  with phase
-  plots or Lissajous figures.
+  phase
+  plots or Lissajous figures
+  that 
   %First reported in 1815 by Nathanial Bowditch
   %and later by Lissajous in 1857  \cite{Lissajous1857}.
-  Lissajous figures
-  combine two periodic signals
+  %Lissajous figures
+  compare two periodic signals
   into a two dimensional plot.
+  In a non-driven system, an appropriate
+  phase space is $v_y$ versus $y$.  
   %and easily generated with a computer code 
   %or oscilloscope \cite{Tong1997}.
-  A mode-locked system is confined to 
+  When a particle velocity
+  synchronizes to a particular spatial location
+  the dynamics
+  appears as 
+  %A mode-locked system is confined to 
   a closed loop in  
-  parametric phase space % showing the relationship
+  phase space, % showing the relationship
   %between two periodic functions
@@
   %where two combined frequencies at perpendicular orientations
-  Note the term phase
-  has two scientific meanings:  
-  %``oscillation phase'' and ``phase space.''
-  %refer to different uses of the word ``phase.''
-  oscillation phase $\phi_0$ is the constant of the argument
-  in a periodic function
-  $\sin{(\omega t + \phi_0)}$ and phase space is
-  used to characterize oscillating systems with
-  parametric plots.
-
-  In a non-driven system, an appropriate
-  phase space is $v_y$ versus $y$
-  in order to characterize whether a particle velocity
-  synchronizes to a particular spatial location.
+  %\footnote{The term phase
+  %has two scientific meanings:  
+  %oscillation phase $\phi_0$ is the constant of the argument
+  %in a periodic function
+  %$\sin{(\omega t + \phi_0)}$ and phase space is
+  %used to characterize oscillating systems with
+  %parametric plots.}.
   In a system driven parallel to the $y-$direction,

### 2021-02-14 manuscript/manuscript_ajp_2020.tex
moved phase into main body

@@
 %as shown
+
+  It is useful to compare
+  mode-locked quantities %periodic signals
+  in a two dimensional phase plot.
+  In a non-driven system, an appropriate
+  phase space is particle velocity $v_y$ versus position $y$.  
+  %and easily generated with a computer code 
+  %or oscilloscope \cite{Tong1997}.
+  When $v_y$ %a particle velocity
+  is mode-locked to %repeat periodically
+  a spatial location
+  a closed loop appears in  
+  $v_y$ vs $y$ space. % showing the relationship
+  %between two periodic functions
+  The pattern is determined by the mode,
+  or frequency ratio,
+  so a $1-1$ mode appears as a circle or oval.
+  Nodes appear in the oval 
+  for higher modes,
+  sometimes forming figure-eights
+  or other recognizable patterns.
+  A system that is not fully phase locked
+  will apppear as an unclosed loop.
+  Such quasiperiodic systems are
+  not fully synchronized.
+  %and the shifts in phase space represent
+  %small changes in system behavior.
+  With a long simulation time,
+  a quasiperiodic phase diagram
+  fills the plotting region due to the gradual shift
+  in the velocity-position relationship.
+  %with a frequency generator,
+  %where two combined frequencies at perpendicular orientations
+  %\footnote{The term phase
+  %has two scientific meanings:  
+  %oscillation phase $\phi_0$ is the constant of the argument
+  %in a periodic function
+  %$\sin{(\omega t + \phi_0)}$ and phase space is
+  %used to characterize oscillating systems with
+  %parametric plots.}.
+
+  In a system driven parallel to the $y-$direction,
+  %the particle velocity and position increase
+  %in time. % due to $F^{dc}$.
+  %Since a system does not form
+  %a closed loop in
+  %$v_y$ vs $y$ space,
+  we define phase variables 
+  to account for the net increase in velocity
+  and position.
+  The phase position is
+  defined as 
+  %within the substrate period as 
+  %We define a phase variable 
+  \begin{equation}
+    %(y mod \lambda) / \lambda
+    \phi(t) = 2\pi(y(t)-\bar{v}_y t)/\lambda
+  \end{equation}
+  centered about the average particle velocity $\bar{v}_y$
+  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
+  We plot this phase
+  versus the phase velocity 
+  \begin{equation}
+    %(y mod \lambda) / \lambda
+    \dot{\phi}(t) = 2\pi(v_y(t)-\bar{v}_y/\lambda.
+  \end{equation}
+  %Juniper %REF 53
+
+  In Fig.~\ref{fig:phase}
+  we plot $\dot{\phi}(t)$ versus $\phi(t)$
+  for increasing substrate amplitude $A_p$.
+  We fix the driving force with parameters
+  $F^{dc} = 0.1$ and frequency $f = 0.01$ and $F^{ac} = 0.2$.
+  In Fig.~\ref{fig:phase}(a)
+  there is no substrate ($A_p = 0.0$)
+  and the phase plot is a closed oval
+  centered at
+  $(\phi,\dot{\phi})=(10,0)$
+  with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
+  and semiminor axis of $\Delta \dot{\phi} = 2\pi/\lambda v_{max}$.
+  [insert analysis.]
+  As the force from the substrate
+  increases,
+  nodes form in the phase diagram
+  and the motion becomes quasiperiodic
+  so the loops in phase space do not fully overlap.
+  In Fig.~\ref{fig:phase}(b)
+  $A_p = 0.05$
+  the spatial properties are similar to
+  those in $A_p = 0.0$
+  with 
+  $(\phi,\dot{\phi})=(10,0)$
+  with a semimajor axis of $\Delta \phi = 20$.
+  The dynamical properties
+  are asymmetric,
+  with nodes in the positive $\dot{\phi}$ values.
+  [insert analysis.]
+  As the substrate
+  force becomes larger,
+  $\phi$ shifts to lower values
+  and $\dot{\phi}$ to positive values,
+  indicating
+  the particle can only move 
+  backward over a short distance.
+  \begin{center}
+    \begin{figure}[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{phase.pdf}
+      \caption{
+        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, (d) $0.2$, (e) $0.25$ and (f) $0.3$.
+      }
+      \label{fig:phase}
+    \end{figure}
+  \end{center}
+
 In Fig.~\ref{fig:1} 
@@
 within a single step.
-
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
+\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
+  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
+  The remaining parameters in $F^D(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
+\label{fig:1}
+\end{figure}
+\end{center}
 %$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
@@
 %and $f = 0.01$ cycles per time unit.
-
 %This synchronization
@@
 %multiples of the substrate period $n\lambda$.
+%\subsection{Phase plots}
+%  \label{ex:phase}
 
@@
 are in Ex.~\ref{ex:animation}.
-
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
-  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
-  The remaining parameters in $F^D(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
-\label{fig:1}
-\end{figure}
-\end{center}
-
 %In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
@@
   %of the system for our original parameters.
-  Here $n_b$ increases from $n_b = 0$ in (a) to
+  Here the number of backwards steps
+  $n_b$ increases from $n_b = 0$ in (a) to
   $n_b = 2$ in (b) to $n_b = 4$ in (c).  
@@
   %\item
-
-\subsection{Phase plots}
-  \label{ex:phase}
-
-  Synchronization 
-  can be detected with 
-  phase
-  plots or Lissajous figures
-  that 
-  %First reported in 1815 by Nathanial Bowditch
-  %and later by Lissajous in 1857  \cite{Lissajous1857}.
-  %Lissajous figures
-  compare two periodic signals
-  into a two dimensional plot.
-  In a non-driven system, an appropriate
-  phase space is $v_y$ versus $y$.  
-  %and easily generated with a computer code 
-  %or oscilloscope \cite{Tong1997}.
-  When a particle velocity
-  synchronizes to a particular spatial location
-  the dynamics
-  appears as 
-  %A mode-locked system is confined to 
-  a closed loop in  
-  phase space, % showing the relationship
-  %between two periodic functions
-  with patterns determined by the mode. % frequency ratio,
-  %with a frequency generator,
-  %where two combined frequencies at perpendicular orientations
-  %\footnote{The term phase
-  %has two scientific meanings:  
-  %oscillation phase $\phi_0$ is the constant of the argument
-  %in a periodic function
-  %$\sin{(\omega t + \phi_0)}$ and phase space is
-  %used to characterize oscillating systems with
-  %parametric plots.}.
-  In a system driven parallel to the $y-$direction,
-  the particle position is monotonically increasing
-  in time.
-  A synchronized driven particle
-  repeats a particular velocity
-  at the same $y-$position of the particle
-  within the substrate period.
-  We define a phase variable 
-  \begin{equation}
-    %(y mod \lambda) / \lambda
-    \phi(t) = 2\pi(y(t)-\bar{v}_y t)/\lambda
-  \end{equation}
-  that is centered about the average particle velocity $\bar{v}_y$
-  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  We plot this phase
-  versus the phase velocity 
-  \begin{equation}
-    %(y mod \lambda) / \lambda
-    \dot{\phi}(t) = 2\pi(v_y(t)-\bar{v}_y/\lambda.
-  \end{equation}
-  %Juniper %REF 53
-
-  \begin{center}
-    \begin{figure}[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{phase.pdf}
-      \caption{
-        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, and (d) $0.2$.
-      }
-      \label{fig:phase}
-    \end{figure}
-  \end{center}
 

### 2021-02-15 manuscript/manuscript_ajp_2020.tex
updated abstract and intro text.  filled in phase diagram results - not analysis.  likewise on hops

@@
   plays a key role in many physical processes.
-  Modeling 
-  single particle
-  synchronization 
-  with simulations or table-top experiments
-  can is a useful technique to isolate
-  complex behaviors %to 
+  %Modeling
+  A particle may
+  execute
+  motion 
+  coordinated  with position,
+  a synchronization behavior
+  that 
+  can be used to isolate
+  complex natural behaviors,  %to
+  either with
+  simulations or table-top experiments.
   %provide insight
-  in the natural world.
   We discuss a %simple
@@
   are synchronized or 
-  phase-locked.
+  phase-locked,
+  forming closed orbits in phase space.
+  Quasi-periodic motion is common, % in this system,
+  where the
+  dynamical center of motion shifts the
+  phase space orbit.
   We include molecular dynamics code %and exercises
@@
 the pendula were observed swing at same rate -- a 1:1 mode.
-For simple pendula of different lengths,
-a 2:1 mode can be seen when a pendulum four
+For a higher modes,
+consider simple pendula of different lengths,
+a 2:1 mode occurs when a pendulum four
 times the length of another swings with twice the period.
@@
 
-Complex dynamics can be studied with
+Complex dynamics such as synchronized mode-locking
+can be studied with
 colloid particles in experiments or simulations.
@@
 colloids are large %-- a few microns in size
-and move slowly %-- a few microns per second,
+and move slowly, %-- a few microns per second,
 particle position 
-can be captured in real time 
+can be measured in real time 
 with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
@@
 understanding synchronization at a single particle level \cite{Juniper2015}. 
-
 %due to the large size and slow speed of the particles.
@@
 Light is a
-tool for manipulating the colloidal environment.
-A circular optical trap uses 
+tool for manipulating the colloidal environment
+to alter synchronization patterns.
+Colloids can be trapped
+with 
+%A circular optical trap uses 
 radiation pressure from 
-a laser beam to confine colloids \cite{Ashkin1997}.
+a laser beam \cite{Ashkin1997}.
 %Since photon density is high at the beam center,
-A colloid centered in the trap is %subject to a
+A colloid centered in an optical trap is %subject to a
 uniformly bombarded by photons. % while 
@@
 %In experiments
-Diffraction gratings can be used to create
+Diffraction gratings can create
 more complex light environments, 
@@
  %and dissipating energy from the system at all driving forces.
- A sinusoidal or ac drive can create mode-locking,
+ When the applied force varies periodically,
+ the ac drive can 
+ cause the particle to hop back and forth across
+ the landscape minima.
+ Many synchronized patterns occur
+ controlled by the substrate period,
+ leading to 
+ %A sinusoidal or ac drive can create
+ mode-locking,
  where the average particle velocity
@@
  %systems.
- When the applied force varies periodically,
- the ac drive can 
- cause the particle to hop back and forth across
- the landscape minima.
- Many synchronized patterns occur
- controlled by the substrate period.
 
@@
 \end{equation}
-for a small time step $\Delta t = 0.001 \tau$.
+for a small time step $\Delta t = 0.01 \tau$.
 In %Section~\ref{sec:problems}
@@
 In this section, we fix the landscape parameters
-to $A_{p} = 0.1$ force units
+to $A_{p} = 0.1 F_0$ %force units
 with $N_p=20$ minima %in the landscape
@@
 forward and backward in the landscape.
-To explore the possible hopping patterns,
-we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
-to illustrate
-distinct oscillation modes. % as a function of $F^{dc}$.
-A mode is a periodic pattern of hops
-with a constant average particle velocity, $\langle {v}_{y} \rangle$
-over a range of driving forces $F^{dc}$.
-%as shown
-
   It is useful to compare
@@
   phase space is particle velocity $v_y$ versus position $y$.  
+  In a system driven parallel to the $y-$direction,
+  %the particle velocity and position increase
+  %in time. % due to $F^{dc}$.
+  %Since a system does not form
+  %a closed loop in
+  %$v_y$ vs $y$ space,
+  we define phase variables 
+  to account for the net increase in velocity
+  and position.
+  The phase position is
+  defined as 
+  %within the substrate period as 
+  %We define a phase variable 
+  \begin{equation}
+    %(y mod \lambda) / \lambda
+    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
+  \end{equation}
+  centered about the average particle velocity $\langle v_y \rangle$
+  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
+  We plot this phase
+  versus the phase velocity 
+  \begin{equation}
+    %(y mod \lambda) / \lambda
+    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
+  \end{equation}
+  %Juniper %REF 53
   %and easily generated with a computer code 
   %or oscilloscope \cite{Tong1997}.
-  When $v_y$ %a particle velocity
+  When velocity
   is mode-locked to %repeat periodically
@@
   a closed loop appears in  
-  $v_y$ vs $y$ space. % showing the relationship
+  phase space. % showing the relationship
   %between two periodic functions
@@
   or frequency ratio,
-  so a $1-1$ mode appears as a circle or oval.
+  so a 1:1 mode appears as a circle or oval.
   Nodes appear in the oval 
@@
   %parametric plots.}.
-
-  In a system driven parallel to the $y-$direction,
-  %the particle velocity and position increase
-  %in time. % due to $F^{dc}$.
-  %Since a system does not form
-  %a closed loop in
-  %$v_y$ vs $y$ space,
-  we define phase variables 
-  to account for the net increase in velocity
-  and position.
-  The phase position is
-  defined as 
-  %within the substrate period as 
-  %We define a phase variable 
-  \begin{equation}
-    %(y mod \lambda) / \lambda
-    \phi(t) = 2\pi(y(t)-\bar{v}_y t)/\lambda
-  \end{equation}
-  centered about the average particle velocity $\bar{v}_y$
-  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  We plot this phase
-  versus the phase velocity 
-  \begin{equation}
-    %(y mod \lambda) / \lambda
-    \dot{\phi}(t) = 2\pi(v_y(t)-\bar{v}_y/\lambda.
-  \end{equation}
-  %Juniper %REF 53
 
@@
   are asymmetric,
-  with nodes in the positive $\dot{\phi}$ values.
+  with three nodes in the positive $\dot{\phi}$ values.
+  The thickening of the line
+  indicates the system is not fully synchronized.
   [insert analysis.]
@@
   backward over a short distance.
+  In Fig.~\ref{fig:phase}(c)
+  $A_p = 0.1$
+  the phase properties are similar to
+  those in $A_p = 0.05$,
+  the three nodes have 
+  increased asymmetry in both phase variables 
+  $(\phi,\dot{\phi})$.
+  The nodes deepen,
+  indicating [insert analysis.].
+  In Fig.~\ref{fig:phase}(d)
+  $A_p = 0.2$
+  the pattern shifts
+  to two nodes,
+  [indicating change analysis].
+  In Fig.~\ref{fig:phase}(e)
+  $A_p = 0.25$
+  the system returns to a nodeless
+  orbit,
+  shaped like a triangle [because why?]
+  In Fig.~\ref{fig:phase}(f)
+  $A_p = 0.3$
+  the particle is trapped between substrate minima,
+  and traces out a small unclosed
+  orbit in phase space [because...]
+  The phase velocity is near zero
+  throughout the motion -
+  [comment on initial conditions]
   \begin{center}
@@
 
+To explore the possible hopping patterns,
+we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
+to illustrate
+distinct oscillation modes. % as a function of $F^{dc}$.
+A mode is a periodic pattern of hops
+with a constant average particle velocity, $\langle {v}_{y} \rangle$
+over a range of driving forces $F^{dc}$.
+%as shown
 In Fig.~\ref{fig:1} 
@@
 can be used to control the
-intrinsic velocity of the dc driven particle,
+net velocity of the dc driven particle,
 and the applied ac drive can cause mode-locking
@@
   In  Fig.~\ref{fig:brownian}(b)
-  $T/A_p = 5.0$ where hops between
+  $T/A_p = 5.0$,  hops between
   potential minima are possible but not probable,
-  a single hop occurs from
-  $y/\lambda = 10$ to $y/\lambda = 12$ at
-  $t \sim 40000 \tau$ and 
-  $y/\lambda = 10$ to $y/\lambda = 8$ at
+  a back-forth hop occurs from
+  $y/\lambda = 10$ to $12$ at
+  $t \sim 40000 \tau$ and a single hop from 
+  $y/\lambda = 10$ to $8$ occurs at
   $t \sim 280000 \tau$.
@@
   a random walk of hops atop the substrate.
+  [prove it]
   %in addition to the small scale random walk executed
@@
   Brownian motion does affect 
-  the formation of Shapiro steps
+  the formation of mode-locked steps
   and can be observed in experiments.
+  [explore]
   %and could be included
@@
   allowing a particle to hop a substrate maxima.
-  Experiments with single colloids \cite{Juniper2015} 
-  show 
-  hopping patterns with backward steps are more difficult
-  to achieve than forward,
-  with $n_f = 0$ to $6$ for $n_b = 0$,
-  $n_f = 0$ to $5$ for $n_b = -1$,
-  and
-  $n_f = 2$ to $3$ for $n_b = -2$
-  were realized 
-  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
-  {\bf Find the parameters
-  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
+  {\bf Explore the effect changing the driving frequency on the hopping pattern.}
 
@@
   ($n_b = 0$) 
-  across a broad range of frequencies.
+  across a broad range of frequencies
+  since $F^{dc} - F^{ac}= 0.05$
+  is too small to overcome $A_p$.
   The number of forward steps 
@@
 
+  Experiments with single colloids \cite{Juniper2015} 
+  show 
+  hopping patterns with backward steps are more difficult
+  to achieve than forward,
+  with $n_f = 0$ to $6$ for $n_b = 0$,
+  $n_f = 0$ to $5$ for $n_b = -1$,
+  and
+  $n_f = 2$ to $3$ for $n_b = -2$
+  were realized 
+  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+  {\bf Find the parameters
+  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
+  %[well, go one...]
   In Fig.~\ref{fig:hops_back}

### 2021-02-16 manuscript/manuscript_ajp_2020.tex
added pure dc sweep

@@
 We show a schematic of the system in Fig.~\ref{fig:landscape0}(a).
+The units of the simulated variables are summarized in Table ~\ref{tab:1}.
 
@@
 %
-The units of the simulated variables are summarized in Table ~\ref{tab:1}.
 
@@
 substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
+%A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
 temperature & $T_0 = 0$ \footnote{to learn more about the effects
@@
 
-A single particle %on this landscape
-responds to the applied driving force
-by moving across the landscape %maxima
-synchronized with 
-the period of $F^D(t)$.
+Here we drive 
+a single particle %on this landscape
+%responds to the applied driving force
+%by moving
+across the landscape %maxima
+to characterize its motion.
+%synchronized with 
+%the period of $F^D(t)$.
 %applied driving force.
@@
 where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
-In this section, we fix the landscape parameters
+In this section we fix the landscape parameters
 to $A_{p} = 0.1 F_0$ %force units
@@
 %In Fig.~\ref{fig:0} 
-The driven particle adjusts
-its motion to traverse
+The driven particle %adjusts
+moves across %its motion to traverse
 the periodic landscape with the same rhythm as 
@@
 average particle velocity $\langle{v}_y\rangle$
-as the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
+as the displacement %$\Delta y = y(t_0+T) - y(t_0)$
 over the period of the driving force.
@@
 when $F_{D}(t) \approx 0 $. 
-
 \begin{center}
@@
 forward and backward in the landscape.
+
   It is useful to compare
@@
 
-  In Fig.~\ref{fig:hops}
-  we show the effects of lowering the frequency
-  of applied driving force,
-  holding the remaining parameters fixed 
+  Fig.~\ref{fig:hops}
+  shows the effects of lowering the frequency
+  of applied driving force
+  We hold the remaining parameters fixed 
   to 
@@
   is too small to overcome $A_p$.
-  The number of forward steps 
-  $n_f$ increases as frequency decreases.
+  The rate of forward hops 
+  increases as frequency decreases,
+  but in each case the particle
+  hops across two substrate periods as in Fig.~\ref{fig:0}.
+  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
+  do not match the temporal period of $F^D(t)$
+  due to the high frequency.
+  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.1$
+  is apparent in the undulations of the particle
+  with a period of $10\tau$.
+  %Due to the high frequency,
+  The particle is trapped between substrate minima $y \approx \lambda/2 $ for
+  a time interval of $400 \tau$.
+  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.05$
+  with a period of $20\tau$
+  arrests the particle between minima,
+  with a hopping rate of $200 \tau$.
+  At intermediate frequencies 
+  such as $f=0.01$
+  the particles are synchronized so that 
+  the hopping rate matches the driving frequency.
+  In Fig.~\ref{fig:hops}(c) $f=0.015$
+  the particle hops forward two minima every $67\tau$.
   Low frequencies
-  result in sustained positive or negative motion of a particle,
-  where in Fig.~\ref{fig:hops}(e)
-  the particle reaches the top edge of the system
+  result in sustained positive motion of a particle.
+  In Fig.~\ref{fig:hops}(d) $f=0.005$
+  the particle executes two subsequent forward hops
+  before becoming trapped
+  for the remainder of the period $200 \tau$.
+  In Fig.~\ref{fig:hops}(e) $f=0.001$
+  the hopping is continuous
+  over the simulation time.
+  Here the particle reaches the top edge of the system
   and wraps back to $y=0$.
+  Given a simulation time of the period length $1000 \tau$,
+  the particle would cease forward motion.
   \begin{center}
@@
       \caption{
-        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency as marked.
-        In (e) the particle wraps the periodic boundary conditions.
+        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.1$,
+        (b) $0.05$, (c) $0.015$, (d) $0.005$ and (e) $0.001$ where  
+        the particle wraps the periodic boundary conditions.
       }
@@
 
-  Experiments with single colloids \cite{Juniper2015} 
+  Experiments with single colloids 
   show 
   hopping patterns with backward steps are more difficult
-  to achieve than forward,
-  with $n_f = 0$ to $6$ for $n_b = 0$,
+  to achieve than forward.
+  In Ref.\cite{Juniper2015} the following
+  combinations of forward and backwards steps where realized:
+  $n_f = 0$ to $6$ for $n_b = 0$,
   $n_f = 0$ to $5$ for $n_b = -1$,
@@
   $n_f = 2$ to $3$ for $n_b = -2$
-  were realized 
-  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+  %were realized 
+  by sweeping through
+  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
   {\bf Find the parameters
@@
   In Fig.~\ref{fig:hops_back}
-  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
-  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
+  we fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$.
+  We show the results for increasing
+  the amplitude of $F^{ac} = 0.2, 0.3, 0.4$.
   %of the system for our original parameters.
@@
   $n_b = 2$ in (b) to $n_b = 4$ in (c).
+  The number of forward steps also increases
+  due to the increased total positive amplitude of $F^D(t)$.
   \begin{center}
@@
   \end{center}
-  %In Fig.~\ref{fig:hops}
-
+
+  In Fig.~\ref{fig:shapiro}
+  we show two additional sweeps of $F^{dc}$.
+  In Fig.~\ref{fig:shapiro}(a) $F^{ac}= 0.0$.
+  With no oscillating component of the driving force,
+  the force-velocity relationship is monotonically increasing
+  above the depinning threshold $F^c$ such that
+  \begin{equation}
+    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}
+  \end{equation}
+  The particle does not phase lock since there is no periodicity to $F^D(t)$,
+  but does exhibit undulations in $\langle v_y \rangle$
+  due to the corregations in the substrate.
+  In Fig.~\ref{fig:shapiro}(b) $F^{ac}=0.4$ and frequency $f=0.01$.
+  Mode-locked steps in $\langle v_y \rangle$ vs. $F^{dc}$
+  At low values of $F^{dc}$ the particle may move backwards,
+  distorting the steps, as seen below $F^{dc}<0.3$
+  Between $0.3< F^{dc}<0.5$ the system exhibits phase locked steps.
     \begin{center}
@@
       \centering
-      \includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
+      \includegraphics[width=\columnwidth]{{fig9_sweep_FDC_vs_vx}.pdf}
+      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
       \caption{
-        Mode-locked steps in $\langle v_y \rangle$ vs.
-$F^{dc}$ of a particle with frequency $f=0.01$ and $F^{ac}=0.4$.
-At low values of $F^{dc}$ the particle may move backwards, distorting the steps.
+        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
+        $F^{ac}=0.0$ (blue) and $0.4$ (orange) with frequency $f=0.01$.
       }

### 2021-02-16 code/MD_colloid.py
added pure DC sweep

@@ -284,11 +284,11 @@ def plot_phase(ax,y_data,avg_vy_data,p):
     if 1:
         ax.scatter(phi_y_data[plot_delay:],dot_phi_y_data[plot_delay:],s=5) #,lw=5)
     else:
-        ax.scatter(phi_y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
+        ax.scatter(y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
 
     ax.set_xlabel(r"$\phi_y(t)$")
     ax.set_ylabel(r"$\dot{\phi}_y(t)$")
-    ax.yaxis.set_label_coords(-0.22, 0.5)
+    ax.yaxis.set_label_coords(-0.2, 0.5)
 
     #ax1.set_xticks([])
     #ax1.set_xlim(0,time_data[-1]+1)
@@ -306,9 +306,7 @@ def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC
     #freq = p['freq']
     #period = p['period']
     
-    fig = plt.figure(figsize=(7,4))
-    gs=gridspec.GridSpec(1,1)
-    ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
+    ax1 = parameters['ax']
 
     #calculate from np.array rather than incrementally from subroutines
     #F_drive = FDC_data + F_AC*np.sin(2*np.pi*freq*time_data)
@@ -323,16 +321,6 @@ def plot_velocity_force(avg_FDC_data,avg_vy_data,parameters): #velocity_data,FDC
 
     #ax1.legend(loc=4,fontsize=20,borderaxespad=0.0,frameon=0,handlelength=1.5) #,labelspacing=0.2
 
-    #plt.xlim(155,157)
-    ax1.set_xlabel("F$^{dc}$")
-    ax1.set_ylabel(r"$\langle$v$_y \rangle$")
-
-    ax1.set_xlim(0,avg_FDC_data[-1])
-    ax1.set_ylim(avg_vy_data[0]-0.001,avg_vy_data[-1])
-        
-    plt.tight_layout(pad=0.2)
-    plt.savefig(parameters['filename'])
-    
     return 
 
 #-------------------------------------------------------------------
@@ -567,7 +555,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #Coded to make figures 2 to 8
-    make_fig = 8
+    make_fig = 9
 
[…]

### 2021-02-19 manuscript/manuscript_ajp_2020.tex
found a mistake in the code

@@
  \begin{equation}
-   U(y) = U_0 \cos{(N_p \pi y / L)}
+   U(y) = U_0 \cos{(2 \pi y / \lambda)}
      \label{eq:ysubstrate}
 \end{equation}
- where $N_p$ are the number of periods,
+ where $\lambda=L/N_p$ with $N_p$ are the number of periods,
  % $L$ is the period length,
@@
  to set the depth of the minima
- with simulation units of energy $E_0 = 1$. 
+ with simulation units of energy $E_0$. 
  %We define the substrate strength to be
@@
 \centering
-\caption{Simulation parameters and units and comparable
-  experimental values~\cite{Juniper2015}.
-  Blanks %in the experimental parameters
-  indicate
-  units, rather than parameters that
-  are not easily represented by a single value.}
+\caption{Simulation parameters and units with comparable
+  experimental values~\cite{Juniper2015}.}
+  %Blanks indicate you are a moron
+  %units, rather than parameters that
+  %are not easily represented by a single value.}
 %{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
@@
 velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
-driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
+driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\ %frequency 0.75 Hz
 viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
@@
 substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
-substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
+substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 25 k_B T \sim 2 J$ \\
+%they have 75 k_B T as the bottom of -U_0
 %A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
@@
   \label{eq:force}
-  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
+  F^l_y(y) = -A_{p} \sin{(2 \pi y / \lambda)} 
 \end{equation}
-where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
+where the force is scaled with parameter $A_{p} = 2\pi U_0/\lambda$.
 In this section we fix the landscape parameters
@@
 corresponding to a spatial period $\lambda = 1.825 a_0$.
+The competition between the driving force and landscape potential
+can produce a variety of hopping patterns in the particle motion. 
+%In Fig.~\ref{fig:0}
+%reaching a minimum position
+%of $y/\lambda = 1$
+%over the total period $T = 100$.
+%In Fig. ~\ref{fig:0}
+%the average displacement during one time period is a single wavelength
+%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
+%single dc case with figure
+%dc_current 0.01
+%ac_current 0.05
+%ac_frequency 0.01
+%fp_y 0.1
+%
+The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
+control the rate and distance a  particle moves 
+forward and backward in the landscape.
+[edit and move:] The addition of an oscillating force
+can lead to interference effects
+that create stepped force-velocity curves.
+Useful model - essentially an overdamped driven pendulum -
+under certain parameters.
+The steps occur
+due to the phase locking between lattice substrate
+and applied driving force.
+Step widths depend on AC drive.
+Discrete modes.
+%Shapiro steps wash out to sloped regions at
+%high vortex numbers,
+%so what is the analog in my system?
+%need to sweep through more parameters to find and report the flat regions
+%not fully phase locked.
 
@@
 $\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
+[TODO: update description!]
 The horizontal dashed lines
@@
 The particle synchronizes its motion such that the 
-driving force is maximum when the landscape 
+edriving force is maximum when the landscape 
 force is minimum,
@@
 \centering
-\includegraphics[width=\columnwidth]{single_particle.pdf}
+\includegraphics[width=\columnwidth]{fig2.pdf}
 \caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
@@
 
-The competition between the driving force and landscape potential
-can produce a variety of hopping patterns in the particle motion. 
-%In Fig.~\ref{fig:0}
-%reaching a minimum position
-%of $y/\lambda = 1$
-%over the total period $T = 100$.
-%In Fig. ~\ref{fig:0}
-%the average displacement during one time period is a single wavelength
-%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
-%single dc case with figure
-%dc_current 0.01
-%ac_current 0.05
-%ac_frequency 0.01
-%fp_y 0.1
-%
-The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
-control the rate and distance a  particle moves 
-forward and backward in the landscape.
-
+{\it NOTE: YOUR $A_P$ VALUES ARE TOO SMALL TO MAKE THIS A MEANINGFUL PHASE VARIALBE.
+YOU NEED TO SCALE WITH THE DRIVE FORCE AMPLITUDES.
+THIS CAN ALSO HELP YOU UNDERSTAND WHY YOU ARE GETTING BIG JUMPS IN POSITION COMPARED TO JUNIPER ET AL.
+YOU ARE WORKING IN THE WEAK SUBSTRATE LIMIT.
+also insert plots of $y/\lambda$ over a single period with the phase plots - like juniper}
   It is useful to compare
   mode-locked quantities %periodic signals
-  in a two dimensional phase plot.
+  in a two dimensional phase plot
+  to distinguish fully and partially synchronized
+  behavior.  
   In a non-driven system, an appropriate
@@
   and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  We plot this phase
+  In phase diagrams we plot $\phi(t)$ %phase
   versus the phase velocity 
@@
 
+  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
   In Fig.~\ref{fig:phase}
@@
   with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
-  and semiminor axis of $\Delta \dot{\phi} = 2\pi/\lambda v_{max}$.
+  and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
   [insert analysis.]
@@
   \end{equation}
-  %where $n$ is an integer indicating
-  %discrete simulation timesteps
-  such that $t = N \Delta t$.
-  Random normal distributions are not correlated 
-  over the independent variable,
-  for the independent variable to be time
-  \begin{equation}
-  \langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
-  \end{equation}
-  for times $t$ and $\tau$,
-  where $\delta(t-\tau)$ is the Dirac-delta function.
-  Here the scaling factor energy of 
-  $k_B T$ is
-  derived from the Boltzmann constant $k_B$
-  and temperature $T$ \cite{Allen2017}.
+  where $n$ is an integer indicating
+  discrete simulation timesteps and 
+  $t = N \Delta t$.
+  %Random normal distributions are not correlated 
+  %over the independent variable,
+  %for the independent variable to be time
+  %\begin{equation}
+  %\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
+  %\end{equation}
+  %for times $t$ and $\tau$,
+  %where $\delta(t-\tau)$ is the Dirac-delta function.
+  %Here the scaling factor energy of 
+  %$k_B T$ is
+  %derived from the Boltzmann constant $k_B$
+  %and temperature $T$ \cite{Allen2017}.
   A particle
@@
   %Measure the position vs. time
-  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
+  a non-driven colloid for $T/A_p = 4.0$, $5.0$, and $6.0$.
   The crossover
@@
 
-  Experiments with single colloids 
-  show 
-  hopping patterns with backward steps are more difficult
+  Hopping patterns with backward steps are more difficult
   to achieve than forward.
-  In Ref.\cite{Juniper2015} the following
-  combinations of forward and backwards steps where realized:
+  In Ref.\cite{Juniper2015}
+  experiments with single colloids 
+  produce 
+  the following
+  combinations of forward and backwards steps:
   $n_f = 0$ to $6$ for $n_b = 0$,
@@
   that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
-  %[well, go one...]
+  %[well, go on...]
+
   In Fig.~\ref{fig:hops_back}
-  we fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$.
-  We show the results for increasing
-  the amplitude of $F^{ac} = 0.2, 0.3, 0.4$.
-  %of the system for our original parameters.
-  Here the number of backwards steps
-  $n_b$ increases from $n_b = 0$ in (a) to
-  $n_b = 2$ in (b) to $n_b = 4$ in (c).
+  we explore a hopping pattern not
+  observed in Ref.~\cite{Juniper2015}.
+  This is possible in simulation because
+  our particle readily hops through
+  $2\lambda$.
+  We fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$
+  and increase
+  the amplitude of $F^{ac}$,
+  which causes the number of backwards steps to increase.
   The number of forward steps also increases
   due to the increased total positive amplitude of $F^D(t)$.
+  In Fig.~\ref{fig:hops_back}(a) 
+  $F^{ac} = 0.2$. %, $0.3$ and $0.4$.
+  %of the system for our original parameters.
+  the number of backwards steps
+  $n_b = 0$ with $n_f = 6$.
+  In Fig.~\ref{fig:hops_back}(b) 
+  $n_b = 2$ and $n_f = 8$.
+  In Fig.~\ref{fig:hops_back}(c) 
+  $n_b = 4$ and $n_f = 10$.
+  In each case the average velocity %net displacement
+  is $\langle v_y \rangle = 6\lambda/T$.
+
   \begin{center}
@@
   In Fig.~\ref{fig:shapiro}
-  we show two additional sweeps of $F^{dc}$.
-  In Fig.~\ref{fig:shapiro}(a) $F^{ac}= 0.0$.
+  we sweep the constant driving force $F^{dc}$
+  for a fixed amplitude $F^{ac}$ and frequency.
+  Fig.~\ref{fig:shapiro}(a) shows $F^{ac}= 0.0$ and (b) shows $F^{ac}=0.4$
+  with frequency $f=0.01$.
   With no oscillating component of the driving force,
@@
   \begin{equation}
-    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}
+    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}.
   \end{equation}
+  The critical force $F^c$ is equal to the maximum substrate force
+  $A_p$ so the applied driving
+  force can move a particle over a substrate barrier.
   The particle does not phase lock since there is no periodicity to $F^D(t)$,
@@
   due to the corregations in the substrate.
-  In Fig.~\ref{fig:shapiro}(b) $F^{ac}=0.4$ and frequency $f=0.01$.
-  Mode-locked steps in $\langle v_y \rangle$ vs. $F^{dc}$
+  %WAIT, THAT DOESN'T MAKE SENSE!
+  %WHAT IS WRONG WITH YOUR MD SIMULATION?
+  When $F^{ac}=0.4$, 
+  mode-locked steps appear in $\langle v_y \rangle$ vs. $F^{dc}$.
   At low values of $F^{dc}$ the particle may move backwards,
@@
         $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
-        $F^{ac}=0.0$ (blue) and $0.4$ (orange) with frequency $f=0.01$.
+        $F^{ac}=0.0$ (blue) and $F^{ac}=0.4$ (orange) with frequency $f=0.01$.
+        The substrate is as in Fig.~\ref{fig:0}
+        with $A_p = 0.1$.
       }
@@
 is %often
-observed
+observed important technologies such as 
 in quantum electronic
@@
 coupled arrays of junctions \cite{Benz1990}.
+%laser gyroscopes
+%Chow, W. W. et al. The ring laser gyro. Rev. Mod. Phys. 57, 61–104 (1985).
+%dusty plasmas?
 Shapiro steps vary in width depending on the strength of the
@@
 and superconducting vortices in landscapes 
-engineered with periodic patterns of pinning sites.
+engineered with periodic patterns of pinning sites \cite{Reichhardt2000}.
 %Thus the study of
@@
 
-    \bibitem{Stewart1968}  W. C. Stewart Current‐Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
+    \bibitem{Stewart1968}  W. C. Stewart, Current-Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
 
@@
 
-    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il’ichev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
+\bibitem{Reichhardt2000} C.
+Reichhardt, R.
+T.
+Scalettar, G.
+T., Zim{\'a}nyi, N.
+Gr{\o}nbech-Jensen,  Phase-locking of vortex lattices interacting with periodic pinning.
+Phys.
+Rev.
+B {\bf 61}, R11914 (2000).
+
+    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
 
@@
 
-    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Muñoz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
+    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Mu{\~n}oz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
 

### 2021-02-19 code/MD_colloid.py
fixed factor of 2 in substrate code

@@ -44,27 +44,28 @@ def brownian_distribution(parameters):
     
 ##################################################################
 def landscape_force(y,parameters):
-    '''landscape potential is equation (1) in the manuscript, while force is equation (5) - for now anyway
+    '''landscape potential is equation (1) in the manuscript, 
+    while force is equation (5) - for now anyway
 
     U(y) = U0 cos(Np*pi*y/L)
 
-    F_y = -dU/dy = -U0/period * sin(Np*pi*y/L)
+    F_y = -dU/dy = -U0/period * sin(Np*2pi*y/L)
 
-    potential minima occur at U(y) = -U0, or cos(Np*pi*y/L) = -1
-    meaning Np*pi*y/L = m pi, where m is odd
+    potential minima occur at U(y) = -U0, or cos(Np*2pi*y/L) = -1
+    meaning Np*2pi*y/L = m pi, where m is odd
     
     Required Parameters
-    period: float 
-    the spatial period of the washboard potential, should be the system length divided by the number of minima  (L/Np)
-
     y: float
     the location in the y-direction of the individual particle
+
+    parameters: dict
+    contains all constants of the simulation, notably the substrate period and barrier height F0
     '''
 
     period = parameters['period']
     F0 = parameters['F0']
     
-    return -F0*np.sin(np.pi*y/period)
+    return -F0*np.sin(2*np.pi*y/period)
 
 ###################################################################
 def external_drive(F_DC,time, parameters):
@@ -120,7 +121,14 @@ def average_velocity(int_time, vy, avg_vy, parameters):
 #####################################################################
 def md_step(y, int_time, F_DC, avg_vy, parameters, ft=0):
     '''
+    Required Arguments
+    y
+    int_time
+    F_DC
+    avg_vy
+    parameters
 
+    Optional Arguments
     ft random kicks due to temperature affects
     '''
 
@@ -153,6 +161,7 @@ def md_step(y, int_time, F_DC, avg_vy, parameters, ft=0):
     y += vy*dt
 
     #check periodic boundary conditions
+    #if we've left the edge of the system, remap 
     if y > SY:
         y -= SY
     elif y < 0:
[…]

### 2021-02-19 code/MD_colloid.py
moved Fdc to fig3 and have level steps now!

@@ -583,7 +583,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #Coded to make figures 2 to 8
-    make_fig = 2
+    make_fig = 3
 
     parameters['filename']="fig%d.pdf"%(make_fig)
 
@@ -660,7 +660,9 @@ if __name__ == "__main__":
         if make_fig == 3:
             delta_Fdc = 0.001
             Fdc_max=0.3+delta_Fdc
-            parameters['filename']="fig3_sweep_FDC_vs_vx.pdf"
+            #parameters['filename']="fig3_sweep_FDC_vs_vx.pdf"
+
+            F_AC = [0.0, 0.05] #, 0.1]
 
             '''
             elif make_fig == 7:
@@ -712,14 +714,14 @@ if __name__ == "__main__":
                 avg_vy_data[i] = single_particle(parameters,plot="y-velocity")            
 
             #plot_velocity_force(Fdc_data,avg_vy_data,parameters)
-            ax1.plot(Fdc_data,avg_vy_data,'.',label=r"F$^{ac}$ = %1.1f"%(F))
+            ax1.plot(Fdc_data,avg_vy_data,label=r"%1.2f"%(F))
             ax1.set_xlim(0,Fdc_data[-1])
             ax1.set_ylim(avg_vy_data[0]-0.001,avg_vy_data[-1])
 
         #plt.xlim(155,157)
         ax1.set_xlabel("F$^{dc}$")
         ax1.set_ylabel(r"$\langle$v$_y \rangle$")
-        ax1.legend(loc='best',fontsize=22,numpoints=3,borderpad=0.1,handletextpad=0.2)
+        ax1.legend(loc='best',fontsize=20,numpoints=3,borderpad=0.1,handletextpad=0.2,title="F$^{ac}$")
                     
         plt.tight_layout(pad=0.2)
         plt.savefig(parameters['filename'])

### 2021-02-20 code/MD_colloid.py
starting to fix the period mistake, regularize the variables, and comment everything

@@ -204,9 +204,9 @@ def plot_position_vs_time(ax2,time_data,y_data,p):
     ax1.xaxis.set_minor_locator(AutoMinorLocator(8))
     ax1.grid(axis='both',which='both')
     '''
-    ax2.yaxis.set_minor_locator(AutoMinorLocator(5))
-    ax2.xaxis.set_minor_locator(AutoMinorLocator(8))
-    ax2.grid(axis='both',which='both')
+    #ax2.yaxis.set_minor_locator(AutoMinorLocator(5))
+    #ax2.xaxis.set_minor_locator(AutoMinorLocator(8))
+    #ax2.grid(axis='both',which='both')
     
     return 
 
@@ -538,7 +538,7 @@ def set_parameters():
     dict['y0'] =  0 #dict['Sy']/2
 
     #landscape potential - Fig2 - 0.1
-    dict['F0'] = 0.125 #parameters 0.1
+    dict['F0'] = 0.1 #25 #parameters 0.1
     dict['Np'] = 20         #number of troughs in the substrate
     dict['period'] = dict['Sy']/dict['Np']  #spatial period of substrate in y-direction
 
@@ -583,7 +583,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #Coded to make figures 2 to 8
-    make_fig = 3
+    make_fig = 2
 
     parameters['filename']="fig%d.pdf"%(make_fig)
 
@@ -736,12 +736,12 @@ if __name__ == "__main__":
 
         #simulating for a long time, 
         parameters['dt'] = 0.1 #timestep in simulation units
-        parameters['maxtime']=3000000        #total time 
-        parameters['writemovietime']=10000   #interval to write data 
+        parameters['maxtime']=300000        #total time 
+        parameters['writemovietime']=1000   #interval to write data 
         parameters['decifactor']=1   #interval to write data to arrays for plotting
 
         #save the figure in
-        parameters['filename']="brownian_particle_dt0.1.pdf"
+        #parameters['filename']="brownian_particle_dt0.1.pdf"
 
         #make the figure
         fig = plt.figure(figsize=(10,12))
@@ -749,12 +749,12 @@ if __name__ == "__main__":
         i=0
 
         #sweep through temperatures
-        for temp in [4.0, 5.0, 6.0]:
+        for temp in [3.0, 3.5, 4.0]:
 
             #create and label the subplot
             ax = fig.add_subplot(gs[i,0])
-            ax.text(0.02,0.89,letter[i],
[…]

### 2021-02-20 manuscript/manuscript_ajp_2020.tex
moved Fdc to fig3 and have level steps now!
updated Brownian figure - some text to update

@@
 \centering
-\includegraphics[width=\columnwidth]{sweep_FDC_vs_vx.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$ as a function of $F^{dc}$,
+\includegraphics[width=\columnwidth]{fig3.pdf}
+\caption{Average particle velocity  $\langle v_{y} \rangle$
+  as a function of $F^{dc}$, 
   the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
-  The remaining parameters in $F^D(t)$ are as in Fig.~\ref{fig:0}, $F^{ac}=0.05$ and $f = 0.01$.  }
+  We fix
+  $F^{ac}=0.0$ (blue) and 
+  $F^{ac}=0.05$ (orange) with $f = 0.01$ 
+  as in Fig.~\ref{fig:0}.}
 \label{fig:1}
@@
   %Measure the position vs. time
-  a non-driven colloid for $T/A_p = 4.0$, $5.0$, and $6.0$.
-  The crossover
-  to a hopping regime occurs at $T/A_p \approx 5.6$.
+  a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.
+  %The crossover
+  %to a hopping regime occurs at $T/A_p \approx 5.6$.
   %Reproduce these results.  
@@
       \centering
-      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
+      \includegraphics[width=\columnwidth]{{fig4}.pdf}
       \caption{
@@
         energy landscape.
-        (a) $T/A_p = 4.0$ no hopping occurs.
-        (b) $T/A_p = 5.0$ a three hops occur %at $t = 130000$
-        across distances of $\Delta y = 2 \lambda$.
-        (c) $T/A_p = 6.0$ many hops occur.
+        (a) $T/A_p = 3.0$ no hopping occurs.
+        (b) $T/A_p = 3.5$ one hop occurs and %at $t = 130000$
+        %across distances of $\Delta y = 2 \lambda$.
+        (c) $T/A_p = 4.0$ many hops occur.
         Note the scale of the $y-$axis differs in each panel
         and the time scale is
-        much greater than in Fig.~\ref{fig:0}.
+        greater than in Fig.~\ref{fig:0}.
+        The precise timing of hops pattern varies
+        by simulation,
+        sometimes exhibiting several hops for $T/A_p = 3.5$. 
       }

### 2021-02-22 manuscript/manuscript_ajp_2020.tex
discovered frequency regimes

@@
 %16 particles in a strong potential energy landscape of 15 minima (trap spacing: l¼5.5 mm; laser power per trap: WE1.75 mW; trap stiffness: k¼8.7?10?7 kg s?2; trap depth: V0¼200 kBT),
-
+%JUNIPER2017
+%The driving force is provided by a PI-542.2CD piezo-stage, controlled using the LabView interface, at driving 0.4 ≤ FAC/ζ ≤ 14 µm s−1, and a frequency of 1 velocities of 0.05 ≤ FDC/ζ ≤ 8 µm s−1.
+AC driving veloc
 %Volpe AJP Parameters
@@
 
-{\it NOTE: YOUR $A_P$ VALUES ARE TOO SMALL TO MAKE THIS A MEANINGFUL PHASE VARIALBE.
+%{\it NOTE: YOUR $A_P$ VALUES ARE TOO SMALL TO MAKE THIS A MEANINGFUL PHASE VARIALBE.
 YOU NEED TO SCALE WITH THE DRIVE FORCE AMPLITUDES.
@@
         Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, (d) $0.2$, (e) $0.25$ and (f) $0.3$.
+        [first 100 timesteps removed to reduce transients]
       }
@@
   $F^{ac}=0.05$ (orange) with $f = 0.01$ 
-  as in Fig.~\ref{fig:0}.}
+  as in Fig.~\ref{fig:0}.
+  {TODO: with these parameters, the steps are fractional!}
+}
 \label{fig:1}

### 2021-02-22 code/MD_colloid.py
exploring step height

@@ -300,7 +300,7 @@ def plot_phase(ax,y_data,avg_vy_data,p):
     vbar = np.average(avg_vy_data)
     time = np.arange(1,p['maxtime']+1,1)*p['dt']
         
-    #plot_delay = 100   
+    plot_delay = 100   
     #no subtraction
     
     # driven phase variables
@@ -316,7 +316,7 @@ def plot_phase(ax,y_data,avg_vy_data,p):
 
     ax.set_xlabel(r"$\phi_y(t)$")
     ax.set_ylabel(r"$\dot{\phi}_y(t)$")
-    ax.yaxis.set_label_coords(-0.2, 0.5)
+    #ax.yaxis.set_label_coords(-0.2, 0.5)
 
     #ax1.set_xticks([])
     #ax1.set_xlim(0,time_data[-1]+1)
@@ -527,7 +527,11 @@ def set_parameters():
     #use a python dict (i.e. a hash to organize the parameters)
     dict={}
 
-    dict['dt'] = 0.005 #timestep in simulation units
+    dict['dt'] = 0.1 #005 #timestep in simulation units
+    
+    #integer time steps
+    dict['maxtime']=4000        #total time steps in simulation
+    dict['writemovietime']=1   #interval to write data to arrays for plotting
 
     dict['Sy']=36.5         #height of system
     dict['Sx']=36.5         #width of system
@@ -545,16 +549,14 @@ def set_parameters():
     #Brownian motion factor
     dict['temperature'] = 5.7*dict['F0']
     
-    #integer time steps
-    dict['maxtime']=400000        #total time steps in simulation
-    dict['writemovietime']=1000   #interval to write data to arrays for plotting
-    
     #control the "constant" component of driving force
     dict['F_DC_max'] = 0.1        #"constant" driving force for most of simulation
+
+    #sweep the DC portion up from zero
     if 0:
         dict['F_DC'] = 0              #initial F_DC
         dict['F_DC_incr'] = 0.01      #amount to increase FDC at every drop step
-        dict['F_DC_max'] = 0.1        #"constant" driving force for most of simulation
+        dict['F_DC_max'] = 0.1        #"max DC driving force
         dict['drop'] = 4000           #integer timesteps to "ramp" the DC force
     else:
         dict['F_DC'] = dict['F_DC_max']  #initial F_DC
@@ -583,10 +585,9 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #Coded to make figures 2 to 8
[…]

### 2021-02-23 code/plot_3Dlandscape.py
cleaned up some files and documentation

@@ -1,153 +1,0 @@
-#!/usr/bin/env python3
-
-#numeric and basic plotting libraries
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.colors as colors
-#from matplotlib import cm
-import matplotlib.cm as cm
-
-import matplotlib.gridspec as gridspec
-
-from mpl_toolkits.mplot3d import Axes3D
-#import mpl_toolkits.mplot3d.Axes3D as Axes3D
-
-
-#set default font of plot
-plt.rc('font', size=20)
-
-##########################################################
-#ADD CONTOUR PLOT
-##########################################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color in the quasi1D potential to contain 
-    the particles in a trough.  
-    Can also add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    #set up plot of 1 row, 3 columns to make the first plot smaller
-    gs=gridspec.GridSpec(1,3)
-    
-    ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
-    ax2 = fig.add_subplot(gs[0,1:], projection='3d')  #scatter plot of particles
-
-    a_p = L/N
-
-    #assuming Tiare's trough system, so we won't want to cover the entire range
-    X = np.arange(0, L/2, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 0.1 # set by what "looks good"
-
-    #create a narrow confining channel for 2D systems
-    if 0:
-        Z = Z_mag*np.cos(2*np.pi*X/L)
-    
-        #create washboard
-    elif corrugated == True:
-        Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
-
-    cmap=cm.coolwarm #_r
-
-    #alphs is the degree of transparency, again, set by what looks good.
-
-    #if 0:
-    cset = ax1.contourf(X, Y, Z, cmap=cmap,alpha=0.5)
-    #else:
[…]

### 2021-02-23 code/plot_landscape.py

@@ -138,7 +138,7 @@ if __name__ == "__main__":
     ax1.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(xp+1, yp-6),ha="left",va="center")
     
     ax1.annotate("", xy=(xp, yp+8), xytext=(xp, yp), arrowprops=dict(color='gray', shrink=0.05), ha="center")
-    ax1.annotate(r"$\mathrm{\vec{F}^{D}(t)}$",  xy=(xp+1, yp+8),ha="left")
+    ax1.annotate(r"$\mathrm{\vec{F}^{d}(t)}$",  xy=(xp+1, yp+8),ha="left")
 
     ax1.text(0.03,0.94,"(a)",transform = ax1.transAxes)
     ax2.text(0.03,0.94,"(b)",transform = ax2.transAxes)

### 2021-02-23 code/MD_colloid.py
found a problem with decifactor - was too big!

@@ -24,87 +24,77 @@ plt.rc('font', size=24)
 
 ##################################################################
 def brownian_distribution(parameters):
-    '''
+    '''calculates a series of normally distributed random numbers 
+
+    Required Parameters
+    parameters: dict
+    contains all constants of the simulation, notably the substrate period and barrier height AP
     '''
     mu, sigma = 0.0, 1.0 # mean and standard deviation
 
-    #temperature has units of force too, because of course it does
+    #scale the prefactor by 2 \eta kb T in simulation units    
+    #where 'temperature' has units of force
     kb_T = parameters['temperature']
 
+    #one force for every timestep
     timesteps = int(parameters['maxtime'])
     
     #use numpy's built-in function to generate a randomized force
     #do so in bulk for every timestep in the simulation
-    #scale the prefactor by 2 \eta kb T in simulation units    
     fy_rand = kb_T * np.random.normal(mu, sigma, timesteps)
 
     return fy_rand
     
-    #fx_rand = np.random.normal(mu, sigma, int(N_part*(N_part-1)))
     
 ##################################################################
 def landscape_force(y,parameters):
     '''landscape potential is equation (1) in the manuscript, 
+    U(y) = U0 cos(Np*2pi*y/L)
     while force is equation (5) - for now anyway
-
-    U(y) = U0 cos(Np*pi*y/L)
-
-    F_y = -dU/dy = -U0/period * sin(Np*2pi*y/L)
-
+    F_y  = -dU/dy = -U0/period * sin(Np*2pi*y/L)
     potential minima occur at U(y) = -U0, or cos(Np*2pi*y/L) = -1
     meaning Np*2pi*y/L = m pi, where m is odd
     
     Required Parameters
-    y: float
-    the location in the y-direction of the individual particle
+    y (float): location of particle
+    parameters (dict): all constants of the simulation, notably the substrate period and barrier height AP
 
-    parameters: dict
-    contains all constants of the simulation, notably the substrate period and barrier height F0
+    Optional arguments
+    none
     '''
 
     period = parameters['period']
-    F0 = parameters['F0']
+    AP = parameters['AP']
     
[…]

### 2021-02-24 code/MD_colloid.py
definitely fixed decifactor

@@ -90,25 +90,6 @@ def external_drive(time, parameters):
 
 
 #####################################################################
-def average_velocity(int_time, vy, avg_vy, parameters):
-    '''calculate the average velocity over 
-    a range of N timesteps, where N=decifactor 
-    Use all vy values, not just those 
-    saved during "writemovietime.  
-    '''
-
-    decifactor = parameters['decifactor']
-
-    avg_vy += vy
-            
-    if int_time % parameters['decifactor'] == 0: 
-        avg_vy /= decifactor
-        #print(int_time, avg_vy)
-        
-    return avg_vy
-
-
-#####################################################################
 def md_step(y, int_time, avg_vy, parameters, ft=0):
     '''
     Required Arguments:
@@ -471,9 +452,11 @@ def set_parameters():
     dict={}
 
     dict['dt'] = 0.1 #005 #timestep in simulation units
+
+    dict['freq'] = 0.01              #frequence of force osillation
     
     #integer time steps
-    dict['maxtime']=4000        #total time steps in simulation
+    dict['maxtime']=int(100/dict['freq'])        #total time steps in simulation
     dict['writemovietime']=1   #interval to write data to arrays for plotting
 
     dict['Sy']=36.5         #height of system
@@ -492,16 +475,15 @@ def set_parameters():
     #Brownian motion factor
     dict['temperature'] = 5.7*dict['AP']
     
-    dict['F_DC'] = 0.05 #0.1
+    dict['F_DC'] = 0.1
     dict['drop'] = dict['maxtime']   #integer timesteps to "ramp" the DC force
         
-    dict['decifactor'] = 1 #5000     #decimation factor integer timesteps to average force
+    dict['decifactor'] = 1      #decimation factor integer timesteps to average force - phasing out - overkill for this system
 
     #control the oscillating component of driving force
 
     #fig2
-    dict['F_AC'] = 0.07 #0.1              #amplitude of force oscillation
-    dict['freq'] = 0.01              #frequence of force osillation
+    dict['F_AC'] = 0.1 #0.1              #amplitude of force oscillation
     
     #parameters
     #dict['F_AC'] = 0.8              #amplitude of force oscillation
@@ -517,7 +499,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #figures 2 to 8
-    make_fig = 3
+    make_fig = 2
 
     parameters['filename']="fig%d.pdf"%(make_fig)
 
[…]

### 2021-02-24 code/MD_colloid.py
added a subset contour plot to fig 2 in order to see how the particle moves through the substrate

@@ -14,13 +14,73 @@ import numpy as np
 import math, sys
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
+import matplotlib.cm as cm
 
 from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
                                AutoMinorLocator)
+from mpl_toolkits.axes_grid.inset_locator import (inset_axes,
+                                                  InsetPosition,
+                                                  mark_inset)
+
 
 #set default font of plot
 plt.rc('font', size=24)
 
+##########################################################
+#ADD CONTOUR PLOT
+##########################################################
+def add_contour(ax,L,N): 
+    '''
+    Hardwired to color in the quasi1D potential to contain 
+    the particles in a trough.  
+    Can also add the washboard/corrugated substrate.
+
+    Required Arguments
+
+    Optional Arguments:
+
+    Adds the washboard in the y-direction.  
+    Hardwired for a single parameter set.    
+    '''
+
+    a_p = L/N
+
+    #assuming Tiare's trough system, so we won't want to cover the entire range
+    X = np.arange(0, 100, 0.1)
+    Y = np.arange(0, L, 0.1)
+    X, Y = np.meshgrid(X, Y)
+
+    Z_mag = 0.1 # set by what "looks good"
+
+    #create a narrow confining channel for multiparticle 2D systems
+    if 0:
+        Z = Z_mag*np.cos(2*np.pi*X/L)
+    
+        #create washboard
+
+    Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
+
+    #blue are minima, red are maxima
+    cmap=cm.coolwarm #_r
+
+    #alpha is the degree of transparency, again, set by what looks good.
+
+    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.5)
+
+    '''
+    ax.set_xlim(0, L/2)
+    ax.set_ylim(0, L)
+
+    ax.set_xlabel(r"x",labelpad=-20)
+    ax.set_ylabel(r"y",rotation='horizontal',ha='right',labelpad=-15)
+
+    ax.set_xticks([0,L/2])
+    ax.set_yticks([0,L])
+
+    ax.set_xticklabels(['0','L/2'])
+    ax.set_yticklabels(['0','L'])
+    '''
+    return 
 
 ##################################################################
[…]

### 2021-02-25 manuscript/manuscript_ajp_2020.tex
rewrote phase section

@@
 %The phenomena
-
 %\section{Colloidal Models}
@@
  %systems.
-
+ The model presented in this paper
+ resembles an overdamped driven pendulum. 
 %Numerical modeling of colloids can provide mechanistic insight
@@
 We describe
-our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
-We choose this model for its
-relevance to condensed matter systems
-and ease of simulation.
+our molecular dynamics model for a single particle in Section~\ref{sec:MD},
+The model
+closely resembles
+a damped driven pendulum,
+and is easy to simulate yet relevant
+to condensed matter systems.
 %In this section, we restrict our discussion to a single particle,
@@
 such as dusty plasmas, superconducting vortices and Josephson junctions.
-
 %Here we model the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
@@
 \label{sec:MD}
-
 We use a classical model for 
@@
 Particles are confined in a two-dimensional (2D) 
-simulation of area $A = L \times L$ where $L=36.5 a_0$
+simulation of area $A = L \times L$ where $L=46.\bar{6} a_0$
 where $a_0$ is a dimensionless unit of length.
@@
  Particles are subject an external time-dependent driving force
-$\vec{F}^{D}(t)$
+$\vec{F}^{d}(t)$
 applied parallel to the y-direction.
@@
 \begin{equation}
-  \vec{F}^{D}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
+  \vec{F}^{d}(t) = [F^{dc} + F^{ac} \sin(\omega t)] \hat{y},
     \label{eq:drive}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %because
@@
 with fluid particles \cite{Purcell1977}.
-In our model
-we assume 
+%In our model
+We assume 
 colloids are overdamped
--- i.e. colloids are suspended in a continuous viscous fluid
+-- suspended in a continuous viscous fluid
 that dissipates energy %at a rate
-such 
-that the particles do not accelerate.
-%that greatly impedes their motions.
-Energy dissipation from the fluid is modeled
-with a frictional force on particle with velocity $\vec{v}_i$ as
-%that removes energy from
-%the particles,
-%which we model as
-$\vec{F}^{drag}_i = -\eta \vec{v}_i$
-%proportional to the particle velocity 
-with a friction coefficient $\eta$
-proportional to the fluid viscosity.
-We discuss friction models for
-spheres moving through fluids in 
-%Section~\ref{sec:problems}
-Exercise~\ref{ex:reynolds}. %for more information
-%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{landscape.pdf}
-\caption{
-  Schematic of the simulation
-  of a single particle
-  driven across a washboard potential
-  energy landscape.
-  The period of the landscape is $\lambda = L/N_p$,  
-  %is marked in red,
-  where $N_p = 3$.  
-  The force due to the landscape %$\vec{F}^l$
-  is calculated from the gradient of the potential
-  energy 
-  $\vec{F}^l = -\nabla U(\vec{r})$.
-  (a) View of the $x-y$ plane. %of the simulation
-  The time-dependent applied driving force $\vec{F}^D$
-  is parallel to the y-axis.
-  The landscape is shown with a contour plot,
-  with maxima in the potential energy marked in red
-  and minima marked in blue.
-  A particle is shown in the region between minima and maxima
-  subject to competing forces of the landscape and applied driving force.
-  (b) The potential energy function
-  along the y-axis $U_l(y)$.  
-  The particle in (a) is shown at the same $y-$position.
-  The slope of $U_l(y)$ is the 
-  magnitude of force $\vec{F}^l$. %is calculated
-  %as the slope of this function,
-  %directed along the $y-$direction in panel (a).
-  }
-\label{fig:landscape0}
-\end{figure}
-\end{center}
+so the particles do not accelerate.
 Newton's second law for an individual particle
@@
 %to
-The overdamped equation of motion for an isolated particle is
+The overdamped equation of motion for
+the velocity $\vec{v}_i$ of 
+an isolated particle is
 %solved for velocity 
 \begin{equation}
-  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{D}(t).
+  \eta \vec{v}_i = \vec{F}^l_{i}(\vec{r}_i) + \vec{F}^{d}(t).
     \label{eq:motion}
 \end{equation}
-with  $\eta = 1$ in units of $v_0 / F_0$. 
-%(see Table~\ref{tab:1}).
-%and Exercise~\ref{ex:reynolds}.
-%In %Section~\ref{sec:problems}
-%Exercise~\ref{ex:n2l}
-%we invite the reader to confirm this result.
+with friction coefficient $\eta = 1$ in units of $v_0 / F_0$. 
+The term $-\eta \vec{v}_i$
+is a drag force used model 
+energy dissipation from the fluid. 
+%that greatly impedes their motions.
+%proportional to the particle velocity 
+%with a $\eta$
+%proportional to the fluid viscosity.
+We discuss friction models for
+spheres moving through fluids in 
+%Section~\ref{sec:problems}
+Exercise~\ref{ex:reynolds}. %for more information
+%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
+
 The equation of motion provides a direct calculation of the velocity
-of an individual particle from its location $\vec{r}_i$ %in the simulation
+of an individual particle from location $\vec{r}_i$ %in the simulation
 and the simulation time.
-
 The molecular dynamics simulation is controlled by a $for()$ loop
@@
 %$t_i$.
-Each integer time step interval %$t_{i+1}-t_i$
-represents a simulation time of $\Delta t$ 
-simulation units $\tau$.  %as described in Table 1
+%Each integer time step interval %$t_{i+1}-t_i$
+%represents a simulation time of $\Delta t$.
+%simulation units $\tau$.  %as described in Table 1
 At each time step
@@
 \end{equation}
-for a small time step $\Delta t = 0.01 \tau$.
+for a time step $\Delta t = 0.1 \tau$.
 In %Section~\ref{sec:problems}
@@
 %
-
-\begin{table}[h!]
+%------------------------------------------------------------------
+\begin{figure} % [h!]
+\centering
+\includegraphics[width=\columnwidth]{landscape.pdf}
+\caption{
+  Schematic of the simulation of a single particle
+  driven across a washboard potential energy landscape.
+  %The period of the landscape is $\lambda = L/N_p$,  
+  %is marked in red,
+  %where $N_p = 3$.  
+  %The force due to the landscape %$\vec{F}^l$
+  %is calculated from the gradient of the potential energy 
+  %$\vec{F}^l = -\nabla U(\vec{r})$.
+  (a) View of the $x-y$ plane. %of the simulation
+  The time-dependent applied driving force $\vec{F}^d$
+  is parallel to the y-axis.
+  The landscape is shown with %a contour plot,
+  %with
+  maxima in the potential energy marked in red
+  and minima marked in blue.
+  A particle is %in the region between minima and maxima
+  subject to competing forces of the landscape and applied driving force.
+  (b) The potential energy function
+  along the y-axis $U_l(y)$.  
+  The particle in (a) is shown at the same $y-$position.
+  The slope of $U_l(y)$ is the 
+  magnitude of force $\vec{F}^l$. 
+  }
+\label{fig:landscape0}
+\end{figure}
+%\section{Results}
+%\label{sec:results}
+% We demonstrate how a single particle (Sec.~\ref{sec:one})
+% and many particles
+% move (Sec.~\ref{sec:sync})
+% in response to this applied force in a variety of environments.
+% In Sec.~\ref{sec:kink} we set $F^{dc}$
+% to zero and track the motion
+% of a high density area of a particle chain
+% (i.e. kink dynamics).
+ %The driving force does add energy into the system, and some of it is lost.
+%
+\section{Mode-locking of a single particle}
+% In subsection headings, only the first word is capitalized.
+\label{sec:one}
+
+Here we drive 
+a single particle %on this landscape
+%responds to the applied driving force
+%by moving
+across the landscape. %maxima
+%to explore the qualitative behavior
+%to characterize its motion.
+%synchronized with 
+%the period of $F^d(t)$.
+%applied driving force.
+%along the y-direction
+%({\it redundant, just refer back to eq. in Model?})
+%and $V_{0y}=0.2$.
+%This is illustrated in Fig.~\ref{fig:1}(a) where
+%the red (blue) regions show local maxima (minima).
+%
+The numerical implementation of the landscape 
+is calculated with Eq.~\ref{eq:ysubstrate} as 
+\begin{equation}
+  \label{eq:force}
+  F^l_y(y) = -A_{p} \sin{(2 \pi y / \lambda)} 
+\end{equation}
+where the force is scaled with parameter $A_{p} = 2\pi U_0/\lambda$.
+In this section we fix the landscape parameters
+to $A_{p} = 0.1 F_0$ %force units
+with $N_p=20$ minima %in the landscape
+corresponding to a spatial period $\lambda = 2.3 a_0$.
+The competition between the driving force and landscape potential
+can produce a variety of hopping patterns in the particle motion. 
+%In Fig.~\ref{fig:0}
+%reaching a minimum position
+%of $y/\lambda = 1$
+%over the total period $T = 100$.
+%In Fig. ~\ref{fig:0}
+%the average displacement during one time period is a single wavelength
+%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
+%single dc case with figure
+%dc_current 0.01
+%ac_current 0.05
+%ac_frequency 0.01
+%fp_y 0.1
+%
+The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
+control the rate and distance a  particle moves 
+forward and backward in the landscape.
+%Here we explore one case in the low frequency regime,
+When $F^d(t) > A_p$, a particle can 
+overcome the barrier height of the landscape,
+and 
+the particle hops between minima in the energy landscape.
+When the driving frequency is low,
+as in Fig.~\ref{fig:0},  
+the driven particle %adjusts
+moves %across %its motion to traverse
+%the periodic landscape
+in a pattern 
+with the same frequency 
+%with the same rhythm as 
+as the time-dependent force $F^d(t)$,
+yet is modulated by the landscape period.
+We explore changes in frequency and $F^{ac}$ 
+in Ex.~\ref{ex:parameters}.
+Here we vary $F^{dc}$ 
+while holding the remaining parameters fixed.
+%------------------------------------------------------------------------
+\begin{table} %[h!]
 \centering
 \caption{Simulation parameters and units with comparable
-  experimental values~\cite{Juniper2015}.}
+  experimental values~\cite{Juniper2015,Juniper2017}.}
   %Blanks indicate you are a moron
@@
 force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
-time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
+time &  $ \tau = \eta a_0 / F_0 $ & $ \tau \sim 3 sec$\\
 velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
-driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\ %frequency 0.75 Hz
-viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
+%driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\ %frequency 0.75 Hz
 %juniper uses water–ethanol mixture
-substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
-substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 25 k_B T \sim 2 J$ \\
+substrate period & $\lambda = 2.3 a_0$ & $\lambda = 3.5 \mu m$ \\
+substrate amplitude\footnote{Our substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of particles.} & $A_p = 0.1 F_0$ & $U_0 = 25 k_B T \sim 1 J$ \\ %$U_0 = 0.037 E_0$
 %they have 75 k_B T as the bottom of -U_0
 %A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
-temperature & $T_0 = 0$ \footnote{to learn more about the effects
-  of temperature on this simulation
-  see Ex.~\ref{ex:brownian} where we study the limit
-  $U_0 \sim k_B T$.} & $T \sim 300K $ \\
-
+temperature\footnote{To learn more about the effects
+  of temperature on this simulation see Ex.~\ref{ex:brownian} where we study 
+  $U_0 \sim k_B T$.} & $T_0 = 0$  & $T \sim 290K $ \\
 %FROM JUNIPER2015
@@
 %~2\times10^9 beads per 30 mg -> 1.5 \times 10^-11 g, 15 ng
-
 \end{tabular}
@@
 
-%\section{Results}
-%\label{sec:results}
-% We demonstrate how a single particle (Sec.~\ref{sec:one})
-% and many particles
-% move (Sec.~\ref{sec:sync})
-% in response to this applied force in a variety of environments.
-% In Sec.~\ref{sec:kink} we set $F^{dc}$
-% to zero and track the motion
-% of a high density area of a particle chain
-% (i.e. kink dynamics).
- %The driving force does add energy into the system, and some of it is lost.
-%
-\section{Mode-locking of a single particle}
-% In subsection headings, only the first word is capitalized.
-\label{sec:one}
-
-Here we drive 
-a single particle %on this landscape
-%responds to the applied driving force
-%by moving
-across the landscape %maxima
-to characterize its motion.
-%synchronized with 
-%the period of $F^D(t)$.
-%applied driving force.
-%along the y-direction
-%({\it redundant, just refer back to eq. in Model?})
-%and $V_{0y}=0.2$.
-%This is illustrated in Fig.~\ref{fig:1}(a) where
-%the red (blue) regions show local maxima (minima).
-%
-The numerical implementation of the landscape 
-is calculated with Eq.~\ref{eq:ysubstrate} as 
-\begin{equation}
-  \label{eq:force}
-  F^l_y(y) = -A_{p} \sin{(2 \pi y / \lambda)} 
-\end{equation}
-where the force is scaled with parameter $A_{p} = 2\pi U_0/\lambda$.
-In this section we fix the landscape parameters
-to $A_{p} = 0.1 F_0$ %force units
-with $N_p=20$ minima %in the landscape
-corresponding to a spatial period $\lambda = 1.825 a_0$.
-The competition between the driving force and landscape potential
-can produce a variety of hopping patterns in the particle motion. 
-%In Fig.~\ref{fig:0}
-%reaching a minimum position
-%of $y/\lambda = 1$
-%over the total period $T = 100$.
-%In Fig. ~\ref{fig:0}
-%the average displacement during one time period is a single wavelength
-%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
-%single dc case with figure
-%dc_current 0.01
-%ac_current 0.05
-%ac_frequency 0.01
-%fp_y 0.1
-%
-The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
-control the rate and distance a  particle moves 
-forward and backward in the landscape.
-[edit and move:] The addition of an oscillating force
-can lead to interference effects
-that create stepped force-velocity curves.
-Useful model - essentially an overdamped driven pendulum -
-under certain parameters.
-The steps occur
-due to the phase locking between lattice substrate
-and applied driving force.
-Step widths depend on AC drive.
-Discrete modes.
-%Shapiro steps wash out to sloped regions at
-%high vortex numbers,
-%so what is the analog in my system?
-%need to sweep through more parameters to find and report the flat regions
-%not fully phase locked.
-
-%In Fig.~\ref{fig:0} 
-The driven particle %adjusts
-moves across %its motion to traverse
-the periodic landscape with the same rhythm as 
-the applied time-dependent force $F^D(t)$.
-When $F^D(t) > A_p$, a particle can 
-overcome the barrier height of the landscape,
-and 
-the particle hops between minima in the energy landscape.
-%
 In Fig.~\ref{fig:0}(a)
-we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
+we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
 as a function of time with
 %The time independent
-constants $F^{dc}=0.1$, 
-$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
+constants $F^{dc}=0.07$, 
+$F^{ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
 The temporal period of the driving force is
-$T = 1/f = 100 \tau$.
+$T = 1/f = 100 \tau$ and 
+the simulation has a maximum
+time of $400 \tau$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$.
-In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
+In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %since $\sin{(0)}=0$.
-We mark the maxima of $F^{ac}(t)$
-with the
-vertical dashed lines %in panels (a) and (b)
--- i.e. $\sin{(\omega t)} = 1$.
-%
-%
+%We mark the maxima of $F^{ac}(t)$
+%with the
+%vertical dashed lines %in panels (a) and (b)
+%-- i.e. $\sin{(\omega t)} = 1$.
 %with the initial driving force at is minimum value 
-%$F^D(0) = F^{dc}$. 
+%$F^d(0) = F^{dc}$. 
 %
@@
 we show the $y-$position of the particle
-as a function of time.
-We 
-normalize $y$ by $\lambda$ %, the spatial period of the potential
-to show  particle motion between substrate minima.  
+as a function of time,
+where we 
+normalize $y$ by $\lambda$.
+%to show  particle motion between substrate minima.  
 The initial particle position is $y = 0 $. %1 a_0$,
 %where the $F^l$ is negative.
-%JUST BECAUSE
 %causing the particle to move to
 %a landscape minima at the start of the simulation.
-As the driving force increases,
-%the effects of the landscape become less obvious,
-the motion of the particle
-synchronizes with the driving period $T$.
-We measure 
-average particle velocity $\langle{v}_y\rangle$
-as the displacement %$\Delta y = y(t_0+T) - y(t_0)$
-over the period of the driving force.
 The particle moves
 in the positive y-direction
-through $\Delta y = 2 \lambda$ over the time period $T$,
+through $\Delta y = \lambda$ over time $T$,
 with 
 the average velocity 
-$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
-[TODO: update description!]
-The horizontal dashed lines
-coincide with the condition the particle is at a substrate minima
-where substrate force  $F^l = -A_p$,  
-i.e. $\sin{(\pi y / \lambda)} = 1$.
- %or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
-%Once the particle motion
-%coincides with the applied drive,
-%indicating synchronization,
-The particle synchronizes its motion such that the 
-edriving force is maximum when the landscape 
+$\langle {v}_y \rangle = \lambda f$. % where $T = 1/f$.
+%For these parameters,
+The inset of Fig.~\ref{fig:0}(b)
+shows $y$ %vs. time
+over one period $100\tau < t < 200 \tau$
+with 
+the contour plot described
+in Fig.~\ref{fig:landscape0}(a).
+The motion is synchronized so the 
+driving force is maximum when the landscape 
 force is minimum,
-as indicated %with the coincidence of 
-with the intersection of
-vertical and horizontal lines.  
-%i.e. the particle position $y/\lambda$.  
-The slope of $y/\lambda$
-is proportional to the net force on the particle.
-This can be seen in 
-Fig.~\ref{fig:0} %we demonstrate this relationship,
-where local extrema appear in $y/\lambda$
-when $F_{D}(t) \approx 0 $. 
-\begin{center}
-\begin{figure}[h!]
+as shown by the coincidence of the
+steep slope in 
+$y/\lambda$ 
+and maxima in $F^d(t)$.
+When $F^d(t)$ is large 
+the particle moves across the substrate minima,
+shown in blue with the contour plot.
+The slope of $y/\lambda$ is zero twice
+during a driving period,
+indicating zero
+forward motion 
+due to a coincidence of negative
+driving force and motion over the landscape maxima.
+%------------------------------------------------------------------------
+%----------------------------------------------------------------
+\begin{figure} %[h!]
 \centering
 \includegraphics[width=\columnwidth]{fig2.pdf}
-\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
+\caption{(a) The applied driving force $F^d(t)$ % (Eq.~\ref{eq:drive}).
+  with parameters $F^{dc} = 0.07$, $F^{dc} = 0.07$ and $f=0.01$.
   %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
@@
   normalized by the period of the substrate $\lambda$.
+  The substrate strength is $A_p=0.1$.
   %as a function of time
+  The inset of (b) shows
+  the $y-$position
+  through the second period $100\tau<t<200\tau$
+  against the contour plot depicting
+  the landscape potential described in Fig.~\ref{fig:landscape0}(a).
   }
@@
 \end{figure}
-\end{center}
-
-%{\it NOTE: YOUR $A_P$ VALUES ARE TOO SMALL TO MAKE THIS A MEANINGFUL PHASE VARIALBE.
-YOU NEED TO SCALE WITH THE DRIVE FORCE AMPLITUDES.
-THIS CAN ALSO HELP YOU UNDERSTAND WHY YOU ARE GETTING BIG JUMPS IN POSITION COMPARED TO JUNIPER ET AL.
-YOU ARE WORKING IN THE WEAK SUBSTRATE LIMIT.
-also insert plots of $y/\lambda$ over a single period with the phase plots - like juniper}
-  It is useful to compare
+
+To explore the possible hopping patterns,
+we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$.
+%to illustrate
+%distinct oscillation modes. % as a function of $F^{dc}$.
+%as shown
+In Fig.~\ref{fig:1} 
+we increase $F^{dc}$ in increments of $0.001 F_0$
+%for $10^5$ simulation timesteps
+and 
+measure the average velocity $\langle v_y \rangle $ 
+as a function of $F^{dc}$.
+We perform the sweep for a non-oscillatory drive $F^{ac} = 0.0$.
+With no oscillating component of the driving force,
+  the force-velocity relationship is monotonically increasing
+  above the depinning threshold $F^c$ such that
+  \begin{equation}
+    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}.
+  \end{equation}
+  The critical force $F^c$ is equal to the maximum substrate force
+  $A_p$ so the applied driving
+  force can move a particle over a substrate barrier.
+  The addition of an $ac$ drive leads
+  to the formation of modes.
+  A mode is a periodic pattern of hops
+  with a constant average particle velocity, $\langle {v}_{y} \rangle$
+  over a range of driving forces $F^{dc}$.
+  In Fig.~\ref{fig:1}
+  we sweep $F^{dc}$
+  with $F^{ac} = 0.07$ and $f=0.01$.
+%the average velocity of the particle
+%is constant 
+%despite the overall magnitude
+%of $F^{dc}$.
+Each step represents a different pattern of hops
+between substrate minima
+performed by the particle
+due to the landscape confinement.  
+At %this occurs at 
+low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
+Since 
+$A_p$ is large compared to the extrema of $F^{d}(t)$,
+the particle oscillates back and forth
+in a single minima with no net velocity.
+%We plot the results in Fig.~\ref{fig:1} for 
+%  The modes appear as 
+%  discrete steps in $\langle v_y \rangle$ %occur because
+%  across a range of $F^{dc}$.
+%  On each of the first four modes,
+%  we mark a values of $F^{dc}$ to illustrate in Fig.~\ref{fig:phase}.
+At higher $F^{dc}$ the particle velocity 
+$\langle v_{y} \rangle$ increases in steps of uniform height,
+$\langle v_{y} \rangle = n \lambda f$,
+where $n$ is an integer.
+The step width is non-linear
+and depends on the strength of $F^{ac}$
+as a Bessel function 
+for this landscape potential \cite{Reichhardt2000,Juniper2017}.
+Known at Shapiro steps,
+these can have a variety of
+interesting patterns
+such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
+%We note the individual steps
+%are not strictly horizontal 
+%since particles move continuously
+%through the landscape, so changes in $F^{dc}$
+%will create linear changes in 
+%net particle displacement that are observable
+%within a single step.
+\begin{figure} %[h!]
+\centering
+\includegraphics[width=\columnwidth]{fig3.pdf}
+\caption{Average particle velocity  $\langle v_{y} \rangle$
+  as a function of $F^{dc}$, 
+  the constant parameter of $F^d(t)$ defined in Eq.~\ref{eq:drive}.
+  We fix
+  $F^{ac}=0.0$ (blue) and 
+  $F^{ac}=0.07$ (orange) with $f = 0.01$ 
+  as in Fig.~\ref{fig:0}.
+  Each of the first four steps
+  has a marked value of $F^{dc}$,
+  indicating a system
+  plotted in Fig.~\ref{fig:phase}.
+}
+\label{fig:1}
+\end{figure}
+%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
+%of the landscape,
+%and $f = 0.01$ cycles per time unit.
+%This synchronization
+%of the particle velocity can be measured
+%in terms of the landscape period.
+%Phase locked steps occur for average displacements integer
+%multiples of the substrate period $n\lambda$.
+%\subsection{Phase plots}
+%  \label{ex:phase}
+
+  To study synchronization patterns, 
+  it is useful to compare
   mode-locked quantities %periodic signals
-  in a two dimensional phase plot
-  to distinguish fully and partially synchronized
-  behavior.  
+  in a two dimensional phase plot. 
   In a non-driven system, an appropriate
   phase space is particle velocity $v_y$ versus position $y$.  
-  In a system driven parallel to the $y-$direction,
+  For a particle driven parallel to the $y-$direction,
   %the particle velocity and position increase
@@
     %(y mod \lambda) / \lambda
-    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
+    \phi(t) = (y(t)-\langle v_y \rangle t)/\lambda
   \end{equation}
-  centered about the average particle velocity $\langle v_y \rangle$
+  centered about the average particle displacement $\langle v_y \rangle t$
   and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  In phase diagrams we plot $\phi(t)$ %phase
-  versus the phase velocity 
+  For clarity we have dropped a prefactor of $2\pi$ 
+  to compare $\phi(t)$ to $\lambda$.
+  %In phase diagrams we plot $\phi(t)$ %phase
+  %versus
+  The phase velocity is
   \begin{equation}
     %(y mod \lambda) / \lambda
-    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
+    \dot{\phi}(t) =(v_y(t)-\langle v_y \rangle) /\lambda.  % 2\pi
   \end{equation}
+  With no landscape force, 
+  the phase velocity will be zero when $F^d(t) = F^{dc}$.
   %Juniper %REF 53
@@
   so a 1:1 mode appears as a circle or oval. 
-  Nodes appear in the oval 
+  Nodes appear %in the oval 
   for higher modes,
@@
   or other recognizable patterns.
-  A system that is not fully phase locked
-  will apppear as an unclosed loop.
+  A system that is nearly phase locked
+  will appear as an unclosed loop.
   Such quasiperiodic systems are
-  not fully synchronized.
+  not fully synchronized
+  so the position-velocity relationship
+  shifts in time.
+  In Fig.~\ref{fig:phase}, 
+  all cases exhibit some line thickening, 
+  indicating the particle location and velocity
+  are not fully synchronized,
+  although this can be tuned by
+  calculating $\langle v_y \rangle$ over
+  shorter time ranges.
   %and the shifts in phase space represent
   %small changes in system behavior.
-  With a long simulation time,
-  a quasiperiodic phase diagram
-  fills the plotting region due to the gradual shift
-  in the velocity-position relationship.
+  %With a long simulation time,
+  %a quasiperiodic phase diagram
+  %fills the plotting region due to the gradual shift
+  %in the velocity-position relationship.
   %with a frequency generator,
@@
   we plot $\dot{\phi}(t)$ versus $\phi(t)$
-  for increasing substrate amplitude $A_p$.
-  We fix the driving force with parameters
-  $F^{dc} = 0.1$ and frequency $f = 0.01$ and $F^{ac} = 0.2$.
-  In Fig.~\ref{fig:phase}(a)
-  there is no substrate ($A_p = 0.0$)
-  and the phase plot is a closed oval
+  for increasing %substrate amplitude $A_p$.
+  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
+  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
+  In Fig.~\ref{fig:phase}(a) with
+  $F^{dc} = 0.04$
+  the phase plot is a small closed oval
   centered at
-  $(\phi,\dot{\phi})=(10,0)$
-  with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
-  and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
-  [insert analysis.]
-  As the force from the substrate
+  $(\phi,\dot{\phi})=(0.1,0)$.
+  A small tail appears
+  due to the initial transient
+  motion of the particle.
+  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
+  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
+  The particle is confined in a single
+  substrate minima,
+  and has no net velocity.
+  In Fig.~\ref{fig:phase}(b)
+  with $F^{dc} = 0.07$
+  the phase loop is a symmetric trianglar shape,
+  indicating a 1:1 match between
+  particle motion and velocity consistent with 
+  Fig.~\ref{fig:0}(a).
+  The maximum $\dot{\phi}$ %with a 1:1 mode locking,
+  occurs at $\phi \sim 0.4$,
+  and maximum $\phi$ occurs
+  when $\dot{\phi} \sim 0$.
+
+  %The dynamical properties are asymmetric,
+  %with three nodes in the positive $\dot{\phi}$ values.
+  %[insert analysis.]
+  As $F^{dc}$ %the constant driving force 
   increases,
   nodes form in the phase diagram
-  and the motion becomes quasiperiodic
+  that occur due to repeated values
+  of $\dot{\phi}$ over multiple phase positions.
+  The motion becomes quasiperiodic
   so the loops in phase space do not fully overlap.
-  In Fig.~\ref{fig:phase}(b)
-  $A_p = 0.05$
-  the spatial properties are similar to
-  those in $A_p = 0.0$
-  with 
-  $(\phi,\dot{\phi})=(10,0)$
-  with a semimajor axis of $\Delta \phi = 20$.
-  The dynamical properties
-  are asymmetric,
-  with three nodes in the positive $\dot{\phi}$ values.
-  The thickening of the line
-  indicates the system is not fully synchronized.
-  [insert analysis.]
-  As the substrate
-  force becomes larger,
-  $\phi$ shifts to lower values
-  and $\dot{\phi}$ to positive values,
-  indicating
-  the particle can only move 
-  backward over a short distance.
   In Fig.~\ref{fig:phase}(c)
-  $A_p = 0.1$
-  the phase properties are similar to
-  those in $A_p = 0.05$,
-  the three nodes have 
-  increased asymmetry in both phase variables 
-  $(\phi,\dot{\phi})$.
-  The nodes deepen,
-  indicating [insert analysis.].
+  with $F^{dc} = 0.1$
+  two nodes form.
+  The particle moves across $2\lambda$
+  during one time period.
   In Fig.~\ref{fig:phase}(d)
-  $A_p = 0.2$
-  the pattern shifts
-  to two nodes,
-  [indicating change analysis].
-  In Fig.~\ref{fig:phase}(e)
-  $A_p = 0.25$
-  the system returns to a nodeless
-  orbit,
-  shaped like a triangle [because why?]
-  In Fig.~\ref{fig:phase}(f)
-  $A_p = 0.3$
-  the particle is trapped between substrate minima,
-  and traces out a small unclosed
-  orbit in phase space [because...]
-  The phase velocity is near zero
-  throughout the motion -
-  [comment on initial conditions]
-  \begin{center}
-    \begin{figure}[h!]
+  with $F^{dc} = 0.125$
+  three nodes form as the particle moves across $3\lambda$.
+    \begin{figure} %[h!]
       \centering
       \includegraphics[width=\columnwidth]{phase.pdf}
+      %\vspace*{-3cm}
       \caption{
-        Phase plot of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0}.  $F^{ac} = 0.2$ and $A_p = $ (a) $0.0$, (b) $0.05$, (c) $0.1$, (d) $0.2$, (e) $0.25$ and (f) $0.3$.
-        [first 100 timesteps removed to reduce transients]
-      }
+        Phase plot of a particle with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
+        in Fig.~\ref{fig:1}.%, (e) $0.25$ and (f) $0.3$.
+      The other parameters
+      are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
+      as Fig.~\ref{fig:0}.}
       \label{fig:phase}
     \end{figure}
-  \end{center}
-
-To explore the possible hopping patterns,
-we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$
-to illustrate
-distinct oscillation modes. % as a function of $F^{dc}$.
-A mode is a periodic pattern of hops
-with a constant average particle velocity, $\langle {v}_{y} \rangle$
-over a range of driving forces $F^{dc}$.
-%as shown
-In Fig.~\ref{fig:1} 
-we keep $F^{dc}$ constant
-for $10^5$ simulation timesteps
-and 
-measure the average velocity $\langle v_y \rangle $ 
-as a function of $F^{dc}$,
-with $F^{ac} = 0.05$, $f=0.01$, and the landscape %force $\vec{F}^{l}$
-shown in Fig.~\ref{fig:0}.
-%We plot the results in Fig.~\ref{fig:1} for 
-The modes appear as 
-discrete steps in $\langle v_y \rangle$ %occur because
-across a range of $F^{dc}$,
-
-%the average velocity of the particle
-%is constant 
-%despite the overall magnitude
-%of $F^{dc}$.
-Each step represents a different pattern of hops
-between substrate minima
-performed by the particle
-due to the landscape confinement.  
-In Fig.~\ref{fig:1} at %this occurs at 
-low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
-Since 
-$A_p$ is large compared to the extrema of $F^{D}(t)$,
-the particle oscillates back and forth
-in a single minima with no net velocity.
-At higher $F^{dc}$ the particle velocity 
-$\langle v_{y} \rangle$ increases in steps of uniform height,
-$\langle v_{y} \rangle = n \lambda f$,
-where $n$ is an integer.
-The step width is non-linear 
-and can have a variety of
-interesting patterns
-such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
-We note the individual steps
-are not strictly horizontal 
-since particles move continuously
-through the landscape, so changes in $F^{dc}$
-will create linear changes in 
-net particle displacement that are observable
-within a single step.
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{fig3.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$
-  as a function of $F^{dc}$, 
-  the constant parameter of $F^D(t)$ defined in Eq.~\ref{eq:drive}.
-  We fix
-  $F^{ac}=0.0$ (blue) and 
-  $F^{ac}=0.05$ (orange) with $f = 0.01$ 
-  as in Fig.~\ref{fig:0}.
-  {TODO: with these parameters, the steps are fractional!}
-}
-\label{fig:1}
-\end{figure}
-\end{center}
-%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
-%of the landscape,
-%and $f = 0.01$ cycles per time unit.
-%This synchronization
-%of the particle velocity can be measured
-%in terms of the landscape period.
-%Phase locked steps occur for average displacements integer
-%multiples of the substrate period $n\lambda$.
-%\subsection{Phase plots}
-%  \label{ex:phase}
-
-We explore a range of parameters in Ex.~\ref{ex:parameters}
-where 
-we perform this sweep for several values
-of $F^{ac}$ including the limiting case that the applied force
-is a constant value.
-When $F^{ac} = 0$, no steps appear
-in the $\langle v_y \rangle $ vs $F^{dc}$ curve. 
-When $F^{dc} - F^{ac} < -A_p$ the particle
-moves in the negative y-direction 
-during part of the cycle.
-%We examine
-The period of the substrate
-can be used to control the
-net velocity of the dc driven particle,
-and the applied ac drive can cause mode-locking
-which appears as non-linear 
-steps in the force-velocity relationship.
 
@@
 with parameter changes in Ex.~\ref{ex:parameters}.
-Methods to visualize the dynamics of the particle motion
-are in Ex.~\ref{ex:animation}.
+%Methods to visualize the dynamics of the particle motion
+%are in Ex.~\ref{ex:animation}.
 %In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
@@
 \label{sec:problems}	% You can label sections for reference
-
 %\begin{enumerate}
@@
 
+  %viscosity coefficient & $\eta = F_0 \tau / {a_0}^2 $ & $\eta \sim 10^{-3}$ Pa-s \\
+  To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s \cite{Volpe2013}.
+  %or $9 \times 10^{-8} kg/s$ \cite{Juniper2017}.
   {\bf Using reasonable values for the
@@
  % %Likewise
- % To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s 
  % since 
@@
   %Likewise
-  the liquid density $\rho$ varies with temperature
-  with $\rho \sim 10^3$ kg/cm$^3$ a reasonable
+  the liquid density %$\rho$ varies with temperature
+  %with
+  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
   first order approximation
@@
   particles with low Reynolds numbers.
-  The mass of the
-  typical experimental colloid particle is $15$ picograms,
+  The mass of a
+  typical colloid particle is $15$ picograms,
   leading to a momentum relaxation time
@@
   {\bf Confirm for the values listed in Table ~\ref{tab:1},
-  the momentum relaxation time is 
-  $m/\gamma \approx 0.5 ~\mu$s. }
+  the momentum relaxation time is }
+  $m/\gamma \approx 0.5 ~\mu s$.
 
@@
   {\bf show that a particle confined to a landscape exerting force
-  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
+  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^d(t)$
   can be modeled with the equation of motion described in 
@@
 
-  The Euler method can be applied to non-linear
-  equations effectively if the time step $\Delta t$
+    The Euler method can be applied to
+    calculate reasonable numerical solutions to 
+    non-linear
+    equations if the time step $\Delta t$
     is kept sufficiently small \cite{Newman}.
-  In our simulations we use the timestep $\Delta t = 0.001$,
-  but we find for a single particle
-  we can just as easily used 
-  %examine 
-  %for
-  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
-  over the same maximum time
-  (i.e. decrease the overall simulation time and sampling rate)
-  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
-  This is due to the linear nature of the solution
-  for an isolated particle.
-  %How to the motions of the particle compare when the timestep
-  %becomes large?
-  %[UPDATE]
-  {\bf Demonstrate the simulation timestep 
-  can be large
-  with no change to the overall physics
-  in the motion of a single particle.}
-  You will need to modify the maximum
-  simulation time, and the frequency of data saved for plotting purposes.
-
-  Interaction with neighboring particles
-  makes a small timestep essential for molecular dynamics simulations.
-  Since particle-particle interactions are typically non-linear,
-  the interaction force changes significantly over small distances,
-  making this simulation a unique
-  exception to typical simulation timesteps.
-  %{\it small timesteps matter a great deal when particle interactions
-  %  are included in the model.  I have demonstrated that
-  %  without particle interactions we can increase the timestep
-  %with no penalty, so this isn't a very interesting problem.}
-  %FOLLOW UP WITH THIS!
-  %Because we are performing molecular dynamics
-  %for a single particle on a smooth potential energy landscape,
-  %we use a large simulation time step of 
-  %$\Delta t = 0.01$.  %In Sec.~\ref{sec:sync},
-  %we decrease the time step
-  %to treat multiple particle interactions.
-
+    %but it is an uncommon choice.
+    In our simulations we use the timestep $\Delta t = 0.1$
+    and find no change in the solution
+    when we decrease the timestep to smaller values.
+    In simulations
+    including many interacting particles,
+    a small
+    timestep is essential for accurate models.
+    Particle-particle interactions are typically non-linear,
+    so the interparticle force changes significantly over small distances.
   Often molecular dynamics algorithms 
@@
   %\item
+
   \subsection{Brownian motion}
@@
   in the model.
-  In Fig.~\ref{fig:brownian},
-  we demonstrate the transition
-  from pinned to hopping
-  in 
-  %Measure the position vs. time
-  a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.
   %The crossover
@@
   %Reproduce these results.  
-  \begin{center}
-    \begin{figure}[h!]
+    \begin{figure} %[h!]
       \centering
@@
     \end{figure}
-  \end{center}
+
   In Fig.~\ref{fig:brownian}
@@
   and can be observed in experiments.
-  [explore]
+  %[explore]
   %and could be included
@@
   In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
-  do not match the temporal period of $F^D(t)$
+  do not match the temporal period of $F^d(t)$
   due to the high frequency.
@@
   the particle would cease forward motion.
-  \begin{center}
-    \begin{figure}[h!]
+    \begin{figure} %[h!]
       \centering
@@
     \end{figure}
-  \end{center}
   %In Fig.~\ref{fig:hops}
@@
   The number of forward steps also increases
-  due to the increased total positive amplitude of $F^D(t)$.
+  due to the increased total positive amplitude of $F^d(t)$.
   In Fig.~\ref{fig:hops_back}(a) 
@@
 
-  \begin{center}
-    \begin{figure}[h!]
+    \begin{figure} %[h!]
       \centering
@@
     \end{figure}
-  \end{center}
 
@@
   with frequency $f=0.01$.
-  With no oscillating component of the driving force,
-  the force-velocity relationship is monotonically increasing
-  above the depinning threshold $F^c$ such that
-  \begin{equation}
-    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}.
-  \end{equation}
-  The critical force $F^c$ is equal to the maximum substrate force
-  $A_p$ so the applied driving
-  force can move a particle over a substrate barrier.
-  The particle does not phase lock since there is no periodicity to $F^D(t)$,
+
+  The particle does not phase lock since there is no periodicity to $F^d(t)$,
   but does exhibit undulations in $\langle v_y \rangle$
@@
   Between $0.3< F^{dc}<0.5$ the system exhibits phase locked steps.
-    \begin{center}
-    \begin{figure}[h!]
+    \begin{figure} %[h!]
       \centering
-      \includegraphics[width=\columnwidth]{{fig9_sweep_FDC_vs_vx}.pdf}
+      \includegraphics[width=\columnwidth]{{fig7}.pdf}
       %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
@@
         $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
-        $F^{ac}=0.0$ (blue) and $F^{ac}=0.4$ (orange) with frequency $f=0.01$.
+        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
+        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
+        with frequency $f=0.01$.
         The substrate is as in Fig.~\ref{fig:0}
@@
   %\item
-
-  \subsection{Visualizing motion}
-  \label{ex:animation}
-
-  Drawing the contour
-
-  The code for generating
-  a two dimensional colored plot
-  of the potential landscape
-  is calculated by evaluating
-  the analytic function in Eq.~\ref{eq:ysubstrate}
-  for a grid of values $(x_n,y_n)$.
+  %\subsection{Visualizing motion}
+  %\label{ex:animation}
+  %Drawing the contour 
+  %The code for generating
+  %a two dimensional colored plot
+  %of the potential landscape
+  %is calculated by evaluating
+  %the analytic function in Eq.~\ref{eq:ysubstrate}
+  %for a grid of values $(x_n,y_n)$.
   %is included in the supplementary material,
-
-  {\it I have python code that does all of this, but I don't have it
-    set up to play nice with my new python MD code}
-
-  Also the animation library in python...
+  %{\it I have python code that does all of this, but I don't have it
+  %  set up to play nice with my new python MD code} 
+  %Also the animation library in python...
 
@@
 %due to interactions between particles.
-Our simulations reproduce experiments presented in 
-Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
+Our simulations reproduce experiments and simulations presented in 
+Juniper {\it et al.} \cite{Juniper2015, Juniper2017}
 of 
@@
 64, 693 (1990); D.
-Dom´ınguez and J.
+Dom{\'i}nguez and J.
 V.
-Jos´e, Giant Shapiro steps with screening currents, Phys.
+Jos{\'e}, Giant Shapiro steps with screening currents, Phys.
 Rev.
@@
       %\bibitem{Juniper2018}
-      Juniper, M.
+
+      \bibitem{Juniper2017} Juniper, M.
 P.
@@
 A.
-L., Löwen, H., and Dullens, R.
+L., L{\"o}wen, H., and Dullens, R.
 P.
@@
 
-    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Castañeda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
-
-    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Castañeda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
+    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
+
+    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
 
@@
 
-    \bibitem{numpy} Harris, C.R., Millman, K.J., van der Walt, S.J. et al. Array programming with NumPy. Nature {\bf 585}, 357 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
+    \bibitem{numpy} C.R. Harris, K.J. Millman, S.J. van der Walt, et al. Array programming with NumPy. Nature {\bf 585}, 357 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
 
@@
 \end{figure}
-\end{center}
 
@@
 $F^{dc}/F^{ac} = 1$ [CHECK!]
+
+The addition of an oscillating force
+can lead to interference effects
+that create stepped force-velocity curves.
+Useful model - essentially an -
+under certain parameters.
+The steps occur
+due to the phase locking between lattice substrate
+and applied driving force.
+Step widths depend on AC drive.
+Discrete modes.
+
+  In Fig.~\ref{fig:phase}(b)
+  $A_p = 0.05$
+  the spatial properties are similar to
+  those in $A_p = 0.0$
+  with 
+  $(\phi,\dot{\phi})=(10,0)$
+  with a semimajor axis of $\Delta \phi = 20$.
+  The dynamical properties
+  are asymmetric,
+  with three nodes in the positive $\dot{\phi}$ values.
+  The thickening of the line
+  indicates the system is not fully synchronized.
+  [insert analysis.]
+  As the substrate
+  force becomes larger,
+  $\phi$ shifts to lower values
+  and $\dot{\phi}$ to positive values,
+  indicating
+  the particle can only move 
+  backward over a short distance.
+  In Fig.~\ref{fig:phase}(c)
+  $A_p = 0.1$
+  the phase properties are similar to
+  those in $A_p = 0.05$,
+  the three nodes have 
+  increased asymmetry in both phase variables 
+  $(\phi,\dot{\phi})$.
+  The nodes deepen,
+  indicating [insert analysis.].
+  In Fig.~\ref{fig:phase}(d)
+  $A_p = 0.2$
+  the pattern shifts
+  to two nodes,
+  [indicating change analysis].
+  In Fig.~\ref{fig:phase}(e)
+  $A_p = 0.25$
+  the system returns to a nodeless
+  orbit,
+  shaped like a triangle [because why?]
+  In Fig.~\ref{fig:phase}(f)
+  $A_p = 0.3$
+  the particle is trapped between substrate minima,
+  and traces out a small unclosed
+  orbit in phase space [because...]
+  The phase velocity is near zero
+  throughout the motion -
+  [comment on initial conditions]
+
+  %------------------------------------
+  We explore a range of parameters in Ex.~\ref{ex:parameters}
+where 
+we perform this sweep for several values
+of $F^{ac}$ including the limiting case that the applied force
+is a constant value.
+%When $F^{ac} = 0$, no steps appear
+%in the $\langle v_y \rangle $ vs $F^{dc}$ curve. 
+When $F^{dc} - F^{ac} < -A_p$ the particle
+moves in the negative y-direction 
+during part of the cycle.
+%We examine
+The period of the substrate
+can be used to control the
+net velocity of the dc driven particle,
+and the applied ac drive can cause mode-locking
+which appears as non-linear 
+steps in the force-velocity relationship.
+
+ we can easily use 
+  %examine 
+  %for
+  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
+  over the same maximum time
+  (i.e. decrease the overall simulation time and sampling rate)
+  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
+  This is due to the linear nature of the solution
+  for an isolated particle.
+  %How to the motions of the particle compare when the timestep
+  %becomes large?
+  %[UPDATE]
+  {\bf Demonstrate the simulation timestep 
+  can be large
+  with no change to the overall physics
+  in the motion of a single particle.}
+  You will need to modify the maximum
+  simulation time, and the frequency of data saved for plotting purposes.
+
+  %--------------------------------------------------------
+    In Fig.~\ref{fig:brownian},
+  we demonstrate the transition
+  from pinned to hopping
+  in 
+  %Measure the position vs. time
+  a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.

### 2021-02-25 code/MD_colloid.py
updated sweep figures

@@ -43,11 +43,11 @@ def add_contour(ax,L,N):
     Hardwired for a single parameter set.    
     '''
 
-    a_p = L/N
+    a_p = 1
 
     #assuming Tiare's trough system, so we won't want to cover the entire range
-    X = np.arange(0, 100, 0.1)
-    Y = np.arange(0, L, 0.1)
+    X = np.arange(100, 200, 0.1)
+    Y = np.arange(L[0], L[1]+0.1, 0.1)
     X, Y = np.meshgrid(X, Y)
 
     Z_mag = 0.1 # set by what "looks good"
@@ -268,9 +268,9 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     # them.
     ax3 = plt.axes([0,0,1,1])
     # Manually set the position and relative size of the inset axes within ax1
-    ip = InsetPosition(ax2, [0.59,0.01,0.4,0.4])
+    ip = InsetPosition(ax2, [0.64,0.18,0.3,0.4])
     ax3.set_axes_locator(ip)
-    L=1.5
+    L=[0.9,2.3]
     N=1
     add_contour(ax3,L,N)
     
@@ -293,17 +293,20 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     ax1.set_ylabel(r"$F^d(t)$")
     ax2.set_xlabel(r"time ($\tau$)")
     ax2.set_ylabel(r"y/$\lambda$")
-
+    ax3.set_xlabel(r"time",backgroundcolor="white") #,y=10)
+    ax3.set_ylabel(r"y/$\lambda$")
+    ax3.xaxis.set_label_coords(0.5,-0.05)
+    
     #ax1.set_xticklabels([])
     #ax1.xaxis.set_ticklabels([])
     plt.setp(ax1.get_xticklabels(), visible=False)
     
     ax1.set_xlim(0,time_data[-1]+1)
     ax2.set_xlim(0,time_data[-1]+1)
-    ax3.set_xlim(0,100)
-    ax3.set_ylim(0.0,1.5)
-    ax3.set_xticks([])
-    ax3.set_yticks([])
+    ax3.set_xlim(100,200)
+    ax3.set_ylim(0.9,2.3)
+    #ax3.set_xticks([])
+    #ax3.set_yticks([])
 
     ax1.text(-0.19,0.86,"(a)",transform = ax1.transAxes,backgroundcolor="white")
[…]

### 2021-02-26 manuscript/manuscript_ajp_2020.tex
shifted phi by phi0 to be centered about zero

@@
     %(y mod \lambda) / \lambda
-    \phi(t) = (y(t)-\langle v_y \rangle t)/\lambda
+    \phi(t) = 2\pi (y(t)-\langle v_y \rangle t)/\lambda
   \end{equation}
@@
   and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  For clarity we have dropped a prefactor of $2\pi$ 
-  to compare $\phi(t)$ to $\lambda$.
+  For clarity our plots are normalized by the prefactor $2\pi$. 
+  %to compare $\phi(t)$ to $\lambda$.
   %In phase diagrams we plot $\phi(t)$ %phase
@@
     %(y mod \lambda) / \lambda
-    \dot{\phi}(t) =(v_y(t)-\langle v_y \rangle) /\lambda.  % 2\pi
+    \dot{\phi}(t) =2\pi (v_y(t)-\langle v_y \rangle) /\lambda.  % 
   \end{equation}
@@
   we sweep the constant driving force $F^{dc}$
-  for a fixed amplitude $F^{ac}$ and frequency.
+  for a fixed amplitude $F^{ac}$ and frequency $f=0.1$.
+  In the high frequency limit,
+  the steps are separated
+  by linearly increasing regions.
+
   Fig.~\ref{fig:shapiro}(a) shows $F^{ac}= 0.0$ and (b) shows $F^{ac}=0.4$
@@
         $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
-        with frequency $f=0.01$.
+        with frequency $f=0.0$.
         The substrate is as in Fig.~\ref{fig:0}

### 2021-02-26 code/MD_colloid.py

@@ -67,19 +67,7 @@ def add_contour(ax,L,N):
 
     cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.5)
 
-    '''
-    ax.set_xlim(0, L/2)
-    ax.set_ylim(0, L)
 
-    ax.set_xlabel(r"x",labelpad=-20)
-    ax.set_ylabel(r"y",rotation='horizontal',ha='right',labelpad=-15)
-
-    ax.set_xticks([0,L/2])
-    ax.set_yticks([0,L])
-
-    ax.set_xticklabels(['0','L/2'])
-    ax.set_yticklabels(['0','L'])
-    '''
     return 
 
 ##################################################################
@@ -188,6 +176,7 @@ def md_step(y, int_time, avg_vy, parameters, ft=0):
         avg_vy = average_velocity(int_time, vy, avg_vy, parameters)
     else:
         avg_vy = vy
+        print(vy, avg_vy)
 
     #calculate the new position
     y += vy*dt
@@ -347,7 +336,11 @@ def plot_phase(ax,y_data,avg_vy_data,p):
 
 
     # driven phase variables
-    phi_y_data = (y_data - (vbar*time+p['y0']))/(p['period']) # 2*np.pi*
+    # 2*np.pi*
+
+    phi_y_data = (y_data - (vbar*time+p['y0']))/(p['period'])
+    phi0=np.average(phi_y_data)
+    phi_y_data-=phi0
     dot_phi_y_data = (avg_vy_data - vbar)/(p['period']) #2*np.pi*
 
     if 1:
@@ -357,14 +350,14 @@ def plot_phase(ax,y_data,avg_vy_data,p):
         #non-driven phase variables
         ax.scatter(y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
 
-    ax.set_xlabel(r"$\phi_y(t)$")
-    ax.set_ylabel(r"$\dot{\phi}_y(t)$")
+    ax.set_xlabel(r"$\phi_y(t) / (2\pi)$")
+    ax.set_ylabel(r"$\dot{\phi}_y(t) / (2\pi)$")
     #ax.yaxis.set_label_coords(-0.2, 0.5)
 
     #ax1.set_xticks([])
     #ax.set_xlim(0.8,2.75) #time_data[-1]+1)
 
-    ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
+    #ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
[…]

### 2021-02-26 code/MD_colloid.py
updated figures in parameters section

@@ -357,7 +357,7 @@ def plot_phase(ax,y_data,avg_vy_data,p):
     #ax1.set_xticks([])
     #ax.set_xlim(0.8,2.75) #time_data[-1]+1)
 
-    #ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
+    ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
     
     return 
 
@@ -575,7 +575,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #figures 2 to 8
-    make_fig = 8
+    make_fig = 6
 
     parameters['filename']="fig%d.pdf"%(make_fig)
 
@@ -773,11 +773,11 @@ if __name__ == "__main__":
 
 
         if make_fig == 5:
-            parameters['maxtime']=5000        #total time steps in simulation
+            parameters['maxtime']=4500        #total time steps in simulation
 
             #we will sweep through the following independent variable
 
-            frequency = [0.1, 0.05, 0.015, 0.005, 0.001]
+            frequency = [0.05,0.022, 0.005, 0.001]
             ind_var = frequency
             str_iv=" f=%1.3f"
 
@@ -785,12 +785,11 @@ if __name__ == "__main__":
             parameters['maxtime']=3000        #total time steps in simulation
 
             #we will sweep through the following independent variable
-            F_AC = [0.2, 0.3, 0.4]
+            F_AC = [0.2, 0.4]
             ind_var = F_AC
             str_iv=" $F^{ac}$=%1.2f"
-            parameters['freq'] = 0.01
-           
-
+            #parameters['freq'] = 0.1
+            #parameters['F_DC'] = 0.1
 
         #make the figure
         n_plots = len(ind_var)
@@ -802,7 +801,7 @@ if __name__ == "__main__":
 
             #make the subplot
             ax = fig.add_subplot(gs[i,0])
-            ax.text(0.02,0.8,letter[i]+str_iv%(ind_var[i]),
+            ax.text(0.7,0.08,letter[i]+str_iv%(ind_var[i]),
                     transform = ax.transAxes,backgroundcolor="white")
             parameters['axis'] = ax
 
@@ -813,8 +812,8 @@ if __name__ == "__main__":
                 parameters['F_AC'] = F_AC[i]
 
                 #horizontal grid so we can count hops
-                ax.set_ylim(-0.9,20.9)
[…]

### 2021-02-26 manuscript/manuscript_ajp_2020.tex
updated text and rearranged to put parameters as the first exercise

@@
   In Fig.~\ref{fig:phase}, 
-  all cases exhibit some line thickening, 
+  all cases exhibit some phase shifts %line thickening, 
   indicating the particle location and velocity
@@
   $F^{dc} = 0.04$
-  the phase plot is a small closed oval
-  centered at
-  $(\phi,\dot{\phi})=(0.1,0)$.
-  A small tail appears
+  the phase plot is a small asymmetric curve.
+  %centered at
+  %$(\phi,\dot{\phi})=(0.1,0)$.
+  A tail appears
   due to the initial transient
@@
   and has no net velocity.
+  The asymmetry is caused by bias induced by $F^{dc}$.
   In Fig.~\ref{fig:phase}(b)
@@
   Fig.~\ref{fig:0}(a).
-  The maximum $\dot{\phi}$ %with a 1:1 mode locking,
-  occurs at $\phi \sim 0.4$,
-  and maximum $\phi$ occurs
-  when $\dot{\phi} \sim 0$.
-
+  %The maximum $\dot{\phi}$ %with a 1:1 mode locking,
+  %occurs at $\phi \sim 0.4$,
+  %and maximum $\phi$ occurs
+  %when $\dot{\phi} \sim 0$.
+  %
   %The dynamical properties are asymmetric,
@@
   of $\dot{\phi}$ over multiple phase positions.
-  The motion becomes quasiperiodic
-  so the loops in phase space do not fully overlap.
+  %The motion becomes quasiperiodic
+  %so the loops in phase space do not fully overlap.
   In Fig.~\ref{fig:phase}(c)
@@
       \caption{
-        Phase plot of a particle with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
-        in Fig.~\ref{fig:1}.%, (e) $0.25$ and (f) $0.3$.
+        Phase plot of $\dot{\phi(t)}/(2\pi)$ vs. $\phi(t)/(2\pi)$.
+        The particle is driven with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
+        in Fig.~\ref{fig:1}. %, (e) $0.25$ and (f) $0.3$.
       The other parameters
@@
 with suggested exercises for interested readers.
+We explore changes in the particle motion
+with parameter changes in Ex.~\ref{ex:parameters}.
 We include analytic exercises to examine the 
@@
 in Ex.~\ref{ex:brownian}.
-We explore changes in the particle motion
-with parameter changes in Ex.~\ref{ex:parameters}.
 %Methods to visualize the dynamics of the particle motion
@@
 %\item
+
+%\item
+  \subsection{Exploring Parameters of the Model}
+  \label{ex:parameters}
+
+  A range of oscillation behaviors
+  can be explored by varying the
+  relative strength of the confining landscape
+  and external driving force.
+  For the single driven particle,
+  the hopping patterns are typically characterized
+  by $n_f$ the number of steps forward
+  versus $n_b$ the number of steps backward within a single
+  time period.
+  The total displacement of $(n_f - n_b) \lambda$ %integer steps of
+  is the net hop length.  
+  %the substrate period $$ characterize
+  In Fig.~\ref{fig:0},
+  the particle moves forward through two minima ($n_f = 2$),
+  and does not move backward a full minima ($n_b = 0$).  
+  %such that the pattern
+  %is characterized as $2(2,0)$.
+  In order to achieve
+  backwards hops,
+  the driving parameters must have
+  a ratio of $F^{ac}/F^{dc} > 1$ 
+  and a difference $|F^{ac} - F^{dc}| > A_p$.
+  %which can also produce large forward hops.
+  %INSERT figure with a range of hopping patterns for a run
+  The frequency must be sufficiently low so that 
+  the applied force is large
+  over a sustained time interval,
+  allowing a particle to hop a substrate maxima.
+  {\bf Explore the effect changing the driving frequency on the hopping pattern.}
+
+  Fig.~\ref{fig:hops}
+  shows the effects of lowering the frequency
+  of applied driving force
+  We hold the remaining parameters fixed 
+  to 
+  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
+  We observe no backward steps 
+  ($n_b = 0$) 
+  across a broad range of frequencies
+  since $F^{dc} - F^{ac}= 0.0$.
+  %is too small to overcome $A_p$.
+  The rate of forward hops 
+  increases as frequency decreases,
+  but in each case the particle
+  hops across one substrate periods as in Fig.~\ref{fig:0}.
+  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
+  do not match the temporal period of $F^d(t)$
+  due to the high frequency.
+  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.05$
+  is apparent in the undulations of the particle
+  with a period of $20\tau$.
+  %Due to the high frequency,
+  The particle is trapped between substrate minima.
+  %$y \approx \lambda/2 $ for
+  %a time interval of $400 \tau$.
+  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.022$
+  with a period of $45\tau$
+  arrests the particle between minima,
+  with a hopping rate of seven periods ($320\tau$).
+  At intermediate frequencies 
+  such as $f=0.01$
+  the particles are synchronized so that 
+  the hopping rate matches the driving frequency,
+  as in Fig.~\ref{fig:2}
+  In Fig.~\ref{fig:hops}(c) $f=0.005$
+  the particle hops forward two minima every period of $200\tau$.
+  Low frequencies
+  result in sustained positive motion of a particle.
+  In Fig.~\ref{fig:hops}(e) $f=0.001$
+  the hopping is continuous
+  over the time $100 \tau < t < 400 \tau$,
+  with the cycle repeating 
+  over the period length $1000 \tau$.
+    \begin{figure} %[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{fig5}.pdf}
+      \caption{
+        Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.05$, 
+        (b) $0.022$, (c) $0.005$ and (d) $0.001$. %where  
+        %the particle wraps the periodic boundary conditions.
+      }
+      \label{fig:hops}
+    \end{figure}
+  %In Fig.~\ref{fig:hops}
+
+  Hopping patterns with backward steps are more difficult
+  to achieve than forward.
+  In Ref.~\cite{Juniper2015}
+  experiments with single colloids 
+  produce 
+  the following
+  combinations of forward and backwards steps:
+  $n_f = 0$ to $6$ for $n_b = 0$,
+  $n_f = 0$ to $5$ for $n_b = -1$,
+  and
+  $n_f = 2$ to $3$ for $n_b = -2$
+  %were realized 
+  by sweeping through
+  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
+  %{\bf Find the parameters
+  %that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
+  %[well, go on...]
+
+  In Fig.~\ref{fig:hops_back}
+  we fix $f=0.01$, $F^{dc}=0.07$, and $A_p = 0.1$
+  and increase
+  the amplitude of $F^{ac}$.
+  This causes the number of backwards steps to increase.
+  The number of forward steps also increases
+  due to the increased total positive amplitude of $F^d(t)$.
+  In Fig.~\ref{fig:hops_back}(a) 
+  $F^{ac} = 0.2$ %, $0.3$ and $0.4$.
+  %of the system for our original parameters.
+  the number of backwards steps
+  $n_b = 0$ with $n_f = 4$.
+  In Fig.~\ref{fig:hops_back}(b) $F^{ac} = 0.4$
+  $n_b = 2$ and $n_f = 6$.
+  %In Fig.~\ref{fig:hops_back}(c) 
+  %$n_b = 4$ and $n_f = 10$.
+  In each case the average velocity %net displacement
+  is $\langle v_y \rangle = 4\lambda f$,
+  which can be reproduced over a variety of $F^{ac}$ values.
+
+    \begin{figure} %[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{fig6}.pdf}
+      \caption{
+        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac} = $
+        (a) $0.2$ and
+        (b) $0.4$.
+      }
+      \label{fig:hops_back}
+    \end{figure}
+
+    In Fig.~\ref{fig:shapiro}
+    we sweep the constant driving force $F^{dc}$
+    for a fixed amplitude $F^{ac}$ and frequency $f=0.01$.
+    In the high frequency limit,
+    the regions of phase locking
+    are separated by regions of $F^{dc}$
+    that do not phase lock,
+    and appear to increase linearly with increasing $F^{dc}$.
+    The width of the phase locked steps
+    grows with increasing $F^{ac}$,
+    since 
+    the particle may move backwards
+    over a broader range of $F^{dc}$.
+    \begin{figure} %[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{fig7}.pdf}
+      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
+      \caption{
+        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
+        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
+        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
+        with frequency $f=0.0$.
+        The substrate is as in Fig.~\ref{fig:0}
+        with $A_p = 0.1$.
+      }
+      \label{fig:shapiro}
+    \end{figure}
+  %In Fig.~\ref{fig:hops}
+%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
+%  \item The Fokker-Planck Equation
+%  \item Aubrey-Kontorova + commensurability
+%  \item nanotribology
+ %   kink motion
+ %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
+  %\item
+  %\subsection{Visualizing motion}
+  %\label{ex:animation}
+  %Drawing the contour 
+  %The code for generating
+  %a two dimensional colored plot
+  %of the potential landscape
+  %is calculated by evaluating
+  %the analytic function in Eq.~\ref{eq:ysubstrate}
+  %for a grid of values $(x_n,y_n)$.
+  %is included in the supplementary material,
+  %{\it I have python code that does all of this, but I don't have it
+  %  set up to play nice with my new python MD code} 
+    %Also the animation library in python...
+
 \subsection{Drag Models and Reynolds Numbers.}
@@
   %%[there is no way I want to run this with python...]
-
-%\item
-  \subsection{Exploring Parameters of the Model}
-  \label{ex:parameters}
-
-  A range of oscillation behaviors
-  can be explored by varying the
-  relative strength of the confining landscape
-  and external driving force.
-  For the single driven particle,
-  the hopping patterns are typically characterized
-  by $n_f$ the number of steps forward
-  versus $n_b$ the number of steps backward within a single
-  time period.
-  The total displacement of $(n_f - n_b) \lambda$ %integer steps of
-  is the net hop length.  
-  %the substrate period $$ characterize
-  In Fig.~\ref{fig:0},
-  the particle moves forward through two minima ($n_f = 2$),
-  and does not move backward a full minima ($n_b = 0$).  
-  %such that the pattern
-  %is characterized as $2(2,0)$.
-  In order to achieve
-  backwards hops,
-  the driving parameters must have
-  a ratio of $F^{ac}/F^{dc} > 1$ 
-  and a difference $|F^{ac} - F^{dc}| > A_p$.
-  %which can also produce large forward hops.
-  %INSERT figure with a range of hopping patterns for a run
-  The frequency must be sufficiently low so that 
-  the applied force is large
-  over a sustained time interval,
-  allowing a particle to hop a substrate maxima.
-  {\bf Explore the effect changing the driving frequency on the hopping pattern.}
-
-  Fig.~\ref{fig:hops}
-  shows the effects of lowering the frequency
-  of applied driving force
-  We hold the remaining parameters fixed 
-  to 
-  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
-  We observe no backward steps 
-  ($n_b = 0$) 
-  across a broad range of frequencies
-  since $F^{dc} - F^{ac}= 0.05$
-  is too small to overcome $A_p$.
-  The rate of forward hops 
-  increases as frequency decreases,
-  but in each case the particle
-  hops across two substrate periods as in Fig.~\ref{fig:0}.
-  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
-  do not match the temporal period of $F^d(t)$
-  due to the high frequency.
-  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.1$
-  is apparent in the undulations of the particle
-  with a period of $10\tau$.
-  %Due to the high frequency,
-  The particle is trapped between substrate minima $y \approx \lambda/2 $ for
-  a time interval of $400 \tau$.
-  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.05$
-  with a period of $20\tau$
-  arrests the particle between minima,
-  with a hopping rate of $200 \tau$.
-  At intermediate frequencies 
-  such as $f=0.01$
-  the particles are synchronized so that 
-  the hopping rate matches the driving frequency.
-  In Fig.~\ref{fig:hops}(c) $f=0.015$
-  the particle hops forward two minima every $67\tau$.
-  Low frequencies
-  result in sustained positive motion of a particle.
-  In Fig.~\ref{fig:hops}(d) $f=0.005$
-  the particle executes two subsequent forward hops
-  before becoming trapped
-  for the remainder of the period $200 \tau$.
-  In Fig.~\ref{fig:hops}(e) $f=0.001$
-  the hopping is continuous
-  over the simulation time.
-  Here the particle reaches the top edge of the system
-  and wraps back to $y=0$.
-  Given a simulation time of the period length $1000 \tau$,
-  the particle would cease forward motion.
-    \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
-      \caption{
-        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.1$,
-        (b) $0.05$, (c) $0.015$, (d) $0.005$ and (e) $0.001$ where  
-        the particle wraps the periodic boundary conditions.
-      }
-      \label{fig:hops}
-    \end{figure}
-  %In Fig.~\ref{fig:hops}
-
-  Hopping patterns with backward steps are more difficult
-  to achieve than forward.
-  In Ref.\cite{Juniper2015}
-  experiments with single colloids 
-  produce 
-  the following
-  combinations of forward and backwards steps:
-  $n_f = 0$ to $6$ for $n_b = 0$,
-  $n_f = 0$ to $5$ for $n_b = -1$,
-  and
-  $n_f = 2$ to $3$ for $n_b = -2$
-  %were realized 
-  by sweeping through
-  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
-  {\bf Find the parameters
-  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
-  %[well, go on...]
-
-  In Fig.~\ref{fig:hops_back}
-  we explore a hopping pattern not
-  observed in Ref.~\cite{Juniper2015}.
-  This is possible in simulation because
-  our particle readily hops through
-  $2\lambda$.
-  We fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$
-  and increase
-  the amplitude of $F^{ac}$,
-  which causes the number of backwards steps to increase.
-  The number of forward steps also increases
-  due to the increased total positive amplitude of $F^d(t)$.
-  In Fig.~\ref{fig:hops_back}(a) 
-  $F^{ac} = 0.2$. %, $0.3$ and $0.4$.
-  %of the system for our original parameters.
-  the number of backwards steps
-  $n_b = 0$ with $n_f = 6$.
-  In Fig.~\ref{fig:hops_back}(b) 
-  $n_b = 2$ and $n_f = 8$.
-  In Fig.~\ref{fig:hops_back}(c) 
-  $n_b = 4$ and $n_f = 10$.
-  In each case the average velocity %net displacement
-  is $\langle v_y \rangle = 6\lambda/T$.
-
-    \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
-      \caption{
-        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
-        (a) The particle moves forward six minima with no steps backward.
-        (b) The particle moves forward eight minima with two steps backward.
-        (c) The particle moves forward nine minima with four steps backward.
-      }
-      \label{fig:hops_back}
-    \end{figure}
-
-  In Fig.~\ref{fig:shapiro}
-  we sweep the constant driving force $F^{dc}$
-  for a fixed amplitude $F^{ac}$ and frequency $f=0.1$.
-  In the high frequency limit,
-  the steps are separated
-  by linearly increasing regions.
-
-  Fig.~\ref{fig:shapiro}(a) shows $F^{ac}= 0.0$ and (b) shows $F^{ac}=0.4$
-  with frequency $f=0.01$.
-
-  The particle does not phase lock since there is no periodicity to $F^d(t)$,
-  but does exhibit undulations in $\langle v_y \rangle$
-  due to the corregations in the substrate.
-  %WAIT, THAT DOESN'T MAKE SENSE!
-  %WHAT IS WRONG WITH YOUR MD SIMULATION?
-  When $F^{ac}=0.4$, 
-  mode-locked steps appear in $\langle v_y \rangle$ vs. $F^{dc}$.
-  At low values of $F^{dc}$ the particle may move backwards,
-  distorting the steps, as seen below $F^{dc}<0.3$
-  Between $0.3< F^{dc}<0.5$ the system exhibits phase locked steps.
-    \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{fig7}.pdf}
-      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
-      \caption{
-        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
-        $F^{ac}=0.1$ (blue), $F^{ac}=0.2$ (orange),
-        $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
-        with frequency $f=0.0$.
-        The substrate is as in Fig.~\ref{fig:0}
-        with $A_p = 0.1$.
-      }
-      \label{fig:shapiro}
-    \end{figure}
-  %In Fig.~\ref{fig:hops}
-%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
-%  \item The Fokker-Planck Equation
-%  \item Aubrey-Kontorova + commensurability
-%  \item nanotribology
- %   kink motion
- %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
-  %\item
-  %\subsection{Visualizing motion}
-  %\label{ex:animation}
-  %Drawing the contour 
-  %The code for generating
-  %a two dimensional colored plot
-  %of the potential landscape
-  %is calculated by evaluating
-  %the analytic function in Eq.~\ref{eq:ysubstrate}
-  %for a grid of values $(x_n,y_n)$.
-  %is included in the supplementary material,
-  %{\it I have python code that does all of this, but I don't have it
-  %  set up to play nice with my new python MD code} 
-  %Also the animation library in python...
 

### 2021-02-28 manuscript/manuscript_ajp_2020.tex
ran ispell, rearranged references

@@
 are useful for
-understanding synchronization at a single particle level \cite{Juniper2015}. 
+understanding synchronization at a single particle level \cite{Juniper2015,Juniper2017}. 
 %due to the large size and slow speed of the particles.
@@
  a particle subject to a constant
- drive force will increase its speed at a rate propotional
+ drive force will increase its speed at a rate proportional
  to the external drive.  
@@
   with $F^{dc} = 0.07$
-  the phase loop is a symmetric trianglar shape,
+  the phase loop is a symmetric triangular shape,
   indicating a 1:1 match between
@@
   the hopping rate matches the driving frequency,
-  as in Fig.~\ref{fig:2}
+  as in Fig.~\ref{fig:0}.
   In Fig.~\ref{fig:hops}(c) $f=0.005$
@@
         $F^{ac}=0.1$ (green) and $F^{ac}=0.2$ (red)
-        with frequency $f=0.0$.
+        with frequency $f=0.01$.
         The substrate is as in Fig.~\ref{fig:0}
@@
   The rate of collisions depends on the temperature, viscosity
-  amd density of 
+  and density of 
   the suspending fluid.
@@
   %\footnote{%In our simulations %np.random.normal
-  We use the normal distristribution from the NumPy random module
+  We use the normal distribution from the NumPy random module
   to generate a series of $f^T_n$ values for
@@
   %substrate free RMSD.
-  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]
+  %%[INSERT EXPECTED RESULTS.  presumably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]
 
@@
 
-\bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygens' clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
-
 \bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima. Synchronization in flickering of three-coupled candle flames. Sci Rep {\bf 6}, 36145 (2016)
@@
 
-    %technological applications
-    \bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
-
-    %condensed matter intro
-    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
-
-    \bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
-
-    \bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
+    \bibitem{Bennett2002} M. Bennett, M.F. Schatz, H. Rockwood, and K. Wiesenfeld, Huygens' clocks, Proc. Roy. Soc. A {\bf 458}, 563 (2002).
 
@@
 %https://doi.org/10.1103/PhysRevLett.87.098303
-
-    \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
-
-      %PRACTICAL APPLICATION
-    %\bibitem{Agrawal2013} D.
-K.
-Agrawal, J.
-Woodhouse, and A.
-A.
-Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
-
-    \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
-    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
-
-    \bibitem{Stewart1968}  W. C. Stewart, Current-Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
-
-    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
-
-    \bibitem{Benz1990}  S.
-P.
-Benz, M.
-S.
-Rzchowski, M.
-Tinkham, and C.
-J.
-Lobb, Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays, Phys.
-Rev.
-Lett.
-64, 693 (1990); D.
-Dom{\'i}nguez and J.
-V.
-Jos{\'e}, Giant Shapiro steps with screening currents, Phys.
-Rev.
-Lett.
-69,
-514 (1992).
-
-\bibitem{Reichhardt2000} C.
-Reichhardt, R.
-T.
-Scalettar, G.
-T., Zim{\'a}nyi, N.
-Gr{\o}nbech-Jensen,  Phase-locking of vortex lattices interacting with periodic pinning.
-Phys.
-Rev.
-B {\bf 61}, R11914 (2000).
-
-    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
-
-      %quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
-
-    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Mu{\~n}oz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
-
-      %reichhardt review
-    \bibitem{Reichhardt2017} C.
-Reichhardt and C.
-J.
-Olson Reichhardt, “Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review,” Rep.
-Prog.
-Phys.
-80, 026501 (2017).
-
-    \bibitem{Reichhardt2015} C.
-Reichhardt, and C.
-J.
-O.
-Reichhardt,  Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
-Phys.
-Rev.
-B {\bf 92}, (22).
-(2015).
 
@@
 
-      \bibitem{Juniper2017} Juniper, M.
+    \bibitem{Juniper2017} M.
 P.
-N., Zimmermann, U., Straube, A.
-V., Besseling, R., Aarts, D.
+N.
+Juniper,  U.
+Zimmermann, A.
+V.
+Straube, R.
+Besseling, D.
 G.
 A.
-L., L{\"o}wen, H., and Dullens, R.
+L.
+Aarts, H.
+L{\"o}wen, and R.
 P.
 A.
-Dynamic mode locking in a driven colloidal system: Experiments and theory.
+Dullens,  Dynamic mode locking in a driven colloidal system: Experiments and theory.
 New Journal of Physics, 19(1).
@@
 
-    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
-
-    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
+    \bibitem{Ashkin1997} A. Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).
 
@@
 
-     \bibitem{Ashkin1997} Arthur Ashkin, Optical trapping and manipulation of neutral particles using lasers, Proc. Natl. Acad. Sci. U.S.A. 94, 4853–4860 (1997).
+      %reichhardt review
+    \bibitem{Reichhardt2017} C.
+Reichhardt and C.
+J.
+Olson Reichhardt, “Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review,” Rep.
+Prog.
+Phys.
+80, 026501 (2017).
+
+    \bibitem{Reichhardt2015} C.
+Reichhardt, and C.
+J.
+O.
+Reichhardt,  Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives.
+Phys.
+Rev.
+B {\bf 92}, (22).
+(2015).
+
+    \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
+
+    %condensed matter intro
+    \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
+
+    \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
 
     \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013
-
-%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
-    \bibitem{Lutz2004} C.
-Lutz, M.
-Kollmann, and C.
-Bechinger, Phys.
-Rev.
-Lett.
-{\bf 93}, 026001 (2004); C.
-Lutz, M.
-Kollmann, C.
-Bechinger, and P.
-Leiderer, J.
-Phys.: Condens.
-Matter {\bf 16}, S4075 (2004).
-
-    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
-
-    \bibitem{Gholami2015} A.
-Gholami, O.
-Steinbock, V.
-Zykov, and E.
-Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
-Rev.
-Lett.
-{\bf 114}, 018103 (2015).
-
-      %Molecular dynamics references
-
-    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
-
-    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).
-
-    \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
-
-      \bibitem{Newman} M. Newman, Computational Physics, CreateSpace Independent Publishing Platform. (2012).
-
-      \bibitem{supp1} Supplementary videos coming soon.
-        %See Figure1.mp4 in appropriate %\url{}
 
@@
       IAPWS R12-08, 
-  Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance, 
-  September 2008, 
+      Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance,  September 2008.
       %IAPWS 2008 -
-  http://www.iapws.org/relguide/viscosity.html
+      \url{http://www.iapws.org/relguide/viscosity.html}
       %[citation for these values better than wikipedia] \cite{} %CONFIRM!
@@
 
+      \bibitem{Newman} M. Newman, Computational Physics, CreateSpace Independent Publishing Platform. (2012).
+
+   %   \bibitem{supp1} Supplementary videos coming soon.
+        %See Figure1.mp4 in appropriate %\url{}
+
   \bibitem{Einstein1905} A Einstein, Investigations on the Theory of the Brownian Movement,  Dover Publications (1956).
@@
     \bibitem{numpy} C.R. Harris, K.J. Millman, S.J. van der Walt, et al. Array programming with NumPy. Nature {\bf 585}, 357 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
+
+           %PRACTICAL APPLICATION
+    %\bibitem{Agrawal2013} D.
+K.
+Agrawal, J.
+Woodhouse, and A.
+A.
+Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
+
+          %technological applications
+    %\bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
+
+    %\bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
+
+    %\bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
+
+    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
+
+    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev. The current-phase relation in Josephson junctions, Rev. Mod. Phys. {\bf 76}, 411 (2004).
+
+    \bibitem{Benz1990}  S.
+P.
+Benz, M.
+S.
+Rzchowski, M.
+Tinkham, and C.
+J.
+Lobb, Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays, Phys.
+Rev.
+Lett.
+64, 693 (1990); D.
+Dom{\'i}nguez and J.
+V.
+Jos{\'e}, Giant Shapiro steps with screening currents, Phys.
+Rev.
+Lett.
+69, 514 (1992).
+
+    \bibitem{Reichhardt2000} C.
+Reichhardt, R.
+T.
+Scalettar, G.
+T., Zim{\'a}nyi, N.
+Gr{\o}nbech-Jensen,  Phase-locking of vortex lattices interacting with periodic pinning.
+Phys.
+Rev.
+B {\bf 61}, R11914 (2000).
+
+      %quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
 
@@
   a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.
+
+  \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
+    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
+
+    \bibitem{Stewart1968}  W. C. Stewart, Current-Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
+
+    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Mu{\~n}oz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
+
+    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
+
+    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
+
+%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
+    \bibitem{Lutz2004} C.
+Lutz, M.
+Kollmann, and C.
+Bechinger, Phys.
+Rev.
+Lett.
+{\bf 93}, 026001 (2004); C.
+Lutz, M.
+Kollmann, C.
+Bechinger, and P.
+Leiderer, J.
+Phys.: Condens.
+Matter {\bf 16}, S4075 (2004).
+
+    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
+
+    \bibitem{Gholami2015} A.
+Gholami, O.
+Steinbock, V.
+Zykov, and E.
+Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
+Rev.
+Lett.
+{\bf 114}, 018103 (2015).
+
+      %Molecular dynamics references
+
+    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
+
+    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).

### 2021-02-28 manuscript/manuscript_ajp_2020.tex
fixed terrible sentence #2 in abstract

@@
   plays a key role in many physical processes.
-  %Modeling
-  A particle may
-  execute
-  motion 
-  coordinated  with position,
-  a synchronization behavior
-  that 
-  can be used to isolate
-  complex natural behaviors,  %to
-  either with
-  simulations or table-top experiments.
-  %provide insight
   We discuss a %simple
@@
   across a washboard potential energy landscape.
+  %Modeling
+  The particle may move with velocity coordinated 
+  to position in the landscape.
+  This synchronized motion %ation behavior
+  is
+  commonly observed in 
+  simulations and table-top experiments,
+  and
+  can be used to isolate
+  complex natural behaviors.  
+  %provide insight
   Our results show many dynamical patterns

### 2021-03-01 manuscript/manuscript_ajp_version1.tex
renamed figures and relabeled

--- 2021-02-28 manuscript/manuscript_ajp_2020.tex
@@
-%\documentclass[prb,preprint]{revtex4} 
-\documentclass[twocolumn,preprintnumbers,amsmath,amssymb,aps,prx]{revtex4}
-% The line above defines the type of LaTeX document.
+\documentclass[twocolumn,preprintnumbers,amsmath,amssymb,aps,prb]{revtex4}
 % Note that AJP uses the same style as Phys. Rev. B (prb).
@@
 \usepackage{graphicx} % needed for figures
-\usepackage{pythontex}
 
@@
 
-% See the REVTeX documentation for more examples of author and affiliation lists.
 \date{\today}
@@
   plays a key role in many physical processes.
-  %Modeling
-  A particle may
-  execute
-  motion 
-  coordinated  with position,
-  a synchronization behavior
-  that 
-  can be used to isolate
-  complex natural behaviors,  %to
-  either with
-  simulations or table-top experiments.
-  %provide insight
-  We discuss a %simple
-  %numerical model %that
+  We discuss a 
   molecular dynamics simulation
@@
   forming closed orbits in phase space.
-  Quasi-periodic motion is common, % in this system,
+  Quasi-periodic motion is common, 
   where the
@@
   phase space orbit.
-  We include molecular dynamics code %and exercises
+  This synchronized motion
+  is
+  observed in 
+  simulations and table-top experiments,
+  and
+  can be used to isolate
+  complex natural behaviors.
+   We include molecular dynamics code
   to simulate and characterize
   particle dynamics.
-  %including 
-  %plotting  particle velocity as a function of applied driving force 
-  %and phase diagrams of position versus velocity.
-  %We demonstrate how to 
-  %visualize
-  %the system with
-  %numerical representations of the landscape
-  %and
-  %animations of the particle motion.
-  %We include sample code
-  %and exercises for students
-  %with 
-  %opportunities
-  %to reproduce our results and propose
-  %new numerical experiments.
-  %With only a few particles in two-dimensions,
-  %the simulation runs quickly,
-  %making this an appropriate model for undergraduates to explore.  
 \end{abstract}
@@
 
-\section{Introduction} %
-%
-%Outline
-%------------------------------------------------------------------
-%synchronization = widest audience possible
+\section{Introduction} 
 Synchronization is a universal phenomena
@@
 and metronomes vibrating through a supporting platform \cite{Jia2015}
-are examples of in-phase coupled oscillations. %of components 
+are examples of in-phase coupled oscillations. 
 Biological systems benefit from cooperative
-synchronization -- %such as 
+synchronization --
 birds coordinate wing flaps
@@
 External forcing can cause or regulate 
-synchronization %. % is often achieved via external forcing
-%such as when
-%single particle oscillators
--- %For instance,
-an electrical pacemaker %(an electrical generator)
+synchronization -- 
+an electrical pacemaker 
 regulates a heart beat 
@@
 a pulsed light modifies the
-flashing pattern of fireflies .% \cite{Agrawal2013}.
-
-%Christiaan Huygens 
-%[has been adapted into many useful technologies...]
+flashing pattern of fireflies.
+
 Synchronized phase-locking or mode-locking 
@@
 pendula in wall-mounted clocks \cite{Bennett2002}.
-%Even when started out of phase, 
-%Huygens demonstrated the tendency of
-%coupled pendula tend to swing in time
-%due to interactions through the wall 
-%phase locking
 A locked-mode is an integer frequency ratio.
 In Huygens clocks,
-%even when started out of phase, 
-the pendula were observed swing at same rate -- a 1:1 mode.
-For a higher modes,
-consider simple pendula of different lengths,
-a 2:1 mode occurs when a pendulum four
+the pendula were observed swing at same rate
+in the same direction (1:1 mode) or
+opposite directions (-1:1 mode).
+A 2:1 mode occurs when a simple pendulum four
 times the length of another swings with twice the period.
-%
-%to a mode or frequency ratio  
-%of an integer number \cite{Bak1986}.
-%Dynamical mode locking
-%The phenomena
-%\section{Colloidal Models}
-%\label{sec:colloids}
 
@@
 de-ionized water or silica beads suspended in organic solvent.
-%experimental - colloids specifically
 Because 
-colloids are large %-- a few microns in size
-and move slowly, %-- a few microns per second,
+colloids are large 
+and move slowly, 
 particle position 
 can be measured in real time 
-with an optical camera \cite{Pertsinidis2001}. %(see Table ~\ref{tab:1}).
+with an optical camera \cite{Pertsinidis2001}. 
 Experimental measurements of 
@@
 understanding synchronization at a single particle level \cite{Juniper2015,Juniper2017}.
-%due to the large size and slow speed of the particles.
-%Individual colloids exhibit 
-%Brownian motion,
-%where particles change direction %in a seemingly random fashion
-%due to 
-%collisions 
-%with unseen particles comprising the suspending fluid \cite{}.
-%[elaborate - move to associated problems?].
 
@@
 with 
-%A circular optical trap uses 
 radiation pressure from 
 a laser beam \cite{Ashkin1997}.
-%Since photon density is high at the beam center,
-A colloid centered in an optical trap is %subject to a
-uniformly bombarded by photons. % while 
-%form a circular pattern with a higher density 
-%central 
-%energy minimum.
-%optical trap  trap colloids
-%with radiation pressure  which uses  photon 
-%control colloid motions 
-%A  is designed
-Off-center colloids %away from center
+A colloid centered in an optical trap is 
+uniformly bombarded by photons. 
+Off-center colloids 
 experience a net force
@@
 the particle surface.
-%Colloids at a trap edge
-%experience a net force
-%due to the 
-Depending on the %shape of the trap and
+Depending on the 
 location of the particle in the trap,
 the radiation pressure either moves colloids toward center 
-%local minimum 
 or ejects it from the trap.
-%In experiments
 Diffraction gratings can create
 more complex light environments, 
-%with one or more laser beams,
 such as periodic patterns of minima
@@
 
+The model presented in this paper
+resembles an overdamped driven pendulum.
 A single particle oscillator
@@
 or moving between substrate minima.
- %The relationship between the driving force and
- %landscape can change the pattern of motion.  
- A constant or 
- dc drive the landscape modulates 
- the particle velocity.
+When 
+a constant or 
+dc drive is applied,
+the particle velocity is modulated by 
+the landscape.
 Below some threshold  
@@
 to the external drive.  
- %and dissipating energy from the system at all driving forces.
 When the applied force varies periodically,
@@
 leading to 
- %A sinusoidal or ac drive can create
 mode-locking,
@@
 is fixed for a range of dc drive forces \cite{Reichhardt2015}.
- %This synchronization phenomena
- %is useful for understanding the complex dynamical 
- %systems.
- The model presented in this paper
- resembles an overdamped driven pendulum. 
-%Numerical modeling of colloids can provide mechanistic insight
-%that can be difficult to achieve in experimental conditions
-%where Brownian motion and other sources of noise dominate.
-%external forces
-%The
-%dynamics of particles subject to 
-%an applied external force apply to many physical systems.
-%For instance the flow of charges in a conductor,
-%or cells responding to a chemical gradient.
-%The external force 
-%increases the diversity of dynamical behaviors,
-%and can cause particles to flow in
-%a variety of non-linear complex patterns
-%that may be 
-%synchronized.
-%Disordered chaotic dynamics are also possible,
-%where irregular, unpredictable time evolution of
-%nonlinear systems occurs in mechanical oscillators \cite{chaos}.
 %-------------------------------------------------------------
 
-%Given the prevalence of synchronization,
-%it is the subject of many computational models.
+%paper outline
 Here we perform numerical studies 
 on the synchronized dynamics
-of confined particles driven over
+of a confined particle driven over
 a washboard shaped potential energy landscape.
-%Numerical studies %of harmonic systems
-%can yield insights
-%to the mechanics of naturally oscillating systems.
-%We choose this model for its
-%relevance to condensed matter systems
-%and ease of simulation.
-%---------------------------------------------------------------
-%kinks and nanofriction
-%-----------------------------------------------------------------
-%transition from synchronized to chaotic
-%describe types of physical systems - particle types
-%%In this work,
-%we perform 
-%numerical simulations of confined, driven particles
-%to model a variety of physical phenomena.
-%-----------------------------------------------------------------------
-%paper outline
-%In Section~\ref{sec:colloids} we describe colloid particles,
-%an relevant
-%experimental analog of our simulations.
 We describe
-our molecular dynamics model for a single particle in Section~\ref{sec:MD},
+our molecular dynamics model for a single particle in Section~\ref{sec:MD}.
 The model
-closely resembles
-a damped driven pendulum,
-and is easy to simulate yet relevant
+is easy to simulate yet relevant
 to condensed matter systems.
-%In this section, we restrict our discussion to a single particle,
-%and include additional information
-%for multiple particles in Section~\ref{sec:sync}.
-%including various  and confining environments.
-We summarize
-our results 
-%in Section~\ref{sec:results} 
+We summarize our results 
 including synchronized motion of a single confined particle
 driven across a periodic landscape in 
-Section~\ref{sec:one}.
-%In Section~\ref{sec:sync}
-%we 
-%extend the model to include multiple particles,
-%and show how confined 
-%interacting particles respond to the same applied driving force.
-%including stationary propagation of high density kinks
-%in Sec.~\ref{sec:kink}.
-%We include code to simulate
-%and visualize the landscape and dynamics in this section
-%and supplementary material.
-%we
-%demonstrate how uniform environments and applied forces
-%and create synchronized flow patterns.
-%We present these results using standard tools of non-linear oscillators
-%such phase diagrams of velocity versus position.
-%PHASE DIAGRAMS SHOWING COUPLING, OR QUASI-PERIODIC COUPLING
-%INDICATE COOPERATIVE MOTION IN THE Q1D SUBSTRATE
-%In Section~\ref{sec:quasiperiod},
-%we show how an aperiodic landscape modifies the particle dynamics.
-%Finally we explore the transition to chaotic dynamics in 
-%Section~\ref{sec:chaos}
-%and conclude 
-We include 
-exercises for interested students 
+Section~\ref{sec:results}.
+We include exercises for interested students 
 in Section~\ref{sec:problems}.
@@
 such as dusty plasmas, superconducting vortices and Josephson junctions.
-%Here we model the microscopic dynamics of phase locking in a colloidal model system using molecular dynamics (MD).
 
@@
 by the transformation $x_i+L \rightarrow x_i$ and $y_i+L \rightarrow y_i$.
-%and particles interact across PBC.
-We show a schematic of the system in Fig.~\ref{fig:landscape0}(a).
+We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
 The units of the simulated variables are summarized in Table ~\ref{tab:1}.
@@
 potential energy function, called a landscape or substrate.
- %The landscape potential energy $U(\vec{r})$ is static 
- %with fixed minima and maxima
- %that are periodic or quasi-periodic,
- %as described in Sec.~\ref{sec:results}.
-% 
 The landscape is modulated in the y-direction
 with the periodic function 
-%% %that used in Sec.~\ref{sec:one}
-% where 
  \begin{equation}
@@
  where $\lambda=L/N_p$ with $N_p$ are the number of periods,
- % $L$ is the period length,
  and $U_0$ is an adjustable parameter
@@
  with simulation units of energy $E_0$. 
- %We define the substrate strength to be
- %the maximum force the substrate can exert on a particle 
- %
  We plot this function in 
- Fig.~\ref{fig:landscape0}
- for $N_p = 3$. %to illustrate the features of
- In Fig.~\ref{fig:landscape0}(a) we show 
- the $x-y$ plane with a contour plot of $U(y)$ %Eq.~\ref{eq:ysubstrate}
+ Fig.~\ref{fig:1_landscape}
+ for $N_p = 3$. 
+ In Fig.~\ref{fig:1_landscape}(a) we show 
+ the $x-y$ plane with a contour plot of $U(y)$ 
  to illustrate
@@
  The confining force on a particle $i$
- %arises from a potential function 
- %creating a landscape of potential minima and maxima
- %that modify the force on a particle as a function of position
  is calculated as 
  $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
- In Fig.~\ref{fig:landscape0}(b) we plot the function
+ In Fig.~\ref{fig:1_landscape}(b) we plot the function
  $U(y)$ to illustrate how the magnitude
  $\vec{F}^{l}_i$ is calculated from particle position $y_i$.
- %in the $y-$direction.
 
@@
 \end{equation}
-with %parameters including
+with 
 a constant component $F^{dc}$,
@@
 and frequency $\omega = 2 \pi f$.
-%in the positive $y-$direction.
-%but it may 
-%be zero or negative depending the the parameters and time.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%RAMP!!!
-%%%When $F^{dc}$ is non-zero,  we slowly increase $F^{dc}$ from zero to avoid transient behavior by ensuring the particle is subject to a smoothly varying force.
-We illustrate the increase of $F^{dc}$ in Fig.~\ref{fig:0}(a).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%because
+%-----------------------------------------------------------
+%overdamped model
+%-----------------------------------------------------------
 The inertia of 
@@
 with fluid particles \cite{Purcell1977}.
-%In our model
 We assume 
-colloids are overdamped
--- suspended in a continuous viscous fluid
-that dissipates energy %at a rate
-so the particles do not accelerate.
+colloids are
+overdamped
+so the particles do not accelerate,
+i.e. suspended in a continuous viscous fluid
+that dissipates energy supplied externally. 
 Newton's second law for an individual particle
-%$m \vec{a}_i = \sum \vec{F}$
 is simplified
-by the assumption $\vec{a}_i$ is zero. % in the overdamped model.
-%Newton's second law can be rearranged %for the velocity
-%to
+by the assumption $\vec{a}_i$ is zero. 
 The overdamped equation of motion for
@@
 an isolated particle is
-%solved for velocity 
 \begin{equation}
@@
 energy dissipation from the fluid. 
-%that greatly impedes their motions.
-%proportional to the particle velocity 
-%with a $\eta$
-%proportional to the fluid viscosity.
 We discuss friction models for
 spheres moving through fluids in 
-%Section~\ref{sec:problems}
-Exercise~\ref{ex:reynolds}. %for more information
-%We model the particle dynamics  with an overdamped equation of motion. Models with inertia set to zero are appropriate for moving through a high viscosity fluid
+Exercise~\ref{ex:reynolds}.
 
 The equation of motion provides a direct calculation of the velocity
-of an individual particle from location $\vec{r}_i$ %in the simulation
+of an individual particle from location $\vec{r}_i$ 
 and the simulation time.
 The molecular dynamics simulation is controlled by a $for()$ loop
-which runs from an initial to maximum integer number of time steps.
-%$t_i$.
-%Each integer time step interval %$t_{i+1}-t_i$
-%represents a simulation time of $\Delta t$.
-%simulation units $\tau$.  %as described in Table 1
+which runs to a maximum integer time step.
 At each time step
@@
 to an updated position.
-%$\vec{r}_i(t+\Delta t)$.%
 Since the acceleration as zero,
@@
 for a time step $\Delta t = 0.1 \tau$.
-In %Section~\ref{sec:problems}
+In 
 Exercise~\ref{ex:euler}
@@
 solving differential equations.
-%
 %------------------------------------------------------------------
@@
 \centering
-\includegraphics[width=\columnwidth]{landscape.pdf}
+\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
 \caption{
@@
   driven across a washboard potential energy landscape.
-  %The period of the landscape is $\lambda = L/N_p$,  
-  %is marked in red,
-  %where $N_p = 3$.  
-  %The force due to the landscape %$\vec{F}^l$
-  %is calculated from the gradient of the potential energy 
-  %$\vec{F}^l = -\nabla U(\vec{r})$.
-  (a) View of the $x-y$ plane. %of the simulation
+  (a) View of the $x-y$ plane. 
   The time-dependent applied driving force $\vec{F}^d$
   is parallel to the y-axis.
-  The landscape is shown with %a contour plot,
-  %with
+  The landscape is shown with 
   maxima in the potential energy marked in red
   and minima marked in blue.
-  A particle is %in the region between minima and maxima
+  A particle is 
   subject to competing forces of the landscape and applied driving force.
@@
   }
-\label{fig:landscape0}
+\label{fig:1_landscape}
 \end{figure}
-%\section{Results}
-%\label{sec:results}
-% We demonstrate how a single particle (Sec.~\ref{sec:one})
-% and many particles
-% move (Sec.~\ref{sec:sync})
-% in response to this applied force in a variety of environments.
-% In Sec.~\ref{sec:kink} we set $F^{dc}$
-% to zero and track the motion
-% of a high density area of a particle chain
-% (i.e. kink dynamics).
- %The driving force does add energy into the system, and some of it is lost.
 %
@@
 % In subsection headings, only the first word is capitalized.
-\label{sec:one}
-
+\label{sec:results}
 Here we drive 
-a single particle %on this landscape
-%responds to the applied driving force
-%by moving
-across the landscape. %maxima
-%to explore the qualitative behavior
-%to characterize its motion.
-%synchronized with 
-%the period of $F^d(t)$.
-%applied driving force.
-%along the y-direction
-%({\it redundant, just refer back to eq. in Model?})
-%and $V_{0y}=0.2$.
-%This is illustrated in Fig.~\ref{fig:1}(a) where
-%the red (blue) regions show local maxima (minima).
-%
+a single particle 
+across the landscape. 
 The numerical implementation of the landscape 
@@
 In this section we fix the landscape parameters
-to $A_{p} = 0.1 F_0$ %force units
-with $N_p=20$ minima %in the landscape
+to $A_{p} = 0.1 F_0$ 
+with $N_p=20$ minima 
 corresponding to a spatial period $\lambda = 2.3 a_0$.
@@
 can produce a variety of hopping patterns in the particle motion. 
-%In Fig.~\ref{fig:0}
-%reaching a minimum position
-%of $y/\lambda = 1$
-%over the total period $T = 100$.
-%In Fig. ~\ref{fig:0}
-%the average displacement during one time period is a single wavelength
-%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
-%single dc case with figure
-%dc_current 0.01
-%ac_current 0.05
-%ac_frequency 0.01
-%fp_y 0.1
-%
 The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
@@
 forward and backward in the landscape.
-%Here we explore one case in the low frequency regime,
 When $F^d(t) > A_p$, a particle can 
@@
 When the driving frequency is low,
-as in Fig.~\ref{fig:0},  
-the driven particle %adjusts
-moves %across %its motion to traverse
-%the periodic landscape
+as in Fig.~\ref{fig:2_Fd_vy_time},  
+the driven particle 
+moves 
 in a pattern 
 with the same frequency 
-%with the same rhythm as 
 as the time-dependent force $F^d(t)$,
@@
   experimental values~\cite{Juniper2015,Juniper2017}.}
-  %Blanks indicate you are a moron
-  %units, rather than parameters that
-  %are not easily represented by a single value.}
-%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
 \begin{ruledtabular}
-\begin{tabular}{c c c } %p{5cm}}
+\begin{tabular}{c c c } 
 Quantity & Simulation Unit & Experimental value\\
@@
 substrate amplitude\footnote{Our substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of particles.} & $A_p = 0.1 F_0$ & $U_0 = 25 k_B T \sim 1 J$ \\ %$U_0 = 0.037 E_0$
-%they have 75 k_B T as the bottom of -U_0
-%A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
 temperature\footnote{To learn more about the effects
@@
   $U_0 \sim k_B T$.} & $T_0 = 0$  & $T \sim 290K $ \\
-%FROM JUNIPER2015
-%l¼3.5 mm and a laser power per trap of WE0.75mW (trap stiffness: k=3.8\times10^7 kg /s^2; trap depth: V0 = 75 k_B T
-%ref51
-%Juniper, M.
-P.
-N., Besseling, R., Aarts, D.
-G.
-A.
-L.
-& Dullens, R.
-P.
-A.
-Acousto- optically generated potential energy landscapes: potential mapping using colloids under flow.
-Opt.
-Express 27, 28707–28716 (2012).
-%U(x) measured in ratio of k_BT from -75 to -25
-%0 < vAC < 8 micrometer/s and frequency f=0.25 to 0.75 Hz.
-%0 < vDC < 5 micrometer/s
-%convert to force units?
-%check when steps exist - in Juniper - steps don't exist for n=1or n=3, even though steps exist for n¼0,2,4,5 and 6.
-%flexible chains
-%dipole interaction $\Gamma \propto B^2$
-%\Gamma =15 (B=0.43mT) and a stiff chain at \Gamma=392 (B=2.2mT).
-%Kink
-%16 particles in a strong potential energy landscape of 15 minima (trap spacing: l¼5.5 mm; laser power per trap: WE1.75 mW; trap stiffness: k¼8.7?10?7 kg s?2; trap depth: V0¼200 kBT),
-%JUNIPER2017
-%The driving force is provided by a PI-542.2CD piezo-stage, controlled using the LabView interface, at driving 0.4 ≤ FAC/ζ ≤ 14 µm s−1, and a frequency of 1 velocities of 0.05 ≤ FDC/ζ ≤ 8 µm s−1.
-AC driving veloc
-%Volpe AJP Parameters
-%We will consider a silica microparticle in water with radius R=1micro m, mass m=11picograms, viscosity eta=0.001 Ns/m^2; $\gamma=6\pi \eta R$,  T=300K, and \tau=0.6\micro s.
-%thermofisher off the shelf paramagnetic beads
-%https://www.thermofisher.com/us/en/home/references/protocols/proteins-expression-isolation-and-analysis/protein-isolation-protocol/m-270-carboxylic-acid.html
-%~2\times10^9 beads per 30 mg -> 1.5 \times 10^-11 g, 15 ng
 \end{tabular}
@@
 
-In Fig.~\ref{fig:0}(a)
-we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
+In Fig.~\ref{fig:2_Fd_vy_time}(a)
+we plot $F^d(t)$ 
 as a function of time with
-%The time independent
 constants $F^{dc}=0.07$, 
@@
 time of $400 \tau$.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%RAMP
-%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$.
-at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$.
-In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%since $\sin{(0)}=0$.
-%We mark the maxima of $F^{ac}(t)$
-%with the
-%vertical dashed lines %in panels (a) and (b)
-%-- i.e. $\sin{(\omega t)} = 1$.
-%with the initial driving force at is minimum value 
-%$F^d(0) = F^{dc}$. 
-%
-In Fig.~\ref{fig:0}(b) 
+In Fig.~\ref{fig:2_Fd_vy_time}(b) 
 we show the $y-$position of the particle
@@
 normalize $y$ by $\lambda$.
-%to show  particle motion between substrate minima.  
-The initial particle position is $y = 0 $. %1 a_0$,
-%where the $F^l$ is negative.
-%causing the particle to move to
-%a landscape minima at the start of the simulation.
+The initial particle position is $y = 0 $. 
 The particle moves
@@
 the average velocity 
-$\langle {v}_y \rangle = \lambda f$. % where $T = 1/f$.
-%For these parameters,
-The inset of Fig.~\ref{fig:0}(b)
-shows $y$ %vs. time
+$\langle {v}_y \rangle = \lambda f$. 
+The inset of Fig.~\ref{fig:2_Fd_vy_time}(b)
+shows $y$ 
 over one period $100\tau < t < 200 \tau$
@@
 the contour plot described
-in Fig.~\ref{fig:landscape0}(a).
+in Fig.~\ref{fig:1_landscape}(a).
 The motion is synchronized so the 
@@
 %------------------------------------------------------------------------
-%----------------------------------------------------------------
 \begin{figure} %[h!]
 \centering
-\includegraphics[width=\columnwidth]{fig2.pdf}
-\caption{(a) The applied driving force $F^d(t)$ % (Eq.~\ref{eq:drive}).
+\includegraphics[width=\columnwidth]{fig2_Fd_vy_time.pdf}
+\caption{(a) The applied driving force $F^d(t)$ 
   with parameters $F^{dc} = 0.07$, $F^{dc} = 0.07$ and $f=0.01$.
-  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
   (b) 
   The $y-$position of the driven particle
-  %of a single driven particle
   normalized by the period of the substrate $\lambda$.
   The substrate strength is $A_p=0.1$.
-  %as a function of time
   The inset of (b) shows
@@
   against the contour plot depicting
-  the landscape potential described in Fig.~\ref{fig:landscape0}(a).
+  the landscape potential described in Fig.~\ref{fig:1_landscape}(a).
   }
-\label{fig:0}
+\label{fig:2_Fd_vy_time}
 \end{figure}
@@
 we sweep through a range of $F^{dc}$ for fixed $F^{ac}$ and $A_p$.
-%to illustrate
-%distinct oscillation modes. % as a function of $F^{dc}$.
-%as shown
-In Fig.~\ref{fig:1} 
+In Fig.~\ref{fig:3_sweep_vyFDC} 
 we increase $F^{dc}$ in increments of $0.001 F_0$
-%for $10^5$ simulation timesteps
 and 
@@
 as a function of $F^{dc}$.
-We perform the sweep for a non-oscillatory drive $F^{ac} = 0.0$.
+We also perform the sweep for a non-oscillatory drive $F^{ac} = 0.0$.
 With no oscillating component of the driving force,
@@
   The critical force $F^c$ is equal to the maximum substrate force
-  $A_p$ so the applied driving
-  force can move a particle over a substrate barrier.
+  $A_p$. 
   The addition of an $ac$ drive leads
@@
   over a range of driving forces $F^{dc}$.
-  In Fig.~\ref{fig:1}
+  In Fig.~\ref{fig:3_sweep_vyFDC}
   we sweep $F^{dc}$
   with $F^{ac} = 0.07$ and $f=0.01$.
-%the average velocity of the particle
-%is constant 
-%despite the overall magnitude
-%of $F^{dc}$.
 Each step represents a different pattern of hops
@@
 due to the landscape confinement.  
-At %this occurs at 
+At 
 low $F^{dc}$ the average velocity $\langle v_y \rangle$ is zero.
@@
 the particle oscillates back and forth
-in a single minima with no net velocity.
-%We plot the results in Fig.~\ref{fig:1} for 
-%  The modes appear as 
-%  discrete steps in $\langle v_y \rangle$ %occur because
-%  across a range of $F^{dc}$.
-%  On each of the first four modes,
-%  we mark a values of $F^{dc}$ to illustrate in Fig.~\ref{fig:phase}.
+in a single minima with no net velocity,
+a 0:0 mode.
 At higher $F^{dc}$ the particle velocity 
@@
 where $n$ is an integer.
+Here we observe a mode of $n=1$
+for the range $0.05 < F^{dc} < 0.08$,
+$n=2$ for $0.08 < F^{dc} < 0.11$,
+$n=3$ for $0.12 < F^{dc} < 0.13$,
+$n=4$ for $0.14 < F^{dc} < 0.155$ and 
+$n=5$ for $0.155 < F^{dc} < 0.16$.
+Higher modes are not visible.
 The step width is non-linear
@@
 such as a devil's staircase related to chaotic dynamics \cite{Bak1986}.
-%We note the individual steps
-%are not strictly horizontal 
-%since particles move continuously
-%through the landscape, so changes in $F^{dc}$
-%will create linear changes in 
-%net particle displacement that are observable
-%within a single step.
 \begin{figure} %[h!]
 \centering
-\includegraphics[width=\columnwidth]{fig3.pdf}
+\includegraphics[width=\columnwidth]{fig3_sweep_vyFDC.pdf}
 \caption{Average particle velocity  $\langle v_{y} \rangle$
@@
   $F^{ac}=0.07$ (orange) with $f = 0.01$ 
-  as in Fig.~\ref{fig:0}.
+  as in Fig.~\ref{fig:2_Fd_vy_time}.
   Each of the first four steps
@@
   indicating a system
-  plotted in Fig.~\ref{fig:phase}.
+  plotted in Fig.~\ref{fig:4_phase}.
 }
-\label{fig:1}
+\label{fig:3_sweep_vyFDC}
 \end{figure}
-%$\lambda = L/N_p = 36.5/20 = 1.825$ is the spatial period, or wavelength
-%of the landscape,
-%and $f = 0.01$ cycles per time unit.
-%This synchronization
-%of the particle velocity can be measured
-%in terms of the landscape period.
-%Phase locked steps occur for average displacements integer
-%multiples of the substrate period $n\lambda$.
-%\subsection{Phase plots}
-%  \label{ex:phase}
 
@@
   it is useful to compare
-  mode-locked quantities %periodic signals
+  mode-locked quantities 
   in a two dimensional phase plot. 
-  In a non-driven system, an appropriate
+  In a driven pendulum confined to a single potential well,
+  an appropriate
   phase space is particle velocity $v_y$ versus position $y$.  
-  For a particle driven parallel to the $y-$direction,
-  %the particle velocity and position increase
-  %in time. % due to $F^{dc}$.
-  %Since a system does not form
-  %a closed loop in
-  %$v_y$ vs $y$ space,
+  For a particle driven 
+  through multiple identical wells 
   we define phase variables 
-  to account for the net increase in velocity
-  and position.
+  to account for the net increase in position.
   The phase position is
-  defined as 
-  %within the substrate period as 
-  %We define a phase variable 
   \begin{equation}
-    %(y mod \lambda) / \lambda
     \phi(t) = 2\pi (y(t)-\langle v_y \rangle t)/\lambda
@@
   and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
-  For clarity our plots are normalized by the prefactor $2\pi$. 
-  %to compare $\phi(t)$ to $\lambda$.
-  %In phase diagrams we plot $\phi(t)$ %phase
-  %versus
   The phase velocity is
   \begin{equation}
-    %(y mod \lambda) / \lambda
-    \dot{\phi}(t) =2\pi (v_y(t)-\langle v_y \rangle) /\lambda.  % 
+    \dot{\phi}(t) =2\pi (v_y(t)-\langle v_y \rangle) /\lambda.  
   \end{equation}
@@
   the phase velocity will be zero when $F^d(t) = F^{dc}$.
-  %Juniper %REF 53
-  %and easily generated with a computer code 
-  %or oscilloscope \cite{Tong1997}.
   When velocity
-  is mode-locked to %repeat periodically
+  is mode-locked to 
   a spatial location
   a closed loop appears in  
-  phase space. % showing the relationship
-  %between two periodic functions
-  The pattern is determined by the mode,
-  or frequency ratio,
-  so a 1:1 mode appears as a circle or oval. 
-  Nodes appear %in the oval 
+  phase space. 
+  A 1:1 mode appears as a circle or oval. 
+  Nodes appear 
   for higher modes,
@@
   shifts in time.
-  In Fig.~\ref{fig:phase}, 
-  all cases exhibit some phase shifts %line thickening, 
+  In Fig.~\ref{fig:4_phase}, 
+  all cases exhibit some phase shift 
   indicating the particle location and velocity
-  are not fully synchronized,
-  although this can be tuned by
-  calculating $\langle v_y \rangle$ over
-  shorter time ranges.
-  %and the shifts in phase space represent
-  %small changes in system behavior.
-  %With a long simulation time,
-  %a quasiperiodic phase diagram
-  %fills the plotting region due to the gradual shift
-  %in the velocity-position relationship.
-  %with a frequency generator,
-  %where two combined frequencies at perpendicular orientations
-  %\footnote{The term phase
-  %has two scientific meanings:  
-  %oscillation phase $\phi_0$ is the constant of the argument
-  %in a periodic function
-  %$\sin{(\omega t + \phi_0)}$ and phase space is
-  %used to characterize oscillating systems with
-  %parametric plots.}.
-
-  %OKAY, WHY AREN'T MY AMPLITIDES \phi \pm 2\pi and \dot{\phi} \pm 4\pi.
-  In Fig.~\ref{fig:phase}
+  are not fully synchronized.
+
+  In Fig.~\ref{fig:4_phase}
   we plot $\dot{\phi}(t)$ versus $\phi(t)$
-  for increasing %substrate amplitude $A_p$.
-  $F^{dc}$, % and frequency $f = 0.01$ and $F^{ac} = 0.2$.
-  with the remaining parameters fixed as in Fig.~\ref{fig:0}.
-  In Fig.~\ref{fig:phase}(a) with
+  for increasing 
+  $F^{dc}$, 
+  with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
+  For clarity our plots are normalized by the prefactor $2\pi$. 
+  In Fig.~\ref{fig:4_phase}(a) with
   $F^{dc} = 0.04$
   the phase plot is a small asymmetric curve.
-  %centered at
-  %$(\phi,\dot{\phi})=(0.1,0)$.
   A tail appears
@@
   motion of the particle.
-  %with a semimajor axis of $\Delta \phi = 20$ %ANALYTIC
-  %and semiminor axis of $\Delta \dot{\phi} = 2\pi v_{max} /\lambda$.
   The particle is confined in a single
@@
   The asymmetry is caused by bias induced by $F^{dc}$.
-  In Fig.~\ref{fig:phase}(b)
+  In Fig.~\ref{fig:4_phase}(b)
   with $F^{dc} = 0.07$
@@
   particle motion and velocity consistent with 
-  Fig.~\ref{fig:0}(a).
-  %The maximum $\dot{\phi}$ %with a 1:1 mode locking,
-  %occurs at $\phi \sim 0.4$,
-  %and maximum $\phi$ occurs
-  %when $\dot{\phi} \sim 0$.
-  %
-  %The dynamical properties are asymmetric,
-  %with three nodes in the positive $\dot{\phi}$ values.
-  %[insert analysis.]
-  As $F^{dc}$ %the constant driving force 
+  Fig.~\ref{fig:2_Fd_vy_time}(a).
+  As $F^{dc}$ 
   increases,
@@
   of $\dot{\phi}$ over multiple phase positions.
-  %The motion becomes quasiperiodic
-  %so the loops in phase space do not fully overlap.
-  In Fig.~\ref{fig:phase}(c)
+  In Fig.~\ref{fig:4_phase}(c)
   with $F^{dc} = 0.1$
@@
   during one time period.
-  In Fig.~\ref{fig:phase}(d)
+  In Fig.~\ref{fig:4_phase}(d)
   with $F^{dc} = 0.125$
@@
       \centering
-      \includegraphics[width=\columnwidth]{phase.pdf}
-      %\vspace*{-3cm}
+      \includegraphics[width=\columnwidth]{fig4_phase.pdf}
       \caption{
@@
         The particle is driven with $F^{dc} = $ (a) $0.04$, (b) $0.07$, (c) $0.1$, (d) $0.125$.  These values are marked as black circles
-        in Fig.~\ref{fig:1}. %, (e) $0.25$ and (f) $0.3$.
+        in Fig.~\ref{fig:3_sweep_vyFDC}. 
       The other parameters
       are $F^{ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
-      as Fig.~\ref{fig:0}.}
-      \label{fig:phase}
+      as Fig.~\ref{fig:2_Fd_vy_time}.}
+      \label{fig:4_phase}
     \end{figure}
@@
 We include analytic exercises to examine the 
-to linear drag equation in Ex.~\ref{ex:reynolds}, 
+linear drag equation in Ex.~\ref{ex:reynolds}, 
 the equation of motion in Ex.~\ref{ex:n2l},
@@
 We extend the model with
-numerical exercises %extend the model
+numerical exercises 
 to include finite temperature effects
 in Ex.~\ref{ex:brownian}.
-%Methods to visualize the dynamics of the particle motion
-%are in Ex.~\ref{ex:animation}.
-%In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\langle v_{y} \rangle$ at which the particle in Fig. 1(a) is moving.
 
 \section{Associated problems}
-\label{sec:problems}	% You can label sections for reference
-%\begin{enumerate}
-%\item
-
-%\item
-  \subsection{Exploring Parameters of the Model}
+\label{sec:problems}
+
+  \subsection{Exploring model parameters}
   \label{ex:parameters}
@@
   and external driving force.
+
+  {\bf Explore the effect of increasing $F^{ac}$ on the hopping pattern.}
   For the single driven particle,
@@
   time period.
-  The total displacement of $(n_f - n_b) \lambda$ %integer steps of
+  The total displacement of $(n_f - n_b) \lambda$ 
   is the net hop length.  
-  %the substrate period $$ characterize
-  In Fig.~\ref{fig:0},
-  the particle moves forward through two minima ($n_f = 2$),
+  In Fig.~\ref{fig:2_Fd_vy_time},
+  the particle moves forward through a minima ($n_f = 1$),
   and does not move backward a full minima ($n_b = 0$).  
-  %such that the pattern
-  %is characterized as $2(2,0)$.
   In order to achieve
@@
   and a difference $|F^{ac} - F^{dc}| > A_p$.
-  %which can also produce large forward hops.
-  %INSERT figure with a range of hopping patterns for a run
-  The frequency must be sufficiently low so that 
+
+  In Ref.~\cite{Juniper2015}
+  experiments with single colloids 
+  produce 
+  the following
+  combinations of forward and backwards steps
+  by sweeping through
+  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$:
+  $n_f = 0$ to $6$ for $n_b = 0$,
+  $n_f = 0$ to $5$ for $n_b = -1$,
+  and
+  $n_f = 2$ to $3$ for $n_b = -2$.
+  In Fig.~\ref{fig:5_Fac_y_vs_time}
+  we fix $f=0.01$, $F^{dc}=0.07$, and $A_p = 0.1$
+  and increase
+  the amplitude of $F^{ac}$.
+  This causes the number of backwards steps to increase.
+  The number of forward steps also increases
+  due to the increased total positive amplitude of $F^d(t)$.
+  In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
+  $F^{ac} = 0.2$ %, $0.3$ and $0.4$.
+  the number of backwards steps
+  $n_b = 0$ with $n_f = 4$.
+  In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F^{ac} = 0.4$
+  $n_b = 2$ and $n_f = 6$.
+  In each case the average velocity 
+  is $\langle v_y \rangle = 4\lambda f$,
+  which can be reproduced over a variety of $F^{ac}$ values.
+
+  %----------------------------------------------------------
+  \begin{figure} %[h!]
+      \centering
+      \includegraphics[width=\columnwidth]{{fig5_Fac_y_vs_time}.pdf}
+      \caption{
+        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:2_Fd_vy_time} and increasing $F^{ac} = $
+        (a) $0.2$ and
+        (b) $0.4$.
+      }
+      \label{fig:5_Fac_y_vs_time}
+    \end{figure}
+  %----------------------------------------------------------
+
+  {\bf Explore the effect of increasing the driving frequency on the hopping pattern.}
+  In Section ~\ref{sec:results}
+  the frequency is sufficiently low so that 
   the applied force is large
@@
   allowing a particle to hop a substrate maxima.
-  {\bf Explore the effect changing the driving frequency on the hopping pattern.}
-
-  Fig.~\ref{fig:hops}
-  shows the effects of lowering the frequency
-  of applied driving force
+  Fig.~\ref{fig:6_freq}
+  shows the effects of increasing the frequency
+  of applied driving force.
   We hold the remaining parameters fixed 
@@
   since $F^{dc} - F^{ac}= 0.0$.
-  %is too small to overcome $A_p$.
   The rate of forward hops 
@@
   but in each case the particle
-  hops across one substrate periods as in Fig.~\ref{fig:0}.
-  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
-  do not match the temporal period of $F^d(t)$
-  due to the high frequency.
-  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.05$
+  hops across at most one substrate periods as in Fig.~\ref{fig:2_Fd_vy_time}.
+  In Fig.~\ref{fig:6_freq}(a)
+  the high frequency $f=0.05$ suppresses forward motion entirely.
+  The high frequency 
   is apparent in the undulations of the particle
   with a period of $20\tau$.
-  %Due to the high frequency,
-  The particle is trapped between substrate minima.
-  %$y \approx \lambda/2 $ for
-  %a time interval of $400 \tau$.
-  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.022$
+
+  In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
   with a period of $45\tau$
@@
   the hopping rate matches the driving frequency,
-  as in Fig.~\ref{fig:0}.
-  In Fig.~\ref{fig:hops}(c) $f=0.005$
+  as in Fig.~\ref{fig:2_Fd_vy_time}.
+  In Fig.~\ref{fig:6_freq}(c) $f=0.005$
   the particle hops forward two minima every period of $200\tau$.
@@
   result in sustained positive motion of a particle.
-  In Fig.~\ref{fig:hops}(e) $f=0.001$
+  In Fig.~\ref{fig:6_freq}(e) $f=0.001$
   the hopping is continuous
@@
   over the period length $1000 \tau$.
+  %------------------------------------------------------------
   \begin{figure} %[h!]
     \centering
-      \includegraphics[width=\columnwidth]{{fig5}.pdf}
+    \includegraphics[width=\columnwidth]{{fig6_freq}.pdf}
     \caption{
-        Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.05$, 
-        (b) $0.022$, (c) $0.005$ and (d) $0.001$. %where  
-        %the particle wraps the periodic boundary conditions.
+      Motion of a particle with the same values of $F^{dc} = 0.07$ and $F^{ac} = 0.07$ as Fig.~\ref{fig:2_Fd_vy_time} and decreasing frequency $f=$ (a) $0.05$, 
+        (b) $0.022$, (c) $0.005$ and (d) $0.001$. 
     }
-      \label{fig:hops}
+    \label{fig:6_freq}
   \end{figure}
-  %In Fig.~\ref{fig:hops}
-
-  Hopping patterns with backward steps are more difficult
-  to achieve than forward.
-  In Ref.~\cite{Juniper2015}
-  experiments with single colloids 
-  produce 
-  the following
-  combinations of forward and backwards steps:
-  $n_f = 0$ to $6$ for $n_b = 0$,
-  $n_f = 0$ to $5$ for $n_b = -1$,
-  and
-  $n_f = 2$ to $3$ for $n_b = -2$
-  %were realized 
-  by sweeping through
-  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
-  %{\bf Find the parameters
-  %that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
-  %[well, go on...]
-
-  In Fig.~\ref{fig:hops_back}
-  we fix $f=0.01$, $F^{dc}=0.07$, and $A_p = 0.1$
-  and increase
-  the amplitude of $F^{ac}$.
-  This causes the number of backwards steps to increase.
-  The number of forward steps also increases
-  due to the increased total positive amplitude of $F^d(t)$.
-  In Fig.~\ref{fig:hops_back}(a) 
-  $F^{ac} = 0.2$ %, $0.3$ and $0.4$.
-  %of the system for our original parameters.
-  the number of backwards steps
-  $n_b = 0$ with $n_f = 4$.
-  In Fig.~\ref{fig:hops_back}(b) $F^{ac} = 0.4$
-  $n_b = 2$ and $n_f = 6$.
-  %In Fig.~\ref{fig:hops_back}(c) 
-  %$n_b = 4$ and $n_f = 10$.
-  In each case the average velocity %net displacement
-  is $\langle v_y \rangle = 4\lambda f$,
-  which can be reproduced over a variety of $F^{ac}$ values.
-
-    \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{fig6}.pdf}
-      \caption{
-        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac} = $
-        (a) $0.2$ and
-        (b) $0.4$.
-      }
-      \label{fig:hops_back}
-    \end{figure}
-
-    In Fig.~\ref{fig:shapiro}
+  %------------------------------------------------------------
+
+  In Fig.~\ref{fig:7_sweep2_vyFDC}
   we sweep the constant driving force $F^{dc}$
@@
   over a broader range of $F^{dc}$.
+  %------------------------------------------------------------
   \begin{figure} %[h!]
     \centering
-      \includegraphics[width=\columnwidth]{{fig7}.pdf}
-      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
+    \includegraphics[width=\columnwidth]{{fig7_sweep2_vyFDC}.pdf}
       \caption{
@@
         with frequency $f=0.01$.
-        The substrate is as in Fig.~\ref{fig:0}
+        The substrate is as in Fig.~\ref{fig:2_Fd_vy_time}
         with $A_p = 0.1$.
       }
-      \label{fig:shapiro}
+      \label{fig:7_sweep2_vyFDC}
     \end{figure}
-  %In Fig.~\ref{fig:hops}
-%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
-%  \item The Fokker-Planck Equation
-%  \item Aubrey-Kontorova + commensurability
-%  \item nanotribology
- %   kink motion
- %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
-  %\item
-  %\subsection{Visualizing motion}
-  %\label{ex:animation}
-  %Drawing the contour 
-  %The code for generating
-  %a two dimensional colored plot
-  %of the potential landscape
-  %is calculated by evaluating
-  %the analytic function in Eq.~\ref{eq:ysubstrate}
-  %for a grid of values $(x_n,y_n)$.
-  %is included in the supplementary material,
-  %{\it I have python code that does all of this, but I don't have it
-  %  set up to play nice with my new python MD code} 
-    %Also the animation library in python...
-
-\subsection{Drag Models and Reynolds Numbers.}
+
+  \subsection{Drag models and Reynolds numbers.}
   Stokes' law describes the drag force
@@
   such that $3 \pi D \eta \rightarrow \eta $.
-  %
   Often drag forces are
@@
   \end{equation}
-  %This model should be familiar to readers
-  %of a standard classical mechanics text, such as Ref.
-  %when studying 
-  %models Millikan's oil drops.
   Truncating the series to the first term
@@
 
-  %viscosity coefficient & $\eta = F_0 \tau / {a_0}^2 $ & $\eta \sim 10^{-3}$ Pa-s \\
   To first order the viscosity is $\eta \sim 10^{-3}$ Pa-s \cite{Volpe2013}.
-  %or $9 \times 10^{-8} kg/s$ \cite{Juniper2017}.
   {\bf Using reasonable values for the
@@
   In addition to the values listed in Table ~\ref{tab:1}, 
- % Approximate experimental values for
- % a colloid size and speed
- % are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
- % %Likewise
- % since 
- % viscosity of water decreases with temperature
- % from $1.3 \times 10^{-3}$ Pa-s at $10^{\circ}$ C to 
- % from $0.31 \times 10^{-3}$ Pa-s at $90^{\circ}$ C,
- % where 1 Pascal is $1$ N/m$^2$.
-  %Likewise
-  the liquid density %$\rho$ varies with temperature
-  %with
+  the liquid density 
   $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
@@
 
-%  [{\it could certainly do more with this question to make it more computational.
-For instance, plot $R$ as a function of any of the parameters $v$, $D$ and $\rho$, include a temperature dependent $\eta(T)$ in the Brownian system.
-Suggest students model something big to imagine their own life at low Reynolds number...
-fairly off topic...}]
-
 \label{ex:reynolds}
 
-%\item
-\subsection{Equation of Motion}
+\subsection{Equation of motion}
   \label{ex:n2l}
-
   Newton's second law states that
@@
   described in Ex.~\ref{ex:reynolds}.
-  The ratio of $m/\gamma$ is %has units of time, % and is 
+  The ratio of $m/\gamma$ is %
   known as the momentum relaxation time, %.
@@
   leading to a momentum relaxation time
-  % \tau = 15 nanograms/(3 pi D \eta)
-  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
   on the order of microseconds.
-  %of $1.6 ~\mu$s.
   {\bf Confirm for the values listed in Table ~\ref{tab:1},
@@
 
-%  {\it this isn't very challenging, but I've see undergraduate students have a ``wow'' factor when they work this out for the first time.
-This is closely related to the next exercise which is also primarily analytic rather than computational}
-
-%\item
-  \subsection{Integration Methods}
+  \subsection{Integration methods}
   \label{ex:euler}
-  %{\it cut this one?  not really saying much}
   To calculate the position of the particle we
@@
   via the 
-    %In our model we use the
-    Euler method. % to solve this equation.
+  Euler method. 
   Our equation of motion provides
@@
   is kept sufficiently small \cite{Newman}.
-    %but it is an uncommon choice.
   In our simulations we use the timestep $\Delta t = 0.1$
@@
   i.e. $dy/dt = v$ and $dv/dt = f_2(y,t)$.
-  %where $f_2(y,t)$ is a second derivative function.
   In Newton's second law $f_2$ would be proportional
@@
   $a = dv/dt = 0$,
-  %and thus rearrange $f_2(y,t)$ to solve directly for $v$,
   as described in Ex.~\ref{ex:n2l}.
-  %The Taylor expansion of the position function $y(t)$
-  %\begin{equation}
-  %  y(t_n \pm \Delta t) = y(t_n) \pm \frac{dy}{dt} \Delta t + \frac{1}{2} \frac{d^2y}{dt^2} (\Delta t)^2 + \ldots
-    %\pm O(\Delta t)^3 ... %\frac{1}{6} \frac{d^3y}{dt^3} (\Delta t)^3 + ...
-  %\end{equation}
-  %is exact at first order
-  %for the $n$-th time step.
-  %Demonstrate how the Verlet method
-  %simplifies to the Euler method when
-  %the particle acceleration $a=0$.
-  %We invite interested students to repeat this
-  %simulation for any initial particle position %of $y$
-  %and a range of simulation constants
-  %to demonstrate that synchronization in this model
-  %does not depend on a particular set of conditions.
-  %but is a direct consequence of the simplicity of the model.
-  %\item
 
@@
 
-  %Consider a non-zero temperature in the simulation.
-  %in which particles will collide with invisible particles
-  %making up the suspending fluid.
   In molecular dynamics simulations
@@
   to the visible particles.
-  %\footnote{%In our simulations %np.random.normal
   We use the normal distribution from the NumPy random module
@@
   A normalized random distribution of forces
-  causes fluctuations in %particles to emulate Brownian
+  causes fluctuations in 
   motion 
@@
   $t = N \Delta t$.
-  %Random normal distributions are not correlated 
-  %over the independent variable,
-  %for the independent variable to be time
-  %\begin{equation}
-  %\langle f^T(t) f^T(\tau)\rangle = 2 \eta k_B T \delta(t-\tau)
-  %\end{equation}
-  %for times $t$ and $\tau$,
-  %where $\delta(t-\tau)$ is the Dirac-delta function.
-  %Here the scaling factor energy of 
-  %$k_B T$ is
-  %derived from the Boltzmann constant $k_B$
-  %and temperature $T$ \cite{Allen2017}.
   A particle
@@
   barriers.
-  % (a) 
   In our simulations,
@@
   to
-  %In these units
   compare directly with force.
-  %in order to estimate the degree of random fluctuation.
 
@@
     to hop over maxima in the potential landscape.}
-  %$T_{min} > A_p$.
   Assume the particle is confined to
@@
   in the model.
-  %The crossover
-  %to a hopping regime occurs at $T/A_p \approx 5.6$.
-  %Reproduce these results.  
+  %----------------------------------------------------
     \begin{figure} %[h!]
       \centering
-      \includegraphics[width=\columnwidth]{{fig4}.pdf}
+      \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
       \caption{
@@
         (a) $T/A_p = 3.0$ no hopping occurs.
-        (b) $T/A_p = 3.5$ one hop occurs and %at $t = 130000$
-        %across distances of $\Delta y = 2 \lambda$.
+        (b) $T/A_p = 3.5$ one hop occurs and 
         (c) $T/A_p = 4.0$ many hops occur.
@@
         and the time scale is
-        greater than in Fig.~\ref{fig:0}.
+        greater than in Fig.~\ref{fig:2_Fd_vy_time}.
         The precise timing of hops pattern varies
@@
       }
-      \label{fig:brownian}
+      \label{fig:8_brownian}
     \end{figure}
 
-  In Fig.~\ref{fig:brownian}
+  In Fig.~\ref{fig:8_brownian}
   we show the position versus time of a particle
@@
   troughs until the particle enters a hopping regime.
-  In  Fig.~\ref{fig:brownian}(a)
-  the temperature is $T/A_p = 4.0$.
+  In  Fig.~\ref{fig:8_brownian}(a)
+  the temperature is $T/A_p = 3.0$.
   The particle executes a 
@@
   within this simulation time.  
-  In  Fig.~\ref{fig:brownian}(b)
-  $T/A_p = 5.0$,  hops between
+  In  Fig.~\ref{fig:8_brownian}(b)
+  $T/A_p = 3.5$,  hops between
   potential minima are possible but not probable,
-  a back-forth hop occurs from
-  $y/\lambda = 10$ to $12$ at
-  $t \sim 40000 \tau$ and a single hop from 
-  $y/\lambda = 10$ to $8$ occurs at
-  $t \sim 280000 \tau$.
+  a hop occurs from
+  $y/\lambda = 10$ to $9$ at
+  $t \sim 23000 \tau$. 
   In other simulations with identical parameters,
@@
   as expected with random fluctuating systems.
-  In  Fig.~\ref{fig:brownian}(c)
-  $T/A_p = 6.0$ 
+  In  Fig.~\ref{fig:8_brownian}(c)
+  $T/A_p = 4.0$ 
   we observe many hops.
@@
   a random walk of hops atop the substrate.
-  [prove it]
-  %in addition to the small scale random walk executed
-  %by all particles in this section.
-
-  %A quantity of interest
-  %for a particle undergoing Brownian motion
-  %is the rate of displacement
-  %of the particle from its initial position 
-  %This is measured as mean square displacement
-  %as a function of time
-  %\begin{equation}
-  %  \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
-  %\end{equation}
-  %where $t_0$ is the initial time at
-  %initial position $\vec{r}(t_0)$.
-  %With no substrate, we would expect
-  %the root mean square displacement (RMSD)
-  %to be proportional to the elapsed time 
-  %\begin{equation}
-  %  \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
-  %\end{equation}
-  %Confirm this result for $A_p = 0$.
-  %%[INSERT advice on length of time to run?]
-  %Measure the RMSD as a function of time
-  %of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
-  %as shown in Fig.~\ref{fig:brownian}.
-  %Compare your result to the
-  %substrate free RMSD.
-  %%[INSERT EXPECTED RESULTS.  presumably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]
-
-  %(b)
+
   For a driven particle,
@@
   in these simulations.  
-  We note that even at $T/A_p = 6.0$ 
+  We note that even at $T/A_p = 4.0$ 
   the hopping rate
@@
   frequency of the applied drive.
-  This can be seen in the time scale in Fig.~\ref{fig:brownian},
+  This can be seen in the time scale in Fig.~\ref{fig:8_brownian},
   where the average hopping rate is approximately
-  every $15000\tau$,
-  a value much larger than $T = 100\tau$.
+  every $4000\tau$,
+  a value much larger than the period of the driving force.  
   At sufficiently high temperatures,
@@
   and can be observed in experiments.
-  %[explore]
-  %and could be included
-  %to emulate noise seen in some 
-  %How does Brownian motion affect
-  %With driving force reproduce the paper figures...
-  %%[there is no way I want to run this with python...]
 
 \section{Conclusion}
-\label{sec:conclusion}	% You can label sections for reference
-
-%Fundamental models
-%of synchronization 
-%can %include many coupled oscillators
-%or
-%focus on
-%We have driven 
+\label{sec:conclusion}	
 A single particle driven across a periodic potential landscape 
-%Single particle studies are useful
-synchronizes its motion %to study synchronization dynamics
-%that arise
+synchronizes its motion 
 to environmental and external forces,
 a phenomena known as mode-locking.  
-%due to interactions between particles.
 Our simulations reproduce experiments and simulations presented in 
@@
 mode locking in
-%experiments and simulations of 
 driven colloids on a
@@
 making ideal proxies 
-for systems %relatively
+for systems 
 such as cold atoms or electron gases \cite{Grier2003}.
-%which are 
-%hard to access and visualize 
-%Collections of colloids can
-%be used to study the properties of solids and liquids
-%or more exotic systems 
-%Oscillators ordered into chains or lattices.
-%has many important
-%technological applications
-Dynamical mode-locking %, the primary synchronization
-%effect explored in this paper, 
-is %often
-observed important technologies such as 
+Dynamical mode-locking 
+is 
+observed in important technologies such as 
 in quantum electronic
-devices %, such as Josephson junctions \cite{Josephson1962,Josephson1965}, 
-%A single junction contains 
-%two superconductoring layers which sandwich an insulating layer.
-%When subject to an external voltage,
-%Cooper pairs in the superconducting materials
-%tunnel through the insulating layer.
-%Phase-locking is observed in these devices
-as 
+devices as 
 stepped regions in current-voltage (I-V) relationship,
@@
 and current is that of particle velocity.
-Known as Shapiro steps, % \cite{},
+Known as Shapiro steps, 
 these mode-locked or phase-locked currents  
@@
 coupled arrays of junctions \cite{Benz1990}.
-%laser gyroscopes
-%Chow, W. W. et al. The ring laser gyro. Rev. Mod. Phys. 57, 61–104 (1985).
-%dusty plasmas?
 Shapiro steps vary in width depending on the strength of the
@@
 displaying
-%are hallmarks of
 non-Ohmic behavior in voltage-current curves,
@@
 engineered with periodic patterns of pinning sites \cite{Reichhardt2000}.
-%Thus the study of
 Mode-locking is a useful probe 
@@
 
-%where these steps are generated
-%by the tendency of the response of a system
-%to be flat across a range of applied driving forces or voltages,
-%which can be probed with
-%  atoms on surfaces.
-%  voltage driven superconducting vortices
-%  confined in a Josephson junction,
-%mini review of synchronization in electronics
-%careful - the following is all simulations
-%Recent studies demonstrate
-%that coupled electronic oscillators can be
-%programmed for use as micro-controllers for robotic locomotion \cite{Dutta2019}.
-
-%\section{Quasi-periodic substrate}
-%\label{sec:quasiperiod}	% You can label sections for reference
-
-%\section{Chaotic dynamics}
-%\label{sec:chaos}	% You can label sections for reference
-
 \begin{acknowledgments}
@@
   % seems to make no discernible difference.
-
-  %useful quick ref
-  %http://www.scholarpedia.org/article/Synchronization
 
@@
 
+    %huygens clocks
   \bibitem{Singer1999} W. Singer. Striving for coherence. Nature, {\bf 397} 391, 1999.
@@
 
+  %colloids
   \bibitem{Pertsinidis2001} A.
@@
 
-      %reichhardt review
+  %general particle on washboard
   \bibitem{Reichhardt2017} C.
@@
 
+  %overdamped justification
   \bibitem{Purcell1977} E. M. Purcell, Life at low Reynolds numbers, Am. J. Phys. {\bf 45}, 3–11 (1977).
 
-    %condensed matter intro
+  %chaos!
   \bibitem{Bak1986} P. Bak. The Devil's Staircase. Physics Today {\bf 39}, 12, 38 (1986).
 
+  %overdamped justification
   \bibitem{Taylor2005} J. Taylor,  Classical mechanics. University Science Books (2005).
 
+  %brownian motion!
   \bibitem{Volpe2013} G. Volpe and G. Volpe, Simulation of a Brownian particle in an optical trap, Am. J. Phys. 81 (3), March 2013
 
+  %viscosity and density citation
   \bibitem{asce}
@@
 
+  %numerical solutions of differential equations
   \bibitem{Newman} M. Newman, Computational Physics, CreateSpace Independent Publishing Platform. (2012).
 
-   %   \bibitem{supp1} Supplementary videos coming soon.
-        %See Figure1.mp4 in appropriate %\url{}
-
-  \bibitem{Einstein1905} A Einstein, Investigations on the Theory of the Brownian Movement,  Dover Publications (1956).
+    %Brownian motion!
+  \bibitem{Einstein1905} A. Einstein, Investigations on the Theory of the Brownian Movement,  Dover Publications (1956).
 
@@
 
-           %PRACTICAL APPLICATION
-    %\bibitem{Agrawal2013} D.
-K.
-Agrawal, J.
-Woodhouse, and A.
-A.
-Seshia, Observation of locked phase dynamics and enhanced frequency stability in synchronized micromechanical oscillators, Physical Review Letters {\bf 111}, 084101 (2013).
-
-          %technological applications
-    %\bibitem{Dutta2019} Dutta, S., Parihar, A., Khanna, A. et al. Programmable coupled oscillators for synchronized locomotion. Nat Commun {\bf 10}, 3299 (2019).
-
-    %\bibitem{Lissajous1857} J. A. Lissajous.  "Mémoire sur l'Etude optique des mouvements vibratoires,"  Annales de chimie et de physique, 3rd series, 51 (1857) 147-232
-
-    %\bibitem{Tong1997} E. Y. C. Tong, Lissajous figures, The Physics Teacher {\bf 35}, 491 (1997).
-
-    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. 11, 80 (1963).
+   %Josephson Junctions and other condensed matter applications
+    \bibitem{Shapiro1963} S. Shapiro, Josephson currents in superconducting tunneling: the effect of microwaves and other observations, Phys. Rev. Lett. {\bf 11}, 80 (1963).
 
@@
 Lett.
-64, 693 (1990); D.
+{\bf 64}, 693 (1990); D.
 Dom{\'i}nguez and J.
@@
 Lett.
-69, 514 (1992).
+{\bf 69}, 514 (1992).
 
@@
 
-      %quote: Phase engineering techniques are used to control the dynamics of long-bosonic Josephson-junction arrays built by linearly coupling Bose-Einstein condensates.
-
-%\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.
-
-%\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.
-
-%\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
-%\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).
-
-%\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.
-
-%\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
-%entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
-%\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.
-
-%\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.
-
-%\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
-%and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
-%are incompatible with AJP's editing process.
-
-%\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook} for an excellent overview of math symbols and equations, with examples.
-
-%\bibitem{labelnames} Thinking up a good label name takes a moment, but 
-%it's worth the trouble; we strongly advise against using labels like 
-%\texttt{eq2}, which become extremely confusing after you decide to add 
-%another equation before Eq.~(\ref{deriv}).
-
-%\bibitem{footnotes} You need to process a file twice to get the counters correct.
-
-%\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
-%Phys. Today \textbf{42} (10), 9--11 (1989).  
-% Note that the issue number (10) in this citation is required, because
-% each issue of Physics Today starts over with page 1.  Also note the use of
-% an en-dash (--), not a hyphen (-), for the page range.
-
-%\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
-%\url{<http://ajp.dickinson.edu>}.
-
-%\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
-%\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
-% Note that this book is paginated by chapter; "3-10" is a single page reference
-% that uses a hyphen, not a range of pages that would us an en-dash (--).
-
-%\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
-%a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
-%bibliographic references must be incorporated into the manuscript file
-%as shown here, at least when you send an editable file for production.
-
-%\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
-%Am. J. Phys. \textbf{58} (3), 209--211.  
-% The issue number (3) in this citation is optional, because AJP's pagination 
-% is by volume.
-
-%\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
-%\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
-%G. W. F. Drake (AIP Press, New York, 1996), p.~520.
-
-%\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
-%Institute of Physics, New York, 1990). Available online at 
-%\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
-%it have been made out of date by advancing technology, most of this manual 
-%is still as useful as ever. Just be sure to follow AJP's specific rules
-%whenever they conflict with those in the manual.
-
 \end{thebibliography}
 
-% If your manuscript is conditionally accepted, the editors will ask you to
-% submit your editable LaTeX source file.  Before doing so, you should move
-% all tables and figure captions to the end, as shown below.  Tables come 
-% first, followed by figure captions (with figure inclusions commented-out).
-% Figures should be submitted as separate files, collected with the
-% LaTeX file into a single .zip archive.
-
-%\newpage   % Start a new page for tables
-
-%\begin{table}[h!]
-%\centering
-%\caption{Elementary bosons}
-%\begin{ruledtabular}
-%\begin{tabular}{l c c c c p{5cm}}
-%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
-%\hline
-%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
-%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
-%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
-%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
-%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
-%\end{tabular}
-%\end{ruledtabular}
-%\label{bosons}
-%\end{table}
-
-%\newpage   % Start a new page for figure captions
-
-%\section*{Figure captions}
-
-%\begin{figure}[h!]
-%\centering
-%\includegraphics{GasBulbData.eps}   % This line stays commented-out
-%\caption{Pressure as a function of temperature for a fixed volume of air.  
-%The three data sets are for three different amounts of air in the container. 
-%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
-%that this is a vector graphic, so it can be viewed at any scale without
-%seeing pixels.)}
-
-%\label{gasbulbdata}
-%\end{figure}
-
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Supplementary Materials}
-
-\subsection{Gridded Contour Plot of landscape}
-%code is located in
-%~/pymodules/animation_code/channel_colloid_movie_maker.py
-
-\begin{verbatim}
-##########################################################
-#ADD CONTOUR PLOT
-##########################################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color in the quasi1D potential to contain 
-    the particles in a trough.  
-    Can also add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    a_p = L/N
-
-    #assuming Tiare's trough system, so we won't want to cover the entire range
-    X = np.arange(0, L/2.0, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 2.0 # set by what "looks good"
-    Z = Z_mag*np.sin(2*np.pi*X/L)
-    if corrugated == True:
-        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
-
-    cmap=cm.coolwarm_r
-
-    #alphs is the degree of transparency, again, set by what looks good.
-    cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.25)
-
-    #ax1.set_xlim(15,20)
-    #ax1.set_ylim(15,20)
-
-    #ax1.set_xlabel(r"$X$")
-    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
-
-    #ax1.set_xticks([])
-    #ax1.set_yticks([])
-    return
-\end{verbatim}
-
-%another confinement technique:
-%Acoustic tweezers and surface acoustic wave (SAW) \cite{}
-%confines single cells and particles with lower energy than light / lasers
-%%X. Ding, J. Shi, S.-C. S. Lin, S. Yazdi, B. Kiraly and T. J. Huang, “Tunable patterning of microparticles and cells using standing surface acoustic waves” Lab Chip, 2012, 12, 2491– 2497.
-%%%Acousto-optically generated potential energy landscapes: Potential mapping using colloids under flow Michael P. N. Juniper,1,∗ Rut Besseling,2 Dirk G. A. L. Aarts,1 and Roel P. A. Dullens1
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Grid Contour Plot of landscape}
-%code is located in
-%~/pymodules/animation_code/channel_colloid_movie_maker.py
-Testing section - how will putting the code directly in the appendix appear?
-
-\begin{verbatim}
-############################################
-#ADD CONTOUR PLOT
-############################################
-def add_contour(ax,L,N,corrugated = True):
-    '''
-    Hardwired to color quasi1D potential
-    that contains 
-    the particles in a trough.  
-    Can add the washboard/corrugated substrate.
-
-    Required Arguments
-
-    Optional Arguments:
-
-    corrugated (default = True)  
-    Adds the washboard in the y-direction.  
-    Hardwired for a single parameter set.    
-    '''
-
-    a_p = L/N
-
-    #we don't want to cover the entire range
-    X = np.arange(0, L/2.0, 0.1)
-    Y = np.arange(0, L, 0.1)
-    X, Y = np.meshgrid(X, Y)
-
-    Z_mag = 2.0 # set by what "looks good"
-    Z = Z_mag*np.sin(2*np.pi*X/L)
-    if corrugated == True:
-        Z += np.sin(2*np.pi*(Y+1.75)/a_p)
-
-    cmap=cm.coolwarm_r
-
-    #alpha = transparency. set by what looks good.
-    cset = ax.contourf(X,Y,Z,cmap=cmap,alpha=0.25)
-
-    #ax1.set_xlim(15,20)
-    #ax1.set_ylim(15,20)
-
-    #ax1.set_xlabel(r"$X$")
-    #ax1.set_ylabel(r"$y$",rotation='horizontal',ha='right')
-
-    #ax1.set_xticks([])
-    #ax1.set_yticks([])
-    return
-\end{verbatim}
-
-\item Kuramoto model = overdamped interacting rotors/oscillators are used to model coupled oscillator systems - no substrate or external drive so far as I can see - this seems baked into the oscillator properties/interactions
-%D. Métivier, L. Wetzel, and S. Gupta
-%Onset of synchronization in networks of second-order Kuramoto oscillators with delayed coupling: Exact results and application to phase-locked loops
-%PHYSICAL REVIEW RESEARCH 2, 023183 (2020)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Supplementary Materials}
-
-\section{Synchronized particle chains}
-\label{sec:sync}
-The interaction forces between colloids can be controlled 
-by altering the chemistry of the suspending fluid
-or surface ligands of the particles.
-Thus colloids can 
-be modified to mimic different
-systems such as hard spheres interacting via contact forces \cite{},
-dipole interactions \cite{},
-and long range electrostatic interactions \cite{}.
-
-Mode-locked 
-colloid dynamics have been achieved in 
-experiments \cite{Juniper2015, Lutz2004} and
-simulations \cite{Herrera-Velarde2007, Herrera-Velarde2008} 
-for a variety of interaction types such as 
-magnetic dipoles and electric forces.
-%-----------------------------------------------------------
-%particle interaction types
-%Particles which interact over long distances
-%include colloids, magnetic beads, superconducting vortices, dusty plasmas, electron gases. [more%e detail and references]
-%Particles which interact over short distances include
-%bubble arrays/emulsions [more systems and references].----------------------
-%The presence of a modulating surface
-%can modify these patterns in a variety of ways,
-%changing the onset of dynamical flows,
-%and the overall flow patterns.
-%  adjustable strength, geometry and length scale of substrate potential
-%Baumgartl, Brunner, Bechinger, PRL 93, 168301 (2004).
-%Baumgartl, Zvyagolskaya, Bechinger, PRL 99, 205503 (2007).
-
-%-----------------------------------------------
-%environments
-Particles in confined geometries behave differently than free particles.
-Stabilized charged particles form patterns
-due to the interplay of the confining landscape 
-and particle interactions.
-Narrow channels studies are useful to provide insights 
-of how particles move through systems 
-such as charge carries in quantum wires \cite{Tarucha1995} and
-slime molds in microchannels \cite{Gholami2015}.
-%Biological systems such as
-%neuron axons and capillaries can also be studied
-%with these models [more detail and references].
-%Many such systems execute local oscillations
-%about stable points [elaborate].
-%------------------------------------
- In multi-particle simulations, we confine
- the particles to a narrow region
- along the $x-$direction 
- using a periodic function 
- \begin{equation}
-   U_{q1D}(x) = U_{q0} \cos{(\pi x / L)}
-     \label{eq:xsubstrate}
- \end{equation}
- where $U_{q0}$ defines the channel depth.
- %%We could also use a Gaussian function.
- This 
- quasi-one-dimensional geometry
- confines the particles
- primarily to move 
- along the y-direction
- but allows for some lateral motion of particles.
- Otherwise the repulsive interaction between
- particles would cause them to spread throughout the system.
- %
- The total landscape potential energy function is the sum
- \begin{equation}
-   U_{landscape}(x,y) =  U_{q1D}(x) + U_{washboard}(y)
-   \label{eq:xylandscape}
- \end{equation}
-
-We explore collective effects in a 
-twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
-with a single period.
-\begin{equation}
-  \label{eq:channel}
-  U_l(x) = U_{0x} \cos{(\pi x/L)}.
-\end{equation}
-%where the trough heights is larger  $V_{0x}$,
-%and the associated force
-%\begin{equation}
-%\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
-%\end{equation}
-%restores particles to the center of a long narrow region of the simulation.
-The landscape potential energy is illustrated in Fig.~\ref{fig:2}(a)
-where red regions are high potential
-and blue regions are low potential.
-
- We model particle interaction forces
-$\vec{F}_{ij} = -\nabla U_{ij}(r_{ij})$ 
-with
-the Yukawa potential $V_{ij} = U_{ij} / q$ 
-\begin{equation}
-  V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
-  \label{eq:yukawa}
-\end{equation}
-where particle $i$ and $j$ are distance
-$r_{ij} = |\vec{r}_i - \vec{r}_j|$ apart.
-This 
-screened Coulomb potential
-%$E_0=2$ scales strength of repulsion
-is scaled in terms of energy unit $E_0$
-defined in Table ~\ref{tab:1}.
-[elaborate for students $F_{Coulomb} = = k q_1 q_2 / r^2$, check scaling/units].
-$\kappa = 1/R_0$ is the screening parameter 
-that describes the length scale at
-which particles interact.
-We fix the screening length scale $R_0$ to be $a_0$
-(i.e. unity in simulation units).
-In experiments charge screening is observed
-due to ions in the suspending fluid and
-the charges of surrounding particles
-which
-reduces the interaction range of individual particles. % \cite{}.
-Because the particles interact over short ranges, 
-the numerical models can be run efficiency
-using a neighbor list algorithm
-determined using a cell method.
-[explain and reference!]
-
-Newton's second law can be rearranged %for the velocity
-to
-the equation of motion a single particle subject to collective effects is 
-\begin{equation}
-  \eta \vec{v}_i = \vec{F}^l_{i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
-    \label{eq:motion}
-\end{equation}
-
-The initial configuration of the system is shown in 
-Fig.~\ref{fig:2}(a).  
-We annealed the system into a ground-state configuration
-by raising the system to a high temperature $T$,
-and slowly lowering the temperature in steps of $dT=-0.01$
-until the particles form a buckled chain in the low region of the channel
-due to the
-competition between particle repulsion and channel confinement.
-The interparticle forces between neighboring particles
-cause the system to form a buckled chain. % when the system is annealed.
-The molecular dynamics of simulated annealing
-is described in Ref.~\ref{Allen2017}.
-Once the ground state particle configuration is obtained,
-no further annealing is necessary,
-so the
-our simulations begin with particle configurations
-that result from the annealing process,
-as listed in Appendix [ref] and available in supplementary material.
-
-When a single particle is driven, the neighboring particles act similarly to a periodic landscape to impede its motion.
-A driven particle can exhibit mode locking with a well-chosen ac drive and frequency.
-In the attached movie, Figure2.mp4, we show the complex dynamics of mode locking, where the driven particle leap-frogs past the other particles.
-
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{twenty}
-\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F^{ac}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel.
-The landscape is colored as in Fig.~\ref{fig1}(a).
-\textbf{(b)} Average $\langle {v}_{y} \rangle $ versus $F^{dc}$, where $\langle {v}_{y} \rangle$ is the average particle velocity of the driven particle in the y-direction.}
-\label{fig:2}
-\end{figure}
-
-\section{Kinked system}
-\label{sec:kink}	% You can label sections for reference
-We confine $N$ particles to $N-1$ troughs to create a
-local high density region.
-$F^{dc}/F^{ac} = 1$ [CHECK!]
-
-The addition of an oscillating force
-can lead to interference effects
-that create stepped force-velocity curves.
-Useful model - essentially an -
-under certain parameters.
-The steps occur
-due to the phase locking between lattice substrate
-and applied driving force.
-Step widths depend on AC drive.
-Discrete modes.
-
-  In Fig.~\ref{fig:phase}(b)
-  $A_p = 0.05$
-  the spatial properties are similar to
-  those in $A_p = 0.0$
-  with 
-  $(\phi,\dot{\phi})=(10,0)$
-  with a semimajor axis of $\Delta \phi = 20$.
-  The dynamical properties
-  are asymmetric,
-  with three nodes in the positive $\dot{\phi}$ values.
-  The thickening of the line
-  indicates the system is not fully synchronized.
-  [insert analysis.]
-  As the substrate
-  force becomes larger,
-  $\phi$ shifts to lower values
-  and $\dot{\phi}$ to positive values,
-  indicating
-  the particle can only move 
-  backward over a short distance.
-  In Fig.~\ref{fig:phase}(c)
-  $A_p = 0.1$
-  the phase properties are similar to
-  those in $A_p = 0.05$,
-  the three nodes have 
-  increased asymmetry in both phase variables 
-  $(\phi,\dot{\phi})$.
-  The nodes deepen,
-  indicating [insert analysis.].
-  In Fig.~\ref{fig:phase}(d)
-  $A_p = 0.2$
-  the pattern shifts
-  to two nodes,
-  [indicating change analysis].
-  In Fig.~\ref{fig:phase}(e)
-  $A_p = 0.25$
-  the system returns to a nodeless
-  orbit,
-  shaped like a triangle [because why?]
-  In Fig.~\ref{fig:phase}(f)
-  $A_p = 0.3$
-  the particle is trapped between substrate minima,
-  and traces out a small unclosed
-  orbit in phase space [because...]
-  The phase velocity is near zero
-  throughout the motion -
-  [comment on initial conditions]
-
-  %------------------------------------
-  We explore a range of parameters in Ex.~\ref{ex:parameters}
-where 
-we perform this sweep for several values
-of $F^{ac}$ including the limiting case that the applied force
-is a constant value.
-%When $F^{ac} = 0$, no steps appear
-%in the $\langle v_y \rangle $ vs $F^{dc}$ curve. 
-When $F^{dc} - F^{ac} < -A_p$ the particle
-moves in the negative y-direction 
-during part of the cycle.
-%We examine
-The period of the substrate
-can be used to control the
-net velocity of the dc driven particle,
-and the applied ac drive can cause mode-locking
-which appears as non-linear 
-steps in the force-velocity relationship.
-
- we can easily use 
-  %examine 
-  %for
-  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
-  over the same maximum time
-  (i.e. decrease the overall simulation time and sampling rate)
-  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
-  This is due to the linear nature of the solution
-  for an isolated particle.
-  %How to the motions of the particle compare when the timestep
-  %becomes large?
-  %[UPDATE]
-  {\bf Demonstrate the simulation timestep 
-  can be large
-  with no change to the overall physics
-  in the motion of a single particle.}
-  You will need to modify the maximum
-  simulation time, and the frequency of data saved for plotting purposes.
-
-  %--------------------------------------------------------
-    In Fig.~\ref{fig:brownian},
-  we demonstrate the transition
-  from pinned to hopping
-  in 
-  %Measure the position vs. time
-  a non-driven colloid for $T/A_p = 3.0$, $3.5$, and $4.0$.
-
-  \bibitem{Josephson1962} B. D. Josephson, Phys. Letters {\bf 16}, 25 (1962). 
-    \bibitem{Josephson1965} B. D. Josephson, Advan. Phys. {\bf 14}, 419 (1965).
-
-    \bibitem{Stewart1968}  W. C. Stewart, Current-Voltage Characteristics of Josephson Junctions, Appl. Phys. Lett. 12, 277 (1968).
-
-    \bibitem{Zhang2020} Dengling Zhang, Haibo Qiu, and Antonio Mu{\~n}oz Mateo, Unlocked-relative-phase states in arrays of Bose-Einstein condensates, Phys. Rev. A {\bf 101}, 063623 (2020).
-
-    \bibitem{Herrera-Velarde2008} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, Superparamagnetic colloids confined in narrow corrugated substrates, Phys. Rev. E {\bf 77}, 041407 (2008).
-
-    \bibitem{Herrera-Velarde2007} S. Herrera-Velarde and R. Casta{\~n}eda-Priego, J. Phys.: Condens. Matter 19, 226215 (2007).
-
-%Lutz  created 1D circular channels by means of scanning optical tweezers in order to avoid the presence of lateral confinement walls
-    \bibitem{Lutz2004} C.
-Lutz, M.
-Kollmann, and C.
-Bechinger, Phys.
-Rev.
-Lett.
-{\bf 93}, 026001 (2004); C.
-Lutz, M.
-Kollmann, C.
-Bechinger, and P.
-Leiderer, J.
-Phys.: Condens.
-Matter {\bf 16}, S4075 (2004).
-
-    \bibitem{Tarucha1995}  S. Tarucha, T. Honda,  T. Saku, Solid State Commun. 1995, 94, 413.
-
-    \bibitem{Gholami2015} A.
-Gholami, O.
-Steinbock, V.
-Zykov, and E.
-Bodenschatz, Flow-Driven Waves and Phase-Locked Self-Organization in Quasi-One-Dimensional Colonies of Dictyostelium discoideum, Phys.
-Rev.
-Lett.
-{\bf 114}, 018103 (2015).
-
-      %Molecular dynamics references
-
-    \bibitem{Frenkel2001} D. Frenkel and B. Smit, Understanding Molecular Simulation: From Algorithms to Applications (Academic Press, London, 2001).
-
-    \bibitem{Allen2017} M. P. Allen and D. J. Tildesley, Computer Simulation of Liquids.  Second Edition. Oxford University Press (2017).

### 2021-03-25 manuscript/manuscript_ajp_version2.tex
working through editor comments

%\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,aps,prb]{revtex4-1}

\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb,aps,prb]{revtex4-1}

%\usepackage[colorlinks, allcolors=blue]{hyperref}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsthm}
\theoremstyle{remark}
\newtheorem{problem}{Problem}

\begin{document}

\title{Molecular dynamics simulation of synchronization in driven particles}

\author{Tiare Guerrero}
\email{guer9330@pacificu.edu}
\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}

\author{Danielle McDermott}
\email{mcdermott@pacific.edu}
\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}

\date{\today}

\begin{abstract}
  Synchronization
  plays an important role in many physical processes.
  We discuss a 
  molecular dynamics simulation
  of a single particle
  moving through
  a viscous liquid
  while being driven 
  across a washboard potential energy landscape.
  Our results show many dynamical patterns
  as the landscape and driving force are altered.
  For certain conditions,
  the particle velocity and location
  are synchronized or 
  phase-locked,
  forming closed orbits in phase space.
  Quasi-periodic motion is common, 
  for which the
  dynamical center of motion shifts the
  phase space orbit.
  This synchronized motion
  is
  observed in 
  simulations and table-top experiments,
  and
  can be used to isolate
  complex natural behaviors.
 %[suggest omitting this sentence. Code not in text. We include molecular dynamics code
 % to simulate and characterize the
  %particle dynamics.] 
\end{abstract}

\maketitle

\section{Introduction} 
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli.\cite{Pikovsky2003}
The
flickering patterns of
candle flames ]xx is a flame an oscillator? xx] mediated by temperature fluctuations,\cite{Okamoto2016}
the vibrations of singing wine glasses interacting 
through sound waves,\cite{Arane2009}
and metronomes vibrating through a supporting platform\cite{Jia2015}
are examples of in-phase coupled oscillations. 
Biological systems benefit from cooperative
synchronization --
birds coordinate wing flaps
to optimize energy use during flight,\cite{Portugal2014}
frogs alternate croaking patterns,\cite{Aihara2014}
humans clap in time with music,\cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle\cite{MartinHall1999}
and brain tissue.\cite{Singer1999}
External forcing can cause or regulate 
synchronization. For example, 
an electrical pacemaker 
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies.

Synchronized phase-locking or mode-locking 
first appeared in the scientific literature
with 
Huygens' 1665 experiments on the
motions of synchronized 
pendula in wall-mounted clocks.\cite{Bennett2002}
A locked-mode is an integer frequency ratio.
In Huygens clocks,
the pendula were observed to swing at the  same rate
in the same direction (1:1 mode) or
opposite directions ($-1$:1 mode).
A 2:1 mode occurs when a simple pendulum four
times the length of another swings with twice the period.

Complex dynamics such as synchronized mode-locking
can be studied with
colloid particles in experiments.
Typical colloids are   
plastic spheres suspended in
de-ionized water or silica beads suspended in organic solvent.
Because 
colloids are large 
and move slowly, the
particle positions 
can be measured in real time 
with an optical camera.\cite{Pertsinidis2001}
Experimental measurements of the
step-by-step dynamics of 
colloids performing phase-locked motions
are useful for
understanding synchronization at a single particle level.\cite{Juniper2015,Juniper2017}

Light is a
tool for manipulating the colloidal environment
to alter synchronization patterns.
Colloids can be trapped
with 
radiation pressure from 
a laser beam.\cite{Ashkin1997}
A colloid centered in an optical trap is 
uniformly bombarded by photons. 
Off-center colloids 
experience a net force
due to uneven photon collisions across
the particle surface.
Depending on the 
location of the particle in the trap,
the radiation pressure either moves colloids toward the center 
or ejects it from the trap.
Diffraction gratings can create
more complex light environments, 
such as periodic patterns of minima
suitable for synchronization studies.\cite{Grier2003}

The model discussed in this paper
resembles an overdamped driven pendulum.
A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
A confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat,
or moving between substrate minima.
When 
a constant or 
dc drive is applied,
the particle velocity is modulated by 
the potential energy landscape exerted on the particle.  %seen by the particle. [DM swapped ``seen by'' for ``exerted on'' xx check added wording xx] 
Below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning.\cite{Reichhardt2017}
Above the pinning threshold,
a particle subject to a constant
drive force  increases its speed at a rate proportional
to the external drive.  
When the applied force varies periodically,
the ac drive can 
cause the particle to hop back and forth across
the landscape minima.
Many synchronized patterns occur,
controlled by the substrate period,
leading to 
mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces.\cite{Reichhardt2015}

In this paper we discuss numerical simulations 
of the synchronized dynamics
of a confined particle driven over
a washboard shaped potential energy landscape.
We describe
our molecular dynamics model  in Sec.~\ref{sec:MD}.
The model
is easy to simulate yet relevant
to condensed matter systems.
We summarize our results 
including the synchronized motion of a single confined particle
driven across a periodic landscape in 
Sec.~\ref{sec:results}.

In Sec.~\ref{sec:conclusion}
we describe how our results apply 
to physical systems,
such as optically trapped colloids
%charge density waves in dusty plasma
%[DM rewrote to better align with conclusion xx added words is this correct? xx]
and superconducting vortices in the presence of periodic pinning arrays.
% and Josephson junctions. %[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
We include problems for interested readers 
in Sec.~\ref{sec:problems}.

\section{Simulation}
\label{sec:MD}
We use a classical model for 
studying the dynamics, %xx you only use single particles xx]
using the net force on a particle to calculate
its trajectory.
The particle is confined in a two-dimensional (2D) %[DM singlular]
simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
where $a_0$ is a dimensionless unit of length.
%[DM - yes.  in the simulation we just use L=46.6 and the a_0 is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?  xx]
The particle %Particle $i$ %[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
has
position $\vec{r} = x \hat{x} + y \hat{y}$
and velocity $\vec{v} = d\vec{r}/dt$.
The edges of the system are treated by
periodic boundary conditions,
such that a particle leaving the edge of the system is mapped
back to a position within the simulation boundaries 
by the transformation $x+L \rightarrow x$ and $y+L \rightarrow y$.
We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
The units of the simulated variables are summarized in Table~\ref{tab:1}.
%\footnote{To learn more about the effects of temperature on this simulation see Problem~\ref{ex:brownian}, where we study $U_0 \sim k_B T$.}

We confine the particles using a position dependent 
potential energy, called a landscape or substrate.
The landscape is modulated in the $y$-direction
by the periodic function 
 \begin{equation}
   U(y) = U_0 \cos{(2 \pi y / \lambda)},
     \label{eq:ysubstrate}
\end{equation}
where $\lambda=L/N_p$, with $N_p$ equal to the number of periods,
and $U_0$ is a parameter
 that sets the depth of the minima
 with simulation units of energy $E_0$. 
 We plot this function in 
 Fig.~\ref{fig:1_landscape}
 for $N_p = 3$.  In Fig.~\ref{fig:1_landscape}(a) we show 
 the $x$-$y$ plane with a contour plot of $U(y)$ 
 to illustrate
 the 2D potential energy landscape;
 the maxima are colored red and the minima colored blue.
 %[xx make sure that all your figures make sense when printed in b/w xx]

The confining force on the particle %[DM removed subscripts] $i$
 is given by
 \begin{equation}
 \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U^{\ell}(\vec{r}).
 \label{eq:dudr}
 \end{equation}
 %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
 In Fig.~\ref{fig:1_landscape}(b) we plot  
 $U(y)$ to illustrate how the magnitude
 $|\vec{F}^{\ell}|$ is calculated from the particle position $y$.
 %[My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.  This is consistent with the textbook I teach from.  xx suggest that you use subscripts instead of superscripts. We can easily make that change in the next iteration of your manuscript. However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$. One of us didn't like superscripts where he was an undergraduate!  xx]

Particles are subject to an external time-dependent driving force
$\vec{F}^{\rm d}(t)$
applied parallel to the $y$-direction.
We model this force as
\begin{equation}
  \vec{F}^{\rm d}(t) = [F^{\rm dc} + F^{\rm ac} \sin(\omega t)] \hat{y},
    \label{eq:drive}
\end{equation}
with 
a constant component $F^{\rm dc}$
and a time dependent component with amplitude $F^{\rm ac}$
with angular frequency $\omega = 2 \pi f$.

The inertia of 
small particles is reduced by interactions
with the fluid particles.\cite{Purcell1977}
We assume 
colloids are
overdamped
so the particles do not accelerate,
that is, they are suspended in a continuous viscous fluid
that dissipates energy supplied externally. 
Newton's second law for an individual particle
is simplified
by the assumption that $\vec{a}$ is zero. 
The overdamped equation of motion for
the velocity $\vec{v}$ of 
an isolated particle is
\begin{equation}
  \eta \vec{v} = \vec{F}^{\ell}(\vec{r}) + \vec{F}^{\rm d}(t).
    \label{eq:motion}
\end{equation}
with friction coefficient $\eta = 1$ in units of $v_0 / F_0$.
%[xx added $v_0$ to table, please check xx] 
The term $-\eta \vec{v}$
is a drag force, which models
energy dissipation due to the fluid. 
We discuss  models for
spheres moving through fluids in 
Problem~\ref{ex:reynolds}.

The equation of motion provides a direct calculation of the velocity
of an individual particle at position $\vec{r}$ 
and simulation time $t$.
The   simulation is controlled by a  loop
which runs to a maximum integer time step.
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}(t)$
and then integrate
the equation of motion to move particles
to an updated position.
Because the acceleration is zero,
the integration of the equation of motion
is performed via 
the simple first-order Euler method 
\begin{equation}
  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
    \label{eq:euler}
\end{equation}
for a time step $\Delta t = 0.1\,\tau$.
In 
Problem~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%------------------------------------------------------------------
\begin{figure} % [h!]
\centering
\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
\caption{
Schematic of the simulation of a single particle
  driven across a washboard potential energy landscape.
  (a) View of the $x$-$y$ plane. 
  The time-dependent applied driving force $\vec{F}^{\rm d}$
  is parallel to the $y$-axis.
  The landscape is shown with 
  maxima in the potential energy marked in red
  and minima marked in blue.
  A particle is 
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the $y$-axis $U^{\ell}(y)$.  
  The particle in (a) is shown at the same $y$-position.
  The slope of $U^{\ell}(y)$ %[DM use the subscripts with the potential, but will move to superscript xx used subscript here xx]
  is the 
  magnitude of force $\vec{F}^{\ell}$. 
  }
\label{fig:1_landscape}
\end{figure}
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:results}
Here we drive 
a single particle 
across the landscape. 
The numerical implementation of the landscape 
is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  %[DM - right, two negative signs, one from the derivative, the other from the definition of force.  I found the ``mistaken'' dropped minus sign in the depths of january and added it.  xx but you should get a + sign not a minus sign xx] 
\begin{equation}
  \label{eq:force}
  F^\ell_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
\end{equation}
where the force is scaled by the parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1\,F_0$ 
with $N_p=20$ minima, 
corresponding to a spatial period $\lambda = 2.3\,a_0$.
The competition between the driving force and the landscape potential
can produce a variety of hopping patterns in the particle motion. 
The relative values of $F^{\rm ac}$, $F^{\rm dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
If $F^{\rm d}(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
If the driving frequency is low,
as in Fig.~\ref{fig:2_Fd_vy_time},  
the driven particle 
moves 
in a pattern 
with the same frequency 
as the time-dependent force $F^{\rm d}(t)$,
but is modulated by the landscape period.
We explore changes in the frequency and different values of $F^{\rm ac}$ 
in Problem~\ref{ex:parameters}.
Here we vary $F^{\rm dc}$ 
while holding the remaining parameters fixed.

%xx AJP does not use footnotes
\begin{table}[h!]
\centering
\caption{Simulation parameters and units with comparable
  experimental values.~\cite{Juniper2015,Juniper2017} The substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of the particles.  }
\begin{ruledtabular}
\begin{tabular}{c c c } 
Quantity & Simulation Units & Experimental values\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ & $ \tau \sim 3$\,s\\
velocity &  $ v_0 = a_0 / \tau $ &  $v \sim 5\,\mu$m/s \\
%driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\ %frequency 0.75 Hz
%juniper uses water–ethanol mixture
substrate period & $\lambda = 2.3\,a_0$ & $\lambda = 3.5\,\mu$m \\
substrate amplitude & $A_p = 0.1\,F_0$ & $U_0 = 25 k_B T \sim 1\, {\rm J}$ \\ %$U_0 = 0.037 E_0$ 
temperature & $T_0 = 0$  & $T \sim 290\,$K  \\
\end{tabular}
\end{ruledtabular}
\label{tab:1}
\end{table}

In Fig.~\ref{fig:2_Fd_vy_time}(a)
we plot $F^{\rm d}(t)$ 
as a function of time with the
constants $F^{\rm dc}=0.07$, 
$F^{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100\,\tau$.
In Fig.~\ref{fig:2_Fd_vy_time}(b) 
we show the $y$-position of the particle
as a function of time,
where we have
normalized $y$ by $\lambda$.
The initial particle position is $y = 0$. 
The particle moves
in the positive $y$-direction
through a distance $\Delta y = \lambda$  in a time $T$,
so that  
the average velocity 
$\langle {v}_y \rangle = \lambda f$. 
The inset of Fig.~\ref{fig:2_Fd_vy_time}(b)
shows $y$ 
over one period $100\,\tau < t < 200\,\tau$
with 
the contour plot described
in Fig.~\ref{fig:1_landscape}(a).
The motion is synchronized such that the 
driving force is a maximum when the landscape 
force is minimum,
as shown by the coincidence of the
steep slope of 
$y/\lambda$ 
and the maxima in $F^{\rm d}(t)$.
If $F^{\rm d}(t)$ is large,
the particle moves across the substrate minima,
shown in blue with the contour plot.
The slope of $y/\lambda$ equals zero twice
during a driving period,
indicating zero
forward motion 
due to a coincidence of the negative
driving force and motion over the landscape maxima.
%------------------------------------------------------------------------
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig2_Fd_vy_time.pdf}
\caption{(a) The applied driving force $F^{\rm d}(t)$ 
  with parameters $F^{\rm dc} = 0.07$, $F^{\rm ac} = 0.07$ and $f=0.01$.
  (b) 
  The $y$-position of the driven particle
  normalized by the period of the substrate $\lambda$.
  The substrate strength is $A_p=0.1$.
  The inset   shows
  the $y$-position
  through the second period $100\tau<t<200\tau$
 along with the contour plot depicting
  the landscape potential described in Fig.~\ref{fig:1_landscape}(a).
  }
\label{fig:2_Fd_vy_time}
\end{figure}

To explore the possible hopping patterns,
we sweep through a range of $F^{\rm dc}$ for fixed $F^{\rm ac}$ and $A_p$.
In Fig.~\ref{fig:3_sweep_vyFDC} 
we increase $F^{\rm dc}$ in increments of $0.001\,F_0$,
and 
measure the average velocity $\langle v_y \rangle $ 
as a function of $F^{\rm dc}$.
We also perform the sweep for a non-oscillatory drive $F^{\rm ac} = 0$.
With no oscillating component of the driving force,
  the force-velocity relation increases monotonically 
  above the depinning threshold $F^c$ such that
  \begin{equation}
    \langle v_y \rangle \propto (F^{\rm dc}-F^c)^{-\beta}.
  \end{equation}
  %[xx what is $\beta$? xx]
  where the power $\beta$ varies with the
  system type and
  can be used to identify universality class. \cite{Reichhardt2017}
  The critical force $F^c$ is equal to the maximum substrate force
  $A_p$.

The addition of an ac drive leads
  to the formation of modes.
  A mode is a periodic pattern of hops
  with a constant average particle velocity, $\langle {v}_{y} \rangle$
  over a range of driving forces $F^{\rm dc}$.
  In Fig.~\ref{fig:3_sweep_vyFDC}
  we sweep $F^{\rm dc}$
  with $F^{\rm ac} = 0.07$ and $f=0.01$.
Each step represents a different pattern of hops
between substrate minima
performed by the particle
due to the landscape confinement.  
At 
low $F^{\rm dc}$ the average velocity $\langle v_y \rangle$ is zero.
Because 
$A_p$ is large compared to the extrema of $F^{\rm d}(t)$,
the particle oscillates back and forth
in a single minima with no net velocity, an example of 
a 0:0 mode.
At higher $F^{\rm dc}$ the particle velocity 
$\langle v_{y} \rangle$ increases in steps of uniform height,
$\langle v_{y} \rangle = n \lambda f$,
where $n$ is an integer.
We observe a mode of $n=1$
for the range $0.05 < F^{\rm dc} < 0.08$,
$n=2$ for $0.08 < F^{\rm dc} < 0.11$,
$n=3$ for $0.12 < F^{\rm dc} < 0.13$,
$n=4$ for $0.14 < F^{\rm dc} < 0.155$, and 
$n=5$ for $0.155 < F^{\rm dc} < 0.16$.
Higher modes are not visible.
The step width is nonlinear
and depends on the strength of $F^{\rm ac}$
%as a Bessel function 
for this landscape potential.\cite{Reichhardt2000,Juniper2017}
%[DM the step width - simply removed xx what quantity depends on a Bessel function? xx]
These steps, known as Shapiro steps, can have a variety of
interesting patterns
such as a devil's staircase related to chaotic dynamics.\cite{Bak1986}

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig3_sweep_vyFDC.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$
  as a function of $F^{\rm dc}$.
  We let
  $F^{\rm ac}=0.0$ (blue) and 
  $F^{\rm ac}=0.07$ (orange) with $f = 0.01$ 
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  The value of $F^{\rm dc}$ for the first four steps
  %is given,
  correspond with the
  panels (a-d) 
  %indicating a system
  plotted in Fig.~\ref{fig:4_phase}.
  %[DM - clarified?  xx don't understand meaning of indicating a system
  %plotted in Fig.~\ref{fig:4_phase} xx]
}
\label{fig:3_sweep_vyFDC}
\end{figure}

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities 
  in a two-dimensional phase plot. 
  For a driven pendulum confined to a single potential well,
  an appropriate
  phase space is the particle velocity $v_y$ versus the position $y$.  
  For a particle driven 
  through multiple identical wells 
  we define phase variables 
  to account for the net increase in the position.
  The phase position is
  \begin{equation}
    \phi(t) = 2\pi [y(t)-\langle v_y \rangle t]/\lambda,
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$.\cite{Juniper2015}
  The phase velocity is
  \begin{equation}
    \dot{\phi}(t) =2\pi [v_y(t)-\langle v_y \rangle] /\lambda.  
  \end{equation}
  For zero landscape force, 
  the phase velocity  is zero when $F^{\rm d}(t) = F^{\rm dc}$.
  If the velocity
  is mode-locked to 
  a spatial location, [xx don't understand meaning of the velocity
  is mode-locked to 
  a spatial location xx]
  a closed loop appears in  
  phase space. 
  A 1:1 mode appears as a circle or oval. 
  Nodes appear 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an almost closed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relation
  shifts in time as in Fig.~\ref{fig:4_phase}.

  In Fig.~\ref{fig:4_phase}
  we plot $\dot{\phi}(t)$ versus $\phi(t)$
  for increasing 
  $F^{\rm dc}$, 
  with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
 [xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
For
  $F^{\rm dc} = 0.04$
  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is a small [xx not clear what small means? can we eliminate this word? xx] asymmetric curve.
  A tail appears
  due to the initial transient
  motion of the particle.
  The particle is confined to a single
  substrate minima,
  and has no net velocity.
  The asymmetry is caused by bias induced by $F^{\rm dc}$.
  In Fig.~\ref{fig:4_phase}(b)
  with $F^{\rm dc} = 0.07$
  the phase loop is a symmetric triangular shape,
  indicating a 1:1 match between the
  particle motion and velocity consistent with 
  Fig.~\ref{fig:2_Fd_vy_time}(a).
  As $F^{\rm dc}$ is
  increased,
  nodes form in the phase diagram, which
   occur due to repeated values
  of $\dot{\phi}$ over multiple phase positions.
  In Fig.~\ref{fig:4_phase}(c)
  with $F^{\rm dc} = 0.1$
  two nodes form.
  The particle moves a distance $2\lambda$
  during one time period.
For $F^{\rm dc} = 0.125$ as in Fig.~\ref{fig:4_phase}(d),
  three nodes form as the particle moves across $3\lambda$.

    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{fig4_phase.pdf}
      \caption{
        Phase plot of $\dot{\phi(t)}/(2\pi)$ versus $\phi(t)/(2\pi)$.
        The particle is driven with $F^{\rm dc}$ equal to  (a) $0.04$, (b) $0.07$, (c) $0.1$, and (d) $0.125$.  These values are denoted as black circles
        in Fig.~\ref{fig:3_sweep_vyFDC}. 
      The other parameters
      are $F^{\rm ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
      as in Fig.~\ref{fig:2_Fd_vy_time}.}
      \label{fig:4_phase}
    \end{figure}

\section{Conclusion}
\label{sec:conclusion}	
A single particle driven across a periodic potential landscape 
synchronizes its motion 
to environmental and external forces.  
Our simulations reproduce the experiments and simulations presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2017}
of 
mode locking in
driven colloids on a
periodic optical landscape.
Colloids are 
relatively easy to 
manipulate and image in experiments,
making ideal proxies 
for systems 
such as cold atoms or electron gases.\cite{Grier2003}
Dynamical mode-locking 
is 
observed in  technologies such as 
 quantum electronic
devices as 
stepped regions in the relation between current-voltage,
where the voltage is the analog of the external driving force
and current is the analog of particle velocity.
These mode-locked or phase-locked currents (Shapiro steps), 
due to applied ac voltages in 
single Josephson junctions\cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions have been observed.\cite{Benz1990}
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of ac and dc driven systems
displaying
non-Ohmic behavior in voltage-current curves,
including
charge density waves, spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.\cite{Reichhardt2000}

Mode-locking is a useful probe 
of complex quantum mechanical systems
because the motions of individual particles can  be inferred only
from other measurements.
Our results are relevant 
to synchronization effects
in a broad range of experimental systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

\section{Suggested problems}
\label{sec:problems}

In the following
we explore the behavior of our model
with suggested problems for interested readers.
We explore changes in the particle motion
with parameter changes in Problem~\ref{ex:parameters}.
We include analytic solutions to  the 
linear drag equation in Problem~\ref{ex:reynolds}, 
the equation of motion in Problem~\ref{ex:n2l},
and 
numerical integration techniques in Problem~\ref{ex:euler}.
%[xx see comment below xx]
We extend the model with
numerical problems 
to include finite temperature effects
in Problem~\ref{ex:brownian}.

\begin{problem}{Exploring model parameters}
\label{ex:parameters}

\noindent A range of oscillation behaviors
can be explored by varying the
  relative strength of the confining landscape
  and the external driving force.

\begin{enumerate}

\item[(a)]
Explore the effect of increasing $F^{\rm ac}$ on the hopping pattern.
  For a single driven particle,
  the hopping patterns are typically characterized
  by $n_f$, the number of forward steps,
  versus $n_b$, the number of backward steps  in one
  time period.
  The total displacement of $(n_f - n_b) \lambda$ 
  is the net hop length.  
  In Fig.~\ref{fig:2_Fd_vy_time},
  the particle moves forward through a minima ($n_f = 1$),
  and does not move backward through a full minima ($n_b = 0$).  
 To achieve
  backward hops,
  the driving parameters must have
  a ratio of $F^{\rm ac}/F^{\rm dc} > 1$ 
  and a difference $|F^{\rm ac} - F^{\rm dc}| > A_p$.

In Ref.~\onlinecite{Juniper2015}
  experiments with single colloids 
  produce 
  the following
  combinations of forward and backward steps
  by sweeping through
  a variety of applied forces parameters $F^{\rm dc}$ and $F^{\rm ac}$:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}
  we fix $f=0.01$, $F^{\rm dc}=0.07$, and $A_p = 0.1$,
  and increase
  the amplitude of $F^{\rm ac}$.
  This increase causes the number of backward steps to increase.
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^{\rm d}(t)$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
  $F^{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
  the number of backward steps
  $n_b = 0$ with $n_f = 4$.
  In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F^{\rm ac} = 0.4$
  $n_b = 2$ and $n_f = 6$.
  In each case the average velocity 
  is $\langle v_y \rangle = 4\lambda f$,
  which can be reproduced over a variety of $F^{\rm ac}$ values. [xx what is the question? leave something to the reader! xx]

  %----------------------------------------------------------
  \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig5_Fac_y_vs_time}.pdf}
      \caption{
The motion of a particle with the same values of $F^{\rm dc}$ and frequency as in Fig.~\ref{fig:2_Fd_vy_time} and  $F^{\rm ac}$ equal to
        (a) $0.2$ and
        (b) $0.4$.
      }
      \label{fig:5_Fac_y_vs_time}
    \end{figure}

\item[(b)] Explore the effect of increasing the driving frequency on the hopping pattern. In Sec.~\ref{sec:results}
  the frequency is sufficiently low so that the effect of 
  the applied force is large
  over a sustained time interval,
  allowing the particle to hop a substrate maxima.
  Figure~\ref{fig:6_freq}
  shows the effects of increasing the frequency
  of the applied driving force.
  The remaining parameters are fixed 
 at
  $F^{\rm dc}=0.1$, $F^{\rm ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  because $F^{\rm dc} - F^{\rm ac}= 0.0$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across at most one substrate periods as in Fig.~\ref{fig:2_Fd_vy_time}.
  In Fig.~\ref{fig:6_freq}(a)
  the high frequency $f=0.05$ suppresses forward motion entirely.
  The high frequency 
  is apparent in the undulations of the particle
  with a period of $20\,\tau$.

  In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
  with a period of $45\,\tau$
  arrests the particle between minima,
  with a hopping rate of seven periods ($320\,\tau$).
  At an intermediate frequency 
  such as $f=0.01$,
  the particles are synchronized so that 
  the hopping rate matches the driving frequency,
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  In Fig.~\ref{fig:6_freq}(c) $f=0.005$
  the particle hops forward two minima for every period of $200\,\tau$.
  Low frequencies
  result in a sustained positive motion of a particle.
  In Fig.~\ref{fig:6_freq}(e) $f=0.001$
  the hopping is continuous
  over the time $100\,\tau < t < 400\,\tau$,
  with the cycle repeating 
  over the period length $1000\,\tau$. [xx same comment. too much information xx]

  \begin{figure} %[h!]
    \centering
    \includegraphics[width=\columnwidth]{{fig6_freq}.pdf}
    \caption{
      Motion of a particle with the same values of $F^{\rm dc} = 0.07$ and $F^{\rm ac} = 0.07$ as Fig.~\ref{fig:2_Fd_vy_time} and  frequency $f$ equal to (a) $0.05$, 
        (b) $0.022$, (c) $0.005$ and (d) $0.001$. 
    }
    \label{fig:6_freq}
  \end{figure}

  In Fig.~\ref{fig:7_sweep2_vyFDC}
  we sweep the constant driving force $F^{\rm dc}$
  for a fixed amplitude $F^{\rm ac}$ and frequency $f=0.01$.
  In the high frequency limit,
  the regions of phase locking
  are separated by regions of $F^{\rm dc}$
  that do not phase lock,
  and appear to increase linearly with increasing $F^{\rm dc}$.
  The width of the phase locked steps
  grows with increasing $F^{\rm ac}$,
  because 
  the particle may move backward
  over a broader range of $F^{\rm dc}$.

  \begin{figure} %[h!]
    \centering
    \includegraphics[width=\columnwidth]{{fig7_sweep2_vyFDC}.pdf}
      \caption{
        $\langle v_y \rangle$ versus $F^{\rm dc}$ of a particle with
        $F^{\rm ac}=0.1$ (blue), $F^{\rm ac}=0.2$ (orange),
        $F^{\rm ac}=0.1$ (green) and $F^{\rm ac}=0.2$ (red)
        with frequency $f=0.01$.
        The substrate is as in Fig.~\ref{fig:2_Fd_vy_time}
        with $A_p = 0.1$.
      }
      \label{fig:7_sweep2_vyFDC}
    \end{figure}
  \end{enumerate}
  \end{problem}

  \begin{problem}{Drag models and Reynolds numbers}
\label{ex:reynolds}

\noindent Stokes' law describes the drag force
  $\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
  on a sphere
  moving through a viscous liquid at velocity $\vec{v}$,
  where $\eta$ is the dynamic fluid viscosity and 
  $D$ is the particle diameter.\cite{Taylor2005}
  In simulations we
  subsume the constants $3 \pi D$
  such that $3 \pi D \eta \rightarrow \eta $.
  Often drag forces are
  modeled as a polynomial series\cite{Taylor2005}
  \begin{equation}
    \vec{F}^{\rm drag} = -b \vec{v} - c v^2 \hat{v} + \cdots  .
  \end{equation}
  Truncating the series to the first term
  is justified by demonstrating the sphere
  has a low Reynolds number  
  $R = D v \rho / \eta$,
  where $\rho$ is the fluid density and $v$ is the particle's speed.
  If $R$ is small, the quadratic and higher order terms
  may be ignored.

To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
Use reasonable values for the
  experimental analog of this system and show 
that the Reynolds number is small.
  In addition to the values listed in Table~\ref{tab:1}, 
  the liquid density 
  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
  first order approximation.\cite{asce}
  \end{problem}

\begin{problem}{Equation of motion}
  \label{ex:n2l}

\noindent Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of the forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i,
  \label{eq:n2l}
  \end{equation}
  where $m_i$ is the
  inertial mass.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  by a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{\rm drag} = - \gamma \vec{v}_i$,
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Problem~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is 
  known as the momentum relaxation time,
  and is small for
  particles with low Reynolds numbers.
  The mass of a
  typical colloid particle is $15$\,picograms,
  leading to a momentum relaxation time
  on the order of microseconds.

\begin{enumerate}

\item [(a)] Given  the values listed in Table~\ref{tab:1},
 show that  the momentum relaxation time is 
  $m/\gamma \approx 0.5\,\mu$s.

\item [(b)] If $m/\gamma$ is small, the
  particle's acceleration can be ignored
  entirely.
Using Newton's second law for
  a small momentum relaxation time, 
  show that a particle confined to a landscape exerting force
  $F^\ell(\vec{r}_i)$ subject to a time dependent drive $F^{\rm d}(t)$
  can be modeled by the equation of motion described in 
  Eq.~\eqref{eq:motion}.
  \end{enumerate}
\end{problem}

\begin{problem}{Integration methods}
  \label{ex:euler}
[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK. Instead you might want to make this problem 1 and guide  readers to write their own program. Then mention that a program is available, which you only mention in the abstract xx]

To calculate the position of the particle we
  numerically integrate the equation of motion using
  the standard definition of velocity
  $\vec{v}_i = d\vec{r}_i/dt$ 
  using the 
  Euler method. 
  The equation of motion provides
  a direct calculation for the particle velocity,
  as demonstrated in Problem~\ref{ex:n2l}.  
The Euler method is effective for solving linear ordinary differential  equations
  of the form
  $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a  solution of a map using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
 Apply the Euler method to our equation
  of motion [xx refer to specific equation by label xx] to determine  the analytic expression
for the position of a particle
  $y_n$ at the $nth$ time step.

  The Euler algorithm can be applied to
  calculate reasonable numerical solutions to 
  nonlinear
  equations if the time step $\Delta t$
  is kept sufficiently small.\cite{Newman}
  In our simulations we use the time step $\Delta t = 0.1$
  and find no change in the solution
  when we decrease the time step to smaller values.
  In simulations of
   many interacting particles,
  a small
  time step is essential for accurate results.
  Particle-particle interactions are typically nonlinear,
  so that the interparticle force changes significantly over small distances and the simple Euler algorithm is insufficient.
\end{problem}

 \begin{problem}{Brownian motion}
  \label{ex:brownian}

\noindent Brownian motion is a phenomena in which 
  visible particles change direction,
  apparently at random, 
  due to collisions with invisible fluid particles.
  The rate of collisions depends on the temperature, viscosity
  and the density of 
  the suspending fluid.\cite{Einstein1905}
  An optically trapped colloid executing Brownian motion
  is a useful probe of microscopic forces.~\cite{Volpe2013}

  In molecular dynamics simulations
  it is common to treat the 
  invisible fluid particles as a continuous fluid
  to reduce computational expense.
  Temperature effects
  can be modeled by applying randomized forces $f^T$
  to the visible particles.
  We use the normal distribution 
  to generate a series of $f^T_n$ values for
  each integer time step $n$.\cite{numpy}
  A normalized random distribution of forces
  causes fluctuations in 
  motion 
  equally in all
  directions such that the force $f^T$
  averaged over a finite time interval
  is zero.  In one dimension we have 
  \begin{equation}
    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0,
  \end{equation}
  where the integer $n$ indicates the number an  
   simulation time steps and 
  $t = N \Delta t$.
  A particle
  with sufficient energy $k_b T_{\min}$ may 
  hop over landscape
  barriers.
  In our simulations,
  we let temperature as 
  $k_b T/E_0 \rightarrow T$
  with constants set to unity
  to
  compare directly with force.

  For  no applied driving force,
    find 
    the minimum temperature required for a single particle
    to hop over the maxima in the potential landscape.
  Assume the particle is confined to
  move along the $y$-direction,
  include Brownian motion 
  in the model.
  %----------------------------------------------------
    \begin{figure} %[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 3.0$ no hopping occurs.
        (b) $T/A_p = 3.5$ one hop occurs and 
        (c) $T/A_p = 4.0$ many hops occur.
        Note the scale of the $y$-axis differs in each panel
        and the time scale is
        greater than in Fig.~\ref{fig:2_Fd_vy_time}.
        The precise timing of the hop pattern varies,
sometimes exhibiting several hops for $T/A_p = 3.5$. 
      }
      \label{fig:8_brownian}
    \end{figure}

  In Fig.~\ref{fig:8_brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:8_brownian}(a)
  the temperature is $T/A_p = 3.0$.
  The particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima
  within this simulation time.  
  In  Fig.~\ref{fig:8_brownian}(b)
  $T/A_p = 3.5$,  hops between
  potential minima are possible but not probable,
  a hop occurs from
  $y/\lambda = 10$ to $9$ at
  $t \sim 23000 \tau$. 
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:8_brownian}(c)
  $T/A_p = 4.0$ 
  we observe many hops.
  The random thermalized kicks are
  sufficiently large to make the particle perform
  what appears to be 
  a random walk of hops atop the substrate. [xx what is the question? xx]

  For a driven particle,
  we ignore 
  the effects of temperature 
  in these simulations.  
  We note that even for $T/A_p = 4.0$ 
  the hopping rate
  is much less than the
  frequency of the applied drive, as
 can be seen in the time scale in Fig.~\ref{fig:8_brownian},
  where the average hopping rate is approximately
  every $4000\tau$,
  a value much larger than the period of the driving force.  
  At sufficiently high temperatures,
  Brownian motion does affect 
  the formation of mode-locked steps
  and can be observed in experiments.
\end{problem}

\begin{acknowledgments}

  %[xx AJP doesn't allow acknowledgments to the editors, but you are welcome xx] 
  Charles and Cynthia Reichhardt advised 
  the project and provided the original molecular dynamics code
  written in the C programming language.
  We acknowledge funding from the M.J.\ Murdock Charitable Trust
  and the Pacific Research Institute for Science and Mathematics. % (PRISM).

\end{acknowledgments}

[xx AJP requires last page numbers for papers xx] 
\begin{thebibliography}{99}

  %intro to oscillators
\bibitem{Pikovsky2003} A. Pikovsky, M. Rosenblum, and J. Kurths, {\it Synchronization: A Universal Concept in Nonlinear Sciences} (Cambridge University Press, Cambridge, 2003).

\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima, ``Synchronization in flickering of three-coupled candle flames," Sci. Rep. {\bf 6}, 36145--xx (2016).

\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--xx (2009). %; https://doi.org/10.1119/1.3119175

\bibitem{Jia2015}  J. Jia, Z. Song, W. Liu, J. Kurths, and J. Xiao, ``Experimental study of the triplet synchronization of coupled nonidentical mechanical metronomes," Sci. Rep. {\bf 5}, 17008--xx (2015).

%Synchronization of a thermoacoustic oscillator by an external sound source
%G. Penelet and T. Biwa
%American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189

  %biological examples

\bibitem{Portugal2014} S. Portugal, T. Hubel, J. Fritz, S. Heese, D. Trobe, B. Voelkl, S. Hailes, A. M. Wilson and J. R. Usherwood,   ``Upwash exploitation and downwash avoidance by flap phasing in ibis formation flight," Nature {\bf 505}, 399--402 (2014).

  \bibitem{Aihara2014} I. Aihara, T. Mizumoto, T. Otsuka, H. Awano, K. Nagira, H. G. Okuno and K. Aihara, ``Spatio-temporal dynamics in collective frog choruses examined by mathematical modeling and field observations," Sci. Rep. {\bf 4}, 3891--xx (2014).

  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, ``Keeping the beat: A Large sample study of bouncing and clapping to music," PLoS ONE 11(7): e0160178. (2016).

  \bibitem{MartinHall1999} G. Martin Hall, Sonya Bahar, and Daniel J. Gauthier, ``Prevalence of rate-dependent behaviors in cardiac muscle," Phys. Rev. Lett. {\bf 82}, 2995--2998 (1999).

    %huygens clocks
  \bibitem{Singer1999} W. Singer, ``Striving for coherence,"  Nature {\bf 397} 391--393 (1999).

  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563--xx (2002).

  %colloids
  \bibitem{Pertsinidis2001} A. Pertsinidis and X. Ling,  ``Equilibrium configurations and energetics of point defects in two-dimensional colloidal crystals," Phys Rev. Lett.  {\bf 87}, 098303-1--xx (2001). %https://doi.org/10.1103/PhysRevLett.87.098303

  \bibitem{Juniper2015} M. P. N. Juniper, A. V. Straube, R. Besseling, D. G. A. L. Aarts, and R. P. A. Dullens, ``Microscopic dynamics of synchronization in driven colloids," Nat. Commun. 6, 7187--xx (2015); 
      %\bibitem{Juniper2018}

  \bibitem{Juniper2017} M. P. N. Juniper,  U. Zimmermann, A. V. Straube, R. Besseling, D. G. A. L. Aarts, H. L{\"o}wen, and R. P. A. Dullens,  ``Dynamic mode locking in a driven colloidal system: Experiments and theory," New J. Phys.{\bf 19} (1), 013010-1--14 (2017).  %https://doi.org/10.1088/1367-2630/aa53cd

  \bibitem{Ashkin1997} A. Ashkin, ``Optical trapping and manipulation of neutral particles using lasers," Proc. Natl. Acad. Sci. U.S.A. {\bf 94}, 4853--4860 (1997).

  \bibitem{Grier2003} D. G. Grier, ``A revolution in optical manipulation," Nature {\bf 424}, 810 (2003).

  %general particle on washboard
  \bibitem{Reichhardt2017} C. Reichhardt and C. J. Olson Reichhardt, ``Depinning and nonequilibrium dynamic phases of particle assemblies driven over random and ordered substrates: a review," Rep. Prog. Phys. {\bf 80}, 026501 (2017).

  \bibitem{Reichhardt2015} C. Reichhardt, and C. J. O. Reichhardt,  ``Shapiro steps for skyrmion motion on a washboard potential with longitudinal and transverse ac drives," Phys. Rev. B {\bf 92} (22), 224432-1--xx (2015).

  %overdamped justification
  \bibitem{Purcell1977} E. M. Purcell, ``Life at low Reynolds numbers,"  Am. J. Phys. {\bf 45}, 3--11 (1977).

  %chaos!
  \bibitem{Bak1986} P. Bak. ``The Devil's staircase," Physics Today {\bf 39}(12), 38--xx (1986).

  %overdamped justification
  \bibitem{Taylor2005} J. Taylor,  {\it Classical Mechanics} (University Science Books, 2005).

  %brownian motion!
  \bibitem{Volpe2013} G. Volpe and G. Volpe, ``Simulation of a Brownian particle in an optical trap,"  Am. J. Phys. {\bf 81}(3), 224--230 (2013).

  %viscosity and density citation
  \bibitem{asce}
    %Non-fundamental constants for water viscosity are available
    %in several databases including 
    %  (1) https://ascelibrary.org/doi/pdf/10.1061/9780784408230.ap02
    IAPWS R12-08, 
    ``Release on the IAPWS formulation 2008 for the viscosity of ordinary water substance,  September 2008,
    %IAPWS 2008 -
    \url{<http://www.iapws.org/relguide/viscosity.html>}.
    %[citation for these values better than wikipedia] \cite{} %CONFIRM!
    %density $\rho = 0.9982 g/cm^3$

  %numerical solutions of differential equations
  \bibitem{Newman} M. Newman, {\it Computational Physics} (CreateSpace Independent Publishing Platform, 2012).

    %Brownian motion!
  \bibitem{Einstein1905} A. Einstein, {\it Investigations on the Theory of the Brownian Movement}  (Dover Publications, 1956).

    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--xx (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).

   %Josephson Junctions and other condensed matter applications
    \bibitem{Shapiro1963} S. Shapiro, ``Josephson currents in superconducting tunneling: The effect of microwaves and other observations," Phys. Rev. Lett. {\bf 11}, 80--xx (1963).

    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev, ``The current-phase relation in Josephson junctions," Rev. Mod. Phys. {\bf 76}, 411--xx (2004).

    \bibitem{Benz1990}  S. P. Benz, M. S. Rzchowski, M. Tinkham, and C. J. Lobb, ``Fractional giant Shapiro steps and spatially correlated phase motion in 2D Josephson arrays," Phys. Rev. Lett. {\bf 64}, 693--xx (1990); D. Dom{\'i}nguez and J. V. Jos{\'e}, ``Giant Shapiro steps with screening currents," Phys. Rev. Lett. {\bf 69}, 514--xx (1992).

    \bibitem{Reichhardt2000} C. Reichhardt, R. T. Scalettar, G. T. Zim{\'a}nyi, and N. Gr{\o}nbech-Jensen,  ``Phase-locking of vortex lattices interacting with periodic pinning,"  Phys. Rev. B {\bf 61}, R11914 (2000).

\end{thebibliography}

\end{document}

### 2021-03-26 manuscript/manuscript_ajp_version2.tex
updated page numbers

@@
 flickering patterns of
-candle flames ]xx is a flame an oscillator? xx] mediated by temperature fluctuations,\cite{Okamoto2016}
+candle flames %[DM - the air molecules are oscillating I think xx is a flame an oscillator? xx]
+mediated by temperature fluctuations,\cite{Okamoto2016}
 the vibrations of singing wine glasses interacting 
@@
  \begin{equation}
- \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U^{\ell}(\vec{r}).
+ \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
  \label{eq:dudr}
@@
   (b) The potential energy function
-  along the $y$-axis $U^{\ell}(y)$.  
+  along the $y$-axis $U(y)$.  %DM removed ^{\ell}
   The particle in (a) is shown at the same $y$-position.
-  The slope of $U^{\ell}(y)$ %[DM use the subscripts with the potential, but will move to superscript xx used subscript here xx]
+  The slope of $U(y)$ %[DM removed ^{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
   is the 
@@
   the phase velocity  is zero when $F^{\rm d}(t) = F^{\rm dc}$.
-  If the velocity
-  is mode-locked to 
-  a spatial location, [xx don't understand meaning of the velocity
-  is mode-locked to 
-  a spatial location xx]
+  %[DM rewrite]
+  If the system
+  is strictly mode-locked,
+  the particle velocity
+  recurs at a particular spatial location, and 
+  %If the velocity
+  %is mode-locked to 
+  %a spatial location,
+  %[xx don't understand meaning of the velocity
+  %is mode-locked to 
+  %a spatial location xx]
   a closed loop appears in  
@@
   with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
- [xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
+ %[xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
   For
   $F^{\rm dc} = 0.04$
-  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is a small [xx not clear what small means? can we eliminate this word? xx] asymmetric curve.
+  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is an
+  % small [xx not clear what small means? can we eliminate this word? xx]
+  asymmetric curve.
   A tail appears
@@
   is $\langle v_y \rangle = 4\lambda f$,
-  which can be reproduced over a variety of $F^{\rm ac}$ values. [xx what is the question? leave something to the reader! xx]
+  which can be reproduced over a variety of $F^{\rm ac}$ values.
+  %[xx what is the question? leave something to the reader! xx]
 
@@
   with the cycle repeating 
-  over the period length $1000\,\tau$. [xx same comment. too much information xx]
+  over the period length $1000\,\tau$.
+  %[xx same comment. too much information xx]
 
@@
   \begin{equation}
-  m_i \vec{a}_i = \sum \vec{F}_i,
+  m \vec{a} = \sum \vec{F},
   \label{eq:n2l}
   \end{equation}
-  where $m_i$ is the
+  where $m$ is the
   inertial mass.  
@@
   in the opposite direction of motion 
-  $\vec{F}^{\rm drag} = - \gamma \vec{v}_i$,
+  $\vec{F}^{\rm drag} = - \gamma \vec{v}$,
   where $\gamma = 3 \pi \eta D$ is the drag coefficient
@@
   show that a particle confined to a landscape exerting force
-  $F^\ell(\vec{r}_i)$ subject to a time dependent drive $F^{\rm d}(t)$
+  $F^\ell(\vec{r})$ subject to a time dependent drive $F^{\rm d}(t)$
   can be modeled by the equation of motion described in 
@@
   \label{ex:euler}
-[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK.
+%[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK.
 Instead you might want to make this problem 1 and guide  readers to write their own program.
@@
   the standard definition of velocity
-  $\vec{v}_i = d\vec{r}_i/dt$ 
+  $\vec{v} = d\vec{r}/dt$ 
   using the 
@@
   $y_{n+1} = y_n + f(t_n,y_n)$.
- Apply the Euler method to our equation
-  of motion [xx refer to specific equation by label xx] to determine  the analytic expression
+  Apply the Euler method to %our equation of motion
+  Eq.~\ref{eq:motion}
+  %[xx refer to specific equation by label xx]
+  to determine  the analytic expression
   for the position of a particle
@@
 
-[xx AJP requires last page numbers for papers xx] 
+%%[xx AJP requires last page numbers for papers xx] 
 \begin{thebibliography}{99}
@@
 
-\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima, ``Synchronization in flickering of three-coupled candle flames," Sci. Rep. {\bf 6}, 36145--xx (2016).
-
-\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--xx (2009). %; https://doi.org/10.1119/1.3119175
+\bibitem{Okamoto2016} K. Okamoto, A. Kijima, Y. Umeno, and H. Shima, ``Synchronization in flickering of three-coupled candle flames," Sci. Rep. {\bf 6}, 36145--36155 (2016).
+
+\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--1067 (2009). %; https://doi.org/10.1119/1.3119175
 
@@
 Rep.
-{\bf 5}, 17008--xx (2015).
+{\bf 5}, 17008--17020 (2015).
 
@@
 %American Journal of Physics 81, 290 (2013); https://doi.org/10.1119/1.4776189
-
   %biological examples
@@
 Rep.
-{\bf 4}, 3891--xx (2014).
+{\bf 4}, 3891--3899 (2014).
 
@@
 
-  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563--xx (2002).
+  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563–579 (2002).
 
@@
 Lett.
-{\bf 87}, 098303-1--xx (2001).
+{\bf 87}, 098303-1--4 (2001).
 %https://doi.org/10.1103/PhysRevLett.87.098303
@@
 Commun.
-6, 7187--xx (2015);
+6, 7187--7194 (2015);
       %\bibitem{Juniper2018}
@@
 Rev.
-B {\bf 92} (22), 224432-1--xx (2015).
+B {\bf 92} (22), 224432-1--12 (2015).
 
@@
   %chaos!
-  \bibitem{Bak1986} P. Bak. ``The Devil's staircase," Physics Today {\bf 39}(12), 38--xx (1986).
+  \bibitem{Bak1986} P. Bak. ``The Devil's staircase," Physics Today {\bf 39}(12), 38--45 (1986).
 
@@
 
-    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--xx (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
+    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--362 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
 
    %Josephson Junctions and other condensed matter applications
-    \bibitem{Shapiro1963} S. Shapiro, ``Josephson currents in superconducting tunneling: The effect of microwaves and other observations," Phys. Rev. Lett. {\bf 11}, 80--xx (1963).
-
-    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev, ``The current-phase relation in Josephson junctions," Rev. Mod. Phys. {\bf 76}, 411--xx (2004).
+    \bibitem{Shapiro1963} S. Shapiro, ``Josephson currents in superconducting tunneling: The effect of microwaves and other observations," Phys. Rev. Lett. {\bf 11}, 80--82 (1963).
+
+    \bibitem{Golubov2004} A. A. Golubov, M. Yu. Kupriyanov, and E. Il{\`i}chev, ``The current-phase relation in Josephson junctions," Rev. Mod. Phys. {\bf 76}, 411--469 (2004).
 
@@
 Lett.
-{\bf 64}, 693--xx (1990); D.
+{\bf 64}, 693--696 (1990); D.
 Dom{\'i}nguez and J.
@@
 Lett.
-{\bf 69}, 514--xx (1992).
+{\bf 69}, 514--517 (1992).
 

### 2021-03-26 code/plot_landscape.py
made changes for review - colormap, subscripts, black arrows

@@ -48,7 +48,7 @@ def add_contour(ax,ax2,L,N):
     Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
 
     #blue are minima, red are maxima
-    cmap=cm.coolwarm #_r
+    cmap=cm.Greys #warm #_r
 
     #alpha is the degree of transparency, again, set by what looks good.
 
@@ -118,8 +118,8 @@ if __name__ == "__main__":
     scatter1=ax1.scatter(xp,yp,edgecolor='k',s=200)
     scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
 
-    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(shrink=0.05,color='magenta')) #arrowstyle="<-",
-    ax2.annotate(r"$|\mathrm{\vec{F}^{\ell}}|$", xy=(0+0.02, Sy/2), ha='center', va='center',color='black') 
+    ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(shrink=0.05,color='black')) #arrowstyle="<-",
+    ax2.annotate(r"$|\mathrm{\vec{F}_{\ell}}|$", xy=(0+0.02, Sy/2), ha='center', va='center',color='black') 
 
     #add annotation showing period
     ax2.annotate(r'$\lambda$', xy=(-0.9*Z_mag,2*Sy/3), ha='center', va='center')
@@ -134,11 +134,11 @@ if __name__ == "__main__":
                  xycoords='data', textcoords='data',
                  arrowprops={'arrowstyle': '<|-|>','color':"black"})
     
-    ax1.annotate("", xy=(xp, yp-4), xytext=(xp, yp), arrowprops=dict(color='magenta', shrink=0.05),ha="center")
-    ax1.annotate(r"$\mathrm{\vec{F}^{\ell}}$", xy=(xp+1, yp-6),ha="left",va="center")
+    ax1.annotate("", xy=(xp, yp-4), xytext=(xp, yp), arrowprops=dict(color='black', shrink=0.05),ha="center")
+    ax1.annotate(r"$\mathrm{\vec{F}_{\ell}}$", xy=(xp+1, yp-6),ha="left",va="center")
     
-    ax1.annotate("", xy=(xp, yp+8), xytext=(xp, yp), arrowprops=dict(color='gray', shrink=0.05), ha="center")
[…]

### 2021-03-26 code/plot_landscape.py
made fig1 fully BW

@@ -54,7 +54,7 @@ def add_contour(ax,ax2,L,N):
 
     cset = ax.contourf(X, Y, Z, cmap=cmap,alpha=0.5)
 
-    ax2.plot(Z,Y)
+    ax2.plot(Z,Y,"k")
     ax2.set_xlabel(r"U(y)",labelpad=-20)
     #ax2.set_ylabel(r"y",rotation='horizontal',ha='right')
 
@@ -115,8 +115,8 @@ if __name__ == "__main__":
     yf=yp - slope*Z_mag/1.8 - 0.6
     
 
-    scatter1=ax1.scatter(xp,yp,edgecolor='k',s=200)
-    scatter2=ax2.scatter(zp,yp,edgecolor='k',s=200)
+    scatter1=ax1.scatter(xp,yp,edgecolor='k',c='k',s=200)
+    scatter2=ax2.scatter(zp,yp,edgecolor='k',c='k',s=200)
 
     ax2.annotate("", xytext=(zp, yp), xy=(zf, yf), arrowprops=dict(shrink=0.05,color='black')) #arrowstyle="<-",
     ax2.annotate(r"$|\mathrm{\vec{F}_{\ell}}|$", xy=(0+0.02, Sy/2), ha='center', va='center',color='black') 

### 2021-03-26 code/MD_colloid.py
updated sub/superscripts and fig2 inset

@@ -6,6 +6,8 @@ Supplementary Material for
 Molecular dynamics simulation of synchronization in driven particles
 American Journal of Physics
 
+Makes Figures 2-9 using a flag to select
+
 Danielle McDermott
 Tiare Guerrero
 '''
@@ -42,10 +44,11 @@ def add_contour(ax,L,N):
     Adds the washboard in the y-direction.  
     Hardwired for a single parameter set.    
     '''
-
+    
+    #locally the period is 1 since the y-axis is normalized by lambda
     a_p = 1
 
-    #assuming Tiare's trough system, so we won't want to cover the entire range
+    #assuming a trough system, so we won't want to cover the entire range
     X = np.arange(100, 200, 0.1)
     Y = np.arange(L[0], L[1]+0.1, 0.1)
     X, Y = np.meshgrid(X, Y)
@@ -61,7 +64,7 @@ def add_contour(ax,L,N):
     Z = Z_mag*np.cos(2*np.pi*(Y)/a_p) 
 
     #blue are minima, red are maxima
-    cmap=cm.coolwarm #_r
+    cmap=cm.Greys #warm #_r
 
     #alpha is the degree of transparency, again, set by what looks good.
 
@@ -114,7 +117,7 @@ def landscape_force(y,parameters):
     period = parameters['period']
     AP = parameters['AP']
     
-    return -AP*np.sin(2*np.pi*y/period)
+    return AP*np.sin(2*np.pi*y/period)
 
 ###################################################################
 def external_drive(time, parameters):
@@ -176,7 +179,7 @@ def md_step(y, int_time, avg_vy, parameters, ft=0):
         avg_vy = average_velocity(int_time, vy, avg_vy, parameters)
     else:
         avg_vy = vy
-        print(vy, avg_vy)
+        #print(vy, avg_vy)
 
     #calculate the new position
     y += vy*dt
@@ -257,9 +260,9 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     # them.
     ax3 = plt.axes([0,0,1,1])
     # Manually set the position and relative size of the inset axes within ax1
-    ip = InsetPosition(ax2, [0.64,0.18,0.3,0.4])
+    ip = InsetPosition(ax2, [0.62,0.18,0.33,0.42])
     ax3.set_axes_locator(ip)
-    L=[0.9,2.3]
+    L=[1.4,2.75]
     N=1
     add_contour(ax3,L,N)
[…]

### 2021-03-27 code/MD_colloid.py
cleaned up code and files

@@ -274,7 +274,7 @@ def plot_force_position_vs_time(time_data,FDC_data,y_data,p):
     # time = m/(4*freq)
 
     #plot the force vs. time data
-    #ax1.plot(time_data,FDC_data,label="F$^{dc}$")
+    #ax1.plot(time_data,FDC_data,label="F$^{\mathrm{dc}}$")
     ax1.plot(time_data,F_drive,label="F$_d$(t)",lw=5)
     
     #plot normalized position by period vs. time
@@ -568,7 +568,7 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #figures 2 to 8
-    make_fig = 2
+    make_fig = 4
 
     parameters['filename']="fig%d.pdf"%(make_fig)
 
@@ -577,7 +577,7 @@ if __name__ == "__main__":
     #--------------------------------------------------------------
     #run a single particle at a single driving force
     #--------------------------------------------------------------
-    if make_fig == 2 or make_fig == 8:
+    if make_fig == 2 or make_fig == 4:
 
         #run a single MD simulation for a set of parameters
         if make_fig == 2:
@@ -587,12 +587,13 @@ if __name__ == "__main__":
 
             single_particle(parameters)
             
-        elif make_fig == 8:
+        elif make_fig == 4:
             #phase figure!!!!
             #parameters['drop'] = 4000   
             parameters['maxtime'] = 2000
 
-            parameters['y0'] = 2*parameters['period'] #*5/4
+            #place in a minima away from the PBC wrap
+            parameters['y0'] = parameters['period']*6/4
 
             #should be as in Fig. 2
             parameters['F_AC'] = 0.07 
@@ -602,11 +603,10 @@ if __name__ == "__main__":
             fig = plt.figure(figsize=(8,8*1.2))
             gs=gridspec.GridSpec(2,2)
 
-            if 1:
-                FDC = [0.04, 0.07, 0.1, 0.125] #, 0.2, 0.3]
-            else:
-                FDC = [0.0, 0.1, 0.2, 0.3]
-                
+            #set different constant currents
+            FDC = [0.04, 0.07, 0.1, 0.125] 
+
+            #k counts up with # of panels
             k=0
             for i in range(2):
                 for j in range(2):
@@ -638,15 +638,9 @@ if __name__ == "__main__":
     #make shapiro steps with a range of F^{dc}
     #this is the place to include the strictly DC force...
     #--------------------------------------------------------------
[…]

### 2021-03-27 manuscript/manuscript_ajp_version2.tex
updated figs

@@
  the 2D potential energy landscape;
- the maxima are colored red and the minima colored blue.
- %[xx make sure that all your figures make sense when printed in b/w xx]
+ the maxima are colored white and the minima colored gray.
+ %[DM - switch from red/blue to white/gray - xx make sure that all your figures make sense when printed in b/w xx]
 
@@
  \begin{equation}
- \vec{F}^{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
+ \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
  \label{eq:dudr}
@@
  $U(y)$ to illustrate how the magnitude
- $|\vec{F}^{\ell}|$ is calculated from the particle position $y$.
- %[My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.
+ $|\vec{F}_{\ell}|$ is calculated from the particle position $y$.
+ %[DM - begrudingly changed - My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.
 This is consistent with the textbook I teach from.
@@
 Particles are subject to an external time-dependent driving force
-$\vec{F}^{\rm d}(t)$
+$\vec{F}_{\rm d}(t)$
 applied parallel to the $y$-direction.
@@
 \begin{equation}
-  \vec{F}^{\rm d}(t) = [F^{\rm dc} + F^{\rm ac} \sin(\omega t)] \hat{y},
+  \vec{F}_{\rm d}(t) = [F_{\rm dc} + F_{\rm ac} \sin(\omega t)] \hat{y},
     \label{eq:drive}
@@
 with 
-a constant component $F^{\rm dc}$
-and a time dependent component with amplitude $F^{\rm ac}$
+a constant component $F_{\rm dc}$
+and a time dependent component with amplitude $F_{\rm ac}$
 with angular frequency $\omega = 2 \pi f$.
@@
 \begin{equation}
-  \eta \vec{v} = \vec{F}^{\ell}(\vec{r}) + \vec{F}^{\rm d}(t).
+  \eta \vec{v} = \vec{F}_{\ell}(\vec{r}) + \vec{F}_{\rm d}(t).
     \label{eq:motion}
@@
   (a) View of the $x$-$y$ plane. 
-  The time-dependent applied driving force $\vec{F}^{\rm d}$
+  The time-dependent applied driving force $\vec{F}_{\rm d}$
   is parallel to the $y$-axis.
   The landscape is shown with
-  maxima in the potential energy marked in red
-  and minima marked in blue.
+  %[DM changed color scheme from red/blue to gray/white for better BW conversion]
+  maxima in the potential energy marked in white %#red
+  and minima marked in gray %.
   A particle is 
@@
   (b) The potential energy function
-  along the $y$-axis $U(y)$.  %DM removed ^{\ell}
+  along the $y$-axis $U(y)$.  %DM removed _{\ell}
   The particle in (a) is shown at the same $y$-position.
-  The slope of $U(y)$ %[DM removed ^{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
+  The slope of $U(y)$ %[DM removed _{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
   is the 
-  magnitude of force $\vec{F}^{\ell}$. 
+  magnitude of force $\vec{F}_{\ell}$. 
   }
@@
   \label{eq:force}
-  F^\ell_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
+  {F_{\ell}}_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
 \end{equation}
@@
 can produce a variety of hopping patterns in the particle motion. 
-The relative values of $F^{\rm ac}$, $F^{\rm dc}$ and $A_p$
+The relative values of $F_{\rm ac}$, $F_{\rm dc}$ and $A_p$
 control the rate and distance a  particle moves 
 forward and backward in the landscape.
-If $F^{\rm d}(t) > A_p$, a particle can 
+If $F_{\rm d}(t) > A_p$, a particle can 
 overcome the barrier height of the landscape,
@@
 with the same frequency 
-as the time-dependent force $F^{\rm d}(t)$,
+as the time-dependent force $F_{\rm d}(t)$,
 but is modulated by the landscape period.
-We explore changes in the frequency and different values of $F^{\rm ac}$ 
+We explore changes in the frequency and different values of $F_{\rm ac}$ 
 in Problem~\ref{ex:parameters}.
-Here we vary $F^{\rm dc}$ 
+Here we vary $F_{\rm dc}$ 
 while holding the remaining parameters fixed.
@@
 In Fig.~\ref{fig:2_Fd_vy_time}(a)
-we plot $F^{\rm d}(t)$ 
+we plot $F_{\rm d}(t)$ 
 as a function of time with the
-constants $F^{\rm dc}=0.07$, 
-$F^{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
+constants $F_{\rm dc}=0.07$, 
+$F_{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
 The temporal period of the driving force is
@@
 $y/\lambda$ 
-and the maxima in $F^{\rm d}(t)$.
-If $F^{\rm d}(t)$ is large,
+and the maxima in $F_{\rm d}(t)$.
+If $F_{\rm d}(t)$ is large,
 the particle moves across the substrate minima,
-shown in blue with the contour plot.
+%[DM - color change]
+shown in gray with the contour plot.
 The slope of $y/\lambda$ equals zero twice
@@
 \includegraphics[width=\columnwidth]{fig2_Fd_vy_time.pdf}
-\caption{(a) The applied driving force $F^{\rm d}(t)$ 
-  with parameters $F^{\rm dc} = 0.07$, $F^{\rm ac} = 0.07$ and $f=0.01$.
+\caption{(a) The applied driving force $F_{\rm d}(t)$ 
+  with parameters $F_{\rm dc} = 0.07$, $F_{\rm ac} = 0.07$ and $f=0.01$.
   (b) 
@@
 To explore the possible hopping patterns,
-we sweep through a range of $F^{\rm dc}$ for fixed $F^{\rm ac}$ and $A_p$.
+we sweep through a range of $F_{\rm dc}$ for fixed $F_{\rm ac}$ and $A_p$.
 In Fig.~\ref{fig:3_sweep_vyFDC} 
-we increase $F^{\rm dc}$ in increments of $0.001\,F_0$,
+we increase $F_{\rm dc}$ in increments of $0.001\,F_0$,
 and 
 measure the average velocity $\langle v_y \rangle $ 
-as a function of $F^{\rm dc}$.
-We also perform the sweep for a non-oscillatory drive $F^{\rm ac} = 0$.
+as a function of $F_{\rm dc}$.
+We also perform the sweep for a non-oscillatory drive $F_{\rm ac} = 0$.
 With no oscillating component of the driving force,
   the force-velocity relation increases monotonically 
-  above the depinning threshold $F^c$ such that
+  above the depinning threshold $F_c$ such that
   \begin{equation}
-    \langle v_y \rangle \propto (F^{\rm dc}-F^c)^{-\beta}.
+    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta}.
   \end{equation}
@@
   can be used to identify universality class. \cite{Reichhardt2017}
-  The critical force $F^c$ is equal to the maximum substrate force
+  The critical force $F_c$ is equal to the maximum substrate force
   $A_p$.
@@
   with a constant average particle velocity, $\langle {v}_{y} \rangle$
-  over a range of driving forces $F^{\rm dc}$.
+  over a range of driving forces $F_{\rm dc}$.
   In Fig.~\ref{fig:3_sweep_vyFDC}
-  we sweep $F^{\rm dc}$
-  with $F^{\rm ac} = 0.07$ and $f=0.01$.
+  we sweep $F_{\rm dc}$
+  with $F_{\rm ac} = 0.07$ and $f=0.01$.
 Each step represents a different pattern of hops
@@
 At 
-low $F^{\rm dc}$ the average velocity $\langle v_y \rangle$ is zero.
+low $F_{\rm dc}$ the average velocity $\langle v_y \rangle$ is zero.
 Because 
-$A_p$ is large compared to the extrema of $F^{\rm d}(t)$,
+$A_p$ is large compared to the extrema of $F_{\rm d}(t)$,
 the particle oscillates back and forth
@@
 a 0:0 mode.
-At higher $F^{\rm dc}$ the particle velocity 
+At higher $F_{\rm dc}$ the particle velocity 
 $\langle v_{y} \rangle$ increases in steps of uniform height,
@@
 We observe a mode of $n=1$
-for the range $0.05 < F^{\rm dc} < 0.08$,
-$n=2$ for $0.08 < F^{\rm dc} < 0.11$,
-$n=3$ for $0.12 < F^{\rm dc} < 0.13$,
-$n=4$ for $0.14 < F^{\rm dc} < 0.155$, and 
-$n=5$ for $0.155 < F^{\rm dc} < 0.16$.
+for the range $0.05 < F_{\rm dc} < 0.08$,
+$n=2$ for $0.08 < F_{\rm dc} < 0.11$,
+$n=3$ for $0.12 < F_{\rm dc} < 0.13$,
+$n=4$ for $0.14 < F_{\rm dc} < 0.155$, and 
+$n=5$ for $0.155 < F_{\rm dc} < 0.16$.
 Higher modes are not visible.
 The step width is nonlinear
-and depends on the strength of $F^{\rm ac}$
+and depends on the strength of $F_{\rm ac}$
 %as a Bessel function 
@@
 \caption{Average particle velocity  $\langle v_{y} \rangle$
-  as a function of $F^{\rm dc}$.
+  as a function of $F_{\rm dc}$.
   We let
-  $F^{\rm ac}=0.0$ (blue) and 
-  $F^{\rm ac}=0.07$ (orange) with $f = 0.01$ 
+  $F_{\rm ac}=0.0$ (blue dashed) and 
+  $F_{\rm ac}=0.07$ (orange) with $f = 0.01$ 
   as in Fig.~\ref{fig:2_Fd_vy_time}.
-  The value of $F^{\rm dc}$ for the first four steps
+  The value of $F_{\rm dc}$ for the first four steps
   %is given,
@@
   For zero landscape force, 
-  the phase velocity  is zero when $F^{\rm d}(t) = F^{\rm dc}$.
+  the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
   %[DM rewrite]
@@
   for increasing 
-  $F^{\rm dc}$, 
+  $F_{\rm dc}$, 
   with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
@@
   For
-  $F^{\rm dc} = 0.04$
+  $F_{\rm dc} = 0.04$
   the phase plot   in Fig.~\ref{fig:4_phase}(a) with is an
@@
   and has no net velocity.
-  The asymmetry is caused by bias induced by $F^{\rm dc}$.
+  The asymmetry is caused by bias induced by $F_{\rm dc}$.
   In Fig.~\ref{fig:4_phase}(b)
-  with $F^{\rm dc} = 0.07$
+  with $F_{\rm dc} = 0.07$
   the phase loop is a symmetric triangular shape,
@@
   Fig.~\ref{fig:2_Fd_vy_time}(a).
-  As $F^{\rm dc}$ is
+  As $F_{\rm dc}$ is
   increased,
@@
   In Fig.~\ref{fig:4_phase}(c)
-  with $F^{\rm dc} = 0.1$
+  with $F_{\rm dc} = 0.1$
   two nodes form.
@@
   during one time period.
-For $F^{\rm dc} = 0.125$ as in Fig.~\ref{fig:4_phase}(d),
+For $F_{\rm dc} = 0.125$ as in Fig.~\ref{fig:4_phase}(d),
   three nodes form as the particle moves across $3\lambda$.
@@
         Phase plot of $\dot{\phi(t)}/(2\pi)$ versus $\phi(t)/(2\pi)$.
-        The particle is driven with $F^{\rm dc}$ equal to  (a) $0.04$, (b) $0.07$, (c) $0.1$, and (d) $0.125$.  These values are denoted as black circles
+        The particle is driven with $F_{\rm dc}$ equal to  (a) $0.04$, (b) $0.07$, (c) $0.1$, and (d) $0.125$.  These values are denoted as black circles
         in Fig.~\ref{fig:3_sweep_vyFDC}. 
       The other parameters
-      are $F^{\rm ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
+      are $F_{\rm ac} = 0.07$, $f=0.01$, and $A_p = 0.1$
       as in Fig.~\ref{fig:2_Fd_vy_time}.}
@@
 
-\begin{problem}{Exploring model parameters}
-\label{ex:parameters}
-
-\noindent A range of oscillation behaviors
-can be explored by varying the
-  relative strength of the confining landscape
-  and the external driving force.
-
-\begin{enumerate}
-
-\item[(a)]
-Explore the effect of increasing $F^{\rm ac}$ on the hopping pattern.
-  For a single driven particle,
-  the hopping patterns are typically characterized
-  by $n_f$, the number of forward steps,
-  versus $n_b$, the number of backward steps  in one
-  time period.
-  The total displacement of $(n_f - n_b) \lambda$ 
-  is the net hop length.  
-  In Fig.~\ref{fig:2_Fd_vy_time},
-  the particle moves forward through a minima ($n_f = 1$),
-  and does not move backward through a full minima ($n_b = 0$).  
- To achieve
-  backward hops,
-  the driving parameters must have
-  a ratio of $F^{\rm ac}/F^{\rm dc} > 1$ 
-  and a difference $|F^{\rm ac} - F^{\rm dc}| > A_p$.
-
-In Ref.~\onlinecite{Juniper2015}
-  experiments with single colloids 
-  produce 
-  the following
-  combinations of forward and backward steps
-  by sweeping through
-  a variety of applied forces parameters $F^{\rm dc}$ and $F^{\rm ac}$:
-  $n_f = 0$ to $6$ for $n_b = 0$,
-  $n_f = 0$ to $5$ for $n_b = -1$,
-  and
-  $n_f = 2$ to $3$ for $n_b = -2$.
-  In Fig.~\ref{fig:5_Fac_y_vs_time}
-  we fix $f=0.01$, $F^{\rm dc}=0.07$, and $A_p = 0.1$,
-  and increase
-  the amplitude of $F^{\rm ac}$.
-  This increase causes the number of backward steps to increase.
-  The number of forward steps also increases
-  due to the increased total positive amplitude of $F^{\rm d}(t)$.
-  In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
-  $F^{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
-  the number of backward steps
-  $n_b = 0$ with $n_f = 4$.
-  In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F^{\rm ac} = 0.4$
-  $n_b = 2$ and $n_f = 6$.
-  In each case the average velocity 
-  is $\langle v_y \rangle = 4\lambda f$,
-  which can be reproduced over a variety of $F^{\rm ac}$ values.
-  %[xx what is the question? leave something to the reader! xx]
-
-  %----------------------------------------------------------
-  \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{fig5_Fac_y_vs_time}.pdf}
-      \caption{
-The motion of a particle with the same values of $F^{\rm dc}$ and frequency as in Fig.~\ref{fig:2_Fd_vy_time} and  $F^{\rm ac}$ equal to
-        (a) $0.2$ and
-        (b) $0.4$.
-      }
-      \label{fig:5_Fac_y_vs_time}
-    \end{figure}
-
-\item[(b)] Explore the effect of increasing the driving frequency on the hopping pattern. In Sec.~\ref{sec:results}
-  the frequency is sufficiently low so that the effect of 
-  the applied force is large
-  over a sustained time interval,
-  allowing the particle to hop a substrate maxima.
-  Figure~\ref{fig:6_freq}
-  shows the effects of increasing the frequency
-  of the applied driving force.
-  The remaining parameters are fixed 
- at
-  $F^{\rm dc}=0.1$, $F^{\rm ac}=0.05$, and $A_p = 0.1$.
-  We observe no backward steps 
-  ($n_b = 0$) 
-  across a broad range of frequencies
-  because $F^{\rm dc} - F^{\rm ac}= 0.0$.
-  The rate of forward hops 
-  increases as frequency decreases,
-  but in each case the particle
-  hops across at most one substrate periods as in Fig.~\ref{fig:2_Fd_vy_time}.
-  In Fig.~\ref{fig:6_freq}(a)
-  the high frequency $f=0.05$ suppresses forward motion entirely.
-  The high frequency 
-  is apparent in the undulations of the particle
-  with a period of $20\,\tau$.
-
-  In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
-  with a period of $45\,\tau$
-  arrests the particle between minima,
-  with a hopping rate of seven periods ($320\,\tau$).
-  At an intermediate frequency 
-  such as $f=0.01$,
-  the particles are synchronized so that 
-  the hopping rate matches the driving frequency,
-  as in Fig.~\ref{fig:2_Fd_vy_time}.
-  In Fig.~\ref{fig:6_freq}(c) $f=0.005$
-  the particle hops forward two minima for every period of $200\,\tau$.
-  Low frequencies
-  result in a sustained positive motion of a particle.
-  In Fig.~\ref{fig:6_freq}(e) $f=0.001$
-  the hopping is continuous
-  over the time $100\,\tau < t < 400\,\tau$,
-  with the cycle repeating 
-  over the period length $1000\,\tau$.
-  %[xx same comment. too much information xx]
-
-  \begin{figure} %[h!]
-    \centering
-    \includegraphics[width=\columnwidth]{{fig6_freq}.pdf}
-    \caption{
-      Motion of a particle with the same values of $F^{\rm dc} = 0.07$ and $F^{\rm ac} = 0.07$ as Fig.~\ref{fig:2_Fd_vy_time} and  frequency $f$ equal to (a) $0.05$, 
-        (b) $0.022$, (c) $0.005$ and (d) $0.001$. 
-    }
-    \label{fig:6_freq}
-  \end{figure}
-
-  In Fig.~\ref{fig:7_sweep2_vyFDC}
-  we sweep the constant driving force $F^{\rm dc}$
-  for a fixed amplitude $F^{\rm ac}$ and frequency $f=0.01$.
-  In the high frequency limit,
-  the regions of phase locking
-  are separated by regions of $F^{\rm dc}$
-  that do not phase lock,
-  and appear to increase linearly with increasing $F^{\rm dc}$.
-  The width of the phase locked steps
-  grows with increasing $F^{\rm ac}$,
-  because 
-  the particle may move backward
-  over a broader range of $F^{\rm dc}$.
-
-  \begin{figure} %[h!]
-    \centering
-    \includegraphics[width=\columnwidth]{{fig7_sweep2_vyFDC}.pdf}
-      \caption{
-        $\langle v_y \rangle$ versus $F^{\rm dc}$ of a particle with
-        $F^{\rm ac}=0.1$ (blue), $F^{\rm ac}=0.2$ (orange),
-        $F^{\rm ac}=0.1$ (green) and $F^{\rm ac}=0.2$ (red)
-        with frequency $f=0.01$.
-        The substrate is as in Fig.~\ref{fig:2_Fd_vy_time}
-        with $A_p = 0.1$.
-      }
-      \label{fig:7_sweep2_vyFDC}
-    \end{figure}
-  \end{enumerate}
-  \end{problem}
-
-  \begin{problem}{Drag models and Reynolds numbers}
-\label{ex:reynolds}
-
-\noindent Stokes' law describes the drag force
-  $\vec{F}^{lin} = -3 \pi \eta D \vec{v}$ 
-  on a sphere
-  moving through a viscous liquid at velocity $\vec{v}$,
-  where $\eta$ is the dynamic fluid viscosity and 
-  $D$ is the particle diameter.\cite{Taylor2005}
-  In simulations we
-  subsume the constants $3 \pi D$
-  such that $3 \pi D \eta \rightarrow \eta $.
-  Often drag forces are
-  modeled as a polynomial series\cite{Taylor2005}
-  \begin{equation}
-    \vec{F}^{\rm drag} = -b \vec{v} - c v^2 \hat{v} + \cdots  .
-  \end{equation}
-  Truncating the series to the first term
-  is justified by demonstrating the sphere
-  has a low Reynolds number  
-  $R = D v \rho / \eta$,
-  where $\rho$ is the fluid density and $v$ is the particle's speed.
-  If $R$ is small, the quadratic and higher order terms
-  may be ignored.
-
-To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
-Use reasonable values for the
-  experimental analog of this system and show 
-that the Reynolds number is small.
-  In addition to the values listed in Table~\ref{tab:1}, 
-  the liquid density 
-  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
-  first order approximation.\cite{asce}
-  \end{problem}
-
-\begin{problem}{Equation of motion}
-  \label{ex:n2l}
-
-\noindent Newton's second law states that
-  the acceleration of a particle $i$
-  is proportional to 
-  the sum of the forces on the particle 
-  \begin{equation}
-  m \vec{a} = \sum \vec{F},
-  \label{eq:n2l}
-  \end{equation}
-  where $m$ is the
-  inertial mass.  
-  The addition of a dissipative force to a dynamical equation 
-  of colloid motion 
-  is typically modeled
-  by a drag force proportional to the particle's velocity
-  in the opposite direction of motion 
-  $\vec{F}^{\rm drag} = - \gamma \vec{v}$,
-  where $\gamma = 3 \pi \eta D$ is the drag coefficient
-  described in Problem~\ref{ex:reynolds}.
-  The ratio of $m/\gamma$ is 
-  known as the momentum relaxation time,
-  and is small for
-  particles with low Reynolds numbers.
-  The mass of a
-  typical colloid particle is $15$\,picograms,
-  leading to a momentum relaxation time
-  on the order of microseconds.
-
-\begin{enumerate}
-
-\item [(a)] Given  the values listed in Table~\ref{tab:1},
- show that  the momentum relaxation time is 
-  $m/\gamma \approx 0.5\,\mu$s.
-
-\item [(b)] If $m/\gamma$ is small, the
-  particle's acceleration can be ignored
-  entirely.
-Using Newton's second law for
-  a small momentum relaxation time, 
-  show that a particle confined to a landscape exerting force
-  $F^\ell(\vec{r})$ subject to a time dependent drive $F^{\rm d}(t)$
-  can be modeled by the equation of motion described in 
-  Eq.~\eqref{eq:motion}.
-  \end{enumerate}
-\end{problem}
-
-\begin{problem}{Integration methods}
+\begin{problem}{Write your own MD code}
   \label{ex:euler}
@@
   Eq.~\ref{eq:motion}
-  %[xx refer to specific equation by label xx]
+  %[DM - resolved xx refer to specific equation by label xx]
   to determine  the analytic expression
@@
   so that the interparticle force changes significantly over small distances and the simple Euler algorithm is insufficient.
+
+  A working example of this code is available
+  in Ref.~\cite{supplemental}
+
 \end{problem}
+
+\begin{problem}{Exploring model parameters}
+\label{ex:parameters}
+
+\noindent A range of oscillation behaviors
+can be explored by varying the
+  relative strength of the confining landscape
+  and the external driving force.
+
+\begin{enumerate}
+
+\item[(a)]
+  Explore the effect of increasing $F_{\rm ac}$ on the hopping pattern.
+  For a single driven particle,
+  the hopping patterns are typically characterized
+  by $n_f$, the number of forward steps,
+  versus $n_b$, the number of backward steps  in one
+  time period.
+  The total displacement of $(n_f - n_b) \lambda$ 
+  is the net hop length.  
+  In Fig.~\ref{fig:2_Fd_vy_time},
+  the particle moves forward through a minima ($n_f = 1$),
+  and does not move backward through a full minima ($n_b = 0$).  
+  To achieve
+  backward hops,
+  the driving parameters must have
+  a ratio of $F_{\rm ac}/F_{\rm dc} > 1$ 
+  and a difference $|F_{\rm ac} - F_{\rm dc}| > A_p$.
+  Holding all other parameters fixed,
+  explore how the hopping pattern
+  changes for increasing $F_{\rm ac}$.
+  For example,
+  what pattern of hops occurs for
+  fixed parameters 
+  $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$
+  and
+  modified parameter
+  $F_{\rm ac} = 0.2, 0.3$ and $0.4$?
+
+  %In Ref.~\onlinecite{Juniper2015}
+  %experiments with single colloids 
+  %produce 
+  %the following
+  %combinations of forward and backward steps
+  %by sweeping through
+  %a variety of applied forces parameters $F_{\rm dc}$ and $F_{\rm ac}$:
+  %$n_f = 0$ to $6$ for $n_b = 0$,
+  %$n_f = 0$ to $5$ for $n_b = -1$,
+  %and
+  %$n_f = 2$ to $3$ for $n_b = -2$.
+  %In Fig.~\ref{fig:5_Fac_y_vs_time}
+  %we fix $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$,
+  %and increase
+  %the amplitude of $F_{\rm ac}$.
+  %This increase causes the number of backward steps to increase.
+  %The number of forward steps also increases
+  %due to the increased total positive amplitude of $F_{\rm d}(t)$.
+  %In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
+  %$F_{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
+  %the number of backward steps
+  %$n_b = 0$ with $n_f = 4$.
+  %In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F_{\rm ac} = 0.4$
+  %$n_b = 2$ and $n_f = 6$.
+  %In each case the average velocity 
+  %is $\langle v_y \rangle = 4\lambda f$,
+  %which can be reproduced over a variety of $F_{\rm ac}$ values.
+  %[xx what is the question? leave something to the reader! xx]
+
+  %----------------------------------------------------------
+  %\begin{figure} %[h!]
+  %    \centering
+  %    \includegraphics[width=\columnwidth]{{fig5_Fac_y_vs_time}.pdf}
+  %    \caption{
+%The motion of a particle with the same values of $F_{\rm dc}$ and frequency as in Fig.~\ref{fig:2_Fd_vy_time} and  $F_{\rm ac}$ equal to
+%        (a) $0.2$ and
+%        (b) $0.4$.
+%      }
+%      \label{fig:5_Fac_y_vs_time}
+%    \end{figure}
+
+\item[(b)] Explore the effect of increasing the driving frequency on the hopping pattern. In Sec.~\ref{sec:results}
+  the frequency is sufficiently low so that the effect of 
+  the applied force is large
+  over a sustained time interval,
+  allowing the particle to hop a substrate maxima.
+  For example fix
+  the parameters
+  $F_{\rm dc}=0.1$, $F_{\rm ac}=0.05$, and $A_p = 0.1$
+  and explore
+  high frequency 
+  ($f = 0.1$),
+  intermediate frequency 
+  ($f = 0.01$),
+  and low frequency
+  ($f = 0.005$).
+  %Figure~\ref{fig:6_freq}
+  %shows the effects of increasing the frequency
+  %of the applied driving force.
+  %The remaining parameters are fixed at
+  %$F_{\rm dc}=0.1$, $F_{\rm ac}=0.05$, and $A_p = 0.1$.
+  %We observe no backward steps 
+  %($n_b = 0$) 
+  %across a broad range of frequencies
+  %because $F_{\rm dc} - F_{\rm ac}= 0.0$.
+  %The rate of forward hops 
+  %increases as frequency decreases,
+  %but in each case the particle
+  %hops across at most one substrate periods as in Fig.~\ref{fig:2_Fd_vy_time}.
+  %In Fig.~\ref{fig:6_freq}(a)
+  %the high frequency $f=0.05$ suppresses forward motion entirely.
+  %The high frequency 
+  %is apparent in the undulations of the particle
+  %with a period of $20\,\tau$.
+  %  
+  %In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
+  %with a period of $45\,\tau$
+  %arrests the particle between minima,
+  %with a hopping rate of seven periods ($320\,\tau$).
+  %At an intermediate frequency 
+  %such as $f=0.01$,
+  %the particles are synchronized so that 
+  %the hopping rate matches the driving frequency,
+  %as in Fig.~\ref{fig:2_Fd_vy_time}.
+  %In Fig.~\ref{fig:6_freq}(c) $f=0.005$
+  %the particle hops forward two minima for every period of $200\,\tau$.
+  %Low frequencies
+  %result in a sustained positive motion of a particle.
+  %In Fig.~\ref{fig:6_freq}(e) $f=0.001$
+  %the hopping is continuous
+  %over the time $100\,\tau < t < 400\,\tau$,
+  %with the cycle repeating 
+  %over the period length $1000\,\tau$.
+  %[xx same comment. too much information xx]
+  %
+  %\begin{figure} %[h!]
+  %  \centering
+  %  \includegraphics[width=\columnwidth]{{fig6_freq}.pdf}
+  %  \caption{
+  %    Motion of a particle with the same values of $F_{\rm dc} = 0.07$ and $F_{\rm ac} = 0.07$ as Fig.~\ref{fig:2_Fd_vy_time} and  frequency $f$ equal to (a) $0.05$, 
+  %      (b) $0.022$, (c) $0.005$ and (d) $0.001$. 
+  %  }
+  %  \label{fig:6_freq}
+  %\end{figure}
+  %
+  %
+\item[(c)] Explore the effect of increasing increasing $F_{\rm ac}$ on the step pattern in Fig.~\ref{fig:3_sweep_vyFDC}.
+  For example sweep the driving force $F_{\rm dc}$
+  over increments of $\Delta F_{\rm dc} = 0.001$
+  for a fixed amplitude $F_{\rm ac}$ and frequency $f=0.01$.
+  Appropriate values for 
+  $F_{\rm ac}=0.1 - 0.4$
+  will demonstrate a change in the step width
+  in a plot of $\langle v_y \rangle$ vs $F_{\rm dc}$
+
+  %In Fig.~\ref{fig:7_sweep2_vyFDC}
+  %we sweep the constant driving force $F_{\rm dc}$
+  %for a fixed amplitude $F_{\rm ac}$ and frequency $f=0.01$.
+  %In the high frequency limit,
+  %the regions of phase locking
+  %are separated by regions of $F_{\rm dc}$
+  %that do not phase lock,
+  %and appear to increase linearly with increasing $F_{\rm dc}$.
+  %The width of the phase locked steps
+  %grows with increasing $F_{\rm ac}$,
+  %because 
+  %the particle may move backward
+  %over a broader range of $F_{\rm dc}$.
+  %
+  %\begin{figure} %[h!]
+  %  \centering
+  %  \includegraphics[width=\columnwidth]{{fig7_sweep2_vyFDC}.pdf}
+  %    \caption{
+  %      $\langle v_y \rangle$ versus $F_{\rm dc}$ of a particle with
+  %      $F_{\rm ac}=0.1$ (blue), $F_{\rm ac}=0.2$ (orange),
+  %      $F_{\rm ac}=0.3$ (green) and $F_{\rm ac}=0.4$ (red)
+  %      with frequency $f=0.01$.
+  %      The substrate is as in Fig.~\ref{fig:2_Fd_vy_time}
+  %      with $A_p = 0.1$.
+  %    }
+  %    \label{fig:7_sweep2_vyFDC}
+  %  \end{figure}
+  \end{enumerate}
+  \end{problem}
+
+  \begin{problem}{Drag models and Reynolds numbers}
+\label{ex:reynolds}
+
+\noindent Stokes' law describes the drag force
+  $\vec{F}_{lin} = -3 \pi \eta D \vec{v}$ 
+  on a sphere
+  moving through a viscous liquid at velocity $\vec{v}$,
+  where $\eta$ is the dynamic fluid viscosity and 
+  $D$ is the particle diameter.\cite{Taylor2005}
+  In simulations we
+  subsume the constants $3 \pi D$
+  such that $3 \pi D \eta \rightarrow \eta $.
+  Often drag forces are
+  modeled as a polynomial series\cite{Taylor2005}
+  \begin{equation}
+    \vec{F}_{\rm drag} = -b \vec{v} - c v^2 \hat{v} + \cdots  .
+  \end{equation}
+  Truncating the series to the first term
+  is justified by demonstrating the sphere
+  has a low Reynolds number  
+  $R = D v \rho / \eta$,
+  where $\rho$ is the fluid density and $v$ is the particle's speed.
+  If $R$ is small, the quadratic and higher order terms
+  may be ignored.
+
+To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
+Use reasonable values for the
+  experimental analog of this system and show 
+that the Reynolds number is small.
+  In addition to the values listed in Table~\ref{tab:1}, 
+  the liquid density 
+  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
+  first order approximation.\cite{asce}
+  \end{problem}
+
+  %-------------------------------------------------------------------------
+
+\begin{problem}{Equation of motion}
+  \label{ex:n2l}
+
+\noindent Newton's second law states that
+  the acceleration of a particle $i$
+  is proportional to 
+  the sum of the forces on the particle 
+  \begin{equation}
+  m \vec{a} = \sum \vec{F},
+  \label{eq:n2l}
+  \end{equation}
+  where $m$ is the
+  inertial mass.  
+  The addition of a dissipative force to a dynamical equation 
+  of colloid motion 
+  is typically modeled
+  by a drag force proportional to the particle's velocity
+  in the opposite direction of motion 
+  $\vec{F}_{\rm drag} = - \gamma \vec{v}$,
+  where $\gamma = 3 \pi \eta D$ is the drag coefficient
+  described in Problem~\ref{ex:reynolds}.
+  The ratio of $m/\gamma$ is 
+  known as the momentum relaxation time,
+  and is small for
+  particles with low Reynolds numbers.
+  The mass of a
+  typical colloid particle is $15$\,picograms,
+  leading to a momentum relaxation time
+  on the order of microseconds.
+
+\begin{enumerate}
+
+\item [(a)] Given  the values listed in Table~\ref{tab:1},
+ show that  the momentum relaxation time is 
+  $m/\gamma \approx 0.5\,\mu$s.
+
+\item [(b)] If $m/\gamma$ is small, the
+  particle's acceleration can be ignored
+  entirely.
+Using Newton's second law for
+  a small momentum relaxation time, 
+  show that a particle confined to a landscape exerting force
+  $F_\ell(\vec{r})$ subject to a time dependent drive $F_{\rm d}(t)$
+  can be modeled by the equation of motion described in 
+  Eq.~\eqref{eq:motion}.
+  \end{enumerate}
+\end{problem}
+
+%--------------------------------------------------------------------------
 
@@
   Temperature effects
-  can be modeled by applying randomized forces $f^T$
+  can be modeled by applying randomized forces $f_T$
   to the visible particles.
   We use the normal distribution 
-  to generate a series of $f^T_n$ values for
+  to generate a series of ${f_T}_n$ values for
   each integer time step $n$.\cite{numpy}
@@
   equally in all
-  directions such that the force $f^T$
+  directions such that the force $f_T$
   averaged over a finite time interval
@@
   \begin{equation}
-    \langle f^T(t) \rangle = \frac{1}{N} \sum_n^N f^T_n = 0,
+    \langle f_T(t) \rangle = \frac{1}{N} \sum_n^N {f_T}_n = 0,
   \end{equation}
@@
   in the model.
+  Appropriate temperatures to explore
+  are $T/A_p = 3.0, 3.5$, and $4.0$.
+  Plot the $y-position$ versus time
+  for this particle.
   %----------------------------------------------------
-    \begin{figure} %[h!]
-      \centering
-      \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
-      \caption{
-        Motion of a particle undergoing Brownian motion
-        on a washboard potential
-        energy landscape.
-        (a) $T/A_p = 3.0$ no hopping occurs.
-        (b) $T/A_p = 3.5$ one hop occurs and 
-        (c) $T/A_p = 4.0$ many hops occur.
-        Note the scale of the $y$-axis differs in each panel
-        and the time scale is
-        greater than in Fig.~\ref{fig:2_Fd_vy_time}.
-        The precise timing of the hop pattern varies,
-sometimes exhibiting several hops for $T/A_p = 3.5$. 
-      }
-      \label{fig:8_brownian}
-    \end{figure}
-
-  In Fig.~\ref{fig:8_brownian}
-  we show the position versus time of a particle
-  confined to a sinusoidal landscape
-  undergoing Brownian motion.
-  We increase the temperature relative
-  to the amplitude of the landscape
-  troughs until the particle enters a hopping regime.
-  In  Fig.~\ref{fig:8_brownian}(a)
-  the temperature is $T/A_p = 3.0$.
-  The particle executes a 
-  random walk centered at the potential minima $y/\lambda = 10$.
-  We ran many simulations and never observed a hop to another minima
-  within this simulation time.  
-  In  Fig.~\ref{fig:8_brownian}(b)
-  $T/A_p = 3.5$,  hops between
-  potential minima are possible but not probable,
-  a hop occurs from
-  $y/\lambda = 10$ to $9$ at
-  $t \sim 23000 \tau$. 
-  In other simulations with identical parameters,
-  we sometimes observed no hops or two hops between minima,
-  as expected with random fluctuating systems.
-  In  Fig.~\ref{fig:8_brownian}(c)
-  $T/A_p = 4.0$ 
-  we observe many hops.
-  The random thermalized kicks are
-  sufficiently large to make the particle perform
-  what appears to be 
-  a random walk of hops atop the substrate. [xx what is the question? xx]
-
-  For a driven particle,
+  %  \begin{figure} %[h!]
+  %    \centering
+  %    \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
+  %    \caption{
+   %     Motion of a particle undergoing Brownian motion
+   %     on a washboard potential
+   %     energy landscape.
+   %     (a) $T/A_p = 3.0$ no hopping occurs.
+   %     (b) $T/A_p = 3.5$ one hop occurs and 
+   %     (c) $T/A_p = 4.0$ many hops occur.
+   %     Note the scale of the $y$-axis differs in each panel
+   %     and the time scale is
+   %     greater than in Fig.~\ref{fig:2_Fd_vy_time}.
+   %     The precise timing of the hop pattern varies,
+%sometimes exhibiting several hops for $T/A_p = 3.5$. 
+%      }
+%      \label{fig:8_brownian}
+%    \end{figure}
+%  
+%  In Fig.~\ref{fig:8_brownian}
+%  we show the position versus time of a particle
+%  confined to a sinusoidal landscape
+%  undergoing Brownian motion.
+ % We increase the temperature relative
+ % to the amplitude of the landscape
+ % troughs until the particle enters a hopping regime.
+ % In  Fig.~\ref{fig:8_brownian}(a)
+ % the temperature is $T/A_p = 3.0$.
+ % The particle executes a 
+ % random walk centered at the potential minima $y/\lambda = 10$.
+ % We ran many simulations and never observed a hop to another minima
+ % within this simulation time.  
+ % In  Fig.~\ref{fig:8_brownian}(b)
+ % $T/A_p = 3.5$,  hops between
+ % potential minima are possible but not probable,
+ % a hop occurs from
+ % $y/\lambda = 10$ to $9$ at
+ % $t \sim 23000 \tau$. 
+ % In other simulations with identical parameters,
+ % we sometimes observed no hops or two hops between minima,
+ % as expected with random fluctuating systems.
+ % In  Fig.~\ref{fig:8_brownian}(c)
+ % $T/A_p = 4.0$ 
+ % we observe many hops.
+ % The random thermalized kicks are
+ % sufficiently large to make the particle perform
+ % what appears to be 
+ % a random walk of hops atop the substrate. %[xx what is the question? xx]
+
+  {\it Comment: } For a driven particle,
   we ignore 
@@
   %[xx AJP doesn't allow acknowledgments to the editors, but you are welcome xx] 
-  Charles and Cynthia Reichhardt advised 
-  the project and provided the original molecular dynamics code
+  Charles and Cynthia Reichhardt
+  inspired the project and
+  provided the original molecular dynamics code
   written in the C programming language.
@@
 
+  \bibitem{supplemental}
+    \url{<https://github.com/mcddanielle/AJP_project/>}.
+
     %Brownian motion!

### 2021-03-28 code/MD_colloid.py
updated some documentation

@@ -142,7 +142,8 @@ def external_drive(time, parameters):
 
 #####################################################################
 def md_step(y, int_time, avg_vy, parameters, ft=0):
-    '''
+    '''Calculate net force and integrate eq. of motion.
+
     Required Arguments:
     y (float): position of particle
     int_time (int): count of MD steps
@@ -357,7 +358,12 @@ def single_particle(parameters,plot="y-position"):
     '''Run MD simulation for a single particle driven across a washboard potential with an oscillating driving force
 
     Required argument(s): 
-    p type: dictionary
+    parameters - all constants of the simulation 
+    type: dictionary
+
+    Optional arguments(s):
+    plot - flag to select data handling/plotting scheme
+    type: string
     '''
 
     #define the constants (parameters and initial conditions)
@@ -516,7 +522,7 @@ def brownian_particle(parameters,ax):
     
 #########################################################################
 def set_parameters():
-    '''set simulation parameters here.  
+    '''set simulation parameters .  
 
     use a python dict (i.e. a hash to organize the parameters).
     In a compiled language like C this would be in a separate file that would be read into the code at execution time, so you wouldn't need to recompile to change the parameters
@@ -525,11 +531,11 @@ def set_parameters():
     #declare the dictionary
     dict={}
 
-    dict['dt'] = 0.1 #005 #timestep in simulation units
+    dict['dt'] = 0.1 #timestep in simulation units
 
     #control the oscillating component of driving force
-    dict['F_AC'] = 0.07 #0.1              #amplitude of force oscillation
-    dict['freq'] = 0.01              #frequence of force osillation
+    dict['F_AC'] = 0.07 #amplitude of force oscillation
+    dict['freq'] = 0.01 #frequency of force oscillation
     
     #integer time steps
     dict['maxtime']=int(40/dict['freq'])        #total time steps in simulation
@@ -564,6 +570,7 @@ def set_parameters():
 #-------------------------------------------------------------------
 if __name__ == "__main__":
 
+    #will pass the parameters dict to subroutines to read constants
     parameters = set_parameters()
 
     #select which figure in the AJP you would like to make
@@ -582,14 +589,10 @@ if __name__ == "__main__":
         #run a single MD simulation for a set of parameters
         if make_fig == 2:
 
-            #parameters['maxtime'] = 40
-            #parameters['F_DC'] = 0.125 #FDC[k]
-
             single_particle(parameters)
[…]

### 2021-03-28 manuscript/manuscript_ajp_version2.tex
added write you own MD exercise

@@
  the 2D potential energy landscape;
- the maxima are colored white and the minima colored gray.
+ the maxima are colored gray and the minima colored white.
  %[DM - switch from red/blue to white/gray - xx make sure that all your figures make sense when printed in b/w xx]
@@
   %[DM changed color scheme from red/blue to gray/white for better BW conversion]
-  maxima in the potential energy marked in white %#red
-  and minima marked in gray %.
+  maxima in the potential energy are gray %#red
+  and minima are white %.
   A particle is 
@@
 and the maxima in $F_{\rm d}(t)$.
-If $F_{\rm d}(t)$ is large,
-the particle moves across the substrate minima,
+When $F_{\rm d}(t)$ is large,
+the particle moves across the substrate maxima,
 %[DM - color change]
 shown in gray with the contour plot.
-The slope of $y/\lambda$ equals zero twice
-during a driving period,
-indicating zero
-forward motion 
-due to a coincidence of the negative
-driving force and motion over the landscape maxima.
+%DM commented out - too much detail
+%The slope of $y/\lambda$ equals zero twice
+%during a driving period,
+%indicating zero
+%forward motion 
+%due to a coincidence of the negative
+%driving force and motion over the landscape maxima.
 %------------------------------------------------------------------------
@@
 with suggested problems for interested readers.
+We discuss the molecular dynamics algorithm
+and
+numerical integration techniques in Problem~\ref{ex:euler}.
 We explore changes in the particle motion
@@
 linear drag equation in Problem~\ref{ex:reynolds}, 
-the equation of motion in Problem~\ref{ex:n2l},
-and 
-numerical integration techniques in Problem~\ref{ex:euler}.
+the equation of motion in Problem~\ref{ex:n2l}.
 %[xx see comment below xx]
@@
 Then mention that a program is available, which you only mention in the abstract xx]
+
+  A working example of this code is available
+  in Ref.~\cite{supplemental}.
+  If you would like to write your own,
+  the following guide
+  will walk you through our choices.
+  In the code excerpts below,
+  most comments and optional details are removed for clarity.
+
+  \begin{enumerate}
+
+  \item[(a)] {\bf Initialization}
+    For convenience,
+    we defined a Python dictionary
+    to contain the simulation constants
+    that could easily be passed by reference
+    to subroutines.
+    We have left as an exercise to the reader the addition
+    of the remaining parameters of the system.
+    \begin{verbatim}
+def set_parameters():           
+    ```set simulation parameters...'''
+
+    #declare the dictionary     
+    dict={}  
+    dict[`dt'] = 0.1 #timestep in simulation units
+    #control the oscillating component of driving force
+    dict[`F_AC'] = 0.07 #amplitude of force oscillation
+    dict[`freq'] = 0.01 #frequency of force oscillation
+    #left as an exercise to the reader
+    #...
+    return dict
+
+    \end{verbatim}
+
+    The function is called at the top of the main function
+    followed by a call to a subroutine
+    containing the MD algorithm.
+
+     \begin{verbatim}
+    if __name__ == "__main__":
+        parameters = set_parameters()
+        #run the MD simulation
+        single_particle(parameters)
+
+\end{verbatim}
+
+  \item[(b)]
+    A key decision for any MD algorithm
+    is how much information to save during and after
+    the simulation.
+    We define the following constants
+    to manage the length of arrays
+    containing data.
+
+\begin{verbatim}
+#integer time steps
+dict[`maxtime']=int(40/dict['freq'])   #total time steps 
+dict[`writemovietime']=1   #write data to arrays for plotting
+\end{verbatim}
+%dict['decifactor'] = 1     #decimation factor - when to average values
+
+    In the subroutine {\bf single\_particle()}
+    calculate the array lengths to hold
+    position, velocity, and time data.
+    Define a loop to 
+    calculate the particle position and velocity through each
+    molecular dynamics time step,
+    calculated in the subroutine {\bf md\_step()}
+    (which will be described in more detail in (c)).
+
+\begin{verbatim}
+def single_particle(parameters,plot="y-position"):
+    ```Run MD simulation...'''    
+    #define empty arrays to hold data as a function of time
+    #(left as an exercise to the reader)
+
+    #loop through the integer time steps in the simulation
+    for int_time in range(0,maxtime):
+        #(left as an exercise to the reader)
+        time += dt
+
+\end{verbatim}
+
+\item[(c)]
 
@@
 
+  In our implementation,
+  we created a subroutine to consider each
+  type of force in the system (external drive, landscape, etc).
+  If the particle moves beyond the limits
+  $0 \le y < L$,
+  it must be returned 
+  using the definition of periodic boundary conditions
+  in Sec.~\ref{sec:MD}.
+
+\begin{verbatim}
+  def md_step(y, int_time, avg_vy, parameters, ft=0):
+    ```Calculate net force and integrate eq. of motion...'''
+
+    #calculate the floating point value for time
+    time = int_time * dt
+
+    #reset vy for every timestep since ay = 0 
+    vy = 0
+
+    #calculate the net force on the particle
+    #(left as an exercise to the reader)
+
+    #calculate the new position
+    #(left as an exercise to the reader)
+
+    #check periodic boundary conditions
+    #(left as an exercise to the reader)
+
+    return y, vy, avg_vy
+
+\end{verbatim}
+
+%  \item[(d)]
+
+  \end{enumerate}
+
   The Euler algorithm can be applied to
@@
 
-  A working example of this code is available
-  in Ref.~\cite{supplemental}
+  The molecular dynamics
+  described above
+  is available in Ref.~\cite{supplemental}.
+  We use the Python programming
+  language
+  for educational purposes.
+  To model additional particles,
+  the authors recommend a more traditional 
+  compiled coding language
+  to perform the many operations associated
+  with neighbor lists to compute particle interactions.
 
@@
   is much less than the
-  frequency of the applied drive, as
- can be seen in the time scale in Fig.~\ref{fig:8_brownian},
-  where the average hopping rate is approximately
-  every $4000\tau$,
-  a value much larger than the period of the driving force.  
+  frequency of the applied drive. %, as
+  %can be seen in the time scale in Fig.~\ref{fig:8_brownian},
+  % where the average hopping rate is approximately
+  % every $4000\tau$,
+  % a value much larger than the period of the driving force.  
   At sufficiently high temperatures,

### 2021-03-29 kink_project/kink_step.sh
removed c code and scripts to another repo

@@ -1,54 +1,0 @@
-#Modify DC current and run the MD simulation by modifying the input file Pcw0
-
-DIR1=""
-echo $DIR1
-
-for current in $(seq 0.001 0.001 0.1)
-do
-    echo $current
-    string_current=`printf "%1.3f" $current`
-    dir0=current_$string_current  #check number precision
-    echo $dir0
-
-    #-------------------
-    if [ ! -d $dir0 ]
-    then
-        mkdir $dir0
-    fi
-    #------------------
-
-    cd $dir0
-    pwd
-
-
-    #make the new configuration file Pa0
-    sed 's/current 0.2/current '"$current"'/' <../Pcw0> Pcw0
-
-    #the high DC currents (current > 0.5) don't need to run
-    #for so long we could include another sed call to reduce the total simulation time
-    #
-    
-    
-    cp ../restart_config .
-    #run the physics MD code
-    rm velocity_data/XV_data_t\=00*
-
-    #run the simulation
-    #/home/danielle/Research/YDrive_AR/Source_Code/substrate_run_wstripe
-
-    #extract velocity info into local file
-    python3 ~/pymodules/animation_code/measuring_kink_velocity.py > avg_kink_vel.txt
-
-    #extract the first line of the file
-    #avg=`tail -n 1 avg_kink_vel.txt`
-
-    #python ~/pymodules/animation_code/channel_colloid_movie_maker.py 
-	
-    cd ../
-    pwd
-
-    #combine all info in a single file
-    echo $current $avg >> avg_kink_vel.txt
-done
-	
-

### 2021-03-29 kink_project/kink_step_analysis.sh

@@ -1,37 +1,0 @@
-#Modify DC current and run the MD simulation by modifying the input file Pcw0
-
-DIR1=""
-echo $DIR1
-
-for current in $(seq 0.001 0.001 0.1)
-do
-    echo $current
-    string_current=`printf "%1.3f" $current`
-    dir0=current_$string_current  #check number precision
-    echo $dir0
-
-    #-------------------
-    if [ ! -d $dir0 ]
-    then
-        mkdir $dir0
-    fi
-    #------------------
-
-    cd $dir0
-    pwd
-
-
-    #extract velocity info into local file
-    python3 ~/pymodules/animation_code/measuring_kink_velocity.py > avg_kink_vel.txt
-
-    #extract the first line of the file
-    avg=`tail -n 1 avg_kink_vel.txt`
-	
-    cd ../
-    pwd
-
-    #combine all info in a single file
-    echo $current $avg >> avg_kink_vel.txt
-done
-	
-

### 2021-03-29 kink_project/measuring_kink_velocity.py

@@ -1,1 +1,0 @@
-/home/danielle/pymodules/animation_code/measuring_kink_velocity.py

### 2021-03-29 kink_step.sh
removed kink script to another repo

@@ -1,51 +1,0 @@
-#Modify DC current and run the MD simulation by modifying the input file Pcw0
-
-DIR1=""
-echo $DIR1
-
-for current in $(seq 0.01 0.1 0.01)
-do
-    echo $current
-    dir0=current_'printf "%1.2" $current'  #check number precision
-    echo $dir0
-
-    #-------------------
-    if [ ! -d $dir0 ]
-    then
-        mkdir $dir0
-    fi
-    #------------------
-
-    cd $dir0
-    pwd
-
-    restart=0
-
-    if [ $restart -eq 0 ] && [ -f *.sh.o* ]
-    then
-	echo "Already run"
-    else
-	#make the new configuration file Pa0
-	sed 's/current 0.2/current '"$current"'/' <../Pcw0> Pcw0
-	cp ../restart_config .
-	#run the physics MD code
-	rm velocity_data/XV_data_t\=00*
-
-	#run the simulation
-	/home/danielle/Research/YDrive_AR/Source_Code/run_wstripe
-
-	#extract velocity info into local file
-	python measuring_kink_velocity.py > avg_kink_vel.txt
-
-	#extract the first line of the file
-	avg=`tail -n 1 avg_kink_vel.txt`
-
-    fi
-
-    cd ../
-
-    #combine all info in a single file
-    echo $current $avg >> avg_kink_vel.txt
-done
-	
-exit

### 2021-03-29 manuscript/manuscript_ajp_version2.tex
updated title

@@
 
-\title{Molecular dynamics simulation of synchronization in driven particles}
+%DM replace?
+%\title{Molecular dynamics simulation of synchronization in driven particles}
+\title{Molecular dynamics simulation of a driven synchronized particle}
 
@@
   A working example of this code is available
-  in Ref.~\cite{supplemental}.
+  in Ref.~\cite{supplemental}
   If you would like to write your own,
@@
 
-  The molecular dynamics
-  described above
-  is available in Ref.~\cite{supplemental}.
+  %The molecular dynamics
+  %described above
+  %is available in Ref.~\cite{supplemental}
   We use the Python programming
@@
   For example,
-  what pattern of hops occurs for
+  calculate the patterns of hops for
   fixed parameters 
@@
   modified parameter
-  $F_{\rm ac} = 0.2, 0.3$ and $0.4$?
+  $F_{\rm ac} = 0.2, 0.3$ and $0.4$.
 

### 2021-03-30 manuscript/manuscript_ajp_version2.tex
updated some language in exercises

@@
 numerical integration techniques in Problem~\ref{ex:euler}.
-We explore changes in the particle motion
-with parameter changes in Problem~\ref{ex:parameters}.
+%DM slight rewrite to remove the redundant ``we'' tense
+Changes to the parameters are described in 
+%We explore changes in the particle motion
+%with parameter changes in
+Problem~\ref{ex:parameters}.
 We include analytic solutions to  the 
@@
 the equation of motion in Problem~\ref{ex:n2l}.
-%[xx see comment below xx]
-We extend the model with
-numerical problems 
+%[DM working on it xx see comment below xx]
+%DM rewrite of the following sentence - unclear as written/edited
+We extend the numerical model %with
+%numerical problems 
 to include finite temperature effects
@@
   \label{ex:euler}
+
   %[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK.
@@
 Then mention that a program is available, which you only mention in the abstract xx]
+  To calculate the position of the particle
+  %DM add
+  as a function of time
+  %DM end
+  we
+  numerically integrate the equation of motion
+  %DM add
+  (Eq.~\ref{eq:motion})
+  %DM end
+  using
+  the standard definition of velocity
+  $\vec{v} = d\vec{r}/dt$ 
+  using the 
+  Euler method.
+  %DM substituted direct reference for ``The equation of motion...''
+  Eq.~\ref{eq:motion} provides
+  a direct calculation for the particle velocity
+  from the net force on the particle,
+  as demonstrated in Problem~\ref{ex:n2l}.
 
@@
   most comments and optional details are removed for clarity.
+    %The molecular dynamics
+  %described above
+  %is available in Ref.~\cite{supplemental}
+  We use the Python programming
+  language
+  for educational purposes.
+  To model additional particles,
+  the authors recommend a more traditional 
+  compiled coding language
+  to perform the many operations associated
+  with neighbor lists to compute particle interactions.
 
@@
 
-  \item[(a)] {\bf Initialization}
+  \item[(a)] {\bf Initialization.}
     For convenience,
-    we defined a Python dictionary
+    we define a Python dictionary
     to contain the simulation constants
@@
 
-  \item[(b)]
-    A key decision for any MD algorithm
-    is how much information to save during and after
-    the simulation.
-    We define the following constants
-    to manage the length of arrays
-    containing data.
-
-\begin{verbatim}
-#integer time steps
-dict[`maxtime']=int(40/dict['freq'])   #total time steps 
-dict[`writemovietime']=1   #write data to arrays for plotting
-\end{verbatim}
-%dict['decifactor'] = 1     #decimation factor - when to average values
-
-    In the subroutine {\bf single\_particle()}
-    calculate the array lengths to hold
-    position, velocity, and time data.
-    Define a loop to 
-    calculate the particle position and velocity through each
-    molecular dynamics time step,
-    calculated in the subroutine {\bf md\_step()}
-    (which will be described in more detail in (c)).
-
-\begin{verbatim}
-def single_particle(parameters,plot="y-position"):
-    ```Run MD simulation...'''    
-    #define empty arrays to hold data as a function of time
-    #(left as an exercise to the reader)
-
-    #loop through the integer time steps in the simulation
-    for int_time in range(0,maxtime):
-        #(left as an exercise to the reader)
-        time += dt
-
-\end{verbatim}
-
-\item[(c)]
-
-  To calculate the position of the particle we
-  numerically integrate the equation of motion using
-  the standard definition of velocity
-  $\vec{v} = d\vec{r}/dt$ 
-  using the 
-  Euler method. 
-  The equation of motion provides
-  a direct calculation for the particle velocity,
-  as demonstrated in Problem~\ref{ex:n2l}.  
-  The Euler method is effective for solving linear ordinary differential  equations
+   \item[(b)] {\bf Time loop.}
+     The Euler method is effective
+     for solving linear ordinary differential  equations
      of the form
@@
 
+     Add a $for$ loop
+     to step through each integer timestep.
+     With this loop, 
+     control
+     the flow of the program
+     and retain information for the particle position and other
+     properties
+     as a function of time.
+     Assume this information
+     will be calculated a subroutine.
+
+     We used the subroutine {\bf single\_particle()}
+     calculate the array lengths to hold
+     position, velocity, and time data.
+     The lengths of these arrays will be affected by
+     how much data you choice to save
+     (see comment following sample code).
+     Define a loop to 
+     calculate the particle position and velocity through each
+     molecular dynamics time step,
+     calculated in the subroutine {\bf md\_step()}
+     which will be described in more detail in (c).
+
+\begin{verbatim}
+def single_particle(parameters,plot="y-position"):
+    ```Run MD simulation...'''    
+    #define empty arrays to hold data as a function of time
+    #(left as an exercise to the reader)
+
+    #loop through the integer time steps in the simulation
+    for int_time in range(0,maxtime):
+        #(left as an exercise to the reader)
+        time += dt
+
+\end{verbatim}
+
+{\it Comment:}     
+     A key decision for any MD algorithm
+     is how much information to save during and after
+     the simulation.
+     %DM if going to emphasize this, have the reader do something with it
+     %cut out - and make a comment rather than a statement going nowhere
+     We define the following constants
+     to manage the length of arrays
+     containing data.
+     We found in practice that for 
+     short simulations times
+     we could save all data.
+
+\begin{verbatim}
+#integer time steps
+dict[`maxtime']=int(40/dict['freq'])   #total time steps 
+dict[`writemovietime']=1   #write data to arrays for plotting
+\end{verbatim}
+%dict['decifactor'] = 1     #decimation factor - when to average values
+
+\item[(c)] {\bf Position and force calculations.}
+  %[DM moved sentences about general numerical solution to beginning
+  %and those about time to (b)]
   In our implementation,
@@
     #calculate the net force on the particle
-    #(left as an exercise to the reader)
+    vy = #(left as an exercise to the reader)
 
     #calculate the new position
-    #(left as an exercise to the reader)
+    y += #(left as an exercise to the reader)
 
@@
   so that the interparticle force changes significantly over small distances and the simple Euler algorithm is insufficient.
-
-  %The molecular dynamics
-  %described above
-  %is available in Ref.~\cite{supplemental}
-  We use the Python programming
-  language
-  for educational purposes.
-  To model additional particles,
-  the authors recommend a more traditional 
-  compiled coding language
-  to perform the many operations associated
-  with neighbor lists to compute particle interactions.
 
@@
 
-To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
+ %DM moved to end of paragraph
+%To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
 Use reasonable values for the
@@
 In addition to the values listed in Table~\ref{tab:1},
+to first order
+the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
+and 
 the liquid density 
-  $\rho \sim 10^3$ kg/cm$^3$ is a reasonable
-  first order approximation.\cite{asce}
+$\rho \sim 10^3$ kg/cm$^3$.\cite{asce}
+%DM removed
+%is a reasonable
+%first order approximation
   \end{problem}
@@
   \bibitem{supplemental}
+    %not sure if the manuscript can remain in the repo - that probably violate AIP rules https://publishing.aip.org/resources/researchers/rights-and-permissions/author-licenses/
+    %will make a DOI for the repo
+    %https://guides.github.com/activities/citable-code/
     \url{<https://github.com/mcddanielle/AJP_project/>}.

### 2021-03-30 code/MD_colloid.py
separated figures from exercises

@@ -554,7 +554,7 @@ def set_parameters():
     dict['Np'] = 20         #number of troughs in the substrate
     dict['period'] = dict['Sy']/dict['Np']  #spatial period of substrate in y-direction
 
-    #Brownian motion factor
+    #Brownian motion factor - for solution to problem X in AJP
     dict['temperature'] = 5.7*dict['AP']
     
     dict['F_DC'] = 0.07
@@ -642,32 +642,17 @@ if __name__ == "__main__":
     #make shapiro steps with a range of F^{dc}
     #this is the place to include the strictly DC force...
     #--------------------------------------------------------------
-    if make_fig == 3 or make_fig == 6: 
+    if make_fig == 3: 
 
         #sweep through a variety of dc values
         delta_Fdc = 0.001
+        Fdc_max=0.2+delta_Fdc
+        #parameters['freq']=0.1
+        F_AC = [0.0, 0.07]
         
-        if make_fig == 3:
-
-            Fdc_max=0.2+delta_Fdc
-            #parameters['freq']=0.1
-
-            F_AC = [0.0, 0.07]
-        
-        elif make_fig == 6:
-
-            #IN EXPLORING THE HIGH FREQUENCY REGIME,
-            #I'M SEEING STEP HEIGHTS LIKE JUNIPER (but still fractional)  
-            parameters['freq'] = 0.1
-            delta_Fdc = 0.01
-            F_AC = [0.1,0.2,0.3,0.4]
-            Fdc_max=0.6+delta_Fdc
-
-
         max_value = int(np.ceil(Fdc_max/delta_Fdc))
         avg_vy_data = np.zeros(max_value)
         Fdc_data = np.arange(0,Fdc_max,delta_Fdc)
-
 
         #make the figure 
         fig = plt.figure(figsize=(7,4.5))
@@ -712,114 +697,8 @@ if __name__ == "__main__":
         plt.tight_layout(pad=0.2)
         plt.savefig(parameters['filename'])
         
-    #--------------------------------------------------------------
-    #modify either frequency (fig5) or F^ac amplitude (fig6) or F^ac = 0
-    #--------------------------------------------------------------
-    if make_fig == 5 or make_fig == 6:
-        
-        parameters['dt'] = 0.1 #timestep in simulation units
-        parameters['writemovietime']=1   #interval to write data to arrays for plotting
 
 
-        if make_fig == 5:
-            parameters['maxtime']=4500        #total time steps in simulation
-
[…]

### 2021-03-30 code/solutions_exercises.py

@@ -1,0 +1,226 @@
+#!/usr/bin/env python3
+
+#################################################################
+'''
+Supplementary Material for
+Molecular dynamics simulation of synchronization in driven particles
+American Journal of Physics
+
+Makes Figures 2-9 using a flag to select
+
+Danielle McDermott
+Tiare Guerrero
+'''
+#################################################################
+import numpy as np
+import math, sys
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import matplotlib.cm as cm
+
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from mpl_toolkits.axes_grid.inset_locator import (inset_axes,
+                                                  InsetPosition,
+                                                  mark_inset)
+
+
+#set default font of plot
+plt.rc('font', size=24)
+
+#main MD routines
+import MD_colloid
+
+
+#-------------------------------------------------------------------
+if __name__ == "__main__":
+
+    #will pass the parameters dict to subroutines to read constants
+    parameters = MD_colloid.set_parameters()
+
+    #select which figure in the AJP you would like to make
+    #figures 2a, 2b, 2c, 5
+    solve_exercise = "5"
+
+    parameters['filename']="exercise_%s.pdf"%(solve_exercise)
+
+    letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
+
+    #--------------------------------------------------------------
+    #make shapiro steps with a range of F^{dc}
+    #this is the place to include the strictly DC force...
+    #--------------------------------------------------------------
+    if solve_exercise == "3c": 
+
+        #sweep through a variety of dc values
+        delta_Fdc = 0.001
+
+        #IN EXPLORING THE HIGH FREQUENCY REGIME,
+        #I'M SEEING STEP HEIGHTS LIKE JUNIPER (but still fractional)  
+        parameters['freq'] = 0.1
+        delta_Fdc = 0.01
+        F_AC = [0.1,0.2,0.3,0.4]
+        Fdc_max=0.6+delta_Fdc
+
+        max_value = int(np.ceil(Fdc_max/delta_Fdc))
+        avg_vy_data = np.zeros(max_value)
+        Fdc_data = np.arange(0,Fdc_max,delta_Fdc)
+
+        #make the figure 
+        fig = plt.figure(figsize=(7,4.5))
+        gs=gridspec.GridSpec(1,1)
+        ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
+
[…]

### 2021-03-30 code/solutions_exercises.py
updated exercise code and checked pdfs produced

@@ -40,73 +40,11 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #figures 2a, 2b, 2c, 5
-    solve_exercise = "5"
+    solve_exercise = "2c"
 
     parameters['filename']="exercise_%s.pdf"%(solve_exercise)
 
     letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
-
-    #--------------------------------------------------------------
-    #make shapiro steps with a range of F^{dc}
-    #this is the place to include the strictly DC force...
-    #--------------------------------------------------------------
-    if solve_exercise == "3c": 
-
-        #sweep through a variety of dc values
-        delta_Fdc = 0.001
-
-        #IN EXPLORING THE HIGH FREQUENCY REGIME,
-        #I'M SEEING STEP HEIGHTS LIKE JUNIPER (but still fractional)  
-        parameters['freq'] = 0.1
-        delta_Fdc = 0.01
-        F_AC = [0.1,0.2,0.3,0.4]
-        Fdc_max=0.6+delta_Fdc
-
-        max_value = int(np.ceil(Fdc_max/delta_Fdc))
-        avg_vy_data = np.zeros(max_value)
-        Fdc_data = np.arange(0,Fdc_max,delta_Fdc)
-
-        #make the figure 
-        fig = plt.figure(figsize=(7,4.5))
-        gs=gridspec.GridSpec(1,1)
-        ax1 = fig.add_subplot(gs[0,0])  #scatter plot of particles
-
-        for F in F_AC:
-            parameters['F_AC'] = F
-
-            #run the MD sim for each value of FD, this takes a while...
-            for i in range(len(avg_vy_data)):
-
-                #sweep through a range of dc values
-                parameters['F_DC'] = Fdc_data[i] 
-                
-                #run a single MD simulation for a set of parameters
-                avg_vy_data[i] = MD_colloid.single_particle(parameters,plot="y-velocity")
-                
-            #normalize <vy> so you can count step number
-            avg_vy_data /= (parameters['freq']*parameters['period'])
-            
-            #plot <vy> vs F_dc
-            if F == 0.0:
-                ax1.plot(Fdc_data,avg_vy_data,"--",linewidth=2,label=r"%1.2f"%(F))
-            else:
-                ax1.plot(Fdc_data,avg_vy_data,linewidth=2,label=r"%1.2f"%(F))
-
[…]

### 2021-03-30 manuscript/manuscript_ajp_version2.tex
cleaned up exercises

@@
 flickering patterns of
-candle flames %[DM - the air molecules are oscillating I think xx is a flame an oscillator? xx]
+candle flames [DM - the air molecules are oscillating xx is a flame an oscillator? xx]
 mediated by temperature fluctuations,\cite{Okamoto2016}
@@
 the particle velocity is modulated by 
-the potential energy landscape exerted on the particle.  %seen by the particle. [DM swapped ``seen by'' for ``exerted on'' xx check added wording xx] 
+the potential energy landscape exerted on the particle.  %seen by the particle.
+[DM swapped ``seen by'' for ``exerted on'' xx check added wording xx] 
 Below some threshold  
@@
 %charge density waves in dusty plasma
-%[DM rewrote to better align with conclusion xx added words is this correct? xx]
+[DM rewrote to better align with conclusion xx added words is this correct? xx]
 and superconducting vortices in the presence of periodic pinning arrays.
-% and Josephson junctions. %[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
+% and Josephson junctions.
+[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
 We include problems for interested readers 
@@
 its trajectory.
-The particle is confined in a two-dimensional (2D) %[DM singlular]
+The particle is confined in a two-dimensional (2D) [DM singular]
 simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
 where $a_0$ is a dimensionless unit of length.
-%[DM - yes.
-in the simulation we just use L=46.6 and the a_0 is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?
+[DM - yes.
+in the simulation we just use $L=46.6$ and the $a_0$ is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?
 xx]
-The particle %Particle $i$ %[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
+The particle %Particle $i$
+[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
 has
@@
  the maxima are colored gray and the minima colored white.
- %[DM - switch from red/blue to white/gray - xx make sure that all your figures make sense when printed in b/w xx]
-
-The confining force on the particle %[DM removed subscripts] $i$
+ [DM - switch from red/blue to gray/white - xx make sure that all your figures make sense when printed in b/w xx]
+
+The confining force on the particle [DM removed subscripts] $i$
  is given by
  \begin{equation}
- \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
+ \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). [DM removed ^{\ell}]
  \label{eq:dudr}
@@
  $|\vec{F}_{\ell}|$ is calculated from the particle position $y$.
- %[DM - begrudingly changed - My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.
+ [DM - begrudingly changed - My collaborators and I usually use superscripts for these equations to separate the force superscripts from the particle index subscripts.
 This is consistent with the textbook I teach from.
@@
   The landscape is shown with
-  %[DM changed color scheme from red/blue to gray/white for better BW conversion]
+  [DM changed color scheme from red/blue to gray/white for better BW conversion]
   maxima in the potential energy are gray %#red
@@
   (b) The potential energy function
-  along the $y$-axis $U(y)$.  %DM removed _{\ell}
+  along the $y$-axis $U(y)$.  [DM removed $_{\ell}$]
   The particle in (a) is shown at the same $y$-position.
-  The slope of $U(y)$ %[DM removed _{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
+  The slope of $U(y)$ [DM removed $_{\ell}$ use the subscripts with the potential, but will move to superscript xx used subscript here xx]
   is the 
@@
 The numerical implementation of the landscape 
-is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  %[DM - right, two negative signs, one from the derivative, the other from the definition of force.
-I found the ``mistaken'' dropped minus sign in the depths of january and added it.
+is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  [DM - right, two negative signs, one from the derivative, the other from the definition of force.
+I found the ``mistakenly'' dropped minus sign in the depths of january and added it.
 xx but you should get a + sign not a minus sign xx]
@@
 the particle moves across the substrate maxima,
-%[DM - color change]
+[DM - color change]
 shown in gray with the contour plot.
@@
   %is given,
-  correspond with the
-  panels (a-d) 
+  correspond with the fixed value of $F_{\rm dc}$
+  in each of the phase plots
   %indicating a system
-  plotted in Fig.~\ref{fig:4_phase}.
-  %[DM - clarified?  xx don't understand meaning of indicating a system
-  %plotted in Fig.~\ref{fig:4_phase} xx]
+  in Fig.~\ref{fig:4_phase}(a-d).
+  [DM - clarified?  xx don't understand meaning of indicating a system
+  plotted in Fig.~\ref{fig:4_phase} xx]
 }
@@
   the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
-  %[DM rewrite]
+  [DM rewrite following sentence]
   If the system
@@
 numerical integration techniques in Problem~\ref{ex:euler}.
-%DM slight rewrite to remove the redundant ``we'' tense
+[DM slight rewrite to remove the redundant ``we'' active voice construction]
 Changes to the parameters are described in 
@@
   \label{ex:euler}
-
   %[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK.
@@
      Eq.~\ref{eq:motion}
-     %[DM - resolved xx refer to specific equation by label xx]
+     [DM - resolved xx refer to specific equation by label xx]
      to determine  the analytic expression
@@
   Appropriate temperatures to explore
-  are $T/A_p = 3.0, 3.5$, and $4.0$.
-  Plot the $y-position$ versus time
+  are $3.0 < T/A_p = 7.0$.
+  %DM moved position out of math mode
+  Plot the $y-$ position versus time
   for this particle.
@@
 
-  {\it Comment: } For a driven particle,
+  %{\it Comment: }
+  For a driven particle,
   we ignore 
@@
   in these simulations.  
-  We note that even for $T/A_p = 4.0$ 
+  We note that even for $T/A_p = 6.0$ 
   the hopping rate

### 2021-03-30 code/MD_colloid.py

@@ -555,7 +555,7 @@ def set_parameters():
     dict['period'] = dict['Sy']/dict['Np']  #spatial period of substrate in y-direction
 
     #Brownian motion factor - for solution to problem X in AJP
-    dict['temperature'] = 5.7*dict['AP']
+    dict['temperature'] = 0.0 
     
     dict['F_DC'] = 0.07
     dict['drop'] = dict['maxtime']   #integer timesteps to "ramp" the DC force

### 2021-03-30 code/solutions_problems.py

@@ -40,22 +40,31 @@ if __name__ == "__main__":
 
     #select which figure in the AJP you would like to make
     #figures 2a, 2b, 2c, 5
-    solve_exercise = "2c"
+    solve_problem = "5"
 
-    parameters['filename']="exercise_%s.pdf"%(solve_exercise)
+    parameters['filename']="problem_%s.pdf"%(solve_problem)
 
     letter=["(a)","(b)","(c)","(d)","(e)","(f)","(g)"]
         
     #--------------------------------------------------------------
-    #modify either frequency (fig5) or F^ac amplitude (fig6) or F^ac = 0
+    #modify either frequency (2b) or F^ac amplitude (2a) or F^ac = 0
     #--------------------------------------------------------------
-    if solve_exercise == "2a" or solve_exercise == "2b":
+    if solve_problem == "2a" or solve_problem == "2b":
         
         parameters['dt'] = 0.1 #timestep in simulation units
         parameters['writemovietime']=1   #interval to write data to arrays for plotting
 
+        if solve_problem == "2a":
+            parameters['maxtime']=3000        #total time steps in simulation
 
-        if solve_exercise == "2a":
+            #we will sweep through the following independent variable
+            F_AC = [0.2, 0.3, 0.4]
+            ind_var = F_AC
+            str_iv=" $F_{\mathrm{ac}}$=%1.2f"
+            #parameters['freq'] = 0.1
+            #parameters['F_DC'] = 0.1
+            
+        else:
             parameters['maxtime']=4500        #total time steps in simulation
 
             #we will sweep through the following independent variable
@@ -63,16 +72,6 @@ if __name__ == "__main__":
             frequency = [0.1,0.015,0.01, 0.005, 0.002, 0.001]
             ind_var = frequency
             str_iv=" f=%1.3f"
-
-        else:
-            parameters['maxtime']=3000        #total time steps in simulation
-
-            #we will sweep through the following independent variable
-            F_AC = [0.2, 0.4]
-            ind_var = F_AC
-            str_iv=" $F_{\mathrm{ac}}$=%1.2f"
-            #parameters['freq'] = 0.1
-            #parameters['F_DC'] = 0.1
 
         #make the figure
         n_plots = len(ind_var)
@@ -89,7 +88,7 @@ if __name__ == "__main__":
             parameters['axis'] = ax
 
             #select the independent variable
-            if solve_exercise == "2a":
+            if solve_problem == "2b":
[…]

### 2021-04-11 manuscript/manuscript_ajp_version3.tex
rearranging introduction

--- 2021-03-30 manuscript/manuscript_ajp_version2.tex
@@
 
-%DM replace?
-%\title{Molecular dynamics simulation of synchronization in driven particles}
-\title{Molecular dynamics simulation of a driven synchronized particle}
+\title{Molecular dynamics simulation of synchronization of a  driven particle}
 
@@
 \email{guer9330@pacificu.edu}
-\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}
+\affiliation{Department of Physics, Pacific University, Forest Grove, Oregon 97116}
 
@@
 \email{mcdermott@pacific.edu}
-\affiliation{Department of Physics, Pacific University, Forest Grove, OR 97116}
+\affiliation{Department of Physics, Pacific University, Forest Grove, Oregon 97116}
 
@@
 \begin{abstract}
-  Synchronization
-  plays an important role in many physical processes.
   We discuss a 
@@
   phase space orbit.
-  This synchronized motion
-  is
-  observed in 
+  %DM removed first sentence,
+  %which was strong and clear, but isolated in the abstract
+  %put those ideas in this final sentence, making it a mouthful [26 words]
+  Isolating
+  synchronized motion
+  in 
   simulations and table-top experiments,
-  and
-  can be used to isolate
-  complex natural behaviors.
+  can be used to study %DM replaced isolate with study
+  complex natural behaviors
+  which
+  play an important role in many physical processes.
  %[suggest omitting this sentence. Code not in text. We include molecular dynamics code
@@
 flickering patterns of
-candle flames [DM - the air molecules are oscillating xx is a flame an oscillator? xx]
+candle flames 
 mediated by temperature fluctuations,\cite{Okamoto2016}
@@
 synchronization --
-birds coordinate wing flaps
+birds  coordinate their wing flaps
 to optimize energy use during flight,\cite{Portugal2014}
@@
 and brain tissue.\cite{Singer1999}
-External forcing can cause or regulate 
-synchronization. For example, 
-an electrical pacemaker 
-regulates a heart beat 
-and 
-a pulsed light modifies the
-flashing pattern of fireflies.
+%DM ended paragraph with fewer examples, added transition sentence
+Mechanisms of synchronization
+can be WHAT
 
@@
 first appeared in the scientific literature
-with 
-Huygens' 1665 experiments on the
+in 1665 with 
+Huygens'  experiments on the
 motions of synchronized 
@@
 times the length of another swings with twice the period.
+%DM transition sentence
+Simulations and laboratory experiments
+of mode-locked synchronization
+can help provide insights to a diverse range of 
+oscillation phenomena.
+
+%DM better main topic
+Experiments with colloids
 
@@
 can be studied with
-colloid particles in experiments.
-Typical colloids are   
+colloid particles.
+In experiments %DM moved the ``in experiments'' to second sentence
+typical colloids are   
 plastic spheres suspended in
@@
 are useful for
-understanding synchronization at a single particle level.\cite{Juniper2015,Juniper2017}
+understanding synchronization
+at a single particle level.\cite{Juniper2015,Juniper2017}
 
@@
 
+%new topic - DM this sentence appeared toward the end of the intro
 The model discussed in this paper
-resembles an overdamped driven pendulum.
+resembles a damped driven pendulum 
+where external forces
+add or remove energy from the system.
+A single pendulum is driven by
+the external force of gravity to return
+to an equilibrium position,
+and may be damped to decreasing amplitude
+by mechanical friction or air resistance.
+Multiple pendula may swing in phase
+when coupled through shared vibrations.
+
+External forcing
+can cause or regulate synchronization.
+For example, 
+an electrical pacemaker 
+regulates a heart beat 
+and 
+a pulsed light modifies the
+flashing pattern of fireflies. 
+%damping
+%transition
+
 A single particle oscillator
@@
 the particle velocity is modulated by 
-the potential energy landscape exerted on the particle.  %seen by the particle.
-[DM swapped ``seen by'' for ``exerted on'' xx check added wording xx] 
+the potential energy landscape exerted on the particle.   
 Below some threshold  
@@
 We describe
-our molecular dynamics model  in Sec.~\ref{sec:MD}.
+our   model  in Sec.~\ref{sec:MD}.
 The model
@@
 driven across a periodic landscape in 
-Sec.~\ref{sec:results}.
-
-In Sec.~\ref{sec:conclusion}
+Sec.~\ref{sec:results}. In Sec.~\ref{sec:conclusion}
 we describe how our results apply 
@@
 such as optically trapped colloids
-%charge density waves in dusty plasma
-[DM rewrote to better align with conclusion xx added words is this correct? xx]
 and superconducting vortices in the presence of periodic pinning arrays.
-% and Josephson junctions.
-[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
 We include problems for interested readers 
@@
 We use a classical model for 
-studying the dynamics, %xx you only use single particles xx]
+studying the dynamics, 
 using the net force on a particle to calculate
 its trajectory.
-The particle is confined in a two-dimensional (2D) [DM singular]
+The particle is confined in a two-dimensional 
 simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
-where $a_0$ is a dimensionless unit of length.
-[DM - yes.
-in the simulation we just use $L=46.6$ and the $a_0$ is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?
-xx]
-The particle %Particle $i$
-[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
+and $a_0$ is a dimensionless unit of length. (In the simulations we   set $a_0 = 1$.)
+The particle 
 has
@@
 The units of the simulated variables are summarized in Table~\ref{tab:1}.
-%\footnote{To learn more about the effects of temperature on this simulation see Problem~\ref{ex:brownian}, where we study $U_0 \sim k_B T$.}
 
@@
  the maxima are colored gray and the minima colored white.
- [DM - switch from red/blue to gray/white - xx make sure that all your figures make sense when printed in b/w xx]
-
-The confining force on the particle [DM removed subscripts] $i$
+
+The confining force on the particle $i$
  is given by
  \begin{equation}
- \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). [DM removed ^{\ell}]
+ \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}),
  \label{eq:dudr}
  \end{equation}
- %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
@@
  $|\vec{F}_{\ell}|$ is calculated from the particle position $y$.
- [DM - begrudingly changed - My collaborators and I usually use superscripts for these equations to separate the force superscripts from the particle index subscripts.
-This is consistent with the textbook I teach from.
-xx suggest that you use subscripts instead of superscripts.
-We can easily make that change in the next iteration of your manuscript.
-However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$.
-One of us didn't like superscripts where he was an undergraduate!
-xx]
-
-Particles are subject to an external time-dependent driving force
+
+The particle is subject to an external time-dependent driving force
 $\vec{F}_{\rm d}(t)$
@@
 \begin{equation}
-  \vec{F}_{\rm d}(t) = [F_{\rm dc} + F_{\rm ac} \sin(\omega t)] \hat{y},
+  \vec{F}_{\rm d}(t) = \big [F_{\rm dc} + F_{\rm ac} \sin(\omega t)\big] \hat{y},
     \label{eq:drive}
@@
 and a time dependent component with amplitude $F_{\rm ac}$
-with angular frequency $\omega = 2 \pi f$.
-
-The inertia of 
-small particles is reduced by interactions
+and angular frequency $\omega = 2 \pi f$.
+
+The inertia of the 
+small particle is reduced by interactions
 with the fluid particles.\cite{Purcell1977}
@@
 overdamped
-so the particles do not accelerate,
-that is, they are suspended in a continuous viscous fluid
+so the particle does not accelerate,
+that is, it is suspended in a continuous viscous fluid
 that dissipates energy supplied externally. 
-Newton's second law for an individual particle
+Newton's second law for the particle
 is simplified
@@
 \begin{equation}
-  \eta \vec{v} = \vec{F}_{\ell}(\vec{r}) + \vec{F}_{\rm d}(t).
+  \eta \vec{v} = \vec{F}_{\ell}(\vec{r}) + \vec{F}_{\rm d}(t),
     \label{eq:motion}
@@
 with friction coefficient $\eta = 1$ in units of $v_0 / F_0$.
-%[xx added $v_0$ to table, please check xx] 
 The term $-\eta \vec{v}$
-is a drag force, which models
+is a drag force that models
 energy dissipation due to the fluid. 
 We discuss  models for
-spheres moving through fluids in 
+a sphere moving through a fluid in 
 Problem~\ref{ex:reynolds}.
@@
 of an individual particle at position $\vec{r}$ 
-and simulation time $t$.
-The   simulation is controlled by a  loop
-which runs to a maximum integer time step.
-At each time step
-we evaluate the net force on each particle as a function of its position
+and simulation time $t$. At each time step
+we evaluate the net force on the particle as a function of its position
 $\vec{r}(t)$
 and then integrate
-the equation of motion to move particles
-to an updated position.
+the equation of motion to move the particle
+to its updated position.
 Because the acceleration is zero,
 the integration of the equation of motion
-is performed via 
+is performed using 
 the simple first-order Euler method 
 \begin{equation}
-  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
+  \vec{r}(t+\Delta t) = \vec{r}(t) + \vec{v}(t) \Delta t
     \label{eq:euler}
@@
 the numerical methods for 
-solving differential equations.
+solving differential equations such as Eq.~\eqref{eq:euler}.
 %------------------------------------------------------------------
@@
   The landscape is shown with
-  [DM changed color scheme from red/blue to gray/white for better BW conversion]
-  maxima in the potential energy are gray %#red
-  and minima are white %.
-  A particle is 
-  subject to competing forces of the landscape and applied driving force.
-  (b) The potential energy function
-  along the $y$-axis $U(y)$.  [DM removed $_{\ell}$]
-  The particle in (a) is shown at the same $y$-position.
-  The slope of $U(y)$ [DM removed $_{\ell}$ use the subscripts with the potential, but will move to superscript xx used subscript here xx]
-  is the 
-  magnitude of force $\vec{F}_{\ell}$. 
+  maxima of the potential energy in gray 
+  and minima in white. 
+  The particle is 
+  subject to competing forces of the landscape and the applied driving force.
+  (b) The potential energy function $U(y)$. 
+  The particle in (a) is shown at the same $y$-position in (b).
+  The slope of $U(y)$ is the 
+  magnitude of the force $\vec{F}_{\ell}$. 
   }
@@
 \end{figure}
-%
+
 \section{Mode-locking of a single particle}
-% In subsection headings, only the first word is capitalized.
+
 \label{sec:results}
@@
 across the landscape. 
-The numerical implementation of the landscape 
-is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  [DM - right, two negative signs, one from the derivative, the other from the definition of force.
-I found the ``mistakenly'' dropped minus sign in the depths of january and added it.
-xx but you should get a + sign not a minus sign xx]
+The numerical implementation of the force due to the landscape 
+is calculated using Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  
 \begin{equation}
@@
 can produce a variety of hopping patterns in the particle motion. 
-The relative values of $F_{\rm ac}$, $F_{\rm dc}$ and $A_p$
+The relative values of $F_{\rm ac}$, $F_{\rm dc}$, and $A_p$
 control the rate and distance a  particle moves 
@@
 
-%xx AJP does not use footnotes
 \begin{table}[h!]
@@
 \caption{Simulation parameters and units with comparable
-  experimental values.~\cite{Juniper2015,Juniper2017} The substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of the particles.  }
+  experimental values.~\cite{Juniper2015,Juniper2017} The substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of the particles.
+}%[DM changed to T xx what does $T_0 = 0$ mean?
+$T_0$ is never used in the paper.
+xx]  }
 \begin{ruledtabular}
@@
 substrate amplitude & $A_p = 0.1\,F_0$ & $U_0 = 25 k_B T \sim 1\, {\rm J}$ \\ %$U_0 = 0.037 E_0$ 
-temperature & $T_0 = 0$  & $T \sim 290\,$K  \\
+temperature & $T = 0$  & $T \sim 290\,$K  \\
 \end{tabular}
@@
 in the positive $y$-direction
-through a distance $\Delta y = \lambda$  in a time $T$,
+through a distance $\Delta y = \lambda$  in the time $T$,
 so that  
@@
 When $F_{\rm d}(t)$ is large,
-the particle moves across the substrate maxima,
-[DM - color change]
-shown in gray with the contour plot.
-%DM commented out - too much detail
-%The slope of $y/\lambda$ equals zero twice
-%during a driving period,
-%indicating zero
-%forward motion 
-%due to a coincidence of the negative
-%driving force and motion over the landscape maxima.
-%------------------------------------------------------------------------
+the particle moves across the substrate maxima.
+%shown in gray with the contour plot. said in caption
+
 \begin{figure}[h]
@@
   the $y$-position
-  through the second period $100\tau<t<200\tau$
+  through the second period $100\,\tau<t<200\,\tau$
  along with the contour plot depicting
@@
   \begin{equation}
-    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta}.
+    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
   \end{equation}
-  %[xx what is $\beta$? xx]
   where the power $\beta$ varies with the
-  system type and
-  can be used to identify universality class. \cite{Reichhardt2017}
+  %system type and
+  type of phase transition and 
+  %can
+  may 
+  be used to identify the universality class.\cite{Reichhardt2017} %[xx what does system type mean? xx - DM modified to phase transition]
   The critical force $F_c$ is equal to the maximum substrate force
@@
 At 
-low $F_{\rm dc}$ the average velocity $\langle v_y \rangle$ is zero.
+low values of $F_{\rm dc}$, the average velocity $\langle v_y \rangle$ is zero.
 Because 
@@
 a 0:0 mode.
-At higher $F_{\rm dc}$ the particle velocity 
+At higher values of $F_{\rm dc}$, the particle velocity 
 $\langle v_{y} \rangle$ increases in steps of uniform height,
@@
 We observe a mode of $n=1$
-for the range $0.05 < F_{\rm dc} < 0.08$,
+for   $0.05 < F_{\rm dc} < 0.08$,
 $n=2$ for $0.08 < F_{\rm dc} < 0.11$,
@@
 and depends on the strength of $F_{\rm ac}$
-%as a Bessel function 
 for this landscape potential.\cite{Reichhardt2000,Juniper2017}
-%[DM the step width - simply removed xx what quantity depends on a Bessel function? xx]
 These steps, known as Shapiro steps, can have a variety of
@@
   The value of $F_{\rm dc}$ for the first four steps
-  %is given,
-  correspond with the fixed value of $F_{\rm dc}$
+  correspond to the fixed value of $F_{\rm dc}$
   in each of the phase plots
-  %indicating a system
   in Fig.~\ref{fig:4_phase}(a-d).
-  [DM - clarified?  xx don't understand meaning of indicating a system
-  plotted in Fig.~\ref{fig:4_phase} xx]
 }
@@
   \end{equation}
-  For zero landscape force, 
+For a zero landscape force, 
   the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
-  [DM rewrite following sentence]
 If the system
@@
   recurs at a particular spatial location, and 
-  %If the velocity
-  %is mode-locked to 
-  %a spatial location,
-  %[xx don't understand meaning of the velocity
-  %is mode-locked to 
-  %a spatial location xx]
 a closed loop appears in  
@@
   with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
- %[xx this sentence not helpful, what is plotted is clear: For clarity the plots are normalized by the prefactor $2\pi$.  xx]
 For
   $F_{\rm dc} = 0.04$
-  the phase plot   in Fig.~\ref{fig:4_phase}(a) with is an
-  % small [xx not clear what small means? can we eliminate this word? xx]
+  the phase plot   in Fig.~\ref{fig:4_phase}(a)  is an
   asymmetric curve.
@@
   and has no net velocity.
-  The asymmetry is caused by bias induced by $F_{\rm dc}$.
+  The asymmetry is caused by the bias induced by $F_{\rm dc}$.
   In Fig.~\ref{fig:4_phase}(b)
@@
   increased,
-  nodes form in the phase diagram, which
-   occur due to repeated values
+  nodes form in the phase diagram, which occur
+  due to repeated values
   of $\dot{\phi}$ over multiple phase positions.
@@
       \caption{
-        Phase plot of $\dot{\phi(t)}/(2\pi)$ versus $\phi(t)/(2\pi)$.
+        Phase plot of $\dot{\phi}(t)/(2\pi)$ versus $\phi(t)/(2\pi)$.
         The particle is driven with $F_{\rm dc}$ equal to  (a) $0.04$, (b) $0.07$, (c) $0.1$, and (d) $0.125$.  These values are denoted as black circles
@@
 devices as 
-stepped regions in the relation between current-voltage,
+stepped regions in the relation between current and voltage,
 where the voltage is the analog of the external driving force
 and current is the analog of particle velocity.
-These mode-locked or phase-locked currents (Shapiro steps), 
-due to applied ac voltages in 
-single Josephson junctions\cite{Shapiro1963, Golubov2004} and
-coupled arrays of junctions have been observed.\cite{Benz1990}
+%DM FIX FOLLOWING SENTENCE
+Known as Shapiro steps, 
+these mode-locked or phase-locked currents
+%arise 
+%due to applied ac voltages
+were first
+observed in single Josephson junctions\cite{Shapiro1963, Golubov2004}.
+%coupled arrays of junctions.\cite{Benz1990}
+%DM END FIX
 Shapiro steps vary in width depending on the strength of the
@@
 numerical integration techniques in Problem~\ref{ex:euler}.
-[DM slight rewrite to remove the redundant ``we'' active voice construction]
 Changes to the parameters are described in 
-%We explore changes in the particle motion
-%with parameter changes in
 Problem~\ref{ex:parameters}.
 We include analytic solutions to  the 
-linear drag equation in Problem~\ref{ex:reynolds}, 
+linear drag equation in Problem~\ref{ex:reynolds}, and consider
 the equation of motion in Problem~\ref{ex:n2l}.
-%[DM working on it xx see comment below xx]
-%DM rewrite of the following sentence - unclear as written/edited
-We extend the numerical model %with
-%numerical problems 
+We extend the numerical model  
 to include finite temperature effects
@@
   \label{ex:euler}
-  %[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK.
-Instead you might want to make this problem 1 and guide readers to write their own program.
-Then mention that a program is available, which you only mention in the abstract xx]
-  To calculate the position of the particle
-  %DM add
-  as a function of time
-  %DM end
+
+  \noindent To calculate the position of the particle
+  as a function of time,
   we
-  numerically integrate the equation of motion
-  %DM add
-  (Eq.~\ref{eq:motion})
-  %DM end
+  numerically integrate the equation of motion,
+  Eq.~(\ref{eq:motion}),
   using
@@
   Euler method.
-  %DM substituted direct reference for ``The equation of motion...''
-  Eq.~\ref{eq:motion} provides
+  Equation~(\ref{eq:motion}) provides
   a direct calculation for the particle velocity
@@
     A working example of this code is available
-  in Ref.~\cite{supplemental}
-  If you would like to write your own,
+  in Ref.~\onlinecite{supplemental}.
+  If you would like to write your own code,
   the following guide
   will walk you through our choices.
-  In the code excerpts below,
+  In the code excerpts,
   most comments and optional details are removed for clarity.
-    %The molecular dynamics
-  %described above
-  %is available in Ref.~\cite{supplemental}
-  We use the Python programming
+We use the Python 
   language
   for educational purposes.
-  To model additional particles,
-  the authors recommend a more traditional 
-  compiled coding language
+  To model many particles,
+we recommend a   
+  compiled  language
   to perform the many operations associated
@@
     to subroutines.
-    We have left as an exercise to the reader the addition
+    We have left as an exercise  the addition
     of the remaining parameters of the system.
@@
     ```set simulation parameters...'''
-
     #declare the dictionary     
     dict={}  
-    dict[`dt'] = 0.1 #timestep in simulation units
+    dict[`dt'] = 0.1 #time step in simulation units
     #control the oscillating component of driving force
@@
     dict[`freq'] = 0.01 #frequency of force oscillation
-    #left as an exercise to the reader
-    #...
+    #...                #left as an exercise to the reader
     return dict
-
     \end{verbatim}
@@
     containing the MD algorithm.
-
      \begin{verbatim}
@@
         single_particle(parameters)
-
 \end{verbatim}
@@
      $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
-     The solution is calculated algorithmically
+     The solution is calculated 
      by stepping in time through $n$ integer steps
@@
      $y_{n+1} = y_n + f(t_n,y_n)$.
-     Apply the Euler method to %our equation of motion
-     Eq.~\ref{eq:motion}
-     [DM - resolved xx refer to specific equation by label xx]
+     Apply the Euler method to 
+     Eq.~(\ref{eq:motion})
      to determine  the analytic expression
      for the position of a particle
-     $y_n$ at the $nth$ time step.
-
-     Add a $for$ loop
-     to step through each integer timestep.
-     With this loop, 
-     control
+     $y_n$ at the $n$th time step.
+
+ \qquad Add a {\tt for} loop
+     to step through each integer time step.
+     This loop 
+     controls
      the flow of the program
-     and retain information for the particle position and other
+     and retains information for the particle position and other
      properties
@@
      Assume this information
-     will be calculated a subroutine.
-
-     We used the subroutine {\bf single\_particle()}
-     calculate the array lengths to hold
+     will be calculated in a subroutine.
+
+\qquad We used the subroutine {\bf single\_particle()}
+     to calculate the  lengths of the arrays that contain the 
      position, velocity, and time data.
-     The lengths of these arrays will be affected by
-     how much data you choice to save
+     The lengths of these arrays are  affected by
+     how much data you choose to save
      (see comment following sample code).
@@
      calculate the particle position and velocity through each
-     molecular dynamics time step,
+       time step,
      calculated in the subroutine {\bf md\_step()}
      which will be described in more detail in (c).
-
 \begin{verbatim}
@@
     #(left as an exercise to the reader)   
-
     #loop through the integer time steps in the simulation
@@
         time += dt
-
 \end{verbatim}
@@
      we could save all data.
-
 \begin{verbatim}
-#integer time steps
 dict[`maxtime']=int(40/dict['freq'])   #total time steps 
@@
 \end{verbatim}
-%dict['decifactor'] = 1     #decimation factor - when to average values
 
 \item[(c)] {\bf Position and force calculations.}
-  %[DM moved sentences about general numerical solution to beginning
-  %and those about time to (b)]
-  In our implementation,
-  we created a subroutine to consider each
+  We created a subroutine to consider each
   type of force in the system (external drive, landscape, etc).
@@
   it must be returned 
-  using the definition of periodic boundary conditions
+  using the   periodic boundary conditions discussed
   in Sec.~\ref{sec:MD}.
-
 \begin{verbatim}
@@
     ```Calculate net force and integrate eq. of motion...'''
-
     #calculate the floating point value for time
     time = int_time * dt
-
-    #reset vy for every timestep since ay = 0 
+    #reset vy for every time step because ay = 0 
     vy = 0 
-
     #calculate the net force on the particle
     vy = #(left as an exercise to the reader)
-
     #calculate the new position
     y += #(left as an exercise to the reader)
-
     #check periodic boundary conditions
     #(left as an exercise to the reader)
-
     return y, vy, avg_vy
-
 \end{verbatim}
-
-%  \item[(d)]
 
@@
   many interacting particles,
-  a small
+  a smaller
   time step is essential for accurate results.
@@
 
-\noindent A range of oscillation behaviors
+\noindent A range of  behaviors
 can be explored by varying the
@@
   backward hops,
-  the driving parameters must have
-  a ratio of $F_{\rm ac}/F_{\rm dc} > 1$ 
-  and a difference $|F_{\rm ac} - F_{\rm dc}| > A_p$.
-  Holding all other parameters fixed,
+  the  ratio of $F_{\rm ac}/F_{\rm dc}$ must be greater that one  
+  and the difference $|F_{\rm ac} - F_{\rm dc}| > A_p$.
+  Hold all other parameters fixed and %DM modified typo ``Holdall''
   explore how the hopping pattern
@@
   calculate the patterns of hops for  
-  fixed parameters 
   $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$
   and
-  modified parameter
   $F_{\rm ac} = 0.2, 0.3$ and $0.4$.
-
-  %In Ref.~\onlinecite{Juniper2015}
-  %experiments with single colloids 
-  %produce 
-  %the following
-  %combinations of forward and backward steps
-  %by sweeping through
-  %a variety of applied forces parameters $F_{\rm dc}$ and $F_{\rm ac}$:
-  %$n_f = 0$ to $6$ for $n_b = 0$,
-  %$n_f = 0$ to $5$ for $n_b = -1$,
-  %and
-  %$n_f = 2$ to $3$ for $n_b = -2$.
-  %In Fig.~\ref{fig:5_Fac_y_vs_time}
-  %we fix $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$,
-  %and increase
-  %the amplitude of $F_{\rm ac}$.
-  %This increase causes the number of backward steps to increase.
-  %The number of forward steps also increases
-  %due to the increased total positive amplitude of $F_{\rm d}(t)$.
-  %In Fig.~\ref{fig:5_Fac_y_vs_time}(a) 
-  %$F_{\rm ac} = 0.2$ %, $0.3$ and $0.4$.
-  %the number of backward steps
-  %$n_b = 0$ with $n_f = 4$.
-  %In Fig.~\ref{fig:5_Fac_y_vs_time}(b) $F_{\rm ac} = 0.4$
-  %$n_b = 2$ and $n_f = 6$.
-  %In each case the average velocity 
-  %is $\langle v_y \rangle = 4\lambda f$,
-  %which can be reproduced over a variety of $F_{\rm ac}$ values.
-  %[xx what is the question? leave something to the reader! xx]
-
-  %----------------------------------------------------------
-  %\begin{figure} %[h!]
-  %    \centering
-  %    \includegraphics[width=\columnwidth]{{fig5_Fac_y_vs_time}.pdf}
-  %    \caption{
-%The motion of a particle with the same values of $F_{\rm dc}$ and frequency as in Fig.~\ref{fig:2_Fd_vy_time} and  $F_{\rm ac}$ equal to
-%        (a) $0.2$ and
-%        (b) $0.4$.
-%      }
-%      \label{fig:5_Fac_y_vs_time}
-%    \end{figure}
 
@@
   ($f = 0.005$).
-  %Figure~\ref{fig:6_freq}
-  %shows the effects of increasing the frequency
-  %of the applied driving force.
-  %The remaining parameters are fixed at
-  %$F_{\rm dc}=0.1$, $F_{\rm ac}=0.05$, and $A_p = 0.1$.
-  %We observe no backward steps 
-  %($n_b = 0$) 
-  %across a broad range of frequencies
-  %because $F_{\rm dc} - F_{\rm ac}= 0.0$.
-  %The rate of forward hops 
-  %increases as frequency decreases,
-  %but in each case the particle
-  %hops across at most one substrate periods as in Fig.~\ref{fig:2_Fd_vy_time}.
-  %In Fig.~\ref{fig:6_freq}(a)
-  %the high frequency $f=0.05$ suppresses forward motion entirely.
-  %The high frequency 
-  %is apparent in the undulations of the particle
-  %with a period of $20\,\tau$.
-  %  
-  %In Fig.~\ref{fig:6_freq}(b) the frequency $f= 0.022$
-  %with a period of $45\,\tau$
-  %arrests the particle between minima,
-  %with a hopping rate of seven periods ($320\,\tau$).
-  %At an intermediate frequency 
-  %such as $f=0.01$,
-  %the particles are synchronized so that 
-  %the hopping rate matches the driving frequency,
-  %as in Fig.~\ref{fig:2_Fd_vy_time}.
-  %In Fig.~\ref{fig:6_freq}(c) $f=0.005$
-  %the particle hops forward two minima for every period of $200\,\tau$.
-  %Low frequencies
-  %result in a sustained positive motion of a particle.
-  %In Fig.~\ref{fig:6_freq}(e) $f=0.001$
-  %the hopping is continuous
-  %over the time $100\,\tau < t < 400\,\tau$,
-  %with the cycle repeating 
-  %over the period length $1000\,\tau$.
-  %[xx same comment. too much information xx]
-  %
-  %\begin{figure} %[h!]
-  %  \centering
-  %  \includegraphics[width=\columnwidth]{{fig6_freq}.pdf}
-  %  \caption{
-  %    Motion of a particle with the same values of $F_{\rm dc} = 0.07$ and $F_{\rm ac} = 0.07$ as Fig.~\ref{fig:2_Fd_vy_time} and  frequency $f$ equal to (a) $0.05$, 
-  %      (b) $0.022$, (c) $0.005$ and (d) $0.001$. 
-  %  }
-  %  \label{fig:6_freq}
-  %\end{figure}
-  %
-  %
-\item[(c)] Explore the effect of increasing increasing $F_{\rm ac}$ on the step pattern in Fig.~\ref{fig:3_sweep_vyFDC}.
-  For example sweep the driving force $F_{\rm dc}$
+
+\item[(c)] Explore the effect of increasing  $F_{\rm ac}$ on the step pattern in Fig.~\ref{fig:3_sweep_vyFDC}.
+  For example, sweep the driving force $F_{\rm dc}$
   over increments of $\Delta F_{\rm dc} = 0.001$
-  for a fixed amplitude $F_{\rm ac}$ and frequency $f=0.01$.
+  for    $F_{\rm ac}$ and frequency $f=0.01$.
   Appropriate values for 
-  $F_{\rm ac}=0.1 - 0.4$
+  $F_{\rm ac}$ in the range $[0.1, 0.4]$
   will demonstrate a change in the step width
-  in a plot of $\langle v_y \rangle$ vs $F_{\rm dc}$
-
-  %In Fig.~\ref{fig:7_sweep2_vyFDC}
-  %we sweep the constant driving force $F_{\rm dc}$
-  %for a fixed amplitude $F_{\rm ac}$ and frequency $f=0.01$.
-  %In the high frequency limit,
-  %the regions of phase locking
-  %are separated by regions of $F_{\rm dc}$
-  %that do not phase lock,
-  %and appear to increase linearly with increasing $F_{\rm dc}$.
-  %The width of the phase locked steps
-  %grows with increasing $F_{\rm ac}$,
-  %because 
-  %the particle may move backward
-  %over a broader range of $F_{\rm dc}$.
-  %
-  %\begin{figure} %[h!]
-  %  \centering
-  %  \includegraphics[width=\columnwidth]{{fig7_sweep2_vyFDC}.pdf}
-  %    \caption{
-  %      $\langle v_y \rangle$ versus $F_{\rm dc}$ of a particle with
-  %      $F_{\rm ac}=0.1$ (blue), $F_{\rm ac}=0.2$ (orange),
-  %      $F_{\rm ac}=0.3$ (green) and $F_{\rm ac}=0.4$ (red)
-  %      with frequency $f=0.01$.
-  %      The substrate is as in Fig.~\ref{fig:2_Fd_vy_time}
-  %      with $A_p = 0.1$.
-  %    }
-  %    \label{fig:7_sweep2_vyFDC}
-  %  \end{figure}
+  in a plot of $\langle v_y \rangle$ versus $F_{\rm dc}$.
+
   \end{enumerate}
@@
 \noindent Stokes' law describes the drag force
-  $\vec{F}_{lin} = -3 \pi \eta D \vec{v}$ 
+  $\vec{F}_{\rm lin} = -3 \pi \eta D \vec{v}$ 
   on a sphere
@@
   modeled as a polynomial series\cite{Taylor2005}
-  \begin{equation}
-    \vec{F}_{\rm drag} = -b \vec{v} - c v^2 \hat{v} + \cdots  .
-  \end{equation}
-  Truncating the series to the first term
+$\vec{F}_{\rm drag} = -b \vec{v} - c v^2 \hat{v} + \cdots\,.$
+Truncating the series at the first term
   is justified by demonstrating the sphere
@@
 
- %DM moved to end of paragraph
-%To first order the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
 Use reasonable values for the
@@
 In addition to the values listed in Table~\ref{tab:1},
-to first order
-the viscosity is $\eta \sim 10^{-3}$\,Pa-s.\cite{Volpe2013}
+the viscosity is $\eta \sim 10^{-3}$\,Pa-s,\cite{Volpe2013}
 and 
 the liquid density 
-$\rho \sim 10^3$ kg/cm$^3$.\cite{asce}
-%DM removed
-%is a reasonable
-%first order approximation
+$\rho \sim 10^3$\,kg/cm$^3$.\cite{asce}
+
 \end{problem}
@@
 \noindent Newton's second law states that
-  the acceleration of a particle $i$
+  the acceleration of a particle 
   is proportional to 
-  the sum of the forces on the particle 
-  \begin{equation}
-  m \vec{a} = \sum \vec{F},
-  \label{eq:n2l}
-  \end{equation}
+  the sum of the forces on the particle, $m \vec{a} = \sum \vec{F}$,
   where $m$ is the
@@
   The ratio of $m/\gamma$ is 
-  known as the momentum relaxation time,
+ the momentum relaxation time,
   and is small for
@@
   $F_\ell(\vec{r})$ subject to a time dependent drive $F_{\rm d}(t)$
-  can be modeled by the equation of motion described in 
+  can be modeled by the equation of motion  in 
   Eq.~\eqref{eq:motion}.
@@
 
-\noindent Brownian motion is a phenomena in which 
-  visible particles change direction,
-  apparently at random, 
+\noindent Brownian motion describes the apparent random motion     of 
+  visible particles  
   due to collisions with invisible fluid particles.
@@
   An optically trapped colloid executing Brownian motion
-  is a useful probe of microscopic forces.~\cite{Volpe2013}
-
-  In molecular dynamics simulations
+  is a useful probe of microscopic forces.\cite{Volpe2013}
+
+  In   simulations
   it is common to treat the 
   invisible fluid particles as a continuous fluid
-  to reduce computational expense.
+  to reduce the computational expense.
   Temperature effects
-  can be modeled by applying randomized forces $f_T$
+  can be modeled by applying randomized forces $f_T$,
+  where $T$ denotes temperature, 
+  %[DM -addressed xx what does the subscript $T$ mean? xx]
   to the visible particles.
@@
   to generate a series of ${f_T}_n$ values for
-  each integer time step $n$.\cite{numpy}
+  each  time step $n$.\cite{numpy}
   A normalized random distribution of forces
-  causes fluctuations in 
+  causes fluctuations in the
   motion 
@@
   is zero.  In one dimension we have 
-  \begin{equation}
-    \langle f_T(t) \rangle = \frac{1}{N} \sum_n^N {f_T}_n = 0,
-  \end{equation}
-  where the integer $n$ indicates the number an  
-   simulation time steps and 
+$
+    \langle f_T(t) \rangle = \frac{1}{N} \sum_n^N {f_T}_n = 0$,
+  where the integer $n$ indicates the number of  
+    time steps and 
   $t = N \Delta t$.
   A particle
-  with sufficient energy $k_b T_{\min}$ may 
+  with sufficient energy $k_B T_{\min}$ may 
   hop over landscape
@@
   In our simulations,
-  we let temperature as 
-  $k_b T/E_0 \rightarrow T$
-  with constants set to unity
+  we let   
+  $k_B T/E_0 \rightarrow T$,
+  with the constants set to unity
   to
-  compare directly with force.
-
-  For no applied driving force,
+  compare directly with the force.
+
+  For zero applied driving force,
   find 
@@
   to hop over the maxima in the potential landscape.
-  Assume the particle is confined to
-  move along the $y$-direction,
-  include Brownian motion 
-  in the model.
+  Assume that the particle is confined to
+  move along the $y$-direction and
+  include Brownian motion.
   Appropriate temperatures to explore
   are $3.0 < T/A_p = 7.0$.
-  %DM moved position out of math mode
-  Plot the $y-$ position versus time
+Plot the $y$ position versus time
   for this particle.
-  %----------------------------------------------------
-  %  \begin{figure} %[h!]
-  %    \centering
-  %    \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
-  %    \caption{
-   %     Motion of a particle undergoing Brownian motion
-   %     on a washboard potential
-   %     energy landscape.
-   %     (a) $T/A_p = 3.0$ no hopping occurs.
-   %     (b) $T/A_p = 3.5$ one hop occurs and 
-   %     (c) $T/A_p = 4.0$ many hops occur.
-   %     Note the scale of the $y$-axis differs in each panel
-   %     and the time scale is
-   %     greater than in Fig.~\ref{fig:2_Fd_vy_time}.
-   %     The precise timing of the hop pattern varies,
-%sometimes exhibiting several hops for $T/A_p = 3.5$. 
-%      }
-%      \label{fig:8_brownian}
-%    \end{figure}
-%  
-%  In Fig.~\ref{fig:8_brownian}
-%  we show the position versus time of a particle
-%  confined to a sinusoidal landscape
-%  undergoing Brownian motion.
- % We increase the temperature relative
- % to the amplitude of the landscape
- % troughs until the particle enters a hopping regime.
- % In  Fig.~\ref{fig:8_brownian}(a)
- % the temperature is $T/A_p = 3.0$.
- % The particle executes a 
- % random walk centered at the potential minima $y/\lambda = 10$.
- % We ran many simulations and never observed a hop to another minima
- % within this simulation time.  
- % In  Fig.~\ref{fig:8_brownian}(b)
- % $T/A_p = 3.5$,  hops between
- % potential minima are possible but not probable,
- % a hop occurs from
- % $y/\lambda = 10$ to $9$ at
- % $t \sim 23000 \tau$. 
- % In other simulations with identical parameters,
- % we sometimes observed no hops or two hops between minima,
- % as expected with random fluctuating systems.
- % In  Fig.~\ref{fig:8_brownian}(c)
- % $T/A_p = 4.0$ 
- % we observe many hops.
- % The random thermalized kicks are
- % sufficiently large to make the particle perform
- % what appears to be 
- % a random walk of hops atop the substrate. %[xx what is the question? xx]
-
-  %{\it Comment: }
+
   For a driven particle,
@@
   in these simulations.  
-  We note that even for $T/A_p = 6.0$ 
+  We note that even for $T/A_p = 6.0$, 
   the hopping rate
   is much less than the
-  frequency of the applied drive. %, as
-  %can be seen in the time scale in Fig.~\ref{fig:8_brownian},
-  % where the average hopping rate is approximately
-  % every $4000\tau$,
-  % a value much larger than the period of the driving force.  
+  frequency of the applied drive.   
   At sufficiently high temperatures,
@@
 \begin{acknowledgments}
-
-  %[xx AJP doesn't allow acknowledgments to the editors, but you are welcome xx] 
 Charles and Cynthia Reichhardt
@@
   provided the original molecular dynamics code
-  written in the C programming language.
+  written in  C.
   We acknowledge funding from the M.J.\ Murdock Charitable Trust
-  and the Pacific Research Institute for Science and Mathematics. % (PRISM).
+  and the Pacific Research Institute for Science and Mathematics.
 
@@
 
-%%[xx AJP requires last page numbers for papers xx] 
 \begin{thebibliography}{99}
@@
 
-\bibitem{Arane2009} T. Arane, A. K. R. Musalem and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--1067 (2009). %; https://doi.org/10.1119/1.3119175
+\bibitem{Arane2009} T. Arane, A. K. R. Musalem, and M. Fridman, ``Coupling between two singing wineglasses," Am. J. Phys. {\bf 77}, 1066--1067 (2009). %; https://doi.org/10.1119/1.3119175
 
@@
 M.
-Wilson and J.
+Wilson, and J.
 R.
@@
 
-  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, ``Keeping the beat: A Large sample study of bouncing and clapping to music," PLoS ONE 11(7): e0160178. (2016).
+  \bibitem{Tranchant2016} P. Tranchant, D. T. Vuvan, and I. Peretz, ``Keeping the beat: A Large sample study of bouncing and clapping to music," PLoS ONE 11(7): e0160178 (2016).
 
@@
 
-  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563–579 (2002).
+  \bibitem{Bennett2002} M. Bennett, M. F. Schatz, H. Rockwood, and K. Wiesenfeld, ``Huygens' clocks," Proc. Roy. Soc. A {\bf 458}, 563--579 (2002).
 
@@
 Commun.
-6, 7187--7194 (2015);
+6, 7187--7194 (2015).
       %\bibitem{Juniper2018}
@@
 Phys.
-{\bf 80}, 026501 (2017).
+{\bf 80}, 026501-1--64 (2017).
+%[I don't know what you mean.
+64?
+xx \# of pages?
+xx - https://iopscience.iop.org/article/10.1088/1361-6633/80/2/026501/meta]
 
@@
 
-    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.. ``Array programming with NumPy,"  Nature {\bf 585}, 357--362 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
+    \bibitem{numpy} C. R. Harris, K. J. Millman, S. J. van der Walt et al.,  ``Array programming with NumPy,"  Nature {\bf 585}, 357--362 (2020). %DOI: 0.1038/s41586-020-2649-2. (Publisher link).
 

### 2021-04-12 manuscript/manuscript_ajp_version3.tex
rejiggered the introduction following, main topic, define, illustrate, transition

@@
 synchronization --
-birds  coordinate their wing flaps
+birds  coordinate wing flaps
 to optimize energy use during flight,\cite{Portugal2014}
@@
 and brain tissue.\cite{Singer1999}
-%DM ended paragraph with fewer examples, added transition sentence
-Mechanisms of synchronization
-can be WHAT
-
+%DM ended paragraph with fewer examples, 
+%Environmental conditions
+%DM add add transition sentence
+%
+External forcing
+can cause or regulate synchronization.
+%where external forces
+%add or remove energy from the system.
+For example, 
+an electrical pacemaker 
+regulates a heart beat and
+a pulsed light modifies the
+flashing pattern of fireflies.
+
+The model discussed in this paper
+resembles an externally forced pendulum.
+%damping
+%transition
+%%DM - focus more on single particle with environment
+A single pendulum 
+may swing in time with an %be driven or damped by
+driving force
+like  %a skateboarder in a half-pipe or
+a pushed child on a swing,
+and may be damped
+by mechanical friction.
+%of gravity to return
+%to an equilibrium position,
+%or  to decreasing amplitude
+% or air resistance.
 Synchronized phase-locking or mode-locking 
@@
 pendula in wall-mounted clocks.\cite{Bennett2002}
+Clock pendula swing in phase
+when coupled through shared vibrations.
 A locked-mode is an integer frequency ratio.
@@
 %DM transition sentence
-Simulations and laboratory experiments
-of mode-locked synchronization
-can help provide insights to a diverse range of 
+Many subsequent 
+simulations and laboratory experiments
+have revealed 
+mode-locked synchronization
+in a diverse range of 
 oscillation phenomena.
 
-%DM better main topic
-Experiments with colloids
-
-Complex dynamics such as synchronized mode-locking
-can be studied with
-colloid particles.
+%Single oscillators 
+%can demonstrate a variety of synchronized behaviors.
+Colloid particles in complex environments are an excellent
+model system to explore %these 
+the dynamics of mode-locking. %synchronization.
 In experiments %DM moved the ``in experiments'' to second sentence
@@
 de-ionized water or silica beads suspended in organic solvent.
-Because 
-colloids are large 
-and move slowly, the
-particle positions 
-can be measured in real time 
-with an optical camera.\cite{Pertsinidis2001}
-Experimental measurements of the
-step-by-step dynamics of 
-colloids performing phase-locked motions
-are useful for
-understanding synchronization
-at a single particle level.\cite{Juniper2015,Juniper2017}
-
-Light is a
-tool for manipulating the colloidal environment
-to alter synchronization patterns.
 Colloids can be trapped
@@
 a laser beam.\cite{Ashkin1997} 
+A colloid in such a confining region,
+an optical trap, oscillates
+about a equilibrium point.
 A colloid centered in an optical trap is 
@@
 or ejects it from the trap.
+
+% such as synchronized mode-locking can be studied with
+%An advantage of colloid studies
+While many systems oscillate,
+trapped colloids are useful for 
+providing controlled 
+measurements of the
+step-by-step dynamics of particle motion.
+Colloids are large 
+and move slowly so
+%colloids are considered model systems
+particle positions 
+can be measured in real time 
+with an optical camera.\cite{Pertsinidis2001}
+Colloids have been
+shown to 
+provide an ideal system to 
+control and study
+phase-locked motions
+%are useful for
+%understanding synchronization
+at a single particle level.\cite{Juniper2015,Juniper2017}
+%Light is a
+%tool for manipulating the colloidal environment,
+%which can alter synchronization patterns.
+%Synchronization patterns can be altered
+%using light to manipulate
+%the colloidal environment.
 Diffraction gratings can create
@@
 suitable for synchronization studies.\cite{Grier2003}
-
-%new topic - DM this sentence appeared toward the end of the intro
-The model discussed in this paper
-resembles a damped driven pendulum 
-where external forces
-add or remove energy from the system.
-A single pendulum is driven by
-the external force of gravity to return
-to an equilibrium position,
-and may be damped to decreasing amplitude
-by mechanical friction or air resistance.
-Multiple pendula may swing in phase
-when coupled through shared vibrations.
-
-External forcing
-can cause or regulate synchronization.
-For example, 
-an electrical pacemaker 
-regulates a heart beat 
-and 
-a pulsed light modifies the
-flashing pattern of fireflies. 
-%damping
-%transition
-
-A single particle oscillator
-in a potential well is 
-like a skateboarder in a half-pipe or
-a child on a swing.
-A confined oscillator may 
+In the following study,
+we assume the colloids are confined
+to move along a periodic light pattern
+with minima and maxima defined by a sine wave.
+
+A colloid driven across a periodic
+substrate may 
 synchronize its location
-to the periodic pattern of the external drive,
-moving back and forth in time with
-the beat,
-or moving between substrate minima.
+to the pattern of the external drive.
+%moving back and forth in time with
+%the beat, or
+%moving between substrate minima.
 When 
@@
 Above the pinning threshold,
-a particle subject to a constant
-drive force  increases its speed at a rate proportional
+a dc driven particle
+%a particle subject to a constant
+%drive force
+increases its speed at a rate proportional
 to the external drive.  
 When the applied force varies periodically,
-the ac drive can 
-cause the particle to hop back and forth across
+an ac drive,
+%cause
+the particle can hop back and forth across
 the landscape minima.
 Many synchronized patterns occur,
-controlled by the substrate period,
-leading to 
-mode-locking,
-where the average particle velocity
+controlled by the substrate pattern and driving force.
+When a particle is driven by combined 
+ac and dc forces,
+mode-locking appears 
+where 
+the average particle velocity
+%of an  driven particle 
 is fixed for a range of dc drive forces.\cite{Reichhardt2015}
@@
 In this paper we discuss numerical simulations 
-of the synchronized dynamics
+of the mode-locked dynamics
 of a confined particle driven over
 a washboard shaped potential energy landscape.
-We describe
-our   model  in Sec.~\ref{sec:MD}.
-The model
-is easy to simulate yet relevant
-to condensed matter systems.
-We summarize our results 
-including the synchronized motion of a single confined particle
-driven across a periodic landscape in 
+The numerical model is presented in Sec.~\ref{sec:MD} and 
+our results are summarized in
+%including the synchronized motion of a single confined particle
+%driven across a periodic landscape in 
 Sec.~\ref{sec:results}. In Sec.~\ref{sec:conclusion}
-we describe how our results apply 
-to physical systems,
-such as optically trapped colloids
-and superconducting vortices in the presence of periodic pinning arrays.
+we relate  our results 
+to a broad variety of physical systems beyond 
+optically trapped colloids.
+%and superconducting vortices in the presence of periodic pinning arrays.
 We include problems for interested readers 
@@
 periodic optical landscape.
+The model
+is easy to simulate yet relevant
+to a broad range of condensed matter systems.
 Colloids are 

### 2021-04-12 manuscript/manuscript_ajp_version3.tex
rejiggered the introduction following, main topic, define, illustrate, transition

@@
 or ejects it from the trap.
-
-% such as synchronized mode-locking can be studied with
-%An advantage of colloid studies
-While many systems oscillate,
-trapped colloids are useful for 
-providing controlled 
-measurements of the
-step-by-step dynamics of particle motion.
-Colloids are large 
-and move slowly so
-%colloids are considered model systems
-particle positions 
-can be measured in real time 
-with an optical camera.\cite{Pertsinidis2001}
+Diffraction gratings can create
+more complex light environments, 
+such as periodic patterns of minima
+suitable for synchronization studies.\cite{Grier2003}
+A driven colloid
+can demonstrate
+synchronized
+motion within one trap,
+or synchronized hopping between multiple traps.
+
 Colloids have been
@@
 at a single particle level.\cite{Juniper2015,Juniper2017}
+% such as synchronized mode-locking can be studied with
+%An advantage of colloid studies
+While many systems oscillate,
+trapped colloids are useful for 
+providing controlled 
+measurements of the
+step-by-step dynamics of particle motion.
+Since
+colloids are large 
+and move slowly, 
+%colloids are considered model systems
+particle positions 
+can be measured in real time 
+with an optical camera.\cite{Pertsinidis2001}
 %Light is a
@@
 %the colloidal environment.
-Diffraction gratings can create
-more complex light environments, 
-such as periodic patterns of minima
-suitable for synchronization studies.\cite{Grier2003}
+Simulations provide complementary
+information,
+where environmental and driving parameters may be precisely
+and quickly modified to explore
+the many oscillation patterns.
+%the dynamics from external
 In the following study,
-we assume the colloids are confined
+we confine colloids  
 to move along a periodic light pattern
-with minima and maxima defined by a sine wave.
+with minima and maxima defined by a sine wave,
+a washboard potential energy substrate.
 

### 2021-04-13 manuscript/manuscript_ajp_version3.tex
fixed intro - todo conclusion

@@
 \begin{abstract}
-  We discuss a 
+  Synchronization
+  plays an important role in many physical processes.
+  We discuss synchronization in a 
   molecular dynamics simulation
@@
   %put those ideas in this final sentence, making it a mouthful [26 words]
-  Isolating
+  By 
+  isolating
   synchronized motion
@@
   simulations and table-top experiments,
-  can be used to study %DM replaced isolate with study
+  we 
+  can study %DM replaced isolate with study
   complex natural behaviors
-  which
-  play an important role in many physical processes.
+  important to many physical processes.
  %[suggest omitting this sentence. Code not in text. We include molecular dynamics code
@@
 and metronomes vibrating through a supporting platform\cite{Jia2015}
-are examples of in-phase coupled oscillations. 
+are examples of in-phase environmentally coupled oscillations. 
 Biological systems benefit from cooperative
@@
 A single pendulum 
-may swing in time with an %be driven or damped by
+can swing in time with an %be driven or damped by
 driving force
@@
 % or air resistance.
-Synchronized phase-locking or mode-locking 
+We focus on 
+synchronized phase-locking or mode-locking,
+which 
 first appeared in the scientific literature
@@
 Huygens'  experiments on the
-motions of synchronized 
+motions of %synchronized 
 pendula in wall-mounted clocks.\cite{Bennett2002}
-Clock pendula swing in phase
-when coupled through shared vibrations.
-A locked-mode is an integer frequency ratio.
-In Huygens clocks,
-the pendula were observed to swing at the same rate
+A locked-mode is an integer frequency ratio
+in coupled oscillators. %Clock pendula swing in phase
+%when coupled through shared vibrations.
+In Huygens' clocks,
+the mode-locked pendula were observed to swing at the same rate
 in the same direction (1:1 mode) or
 opposite directions ($-1$:1 mode).
-A 2:1 mode occurs when a simple pendulum four
-times the length of another swings with twice the period.
+Higher modes might be achieved
+by altering the pendula lengths - 
+a 2:1 mode occurs when a simple pendulum
+swings with twice the period
+of another one quarter the length.
 %DM transition sentence
-Many subsequent 
-simulations and laboratory experiments
+%Many subsequent 
+Simulations and laboratory experiments
 have revealed 
@@
 suitable for synchronization studies.\cite{Grier2003}
-A driven colloid
-can demonstrate
-synchronized
-motion within one trap,
-or synchronized hopping between multiple traps.
 
@@
 %An advantage of colloid studies
+A driven colloid
+can demonstrate
+synchronized
+motion within one trap,
+or synchronized hopping between multiple traps. 
 While many systems oscillate,
@@
 the landscape minima.
-Many synchronized patterns occur,
-controlled by the substrate pattern and driving force.
-When a particle is driven by combined 
+When a particle is driven across a substrate
+by combined 
 ac and dc forces,
-mode-locking appears 
-where 
-the average particle velocity
+it is possible for the particle to demonstrate 
+mode-locking.
+In these modes,  
+%Due to the combination of external drive
+%and substrate minima,
+the particle hops at a controlled rate such that 
+the average particle velocity is 
 %of an  driven particle 
-is fixed for a range of dc drive forces.\cite{Reichhardt2015}
+fixed for a range of dc drive forces
+with a magnitude proportional to the
+landscape period and driving frequency.\cite{Reichhardt2015}
+%Many synchronized patterns occur,
+%controlled by the substrate pattern and driving force.
 
@@
 its trajectory.
-The particle is confined in a two-dimensional 
-simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
-and $a_0$ is a dimensionless unit of length. (In the simulations we   set $a_0 = 1$.)
+The particle is confined in a one-dimensional %DM reduced to 1D
+simulation of length $L=46.\bar{6}\,a_0$, %DM 1D
+where $a_0$ is a dimensionless unit of length.
+(In the simulations we set $a_0 = 1$.)
 The particle 
 has
-position $\vec{r} = x \hat{x} + y \hat{y}$
+position $\vec{r} = y \hat{y}$ %DM 1D
 and velocity $\vec{v} = d\vec{r}/dt$.
@@
 back to a position within the simulation boundaries 
-by the transformation $x+L \rightarrow x$ and $y+L \rightarrow y$.
+by the transformation $y+L \rightarrow y$. %DM 1D
 We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
@@
 \label{sec:conclusion}
-A single particle driven across a periodic potential landscape 
-synchronizes its motion 
-to environmental and external forces.  
+
 Our simulations reproduce the experiments and simulations presented in 
@@
 periodic optical landscape.
-The model
-is easy to simulate yet relevant
-to a broad range of condensed matter systems.
+A single particle driven across a periodic potential landscape 
+synchronizes its motion 
+to environmental and external forces. 
+%The model
+%is easy to simulate yet relevant
+%to a broad range of condensed matter systems.
+Our results are relevant 
+to synchronization effects
+in a broad range of experimental systems
+including optically confined colloids,
+superconductors with periodic pinning arrays, 
+and the charge and spin of atomic systems.
+
 Colloids are 
@@
 such as cold atoms or electron gases.\cite{Grier2003}
+%DM FIX FOLLOWING SENTENCE
 Dynamical mode-locking 
@@
 engineered with periodic patterns of pinning sites.\cite{Reichhardt2000}
-
 Mode-locking is a useful probe 
@@
 from other measurements.
-Our results are relevant 
-to synchronization effects
-in a broad range of experimental systems
-including optically confined colloids,
-superconductors with periodic pinning arrays, 
-and the charge and spin of atomic systems.
+%insert final sentence summarizing all the things.
 

### 2021-04-23 code/MD_colloid.py
removed y subscript from fig4

@@ -346,10 +346,11 @@ def plot_phase(ax,y_data,avg_vy_data,p):
         #non-driven phase variables
         ax.scatter(y_data[plot_delay:],avg_vy_data[plot_delay:]) #,lw=5)
 
-    ax.set_xlabel(r"$\phi_y(t) / (2\pi)$")
-    ax.set_ylabel(r"$\dot{\phi}_y(t) / (2\pi)$")
+    ax.set_xlabel(r"$\phi(t) / (2\pi)$")
+    ax.set_ylabel(r"$\dot{\phi}(t) / (2\pi)$")
 
-    ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
+    if 1:
+        ax.set_ylim(-0.04,0.1) #time_data[-1]+1)
     
     return 
 
@@ -600,7 +601,7 @@ if __name__ == "__main__":
 
             #should be as in Fig. 2
             parameters['F_AC'] = 0.07 
-            parameters['freq'] = 0.01
+            parameters['freq'] = 0.01 # 0.01
             parameters['AP'] = 0.1
 
             fig = plt.figure(figsize=(8,8*1.2))

### 2021-04-23 manuscript/manuscript_ajp_version3.tex
revisions to text, fig 4

@@
 oscillation phenomena.
-
 %Single oscillators 
 %can demonstrate a variety of synchronized behaviors.
-Colloid particles in complex environments are an excellent
-model system to explore %these 
-the dynamics of mode-locking. %synchronization.
-In experiments %DM moved the ``in experiments'' to second sentence
-typical colloids are   
-plastic spheres suspended in
-de-ionized water or silica beads suspended in organic solvent.
-Colloids can be trapped
-with 
-radiation pressure from 
-a laser beam.\cite{Ashkin1997} 
-A colloid in such a confining region,
-an optical trap, oscillates
-about a equilibrium point.
-A colloid centered in an optical trap is 
-uniformly bombarded by photons. 
-Off-center colloids 
-experience a net force
-due to uneven photon collisions across
-the particle surface.
-Depending on the 
-location of the particle in the trap,
-the radiation pressure either moves colloids toward the center 
-or ejects it from the trap.
-Diffraction gratings can create
-more complex light environments, 
-such as periodic patterns of minima
-suitable for synchronization studies.\cite{Grier2003}
+%Colloid particles in optical traps are an excellent
+%model system to explore %these 
+%the dynamics of mode-locking. %synchronization.
 
@@
 %An advantage of colloid studies
+In experiments %DM moved the ``in experiments'' to second sentence
+typical colloids are   
+plastic spheres suspended in
+de-ionized water or silica beads suspended in organic solvent.
+Colloids can be trapped
+with 
+radiation pressure from 
+a laser beam.\cite{Ashkin1997} 
+%A colloid in such a confining region,
+%an optical trap,
+A colloid centered in an optical trap is 
+uniformly bombarded by photons
+and oscillates
+about a equilibrium point.
+Off-center colloids 
+experience a net force
+due to uneven photon collisions across
+the particle surface.
+%Depending on the 
+%location of the particle in the trap,
+%the radiation pressure either moves colloids toward the center 
+%or ejects it from the trap.
+Diffraction gratings can be used to create
+more complex light environments, 
+such as periodic patterns of minima
+suitable for synchronization studies.\cite{Grier2003}  
 A driven colloid
@@
 we confine colloids  
-to move along a periodic light pattern
-with minima and maxima defined by a sine wave,
-a washboard potential energy substrate.
+to move along a periodic pattern
+with minima and maxima defined by a sine wave.
+%a washboard potential energy substrate.
 
@@
 
-The confining force on the particle $i$
+The confining force on the particle %$i$ DM removed
  is given by
@@
 The inertia of the 
-small particle is reduced by interactions
+%small
+particle is reduced by interactions
 with the fluid particles.\cite{Purcell1977}
@@
   \end{equation}
-For a zero landscape force, 
-  the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
+  %DM removed
+  %For a zero landscape force, 
+  %the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
 If the system
@@
   with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
+  %DM add
+  We choose values of $F_{\rm dc}$
+  corresponding to the first four modes in
+  Fig.~\ref{fig:3_sweep_vyFDC},
+  as marked with black circles.
+  %DM end add
   For
@@
 three nodes form as the particle moves across $3\lambda$.
+%DM add
+It is possible to create
+more patterns in phase diagrams are possible
+by changing the driving parameters.
+At higher values of $F_{\rm dc}$
+additional nodes appear.
+When the values of $F_{\rm ac}$ and $f$
+are tuned to produce backwards hops in the substrate,
+as suggested in Problem~\ref{ex:parameters}, 
+negative nodes appear in $\phi_y(t)$.
+%DM end add
 
@@
 
-Our simulations reproduce the experiments and simulations presented in 
+A single particle driven across a periodic potential landscape 
+can synchronize its motion 
+to environmental and external forces. 
+The simulations described above
+reproduce the experiments and simulations presented in 
 Juniper {\it et al.} \cite{Juniper2015, Juniper2017}
-of 
+of dynamical 
 mode locking in
@@
 periodic optical landscape.
-A single particle driven across a periodic potential landscape 
-synchronizes its motion 
-to environmental and external forces. 
+Further simulations can be extended
+to include multiple particles
+and more complex environments,
+leading to
+synchronization effects relevant 
+to a broad range of experimental systems.
 %The model
@@
 %to a broad range of condensed matter systems.
-Our results are relevant 
-to synchronization effects
-in a broad range of experimental systems
-including optically confined colloids,
-superconductors with periodic pinning arrays, 
-and the charge and spin of atomic systems.
-
+
+The study of motions of particles 
+sliding across periodic and aperiodic surfaces 
+is relevant 
+to a broad range of condensed matter systems.
+%beyond optically confined colloids.
 Colloids are 
@@
 for systems
+more difficult to access experimentally 
 such as cold atoms or electron gases.\cite{Grier2003}
+Many systems can be modeled
+as particles moving across a surface
+including 
+the propagation of patterns
+in charge and spin properties of atomic systems.
+%superconductors with periodic pinning arrays, and 
 %DM FIX FOLLOWING SENTENCE
@@
 is 
-observed in technologies such as 
+observed in %technologies such as 
 quantum electronic
@@
 displaying
-non-Ohmic behavior in voltage-current curves,
+non-Ohmic behavior in voltage-current curves.
+The study of 
+mode-locking in colloids provides insights
+into 
+%is a useful probe of
+complex %quantum mechanical
+systems in which 
+the motions of individual particles can  be inferred only
+from other measurements, 
+%insert final sentence summarizing all the things.
 including
@@
 engineered with periodic patterns of pinning sites.\cite{Reichhardt2000}
-Mode-locking is a useful probe 
-of complex quantum mechanical systems
-because the motions of individual particles can  be inferred only
-from other measurements.
-%insert final sentence summarizing all the things.
 
@@
   $\vec{v} = d\vec{r}/dt$ 
-  using the 
+  with the %DM sub ``with'' for using
   Euler method.
-  Equation~(\ref{eq:motion}) provides
+  %DM - fix Equation/Eq. discontinuity
+  Eq.~(\ref{eq:motion}) provides
   a direct calculation for the particle velocity
@@
     to subroutines.
-    We have left as an exercise  the addition
-    of the remaining parameters of the system.
+    %DM - more clearly defined task in active / command tense
+    %We have left as an exercise  the addition
+    Define 
+    the remaining parameters of the system using the dictionary outlined below.
     \begin{verbatim}

### 2021-05-04 manuscript/manuscript_ajp_version4b.tex
cleaned up, added ignore

--- 2021-04-23 manuscript/manuscript_ajp_version3.tex
@@
   For certain conditions,
-  the particle velocity and location
+  the particle's velocity and location
   are synchronized or 
-  phase-locked,
-  forming closed orbits in phase space.
+  phase-locked and
+  form closed orbits in phase space.
   Quasi-periodic motion is common, 
@@
 synchronization --
-birds  coordinate wing flaps
+birds  coordinate their wing flaps
 to optimize energy use during flight,\cite{Portugal2014}
@@
 and brain tissue.\cite{Singer1999}
-%DM ended paragraph with fewer examples, 
-%Environmental conditions
-%DM add add transition sentence
-%
 External forcing
@@
 
-The model discussed in this paper
+The model we discuss
+%DM add
+in this paper 
+%DM end
 resembles an externally forced pendulum.
@@
 A single pendulum 
-can swing in time with an %be driven or damped by
+can swing in time with a %be driven or damped by
 driving force
@@
 the mode-locked pendula were observed to swing at the same rate
-in the same direction (1:1 mode) or
+in the same direction (1:1 mode) or in
 opposite directions ($-1$:1 mode).
 Higher modes might be achieved
-by altering the pendula lengths - 
+by altering the pendula lengths --
 a 2:1 mode occurs when a simple pendulum
@@
 
-Colloids have been
-shown to 
+Colloids 
 provide an ideal system to 
@@
 a laser beam.\cite{Ashkin1997} 
-%A colloid in such a confining region,
-%an optical trap,
 A colloid centered in an optical trap is 
@@
 due to uneven photon collisions across
-the particle surface.
-%Depending on the 
-%location of the particle in the trap,
-%the radiation pressure either moves colloids toward the center 
-%or ejects it from the trap.
+the particle's surface.
 Diffraction gratings can be used to create
@@
 or synchronized hopping between multiple traps.
-While many systems oscillate,
+%DM moved this sentence up for better flow
+In the following simulations, we confine colloids  
+to move along a periodic pattern of 
+minima and maxima defined by a sine wave.
+
+Although many systems oscillate,
 trapped colloids are useful for 
@@
 measurements of the
-step-by-step dynamics of particle motion.
-Since
+step-by-step dynamics of the particle motion.
+Because
 colloids are large 
-and move slowly, 
-%colloids are considered model systems
-particle positions 
+and move slowly,  the positions of the
+particles
 can be measured in real time 
 with an optical camera.\cite{Pertsinidis2001}
-%Light is a
-%tool for manipulating the colloidal environment,
-%which can alter synchronization patterns.
-%Synchronization patterns can be altered
-%using light to manipulate
-%the colloidal environment.
 Simulations provide complementary
@@
 the many oscillation patterns.
-%the dynamics from external
-In the following study,
-we confine colloids  
-to move along a periodic pattern
-with minima and maxima defined by a sine wave.
-%a washboard potential energy substrate.
 
@@
 dc drive is applied,
-the particle velocity is modulated by 
+the particle's velocity is modulated by 
 the potential energy landscape exerted on the particle.   
@@
 
-In this paper we discuss numerical simulations 
+In this paper we discuss simulations 
 of the mode-locked dynamics
@@
 a washboard shaped potential energy landscape.
-The numerical model is presented in Sec.~\ref{sec:MD} and 
+The model is presented in Sec.~\ref{sec:MD} and 
 our results are summarized in
@@
 its trajectory.
-The particle is confined in a one-dimensional %DM reduced to 1D
-simulation of length $L=46.\bar{6}\,a_0$, %DM 1D
+The particle is confined in a one-dimensional 
+box of length $L=46.\bar{6}\,a_0$,
 where $a_0$ is a dimensionless unit of length.
@@
 has
-position $\vec{r} = y \hat{y}$ %DM 1D
+position $\vec{r} = y \hat{y}$ 
 and velocity $\vec{v} = d\vec{r}/dt$.
@@
 back to a position within the simulation boundaries 
-by the transformation $y+L \rightarrow y$. %DM 1D
+by the transformation $y+L \rightarrow y$. 
 We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
@@
  that sets the depth of the minima
- with simulation units of energy $E_0$. 
+ with  units of energy $E_0$. 
  We plot this function in 
@@
  to illustrate
- the 2D potential energy landscape;
- the maxima are colored gray and the minima colored white.
-
-The confining force on the particle %$i$ DM removed
+ the two-dimensional potential energy landscape;
+ the maxima are colored gray and the minima are colored white.  
+ Because the motion is one-dimensional, the particle only moves along the $y$-direction in the two-dimensional plane.
+%[xx added this sentence because the reader might be confused that you stated that the particle is confined to one dimension xx]
+
+The confining force on the particle 
 is given by
@@
 
-The equation of motion provides a direct calculation of the velocity
-of an individual particle at position $\vec{r}$ 
+The equation of motion  yields the velocity
+of a particle at position $\vec{r}$ 
 and simulation time $t$. At each time step
@@
 Problem~\ref{ex:euler}
-we describe 
-the numerical methods for 
-solving differential equations such as Eq.~\eqref{eq:euler}.
-%------------------------------------------------------------------
+we describe a program for 
+treating differential equations such as Eq.~\eqref{eq:euler}. %[xx note change xx]
+
 \begin{figure} % [h!]
@@
   The particle is 
-  subject to competing forces of the landscape and the applied driving force.
+  subject to the competing forces of the landscape and the applied driving force.
   (b) The potential energy function $U(y)$. 
@@
 \label{sec:results}
-Here we drive 
-a single particle 
-across the landscape. 
+%Here we drive 
+%a single particle 
+%across the landscape. 
 The numerical implementation of the force due to the landscape 
-is calculated using Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  
+is calculated using Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr} with
 \begin{equation}
@@
 to $A_{p} = 0.1\,F_0$ 
-with $N_p=20$ minima, 
+with $N_p=20$, 
 corresponding to a spatial period $\lambda = 2.3\,a_0$.
@@
 \caption{Simulation parameters and units with comparable
-  experimental values.~\cite{Juniper2015,Juniper2017} The substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of the particles.
-}%[DM changed to T xx what does $T_0 = 0$ mean?
-$T_0$ is never used in the paper.
-xx]  }
+  experimental values.~\cite{Juniper2015,Juniper2017} The substrate is scaled by our force units, while an experimental landscape is scaled by the Brownian motion of the particles. }
 \begin{ruledtabular}
 \begin{tabular}{c c c } 
-Quantity & Simulation Units & Experimental values\\
+Quantity & Simulation units & Experimental values\\
 \hline
@@
 we plot $F_{\rm d}(t)$ 
-as a function of time with the
-constants $F_{\rm dc}=0.07$, 
-$F_{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
+as a function of time with $F_{\rm dc}=0.07$, 
+$F_{\rm ac}=0.07$, and $f=0.01$ cycles per time unit $\tau$.
 The  temporal period of the driving force is
@@
 the particle moves across the substrate maxima.
-%shown in gray with the contour plot. said in caption
 
@@
 \caption{(a) The applied driving force $F_{\rm d}(t)$ 
-  with parameters $F_{\rm dc} = 0.07$, $F_{\rm ac} = 0.07$ and $f=0.01$.
+  with  $F_{\rm dc} = 0.07$, $F_{\rm ac} = 0.07$, and $f=0.01$.
   (b) 
-  The $y$-position of the driven particle
+  The $y$-position of the  particle
   normalized by the period of the substrate $\lambda$.
@@
  along with the contour plot depicting
-  the landscape potential described in Fig.~\ref{fig:1_landscape}(a).
+  the landscape potential shown in Fig.~\ref{fig:1_landscape}(a).
   }
@@
 To explore the possible hopping patterns,
-we sweep through a range of $F_{\rm dc}$ for fixed $F_{\rm ac}$ and $A_p$.
+we sweep through a range of values of $F_{\rm dc}$ for fixed $F_{\rm ac}$ and $A_p$.
 In Fig.~\ref{fig:3_sweep_vyFDC} 
@@
   where the power $\beta$ varies with the
-  %system type and
   type of phase transition and 
@@
   may 
-  be used to identify the universality class.\cite{Reichhardt2017} %[xx what does system type mean? xx - DM modified to phase transition]
+  be used to identify the universality class.\cite{Reichhardt2017} 
   The critical force $F_c$ is equal to the maximum substrate force
   $A_p$.
+  % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
+  %DM - in my experience, we use beta for this parameter.  For example
+  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301
 
@@
   A mode is a periodic pattern of hops
-  with a constant average particle velocity, $\langle {v}_{y} \rangle$
+  with a constant average particle velocity $\langle {v}_{y} \rangle$
   over a range of driving forces $F_{\rm dc}$.
@@
   with $F_{\rm ac} = 0.07$ and $f=0.01$.
-Each step represents a different pattern of hops
+Each value of $F_{\rm dc}$ yields a different pattern of hops
 between substrate minima
 performed by the particle
-due to the landscape confinement.  
+due to the landscape confinement.  %xx note change xx]
 At 
@@
 a 0:0 mode.
-At higher values of $F_{\rm dc}$, the particle velocity 
+At higher values of $F_{\rm dc}$,    
 $\langle v_{y} \rangle$ increases in steps of uniform height,
@@
 for this landscape potential.\cite{Reichhardt2000,Juniper2017}
-These steps, known as Shapiro steps, can have a variety of
+These steps, known as Shapiro steps, can exhibit a variety of
 interesting patterns
@@
 \includegraphics[width=\columnwidth]{fig3_sweep_vyFDC.pdf}
-\caption{Average particle velocity  $\langle v_{y} \rangle$
+\caption{The average particle velocity  $\langle v_{y} \rangle$
   as a function of $F_{\rm dc}$.
@@
   The value of $F_{\rm dc}$ for the first four steps
-  correspond to the fixed value of $F_{\rm dc}$
+  corresponds to the fixed value of $F_{\rm dc}$
   in each of the phase plots
-  in Fig.~\ref{fig:4_phase}(a-d).
+  in Figs.~\ref{fig:4_phase}(a)--(d).
 }
@@
   we plot $\dot{\phi}(t)$ versus $\phi(t)$
-  for increasing 
+  for increasing values of
   $F_{\rm dc}$, 
   with the remaining parameters fixed as in Fig.~\ref{fig:2_Fd_vy_time}.
-  %DM add
   We choose values of $F_{\rm dc}$
@@
   as marked with black circles.
-  %DM end add
   For
@@
 It is possible to create
-more patterns in phase diagrams are possible
+more patterns in phase diagrams 
 by changing the driving parameters.
@@
 When the values of $F_{\rm ac}$ and $f$
-are tuned to produce backwards hops in the substrate,
+are tuned to produce backward hops in the substrate,
 as suggested in Problem~\ref{ex:parameters}, 
@@
 
-\section{Conclusion}
+\section{Discussion} %[xx note change
 \label{sec:conclusion}
@@
 to environmental and external forces. 
-The simulations described above
-reproduce the experiments and simulations presented in 
-Juniper {\it et al.} \cite{Juniper2015, Juniper2017}
+The simulations we have described 
+reproduce the experiments and simulations 
 of dynamical 
@@
 driven colloids on a
-periodic optical landscape.
-Further simulations can be extended
+periodic optical landscape.\cite{Juniper2015, Juniper2017}
+The simulations can be extended
 to include multiple particles
@@
 
-The study of motions of particles 
+The study of the motions of particles 
 sliding across periodic and aperiodic surfaces 
@@
 in charge and spin properties of atomic systems.
-%superconductors with periodic pinning arrays, and 
-%DM FIX FOLLOWING SENTENCE
 Dynamical mode-locking 
 is 
-observed in %technologies such as 
+observed in  
 quantum electronic
@@
 and current is the analog of particle velocity.
-%DM FIX FOLLOWING SENTENCE
-Known as Shapiro steps, 
-these mode-locked or phase-locked currents
-%arise 
-%due to applied ac voltages
+These mode-locked or phase-locked currents, known as Shapiro steps,
 were first
-observed in single Josephson junctions\cite{Shapiro1963, Golubov2004}.
-%coupled arrays of junctions.\cite{Benz1990}
-%DM END FIX
+observed in single Josephson junctions.\cite{Shapiro1963, Golubov2004}
 Shapiro steps vary in width depending on the strength of the
@@
 with suggested problems for interested readers.
-We discuss the molecular dynamics algorithm
+We discuss the molecular dynamics (MD) algorithm
 and
@@
   using
-  the standard definition of velocity
+  the  definition of velocity
   $\vec{v} = d\vec{r}/dt$ 
-  with the %DM sub ``with'' for using
+  using the 
   Euler method.
-  %DM - fix Equation/Eq. discontinuity
-  Eq.~(\ref{eq:motion}) provides
+  Equation~(\ref{eq:motion}) provides
   a direct calculation for the particle velocity
@@
     to subroutines.
-    %DM - more clearly defined task in active / command tense
-    %We have left as an exercise  the addition
  Define 
@@
 
-\qquad We used the subroutine {\bf single\_particle()}
+\qquad We used the subroutine {\tt single\_particle()}
      to calculate the  lengths of the arrays that contain the 
@@
        time step,
-     calculated in the subroutine {\bf md\_step()}
+     calculated in the subroutine {\tt md\_step()}
      which will be described in more detail in (c).
@@
      short simulations times
-     we could save all data.
+     we could save all the data.
 \begin{verbatim}
@@
   Particle-particle interactions are typically nonlinear,
-  so that the interparticle force changes significantly over small distances and the simple Euler algorithm is insufficient.
+  so that the interparticle force changes significantly over small distances.
+  %and the simple Euler algorithm is insufficient.
+  %[xx we are confused.
+First you say that Euler works for nonlinear equations, and now you say it is insufficient?
+suggest omitting this paragraph  xx] Justifiably!
+The last phrase is wrong.
+Does the paragraph hold if the last phrase was removed, or should the entire paragraph go?
 
@@
 
-\begin{problem}{Exploring model parameters}
+\medskip \begin{problem}{Exploring model parameters}
 \label{ex:parameters}
@@
   Explore the effect of increasing $F_{\rm ac}$ on the hopping pattern.
-  For a single driven particle,
+  For a single  particle,
   the hopping patterns are typically characterized
@@
   For example,
-  calculate the patterns of hops for  
+  compute the patterns of hops for  
   $f=0.01$, $F_{\rm dc}=0.07$, and $A_p = 0.1$
@@
   allowing the particle to hop a substrate maxima.
-  For example fix
-  the parameters
-  $F_{\rm dc}=0.1$, $F_{\rm ac}=0.05$, and $A_p = 0.1$
+  For example, fix 
+  $F_{\rm dc}=0.1$, $F_{\rm ac}=0.05$, and $A_p = 0.1$,
   and explore
@@
   over increments of $\Delta F_{\rm dc} = 0.001$
-  for    $F_{\rm ac}$ and frequency $f=0.01$.
+  for    $F_{\rm ac}$ and  $f=0.01$.
   Appropriate values for 
@@
 
-\noindent Stokes' law describes the drag force
-  $\vec{F}_{\rm lin} = -3 \pi \eta D \vec{v}$ 
+\noindent Stokes' law describes the drag force %xx changed $\vec{F}_{\rm lin}$  to  $\vec{F}_{\rm drag}$     since   you use this notation in Problem 3
+  $\vec{F}_{\rm drag} = -3 \pi \eta D \vec{v}$ 
   on a sphere
@@
   entirely.
-Using Newton's second law for
-  a small momentum relaxation time, 
+Use Newton's second law for
+  a small momentum relaxation time and
   show that a particle confined to a landscape exerting force
@@
   Temperature effects
-  can be modeled by applying randomized forces $f_T$,
-  where $T$ denotes temperature, 
-  %[DM -addressed xx what does the subscript $T$ mean? xx]
-  to the visible particles.
+  can be modeled by applying randomized forces $f_T$ 
+ to the visible particles ($T$ denotes the temperature).
   We use the normal distribution 
@@
 
+ \begin{problem}{Critical Exponents of Depinning}
+   \label{ex:critical}
+
+   \noindent
+   With no oscillating component of the driving force,
+  the force-velocity relation increases monotonically 
+  above the depinning threshold $F_c$ such that
+  \begin{equation}
+    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
+  \end{equation}
+  where the power $\beta$ varies with the
+  type of phase transition and 
+  %can
+  may 
+  be used to identify the universality class.\cite{Reichhardt2017} 
+  The critical force $F_c$ is equal to the maximum substrate force
+  $A_p$.
+   % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
+  %DM - in my experience, we use beta for this parameter.  For example
+  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301
+
+  \end{problem}
+
 \begin{acknowledgments}
@@
 G.
-Okuno and K.
+Okuno, and K.
 Aihara, ``Spatio-temporal dynamics in collective frog choruses examined by mathematical modeling and field observations," Sci.
@@
 Dullens,  ``Dynamic mode locking in a driven colloidal system: Experiments and theory," New J.
-Phys.{\bf 19} (1), 013010-1--14 (2017).
+Phys.
+{\bf 19} (1), 013010-1--14 (2017).
 %https://doi.org/10.1088/1367-2630/aa53cd
@@
 
-  \bibitem{Grier2003} D. G. Grier, ``A revolution in optical manipulation," Nature {\bf 424}, 810 (2003).
+  \bibitem{Grier2003} D. G. Grier, ``A revolution in optical manipulation," Nature {\bf 424}, 810--816 (2003).
 

### 2021-05-05 code/solutions_problems.py
documented problem 6

@@ -6,7 +6,7 @@ Supplementary Material for
 Molecular dynamics simulation of synchronization in driven particles
 American Journal of Physics
 
-Makes Figures 2-9 using a flag to select
+Solutions to Problems 1-6
 
 Danielle McDermott
 Tiare Guerrero
@@ -17,6 +17,8 @@ import math, sys
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import matplotlib.cm as cm
+
+from scipy.optimize import curve_fit
 
 from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
                                AutoMinorLocator)
@@ -31,16 +33,33 @@ plt.rc('font', size=24)
 #main MD routines
 import MD_colloid
 
+#############################################################
+#function that curve_fit will call/fit for problem 6
+#############################################################
+def func(x, a, b, c):
+    '''
+    function to use in scipy optimize curve_fit call
 
+    required arguments
+    x is an independent variable
+    a,b,c are fit parameters which are returned by value
+    
+    returns:
+    popt : array, Optimal values for the parameters so that the sum of the squared residuals of f(xdata, *popt) - ydata is minimized
+    pcov : 2d array, The estimated covariance of popt.
+    '''
+    
+    return a*((x+c)**(-b))
 #-------------------------------------------------------------------
+
 if __name__ == "__main__":
 
     #will pass the parameters dict to subroutines to read constants
     parameters = MD_colloid.set_parameters()
 
     #select which figure in the AJP you would like to make
-    #figures 2a, 2b, 2c, 5
-    solve_problem = "5"
+    #figures 2a, 2b, 2c, 5, 6
+    solve_problem = "6"
 
     parameters['filename']="problem_%s.pdf"%(solve_problem)
 
@@ -212,8 +231,75 @@ if __name__ == "__main__":
         plt.tight_layout(pad=0.1,h_pad=-0.3)
         plt.savefig(parameters['filename'])
         
-    #--------------------------------------------------------------------------
+    #--------------------------------------------------------------
+    #Problem 6
+    #Fit depinning exponent using data from Fig. 3
+    #--------------------------------------------------------------
+    if solve_problem == "6":
 
+        #substrate height
[…]

### 2021-05-05 code/solutions_problems.py
moved ex. 3 to solutions

@@ -6,7 +6,7 @@ Supplementary Material for
 Molecular dynamics simulation of synchronization in driven particles
 American Journal of Physics
 
-Solutions to Problems 1-6
+Solutions to Problems 2,3,5,6
 
 Danielle McDermott
 Tiare Guerrero
@@ -183,6 +183,34 @@ if __name__ == "__main__":
                     
         plt.tight_layout(pad=0.2)
         plt.savefig(parameters['filename'])
+
+    #--------------------------------------------------------------
+    #calculate the approximate Reynolds number
+    #at standard temperature and pressure, converted to SI units (i.e. m-kg-sec)
+
+    if solve_problem == "3":
+
+        D = 1e-6 #micrometer
+        rho = 0.9982 * 1e-3 * 1e6 #g/cm^3  1g=10^-3kg, 1/cm^3*(100cm/1m)^3
+        v = 1e-6 #micrometer / sec
+
+        #"kinematic viscosity" - not the right units
+        #eta = 0.01 #cm^2 / sec
+
+        #"dynamics viscosity" - same units as Taylor
+        eta = 1.0016e-3 #mPa *sec = mN/m^2 *sec
+
+
+        #unit check:  m*m/sec*kg/(m^3)*1/(N/m^2*sec)
+        #blech! 
+        #unit check:  kg/m * m^2 / (N*sec^2) 
+        #unit check:  m*kg / (N*sec^2) = m*kg / (kg*m s^2 /s^2)
+        #kg cancels!  m cancels! s^2 cancels!
+        #unitless Reynold's number
+
+
+        R = D*v*rho/eta
+        print("The Reynolds number is: ",R)
         
     #--------------------------------------------------------------
     #study Brownian motion for increasing temperature

### 2021-05-05 manuscript/manuscript_ajp_version4b.tex
final version - includes problem 6

@@
   $A_p$.
+  %DM ADD
+  We demonstrate how to fit our data to this model in Problem~\ref{ex:critical}.
+  %DM end
   % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
@@
    \noindent
-   With no oscillating component of the driving force,
-  the force-velocity relation increases monotonically 
-  above the depinning threshold $F_c$ such that
+   In Fig.~\ref{fig:3_sweep_vyFDC}
+   we show the force-velocity relation when
+   the driving force has 
+   no oscillating component.
+   The data can be fit with a model 
    \begin{equation}
@@
    \end{equation}
-  where the power $\beta$ varies with the
-  type of phase transition and 
-  %can
-  may 
-  be used to identify the universality class.\cite{Reichhardt2017} 
-  The critical force $F_c$ is equal to the maximum substrate force
-  $A_p$.
-   % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
-  %DM - in my experience, we use beta for this parameter.  For example
-  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301
+   where
+   the critical force is $F_c$ and 
+   the power $\beta$ varies with the
+   type of phase transition.
+   For elastic depinning, a
+   typical value of $\beta$ is
+   approximately $\beta = 2/3$.\cite{Reichhardt2017}
+
+   Given the data generated in 
+   a non-oscillatory drive $F_{\rm ac} = 0$,
+   fit the data and find the critical exponent $\beta$.
+   The Python SciPy optimize package has curve fit routine
+   suitable for this purpose.  
+   %For the data in Fig.~\ref{fig:3_sweep_vyFDC}, 
+   %we obtained $\beta = 0.625 \pm 0.003$ 
+   %and $F_c = 0.0980 \pm 0.0001$.
+   %is equal to the maximum substrate force
+   %$A_p = 0.1$.
+   Explore how $\beta$ and $F_c$ vary as $A_p$
+   is tuned to higher and lower values.
 
